### 2024-11-11 latex/main.tex
Add files via upload
修改main.tex

%!TEX program = xelatex
% 编译顺序: xelatex -> bibtex -> xelatex -> xelatex
% 国家自然科学基金NSFC面上项目申请书正文模板（2023年版）version1.0
% 声明：
% 注意！！！非国家自然科学基金委官方模版！！！由个人根据官方MsWord模版制作。本模版的作者尽力使本模版和官方模版生成的PDF文件视觉效果大致一样，然而，并不保证本模版有用，也不对使用本模版造成的任何直接或间接后果负责。 不得将本模版用于商用或获取经济利益。本模版可以自由修改以满足用户自己的需要。但是如果要传播本模版，则只能传播未经修改的版本。使用本模版意味着同意上述声明。
% 强烈建议自己对照官方MsWord模板确认格式和文字是否一致，尤其是蓝字部分。
% 如有问题，可以发邮件到ryanzz@foxmail.com

\documentclass[12pt,UTF8,AutoFakeBold=2,a4paper]{ctexart} %默认小四号字。允许楷体粗体。
\usepackage[english]{babel} %支持混合语言
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx} 
\usepackage{amsmath} %更多数学符号
\usepackage{wasysym}
\usepackage[unicode]{hyperref} %提供跳转链接
\usepackage{geometry} %改改尺寸
\usepackage{gbt7714}
\usepackage{natbib}
\setlength{\bibsep}{0.0pt}

%\geometry{left=3.23cm,right=3.23cm,top=2.54cm,bottom=2.54cm}
%latex的页边距比word的视觉效果要大一些，稍微调整一下
%\geometry{left=2.95cm,right=2.95cm,top=2.54cm,bottom=2.54cm}%2020
%\geometry{left=2.95cm,right=2.95cm,top=2.54cm,bottom=2.54cm}
\geometry{left=3.00cm,right=3.07cm,top=2.67cm,bottom=3.27cm}
\pagestyle{empty}
\setcounter{secnumdepth}{-2} %不让那些section和subsection自带标号，标号格式自己掌握
\definecolor{MsBlue}{RGB}{0,112,192} %Ms Word 的蓝色和latex xcolor包预定义的蓝色不一样。通过屏幕取色得到。
% Renaming floats with babel
\addto\captionsenglish{
    \renewcommand{\contentsname}{目录}
    \renewcommand{\listfigurename}{插图目录}
    \renewcommand{\listtablename}{表格}
    %\renewcommand{\refname}{\sihao 参考文献}
    \renewcommand{\refname}{\sihao \kaishu \leftline{参考文献}} %这几个字默认字号稍大，改成四号字，楷书，居左(默认居中) 根据喜好自行修改，官方模板未作要求
    \renewcommand{\abstractname}{摘要}
    \renewcommand{\indexname}{索引}
    \renewcommand{\tablename}{表}
    \renewcommand{\figurename}{图}
    } %把Figure改成‘图’，reference改成‘参考文献’。如此处理是为了避免和babel包冲突。
%定义字号
\newcommand{\chuhao}{\fontsize{42pt}{\baselineskip}\selectfont}
\newcommand{\xiaochuhao}{\fontsize{36pt}{\baselineskip}\selectfont}
\newcommand{\yihao}{\fontsize{26pt}{\baselineskip}\selectfont}
\newcommand{\erhao}{\fontsize{22pt}{\baselineskip}\selectfont}
\newcommand{\xiaoerhao}{\fontsize{18pt}{\baselineskip}\selectfont}
\newcommand{\sanhao}{\fontsize{16pt}{\baselineskip}\selectfont}
\newcommand{\sihao}{\fontsize{14pt}{\baselineskip}\selectfont}
\newcommand{\xiaosihao}{\fontsize{12pt}{\baselineskip}\selectfont}
\newcommand{\wuhao}{\fontsize{10.5pt}{\baselineskip}\selectfont}
\newcommand{\xiaowuhao}{\fontsize{9pt}{\baselineskip}\selectfont}
\newcommand{\liuhao}{\fontsize{7.875pt}{\baselineskip}\selectfont}
\newcommand{\qihao}{\fontsize{5.25pt}{\baselineskip}\selectfont}
%字号对照表
%二号 21pt
%四号 14
%小四 12
%五号 10.5
%设置行距 1.5倍
\renewcommand{\baselinestretch}{1.5}
\XeTeXlinebreaklocale "zh"           % 中文断行

%%%% 正文开始 %%%%
\begin{document}
\begin{center}
{\sanhao \kaishu \bfseries  Hybrid ANNS }
\end{center}

\section{Filtered−DiskANN}
\subsection{1.主要贡献：}
{\sihao \kaishu 本文的主要贡献是两种简单而有效的基于图的过滤 ANNS 算法 - FilteredVamana 和 StitchedVamana，这两种算法均基于Vamana图构建，该图通过创建一个可导航的图结构来高效引导局部“贪心”搜索，使其朝向查询点的最近邻候选者。与现有算法不同，本算法不仅考虑数据集中点的空间位置（即向量坐标），还利用了点的过滤元数据信息。通过结合点之间的几何关系和每个点的标签信息，这两种算法能够构建出更优的图导航结构，从而在近似最近邻搜索中实现更高的效率和准确性。。}

\subsection{2.实现原理：}
\subsubsection{2.1 filteredVamana：}
{\sihao \kaishu filteredVamana图构造属于增量式构建。初始化空图G，为每个过滤标签选择一组起点S，从S出发，对于每个数据点p运行贪婪搜索算法FilteredGreedySearch，从而返回访问顶点集合（集合中所有顶点都具有该过滤标签）。}
{\sihao \kaishu 当搜索过程中某个点的出度超过规定范围，使用剪枝算法FilteredRobustPrune修剪。 }

\subsubsection{2.2 stitchedVamana：}
{\sihao \kaishu 如图\ref{fig:1}所示，对于每一个过滤标签f，构建对应的vamana图，然后将这些图合并（边集取并）成一个图G，G与filteredVamana所构建的图兼容。它只能在提前知道点集的情况下使用，无法实现增量式构建。}
\begin{figure}[!th]
\begin{center}
\includegraphics[width=5in]{stitchedvamana.png}
\caption{{\kaishu stitchedVamana实现原理}}
\label{fig:1}
\end{center}
\end{figure}
\subsubsection{2.3 比较：}
{\sihao \kaishu filteredVamana：能够通过点插入实现动态索引增长。稳健性更好，索引构建时间更快。}

{\sihao \kaishu stitchedVamana：不能实现动态索引增长。QPS和召回率表现更好。}

\subsection{3.优势：}
{\sihao \kaishu （1）索引构建时，不仅考虑点的向量坐标，也考虑过滤标签，真正将过滤信息融合在图索引构建中。}

{\sihao \kaishu （2）filteredVamana支持在SSD上查询，节约内存。}

{\sihao \kaishu （3）稀疏属性不受影响。}

{\sihao \kaishu （4）filteredVamana支持动态插入。}

\subsection{4.缺陷：}
{\sihao \kaishu 本方法无法支持任意复杂的过滤条件，而只能支持简单枚举型条件，可以支持多个条件的OR，但是不支持AND。专注于单个过滤器与查询相关联的情况。}

{\section{NHQ 算法}}
{\subsection{ 1.1 概述}}
本文通过提出融合距离来实现混合索引，以便在查询过程中同时支持特征向量和属性约束，而不是像传统方法那样将查询分解为独立的向量相似性搜索和属性过滤两个子任务；还提出了两种新颖的可导航近邻图，它们采用优化的边选择和路由策略，从而显著提高了混合查询的整体性能。

{\subsection{1.2具体实现}}
NHQ 提出了融合距离来实现原生的混合查询框架，融合距离定义如~\ref{eq:merged_distance}所示，其中的$\chi\left(\ell\left(e_i\right), \ell\left(e_j\right)\right)$表示标签距离，用于描述两个对象之间的标签是否相同，通过计算其相同的属性数来获得，如~\ref{eq:lable_dist}和~\ref{eq:lable_dist2}所示.

\begin{equation}
\chi\left(\ell\left(e_i\right), \ell\left(e_j\right)\right)=\sum_{k=0}^{m-1} \phi\left(\ell\left(e_i\right)^k, \ell\left(e_j\right)^k\right)
    \label{eq:lable_dist}
\end{equation}
\begin{equation}
\phi\left(\ell\left(e_i\right)^k, \ell\left(e_j\right)^k\right)= \begin{cases}0, & \ell\left(e_i\right)^k=\ell\left(e_j\right)^k \\ 1, & \ell\left(e_i\right)^k \neq \ell\left(e_j\right)^k\end{cases}
    \label{eq:lable_dist2}
\end{equation}

\begin{equation}
\Gamma\left(e_i, e_j\right)=\omega_\nu \cdot \delta\left(\nu\left(e_i\right), \nu\left(e_j\right)\right)+\omega_{\ell} \cdot \chi\left(\ell\left(e_i\right), \ell\left(e_j\right)\right)
\label{eq:merged_distance}
\end{equation}

在公式 $1-2$ 中，$m$ 是 $\ell\left(e_i\right)$ 的维度数量，$\ell\left(e_i\right)^k$ 表示 $\ell\left(e_i\right)$ 在第 $k$ 个维度上的取值。$\chi\left(\ell\left(e_i\right), \ell\left(e_j\right)\right)$ 越小，$\ell\left(e_i\right)$ 与 $\ell\left(e_j\right)$ 的相似度越高。

通过融合距离的定义，NHQ算法可以在索引构建时直接考虑向量相似度和标签相似度，构建出PG混合索引，直接在该索引上进行混合查询，而不需要额外的计算和内存开销。并且，该框架对PG图支持友好，可以将融合距离用于其他PG图，从而达到混合查询的效果。

除了原生的混合查询框架，文中还提出了新的边缘选择策略以及路由策略来实现可导航近邻图。由于PG图直接选取最近的点作为邻居可能会导致邻居聚集在一起，搜索时探索区域有限。文中提出了新的边缘选择策略来解决邻居分布聚集的问题，在选择邻居时，首先选取最近的，之后通过远点和邻居节点的垂直平分线分割出原点所在区域，以及原点和邻居节点的距离为半径画的圆外的区域，两个区域的交集定义为着陆区，新的邻居必须从着陆区选取，循环选取邻居，从而实现邻居分布均匀。如图\ref{fig:edge}所示。
\begin{figure}[h] % 这里的 [h] 表示将图片放在当前位置（here）
    \centering % 使图片居中
    \includegraphics[width=1\textwidth]{edge_selection.pdf} % 调整图片的宽度，并插入图片文件
    \caption{边选择策略}
    \label{fig:edge} % 设置图片的标签，以便引用
\end{figure}

边选择策略使得邻居分布均匀，随机两阶段路由策略则加速搜索过程。文中提出的两阶段路由策略在最开始时，随机选取部分点进行探索，当靠近目标点之后，再进行贪心策略进行搜索，从而减少访问点的次数以及计算量。

{\subsection{1.3优势}}
目前的混合查询方法基本采用分别维护两个索引的方式来进行混合查询，在查询时先进行向量相似化搜索，之后再进行属性过滤，或者顺序相反；但同时维护两个索引的方法，会产生不必要的内存花销和计算，查询结果依赖于两个结果的合并，可能不精确，对现有的PG图支持也不是很友好，没能利用PG图的优势。NHQ通过使用其融合距离，在构建索引时同时考虑向量相似度和标签，只用构建一个索引即可完成混合查询，且兼容大部分的PG图，提出了原生的混合查询框架，并且查询时，尽可能的满足多标签，而不是只满足其中一个，有着不错的效果。

{\subsection{1.4缺陷}}
论文提出的融合距离，实现了原生的混合查询框架，适用于大部分PG图，同时正对PG图，又提出了新的边缘选择策略以及路由策略，以此来加快搜索，二者结合，再最终的实验表现上有着很好的结果。但NHQ考虑的设置是每个数据点实际上只有一个相关的过滤器标签，即一一类标签下，各标签点的集合不相交，这种情况可以通过每个过滤器的单独标准 ANNS 索引来处理。此外，这种技术在缩放到每个点多个过滤器/标签时可能无效，而不显著影响召回。如果索引中的一个点有三个过滤器标签，而查询只有一个，则其他两个标签中的距离会对总的距离产生不利影响。

% {\sihao \kaishu 参照以下提纲撰写，要求内容翔实、清晰，层次分明，标题突出。{\color{MsBlue} \bfseries 请勿删除或改动下述提纲标题及括号中的文字。}}
% \vskip -5mm
% {\color{MsBlue} \subsection{\sihao \kaishu \quad \ （一）立项依据与研究内容(建议8000字以下)： }}

% {\sihao \kaishu \color{MsBlue} 1.{\bfseries 项目的立项依据}（研究意义、国内外研究现状及发展动态分析，需结合科学研究发展趋势来论述科学意义；或结合国民经济和社会发展中迫切需要解决的关键科技问题来论述其应用前景。附主要参考文献目录）；}

% 对于习惯用 \LaTeX 写文档的老师和同学们，一个写基金申请书的模版可能有参考作用。因此我做了这个{\bfseries \color{Bittersweet} 面上项目}申请书正文部分模版，供参考。

% 2023-01-20： 根据2023年面上项目申请书正文的官方MsWord模板，对本模板的字号和少量蓝色文字做了更新。

% 2023-01-29\&02-01： 根据几位老师的建议，对section的缩进，“参考文献”四个字的大小、字体和居左等做了调整。官方模板中阿拉伯数字不加粗，因此也做了相应的调整。

% \begin{figure}[!th]
% \begin{center}
% \includegraphics[width=2in]{fig-example.eps}
% \caption{{\kaishu 插图可以使用EPS、PNG、JPG等格式。}}
% \label{fig:example}
% \end{center}
% \end{figure}

% 2023-02-06： 根据@Readon的commits，做了如下修改：1. 更正了一处蓝字部分：``（三）其他需要说明的问题'' $\rightarrow$ ``（三）其他需要说明的情况'' 。这个非常重要！2. 设置 AutoFakeBold=3，这样楷体粗体稍微细一点，和官方模板更加接近。3. 调整了页面空白的宽度，大家可以自行微调。作为\LaTeX 菜鸟，非常感谢Readon的专业建议！更多专业的修改请见\url{https://github.com/Readon/NSFC-application-template-latex}

% 2023-12-04：一转眼2024年的申请又要开始了。主要做了两点修改：1. 把图的caption字体调整为楷体。2. 设置AutoFakeBold=2，个人感觉这样和MsWord模板中的粗体更接近一点。等官方模板更新之后我再做相应更新。

% 2023-12-30：改用GB/T 7714 (numerical) 样式以支持中文文献。 这样做的另外一个优点是该包兼容natbib，修改参考文献的行距也比较方便，这里也缩短了一些。如有需要，也可以切换回ieeetrNSFC。

% \vskip 2mm
% \subsubsection{1.1 声明}
% {\bfseries \color{red} 注意！！！非国家自然科学基金委官方模版！！！}由个人根据官方MsWord模版制作。本模版的作者尽力使本模版和官方模版生成的PDF文件视觉效果大致一样，然而，并不保证本模版有用，也不对使用本模版造成的任何直接或间接后果负责。 不得将本模版用于商用或获取经济利益。本模版可以自由修改以满足用户自己的需要。但是如果要传播本模版，则只能传播未经修改的版本。使用本模版意味着同意上述声明。

% 祝大家基金申请顺利！如有问题，请发送邮件到 \href{mailto:ryanzz@foxmail.com}{ryanzz@foxmail.com}。中了基金的也欢迎反馈。$\smiley$

% \subsubsection{1.2 使用说明}\label{sss:instruction}

% \begin{enumerate}
% \item 编译环境：推荐使用跨平台编译器texlive2017以后的版本，编译顺序为：xelatex+bibtex+xelatex(x2)。windows用户可以用命令行运行批处理文件getpdf.bat，linux用户可以运行runpdf。
% \item 本模版力求简单，语句自身说明问题(self explanatory）。几乎只需要修改本tex文件即可满足排版需求，没有sty cls 等文件。用户掌握最基本的\LaTeX 语句即可操作，其余的可以用搜索引擎较容易地获得。
% \item 参考文献样式：从2023.12.30版本开始，采用GB/T 7714 (numerical) 样式以支持中文文献，这样做的另外一个优点是该包兼容natbib，修改参考文献的行距也比较方便，缩短了一些。如有需要，也可以切换回ieeetrNSFC。
% \end{enumerate}

% \subsubsection{1.3 图、公式和参考文献的引用示例}
% 尽管不大可能会用到像下面这样简单的公式：
% \begin{equation}
% \label{eq:ex}
% \sqrt[15]{a}=\frac{1}{2},
% \end{equation}
% 我们还是用公式(\ref{eq:ex})举个数学公式的例子。同时，我们也不大可能会用到一个长得很像\LaTeX 的图，但是还是引用一下图\ref{fig:example}。图\ref{fig:example}并没有告诉我们关于Jinkela\cite{John1997,Smith1900}的任何信息，也没有透露它的产地\cite{Piter1992,grif1998}。尽管如此，最近的研究表明，Feizhou非常需要Jinkela\cite{John1997}。

% %从2023.12.30版本开始，采用GB/T 7714 (numerical) 样式以支持中文文献，这样做的另外一个优点是该包兼容natbib，修改参考文献的行距也比较方便，缩短了一些。如有需要，也可以切换回之前版本用的ieeetrNSFC
% %\newpage
% %\bibliographystyle{ieeetrNSFC}
% \bibliographystyle{gbt7714-numerical}
% \bibliography{myexample}
% \newpage

% {\sihao \color{MsBlue} \kaishu 2． {\bfseries 项目的研究内容、研究目标，以及拟解决的关键科学问题}（此部分为重点阐述内容）；}

% 本项目的{\bfseries 研究目标}是获得申请面上项目的\LaTeX 模版。

% 拟解决的{\bfseries 关键问题}包括：

% \begin{itemize}
% \item 中文的处理。
% \item 参考文献\cite{John1997,Smith1900,Piter1992}的样式。
% \item 官方word模版中蓝色的获得。
% \end{itemize}

% {\sihao \color{MsBlue} \kaishu 3．{\bfseries 拟采取的研究方案及可行性分析} （包括研究方法、技术路线、实验手段、关键技术等说明）；}

% 详见1.2使用说明。

% {\sihao \color{MsBlue} \kaishu 4．{\bfseries 本项目的特色与创新之处；}}

% 本模版修改自由度很高，可以按照用户自己的需求修改而不要求用户具有很多\LaTeX 技巧。

% {\sihao \color{MsBlue} \kaishu 5．{\bfseries 年度研究计划及预期研究结果}（包括拟组织的重要学术交流活动、国际合作与交流计划等）。}

% 拟组织研讨会1次，将这个模版广而告之。但是目前还没有经费。

% \vskip -5mm %可以通过类似的命令微调行距以使得排版美观

% {\color{MsBlue} \subsection{\sihao \kaishu \quad \ （二）研究基础与工作条件 }}

% {\sihao \color{MsBlue} \kaishu 1．{\bfseries 研究基础}（与本项目相关的研究工作积累和已取得的研究工作成绩）；}

% 申请人用\LaTeX 写过几篇文章，包括自己的博士论文。

% {\sihao \color{MsBlue} \kaishu 2．{\bfseries 工作条件}（包括已具备的实验条件，尚缺少的实验条件和拟解决的途径，包括利用国家实验室、国家重点实验室和部门重点实验室等研究基地的计划与落实情况）；}

% 申请人课题组具有可以编译 \LaTeX 的计算机，可以成功编译此模版。

% {\sihao \color{MsBlue} \kaishu 3．{\bfseries 正在承担的与本项目相关的科研项目情况}（申请人和主要参与者正在承担的与本项目相关的科研项目情况，包括国家自然科学基金的项目和国家其他科技计划项目，要注明项目的资助机构、项目类别、批准号、项目名称、获资助金额、起止年月、与本项目的关系及负责的内容等）；}

% 无。

% {\sihao \color{MsBlue} \kaishu 4．{\bfseries 完成国家自然科学基金项目情况}（对申请人负责的前一个已资助期满的科学基金项目（项目名称及批准号）完成情况、后续研究进展及与本申请项目的关系加以详细说明。另附该项目的研究工作总结摘要（限500字）和相关成果详细目录）。}

% 不告诉你。

% {\color{MsBlue} \subsection{\sihao \kaishu \quad \ （三）其他需要说明的情况 }}

% {\sihao \color{MsBlue} \kaishu 1. 申请人同年申请不同类型的国家自然科学基金项目情况（列明同年申请的其他项目的项目类型、项目名称信息，并说明与本项目之间的区别与联系）。 }

% 无。

% {\sihao \color{MsBlue} \kaishu 2. 具有高级专业技术职务（职称）的申请人或者主要参与者是否存在同年申请或者参与申请国家自然科学基金项目的单位不一致的情况；如存在上述情况，列明所涉及人员的姓名，申请或参与申请的其他项目的项目类型、项目名称、单位名称、上述人员在该项目中是申请人还是参与者，并说明单位不一致原因。}

% 无。

% {\sihao \color{MsBlue} \kaishu 3. 具有高级专业技术职务（职称）的申请人或者主要参与者是否存在与正在承担的国家自然科学基金项目的单位不一致的情况；如存在上述情况，列明所涉及人员的姓名，正在承担项目的批准号、项目类型、项目名称、单位名称、起止年月，并说明单位不一致原因。}

% 无。

% {\sihao \color{MsBlue} \kaishu 4. 其他。}

% 无。
\end{document}

### 2025-02-10 latex/main.tex
add vabse latex

@@
 
+{\section{VBASE系统}}
+{\subsection{1.概述}}
+本文介绍了VBASE系统，它基于PostgreSQL数据库，它能够高效支持包含近似相似性搜索和关系运算符的复杂查询。论文发现，向量索引系统普遍遵循一种两阶段模式，并用数学公式的形式，正式定义了松弛单调性的概念，它抽象了大多数现有向量索引的核心遍历模式。借助松弛单调性，VBASE构建了一个统一的查询执行引擎，它基于Next接口而非TopK接口，以支持向量和标量索引的遍历。同时，该引擎通过松弛单调性推导出通用的终止条件，从而能够及时停止查询执行。此外，凭借松弛单调性，VBASE甚至可以支持以前系统无法处理的近似查询类型，并展现出更优的查询性能和准确性。
+{\subsection{2.实现细节}}
+{\subsubsection{2.1 Relax Monotonicity Definition}}
+论文展示了几种向量索引，包括基于图结构的（如hnsw）和基于分区的（如FAISS IVFFlat），他们的遍历过程都满足两阶段的性质，第一阶段，尽管向量距离波动较大，但索引遍历大致接近目标向量区域。在第二阶段，索引遍历趋于稳定，并以近似方式逐渐远离目标向量区域。且不仅仅是这两种索引结构，凡是经过精心设计的向量索引都应该满足两阶段。
+基于两阶段遍历模式，我们可以正式定义松弛单调性，如图\ref{fig:3}，用以判断向量索引遍历是否进入了第二阶段。
+
+正式地，\( R_q \)，即\( q \)邻域的半径，被定义为：
+\begin{equation}
+    R_q = \max\left(\text{TopE}\left(\left\{\text{Distance}(q, v_j) \mid j \in [1, s - 1] \right\}\right)\right)\tag{1}
+\end{equation}
+
+\( M_{q}^{s} \) 被定义为在最近 \( w \) 步内遍历的所有向量到 \( q \) 的中位距离，即遍历窗口：
+\begin{equation}
+    M_{q}^{s} = \text{Median}\left(\left\{\text{Distance}(q, v_i) \mid i \in [s - w + 1, s]\right\}\right) \tag{2}
+\end{equation}
+
+结合公式 (1) 和公式 (2)，我们定义松弛单调性（Relaxed Monotonicity）为：
+\begin{equation}
+    \exists s, \ M_{q}^{t} \geq R_{q}, \ \forall t \geq s. \tag{3}
+\end{equation}
+\begin{figure}[!th]
+\begin{center}
+\includegraphics[width=5in]{Relaxed Monotonicity.png}
+\caption{{ An Illustration of Relaxed Monotonicity’s intuition.}}
+\label{fig:3}
+\end{center}
+\end{figure}
+{\subsubsection{2.2 Unified Query Execution Engine}}
+借助松弛单调性，VBASE在传统数据库引擎的基础上构建了一个统一的查询执行引擎。VBASE完全遵循Volcano模型，重用了传统的Open、Next和Close接口，无需对传统的索引进行修改。对于仅支持TopK接口的向量索引，VBASE进行简单调整，使其能够公开内部索引遍历过程，以符合VBASE的Next接口。
+
+统一引擎为向量查询带来了新的优化机会，例如，VBASE可以在索引遍历过程中进行过滤，而不是在TopK之后再过滤，通过灵活的终止条件（用于TopK或范围查询）提高效率。一旦索引遍历通过上游索引扫描操作符中的松弛单调性检查，并且优先队列中填满了K个向量，TopK查询即终止。
+
+{\subsection{3.优点}}
+1. VBASE克服了TopK接口的限制，将属性过滤融入索引遍历过程
+
+2. 提出松弛单调性的概念，揭示了优秀向量索引设计的核心以及其在实践中有效运作的原因。
+
+3. 证明了VBASE的统一引擎和向量索引的TopK-only方法等效的结构
+
+4. VBASE原生支持了多列向量查询和范围过滤查询，这是之前的向量数据库系统所不支持的
+
+{\subsection{4.缺点}}
+1. 一经编译，就不允许调参来修改向量索引的性能
+
+2. 实现复杂度高，VBASE的参数（例如遍历窗口 w 和候选结果数量 E）需要根据数据分布和查询需求进行调整，这可能需要多次调试和优化。
+
 % {\sihao \kaishu 参照以下提纲撰写，要求内容翔实、清晰，层次分明，标题突出。{\color{MsBlue} \bfseries 请勿删除或改动下述提纲标题及括号中的文字。}}

### 2025-02-10 Results/Label-Filter/faiss+HQI_batch/1.py
添加多个SPTAG和faiss+HQI_batch的CSV结果文件

@@ -1,0 +1,36 @@
+import os
+import pandas as pd
+
+# 获取当前目录下所有的文件
+for filename in os.listdir('.'):
+    # 排除 Python 脚本文件 (.py) 和没有.csv后缀的文件
+    if filename.endswith('.py'):
+        continue
+
+    try:
+        # 读取CSV文件
+        df = pd.read_csv(filename, encoding='utf-8-sig')
+
+        # 去除列名中的多余空格
+        df.columns = df.columns.str.strip()
+
+        # 打印列名确认
+        print(f"正在处理文件: {filename}")
+        print(f"列名: {df.columns}")
+
+        # 只保留后两列
+        df_filtered = df[['QPS', 'Recall@k10']]
+
+        # 构建新的文件名
+        new_filename = f'{filename}_faiss-ivf.csv'
+
+        # 保存结果到新的CSV文件
+        df_filtered.to_csv(new_filename, index=False)
+
+        # 删除原始文件
+        os.remove(filename)
+
+        print(f"{filename} 已处理，结果已保存到 {new_filename}")
+    
+    except Exception as e:
+        print(f"处理 {filename} 时出错: {e}")

### 2025-04-01 VLDB2026/main.tex
create paper

% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template

\documentclass[sigconf, nonacm]{acmart}
\usepackage{fontspec}
\usepackage{balance}
\usepackage{xeCJK}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{svg} % For SVG support
\usepackage{graphicx}
\usepackage{microtype}  %处理换行

\usepackage{subcaption} % 需要subcaption宏包支持子图
% \newtheorem{definition}{DEFINITION} % 定义“定义”环境
% % \newtheorem{example}{例} % 定义“例”环境，不与“定义”共享编号
% %% The following content must be adapted for the final version
% % paper-specific
\newcommand\vldbdoi{XX.XX/XXX.XX}
\newcommand\vldbpages{XXX-XXX}
% issue-specific
\newcommand\vldbvolume{14}
\newcommand\vldbissue{1}
\newcommand\vldbyear{2020}
% should be fine as it is
\newcommand\vldbauthors{\authors}
\newcommand\vldbtitle{\shorttitle} 
% leave empty if no availability url should be set
\newcommand\vldbavailabilityurl{URL_TO_YOUR_ARTIFACTS}
% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
\newcommand\vldbpagestyle{plain}

\begin{document}
\begin{sloppypar}

\title{An Experimental Evaluation of Hybrid Query Algorithms}

%%
%% The "author" command and its associated commands are used to define the authors and their affiliations.
% \author{Ben Trovato}
% \affiliation{%
%   \institution{Institute for Clarity in Documentation}
%   \streetaddress{P.O. Box 1212}
%   \city{Dublin}
%   \state{Ireland}
%   \postcode{43017-6221}
% }
% \email{trovato@corporation.com}

% \author{Lars Th{\o}rv{\"a}ld}
% \orcid{0000-0002-1825-0097}
% \affiliation{%
%   \institution{The Th{\o}rv{\"a}ld Group}
%   \streetaddress{1 Th{\o}rv{\"a}ld Circle}
%   \city{Hekla}
%   \country{Iceland}
% }
% \email{larst@affiliation.org}

% \author{Valerie B\'eranger}
% \orcid{0000-0001-5109-3700}
% \affiliation{%
%   \institution{Inria Paris-Rocquencourt}
%   \city{Rocquencourt}
%   \country{France}
% }
% \email{vb@rocquencourt.com}

% \author{J\"org von \"Arbach}
% \affiliation{%
%   \institution{University of T\"ubingen}
%   \city{T\"ubingen}
%   \country{Germany}
% }
% \email{jaerbach@uni-tuebingen.edu}
% \email{myprivate@email.com}
% \email{second@affiliation.mail}

% \author{Wang Xiu Ying}
% \author{Zhe Zuo}
% \affiliation{%
%   \institution{East China Normal University}
%   \city{Shanghai}
%   \country{China}
% }
% \email{firstname.lastname@ecnu.edu.cn}

% \author{Donald Fauntleroy Duck}
% \affiliation{%
%   \institution{Scientific Writing Academy}
%   \city{Duckburg}
%   \country{Calisota}
% }
% \affiliation{%
%   \institution{Donald's Second Affiliation}
%   \city{City}
%   \country{country}
% }
% \email{donald@swa.edu}
\author{Ben Trovato$^1$, Lars Th{\o}rv{\"a}ld$^2$, Valerie B\'eranger$^3$, J\"org von \"Arbach$^3$, Wang Xiu Ying$^3$, Donald Fauntleroy Duck$^3$}

\affiliation{%
  \institution{1. Institute for Clarity in Documentation, Ireland}
  \institution{2. The Th{\o}rv{\"a}ld Group, Iceland}
  \institution{3. Inria Paris-Rocquencourt, France}
}

\email{trovato@corporation.com, larst@affiliation.org, vb@rocquencourt.com, jaerbach@uni-tuebingen.edu, firstname.lastname@ecnu.edu.cn, donald@swa.edu}

%
% The abstract is a short summary of the work to be presented in the
% article.
\begin{abstract}
% Approximate Nearest Neighbor (ANN) search is a foundational technique in fields such as recommendation systems and information retrieval. However, in practical applications, users not only expect search results to be similar to the query in vector space but also to satisfy specific constraints, such as price ranges or categories. To meet these demands, researchers have proposed various hybrid query algorithms, including attribute filtering and range filtering. However, especially for attribute filtering, existing datasets often lack attribute values, and different researchers use varied testing configurations with simplified attribute value settings in their evaluations. Therefore, we select multiple real-world datasets and generate rich attribute values for various query scenarios, establishing a unified and comprehensive evaluation framework to compare these algorithms. Our study establishes a systematic taxonomy of hybrid query algorithms, exhaustively evaluates their time-space tradeoffs, performance, and robustness, and ultimately provides practical recommendations for different application scenarios.

Recent studies have shown that hybrid queries, including attribute filtering and range filtering, hold significant practical value. However, current evaluation efforts lack a unified benchmark and comprehensive testing. Existing research has failed to cover mainstream algorithms and has not systematically compared or deeply analyzed different methods. To address this issue, we have designed a complete evaluation framework for hybrid queries. Our study introduces more than ten hybrid query algorithms and systematically classifies them based on multiple dimensions such as index structure and filtering strategy, providing a reference for the categorization of hybrid queries. In the experimental section, for attribute filtering, we constructed standardized attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness. For range filtering, we systematically tested the algorithms' performance in these three aspects by varying the query ranges. Additionally, we conducted an in-depth analysis of the experimental results based on the underlying principles of the algorithms. The extensive experimental results reveal the strengths and weaknesses of each algorithm. Based on these findings, we have developed a set of practical guidelines for algorithm selection, offering reliable references for different application scenarios. Furthermore, we have identified potential directions for improvement to address the current limitations of these algorithms.
\vspace{-0.2cm}
\end{abstract}

\maketitle

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\pagestyle{\vldbpagestyle}
\begingroup\small\noindent\raggedright\textbf{PVLDB Reference Format:}\\
\vldbauthors. \vldbtitle. PVLDB, \vldbvolume(\vldbissue): \vldbpages, \vldbyear.\\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
\vspace{-0.1cm}
\endgroup
\begingroup
\renewcommand\thefootnote{}\footnote{\noindent
This work is licensed under the Creative Commons BY-NC-ND 4.0 International License. Visit \url{https://creativecommons.org/licenses/by-nc-nd/4.0/} to view a copy of this license. For any use beyond those covered by this license, obtain permission by emailing \href{mailto:info@vldb.org}{info@vldb.org}. Copyright is held by the owner/author(s). Publication rights licensed to the VLDB Endowment. \\
\raggedright Proceedings of the VLDB Endowment, Vol. \vldbvolume, No. \vldbissue\ %
ISSN 2150-8097. \\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi} \\
}\addtocounter{footnote}{-1}\endgroup
%%% VLDB block end %%%

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\ifdefempty{\vldbavailabilityurl}{}{
\vspace{.3cm}
\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
The source code, data, and/or other artifacts have been made available at \url{https://github.com/zhujx001/Hybrid-ANNS}.
\endgroup
}
%%% VLDB block end %%%

\section{Introduction}

Nearest Neighbor (NN) search \cite{cover1967nearest}aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems  \cite{monolith, Airbnb, Related_Pins_at_Pinterest, wang2018billion, pal2020pinnersage, okura2017embedding}  and image retrieval \cite{wang2012scalable}.
% 需要添加引用，下面这段
However, with the exponential growth of data volume and the increasing dimensionality of vectors \cite{weber1998quantitative}, traditional NN search methods struggle to meet the demands of real-time search. To address this issue, researchers have turned to more efficient approaches—Approximate Nearest Neighbor search ~\cite{arya1998optimal,beis1997shape,gionis1999similarity,malkov2018efficient}. ANN algorithms significantly improve search efficiency by constructing effective indexing structures, albeit at the cost of reduced accuracy.

Nevertheless, as application scenarios grow increasingly complex, simple ANN search can no longer satisfy all practical needs. For instance, as shown in Figure\ref{fig:hybrid ANNS}, users on e-commerce platforms may search for clothing items by retrieving visually similar products based on an image. Additionally, users may impose further requirements such as price, color, or brand preferences. Such scenarios necessitate a retrieval system capable of simultaneously addressing vector similarity (e.g., product image) and attribute constraints (e.g., brand name) \cite{tian2023approximate}. When the constraint involves a specific attribute value, this problem is referred to as Attribute Filtering Approximate Nearest Neighbor (AF-ANN) search ~\cite{NHQ,Filtered-diskann} . For example, a user may seek a green piece of clothing. If the constraint involves a range condition, it is termed Range Filtering Approximate Nearest Neighbor (RF-ANN) search  ~\cite{serf,iRangeGraph}. For instance, filtering clothes priced between $100 and $200. To meet these application demands, hybrid query \cite{JD-e-commerce, analyticdb} techniques have emerged. Hybrid queries integrate vector retrieval with conditional filtering, optimizing their interaction to significantly enhance efficiency and flexibility in complex query scenarios.

% However, as application scenarios become more complex, simple ANN search is no longer sufficient to meet all practical needs. New requirements have emerged for ANN search systems. For example, as Figure \ref{fig:hybrid ANNS}, a user on an e-commerce platform may search for a dress by retrieving similar items based on an image. Additionally, the user can apply structured attribute filters such as price, color, or brand. This scenario necessitates a retrieval system that satisfies both vector similarity and attribute constraints \cite{tian2023approximate}. When the constraint is a Boolean condition—e.g., the user specifically requires a green dress—the problem is referred to as Attribute Filtering Approximate Nearest Neighbor (AF-ANN) search ~\cite{NHQ,Filtered-diskann} problem. If the constraint is a range condition, such as filtering dresses priced between 100 and 200, it becomes the Range Filtering Approximate Nearest Neighbor (RF-ANN) search ~\cite{serf,iRangeGraph} problem. To address such cases, hybrid query \cite{JD-e-commerce, analyticdb} has been proposed. It jointly optimizes vector retrieval and conditional filtering. This approach significantly improves efficiency and flexibility in complex query scenarios.
\begin{figure*}
    \centering
    \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{-0.4cm}
    \includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
    \caption{Hybrid query example}
    % \vspace{-10pt} % 调整这个值来缩小空隙
    \label{fig:hybrid ANNS}
\end{figure*}
\subsection{Motivation}
% 近年来，混合查询算法发展迅速，已有多种属性过滤或范围过滤工作被提出。尽管 BigANN 2023 大赛\cite{bigann2023}的 filter 赛道对部分算法进行了性能测试，但其评估仍存在局限性：1) 参赛算法数量有限，未能覆盖当前主流方法；2) 仅评估单属性和双属性查询，未涉及更复杂的多属性场景；3) 测试数据集的属性分布不够全面。此外，不同算法在索引构建的时空开销、查询性能随属性数量变化的表现、以及对不同属性分布的适应性等方面尚缺乏系统性评估。目前，大多数研究仅关注属性过滤或范围查询的单一问题，而未能全面衡量混合查询的整体性能。为此，我们基于混合查询进行完整实验评估，全面分析不同算法在索引构建成本、查询效率及鲁棒性等方面的表现。
In recent years, hybrid query algorithms have developed rapidly, giving rise to numerous attribute filtering ~\cite{NHQ,diskann} and range-filtering algorithms \cite{serf,iRangeGraph}. In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data. For attribute filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance. As for range filtering algorithms, the size of the query range and the characteristics of different datasets also play an important role in determining algorithm performance.

% In recent years, hybrid query algorithms have advanced rapidly, with numerous algorithms  proposed for attribute filtering and range filtering. 
% In practice, the performance of hybrid query algorithms is also influenced by the characteristics of structured data. For attribute filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distributions \cite{UNG}, and attribute selectivity \cite{ACORN} all affect actual performance. For range filtering algorithms, query range size and different datasets will affect the performance of the algorithm.
Despite BigANN 2023 \cite{bigann2023}  evaluating the performance of some algorithms, its study still has several notable limitations:
1)The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. For instance, NHQ and Filtered-DiskANN in attribute filtering algorithms have not been assessed.
2)It focuses only on single-attribute and dual-attribute query scenarios, neglecting the more complex demands of multi-attribute queries. In real-world applications, an object typically involves multiple attributes. For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range, etc.) simultaneously when searching.
3)It does not evaluate algorithm performance under different attribute distributions. However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.

Moreover, aside from BigANN, there is currently a lack of systematic evaluation specifically targeting hybrid query algorithms. To fill this research gap, we conducted a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios. Additionally, we further assessed the robustness of each algorithm under varying conditions.

% Although the filter track of the BigANN 2023 competition \cite{bigann2023} evaluated the performance of some algorithms, its assessment has several limitations: 
% 1) The number of evaluated algorithms is limited, failing to cover mainstream methods. Mainstream attribute filtering algorithms such as NHQ and Filtered-DiskANN were not evaluated.
% 2) The evaluation focuses only on single-attribute and dual-attribute queries, without considering more complex multi-attribute scenarios. However, in actual applications, an object often involves multiple attributes, and the same is true for queries. For example, in e-commerce scenarios, users often specify multiple attributes (such as color, brand, price range, etc.) for search at the same time.
% 3) It did not include algorithm performance under different attribute distributions. Different distribution of attributes may have a direct impact on the filtering strategy and index construction of the hybrid query algorithm.
% In addition, there is no relevant research to summarize and evaluate the relevant algorithms for hybrid queries.

% Furthermore, with the exception of the BigANN competition, there has been no dedicated study that provides a comprehensive review and evaluation of hybrid query algorithms. 
% In addition, apart from the BigANN competition, no dedicated evaluation of hybrid query algorithms exists. To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing index construction overhead and query efficiency across diverse scenarios. In addition, we assess the robustness of each algorithm.

% Moreover, there has been no systematic evaluation of different algorithms in terms of index construction overhead, query performance across varying attribute numbers, and adaptability to different attribute distributions. Most existing studies focus solely on attribute filtering or range filtering, without providing a holistic assessment of hybrid queries. To address this gap, we conduct a comprehensive experimental evaluation of hybrid queries, analyzing the indexing overhead, query efficiency, and robustness of different algorithms.
% In recent years, hybrid query algorithms have advanced rapidly, but their differences in attribute distribution adaptability and multi-attribute query performance have not been systematically evaluated. Although the filter track of the BigANN 2023 competition\cite{bigann2023} tested the performance of some algorithms, its evaluation scope has several limitations. First, the number of participating algorithms was limited, failing to cover the mainstream hybrid query algorithms. Second, the test dataset lacked diversity in attribute cardinality and attribute distribution, which may not fully reflect algorithm performance under different data characteristics. Third, the evaluation focused only on single-attribute and two-attribute query, without considering more complex multi-attribute scenarios, limiting the generalizability and practical value of the results. Moreover, the competition did not include evaluations of range filtered algorithms.

% Based on this background, we aim to design a series of systematic experiments. We will construct diverse datasets for attribute filtered query and comprehensively evaluate mainstream hybrid query algorithms.
\subsection{Our Contributions}
% The core contribution of this study lies in the systematic evaluation of hybrid query algorithms, which specifically includes the following aspects:
% We focus on ANN search in hybrid query scenarios. We systematically review and evaluate existing algorithms and systems. Our main contributions are summarized in four parts:
This study focuses on the problem of ANN search in hybrid query scenarios and provides a comprehensive review and evaluation of existing algorithms and systems. The main contributions are summarized in the following four aspects.

（1）\textbf{ Systematic Classification and Overview.}
We systematically classify more than ten representative attribute filtering algorithms from multiple dimensions, including index structure, filtering strategy, Boolean logic support, and index construction methods. Additionally, we survey range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE). These efforts provide a unified reference framework for future research.

（2）\textbf{ Evaluation of Attribute-Filtering Algorithms.}
% We select several representative algorithms for Attribute Filtered ANN Search. Using six real-world datasets, we evaluate their performance under different settings, such as the number of attributes, attribute distribution, and selectivity. We analyze their performance in terms of index construction time, index size,peak memory usage, query speed (QPS), and query accuracy. We also discuss their robustness and adaptability in complex scenarios.
We experimentally evaluate 13 attribute filtering ANN algorithms on six real-world datasets. By analyzing the performance variations of these algorithms under different numbers of attributes, attribute distributions, and selectivity conditions, we reveal the strengths and weaknesses of each algorithm. Furthermore, we explore the robustness and adaptability of these algorithms under complex query conditions. Evaluation metrics include index construction time, index size, peak memory usage,QPS and search accuracy.

（3）\textbf{ Evaluation of Range-Filtering Algorithms.}
% We evaluate five main algorithms (SeRF, WinFilter, iRangeGraph, DSG, and UNIFY) for Range Filtered ANN Search. We run experiments on three large-scale datasets with different query range settings. We compare their performance in index construction, storage usage, and query efficiency. We also study the effect of index structures on algorithm performance. This provides useful insights for future improvements.
We benchmark five mainstream range filtering ANN algorithms on three large-scale datasets, using varying query range settings in the experiments. The results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance. Additionally, we conduct an in-depth analysis of how index structures impact algorithm performance, providing valuable insights for algorithm design.

（4）\textbf{ Recommendations and Challenges.}

Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries. These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution. Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.

\section{PRELIMINARIES}

\subsection{Problem Definition}

We first define the Nearest Neighbor (NN) search problem.

\begin{definition}[NN Search]

Let \( D = \{v_1, \ldots, v_n\} \) be a dataset of \( n \) \( d \)-dimensional vectors. Given a query \( Q = (q_v, k) \), where \( q_v \) is the query vector and \( k \) is a positive integer, the NN search aims to return a set \( R \subseteq D \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D \setminus R \), \( \textit{dist}\!\left(q_v, x\right) \leq \textit{dist}\!\left(q_v, y\right) \). Here, \( \textit{dist}\!\left(\cdot, \cdot\right) \) denotes the distance metric, and we adopt Euclidean distance in this paper.
\end{definition}

However, to address the curse of dimensionality faced by NN search \cite{dimcurse}, existing researches focus on approximate solutions, known as ANN  search. We typically use $\text{Recall}@k = \frac{|R \cap \hat{R}|}{k}$ to evaluate the accuracy of ANN search algorithms, where $R$ denotes the true top-$k$ nearest neighbors of the query, $\hat{R}$ denotes the approximate top-$k$ nearest neighbors returned by the ANN search algorithm.

As the complexity of real-world application requirements increases, NN search has evolved into hybrid NN search with attribute constraints. Depending on the nature of the attribute constraints, hybrid NN search can be divided into two categories: 1) Attribute Filtering Nearest Neighbor (\textit{AF-NN}) search. 2) Range Filtering Nearest Neighbor (\textit{RF-NN}) search. We provide their formal definitions below.

\begin{definition}[AF-NN Search]
Let \( D = \{(v_1, s_1), \ldots, (v_n, s_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute set \( s_i \). Given a query \( Q = (q_v, q_s, k) \), where \( q_s \) is the query attribute set, the AF-NN search aims to return a set \( R \subseteq D_s \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_s \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_s = \{ v_i \mid (v_i, s_i) \in D \land q_s \subseteq s_i \} \).
\end{definition}

We further classify AF-NN search according to the number of the attribute set \( s_i \): 1) Single-Attribute Filtering Nearest Neighbor (\textit{SAF-NN}) search, where $\forall i,\, |s_i| = 1$. 2) Multi-Attribute Filtering Nearest Neighbor (\textit{MAF-NN}) search, where $\exists i,\, |s_i| > 1$.

\begin{definition}[RF-NN Search]

Let \( D = \{(v_1, s_1), \ldots, (v_n, s_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \). Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).
\end{definition}

Similar to the conventional ANN search, most existing studies focus on approximate solutions for hybrid NN search, referred to as hybrid ANN search, which includes both \textit{AF-ANN} search and \textit{RF-ANN} search.

\subsection{Index Structures in ANN Search}

Current hybrid query methods mainly adopt graph-based ~\cite{nsw,kgraph,nsg,fanng,ngt} or Inverted File Index (IVF)-based \cite{PQ} index structures. We briefly introduce the fundamental principles of these two types in the following.

\vspace{1em}
\noindent\textbf{\underline{Graph.}}
Graph-based ANN search algorithms accelerate queries by building graph indexes on datasets. As illustrated in Figure~\ref{fig:graph}, each data point in the dataset corresponds to a point in the graph, and neighboring vertices (e.g., $a$ and $b$) are connected via edges based on their distance $\textit{dist}(a, b)$. In the graph index, each point maintains connections only to its nearest neighbors to preserve query efficiency. For instance, in Figure~\ref{fig:graph}, the gray point $c$ is connected to five neighbors $(a, b, d, e, f)$ and can traverse to them via corresponding edges.

Given a query point $q$, the graph-based ANN search typically follows a greedy search strategy to find the $k$ nearest neighbors. For illustration, consider the case where $k = 1$ (i.e., finding the single nearest neighbor of $q$): The algorithm initiates the search from an entry point (the gray point $c$). If there exists a neighbor $n$ (the point $f$) of the current point such that $\textit{dist}(n, q) < \textit{dist}(c, q)$, the algorithm updates the current point to $n$. This process is iteratively repeated—always moving to the neighbor closest to $q$—until no neighbor is found that is closer than the current point. The final point reached (the blue point $j$) is returned as the approximate nearest neighbor of $q$.

\vspace{1em}
\noindent\textbf{\underline{IVF.}}
IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point. Specifically, as shown in Figure~\ref{fig:ivf}, IVF first selects a subset of data points and applies a clustering algorithm (e.g., K-Means) to obtain a set of centroids $(C_0, C_1, ..., C_6)$, each representing a distinct cluster. Every data point (gray dots) is then assigned to the cluster corresponding to its nearest centroid based on the distance metric, thereby forming the index structure.

During the query process, given a query point $q$, the algorithm computes distances between $q$ and all centroids, selects a small number of the closest centroids ($C_0, C_1, C_2$), and then performs a search only within the associated clusters to identify the approximate nearest neighbors.

\begin{figure}
    \begin{subfigure}{0.60\columnwidth}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.3cm}
        \includegraphics[width=\linewidth]{figures/graph.pdf}
        \caption{Graph Index}
        \label{fig:graph}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.38\columnwidth}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.3cm}
        \includegraphics[width=\linewidth]{figures/ivf.pdf}
        \caption{IVF Index}
        \label{fig:ivf}
    \end{subfigure}
    % \vspace{-10pt} % 调整这个值来缩小空隙
    \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{0.2cm}
    \caption{Graph index and IVF index}
    % \vspace{-2em} % 调整这个值来缩小空隙
\end{figure}

\section{Overview of Hybrid query Algorithms}

\setlength{\textfloatsep}{0cm}
\setlength{\floatsep}{0cm}
\begin{table*}[t]
	\centering
        \setlength{\abovecaptionskip}{0.05cm}
        %\setlength{\belowcaptionskip}{-0.3cm}

	\caption{Comparison of AF-ANN search algorithms}
	\small
	\label{tab:compair_1}
    \begin{tabular}{|l|l|c|c|c|c|c|c|c|}
		\hline
        \textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		\hline
         NHQ & Graph & C & Y & N& N& N & N & N \\
         FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
	StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
        CAPS & IVF & C & Y & N & N & N & Y & Y \\
        ACORN & Graph & C & Y & Y & Y & Y & Y & Y \\
       UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
        Puck & IVF & B & Y & Y & Y & N & Y & Y \\
        % ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\

		\hline
	\end{tabular}

    \vspace{0.2em}
	\centering
    \footnotesize{
	\begin{minipage}{\linewidth}
		\textsuperscript{A} Post-filtering, 
		\textsuperscript{B} Pre-filtering, 
		\textsuperscript{C} Simultaneous filtering, 
		\textsuperscript{Y} Support, 
		\textsuperscript{N} Unsupport. 
		\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
		\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
		\textit{OR} indicates whether the algorithm supports attribute filtering with OR operations. 
		\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
		\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
		\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
	\end{minipage}}
    \vspace{-0.5cm}
\end{table*}

We provide an overview and analysis of over ten hybrid query methods, all drawn from recent research efforts, and collectively referred to as algorithms in the following text. Specifically, Section~3.1 describes methods based on attribute filtering, Section~3.2 discusses those based on range filtering, and Section~3.3 introduces vector libraries and databases that support both attribute and range filters.

\vspace{-10pt}
\subsection{Attribute Filtering Algorithms}

We summarize six attribute filtering algorithms and provide an intuitive comparison in Table~\ref{tab:compair_1}.

\vspace{1em}
\noindent\textbf{\underline{NHQ \cite{NHQ}.}}  
Traditional attribute filtering algorithms usually perform attribute constraints and ANN search separately. In contrast, NHQ is the first to implement simultaneous filtering, integrating both aspects into a unified framework. NHQ constructs an index based on a nearest neighbor graph and introduces a fusion distance that jointly captures vector similarity and attribute similarity. Leveraging this fusion distance, NHQ unifies vector similarity and attribute matching into a single comprehensive similarity measure and builds the graph accordingly. During the query process, NHQ efficiently prunes irrelevant edges via this composite index, enabling fast retrieval of results that satisfy both vector similarity and attribute constraints.

\vspace{1em}
\noindent\textbf{\underline{Filtered-DiskANN \cite{Filtered-diskann}.}}  
The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.

Filtered-DiskANN also supports simultaneous filtering. Built upon the Vamana \cite{diskann} graph-based ANN index, it incorporates attribute information directly into the graph during index construction. This integration ensures that the index reflects both vector proximity and attribute constraints. Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.

Filtered-DiskANN proposes two index variants:  
1) \textbf{FilteredVamana}, which incrementally builds the graph index by inserting data points and dynamically adding edges, allowing adaptive expansion.  
2) \textbf{StitchedVamana}, which adopts a batch construction strategy—constructing separate Vamana subgraphs for each attribute, followed by merging and edge pruning.

A key limitation of Filtered-DiskANN is that while it supports both single-attribute and multi-attribute filtering, it only supports the Boolean OR logic for multi-attribute filtering, lacking support for Boolean AND logic.

\vspace{1em}
\noindent\textbf{\underline{CAPS \cite{CAPS}.}}  
As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes. CAPS addresses this issue by being the first simultaneous filtering algorithm based on spatial partitioning, significantly reducing index size.

CAPS introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods. CAPS adopts a two-level partitioning strategy:  
1) The first level clusters vectors based on similarity using K-Means or learning-based methods such as BLISS.  
2) Within each cluster, AFT partitions data further based on attribute frequencies, enabling finer-grained indexing and improving query efficiency.

\vspace{1em}
\noindent\textbf{\underline{ACORN \cite{ACORN}.}}  
Above simultaneous filtering methods struggle with large-scale, unbounded, or unknown predicate sets.
%The above simultaneous filtering methods are less effective in scenarios involving large-scale, unbounded, or unknown predicate sets, where a predicate refers to a condition or rule used for filtering. 
ACORN addresses this issue by introducing a predicate-agnostic indexing framework.

ACORN is built upon HNSW \cite{hnsw}, a hierarchical graph-based ANN index. It supports high-cardinality and unrestricted predicate sets, overcoming the limitations of methods restricted to small-scale equality filters. It constructs a denser hierarchical graph by expanding node neighborhoods and prunes edges at lower levels to control index size. During querying, ACORN eliminates unnecessary distance computations by filtering out nodes that violate attribute constraints. This effectively maintains a nearest neighbor graph over valid nodes only. 
%During the query process, ACORN avoids unnecessary distance computations by filtering out nodes that do not meet attribute constraints, effectively simulating a nearest neighbor graph over valid nodes only.

ACORN includes two index variants:  
1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.

\vspace{1em}
\noindent\textbf{\underline{UNG \cite{UNG}.}} 
Graph-based methods（NHQ, Filtered-DiskANN, ACO-\\RN）do not guarantee result completeness, while CAPS lacks robustness when base and query vectors differ in attribute cardinality. UNG is proposed to overcome both limitations.

UNG is a unified framework that integrates diverse graph-based ANN indexes for hybrid query. It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes. Then, it constructs a Label Navigating Graph (LNG) to encode inclusion relationships among attribute sets. Within each group, UNG builds graph-based ANN indexes (e.g., Vamana, HNSW) and connects them via cross-group edges to enable efficient cross-group search.

UNG supports Boolean filtering with two modes:  
1) The query attribute set is a subset of the data attribute set.  
2) The query attribute set exactly matches the data attribute set.

\vspace{1em}
\noindent\textbf{\underline{Puck \cite{puck}.}}  
While simultaneous filtering performs well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints. In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.

Developed by Baidu, Puck utilizes two-level quantization for indexing. It maintains an attribute set for each cluster to track vector attributes. During the query process, it employs pre-filtering to exclude clusters without required attributes, thereby reducing the search space.
%Developed by Baidu, Puck adopts a pre-filtering approach and employs a multi-level filtering mechanism for hybrid query. Its index structure comprises four layers: the first two use vector quantization for training, while the latter two leverage product quantization.

\setlength{\textfloatsep}{0.1cm}
\setlength{\floatsep}{0cm}
\begin{table}[t]
	\centering
        \setlength{\abovecaptionskip}{0.05cm}
        %\setlength{\belowcaptionskip}{-0.3cm}
        \setlength{\textfloatsep}{0cm}
	\caption{Comparison of RF-ANN search algorithms}
	\small	% 只会影响当前组的内容
	\label{tab:range_algo}
    \begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		\hline
        DSG & Graph & Y & N \\
        iRange & Graph & N & Y \\
        SeRF & Graph & Y & Y \\
		UNIFY & Graph & Y & Y \\
		WinFilter & Graph & N & Y  \\
		\hline
	\end{tabular}

    \vspace{0.2em} % 调整间距
	\footnotesize{
            \begin{minipage}{\linewidth}
            \textsuperscript{Y} Support, 
            \textsuperscript{N} Unsupport.
            \textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
    		\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
            \end{minipage} 
        }

\end{table}

\subsection{Range Filtering Algorithms}

We introduce five representative range filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.

\vspace{1em}
\noindent\textbf{\underline{SeRF \cite{serf}.}}  
Conventional RF-ANN search approaches typically follow one of two paradigms: 1) conducting ANN search first followed by attribute-based filtering; 2) filtering the dataset based on attribute ranges before performing ANN search. However, both approaches suffer from suboptimal performance. Building a separate neighbor graph (e.g., HNSW) for each attribute range could ensure efficient querying but incurs an $O(n^2)$ cost in constructing and storing $n$ graphs. Since many edges are shared across these graphs, SeRF introduces a validity-range aware design where each edge records the interval in which it is valid, indicating in which subgraphs the edge remains valid. This compresses $n$ graphs into a single unified graph, maintaining search effectiveness while significantly reducing memory and index construction overhead.

\vspace{1em}
\noindent\textbf{\underline{WinFilter \cite{winFilter}.}}  
Unlike SeRF, which focuses on graph compression, WinFilter proposes a structural partitioning framework called the $\beta$-Window Search Tree ($\beta$-WST). After the dataset is sorted by attribute values, it is partitioned into multiple intervals and organized into a tree structure. Each node in the tree corresponds to an attribute range and maintains a local ANN index (e.g., Vamana). For a range-filtering query, WinFilter only searches within nodes overlapping the query range and merges partial results. With a tree height of $O(\log n)$, each query accesses at most $O(\log n)$ sub-indexes, resulting in significant speedups.

\vspace{1em}
\noindent\textbf{\underline{iRange \cite{iRangeGraph}.}}  
To address the query efficiency degradation caused by the graph compression in SeRF, iRange adopts a more flexible strategy. Rather than prebuilding indexes for all possible ranges, it dynamically assembles a query-specific subgraph at runtime. iRange partitions the dataset into intervals based on attribute values and independently constructs a local graph for each interval, storing only edge information. During the query process, the relevant local graphs overlapping with the query range are merged into a temporary search graph, and a pruning strategy is applied to enable efficient search.

\vspace{1em}
\noindent\textbf{\underline{DSG \cite{DSG}.}}  
Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets. SeRF allows incremental insertion but requires attributes to be ordered. DSG introduces the first truly dynamic RF-ANN framework that supports inserting data with unordered attributes while maintaining efficient range filtering.
DSG is built on two key data structures. 1) The rectangle tree partitions the query space into rectangular regions, each corresponding to a group of queries that share the same nearest neighbors. 2) The dynamic segment graph is a neighbor graph where each edge is annotated with the attribute range in which it is valid.
With these structures, only a few regions need to be updated when inserting new data. During queries, the system considers only edges valid for the current attribute range, improving efficiency.

\vspace{1em}
\noindent\textbf{\underline{UNIFY \cite{UNIFY}.}}  
Unlike DSG, which relies on rectangle trees and range-aware edges, UNIFY adopts a segmentation-based approach and proposes a range query index structure. UNIFY introduces the Segmented Inclusive Graph (SIG), which partitions the dataset into segments by attribute and constructs an independent neighbor graph for each segment. These segment graphs are then integrated into a unified global graph. SIG adheres to a graph inclusiveness principle: any query subgraph can be composed from existing segment graphs, avoiding the need for range-specific index construction. Its hierarchical variant, HSIG, enhances SIG by incorporating the multilayer design of HNSW, skip lists, and edge bitmaps for efficient range localization and post-filter pruning. UNIFY supports three filtering strategies—pre-filtering, post-filtering, and  simultaneous filtering—enabling robust and flexible performance across diverse application scenarios.

\subsection{Vector Libraries and Databases}

The vector libraries and databases discussed in this section are not explicitly designed for hybrid query, but they support both attribute filtering and range filtering. Additionally, all the functionalities shown in Table 1 are also supported.

\vspace{1em}
\noindent\textbf{\underline{Faiss \cite{Faiss}.}}  
Faiss is a library designed for efficient similarity search and clustering of dense vectors. It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.

In hybrid query scenarios, Faiss supports vector search with an ID selector, which is a bitmap aligned with the dataset size. Users can generate this selector by first applying custom attribute filtering methods. During the query, Faiss excludes vectors based on the selector, enabling efficient integration of attribute filtering with ANN search.

% HQI~\cite{HQI} further proposes an optimization scheme for the IVF index in Faiss, improving efficiency in two aspects:  
% 1) Workload-Aware Vector Index: Constructs an attribute filtering tree using historical query workloads and vector cluster centroids to improve filtering efficiency.  
% 2) Batch Query Optimization: Groups queries sharing the same filter conditions, performs filtering once per group, and then conducts batch vector similarity computations using efficient matrix operations.  
% Since this paper does not focus on query workload optimization, we adopt only the batch optimization strategy in our analysis.
In addition, we adopted the batch optimization strategy of HQI~\cite{HQI} for the IVF index in Faiss. This strategy groups queries with the same filter conditions, performs filtering once per group, and then uses efficient matrix operations to perform batch vector similarity calculations.

\vspace{1em}
\noindent\textbf{\underline{PASE \cite{pase}.}}  
PASE is a vector indexing plugin for the PostgreSQL database \cite{postgresql13.4}, supporting two index types: IVF\_Flat \cite{johnson2019billion} and HNSW. By leveraging database capabilities, PASE enables both attribute filtering and range filtering. We focus on the post-filtering strategy based on HNSW.

When a query request is received, PASE first obtains a candidate set using the HNSW index. It then applies the filtering conditions from the WHERE clause to refine the results. However, since the candidate set has a fixed size, low-selectivity filters may result in fewer than $k$ results being returned.

\vspace{1em}
\noindent\textbf{\underline{VBASE \cite{vbase}.}}  
Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}. We focus on HNSW-based search.

VBASE adopts a post-filtering strategy. However, it employs an iterative filtering mechanism: during index traversal, each node is immediately checked against the WHERE clause, and non-matching nodes are discarded. This avoids the issue in PASE where the final result set may contain fewer than $k$ results.

\vspace{1em}
\noindent\textbf{\underline{Milvus \cite{milvus}.}}  
Unlike PASE and VBASE, which are database extensions, Milvus is an open-source vector database purpose-built for large-scale similarity search. It supports multiple index types, including HNSW, IVF\_Flat, and IVF\_PQ, and provides extensive optimization for real-world deployment.

Among its indexes, IVF\_Flat is commonly used due to its balance between performance and simplicity. In hybrid queries, Milvus first pre-filters the dataset using user-specified conditions, then traverses only the corresponding clusters for ANN search—similar to the ID selector mechanism of Faiss.

\section{Experiments}
\subsection{Experimental Setup}
\subsubsection{Datasets}

For attribute filtering tasks, we employ six real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, and Enron~\cite{enron2015}, covering a diverse range of domains. We independently generate attribute for each dataset.

For range filtering queries, we evaluate three widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}. Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute. This ensures that the data is initially sorted.

Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets. In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness. Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation. A higher LID indicates greater intrinsic complexity.

\setlength{\textfloatsep}{0.1cm}
\setlength{\floatsep}{0cm}
\begin{table}[t]
\centering
% \vspace{-6pt} % 调整这个值来缩小空隙
\setlength{\abovecaptionskip}{0.05cm}
\setlength{\textfloatsep}{0.cm}
\caption{Datassets}

\label{tab:datasets_combined}
\resizebox{\columnwidth}{!}{
\begin{tabular}{cccccc}
\toprule
Dataset & Dimension & Base Data & Queries & LID & Type \\
\midrule
Msong & 420 & 992,272 & 200 & 23& Audio \\[2pt]
Audio & 192 & 53,387 & 200 & 14& Audio \\[2pt]
SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\[2pt]
GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\[2pt]
GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\[2pt]
Enron & 1369 & 94,987 & 200 & 23& Text \\[2pt]
Deep & 96 & 1,000,000 & 10,000 & 22& Image \\[2pt]
YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\[2pt] 
WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\[2pt]

\bottomrule
\end{tabular}
}
\end{table}

\subsubsection{Evaluation Metrics}

To comprehensively assess the overall performance of different algorithms, we adopt a multi-dimensional quantitative evaluation framework~\cite{compare}, which includes the following five core metrics:

\begin{enumerate}

    \item \textbf{Recall@k}: The proportion of overlap between the returned approximate $k$ nearest neighbors and the ground-truth $k$ nearest neighbors.
    \item \textbf{QPS (Queries Per Second)}: The number of queries processed per second.
    \item \textbf{Index Construction Time}: The total time required to transform the raw dataset into a queryable index structure.
    \item \textbf{Index Size}: The storage size of the persisted index on disk.
    \item \textbf{Peak Memory Usage}: The maximum memory consumption observed during the index construction phase.
\end{enumerate}

\subsubsection{Parameter Settings}

For all evaluated algorithms, we adopt the parameter settings recommended in the original paper and adjust the parameters related to search in order to obtain different recall and QPS.

\subsubsection{Platform}

We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) and 256GB of RAM. Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}. By default, queries run on a single thread; we also report results for 16-thread parallelism in specific scenarios.

We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1} and Table~\ref{tab:range_algo}. For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance characteristics.

%4.2
\subsection{Attribute Filtering}

%4.2.1
\subsubsection{Time and Space overhead of index construction}
% \subsubsection{\textbf{Attribute Filtering}}
\begin{figure}[t]
    \centering
        \setlength{\abovecaptionskip}{0.3cm}
        \setlength{\belowcaptionskip}{0cm}

    % 上面的图例，居中并可通过 hspace 调整左右位置
    \hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
    \includegraphics[width=0.94\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径
    \vspace{-12pt} % 使用负值拉近两张图的距离，可以根据需要调整

    \begin{subfigure}{\columnwidth}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.3cm}
        \includegraphics[width=\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
        \caption{Index construction time}
        \label{fig:build_time_comparison_query1}
    \end{subfigure}

    \vspace{0.3cm} % 增加间距

    \begin{subfigure}{\columnwidth}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.3cm}
        \includegraphics[width=\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
        \caption{Index size}
        \label{fig:index_size_mb_comparison_query1}
    \end{subfigure}

    \vspace{0.3cm} % 增加间距

    \begin{subfigure}{\columnwidth}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.3cm}
        \includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
        \caption{Peak memory usage}
        \label{fig:memory_mb_comparison_query1}
    \end{subfigure}

    \caption{Time and space overhead of attribute filtering index construction}
    \label{fig:build_index_comparison}
\end{figure}

\vspace{0.5em}

To investigate the performance of different attribute filtering algorithms during index construction, we evaluate three key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage. Notably, PASE is evaluated exclusively on Audio, GloVe, Msong, and SIFT1M as it supports only data with dimensionality less than 512.

\vspace{0.5em}
\textit{\textbf{Index construction time.}}
As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned four datasets, PASE has the longest index construction time due to its single-threaded indexing support. Additionally, VBASE also supports only single-threaded indexing but achieves better query performance than PASE.

For algorithms supporting 32-thread, index construction time differences are negligible on small-scale datasets (Audio and Enron) due to their limited complexity. On large-scale datasets (SIFT1M, GIST1M, GloVe, and Msong), ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors. In contrast, ACORN-$\gamma$ incurs the highest index construction time, as it expands neighbor lists and evaluates a large candidate pool, leading to increased computational overhead.

\vspace{0.5em}
\textit{\textbf{Index size.}}
Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data. In order to unify the comparison standard, we include both the index structure generated by the algorithm and the original data when evaluating the index size. As shown in the figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets. This overhead stems primarily from its extensive metadata requirements. Other methods demonstrate comparable index sizes, with Faiss consistently achieving the most compact representations through its efficient index design.

\vspace{0.5em}
\textit{\textbf{Peak memory usage.}}
As shown in Figure~\ref{fig:memory_mb_comparison_query1}, on small-scale datasets, all methods except NHQ exhibit low memory usage. The substantially higher memory consumption of NHQ is attributed to its graph construction procedure, which requires loading the entire dataset into memory. On large-scale datasets, CPAS exhibits slightly lower memory usage compared to other algorithms. Due to their special characteristics, databases were not included in the peak memory usage testing during index construction.

\subsubsection{Performance Evaluation}

%4.2.2

\begin{figure*}
    \centering
        \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{-0.4cm}
    \includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
    \caption{Single-Attribute Building and Query (single thread) }
    \label{fig:exp_1_1_SingleLabel_1thread}
\end{figure*}

\begin{figure*}
    \centering
    \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{-0.4cm}
    \includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
    \caption{Single-Attribute Building and Query (16 threads)}
    \label{fig:exp_1_2_SingleLabel_16thread}
\end{figure*}

%4.2.2

\begin{figure}
    \centering
    \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{-0.1cm}
    % 上面的图例，居中并可通过 hspace 调整左右位置
    \hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
    \includegraphics[width=0.98\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
    \vspace{-10pt} % 使用负值拉近两张图的距离，可以根据需要调整

    % 下面的子图，居中显示
    \includegraphics[width=0.9\columnwidth]{figures/exp/exp_2_1.pdf}
    \caption{Effect of Multi-Attribute Index Construction on Single Query Performance. ($S$ denotes single-attribute index construction and single-attribute query; $M$ denotes multi-attribute index construction and single-attribute query)}
    \label{fig:exp_2_1}

\end{figure}

We next evaluate the query performance of AF-ANN search algorithms, focusing on three main scenarios.

\textit{\textbf{Single-Attribute Building and Single-Attribute Query.}}
In this scenario, we construct the index using a single attribute and issue queries on the same attribute.

\textit{Single-Threaded Search.}  
As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under full-recall conditions (recall = 1), search often requires traversing larger candidate sets or deeper graph paths, leading to increased computational cost and a sharp QPS drop for most methods. Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency. But, UNG slightly underperforms on high-LID datasets such as GloVe. In contrast, CAPS performs better on high-LID datasets but is more sensitive to dataset characteristics. CAPS leverages multi-level spatial partitioning and attribute filtering to efficiently explore sparse spaces, whereas UNG relies on structured attribute organization, which limits its adaptability to sparse high-dimensional distributions.

NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets. This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements. As observed in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, StitchedVamana outperforms FilteredVamana in query efficiency. The difference arises from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.

Among all methods, vector database systems (PASE, VBASE, Milvus) perform the worst. These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing. Additionally, we observe that Faiss+HQI\_Batch outperforms vanilla Faiss, indicating that batch querying via HQI can effectively enhance query performance.

\textit{Multi-Threaded Search.}
As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance. Puck performs well on large-scale datasets, but its performance degrades on small datasets. Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets. 
CAPS maintains a relatively high throughput under multi-threading but exhibits limited adaptability to different datasets. The vector distribution of the dataset affects the construction of its partitioned index.

ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity. Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.

\vspace{1em}
\textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
In this scenario, the index is constructed using multiple attributes but applies filtering condition on only one attribute during query processing.

In database systems (VBASE, PASE, Milvus), when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree. Faiss offers an ID filtering mechanism, it operates solely during query execution and does not influence index building. CAPS requires that the number of attributes in a query match those used during index construction. ACORN-1 and ACORN-\(\gamma\) are specifically designed for single-attribute indexing. Hence, they are excluded from this comparison.

\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation. In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: FilteredVamana increases the complexity introduced by retaining attribute during index construction; the complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs; The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness; UNG employs a distinct construction and search strategy, leading to a significant drop in query performance.

\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
As shown in \ref{fig:exp_2_1}, Puck achieves the best query performance, surpassing other algorithms by an order of magnitude. It filters out irrelevant results during retrieval rather than searching for more candidates. FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, hurting single-attribute query efficiency. This leads to excessive irrelevant node traversal, making it slower than other methods.

\begin{figure*}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.4cm}
        \includegraphics[width=\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
        \caption{Multi-attribute build and query (single thread)}
        \label{fig:exp_4_1_MultiLabel_1thread}
\end{figure*}

\begin{figure*}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{-0.4cm}
        \includegraphics[width=\textwidth]{figures/exp/exp_3_1.pdf}
        \caption{Effect of attribute distribution on on query performance (single thread)}
        \label{fig:exp_3_1}
\end{figure*}

\vspace{10pt}
\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using three uniformly distributed attributes and apply filtering conditions on all three attributes simultaneously during the query process.

As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets. For IVF-based methods that are not specifically optimized for hybrid query scenarios (Faiss\_IVF and Milvus), their QPS remains relatively stable as the recall varies. Milvus, being a general-purpose system, exhibits comparatively poor performance. In contrast, Faiss—especially when combined with HQI\_Batch—achieves moderate performance. Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes. In fact, filtering can reduce the effective candidate set, improving efficiency.

The IVF-based algorithm CAPS, optimized for hybrid query scenarios, employs a multi-level partitioning strategy that introduces additional overhead. This overhead negatively impacts performance on small datasets. However, on large datasets, the overhead is amortized, and the benefits of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.

NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets. It relies on fused distance calculations. The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.

\subsubsection{Robustness}In this section, we evaluate the robustness of these algorithms.

\textit{\textbf{Attribute Distribution.}} To comprehensively evaluate performance across different attribute distributions, we generate base and query attribute sets with four representative distributions—long-tailed, normal, power-law, and uniform—across the six datasets described in Section~4.1.1. We evaluate all algorithms under these distributions on each dataset. The performance differences observed for the same algorithm across different datasets are relatively minor. Thus, due to space constraints, we present only the results on SIFT1M.

As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts. Specifically, ACORN-1, ACORN-$\gamma$, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.

Among all algorithms, ACORN-\(\gamma\) demonstrates the highest robustness. During its index construction, attribute is mainly used for pruning in the lowest layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected. As a result, changes in attribute distribution have a limited impact on overall performance.

In contrast, VBASE exhibits the weakest robustness. As a post-filtering system, it performs significantly better under uniform distributions but degrades under long-tailed, normal, and power-law distributions. This degradation stems from the low selectivity of certain attributes in the last three distributions, which increases unnecessary distance computations, thus reducing overall efficiency.

\begin{figure}
    \centering
    \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
    \caption{Effect of Single-Attribute Selectivity on Query}
    \label{fig:exp_5_1_1_SingleLabel_1thread}
\end{figure}

\textit{\textbf{Single-Attribute Selectivity.}}
In hybrid queries, different attribute selectivity (AS) levels can significantly affect computational cost and query efficiency, as the algorithm must effectively identify matching data points with specific attributes within a large dataset. AS refers to the proportion of data points in the dataset that share a specific attribute value. For example, an AS of 1\% indicates that only 1\% of the dataset satisfies the given attribute condition.

To investigate this effect, we evaluate four AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset. Using a single-threaded execution environment, we compare the query performance of 13 algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.

Experimental results show that UNG achieves the best performance across all AS levels, especially at extremely low AS (1\%). 
This advantage stems from its pre-filtering strategy. Pre-filtering strategy significantly reduces the ANN search space by narrowing down candidates prior to vector computation. In contrast, VBASE performs the worst at 1\% AS due to its post-filtering strategy. Post-filtering strategy first retrieves a large number of candidates and then applies filtering, incurring substantial computational overhead.

\begin{figure*}
    \centering

    % 第一行：单独一张大图
    \begin{subfigure}{\textwidth}
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{0cm}
        \includegraphics[width=\textwidth]{figures/exp/exp_5_2_1.pdf}
        \caption{Algorithms optimized for low AS levels.}
        \label{fig:exp_5_2_1}
    \end{subfigure}

    \vfill % 增加垂直间距

    % 第二行：两张子图，左侧宽度是右侧的两倍
    \begin{subfigure}{0.66\textwidth} % 2/3 宽度
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{0cm}
        \includegraphics[width=\textwidth]{figures/exp/exp_5_2_2.pdf}
        \caption{Algorithms optimized for high AS levels.}
        \label{fig:exp_5_2_2}
    \end{subfigure}
    \hfill % 增加水平间距
    \begin{subfigure}{0.33\textwidth} % 1/3 宽度
        \centering
        \setlength{\abovecaptionskip}{0cm}
        \setlength{\belowcaptionskip}{0cm}
        \includegraphics[width=\textwidth]{figures/exp/exp_5_2_3.pdf}
        \caption{Algorithms insensitive to AS level.}
        \label{fig:exp_5_2_3}
    \end{subfigure}

    \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{-0.4cm}
    \caption{Different AS under the same algorithm}
    \label{fig:exp_5_2_combined}
\end{figure*}

According to the query performance trends of different algorithms under varying AS levels, we categorize the algorithms into three groups:

\par
(1) \textit{Algorithms optimized for low AS levels.}  
This category includes ACORN-1, CAPS, StitchedVamana, UNG, Faiss, Puck, and Faiss+HQI\_Batch, as illustrated in Figure~\ref{fig:exp_5_2_1}.

ACORN-1 performs well in low AS scenarios because fewer nodes share the same attribute. This increases the average degree of retained nodes and improves graph connectivity. CAPS efficiently skips irrelevant subpartitions, reducing computational overhead. However, as AS increases, it must process more subpartitions and handle a larger dataset. StitchedVamana optimizes local adjacency using independent subgraphs, enabling fast localization at low AS. However, at higher AS levels, it requires broader global exploration. UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS conditions, leading to better performance.

Interestingly, Faiss and Faiss+HQI\_Batch perform worst at the 50\% AS level instead of 75\%, which might seem unexpected. This happens because, when AS decreases from 75\% to 50\%, fewer data points are filtered out. As a result, more clusters must be searched, increasing computational cost.

\par
(2) \textit{Algorithms optimized for high AS levels.}  
This group includes NHQ, FilteredVamana, VBASE, and PASE, as shown in Figure~\ref{fig:exp_5_2_2}.

At low AS levels, NHQ struggles to locate relevant regions efficiently, leading to excessive computations on non-matching nodes. FilteredVamana also performs poorly in these scenarios. Its dynamic pruning strategy makes it difficult to balance vector distance and attribute relevance, resulting in overly restricted search paths.
VBASE relies on post-filtering, which increases computational overhead at low AS. PASE performs poorly at extremely low AS (e.g., 1\%), with recall dropping below 0.2. Its fixed candidate set may not contain enough valid results after filtering, leading to incomplete top-$k$ results and significantly reducing recall.

\par
(3) \textit{Algorithms insensitive to AS level.}  
This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.

Milvus is mainly limited by system-level communication overhead, such as API latency. As a result, its query performance remains largely unaffected by AS variations. ACORN-\(\gamma\) maintains stable performance across different AS levels by using a higher index construction parameter $\gamma$. This ensures a relatively stable average node degree, even after attribute pruning, minimizing the impact of AS changes on query efficiency.

\begin{figure*}
    \centering
    \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{-0.4cm}
    \includegraphics[width=\textwidth]{figures/exp/exp_6_1.pdf}
    \caption{Effect of dataset on Query}
    \label{fig:exp_6_1}
\end{figure*}

%4.2.7
\textit{\textbf{Different Datasets .}}  
To evaluate the performance of various methods across different datasets, we conduct experiments on six datasets. Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.

As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.Because Audio has small scale, low dimensionality, and low LID.In contrast,all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset. Because these two dataset have the largest scale and highest LID.

SIFT1M and Msong are similar datasets, with the key difference being that SIFT1M has lower dimensionality. The four algorithms (ACORN,Faiss,PASE, and NHQ) perform similarly on these two datasets, suggesting strong robustness to high dimensional dataset. In contrast, the remaining algorithms exhibit degraded performance on Msong, revealing a lack of adaptability to high dimensional dataset.

Most algorithms struggle to achieve high recall on GloVe,because it has the highest LID. Compare to other algorithms, the four algorithms (UNG, Faiss, CAPS, and Milvus) manage to maintain relatively high recall, demonstrating better adaptability to complex datasets. Notably, although vanilla Faiss performs worse on SIFT1M compared to Enron dataset, Faiss+HQI\_Batch outperforms on SIFT1M. Because batch optimization in HQI reduces query overhead and increases throughput.

\subsection{Range Filtering}
Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we will only compare several range filtering algorithms.
\subsubsection{Time and Space overhead of index construction.}

\begin{table}[htbp]
\centering
\setlength{\abovecaptionskip}{0.05cm}
\caption{Time and space overhead of range filtering index construction}
% \vspace{-7pt}
\label{tab:Range Filtered}
\resizebox{\columnwidth}{!}{
\begin{tabular}{l l c c c c c }
\toprule
\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{IRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
\midrule
\multirow{3}{*}{DEEP} 
& Index time(s)  & 4156 & 1128 & \textbf{189.89} & 7510 & 32843 \\
& Index size(GB)  &  4.6 & 0.92 & \textbf{0.80} & 1.43 & 2.41  \\
& Peak memory(GB) &  7.78 & 3.54 & \textbf{1.38} & 2.61 & 7.08   \\
% \cmidrule{1-7}
\midrule
\multirow{3}{*}{YT-Audio} 
& Index time(s)   & 15314 & 1039 & \textbf{187.20} & 5905 & 30904    \\
& Index size(GB)    & 4.3 & \textbf{0.7} & 1.04 & 1.55 & 1.32  \\
& Peak memory(GB)   & 7.5 & 3.16 & \textbf{1.57} & 2.97 & 6.95  \\
\midrule
\multirow{3}{*}{WIT} 
& Index time(s)  & 29492 & 7068 & \textbf{828.12} & 28759 & 94909\\
& Index size(GB) &  4.2 & \textbf{1.5 }& 15.34 & 8.71 & 1.59  \\
& Peak memory(GB)  & 21.7 & \textbf{12.32} & 15.87 & 24.38 & 15.29\\
% \cmidrule{1-7}

\bottomrule
\end{tabular}
}
\end{table}
Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate three key metrics mentioned above in \textit{Range Filtering} algorithms.

\vspace{0.5em}
\textit{\textbf{Index construction time.}}
As shown in Table \ref{tab:Range Filtered}, SeRF achieves the fastest index construction time among the five algorithms. It incrementally builds the index in attribute order. It requires only a single pass and adds edges within local graphs. The structure is simple, with no redundant operations.

In contrast, WinFilter has the longest construction time. This is mainly due to its tree-based structure, where each node requires an independent nearest neighbor graph. This leads to significant redundant computations and high resource costs, especially for large datasets.
% 如表\ref{tab:Range Filtered}所示，在五种算法中，SeRF的构建时间最短，原因是其按属性值顺序增量构建的方式，仅需一次遍历并在局部图中添加边，结构简单、无冗余操作。而 WinFilter 的构建时间最长，主要由于其采用树状结构，在每个节点上需构建独立的近邻图索引，造成大量重复计算和资源开销，尤其在数据量大时更为明显。

\vspace{0.5em}

\textit{\textbf{Index size.}} Across the three datasets, IRange maintains a relatively small index size. It builds independent local neighbor graphs within each interval and merges indices dynamically during queries. This prevents space explosion. On low-dimensional datasets (Deep, YT-Audio), SeRF compresses the index using sparse vector distributions, keeping it small. However, in the high-dimensional WIT dataset with high LID, vector connectivity increases. This reduces compression efficiency, leading to a sharp rise in index size. DSG maintains a stable index size across datasets but is generally larger. It uses edge structures with interval labels to support streaming insertions and range queries, increasing storage overhead.
\vspace{0.5em}

\textit{\textbf{Peak memory usage.}}

In terms of peak memory usage, all five algorithms consume less memory on the first two datasets. However, memory usage increases significantly on WIT, likely due to its high dimensionality.

SeRF achieves the lowest memory usage on low-dimensional datasets. Its Segment Graph efficiently compresses sparse vector spaces. However, on high-dimensional datasets with high LID, the “curse of dimensionality” causes distance concentration. As a result, the index structure of SeRF expands rapidly, reducing compression efficiency.

In contrast, IRange achieves the lowest peak memory usage on WIT. It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges. Its index structure remains stable in high dimensions without significant graph growth. This effectively controls index size, making IRange more advantageous for high-dimensional datasets.
\vspace{0.5em}

\begin{figure*}[htbp]
  \centering
  \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{-0.4cm}
  \includegraphics[width=\textwidth]{figures/exp/exp_8_2.pdf}
  \caption{RF-ANN search }
  \label{fig:exp_8_2}
\end{figure*}
\subsubsection{Performance Evaluation. }

In this experiment, we follow the query range definition adopted by prior work~\cite{HQI}. Specifically, for a given query, if the range covers $n/2^i$ data points—where $n$ is the total dataset size—we define the range ratio as $2^{-i}$. Based on this definition, we evaluate algorithm performance under four query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.

Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios. The experimental results show that across all datasets (Deep, YT-Audio, and WIT) and query ranges, WinFilter consistently delivers the best performance. This highlights the robustness of its design, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.

iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes. In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios. However, by leveraging HNSW and bitmap-based post-filtering, UNIFY performs competitively under broader range conditions, demonstrating strong scalability.

SeRF exhibits relatively weak overall performance, with a significant drop in recall under small-range query scenarios. This suggests that while its compressed graph structure is space-efficient, it has a substantial negative impact on query performance.

It is important to note that this range query experiment is conducted under a fully static setting. Under such conditions, UNIFY, iRange, SeRF, and WinFilter require the dataset to be sorted by attribute prior to index construction. In contrast, DSG  support dynamic index construction with unordered attribute insertions, making them more suitable for streaming or incremental data scenarios. This flexibility highlights their superior extensibility in real-world applications.
\subsubsection{Robustness.}

\begin{figure*}[htbp]
    \centering
    \setlength{\abovecaptionskip}{0cm}
    \setlength{\belowcaptionskip}{-0.4cm}
    \includegraphics[width=\textwidth]{figures/exp/exp_8_3.pdf}
    \caption{Dataset Effect on RF-ANN Search}
    \label{fig:exp_8_3}
\end{figure*}

To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets. As shown in Figure~\ref{fig:exp_8_3}, the performance differences. All methods perform worst on WIT, which has the highest LID. On Deep and YT-Audio, which have similar LID, most algorithms achieve comparable performance. 
This suggests that the effectiveness of RF-ANN search is mainly influenced by Lid of the dataset. A higher LID inherently increases the difficulty of hybrid query.

However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID. This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.

\section{DISCUSSION}
Based on the performance of the algorithms on different experimental scenarios, we discuss our findings as follows.

\subsection{Recommendations.}
\subsubsection{\textbf{Attribute Filtering}}

\begin{table}[htbp]
\centering
\setlength{\abovecaptionskip}{0.05cm}
\caption{Algorithm Recommendation per Scenario}
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|c|c|}
\hline
\textbf{Scenario} & \textbf{Attribute Filtering} & \textbf{Range Filtering}\\
\hline
S1: Large-scale Datasets & Puck, UNG & iRange\\
\hline
S2: Fast Index Construction & ACORN-1, UNG  &SeRF, iRange\\
\hline
S3: Query on Hard Datasets & CAPS, UNG &iRange, DSG\\
\hline
S4: Query on Easy Datasets & StitchedVamana, NHQ & iRange\\

\hline
S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\
\hline
S6: Resource-constrained Environments & CAPS, Faiss&SeRF, IRange \\
\hline
S7: High-Recall Querying & UNG & WinFilter \\
\hline
\end{tabular}
}
\label{tab:algo_scenarios}
\vspace{-0.3cm}
\end{table}

We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.
Puck and UNG excel on large-scale datasets (S1); ACORN-1 and UNG achieve fast index construction (S2); CAPS performs best on hard datasets with high LID (S3), while NHQ, StitchedVamana, and UNG are superior for easy datasets with low LID (S4); Faiss and CAPS can generate relatively compact indexes with low memory usage, which is suitable for resource-constrained situations (S6); Milvus and Faiss serve as general-purpose solutions (S5); UNG stands out for its high recall, precision, and QPS (S7).

\subsubsection{\textbf{Range Filtering}}

% \end{tabular}
% \label{tab:range_algo_scenarios}
% \end{table}
Table~\ref{tab:algo_scenarios} also presents the application scenarios for range filtering. iRange demonstrates strong performance on large-scale datasets, combining efficient construction with excellent query capabilities (S1). For fast index construction, SeRF leads with iRange as a close second (S2). Both SeRF and iRange show superior memory efficiency (S6). When handling hard datasets, iRange and DSG are recommended (S3), while iRange also performs well on easy datasets (S4). For general-purpose applications, DSG supports dynamic updates while UNIFY provides flexible filtering strategies (S5). WinFilter emerges as the optimal choice for high-recall static queries (S7).

\subsection{Challenges}
\subsubsection{\textbf{Attribute Filtering}}
%修改语序
Most existing attribute filtering algorithms are graph-based, and they typically outperform other methods in terms of query accuracy and efficiency. However, graph-based algorithms often incur high indexing costs and significant memory overhead. In contrast, IVF algorithms  generally consume less memory but suffer from limited performance. Filtered−DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments. Moreover, the index construction phase of graph-based algorithms is computationally intensive. Therefore, exploring GPU-based acceleration for graph construction and vector computation during indexing is promising. It can significantly improve the performance of graph-based methods.

Furthermore, current attribute filtering algorithms offer limited support for complex filtering conditions. For example, Filtered-DiskANN  supports single-attribute filtering, and in multi-attribute scenarios, it only supports OR conditions between attributes. 
%The original implementations of 
NHQ and CAPS impose strict constraints on the number of base and query attributes and only support AND conditions. While UNG is relatively flexible—supporting both AND and OR logic—it still lacks support for arbitrary Boolean expressions (e.g., combinations of AND and OR). The lack of flexible Boolean filtering remains a key challenge, limiting the practicality of hybrid query methods in real-world systems with diverse and complex query requirements.

\subsubsection{\textbf{Range Filtering}}

Except for DSG, most Range Filtered algorithms require the dataset to be pre-sorted before building the index. Moreover, these methods do not support multi-attribute range queries. Enhancing these methods to support an arbitrary number of range-filterable attributes remains an open research challenge.

Our experiments show that graph compression methods often lead to poor query performance in RF-ANN search. To address this problem, subsequent algorithms usually optimize the index processing at the segment tree nodes. UNIFY newly proposes segment graphs and integrates multiple data structures to process queries. Although UNIFY performs slightly worse on small-range queries, its proposed index structure broadens the research direction.

It is also worth noting that range filtering and attribute filtering are both forms of hybrid queries. However, aside from vector databases and ACORN, few existing algorithms support both modalities simultaneously. Designing unified frameworks that simultaneously support both is an important research frontier.

Lastly, our findings show that the distribution and cardinality of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute-filtering methods. Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.

\section{CONCLUSION}

In this paper, we evaluate various hybrid query methods, including different algorithms , vector databases, and vector libraries. For attribute filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance. We then perform experiments on six real-world datasets to analyze the effectiveness of attribute filtering algorithms in depth. Additionally, we compare existing range filtering algorithms using three range query datasets. Finally, we provide a detailed analysis of the experimental results, summarize key findings, and highlight areas for improvement. Our study not only validates previous research but also offers insights for future work.

\clearpage

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample}
\end{sloppypar}
\end{document}
\endinput

### 2025-04-01 VLDB2026/main.tex
Update main.tex

@@
 \usepackage{balance}
-\usepackage{xeCJK}
+% \usepackage{xeCJK}
 \usepackage{enumitem}
 \usepackage{multirow}
-\usepackage{svg} % For SVG support
+% \usepackage{svg} % For SVG support
 \usepackage{graphicx}
@@
 
-Nearest Neighbor (NN) search \cite{cover1967nearest}aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems  \cite{monolith, Airbnb, Related_Pins_at_Pinterest, wang2018billion, pal2020pinnersage, okura2017embedding}  and image retrieval \cite{wang2012scalable}.
+Nearest Neighbor (NN) search \cite{cover1967nearest} aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems  \cite{monolith, Airbnb, Related_Pins_at_Pinterest, wang2018billion, pal2020pinnersage, okura2017embedding}  and image retrieval \cite{wang2012scalable}.
 % 需要添加引用，下面这段
@@
 
-（1）\textbf{ Systematic Classification and Overview.}
+(1)\textbf{ Systematic Classification and Overview.}
 We systematically classify more than ten representative attribute filtering algorithms from multiple dimensions, including index structure, filtering strategy, Boolean logic support, and index construction methods.
@@
 
-（2）\textbf{ Evaluation of Attribute-Filtering Algorithms.}
+(2)\textbf{ Evaluation of Attribute-Filtering Algorithms.}
 % We select several representative algorithms for Attribute Filtered ANN Search.
@@
 
-（3）\textbf{ Evaluation of Range-Filtering Algorithms.}
+(3)\textbf{ Evaluation of Range-Filtering Algorithms.}
 % We evaluate five main algorithms (SeRF, WinFilter, iRangeGraph, DSG, and UNIFY) for Range Filtered ANN Search.
@@
 
-（4）\textbf{ Recommendations and Challenges.}
-
+(4)\textbf{ Recommendations and Challenges.}
 Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
@@
 \noindent\textbf{\underline{UNG \cite{UNG}.}} 
-Graph-based methods（NHQ, Filtered-DiskANN, ACO-\\RN）do not guarantee result completeness, while CAPS lacks robustness when base and query vectors differ in attribute cardinality.
+Graph-based methods(NHQ, Filtered-DiskANN, ACO-\\RN)do not guarantee result completeness, while CAPS lacks robustness when base and query vectors differ in attribute cardinality.
 UNG is proposed to overcome both limitations.
@@
 Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets.
-SeRF allows incremental insertion but requires attributes to be ordered.
-DSG introduces the first truly dynamic RF-ANN framework that supports inserting data with unordered attributes while maintaining efficient range filtering.
-DSG is built on two key data structures.
-1) The rectangle tree partitions the query space into rectangular regions, each corresponding to a group of queries that share the same nearest neighbors.
-2) The dynamic segment graph is a neighbor graph where each edge is annotated with the attribute range in which it is valid.
-With these structures, only a few regions need to be updated when inserting new data. During queries, the system considers only edges valid for the current attribute range, improving efficiency.
+SeRF allows incremental insertion but requires ordered attributes.
+DSG introduces the first dynamic RF-ANN framework supporting data insertion with unordered attributes while maintaining efficient range filtering.
+DSG relies on two key data structures: 1) A rectangle tree partitions query space into rectangular regions, each corresponding to a group of queries sharing nearest neighbors.
+2) A dynamic segment graph is a neighbor graph where each edge is annotated with its valid attribute range.
+With these structures, only few regions need updates when inserting new data. During queries, the system considers only edges valid for current attribute range, boosting efficiency.
 
@@
         \setlength{\abovecaptionskip}{0cm}
+
         \setlength{\belowcaptionskip}{-0.3cm}
@@
 
-\vspace{0.5em}
-
 To investigate the performance of different attribute filtering algorithms during index construction, we evaluate three key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage.
@@
 
-\vspace{0.5em}
+\begin{figure*}
+    \centering
+        \setlength{\abovecaptionskip}{0cm}
+    \setlength{\belowcaptionskip}{-0.4cm}
+    \includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
+    \caption{Single-Attribute Building and Query (single thread) }
+    \label{fig:exp_1_1_SingleLabel_1thread}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \setlength{\abovecaptionskip}{0cm}
+    \setlength{\belowcaptionskip}{-0.4cm}
+    \includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
+    \caption{Single-Attribute Building and Query (16 threads)}
+    \label{fig:exp_1_2_SingleLabel_16thread}
+\end{figure*}
+
 \textit{\textbf{Index construction time.}}
@@
 
-\vspace{0.5em}
 \textit{\textbf{Index size.}}
 Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data.
-In order to unify the comparison standard, we include both the index structure generated by the algorithm and the original data when evaluating the index size.
+In order to unify the comparison standard,
+we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
+% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it.
+To ensure a consistent comparison, we consider both the index structure and the original data when measuring index size.
 As shown in the figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets.
 This overhead stems primarily from its extensive metadata requirements.
-Other methods demonstrate comparable index sizes, with Faiss consistently achieving the most compact representations through its efficient index design.
-
-\vspace{0.5em}
+The index sizes of other methods show minimal variation.
+Among these, Faiss generates slightly smaller indexes due to its efficient index design.
+
 \textit{\textbf{Peak memory usage.}}
@@
 %4.2.2
-
-\begin{figure*}
-    \centering
-        \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.4cm}
-    \includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
-    \caption{Single-Attribute Building and Query (single thread) }
-    \label{fig:exp_1_1_SingleLabel_1thread}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.4cm}
-    \includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
-    \caption{Single-Attribute Building and Query (16 threads)}
-    \label{fig:exp_1_2_SingleLabel_16thread}
-\end{figure*}
-
-%4.2.2
-
-\begin{figure}
-    \centering
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.1cm}
-    % 上面的图例，居中并可通过 hspace 调整左右位置
-    \hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-    \includegraphics[width=0.98\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
-    \vspace{-10pt} % 使用负值拉近两张图的距离，可以根据需要调整
-
-    % 下面的子图，居中显示
-    \includegraphics[width=0.9\columnwidth]{figures/exp/exp_2_1.pdf}
-    \caption{Effect of Multi-Attribute Index Construction on Single Query Performance.
-($S$ denotes single-attribute index construction and single-attribute query; $M$ denotes multi-attribute index construction and single-attribute query)}
-    \label{fig:exp_2_1}
-
-\end{figure}
 
@@
 
-\vspace{1em}
 \textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
@@
 
+\begin{figure}[th]
+    \centering
+    \setlength{\abovecaptionskip}{0cm}
+    \setlength{\belowcaptionskip}{-0.1cm}
+    % 上面的图例，居中并可通过 hspace 调整左右位置
+    \hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
+    \includegraphics[width=0.98\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
+    \vspace{-10pt} % 使用负值拉近两张图的距离，可以根据需要调整
+
+    % 下面的子图，居中显示
+    \includegraphics[width=0.8\columnwidth]{figures/exp/exp_2_1.pdf}
+    \caption{Effect of Multi-Attribute Index Construction on Single Query Performance.
+($S$ denotes single-attribute index construction and single-attribute query; $M$ denotes multi-attribute index construction and single-attribute query)}
+    \label{fig:exp_2_1}
+
+\end{figure}
+
 \textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
@@
 
-\vspace{10pt}
 \textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
@@
 The IVF-based algorithm CAPS, optimized for hybrid query scenarios, employs a multi-level partitioning strategy that introduces additional overhead.
-This overhead negatively impacts performance on small datasets.
+This overhead negatively impacts performan-\\ce on small datasets.
 However, on large datasets, the overhead is amortized, and the benefits of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
@@
 %4.2.7
-\textit{\textbf{Different Datasets .}}  
-To evaluate the performance of various methods across different datasets, we conduct experiments on six datasets.
-Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.
-
-As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.Because Audio has small scale, low dimensionality, and low LID.In contrast,all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset.
-Because these two dataset have the largest scale and highest LID.
-
-SIFT1M and Msong are similar datasets, with the key difference being that SIFT1M has lower dimensionality.
-The four algorithms (ACORN,Faiss,PASE, and NHQ) perform similarly on these two datasets, suggesting strong robustness to high dimensional dataset.
-In contrast, the remaining algorithms exhibit degraded performance on Msong, revealing a lack of adaptability to high dimensional dataset.
-
-Most algorithms struggle to achieve high recall on GloVe,because it has the highest LID.
-Compare to other algorithms, the four algorithms (UNG, Faiss, CAPS, and Milvus) manage to maintain relatively high recall, demonstrating better adaptability to complex datasets.
-Notably, although vanilla Faiss performs worse on SIFT1M compared to Enron dataset, Faiss+HQI\_Batch outperforms on SIFT1M.
-Because batch optimization in HQI reduces query overhead and increases throughput.
-
-\subsection{Range Filtering}
-Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we will only compare several range filtering algorithms.
-\subsubsection{Time and Space overhead of index construction.}
-
-\begin{table}[htbp]
+
+\begin{table}[t]
 \centering
@@
 % \cmidrule{1-7}
-
 \bottomrule
@@
 \end{table}
+
+\textit{\textbf{Different Datasets .}}  
+To evaluate the performance of various methods across different datasets, we conduct experiments on six datasets.
+Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.
+
+As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.Because Audio has small scale, low dimensionality, and low LID.In contrast,all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset.
+Because these two dataset have the largest scale and highest LID.
+
+SIFT1M and Msong are similar datasets, with the key difference being that SIFT1M has lower dimensionality.
+The four algorithms (ACORN,Faiss,PASE, and NHQ) perform similarly on these two datasets, suggesting strong robustness to high dimensional dataset.
+In contrast, the remaining algorithms exhibit degraded performance on Msong, revealing a lack of adaptability to high dimensional dataset.
+
+Most algorithms struggle to achieve high recall on GloVe,because it has the highest LID.
+Compare to other algorithms, the four algorithms (UNG, Faiss, CAPS, and Milvus) manage to maintain relatively high recall, demonstrating better adaptability to complex datasets.
+Notably, although vanilla Faiss performs worse on SIFT1M compared to Enron dataset, Faiss+HQI\_Batch outperforms on SIFT1M.
+Because batch optimization in HQI reduces query overhead and increases throughput.
+
+\subsection{Range Filtering}
+Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we will only compare several range filtering algorithms.
+\subsubsection{Time and Space overhead of index construction.}
+
 Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate three key metrics mentioned above in \textit{Range Filtering} algorithms.
 
-\vspace{0.5em}
 \textit{\textbf{Index construction time.}}
@@
 % 如表\ref{tab:Range Filtered}所示，在五种算法中，SeRF的构建时间最短，原因是其按属性值顺序增量构建的方式，仅需一次遍历并在局部图中添加边，结构简单、无冗余操作。而 WinFilter 的构建时间最长，主要由于其采用树状结构，在每个节点上需构建独立的近邻图索引，造成大量重复计算和资源开销，尤其在数据量大时更为明显。
-
-\vspace{0.5em}
 
@@
 It uses edge structures with interval labels to support streaming insertions and range queries, increasing storage overhead.
-\vspace{0.5em}
 
 \textit{\textbf{Peak memory usage.}}
-
 In terms of peak memory usage, all five algorithms consume less memory on the first two datasets. However, memory usage increases significantly on WIT, likely due to its high dimensionality.
@@
 This effectively controls index size, making IRange more advantageous for high-dimensional datasets.
-\vspace{0.5em}
 
@@
 \end{figure*}
+
 \subsubsection{Performance Evaluation. }
@@
 
+% \begin{figure*}[htbp]
+%     \centering
+%     \setlength{\abovecaptionskip}{0cm}
+%     \setlength{\belowcaptionskip}{-0.4cm}
+%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
+%     \caption{Dataset Effect on RF-ANN Search}
+%     \label{fig:exp_8_3}
+% \end{figure*}
 \begin{figure*}[htbp]
@@
     \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.4cm}
+    \setlength{\belowcaptionskip}{-0.5cm}
     \includegraphics[width=\textwidth]{figures/exp/exp_8_3.pdf}
@@
 
-\begin{table}[htbp]
+\begin{table}[t]
 \centering
@@
 \label{tab:algo_scenarios}
-\vspace{-0.3cm}
+\vspace{-0.1cm}
 \end{table}
@@
 For fast index construction, SeRF leads with iRange as a close second (S2).
-Both SeRF and iRange show superior memory efficiency (S6).
 When handling hard datasets, iRange and DSG are recommended (S3), while iRange also performs well on easy datasets (S4).
 For general-purpose applications, DSG supports dynamic updates while UNIFY provides flexible filtering strategies (S5).
+Both SeRF and iRange show superior memory efficiency (S6).
 WinFilter emerges as the optimal choice for high-recall static queries (S7).
@@
 %修改语序
-Most existing attribute filtering algorithms are graph-based, and they typically outperform other methods in terms of query accuracy and efficiency.
+Most existing attribute filtering algorithms are graph-based, %and 
+they typically outperform other methods in terms of query accuracy and efficiency.
 However, graph-based algorithms often incur high indexing costs and significant memory overhead.

### 2025-04-01 VLDB2026/main.tex
Create main.tex

@@
 
+\author{xxxxxxxx}
+\affiliation{%
+ \institution{Huazhong University of Science and Technology}
+}
+
+\author{xxxxxxxx}
+\affiliation{%
+ \institution{Huazhong University of Science and Technology}
+}
+
+\author{xxxxxxxx}
+\affiliation{%
+ \institution{Huazhong University of Science and Technology}
+}
+
+\author{xxxxxxxx}
+\affiliation{%
+ \institution{Huazhong University of Science and Technology}
+}
+
+\author{xxxxxxxx}
+\affiliation{%
+ \institution{Huazhong University of Science and Technology}
+}
+
+\author{xxxxxxxx}
+\affiliation{%
+ \institution{Huazhong University of Science and Technology}
+}
+
+\author{xxxxxxxx}
+\affiliation{%
+ \institution{Huazhong University of Science and Technology}
+}
+
+\author{xxxxxxxx}
+\affiliation{%
+ \institution{Huazhong University of Science and Technology}
+}
 %%
 %% The "author" command and its associated commands are used to define the authors and their affiliations.
-% \author{Ben Trovato}
+
+% \author{Mengzhao Wang$^1$, Xiaoliang Xu$^1$, Qiang Yue$^1$, Yuxiang Wang$^{1,*}$}
 % \affiliation{%
-%   \institution{Institute for Clarity in Documentation}
-%   \streetaddress{P.O. Box 1212}
-%   \city{Dublin}
-%   \state{Ireland}
-%   \postcode{43017-6221}
+%  \institution{$^1$Hangzhou Dianzi University, China}
 % }
-% \email{trovato@corporation.com}
-
-% \author{Lars Th{\o}rv{\"a}ld}
-% \orcid{0000-0002-1825-0097}
+% \email{{mzwang,xxl,yq,lsswyx}@hdu.edu.cn}
+% \author{Ben Trovato$^1$, Lars Th{\o}rv{\"a}ld$^2$, Valerie B\'eranger$^3$, J\"org von \"Arbach$^3$, Wang Xiu Ying$^3$, Donald Fauntleroy Duck$^3$}
+
 % \affiliation{%
-%   \institution{The Th{\o}rv{\"a}ld Group}
-%   \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-%   \city{Hekla}
-%   \country{Iceland}
+%   \institution{1. Institute for Clarity in Documentation, Ireland}
+%   \institution{2. The Th{\o}rv{\"a}ld Group, Iceland}
+%   \institution{3. Inria Paris-Rocquencourt, France}
 % }
-% \email{larst@affiliation.org}
-
-% \author{Valerie B\'eranger}
-% \orcid{0000-0001-5109-3700}
-% \affiliation{%
-%   \institution{Inria Paris-Rocquencourt}
-%   \city{Rocquencourt}
-%   \country{France}
-% }
-% \email{vb@rocquencourt.com}
-
-% \author{J\"org von \"Arbach}
-% \affiliation{%
-%   \institution{University of T\"ubingen}
-%   \city{T\"ubingen}
-%   \country{Germany}
-% }
-% \email{jaerbach@uni-tuebingen.edu}
-% \email{myprivate@email.com}
-% \email{second@affiliation.mail}
-
-% \author{Wang Xiu Ying}
-% \author{Zhe Zuo}
-% \affiliation{%
-%   \institution{East China Normal University}
-%   \city{Shanghai}
-%   \country{China}
-% }
-% \email{firstname.lastname@ecnu.edu.cn}
-
-% \author{Donald Fauntleroy Duck}
-% \affiliation{%
-%   \institution{Scientific Writing Academy}
-%   \city{Duckburg}
-%   \country{Calisota}
-% }
-% \affiliation{%
-%   \institution{Donald's Second Affiliation}
-%   \city{City}
-%   \country{country}
-% }
-% \email{donald@swa.edu}
-\author{Ben Trovato$^1$, Lars Th{\o}rv{\"a}ld$^2$, Valerie B\'eranger$^3$, J\"org von \"Arbach$^3$, Wang Xiu Ying$^3$, Donald Fauntleroy Duck$^3$}
-
-\affiliation{%
-  \institution{1. Institute for Clarity in Documentation, Ireland}
-  \institution{2. The Th{\o}rv{\"a}ld Group, Iceland}
-  \institution{3. Inria Paris-Rocquencourt, France}
-}
-
-\email{trovato@corporation.com, larst@affiliation.org, vb@rocquencourt.com, jaerbach@uni-tuebingen.edu, firstname.lastname@ecnu.edu.cn, donald@swa.edu}
+
+% \email{trovato@corporation.com, larst@affiliation.org, vb@rocquencourt.com, jaerbach@uni-tuebingen.edu, firstname.lastname@ecnu.edu.cn, donald@swa.edu}
 
@@
 
-Recent studies have shown that hybrid queries, including attribute filtering and range filtering, hold significant practical value.
-However, current evaluation efforts lack a unified benchmark and comprehensive testing.
-Existing research has failed to cover mainstream algorithms and has not systematically compared or deeply analyzed different methods.
-To address this issue, we have designed a complete evaluation framework for hybrid queries.
-Our study introduces more than ten hybrid query algorithms and systematically classifies them based on multiple dimensions such as index structure and filtering strategy, providing a reference for the categorization of hybrid queries.
-In the experimental section, for attribute filtering, we constructed standardized attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
-For range filtering, we systematically tested the algorithms' performance in these three aspects by varying the query ranges.
-Additionally, we conducted an in-depth analysis of the experimental results based on the underlying principles of the algorithms.
+Recent studies demonstrate the significant practical value of hybrid queries, which integrate vector search with structured filters (e.g., attribute and range filtering) for refined retrieval.
+However, current evaluations lack unified benchmarking standards and systematic assessment methodologies.
+Existing studies not only fail to cover mainstream algorithms but also omit systematic comparisons or in-depth analyses of different methods.
+To address this issue, we design a complete evaluation framework for hybrid queries.
+Our study introduces 15 hybrid query algorithms and systematically classifies them based on multiple dimensions such as index organization and filtering strategy, providing a reference for the categorization of hybrid queries.
+In the experiments, for attribute filtering, we construct standarded attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
+For range filtering, we systematically evaluate algorithm performance across these 3 metrics through controlled variation of query ranges.
+Additionally, we conduct an in-depth analysis of the experimental results based on the underlying principles of the algorithms.
 The extensive experimental results reveal the strengths and weaknesses of each algorithm.
-Based on these findings, we have developed a set of practical guidelines for algorithm selection, offering reliable references for different application scenarios.
-Furthermore, we have identified potential directions for improvement to address the current limitations of these algorithms.
+Based on these findings, we develop a set of practical guidelines for algorithm selection, offering reliable references for different application scenarios.
+Furthermore, we identify potential directions for improvement to address the current limitations of these algorithms.
 \vspace{-0.2cm}
@@
 However, with the exponential growth of data volume and the increasing dimensionality of vectors \cite{weber1998quantitative}, traditional NN search methods struggle to meet the demands of real-time search.
-To address this issue, researchers have turned to more efficient approaches—Approximate Nearest Neighbor search ~\cite{arya1998optimal,beis1997shape,gionis1999similarity,malkov2018efficient}.
+To address this issue, researchers turn to more efficient approaches - Approximate NN search ~\cite{arya1998optimal,beis1997shape,gionis1999similarity,malkov2018efficient}.
 ANN algorithms significantly improve search efficiency by constructing effective indexing structures, albeit at the cost of reduced accuracy.
@@
 Nevertheless, as application scenarios grow increasingly complex, simple ANN search can no longer satisfy all practical needs.
-For instance, as shown in Figure\ref{fig:hybrid ANNS}, users on e-commerce platforms may search for clothing items by retrieving visually similar products based on an image.
+For instance, Figure ~\ref{fig:hybrid ANNS} illustrates a case where users on e-commerce platforms search for clothing items by retrieving visually similar products based on an image.
 Additionally, users may impose further requirements such as price, color, or brand preferences.
 Such scenarios necessitate a retrieval system capable of simultaneously addressing vector similarity (e.g., product image) and attribute constraints (e.g., brand name) \cite{tian2023approximate}.
-When the constraint involves a specific attribute value, this problem is referred to as Attribute Filtering Approximate Nearest Neighbor (AF-ANN) search ~\cite{NHQ,Filtered-diskann} .
+When the constraint involves a specific attribute value, this problem refers to Attribute Filtering Approximate Nearest Neighbor (AF-ANN) search ~\cite{NHQ,Filtered-diskann} .
 For example, a user may seek a green piece of clothing.
-If the constraint involves a range condition, it is termed Range Filtering Approximate Nearest Neighbor (RF-ANN) search  ~\cite{serf,iRangeGraph}.
-For instance, filtering clothes priced between $100 and $200.
-To meet these application demands, hybrid query \cite{JD-e-commerce, analyticdb} techniques have emerged.
+If the constraint involves a range condition, the problem is known as Range Filtering Approximate Nearest Neighbor (RF-ANN) search ~\cite{serf,iRangeGraph}.
+For instance, filtering clothes priced between 100 and 200.
+To meet these application demands, hybrid query \cite{JD-e-commerce, analyticdb} techniques emerge.
 Hybrid queries integrate vector retrieval with conditional filtering, optimizing their interaction to significantly enhance efficiency and flexibility in complex query scenarios.
 
-% However, as application scenarios become more complex, simple ANN search is no longer sufficient to meet all practical needs.
-New requirements have emerged for ANN search systems.
-For example, as Figure \ref{fig:hybrid ANNS}, a user on an e-commerce platform may search for a dress by retrieving similar items based on an image.
-Additionally, the user can apply structured attribute filters such as price, color, or brand.
-This scenario necessitates a retrieval system that satisfies both vector similarity and attribute constraints \cite{tian2023approximate}.
-When the constraint is a Boolean condition—e.g., the user specifically requires a green dress—the problem is referred to as Attribute Filtering Approximate Nearest Neighbor (AF-ANN) search ~\cite{NHQ,Filtered-diskann} problem.
-If the constraint is a range condition, such as filtering dresses priced between 100 and 200, it becomes the Range Filtering Approximate Nearest Neighbor (RF-ANN) search ~\cite{serf,iRangeGraph} problem.
-To address such cases, hybrid query \cite{JD-e-commerce, analyticdb} has been proposed.
-It jointly optimizes vector retrieval and conditional filtering.
-This approach significantly improves efficiency and flexibility in complex query scenarios.
 \begin{figure*}
@@
 \subsection{Motivation}
-% 近年来，混合查询算法发展迅速，已有多种属性过滤或范围过滤工作被提出。尽管 BigANN 2023 大赛\cite{bigann2023}的 filter 赛道对部分算法进行了性能测试，但其评估仍存在局限性：1) 参赛算法数量有限，未能覆盖当前主流方法；2) 仅评估单属性和双属性查询，未涉及更复杂的多属性场景；3) 测试数据集的属性分布不够全面。此外，不同算法在索引构建的时空开销、查询性能随属性数量变化的表现、以及对不同属性分布的适应性等方面尚缺乏系统性评估。目前，大多数研究仅关注属性过滤或范围查询的单一问题，而未能全面衡量混合查询的整体性能。为此，我们基于混合查询进行完整实验评估，全面分析不同算法在索引构建成本、查询效率及鲁棒性等方面的表现。
-In recent years, hybrid query algorithms have developed rapidly, giving rise to numerous attribute filtering ~\cite{NHQ,diskann} and range-filtering algorithms \cite{serf,iRangeGraph}.
+
+In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute-filtering ~\cite{NHQ,diskann} and range-filtering algorithms \cite{serf,iRangeGraph}.
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
-As for range filtering algorithms, the size of the query range and the characteristics of different datasets also play an important role in determining algorithm performance.
-
-% In recent years, hybrid query algorithms have advanced rapidly, with numerous algorithms  proposed for attribute filtering and range filtering. 
-% In practice, the performance of hybrid query algorithms is also influenced by the characteristics of structured data.
-For attribute filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distributions \cite{UNG}, and attribute selectivity \cite{ACORN} all affect actual performance.
-For range filtering algorithms, query range size and different datasets will affect the performance of the algorithm.
-Despite BigANN 2023 \cite{bigann2023}  evaluating the performance of some algorithms, its study still has several notable limitations:
-1)The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods.
-For instance, NHQ and Filtered-DiskANN in attribute filtering algorithms have not been assessed.
-2)It focuses only on single-attribute and dual-attribute query scenarios, neglecting the more complex demands of multi-attribute queries.
+For attribute-filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
+As for range-filtering algorithms, the size of the query range and the characteristics of different datasets also play an important role in determining algorithm performance.
+
+Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some algorithms, it presents several notable limitations:
+1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods.
+For instance, attribute-filtering algorithms such as NHQ and UNG are not included in the evaluation.
+2) It focuses only on single-attribute and dual-attribute query scenarios, neglecting the more complex demands of multi-attribute queries.
 In real-world applications, an object typically involves multiple attributes.
-For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range, etc.) simultaneously when searching.
-3)It does not evaluate algorithm performance under different attribute distributions.
+For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.
+3) It does not evaluate algorithm performance under different attribute distributions.
 However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.
@@
 Moreover, aside from BigANN, there is currently a lack of systematic evaluation specifically targeting hybrid query algorithms.
-To fill this research gap, we conducted a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
-Additionally, we further assessed the robustness of each algorithm under varying conditions.
-
-% Although the filter track of the BigANN 2023 competition \cite{bigann2023} evaluated the performance of some algorithms, its assessment has several limitations: 
-% 1) The number of evaluated algorithms is limited, failing to cover mainstream methods. Mainstream attribute filtering algorithms such as NHQ and Filtered-DiskANN were not evaluated.
-% 2) The evaluation focuses only on single-attribute and dual-attribute queries, without considering more complex multi-attribute scenarios.
-However, in actual applications, an object often involves multiple attributes, and the same is true for queries.
-For example, in e-commerce scenarios, users often specify multiple attributes (such as color, brand, price range, etc.) for search at the same time.
-% 3) It did not include algorithm performance under different attribute distributions.
-Different distribution of attributes may have a direct impact on the filtering strategy and index construction of the hybrid query algorithm.
-% In addition, there is no relevant research to summarize and evaluate the relevant algorithms for hybrid queries.
-
-% Furthermore, with the exception of the BigANN competition, there has been no dedicated study that provides a comprehensive review and evaluation of hybrid query algorithms. 
-% In addition, apart from the BigANN competition, no dedicated evaluation of hybrid query algorithms exists.
-To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing index construction overhead and query efficiency across diverse scenarios.
-In addition, we assess the robustness of each algorithm.
-
-% Moreover, there has been no systematic evaluation of different algorithms in terms of index construction overhead, query performance across varying attribute numbers, and adaptability to different attribute distributions.
-Most existing studies focus solely on attribute filtering or range filtering, without providing a holistic assessment of hybrid queries.
-To address this gap, we conduct a comprehensive experimental evaluation of hybrid queries, analyzing the indexing overhead, query efficiency, and robustness of different algorithms.
-% In recent years, hybrid query algorithms have advanced rapidly, but their differences in attribute distribution adaptability and multi-attribute query performance have not been systematically evaluated.
-Although the filter track of the BigANN 2023 competition\cite{bigann2023} tested the performance of some algorithms, its evaluation scope has several limitations.
-First, the number of participating algorithms was limited, failing to cover the mainstream hybrid query algorithms.
-Second, the test dataset lacked diversity in attribute cardinality and attribute distribution, which may not fully reflect algorithm performance under different data characteristics.
-Third, the evaluation focused only on single-attribute and two-attribute query, without considering more complex multi-attribute scenarios, limiting the generalizability and practical value of the results.
-Moreover, the competition did not include evaluations of range filtered algorithms.
-
-% Based on this background, we aim to design a series of systematic experiments.
-We will construct diverse datasets for attribute filtered query and comprehensively evaluate mainstream hybrid query algorithms.
+To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
+Additionally, we further assess the robustness of each algorithm under varying conditions.
+
 \subsection{Our Contributions}
-% The core contribution of this study lies in the systematic evaluation of hybrid query algorithms, which specifically includes the following aspects:
-% We focus on ANN search in hybrid query scenarios. We systematically review and evaluate existing algorithms and systems. Our main contributions are summarized in four parts:
-This study focuses on the problem of ANN search in hybrid query scenarios and provides a comprehensive review and evaluation of existing algorithms and systems.
-The main contributions are summarized in the following four aspects.
+
+Our study focuses on the problem of ANN search in hybrid query scenarios and provides a comprehensive review and evaluation of existing algorithms and systems.
+The main contributions are summarized in the following 4 aspects.
 
 (1)\textbf{ Systematic Classification and Overview.}
-We systematically classify more than ten representative attribute filtering algorithms from multiple dimensions, including index structure, filtering strategy, Boolean logic support, and index construction methods.
-Additionally, we survey range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
-These efforts provide a unified reference framework for future research.
+We systematically classify 10 representative attribute-filtering algorithms from multiple dimensions, including index organization, filtering strategy, Boolean logic support, and index construction methods.
+Additionally, we survey range-filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
+These efforts provide a unified reference framework for future study.
 
 (2)\textbf{ Evaluation of Attribute-Filtering Algorithms.}
-% We select several representative algorithms for Attribute Filtered ANN Search.
-Using six real-world datasets, we evaluate their performance under different settings, such as the number of attributes, attribute distribution, and selectivity.
-We analyze their performance in terms of index construction time, index size,peak memory usage, query speed (QPS), and query accuracy.
-We also discuss their robustness and adaptability in complex scenarios.
-We experimentally evaluate 13 attribute filtering ANN algorithms on six real-world datasets.
-By analyzing the performance variations of these algorithms under different numbers of attributes, attribute distributions, and selectivity conditions, we reveal the strengths and weaknesses of each algorithm.
-Furthermore, we explore the robustness and adaptability of these algorithms under complex query conditions.
-Evaluation metrics include index construction time, index size, peak memory usage,QPS and search accuracy.
+We conduct a systematic evaluation of 13 attribute filtering algorithms on 6 real-world datasets.
+By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
+We further examine their behavior under different attribute distributions and selectivity conditions to assess robustness and adaptability in complex query scenarios.
+Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
 
 (3)\textbf{ Evaluation of Range-Filtering Algorithms.}
-% We evaluate five main algorithms (SeRF, WinFilter, iRangeGraph, DSG, and UNIFY) for Range Filtered ANN Search.
-We run experiments on three large-scale datasets with different query range settings.
-We compare their performance in index construction, storage usage, and query efficiency.
-We also study the effect of index structures on algorithm performance.
-This provides useful insights for future improvements.
-We benchmark five mainstream range filtering ANN algorithms on three large-scale datasets, using varying query range settings in the experiments.
-The results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-Additionally, we conduct an in-depth analysis of how index structures impact algorithm performance, providing valuable insights for algorithm design.
+We benchmark 5 mainstream range-filtering algorithms on 3 large-scale datasets, using varying query range settings in the experiments.
+The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
+Additionally, we conduct an in-depth analysis of how index organization impacts algorithm performance, providing valuable insights for algorithm design.
 
@@
 Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
-These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution.
+These challenges include limited Boolean logic support, the lack of multi-attribute range-filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution.
 Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.
@@
 
-However, to address the curse of dimensionality faced by NN search \cite{dimcurse}, existing researches focus on approximate solutions, known as ANN  search.
-We typically use $\text{Recall}@k = \frac{|R \cap \hat{R}|}{k}$ to evaluate the accuracy of ANN search algorithms, where $R$ denotes the true top-$k$ nearest neighbors of the query, $\hat{R}$ denotes the approximate top-$k$ nearest neighbors returned by the ANN search algorithm.
+However, to address the curse of dimensionality faced by NN search \cite{dimcurse}, existing studies focus on approximate solutions, known as ANN  search.
+We typically use $\text{Recall}@k = \frac{|R \cap \hat{R}|}{k}$ to evaluate the accuracy of ANN search algorithms, where $R$ denotes the true top-$k$ nearest neighbors of the query, and $\hat{R}$ denotes the approximate top-$k$ nearest neighbors returned by the ANN search algorithm.
 
 As the complexity of real-world application requirements increases, NN search has evolved into hybrid NN search with attribute constraints.
-Depending on the nature of the attribute constraints, hybrid NN search can be divided into two categories: 1) Attribute Filtering Nearest Neighbor (\textit{AF-NN}) search.
+Depending on the nature of the attribute constraints, hybrid NN search can be divided into 2 categories: 1) Attribute Filtering Nearest Neighbor (\textit{AF-NN}) search.
 2) Range Filtering Nearest Neighbor (\textit{RF-NN}) search.
@@
 
-\subsection{Index Structures in ANN Search}
-
-Current hybrid query methods mainly adopt graph-based ~\cite{nsw,kgraph,nsg,fanng,ngt} or Inverted File Index (IVF)-based \cite{PQ} index structures.
-We briefly introduce the fundamental principles of these two types in the following.
+\subsection{Index Organization in Hybrid ANN Search}
+
+Current hybrid query methods mainly adopt graph-based ~\cite{nsw,kgraph,nsg,fanng,ngt} or Inverted File Index (IVF)-based \cite{PQ} index organization.
+We briefly introduce the fundamental principles of these 2 types in the following.
 
@@
 In the graph index, each point maintains connections only to its nearest neighbors to preserve query efficiency.
-For instance, in Figure~\ref{fig:graph}, the gray point $c$ is connected to five neighbors $(a, b, d, e, f)$ and can traverse to them via corresponding edges.
+For instance, in Figure~\ref{fig:graph}, the gray point $c$ is connected to 5 neighbors $(a, b, d, e, f)$ and can traverse to them via corresponding edges.
 
 Given a query point $q$, the graph-based ANN search typically follows a greedy search strategy to find the $k$ nearest neighbors.
-For illustration, consider the case where $k = 1$ (i.e., finding the single nearest neighbor of $q$): The algorithm initiates the search from an entry point (the gray point $c$).
+For illustration, consider the case where $k = 1$ (i.e., 1NN): The algorithm initiates the search from an entry point (the gray point $c$).
 If there exists a neighbor $n$ (the point $f$) of the current point such that $\textit{dist}(n, q) < \textit{dist}(c, q)$, the algorithm updates the current point to $n$.
@@
 \vspace{1em}
-\noindent\textbf{\underline{IVF.}}
-IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
+\noindent\textbf{\underline{IVF.}} IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
 Specifically, as shown in Figure~\ref{fig:ivf}, IVF first selects a subset of data points and applies a clustering algorithm (e.g., K-Means) to obtain a set of centroids $(C_0, C_1, ..., C_6)$, each representing a distinct cluster.
@@
 
-We provide an overview and analysis of over ten hybrid query methods, all drawn from recent research efforts, and collectively referred to as algorithms in the following text.
-Specifically, Section~3.1 describes methods based on attribute filtering, Section~3.2 discusses those based on range filtering, and Section~3.3 introduces vector libraries and databases that support both attribute and range filters.
+We provide an overview and analysis of 15 hybrid query methods, all drawn from recent studies, and collectively referred to as algorithms in the following.
+Specifically, Section~3.1 describes methods for attribute filtering, Section~3.2 discusses those for range filtering, and Section~3.3 introduces vector libraries and databases that support both attribute filtering and range filtering.
 
 \vspace{-10pt}
-\subsection{Attribute Filtering Algorithms}
-
-We summarize six attribute filtering algorithms and provide an intuitive comparison in Table~\ref{tab:compair_1}.
+\subsection{Attribute-Filtering Algorithms}
+
+We summarize 6 attribute-filtering algorithms and provide an intuitive comparison in Table~\ref{tab:compair_1}.
 
@@
 \noindent\textbf{\underline{NHQ \cite{NHQ}.}}  
-Traditional attribute filtering algorithms usually perform attribute constraints and ANN search separately.
+Traditional attribute-filtering algorithms usually perform attribute constraints and ANN search separately.
 In contrast, NHQ is the first to implement simultaneous filtering, integrating both aspects into a unified framework.
@@
 Built upon the Vamana \cite{diskann} graph-based ANN index, it incorporates attribute information directly into the graph during index construction.
-This integration ensures that the index reflects both vector proximity and attribute constraints.
+This integration ensures that the index reflects both vector similarity and attribute constraints.
 Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.
 
-Filtered-DiskANN proposes two index variants:  
+Filtered-DiskANN proposes 2 index variants:  
 1) \textbf{FilteredVamana}, which incrementally builds the graph index by inserting data points and dynamically adding edges, allowing adaptive expansion.  
@@
 \vspace{1em}
-\noindent\textbf{\underline{CAPS \cite{CAPS}.}}  
-As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes.
+\noindent\textbf{\underline{CAPS \cite{CAPS}.}} As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes.
 CAPS addresses this issue by being the first simultaneous filtering algorithm based on spatial partitioning, significantly reducing index size.
@@
 
-ACORN is built upon HNSW \cite{hnsw}, a hierarchical graph-based ANN index.
+ACORN is built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}.
 It supports high-cardinality and unrestricted predicate sets, overcoming the limitations of methods restricted to small-scale equality filters.
 It constructs a denser hierarchical graph by expanding node neighborhoods and prunes edges at lower levels to control index size.
-During querying, ACORN eliminates unnecessary distance computations by filtering out nodes that violate attribute constraints.
+During the query process, ACORN eliminates unnecessary distance computations by filtering out nodes that violate attribute constraints.
 This effectively maintains a nearest neighbor graph over valid nodes only.
@@
 
-ACORN includes two index variants:  
+ACORN includes 2 index variants:  
 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
@@
 \vspace{1em}
-\noindent\textbf{\underline{UNG \cite{UNG}.}} 
-Graph-based methods(NHQ, Filtered-DiskANN, ACO-\\RN)do not guarantee result completeness, while CAPS lacks robustness when base and query vectors differ in attribute cardinality.
+\noindent\textbf{\underline{UNG \cite{UNG}.}} Graph-based methods (NHQ, Filtered-DiskANN, ACO-\\RN) do not guarantee result completeness, while CAPS lacks robustness when base and query vectors differ in attribute cardinality.
 UNG is proposed to overcome both limitations.
@@
 
-UNG supports Boolean filtering with two modes:  
+UNG supports Boolean filtering with 2 modes:  
 1) The query attribute set is a subset of the data attribute set.  
@@
 
-\subsection{Range Filtering Algorithms}
-
-We introduce five representative range filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.
+\subsection{Range-Filtering Algorithms}
+
+We introduce 5 representative range-filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.
 
@@
 \noindent\textbf{\underline{SeRF \cite{serf}.}}  
-Conventional RF-ANN search approaches typically follow one of two paradigms: 1) conducting ANN search first followed by attribute-based filtering; 2) filtering the dataset based on attribute ranges before performing ANN search.
+Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
+2) Filtering the dataset based on attribute ranges before performing ANN search.
 However, both approaches suffer from suboptimal performance.
@@
 DSG introduces the first dynamic RF-ANN framework supporting data insertion with unordered attributes while maintaining efficient range filtering.
-DSG relies on two key data structures: 1) A rectangle tree partitions query space into rectangular regions, each corresponding to a group of queries sharing nearest neighbors.
+DSG relies on two data structures: 1) A rectangle tree partitions query space into rectangular regions, each corresponding to a group of queries sharing nearest neighbors.
 2) A dynamic segment graph is a neighbor graph where each edge is annotated with its valid attribute range.
-With these structures, only few regions need updates when inserting new data. During queries, the system considers only edges valid for current attribute range, boosting efficiency.
+With these structures, only few regions need updates when inserting new data. During the query process, the system considers only edges valid for current attribute range, boosting efficiency.
 
@@
 SIG adheres to a graph inclusiveness principle: any query subgraph can be composed from existing segment graphs, avoiding the need for range-specific index construction.
-Its hierarchical variant, HSIG, enhances SIG by incorporating the multilayer design of HNSW, skip lists, and edge bitmaps for efficient range localization and post-filter pruning.
-UNIFY supports three filtering strategies—pre-filtering, post-filtering, and  simultaneous filtering—enabling robust and flexible performance across diverse application scenarios.
+Its hierarchical variant, HSIG, enhances SIG by incorporating the multilayer design of HNSW, skip lists, and edge bitmaps for efficient range localization and post-filtering pruning.
+UNIFY supports 3 filtering strategies—pre-filtering, post-filtering, and  simultaneous filtering—enabling robust and flexible performance across diverse application scenarios.
 
@@
 
-The vector libraries and databases discussed in this section are not explicitly designed for hybrid query, but they support both attribute filtering and range filtering.
+The vector libraries and databases discussed in the following are not explicitly designed for hybrid query, but they support both attribute filtering and range filtering.
 Additionally, all the functionalities shown in Table 1 are also supported.
@@
 \vspace{1em}
-\noindent\textbf{\underline{Faiss \cite{Faiss}.}}  
-Faiss is a library designed for efficient similarity search and clustering of dense vectors. It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.
+\noindent\textbf{\underline{Faiss \cite{Faiss}.}} Faiss is a library designed for efficient similarity search and clustering of dense vectors.
+It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.
 
@@
 Users can generate this selector by first applying custom attribute filtering methods.
-During the query, Faiss excludes vectors based on the selector, enabling efficient integration of attribute filtering with ANN search.
+During the query process, Faiss excludes vectors based on the selector, enabling efficient integration of attribute filtering with ANN search.
 
@@
 % Since this paper does not focus on query workload optimization, we adopt only the batch optimization strategy in our analysis.
-In addition, we adopted the batch optimization strategy of HQI~\cite{HQI} for the IVF index in Faiss.
+In addition, we adopt the batch optimization strategy of HQI~\cite{HQI} for the IVF index in Faiss.
 This strategy groups queries with the same filter conditions, performs filtering once per group, and then uses efficient matrix operations to perform batch vector similarity calculations.
@@
 By leveraging database capabilities, PASE enables both attribute filtering and range filtering.
-We focus on the post-filtering strategy based on HNSW.
+We focus on the post-filtering strategy based on HNSW, which facilitate comparison with other methods.
 
@@
 
-For attribute filtering tasks, we employ six real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, and Enron~\cite{enron2015}, covering a diverse range of domains.
+For attribute-filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, and Enron~\cite{enron2015}, covering a diverse range of domains.
 We independently generate attribute for each dataset.
 
-For range filtering queries, we evaluate three widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
+For range-filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
 Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
@@
 
-To comprehensively assess the overall performance of different algorithms, we adopt a multi-dimensional quantitative evaluation framework~\cite{compare}, which includes the following five core metrics:
+To comprehensively assess the overall performance of different algorithms, we adopt a multi-dimensional quantitative evaluation framework~\cite{compare}, which includes the following 5 core metrics:
 
@@
     \item \textbf{Index Size}: The storage size of the persisted index on disk.
-    \item \textbf{Peak Memory Usage}: The maximum memory consumption observed during the index construction phase.
+    \item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction.
 \end{enumerate}
@@
 
-For all evaluated algorithms, we adopt the parameter settings recommended in the original paper and adjust the parameters related to search in order to obtain different recall and QPS.
+For all evaluated algorithms, we adopt the parameter settings recommended in the original study and adjust the parameters related to search in order to obtain different recall and QPS.
 
@@
 Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}.
-By default, queries run on a single thread; we also report results for 16-thread parallelism in specific scenarios.
+By default, queries run on a single thread.
+We also report results for 16-thread parallelism in specific scenarios.
 
 We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1} and Table~\ref{tab:range_algo}.
-For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance characteristics.
+For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance.
 
@@
 
-To investigate the performance of different attribute filtering algorithms during index construction, we evaluate three key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage.
+To investigate the performance of different attribute filtering algorithms during index construction, we evaluate 3 key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage.
 Notably, PASE is evaluated exclusively on Audio, GloVe, Msong, and SIFT1M as it supports only data with dimensionality less than 512.
@@
 \textit{\textbf{Index construction time.}}
-As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned four datasets, PASE has the longest index construction time due to its single-threaded indexing support.
-Additionally, VBASE also supports only single-threaded indexing but achieves better query performance than PASE.
+As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 4 datasets, PASE has the longest index construction time due to its single-thread indexing support.
+Additionally, VBASE also supports only single-thread indexing but achieves better query performance than PASE.
 
@@
 To ensure a consistent comparison, we consider both the index structure and the original data when measuring index size.
-As shown in the figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets.
+As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets.
 This overhead stems primarily from its extensive metadata requirements.
-The index sizes of other methods show minimal variation.
+The index sizes of other methods show moderate variation.
 Among these, Faiss generates slightly smaller indexes due to its efficient index design.
@@
 On large-scale datasets, CPAS exhibits slightly lower memory usage compared to other algorithms.
-Due to their special characteristics, databases were not included in the peak memory usage testing during index construction.
+Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.
 
@@
 
-We next evaluate the query performance of AF-ANN search algorithms, focusing on three main scenarios.
+We next evaluate the query performance of AF-ANN search algorithms, focusing on 3 main scenarios.
 
 \textit{\textbf{Single-Attribute Building and Single-Attribute Query.}}
-In this scenario, we construct the index using a single attribute and issue queries on the same attribute.
-
-\textit{Single-Threaded Search.}  
+In this scenario, we construct the index using an attribute and apply filtering conditions on the same attribute.
+
+\textit{Single-Thread Search.}  
 As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under full-recall conditions (recall = 1), search often requires traversing larger candidate sets or deeper graph paths, leading to increased computational cost and a sharp QPS drop for most methods.
@@
 These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
-Additionally, we observe that Faiss+HQI\_Batch outperforms vanilla Faiss, indicating that batch querying via HQI can effectively enhance query performance.
-
-\textit{Multi-Threaded Search.}
+Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
+
+\textit{Multi-Thread Search.}
 As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance.
@@
 Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets.
-CAPS maintains a relatively high throughput under multi-threading but exhibits limited adaptability to different datasets.
+CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
 The vector distribution of the dataset affects the construction of its partitioned index.
@@
 \textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
-In this scenario, the index is constructed using multiple attributes but applies filtering condition on only one attribute during query processing.
+In this scenario, the index is constructed using multiple attributes but applies filtering condition on only one attribute during the query process.
 
@@
 As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
-In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: FilteredVamana increases the complexity introduced by retaining attribute during index construction; the complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs; The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness; UNG employs a distinct construction and search strategy, leading to a significant drop in query performance.
+In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drop significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
+2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs.
+3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness.
+4) UNG employs a distinct construction and search strategy, leading to a significant drop in query performance.
 
 \textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
-As shown in \ref{fig:exp_2_1}, Puck achieves the best query performance, surpassing other algorithms by an order of magnitude.
+As shown in Figur \ref{fig:exp_2_1}, Puck achieves the best query performance, surpassing other algorithms by an order of magnitude.
 It filters out irrelevant results during retrieval rather than searching for more candidates.
@@
         \includegraphics[width=\textwidth]{figures/exp/exp_3_1.pdf}
-        \caption{Effect of attribute distribution on on query performance (single thread)}
+        \caption{Effect of attribute distribution on query performance (single thread)}
         \label{fig:exp_3_1}
@@
 Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
-To evaluate algorithm performance under such scenario, we construct the index using three uniformly distributed attributes and apply filtering conditions on all three attributes simultaneously during the query process.
+To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.
 
@@
 Milvus, being a general-purpose system, exhibits comparatively poor performance.
-In contrast, Faiss—especially when combined with HQI\_Batch—achieves moderate performance.
+In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance.
 Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes.
@@
 NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets.
-It relies on fused distance calculations.
+It relies on fusion distance calculations.
 The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
 
-\subsubsection{Robustness}In this section, we evaluate the robustness of these algorithms.
-
-\textit{\textbf{Attribute Distribution.}} To comprehensively evaluate performance across different attribute distributions, we generate base and query attribute sets with four representative distributions—long-tailed, normal, power-law, and uniform—across the six datasets described in Section~4.1.1.
+\subsubsection{Robustness}In the following, we evaluate the robustness of these algorithms.
+
+\textit{\textbf{Attribute Distribution.}} To comprehensively evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
 We evaluate all algorithms under these distributions on each dataset.
@@
 Among all algorithms, ACORN-\(\gamma\) demonstrates the highest robustness.
-During its index construction, attribute is mainly used for pruning in the lowest layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
+During index construction, attribute is mainly used for pruning in the lowest layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
 As a result, changes in attribute distribution have a limited impact on overall performance.
@@
 As a post-filtering system, it performs significantly better under uniform distributions but degrades under long-tailed, normal, and power-law distributions.
-This degradation stems from the low selectivity of certain attributes in the last three distributions, which increases unnecessary distance computations, thus reducing overall efficiency.
+This degradation stems from the low selectivity of certain attributes in the last 3 distributions, which increases unnecessary distance computations, thus reducing overall efficiency.
 
@@
 \textit{\textbf{Single-Attribute Selectivity.}}
-In hybrid queries, different attribute selectivity (AS) levels can significantly affect computational cost and query efficiency, as the algorithm must effectively identify matching data points with specific attributes within a large dataset.
-AS refers to the proportion of data points in the dataset that share a specific attribute value.
-For example, an AS of 1\% indicates that only 1\% of the dataset satisfies the given attribute condition.
-
-To investigate this effect, we evaluate four AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset.
-Using a single-threaded execution environment, we compare the query performance of 13 algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
+In hybrid queries, varying levels of attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
+AS is defined as the proportion of data points sharing a given attribute value.
+For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute.
+
+To investigate this effect, we evaluate 4 AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset.
+Using a single-thread execution environment, we compare the query performance of 13 algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
 
@@
 
-According to the query performance trends of different algorithms under varying AS levels, we categorize the algorithms into three groups:
+According to the query performance trends of different algorithms under varying AS levels, we categorize the algorithms into 3 groups:
 
@@
 (1) \textit{Algorithms optimized for low AS levels.}  
-This category includes ACORN-1, CAPS, StitchedVamana, UNG, Faiss, Puck, and Faiss+HQI\_Batch, as illustrated in Figure~\ref{fig:exp_5_2_1}.
+This group includes ACORN-1, CAPS, StitchedVamana, UNG, Faiss, Puck, and Faiss+HQI\_Batch, as illustrated in Figure~\ref{fig:exp_5_2_1}.
 
@@
 \toprule
-\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{IRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
+\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
 \midrule
@@
 
-\textit{\textbf{Different Datasets .}}  
-To evaluate the performance of various methods across different datasets, we conduct experiments on six datasets.
+\textit{\textbf{Different Datasets.}}  
+To evaluate the performance of various methods across different datasets, we conduct experiments on 6 datasets.
 Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.
 
-As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.Because Audio has small scale, low dimensionality, and low LID.In contrast,all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset.
-Because these two dataset have the largest scale and highest LID.
+As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.
+Because Audio has small scale, low dimensionality, and low LID.
+In contrast, all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset.
+Because these two datasets have the largest scale and highest LID.
 
 SIFT1M and Msong are similar datasets, with the key difference being that SIFT1M has lower dimensionality.
-The four algorithms (ACORN,Faiss,PASE, and NHQ) perform similarly on these two datasets, suggesting strong robustness to high dimensional dataset.
-In contrast, the remaining algorithms exhibit degraded performance on Msong, revealing a lack of adaptability to high dimensional dataset.
-
-Most algorithms struggle to achieve high recall on GloVe,because it has the highest LID.
-Compare to other algorithms, the four algorithms (UNG, Faiss, CAPS, and Milvus) manage to maintain relatively high recall, demonstrating better adaptability to complex datasets.
+The 4 algorithms (ACORN, Faiss, PASE, and NHQ) perform similarly on these two datasets, suggesting strong robustness to high dimensional datasets.
+In contrast, the remaining algorithms exhibit degraded performance on Msong, revealing a lack of adaptability to high dimensional datasets.
+
+Most algorithms struggle to achieve high recall on GloVe, because it has the highest LID.
+Compare to other algorithms, the 4 algorithms (UNG, Faiss, CAPS, and Milvus) manage to maintain relatively high recall, demonstrating better adaptability to complex datasets.
 Notably, although vanilla Faiss performs worse on SIFT1M compared to Enron dataset, Faiss+HQI\_Batch outperforms on SIFT1M.
@@
 \subsection{Range Filtering}
-Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we will only compare several range filtering algorithms.
+Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range-filtering algorithms.
 \subsubsection{Time and Space overhead of index construction.}
 
-Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate three key metrics mentioned above in \textit{Range Filtering} algorithms.
+Similar to the evaluation of \textit{Attribute-Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range-Filtering} algorithms.
 
 \textit{\textbf{Index construction time.}}
-As shown in Table \ref{tab:Range Filtered}, SeRF achieves the fastest index construction time among the five algorithms.
+As shown in Table \ref{tab:Range Filtered}, SeRF achieves the fastest index construction time among the 5 algorithms.
 It incrementally builds the index in attribute order.
@@
 
-\textit{\textbf{Index size.}} Across the three datasets, IRange maintains a relatively small index size.
-It builds independent local neighbor graphs within each interval and merges indices dynamically during queries.
+\textit{\textbf{Index size.}} Across the 3 datasets, iRange maintains a relatively small index size.
+It builds independent local neighbor graphs within each interval and merges indices dynamically during the query process.
 This prevents space explosion.
@@
 \textit{\textbf{Peak memory usage.}}
-In terms of peak memory usage, all five algorithms consume less memory on the first two datasets. However, memory usage increases significantly on WIT, likely due to its high dimensionality.
+In terms of peak memory usage, all 5 algorithms consume less memory on the first 2 datasets. However, memory usage increases significantly on WIT, likely due to its high dimensionality.
 
@@
 
-In contrast, IRange achieves the lowest peak memory usage on WIT.
+In contrast, iRange achieves the lowest peak memory usage on WIT.
 It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
 Its index structure remains stable in high dimensions without significant graph growth.
-This effectively controls index size, making IRange more advantageous for high-dimensional datasets.
+This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
 
@@
 Specifically, for a given query, if the range covers $n/2^i$ data points—where $n$ is the total dataset size—we define the range ratio as $2^{-i}$.
-Based on this definition, we evaluate algorithm performance under four query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
+Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
 
@@
 On Deep and YT-Audio, which have similar LID, most algorithms achieve comparable performance.
-This suggests that the effectiveness of RF-ANN search is mainly influenced by Lid of the dataset. A higher LID inherently increases the difficulty of hybrid query.
+This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
 
@@
 \hline
-S6: Resource-constrained Environments & CAPS, Faiss&SeRF, IRange \\
+S6: Resource-constrained Environments & CAPS, Faiss&SeRF, iRange \\
 \hline
@@
 We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.
-Puck and UNG excel on large-scale datasets (S1); ACORN-1 and UNG achieve fast index construction (S2); CAPS performs best on hard datasets with high LID (S3), while NHQ, StitchedVamana, and UNG are superior for easy datasets with low LID (S4); Faiss and CAPS can generate relatively compact indexes with low memory usage, which is suitable for resource-constrained situations (S6); Milvus and Faiss serve as general-purpose solutions (S5); UNG stands out for its high recall, precision, and QPS (S7).
+Puck and UNG excel on large-scale datasets (S1).
+ACORN-1 and UNG achieve fast index construction (S2).
+CAPS performs best on hard datasets with high LID (S3), while NHQ, StitchedVamana, and UNG are superior for easy datasets with low LID (S4).
+Faiss and CAPS can generate relatively compact indexes with low memory usage, which is suitable for resource-constrained situations (S6).
+Milvus and Faiss serve as general-purpose solutions (S5).
+UNG stands out for its high recall, precision, and QPS (S7).
 
@@
 %修改语序
-Most existing attribute filtering algorithms are graph-based, %and 
+Most existing attribute-filtering algorithms are graph-based, %and 
 they typically outperform other methods in terms of query accuracy and efficiency.
@@
 
-Furthermore, current attribute filtering algorithms offer limited support for complex filtering conditions.
+Furthermore, current attribute-filtering algorithms offer limited support for complex filtering conditions.
 For example, Filtered-DiskANN  supports single-attribute filtering, and in multi-attribute scenarios, it only supports OR conditions between attributes.
@@
 
-Except for DSG, most Range Filtered algorithms require the dataset to be pre-sorted before building the index.
+Except for DSG, most range-filtering algorithms require the dataset to be pre-sorted before building the index.
 Moreover, these methods do not support multi-attribute range queries.
@@
 
-It is also worth noting that range filtering and attribute filtering are both forms of hybrid queries.
+It is also worth noting that range filtering and attribute filtering are both forms of hybrid query.
 However, aside from vector databases and ACORN, few existing algorithms support both modalities simultaneously.
@@
 
-In this paper, we evaluate various hybrid query methods, including different algorithms , vector databases, and vector libraries.
-For attribute filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance.
-We then perform experiments on six real-world datasets to analyze the effectiveness of attribute filtering algorithms in depth.
-Additionally, we compare existing range filtering algorithms using three range query datasets.
+In this paper, we evaluate various hybrid query methods, including different algorithms, vector databases, and vector libraries.
+For attribute-filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance.
+We then perform experiments on 6 real-world datasets to analyze the effectiveness of attribute-filtering algorithms in depth.
+Additionally, we compare existing range-filtering algorithms using 3 range query datasets.
 Finally, we provide a detailed analysis of the experimental results, summarize key findings, and highlight areas for improvement.

### 2025-04-01 VLDB2026/main.tex
Update main.tex

@@
 \documentclass[sigconf, nonacm]{acmart}
-\usepackage{fontspec}
+%\usepackage{fontspec}
 \usepackage{balance}
-% \usepackage{xeCJK}
 \usepackage{enumitem}
@@
 \begin{document}
-\begin{sloppypar}
+%\begin{sloppypar}
 
@@
 
-\author{xxxxxxxx}
+\author{Yan Li}
 \affiliation{%
- \institution{Huazhong University of Science and Technology}
+ \institution{Wuhan University of Technology}
 }
 
-\author{xxxxxxxx}
+\author{Bolong Zheng}
 \affiliation{%
@@
 \begin{abstract}
-% Approximate Nearest Neighbor (ANN) search is a foundational technique in fields such as recommendation systems and information retrieval.
-However, in practical applications, users not only expect search results to be similar to the query in vector space but also to satisfy specific constraints, such as price ranges or categories.
-To meet these demands, researchers have proposed various hybrid query algorithms, including attribute filtering and range filtering.
-However, especially for attribute filtering, existing datasets often lack attribute values, and different researchers use varied testing configurations with simplified attribute value settings in their evaluations.
-Therefore, we select multiple real-world datasets and generate rich attribute values for various query scenarios, establishing a unified and comprehensive evaluation framework to compare these algorithms.
-Our study establishes a systematic taxonomy of hybrid query algorithms, exhaustively evaluates their time-space tradeoffs, performance, and robustness, and ultimately provides practical recommendations for different application scenarios.
-
 Recent studies demonstrate the significant practical value of hybrid queries, which integrate vector search with structured filters (e.g., attribute and range filtering) for refined retrieval.
@@
 Furthermore, we identify potential directions for improvement to address the current limitations of these algorithms.
-\vspace{-0.2cm}
+%\vspace{-0.2cm}
 \end{abstract}
@@
 \subsubsection{\textbf{Attribute Filtering}}
-%修改语序
-Most existing attribute-filtering algorithms are graph-based, %and 
-they typically outperform other methods in terms of query accuracy and efficiency.
+Most existing attribute-filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
 However, graph-based algorithms often incur high indexing costs and significant memory overhead.
 In contrast, IVF algorithms generally consume less memory but suffer from limited performance.
-Filtered−DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
+Filtered-DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
 Moreover, the index construction phase of graph-based algorithms is computationally intensive.
@@
 \bibliography{sample}
-\end{sloppypar}
+%\end{sloppypar}
 \end{document}

### 2025-04-01 VLDB2026/main.tex
Update main.tex

@@
 \usepackage{microtype}  %处理换行
-
 \usepackage{subcaption} % 需要subcaption宏包支持子图
@@
 % leave empty if no availability url should be set
-\newcommand\vldbavailabilityurl{URL_TO_YOUR_ARTIFACTS}
+\newcommand\vldbavailabilityurl{https://github.com/zhujx001/Hybrid-ANNS-Experiment}
 % whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
@@
 \href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
-\vspace{-0.1cm}
 \endgroup
@@
 	\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
-The source code, data, and/or other artifacts have been made available at \url{https://github.com/zhujx001/Hybrid-ANNS}.
+	The source code, data, and/or other artifacts have been made available at \url{\vldbavailabilityurl}.
 	\endgroup
@@
 
-\par
 (1) \textit{Algorithms optimized for low AS levels.}  

### 2025-04-01 VLDB2026/main.tex
Update main.tex
change

@@
 
-\title{An Experimental Evaluation of Hybrid Query Algorithms}
-
-\author{xxxxxxxx}
+\title{An Experimental Evaluation of Hybrid Search Algorithms (EA\&B)}
+
+\author{Jiaxu Zhu}
 \affiliation{%
@@
 
-\author{xxxxxxxx}
+\author{Jiayu Yuan}
 \affiliation{%
@@
 
-\author{xxxxxxxx}
+\author{Kaiwen Yang}
 \affiliation{%
@@
 
-\author{xxxxxxxx}
+\author{Xiaobao Chen}
 \affiliation{%
@@
 
-\author{xxxxxxxx}
+\author{Shihuan Yu}
 \affiliation{%
@@
 
-\author{xxxxxxxx}
+\author{Hongchang Lv}
 \affiliation{%
@@
 Furthermore, we identify potential directions for improvement to address the current limitations of these algorithms.
-%\vspace{-0.2cm}
+
 \end{abstract}
@@
 \ifdefempty{\vldbavailabilityurl}{}{
-	\vspace{.3cm}
+
 	\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
@@
     \centering
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.4cm}
+%    \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{-0.4cm}
     \includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
     \caption{Hybrid query example}
-    % \vspace{-10pt} % 调整这个值来缩小空隙
+
     \label{fig:hybrid ANNS}
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{Graph.}}
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{IVF.}} IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
@@
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-        \setlength{\belowcaptionskip}{-0.3cm}
+
         \includegraphics[width=\linewidth]{figures/graph.pdf}
@@
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-        \setlength{\belowcaptionskip}{-0.3cm}
+
         \includegraphics[width=\linewidth]{figures/ivf.pdf}
@@
     \end{subfigure}
-    % \vspace{-10pt} % 调整这个值来缩小空隙
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{0.2cm}
+
+%    \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{0.2cm}
     \caption{Graph index and IVF index}
-    % \vspace{-2em} % 调整这个值来缩小空隙
+
 \end{figure}
@@
 	\centering
-        \setlength{\abovecaptionskip}{0.05cm}
         %\setlength{\belowcaptionskip}{-0.3cm}
@@
 
-    \vspace{0.2em}
 	\centering
@@
 	\end{minipage}}
-    \vspace{-0.5cm}
+
 \end{table*}
@@
 
-\vspace{-10pt}
 \subsection{Attribute-Filtering Algorithms}
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{NHQ \cite{NHQ}.}}  
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{Filtered-DiskANN \cite{Filtered-diskann}.}}  
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{CAPS \cite{CAPS}.}} As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes.
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{ACORN \cite{ACORN}.}}  
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{UNG \cite{UNG}.}} Graph-based methods (NHQ, Filtered-DiskANN, ACO-\\RN) do not guarantee result completeness, while CAPS lacks robustness when base and query vectors differ in attribute cardinality.
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{Puck \cite{puck}.}}  
@@
 	\centering
-        \setlength{\abovecaptionskip}{0.05cm}
+%        \setlength{\abovecaptionskip}{0.05cm}
         %\setlength{\belowcaptionskip}{-0.3cm}
-        \setlength{\textfloatsep}{0cm}
+%        \setlength{\textfloatsep}{0cm}
 	\caption{Comparison of RF-ANN search algorithms}
@@
 
-    \vspace{0.2em} % 调整间距
 	\footnotesize{
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{SeRF \cite{serf}.}}  
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{WinFilter \cite{winFilter}.}}  
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{iRange \cite{iRangeGraph}.}}  
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{DSG \cite{DSG}.}}   
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{UNIFY \cite{UNIFY}.}}  
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{Faiss \cite{Faiss}.}} Faiss is a library designed for efficient similarity search and clustering of dense vectors.
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{PASE \cite{pase}.}}  
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{VBASE \cite{vbase}.}}  
@@
 
-\vspace{1em}
 \noindent\textbf{\underline{Milvus \cite{milvus}.}}  
@@
 \centering
-% \vspace{-6pt} % 调整这个值来缩小空隙
+
 \setlength{\abovecaptionskip}{0.05cm}
@@
     \centering
-        \setlength{\abovecaptionskip}{0.3cm}
-        \setlength{\belowcaptionskip}{0cm}
+%        \setlength{\abovecaptionskip}{0.3cm}
+%        \setlength{\belowcaptionskip}{0cm}
 
@@
     \includegraphics[width=0.94\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径
-    \vspace{-12pt} % 使用负值拉近两张图的距离，可以根据需要调整
 
@@
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-
-        \setlength{\belowcaptionskip}{-0.3cm}
+%        \setlength{\abovecaptionskip}{0cm}
+%        
+%        \setlength{\belowcaptionskip}{-0.3cm}
         \includegraphics[width=\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
@@
 
-    \vspace{0.3cm} % 增加间距
-
     \begin{subfigure}{\columnwidth}
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-        \setlength{\belowcaptionskip}{-0.3cm}
+%        \setlength{\abovecaptionskip}{0cm}
+%        \setlength{\belowcaptionskip}{-0.3cm}
         \includegraphics[width=\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
@@
 
-    \vspace{0.3cm} % 增加间距
-
     \begin{subfigure}{\columnwidth}
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-        \setlength{\belowcaptionskip}{-0.3cm}
+%        \setlength{\abovecaptionskip}{0cm}
+%        \setlength{\belowcaptionskip}{-0.3cm}
         \includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
@@
     \centering
-        \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.4cm}
+%        \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{-0.4cm}
     \includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
@@
     \centering
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.4cm}
+%    \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{-0.4cm}
     \includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
@@
     \centering
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.1cm}
+%    \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{-0.1cm}
     % 上面的图例，居中并可通过 hspace 调整左右位置
@@
     \includegraphics[width=0.98\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
-    \vspace{-10pt} % 使用负值拉近两张图的距离，可以根据需要调整
 
@@
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-        \setlength{\belowcaptionskip}{-0.4cm}
+%        \setlength{\abovecaptionskip}{0cm}
+%        \setlength{\belowcaptionskip}{-0.4cm}
         \includegraphics[width=\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
@@
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-        \setlength{\belowcaptionskip}{-0.4cm}
+%        \setlength{\abovecaptionskip}{0cm}
+%        \setlength{\belowcaptionskip}{-0.4cm}
         \includegraphics[width=\textwidth]{figures/exp/exp_3_1.pdf}
@@
     \centering
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.1cm}
+%    \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{-0.1cm}
     \includegraphics[width=\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
@@
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-        \setlength{\belowcaptionskip}{0cm}
+%        \setlength{\abovecaptionskip}{0cm}
+%        \setlength{\belowcaptionskip}{0cm}
         \includegraphics[width=\textwidth]{figures/exp/exp_5_2_1.pdf}
@@
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-        \setlength{\belowcaptionskip}{0cm}
+%        \setlength{\abovecaptionskip}{0cm}
+%        \setlength{\belowcaptionskip}{0cm}
         \includegraphics[width=\textwidth]{figures/exp/exp_5_2_2.pdf}
@@
         \centering
-        \setlength{\abovecaptionskip}{0cm}
-        \setlength{\belowcaptionskip}{0cm}
+%        \setlength{\abovecaptionskip}{0cm}
+%        \setlength{\belowcaptionskip}{0cm}
         \includegraphics[width=\textwidth]{figures/exp/exp_5_2_3.pdf}
@@
 
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.4cm}
+%    \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{-0.4cm}
     \caption{Different AS under the same algorithm}
@@
 (1) \textit{Algorithms optimized for low AS levels.}  
-This group includes ACORN-1, CAPS, StitchedVamana, UNG, Faiss, Puck, and Faiss+HQI\_Batch, as illustrated in Figure~\ref{fig:exp_5_2_1}.
+This group includes ACORN-1, Faiss+HQI\_Batch, StitchedVamana, UNG, Faiss, Puck, and CAPS, as illustrated in Figure~\ref{fig:exp_5_2_1}.
 
@@
     \centering
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.4cm}
+%    \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{-0.4cm}
     \includegraphics[width=\textwidth]{figures/exp/exp_6_1.pdf}
@@
 \caption{Time and space overhead of range filtering index construction}
-% \vspace{-7pt}
+
 \label{tab:Range Filtered}
@@
   \centering
-  \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.4cm}
+%  \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{-0.4cm}
   \includegraphics[width=\textwidth]{figures/exp/exp_8_2.pdf}
@@
     \centering
-    \setlength{\abovecaptionskip}{0cm}
-    \setlength{\belowcaptionskip}{-0.5cm}
+%    \setlength{\abovecaptionskip}{0cm}
+%    \setlength{\belowcaptionskip}{-0.5cm}
     \includegraphics[width=\textwidth]{figures/exp/exp_8_3.pdf}
@@
 \label{tab:algo_scenarios}
-\vspace{-0.1cm}
+
 \end{table}

### 2025-04-01 VLDB2026/main.tex
Update main.tex
change
Merge remote changes

@@
 
-\title{An Experimental Evaluation of Hybrid Search Algorithms (EA\&B)}
+\title{An Experimental Evaluation of Hybrid Vector Search (EA\&B)}
 
@@
 
-Nearest Neighbor (NN) search \cite{cover1967nearest} aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems  \cite{monolith, Airbnb, Related_Pins_at_Pinterest, wang2018billion, pal2020pinnersage, okura2017embedding}  and image retrieval \cite{wang2012scalable}.
+Nearest Neighbor (NN) search \cite{cover1967nearest} aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems  \cite{monolith}  and image retrieval \cite{wang2012scalable}.
 % 需要添加引用，下面这段
@@
     \centering
-%    \setlength{\abovecaptionskip}{0cm}
-%    \setlength{\belowcaptionskip}{-0.4cm}
+    \setlength{\abovecaptionskip}{0.1cm}
+    \setlength{\belowcaptionskip}{-0.2cm}
     \includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
@@
 
-%    \setlength{\abovecaptionskip}{0cm}
-%    \setlength{\belowcaptionskip}{0.2cm}
+    \setlength{\abovecaptionskip}{0.1cm}
+    \setlength{\belowcaptionskip}{0.2cm}
     \caption{Graph index and IVF index}
@@
         %\setlength{\belowcaptionskip}{-0.3cm}
-
+      \setlength{\abovecaptionskip}{0.1cm}
+     \setlength{\belowcaptionskip}{-0.2cm}
 	\caption{Comparison of AF-ANN search algorithms}
@@
 		\hline
+
 	\end{tabular}
@@
 	\centering
+%	 \setlength{\abovecaptionskip}{0cm}
+%	\setlength{\belowcaptionskip}{0.1cm}
     \footnotesize{
 	\begin{minipage}{\linewidth}
+		\vspace{0.1cm}
 		\textsuperscript{A} Post-filtering, 
@@
 	\end{minipage}}
-
+  \vspace{-0.3cm}
 \end{table*}
@@
 	\centering
-%        \setlength{\abovecaptionskip}{0.05cm}
-        %\setlength{\belowcaptionskip}{-0.3cm}
-%        \setlength{\textfloatsep}{0cm}
+        \setlength{\abovecaptionskip}{0.1cm}
+        \setlength{\belowcaptionskip}{-0.1cm}
+        \setlength{\textfloatsep}{0.1cm}
 	\caption{Comparison of RF-ANN search algorithms}
@@
     \centering
-%        \setlength{\abovecaptionskip}{0.3cm}
-%        \setlength{\belowcaptionskip}{0cm}
+        \setlength{\abovecaptionskip}{0.3cm}
+        \setlength{\belowcaptionskip}{0cm}
 
@@
         \centering
-%        \setlength{\abovecaptionskip}{0cm}
-%        
-%        \setlength{\belowcaptionskip}{-0.3cm}
+        \setlength{\abovecaptionskip}{0cm}
+        \setlength{\belowcaptionskip}{-0.1cm}
         \includegraphics[width=\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
@@
         \centering
-%        \setlength{\abovecaptionskip}{0cm}
-%        \setlength{\belowcaptionskip}{-0.3cm}
+        \setlength{\abovecaptionskip}{0cm}
+        \setlength{\belowcaptionskip}{-0.1cm}
         \includegraphics[width=\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
@@
         \centering
-%        \setlength{\abovecaptionskip}{0cm}
-%        \setlength{\belowcaptionskip}{-0.3cm}
+        \setlength{\abovecaptionskip}{0cm}
+        \setlength{\belowcaptionskip}{-0.1cm}
         \includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
@@
     \centering
-%    \setlength{\abovecaptionskip}{0cm}
-%    \setlength{\belowcaptionskip}{-0.1cm}
+    \setlength{\abovecaptionskip}{0.1cm}
+    \setlength{\belowcaptionskip}{-0.1cm}
     % 上面的图例，居中并可通过 hspace 调整左右位置
@@
         \centering
-%        \setlength{\abovecaptionskip}{0cm}
-%        \setlength{\belowcaptionskip}{-0.4cm}
+        \setlength{\abovecaptionskip}{0.1cm}
+        \setlength{\belowcaptionskip}{-0.4cm}
         \includegraphics[width=\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
@@
         \centering
-%        \setlength{\abovecaptionskip}{0cm}
-%        \setlength{\belowcaptionskip}{-0.4cm}
+\setlength{\abovecaptionskip}{0.1cm}
+\setlength{\belowcaptionskip}{-0.4cm}
         \includegraphics[width=\textwidth]{figures/exp/exp_3_1.pdf}
@@
     \centering
-%    \setlength{\abovecaptionskip}{0cm}
-%    \setlength{\belowcaptionskip}{-0.1cm}
+    \setlength{\abovecaptionskip}{0.1cm}
+    \setlength{\belowcaptionskip}{-0.1cm}
     \includegraphics[width=\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}

### 2025-04-08 VLDB2026/main.tex
Update main.tex
change  conclusion and Peak memory usage

@@
 \affiliation{%
- \institution{Wuhan University of Technology}
+ \institution{Huazhong University of Science and Technology}
 }
@@
 As shown in Figure~\ref{fig:memory_mb_comparison_query1}, on small-scale datasets, all methods except NHQ exhibit low memory usage.
-The substantially higher memory consumption of NHQ is attributed to its graph construction procedure, which requires loading the entire dataset into memory.
+This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
 On large-scale datasets, CPAS exhibits slightly lower memory usage compared to other algorithms.
@@
 Most existing attribute-filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
-However, graph-based algorithms often incur high indexing costs and significant memory overhead.
-In contrast, IVF algorithms generally consume less memory but suffer from limited performance.
 Filtered-DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.

### 2025-04-10 VLDB2026/main.tex
Update main.tex
change the filter type of ACORN

@@
         CAPS & IVF & C & Y & N & N & N & Y & Y \\
-        ACORN & Graph & C & Y & Y & Y & Y & Y & Y \\
+        ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
        UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 

### 2025-04-10 exp1-9/exp_3.py
change exp code

@@ -15,29 +15,37 @@ data_path = "/data/result"  # 请修改为实际路径
 
 libertine_font = fm.FontProperties(
     fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
-# 基础颜色列表
-colors = [
-    '#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', 
-    '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf',
-    '#1a55FF', '#FF4444', '#47D147', '#AA44FF', '#FF9933'
+colors = [ # 主色系（增强饱和度）
+ '#F39C12', # 深邃蓝（原#5E81AC提纯）
+ '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
+ '#E74C3C', # 警报红（原#BF616A加深）
+
+ '#2ECC71', # 翡翠绿
+
+ # 辅助色（强化对比）
+ '#48D1CC', # 土耳其蓝
+ '#9B59B6', # 宝石紫（原#B48EAD增饱和）
+ '#E67E22', # 南瓜橙（替换原#D08770）
+ '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
+ '#3498DB', # 荧光蓝（原#81A1C1提亮）
 ]
 
 plot_params = {
-    'markersize': 4,                # 标记大小
-    'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
-    'markeredgewidth': 1,         # 标记边缘宽度
-    'linewidth': 1.2           # 线条粗细
-}
-
-plot_legend_params = {
     'markersize': 6,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
 }
 
+plot_legend_params = {
+    'markersize': 8,                # 标记大小
+    'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
+    'markeredgewidth': 1,         # 标记边缘宽度
+    'linewidth': 1.2           # 线条粗细
+}
+
 line_styles = ['-', '--', '-.', '-', '--', '-.', '-', '--', '-.', '-', '--', '-.']
[…]

### 2025-04-10 exp1-9/exp_8_2.py

@@ -1,0 +1,365 @@
+import os
+import pandas as pd
+import numpy as np
+import glob
+import re
+import matplotlib.pyplot as plt
+from matplotlib.gridspec import GridSpec
+import matplotlib.font_manager as fm
+import warnings
+
+warnings.filterwarnings("ignore")
+
+# 定义数据路径
+data_path = "/data/rangefilter/result"  # 请修改为实际路径
+
+libertine_font = fm.FontProperties(
+    fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
+
+colors = [ # 主色系（增强饱和度）
+ '#F39C12', # 深邃蓝（原#5E81AC提纯）
+ '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
+ '#E74C3C', # 警报红（原#BF616A加深）
+
+ 
+ 
+ # 扩展高冲击力颜色
+ '#34495E', # 钢蓝灰（原#4C566A微调）
+
+ '#2ECC71', # 翡翠绿
+
+ # 辅助色（强化对比）
+ '#48D1CC', # 土耳其蓝
+ '#9B59B6', # 宝石紫（原#B48EAD增饱和）
+ '#E67E22', # 南瓜橙（替换原#D08770）
+ '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
+ '#3498DB', # 荧光蓝（原#81A1C1提亮）
+]
+
+plot_params = {
+    'markersize': 6,                # 标记大小
+    'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
+    'markeredgewidth': 1,         # 标记边缘宽度
+    'linewidth': 1.2           # 线条粗细
+}
+
+plot_legend_params = {
+    'markersize': 8,                # 标记大小
+    'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
+    'markeredgewidth': 1,         # 标记边缘宽度
+    'linewidth': 1.2           # 线条粗细
+}
+
+line_styles = ['-', '--', '-.', '-', '--', '-.', '-', '--', '-.', '-', '--', '-.']
+markers = ['o', 's', '^', 'D', 'v', 'p', 'h', 'X', '*', '+', 'x', '|', '1', '2', '3', '4']
+
+
+def get_all_result_files():
+    result_files = []
+    # Get all range directories (range_2, range_4, range_6, range_8)
[…]

### 2025-04-10 exp1-9/exp_5_2.py
change exp code

@@ -16,39 +16,47 @@ data_path = "/data/result"  # 请修改为实际路径
 libertine_font = fm.FontProperties(
     fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
 # 基础颜色列表
-colors = [
-    '#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', 
-    '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf',
-    '#1a55FF', '#FF4444', '#47D147', '#AA44FF', '#FF9933',
-    '#66CCCC', '#CC99FF', '#FF66B2', '#99CC00', '#47d147'
+colors = [ # 主色系（增强饱和度）
+ '#F39C12', # 深邃蓝（原#5E81AC提纯）
+ '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
+ '#E74C3C', # 警报红（原#BF616A加深）
+
+ '#2ECC71', # 翡翠绿
+
+ # 辅助色（强化对比）
+ '#48D1CC', # 土耳其蓝
+ '#9B59B6', # 宝石紫（原#B48EAD增饱和）
+ '#E67E22', # 南瓜橙（替换原#D08770）
+ '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
+ '#3498DB', # 荧光蓝（原#81A1C1提亮）
 ]
 
 plot_params = {
-    'markersize': 4,                # 标记大小
-    'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
-    'markeredgewidth': 1,         # 标记边缘宽度
-    'linewidth': 1.2           # 线条粗细
-}
-
-plot_legend_params = {
     'markersize': 6,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
 }
 
+plot_legend_params = {
+    'markersize': 8,                # 标记大小
+    'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
+    'markeredgewidth': 1,         # 标记边缘宽度
+    'linewidth': 1.2           # 线条粗细
+}
+
 line_styles = ['-', '--', '-.', '-', '--', '-.', '-', '--', '-.', '-', '--', '-.']
[…]

### 2025-04-11 VLDB2026/main.tex
Add files via upload
Modify the reason why UNG multi-label construction single-label search performs poorly
 and try again.

@@
 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness.
-4) UNG employs a distinct construction and search strategy, leading to a significant drop in query performance.
+4) The reason why UNG has poor performance is that each base vector has 8 attributes, but only one query attribute, which results in a large number of entry points that need to be traversed.
+It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.
 

### 2025-04-11 VLDB2026/main.tex
Add files via upload
Add caps Experiment 2-2

@@
 			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
-			CAPS & IVF & C & Y & N & N & N & Y & Y \\
+			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
 			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
@@
 
-	\noindent\textbf{\underline{UNG \cite{UNG}.}} Graph-based methods (NHQ, Filtered-DiskANN, ACO-\\RN) do not guarantee result completeness, while CAPS lacks robustness when base and query vectors differ in attribute cardinality.
-UNG is proposed to overcome both limitations.
+	\noindent\textbf{\underline{UNG \cite{UNG}.}} Graph-based methods (NHQ, Filtered-DiskANN, ACO-\\RN) do not guarantee result completeness. UNG is proposed to overcome both limitations.
 
@@
 Faiss offers an ID filtering mechanism, it operates solely during query execution and does not influence index building.
-CAPS requires that the number of attributes in a query match those used during index construction.
 ACORN-1 and ACORN-\(\gamma\) are specifically designed for single-attribute indexing.
@@
 %The original implementations of 
-NHQ and CAPS impose strict constraints on the number of base and query attributes and only support AND conditions.
+NHQ imposes strict constraints on the number of base and query attributes and only support AND conditions.
 While UNG is relatively flexible—supporting both AND and OR logic—it still lacks support for arbitrary Boolean expressions (e.g., combinations of AND and OR).

### 2025-04-14 exp1-9/exp_2.py
Revert "Merge branch 'main' of https://github.com/zhujx001/Hybrid-ANNS"
This reverts commit 8bb04b9d801713304c88506f7431ea6357882dc1, reversing
changes made to 9027b0d595526968d6730e2594e92382d81226ff.

@@ -23,27 +23,38 @@ libertine_font = fm.FontProperties(
 
 # 为每个算法定义唯一的颜色（标准版本和16位版本使用相同颜色）
 ALGORITHM_COLORS = {
-    'FilteredVamana': '#F39C12',     # 绿色
-    'StitchedVamana': '#6EC1E0',     # 红色
-    'NHQ': '#8FCB6B',           # 紫色
-    'Puck': '#E74C3C',          # 粉色
-    'UNG': '#34495E',           # 灰色
+    'ACORN-1': '#1f77b4',       # 蓝色
+    'ACORN-1-16': '#1f77b4',    # 蓝色
+    'ACORN-γ': '#ff7f0e',    # 橙色
+    'ACORN-γ-16': '#ff7f0e', # 橙色
+    'FilteredVamana': '#2ca02c',     # 绿色
+    'FilteredVamana-16': '#2ca02c',  # 绿色
+    'StitchedVamana': '#d62728',     # 红色
+    'StitchedVamana-16': '#d62728',  # 红色
+    'NHQ': '#9467bd',           # 紫色
+    'parlayivf-16': '#8c564b',     # 棕色
+    # 'puck': '#e377c2',          # 粉色
+    'puck-16': '#e377c2',       # 粉色 (添加puck-16)
+    'UNG': '#7f7f7f',           # 灰色
+    'UNG-16': '#7f7f7f',        # 灰色
 }
 
 # 为不同的数据集定义不同的线型
 DATASET_LINESTYLES = {
     'sift_1': '-',      # 实线
     'sift_2_1': '--',   # 虚线
+    'sift_2_2': '-.'    # 点划线
 }
 
 # 标记样式
 DATASET_MARKERS = {
     'sift_1': 'o',      # 圆形
-    'sift_2_1': '^',    # 方形
+    'sift_2_1': 's',    # 方形
+    'sift_2_2': '^'     # 三角形
 }
 
 plot_params = {
-    'markersize': 12,                # 标记大小
+    'markersize': 7,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 2,         # 标记边缘宽度
     'linewidth': 1.4        # 线条粗细
@@ -53,10 +64,12 @@ plot_params = {
 def get_result_files():
     # 目标算法列表，添加了puck-16
     target_algorithms = [
-        'FilteredVamana',
-        'StitchedVamana',
-        'NHQ', 'Puck',
[…]

### 2025-04-14 exp1-9/exp_3.py

@@ -15,37 +15,29 @@ data_path = "/data/result"  # 请修改为实际路径
 
 libertine_font = fm.FontProperties(
     fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
-colors = [ # 主色系（增强饱和度）
- '#F39C12', # 深邃蓝（原#5E81AC提纯）
- '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
- '#E74C3C', # 警报红（原#BF616A加深）
-
- '#2ECC71', # 翡翠绿
-
- # 辅助色（强化对比）
- '#48D1CC', # 土耳其蓝
- '#9B59B6', # 宝石紫（原#B48EAD增饱和）
- '#E67E22', # 南瓜橙（替换原#D08770）
- '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
- '#3498DB', # 荧光蓝（原#81A1C1提亮）
+# 基础颜色列表
+colors = [
+    '#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', 
+    '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf',
+    '#1a55FF', '#FF4444', '#47D147', '#AA44FF', '#FF9933'
 ]
 
 plot_params = {
-    'markersize': 6,                # 标记大小
+    'markersize': 4,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
 }
 
 plot_legend_params = {
-    'markersize': 8,                # 标记大小
+    'markersize': 6,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
 }
 
 line_styles = ['-', '--', '-.', '-', '--', '-.', '-', '--', '-.', '-', '--', '-.']
-markers = ['o', 's', '^', 'D', 'v', 'p', 'h', 'X', '*', 'P', 'x', 'd', '8', 'H', '6', '4']
+markers = ['o', 's', '^', 'D', 'v', 'p', 'h', 'X', '*', '+', 'x', '|', '1', '2', '3', '4']
 
 # 将算法分组（单线程和16线程）
[…]

### 2025-04-14 exp1-9/exp_5_2.py

@@ -16,47 +16,39 @@ data_path = "/data/result"  # 请修改为实际路径
 libertine_font = fm.FontProperties(
     fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
 # 基础颜色列表
-colors = [ # 主色系（增强饱和度）
- '#F39C12', # 深邃蓝（原#5E81AC提纯）
- '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
- '#E74C3C', # 警报红（原#BF616A加深）
-
- '#2ECC71', # 翡翠绿
-
- # 辅助色（强化对比）
- '#48D1CC', # 土耳其蓝
- '#9B59B6', # 宝石紫（原#B48EAD增饱和）
- '#E67E22', # 南瓜橙（替换原#D08770）
- '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
- '#3498DB', # 荧光蓝（原#81A1C1提亮）
+colors = [
+    '#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', 
+    '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf',
+    '#1a55FF', '#FF4444', '#47D147', '#AA44FF', '#FF9933',
+    '#66CCCC', '#CC99FF', '#FF66B2', '#99CC00', '#47d147'
 ]
 
 plot_params = {
-    'markersize': 6,                # 标记大小
+    'markersize': 4,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
 }
 
 plot_legend_params = {
-    'markersize': 8,                # 标记大小
+    'markersize': 6,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
 }
 
 line_styles = ['-', '--', '-.', '-', '--', '-.', '-', '--', '-.', '-', '--', '-.']
-markers = ['o', 's', '^', 'D', 'v', 'p', 'h', 'X', '*', 'P', 'x', 'd', '8', 'H', '6', '4']
[…]

### 2025-04-14 exp1-9/exp_6.py

@@ -17,18 +17,11 @@ data_path = "/data/result"  # 请修改为实际路径
 libertine_font = fm.FontProperties(
     fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
 
-colors = [ # 主色系（增强饱和度）
- '#F39C12', # 深邃蓝（原#5E81AC提纯）
- '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
- '#E74C3C', # 警报红（原#BF616A加深）
- '#2ECC71', # 翡翠绿
-
- # 辅助色（强化对比）
- '#48D1CC', # 土耳其蓝
- '#9B59B6', # 宝石紫（原#B48EAD增饱和）
- '#E67E22', # 南瓜橙（替换原#D08770）
- '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
- '#3498DB', # 荧光蓝（原#81A1C1提亮）
+# 基础颜色列表
+colors = [
+    '#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', 
+    '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf',
+    '#1a55FF', '#FF4444', '#47D147', '#AA44FF', '#FF9933'
 ]
 
 # 扩展线型和标记列表
@@ -36,14 +29,14 @@ line_styles = ['-', '--', '-.', '-', '--', '-.', '-', '--', '-.', '-', '--', '-.
 markers = ['o', 's', '^', 'D', 'v', 'p', 'h', 'X', '*', '+', 'x', '|', '1', '2', '3', '4']
 
 plot_params = {
-    'markersize': 6,                # 标记大小
+    'markersize': 4,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
 }
 
 plot_legend_params = {
-    'markersize': 8,                # 标记大小
+    'markersize': 6,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
@@ -219,18 +212,10 @@ def superscript(n):
 def plot_all_datasets_comparison(all_data):
[…]

### 2025-04-14 exp1-9/exp_8_2.py

@@ -1,365 +1,0 @@
-import os
-import pandas as pd
-import numpy as np
-import glob
-import re
-import matplotlib.pyplot as plt
-from matplotlib.gridspec import GridSpec
-import matplotlib.font_manager as fm
-import warnings
-
-warnings.filterwarnings("ignore")
-
-# 定义数据路径
-data_path = "/data/rangefilter/result"  # 请修改为实际路径
-
-libertine_font = fm.FontProperties(
-    fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
-
-colors = [ # 主色系（增强饱和度）
- '#F39C12', # 深邃蓝（原#5E81AC提纯）
- '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
- '#E74C3C', # 警报红（原#BF616A加深）
-
- 
- 
- # 扩展高冲击力颜色
- '#34495E', # 钢蓝灰（原#4C566A微调）
-
- '#2ECC71', # 翡翠绿
-
- # 辅助色（强化对比）
- '#48D1CC', # 土耳其蓝
- '#9B59B6', # 宝石紫（原#B48EAD增饱和）
- '#E67E22', # 南瓜橙（替换原#D08770）
- '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
- '#3498DB', # 荧光蓝（原#81A1C1提亮）
-]
-
-plot_params = {
-    'markersize': 6,                # 标记大小
-    'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
-    'markeredgewidth': 1,         # 标记边缘宽度
-    'linewidth': 1.2           # 线条粗细
-}
-
-plot_legend_params = {
-    'markersize': 8,                # 标记大小
-    'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
-    'markeredgewidth': 1,         # 标记边缘宽度
-    'linewidth': 1.2           # 线条粗细
-}
-
-line_styles = ['-', '--', '-.', '-', '--', '-.', '-', '--', '-.', '-', '--', '-.']
-markers = ['o', 's', '^', 'D', 'v', 'p', 'h', 'X', '*', '+', 'x', '|', '1', '2', '3', '4']
-
-
-def get_all_result_files():
-    result_files = []
-    # Get all range directories (range_2, range_4, range_6, range_8)
[…]

### 2025-04-14 exp1-9/exp_8_range.py

@@ -16,35 +16,21 @@ data_path = "/data/rangefilter/result"  # 请修改为实际路径
 libertine_font = fm.FontProperties(
     fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
 # 基础颜色列表
-colors = [ # 主色系（增强饱和度）
- '#F39C12', # 深邃蓝（原#5E81AC提纯）
- '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
- '#E74C3C', # 警报红（原#BF616A加深）
-
- 
- 
- # 扩展高冲击力颜色
- '#34495E', # 钢蓝灰（原#4C566A微调）
-
- '#2ECC71', # 翡翠绿
-
- # 辅助色（强化对比）
- '#48D1CC', # 土耳其蓝
- '#9B59B6', # 宝石紫（原#B48EAD增饱和）
- '#E67E22', # 南瓜橙（替换原#D08770）
- '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
- '#3498DB', # 荧光蓝（原#81A1C1提亮）
+colors = [
+    '#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', 
+    '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf',
+    '#1a55FF', '#FF4444', '#47D147', '#AA44FF', '#FF9933'
 ]
 
 plot_params = {
-    'markersize': 6,                # 标记大小
+    'markersize': 4,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
 }
 
 plot_legend_params = {
-    'markersize': 8,                # 标记大小
+    'markersize': 6,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
@@ -360,15 +346,8 @@ def plot_3_4_comparison(all_data):
 # 创建一个新的函数用于绘制多线程算法图表
 def plot_1_6_comparison(all_data):
     range_set = ['range_2', 'range_8']
[…]

### 2025-04-14 exp1-9/exp_9.py

@@ -1,4 +1,3 @@
-'''实验一/四绘图代码'''
 import os
 import pandas as pd
 import numpy as np
@@ -19,23 +18,11 @@ libertine_font = fm.FontProperties(
     fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
 
 # 基础颜色列表
-colors = [ # 主色系（增强饱和度）
- '#F39C12', # 深邃蓝（原#5E81AC提纯）
- '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
- '#F39C12', # 亮橙
- '#E74C3C', # 警报红（原#BF616A加深）
- 
- # 扩展高冲击力颜色
- '#34495E', # 钢蓝灰（原#4C566A微调）
-
- '#2ECC71', # 翡翠绿
-
- # 辅助色（强化对比）
- '#48D1CC', # 土耳其蓝
- '#9B59B6', # 宝石紫（原#B48EAD增饱和）
- '#E67E22', # 南瓜橙（替换原#D08770）
- '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
- '#3498DB', # 荧光蓝（原#81A1C1提亮）
+colors = [
+    '#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', 
+    '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf',
+    '#1a55FF', '#FF4444', '#CC79A7', '#AA44FF', '#FF9933',
+    '#66CCCC', '#CC99FF', '#FF66B2', '#99CC00', '#47d147'
 ]
 
 
@@ -44,14 +31,14 @@ line_styles = ['-', '--', '-.', '-', '--', '-.', '-', '--', '-.', '-', '--', '-.
 markers = ['o', 's', '^', 'D', 'v', 'p', 'h', 'X', '*', '+', 'x', '|', '1', '2', '3', '4']
 
 plot_params = {
-    'markersize': 6,                # 标记大小
+    'markersize': 4,                # 标记大小
     'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
     'markeredgewidth': 1,         # 标记边缘宽度
     'linewidth': 1.2           # 线条粗细
 }
 
 plot_params_Legend = {
-    'markersize': 8,                # 标记大小
+    'markersize': 6,                # 标记大小
[…]

### 2025-04-14 exp1-9/exp_2.py
change vldb2026 plots

@@ -28,6 +28,7 @@ ALGORITHM_COLORS = {
     'NHQ': '#8FCB6B',           # 紫色
     'Puck': '#E74C3C',          # 粉色
     'UNG': '#34495E',           # 灰色
+    'CAPS': '#9B59B6',          # 橙色
 }
 
 # 为不同的数据集定义不同的线型
@@ -56,7 +57,7 @@ def get_result_files():
         'FilteredVamana',
         'StitchedVamana',
         'NHQ', 'Puck',
-        'UNG',
+        'UNG', 'CAPS'
     ]
     
     result_files = []
@@ -331,7 +332,9 @@ def create_standalone_legend():
     
     column3_items = [
         ('UNG', 'sift_1'),
-        ('UNG', 'sift_2_1')
+        ('UNG', 'sift_2_1'),
+        ('CAPS', 'sift_1'),
+        ('CAPS', 'sift_2_1')
     ]
     
     # Create three separate legend objects with much wider spacing

### 2025-04-14 exp1-9/exp_6.py

@@ -18,17 +18,13 @@ libertine_font = fm.FontProperties(
     fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
 
 colors = [ # 主色系（增强饱和度）
- '#F39C12', # 深邃蓝（原#5E81AC提纯）
- '#6EC1E0', # 电光冰蓝（原#88C0D0去灰）
- '#E74C3C', # 警报红（原#BF616A加深）
- '#2ECC71', # 翡翠绿
-
- # 辅助色（强化对比）
- '#48D1CC', # 土耳其蓝
- '#9B59B6', # 宝石紫（原#B48EAD增饱和）
- '#E67E22', # 南瓜橙（替换原#D08770）
- '#8FCB6B', # 苹果绿（原#A3BE8C增艳）
- '#3498DB', # 荧光蓝（原#81A1C1提亮）
+'#E74C3C', #(Alert Red)
+'#F39C12', #(Orange)
+'#2ECC71', #(Emerald Green)
+'#9B59B6', #(Gem Purple)
+'#48D1CC', #(Turquoise)
+'#3498DB', #(Fluorescent Blue)
+'#34495E', #(Steel Blue Gray)
 ]
 
 # 扩展线型和标记列表
@@ -218,7 +214,7 @@ def superscript(n):
 # 绘制所有数据集的QPS vs Recall对比图
 def plot_all_datasets_comparison(all_data):
     query_set = '1' # 这里假设我们只关心查询集1
-    datasets = ['sift', 'gist', 'glove-100', 'audio', 'msong', 'enron']
+    datasets = ['sift', 'gist', 'glove-100', 'audio', 'msong', 'enron', 'text2image']
     single_thread_algs = single_thread_algs = ['ACORN-1','ACORN-γ', 'CAPS', 'Faiss', 'Faiss+HQI_Batch', 'FilteredVamana', 'Milvus', 'NHQ', 'Puck', 'StitchedVamana', 'UNG', 'VBASE']
 
     # 为图例创建格式化后的数据集名称映射
@@ -228,7 +224,8 @@ def plot_all_datasets_comparison(all_data):
         'glove-100': 'GloVe',
         'audio': 'Audio',
         'msong': 'Msong',
-        'enron': 'Enron'
+        'enron': 'Enron',
+        'text2image': 'Text2Image'
     }
     
     # 预处理：收集所有算法并为它们分配统一的颜色、线型和标记
@@ -578,12 +575,12 @@ else:
[…]

### 2025-04-14 exp1-9/exp_8_2.py

@@ -232,12 +232,13 @@ def superscript(n):
 def plot_2_5_comparison(all_data):
     range_set = ['range_2', 'range_8']
     alg_set = ['DSG', 'IRange', 'SeRF', 'UNIFY', 'WinFilter','ACORN-1', 'ACORN-γ', 'Faiss', 'Milvus', 'VBASE']
-    datasets = ['wit', 'deep', 'yt8m']
+    datasets = ['wit', 'deep', 'yt8m', 'text2image']
     # 为图例创建格式化后的数据集名称映射
     dataset_display_names = {
         'wit': 'WIT',
         'deep': 'Deep',
-        'yt8m': 'YT-Audio'
+        'yt8m': 'YT-Audio',
+        'text2image': 'Text2Image'
     }
     
     dataset_colors = {}
@@ -353,7 +354,7 @@ else:
     print(f"成功加载数据，共有 {total_files} 个数据文件。")
     
     
-    print("创建1x5对比图...")
+    print("创建2x5对比图...")
     fig2 = plot_2_5_comparison(all_data)
     # save_path_svg = os.path.join("exp_8_2.svg")
     save_path_svg = os.path.join("/data/plots/exp","exp_8_3.svg")

### 2025-04-14 exp1-9/exp_6.py
change exp 6

@@ -271,7 +271,7 @@ def plot_all_datasets_comparison(all_data):
             pareto_df = compute_pareto_frontier(df, 'Recall', 'QPS')
             if not pareto_df.empty:
                 # 过滤 Recall 小于0.7以及等于1.01的数据
-                filtered_df = pareto_df[(pareto_df['Recall'] >= 0.7) & (pareto_df['Recall'] != 1.01)]
+                filtered_df = pareto_df[(pareto_df['Recall'] >= 0.4) & (pareto_df['Recall'] != 1.01)]
                 if not filtered_df.empty:
                     x_data = filtered_df['Recall'].tolist()
                     y_data = filtered_df['QPS'].tolist()
@@ -290,9 +290,9 @@ def plot_all_datasets_comparison(all_data):
         ax_single.tick_params(axis='both', labelsize=16)
 
         # 设置x轴范围为0.7到1.01，但仅显示刻度至1.0
-        ax_single.set_xlim(0.7, 1.01)
-        ax_single.set_xticks([0.7, 0.8, 0.9, 1.0])
-        ax_single.set_xticklabels([f"{tick:.1f}" for tick in [0.7, 0.8, 0.9, 1.0]])
+        ax_single.set_xlim(0.4, 1.01)
+        ax_single.set_xticks([0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0])
+        ax_single.set_xticklabels([f"{tick:.1f}" for tick in [0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0]])
         ax_single.axvline(x=0.95, color='gray', linestyle='--', alpha=0.7)
         ax_single.grid(True, linestyle=':', alpha=0.6)
         # 设置x轴标签

### 2025-04-14 VLDB2026/main.tex
Revert "Merge branch 'main' of https://github.com/zhujx001/Hybrid-ANNS"
This reverts commit 8bb04b9d801713304c88506f7431ea6357882dc1, reversing
changes made to 9027b0d595526968d6730e2594e92382d81226ff.
add CAPS exp 2

@@
 	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
-	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
-In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drop significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
+	As shown in Figure \ref{fig:exp_2_1}, Puck and CAPS demonstrate nearly no performance degradation.
+In contrast, the performance of FilteredVamana,StitchedVamana, NHQ, and UNG drop significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs.
@@
 	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
-	As shown in Figur \ref{fig:exp_2_1}, Puck achieves the best query performance, surpassing other algorithms by an order of magnitude.
-It filters out irrelevant results during retrieval rather than searching for more candidates.
+	As shown in Figur \ref{fig:exp_2_1}, CAPS has the best QPS performance, while Puck has better recall accuracy.
+CAPS first partitions by clustering, and then builds AFT under each partition.
+For CAPS, whether it is built with multiple attributes or a single attribute, the number of points required to be retrieved will not change after AFT filtering during search, so the performance is not greatly affected.
+Puck filters out irrelevant results during retrieval rather than searching for more candidates.
 FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, hurting single-attribute query efficiency.

### 2025-04-14 VLDB2026/main.tex
Update main.tex

@@
 	\textit{\textbf{Different Datasets.}}  
-	To evaluate the performance of various methods across different datasets, we conduct experiments on 6 datasets.
+	To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset for out-of-distribution (OOD) queries.
 Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.
@@
 Because Audio has small scale, low dimensionality, and low LID.
-In contrast, all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset.
+In contrast, all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset besides the OOD dataset Text2Image.
 Because these two datasets have the largest scale and highest LID.

### 2025-04-14 VLDB2026/main.tex
Update main.tex

@@
 
+	Most algorithms exhibit the worst performance on the OOD dataset text2image.
+However, ACORN, UNG, and FilteredVamana show relatively stable performance on text2image.
+Their performance drops less compared to in-distribution (ID) datasets such as GIST and GLOVE, indicating better adaptability to OOD queries.
+
 	\subsection{Range Filtering}

### 2025-04-14 exp1-9/exp_8_1.py
IRange 2 iRange

@@ -360,7 +360,7 @@ def plot_3_4_comparison(all_data):
 # 创建一个新的函数用于绘制多线程算法图表
 def plot_1_6_comparison(all_data):
     range_set = ['range_2', 'range_8']
-    alg_set = ['DSG', 'IRange', 'SeRF', 'UNIFY', 'WinFilter','ACORN-1', 'ACORN-γ', 'Faiss', 'Milvus', 'VBASE','PASE']
+    alg_set = ['DSG', 'iRange', 'SeRF', 'UNIFY', 'WinFilter','ACORN-1', 'ACORN-γ', 'Faiss', 'Milvus', 'VBASE','PASE']
     datasets = ['wit', 'deep', 'yt8m']
     
     # 为图例创建格式化后的数据集名称映射

### 2025-04-14 exp1-9/exp_8_2.py

@@ -231,7 +231,7 @@ def superscript(n):
 # 创建一个新的函数用于绘制多线程算法图表
 def plot_2_5_comparison(all_data):
     range_set = ['range_2', 'range_8']
-    alg_set = ['DSG', 'IRange', 'SeRF', 'UNIFY', 'WinFilter','ACORN-1', 'ACORN-γ', 'Faiss', 'Milvus', 'VBASE']
+    alg_set = ['DSG', 'iRange', 'SeRF', 'UNIFY', 'WinFilter','ACORN-1', 'ACORN-γ', 'Faiss', 'Milvus', 'VBASE']
     datasets = ['wit', 'deep', 'yt8m', 'text2image']
     # 为图例创建格式化后的数据集名称映射
     dataset_display_names = {

### 2025-04-14 VLDB2026/main.tex

@@
 		\setlength{\textfloatsep}{0.cm}
-		\caption{Datassets}
+		\caption{Datasets}
 
@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\[2pt]
+				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\[2pt]
 

### 2025-04-14 VLDB2026/main.tex

@@
 
+%	 修改此处
+	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
+
+	For third-party libraries and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
+Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
+With a smaller range, fewer points remain after filtering, resulting in lower computational cost.
+In addition, the performance of Faiss is influenced by data dimensionality; it tends to work better on low-dimensional datasets.
+
+	Vector databases also show relatively poor performance on range queries.
+Among them, Milvus performs better than the others, even surpassing ACORN under high recall settings.
+PASE performs poorly on small-range queries, with recall lower than 0.1, so it does not appear in Figure~\ref{fig:exp_8_2}.
+VPASE also performs better on large-range queries, but compared to PASE, its performance on small ranges is significantly better, achieving higher recall despite very low QPS.
+
 	It is important to note that this range query experiment is conducted under a fully static setting.

### 2025-04-14 VLDB2026/main.tex
range filter pic

@@
 	\textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
-	In this scenario, the index is constructed using multiple attributes but applies filtering condition on only one attribute during the query process.
-
-	In database systems (VBASE, PASE, Milvus), when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.
+	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query process.
+
 	 Faiss offers an ID filtering mechanism, it operates solely during query execution and does not influence index building.
 ACORN-1 and ACORN-\(\gamma\) are specifically designed for single-attribute indexing.
+In database systems (VBASE, PASE, Milvus), when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.
 Hence, they are excluded from this comparison.
@@
 	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
-	As shown in Figure \ref{fig:exp_2_1}, Puck and CAPS demonstrate nearly no performance degradation.
-In contrast, the performance of FilteredVamana,StitchedVamana, NHQ, and UNG drop significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
+	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
+In contrast, CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping.
+Compared with CAPS, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs.
 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness.
-4) The reason why UNG has poor performance is that each base vector has 8 attributes, but only one query attribute, which results in a large number of entry points that need to be traversed.
+4) UNG has poor performance because large number of entry points that need to be traversed.
 It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.
@@
 	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
-	As shown in Figur \ref{fig:exp_2_1}, CAPS has the best QPS performance, while Puck has better recall accuracy.
-CAPS first partitions by clustering, and then builds AFT under each partition.
-For CAPS, whether it is built with multiple attributes or a single attribute, the number of points required to be retrieved will not change after AFT filtering during search, so the performance is not greatly affected.
-Puck filters out irrelevant results during retrieval rather than searching for more candidates.
-FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, hurting single-attribute query efficiency.
-This leads to excessive irrelevant node traversal, making it slower than other methods.
+	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods.
+The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
+The performance of CPAS is as good as that of Puck.
+The difference between them is that CPAS further groups the results by attributes within clusters.
+In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries.
+This results in excessive traversal of irrelevant nodes, making it slower than other methods.
 
@@
 
-	\begin{table}[t]
-		\centering
-		\setlength{\abovecaptionskip}{0.05cm}
-		\caption{Time and space overhead of range filtering index construction}
-
-		\label{tab:Range Filtered}
-		\resizebox{\columnwidth}{!}{
-			\begin{tabular}{l l c c c c c }
-				\toprule
-				\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
-				\midrule
-				\multirow{3}{*}{DEEP} 
-				& Index time(s)  & 4156 & 1128 & \textbf{189.89} & 7510 & 32843 \\
-				& Index size(GB)  &  4.6 & 0.92 & \textbf{0.80} & 1.43 & 2.41  \\
-				& Peak memory(GB) &  7.78 & 3.54 & \textbf{1.38} & 2.61 & 7.08   \\
-				% \cmidrule{1-7}
-				\midrule
-				\multirow{3}{*}{YT-Audio} 
-				& Index time(s)   & 15314 & 1039 & \textbf{187.20} & 5905 & 30904    \\
-				& Index size(GB)    & 4.3 & \textbf{0.7} & 1.04 & 1.55 & 1.32  \\
-				& Peak memory(GB)   & 7.5 & 3.16 & \textbf{1.57} & 2.97 & 6.95  \\
-				\midrule
-				\multirow{3}{*}{WIT} 
-				& Index time(s)  & 29492 & 7068 & \textbf{828.12} & 28759 & 94909\\
-				& Index size(GB) &  4.2 & \textbf{1.5 }& 15.34 & 8.71 & 1.59  \\
-				& Peak memory(GB)  & 21.7 & \textbf{12.32} & 15.87 & 24.38 & 15.29\\
-				% \cmidrule{1-7}
-				\bottomrule
-			\end{tabular}
-		}
-	\end{table}
+	% \begin{table}[t]
+	% 	\centering
+	% 	\setlength{\abovecaptionskip}{0.05cm}
+	% 	\caption{Time and space overhead of range filtering index construction}
+
+	% 	\label{tab:Range Filtered}
+	% 	\resizebox{\columnwidth}{!}{
+	% 		\begin{tabular}{l l c c c c c }
+	% 			\toprule
+	% 			\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
+	% 			\midrule
+	% 			\multirow{3}{*}{DEEP} 
+	% 			& Index time(s)  & 4156 & 1128 & \textbf{189.89} & 7510 & 32843 \\
+	% 			& Index size(GB)  &  4.6 & 0.92 & \textbf{0.80} & 1.43 & 2.41  \\
+	% 			& Peak memory(GB) &  7.78 & 3.54 & \textbf{1.38} & 2.61 & 7.08   \\
+	% 			% \cmidrule{1-7}
+	% 			\midrule
+	% 			\multirow{3}{*}{YT-Audio} 
+	% 			& Index time(s)   & 15314 & 1039 & \textbf{187.20} & 5905 & 30904    \\
+	% 			& Index size(GB)    & 4.3 & \textbf{0.7} & 1.04 & 1.55 & 1.32  \\
+	% 			& Peak memory(GB)   & 7.5 & 3.16 & \textbf{1.57} & 2.97 & 6.95  \\
+	% 			\midrule
+	% 			\multirow{3}{*}{WIT} 
+	% 			& Index time(s)  & 29492 & 7068 & \textbf{828.12} & 28759 & 94909\\
+	% 			& Index size(GB) &  4.2 & \textbf{1.5 }& 15.34 & 8.71 & 1.59  \\
+	% 			& Peak memory(GB)  & 21.7 & \textbf{12.32} & 15.87 & 24.38 & 15.29\\
+	% 			% \cmidrule{1-7}
+	% 			\bottomrule
+	% 		\end{tabular}
+	% 	}
+	% \end{table}
 
@@
 	\subsubsection{Time and Space overhead of index construction.}
+	%4.2.1
+
+	\begin{figure}[t]
+		\centering
+		\setlength{\abovecaptionskip}{0.3cm}
+		\setlength{\belowcaptionskip}{0cm}
+
+		% 放大的图例（占满单栏）
+		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
+
+		\vspace{0.3cm}
+
+		% 三图横排
+		\begin{subfigure}[t]{0.31\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
+			\caption{Index construction time}
+			\label{fig:rangeFilter_build_time}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.31\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
+			\caption{Index size}
+			\label{fig:rangeFilter_ndex_size_mb}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.31\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
+			\caption{Peak memory usage}
+			\label{fig:rangeFilter_memory_mb}
+		\end{subfigure}
+
+		\caption{Time and space overhead of range filtering index construction}
+		\label{fig:rangeFilter_build_index_comparison}
+	\end{figure}
 
@@
 	\textit{\textbf{Index construction time.}}
-	As shown in Table \ref{tab:Range Filtered}, SeRF achieves the fastest index construction time among the 5 algorithms.
+, SeRF achieves the fastest index construction time among the 5 algorithms.
 It incrementally builds the index in attribute order.
@@
 	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
+Unlike other range-filtering algorithms, ACORN is not designed with specialized data structures  to achieve efficient range filtering.
+In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
 
@@
 
-	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets.
+To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we added an Out-of-Distribution (OOD) dataset to the three standard datasets and tested performance under large-range queries.
+As shown in Figure~\ref{fig:exp_8_3}, most methods performed worst on the Text2Image dataset.
+This is because OOD queries make the $k$-nearest neighbor distribution more sparse.
+As a result, the search needs to visit more nodes, which leads to an exponential growth in the search space and a sharp drop in efficiency.
+
+WinFilter showed the worst performance on the WIT dataset.
+This suggests that its performance is sensitive to the data dimensionality.
+ACORN had large performance differences across datasets, indicating weak robustness.
+
+Among vector databases, Milvus performed well. PASE was not included in this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
+
+It is worth noting that most methods achieved similar performance on the Deep and YT-Audio datasets, which have similar LID values.
+This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
+A high LID and high dimensionality make hybrid queries more difficult.
+
+However, even though Deep and YT-Audio have similar LID values, the DSG algorithm showed large performance differences between them.
+This means that DSG is more sensitive to changes in data distribution.
+Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.
+%	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets.
 As shown in Figure~\ref{fig:exp_8_3}, the performance differences.
@@
 On Deep and YT-Audio, which have similar LID, most algorithms achieve comparable performance.
-	This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
-
-	However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID.
+%	This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
+%	
+%	However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID.
 This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.

### 2025-04-15 VLDB2026/main.tex
Update main.tex

--- 2025-04-14 VLDB2026/main.tex
@@
 	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
+Unlike other range-filtering algorithms, ACORN is not designed with specialized data structures (such as the $\beta$-WST in WinFilter, the rectangle tree and dynamic segment graph in SeRF, or the HSIG in UNIFY) to achieve efficient range filtering.
+In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
 

### 2025-04-15 exp1-9/exp_2.py
change main.tex and exp_2

@@ -23,12 +23,12 @@ libertine_font = fm.FontProperties(
 
 # 为每个算法定义唯一的颜色（标准版本和16位版本使用相同颜色）
 ALGORITHM_COLORS = {
-    'FilteredVamana': '#F39C12',     # 绿色
-    'StitchedVamana': '#6EC1E0',     # 红色
-    'NHQ': '#8FCB6B',           # 紫色
+    'FilteredVamana': '#F39C12',     # 橙色
+    'StitchedVamana': '#316bea',     # 蓝色
+    'NHQ': '#00bf00',           # 绿色
     'Puck': '#E74C3C',          # 粉色
-    'UNG': '#34495E',           # 灰色
-    'CAPS': '#9B59B6',          # 橙色
+    'UNG': '#bfbf00',           # 灰色
+    'CAPS': '#AE73D0',          # 紫色
 }
 
 # 为不同的数据集定义不同的线型

### 2025-04-15 VLDB2026/main.tex
Update main.tex
change RFANN Robustness

--- 2025-04-14 VLDB2026/main.tex
@@
 
-	% \begin{table}[t]
-	% 	\centering
-	% 	\setlength{\abovecaptionskip}{0.05cm}
-	% 	\caption{Time and space overhead of range filtering index construction}
-
-	% 	\label{tab:Range Filtered}
-	% 	\resizebox{\columnwidth}{!}{
-	% 		\begin{tabular}{l l c c c c c }
-	% 			\toprule
-	% 			\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
-	% 			\midrule
-	% 			\multirow{3}{*}{DEEP} 
-	% 			& Index time(s)  & 4156 & 1128 & \textbf{189.89} & 7510 & 32843 \\
-	% 			& Index size(GB)  &  4.6 & 0.92 & \textbf{0.80} & 1.43 & 2.41  \\
-	% 			& Peak memory(GB) &  7.78 & 3.54 & \textbf{1.38} & 2.61 & 7.08   \\
-	% 			% \cmidrule{1-7}
-	% 			\midrule
-	% 			\multirow{3}{*}{YT-Audio} 
-	% 			& Index time(s)   & 15314 & 1039 & \textbf{187.20} & 5905 & 30904    \\
-	% 			& Index size(GB)    & 4.3 & \textbf{0.7} & 1.04 & 1.55 & 1.32  \\
-	% 			& Peak memory(GB)   & 7.5 & 3.16 & \textbf{1.57} & 2.97 & 6.95  \\
-	% 			\midrule
-	% 			\multirow{3}{*}{WIT} 
-	% 			& Index time(s)  & 29492 & 7068 & \textbf{828.12} & 28759 & 94909\\
-	% 			& Index size(GB) &  4.2 & \textbf{1.5 }& 15.34 & 8.71 & 1.59  \\
-	% 			& Peak memory(GB)  & 21.7 & \textbf{12.32} & 15.87 & 24.38 & 15.29\\
-	% 			% \cmidrule{1-7}
-	% 			\bottomrule
-	% 		\end{tabular}
-	% 	}
-	% \end{table}
+	\begin{table}[t]
+		\centering
+		\setlength{\abovecaptionskip}{0.05cm}
+		\caption{Time and space overhead of range filtering index construction}
+
+		\label{tab:Range Filtered}
+		\resizebox{\columnwidth}{!}{
+			\begin{tabular}{l l c c c c c }
+				\toprule
+				\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
+				\midrule
+				\multirow{3}{*}{DEEP} 
+				& Index time(s)  & 4156 & 1128 & \textbf{189.89} & 7510 & 32843 \\
+				& Index size(GB)  &  4.6 & 0.92 & \textbf{0.80} & 1.43 & 2.41  \\
+				& Peak memory(GB) &  7.78 & 3.54 & \textbf{1.38} & 2.61 & 7.08   \\
+				% \cmidrule{1-7}
+				\midrule
+				\multirow{3}{*}{YT-Audio} 
+				& Index time(s)   & 15314 & 1039 & \textbf{187.20} & 5905 & 30904    \\
+				& Index size(GB)    & 4.3 & \textbf{0.7} & 1.04 & 1.55 & 1.32  \\
+				& Peak memory(GB)   & 7.5 & 3.16 & \textbf{1.57} & 2.97 & 6.95  \\
+				\midrule
+				\multirow{3}{*}{WIT} 
+				& Index time(s)  & 29492 & 7068 & \textbf{828.12} & 28759 & 94909\\
+				& Index size(GB) &  4.2 & \textbf{1.5 }& 15.34 & 8.71 & 1.59  \\
+				& Peak memory(GB)  & 21.7 & \textbf{12.32} & 15.87 & 24.38 & 15.29\\
+				% \cmidrule{1-7}
+				\bottomrule
+			\end{tabular}
+		}
+	\end{table}
 
@@
 	\subsubsection{Time and Space overhead of index construction.}
-	%4.2.1
-
-	\begin{figure}[t]
-		\centering
-		\setlength{\abovecaptionskip}{0.3cm}
-		\setlength{\belowcaptionskip}{0cm}
-
-		% 放大的图例（占满单栏）
-		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
-
-		\vspace{0.3cm}
-
-		% 三图横排
-		\begin{subfigure}[t]{0.31\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
-			\caption{Index construction time}
-			\label{fig:rangeFilter_build_time}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.31\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
-			\caption{Index size}
-			\label{fig:rangeFilter_ndex_size_mb}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.31\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
-			\caption{Peak memory usage}
-			\label{fig:rangeFilter_memory_mb}
-		\end{subfigure}
-
-		\caption{Time and space overhead of range filtering index construction}
-		\label{fig:rangeFilter_build_index_comparison}
-	\end{figure}
 
@@
 	\textit{\textbf{Index construction time.}}
-, SeRF achieves the fastest index construction time among the 5 algorithms.
+	As shown in Table \ref{tab:Range Filtered}, SeRF achieves the fastest index construction time among the 5 algorithms.
 It incrementally builds the index in attribute order.

### 2025-04-15 VLDB2026/main.tex
range filter time and space

@@
 	\subsection{Range Filtering}
-	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range-filtering algorithms.
+
 	\subsubsection{Time and Space overhead of index construction.}
+	%4.2.1
+
+	\begin{figure}[t]
+		\centering
+		\setlength{\abovecaptionskip}{0.3cm}
+		\setlength{\belowcaptionskip}{0cm}
+
+		% 放大的图例（占满单栏）
+		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
+
+		\vspace{0.3cm}
+
+		% 三图横排
+		\begin{subfigure}[t]{0.31\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
+			\caption{Index construction time}
+			\label{fig:rangeFilter_build_time}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.31\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
+			\caption{Index size}
+			\label{fig:rangeFilter_index_size_mb}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.31\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
+			\caption{Peak memory usage}
+			\label{fig:rangeFilter_memory_mb}
+		\end{subfigure}
+
+		\caption{Time and space overhead of range filtering index construction}
+		\label{fig:rangeFilter_build_index_comparison}
+	\end{figure}
 
 	Similar to the evaluation of \textit{Attribute-Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range-Filtering} algorithms.
+	%serf: It incrementally builds the index in attribute order. It requires only a single pass and adds edges within local graphs. The structure is simple, with no redundant operations.
 
 	\textit{\textbf{Index construction time.}}
-	As shown in Table \ref{tab:Range Filtered}, SeRF achieves the fastest index construction time among the 5 algorithms.
-It incrementally builds the index in attribute order.
-It requires only a single pass and adds edges within local graphs.
-The structure is simple, with no redundant operations.
-
-	In contrast, WinFilter has the longest construction time.
-This is mainly due to its tree-based structure, where each node requires an independent nearest neighbor graph.
-This leads to significant redundant computations and high resource costs, especially for large datasets.
-	% 如表\ref{tab:Range Filtered}所示，在五种算法中，SeRF的构建时间最短，原因是其按属性值顺序增量构建的方式，仅需一次遍历并在局部图中添加边，结构简单、无冗余操作。而 WinFilter 的构建时间最长，主要由于其采用树状结构，在每个节点上需构建独立的近邻图索引，造成大量重复计算和资源开销，尤其在数据量大时更为明显。
-
-	\textit{\textbf{Index size.}} Across the 3 datasets, iRange maintains a relatively small index size.
-It builds independent local neighbor graphs within each interval and merges indices dynamically during the query process.
-This prevents space explosion.
-On low-dimensional datasets (Deep, YT-Audio), SeRF compresses the index using sparse vector distributions, keeping it small.
-However, in the high-dimensional WIT dataset with high LID, vector connectivity increases.
-This reduces compression efficiency, leading to a sharp rise in index size.
-DSG maintains a stable index size across datasets but is generally larger.
-It uses edge structures with interval labels to support streaming insertions and range queries, increasing storage overhead.
+	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. Faiss builds the index fastest.
+
+	WinFilter and ACORN-\(\gamma\) take the longest.
+	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
+
+	ACORN-\(\gamma\) expands each node’s neighbor list to offer more candidate paths, increasing computation and storage.
+It also prunes distant neighbors to reduce storage, but this adds extra overhead, slowing construction.
+
+	\textit{\textbf{Index size.}} 
+	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index structure because.
+On low-dimensional datasets (deep, yt-audio), PASE has the largest index size because its implementation may have wasteful alignment and padding of data structures, as well as the use of storage methods such as Base64 encoding, which significantly increase storage overhead.
+	The index size of SeRF on low-dimensional datasets is not large, but on high-dimensional datasets (wit), SeRF is forced to store more edges and dynamic range information, so the index increases significantly
 
 	\textit{\textbf{Peak memory usage.}}
-	In terms of peak memory usage, all 5 algorithms consume less memory on the first 2 datasets. However, memory usage increases significantly on WIT, likely due to its high dimensionality.
-
-	SeRF achieves the lowest memory usage on low-dimensional datasets.
-Its Segment Graph efficiently compresses sparse vector spaces.
-However, on high-dimensional datasets with high LID, the “curse of dimensionality” causes distance concentration.
-As a result, the index structure of SeRF expands rapidly, reducing compression efficiency.
-
-	In contrast, iRange achieves the lowest peak memory usage on WIT.
+	As shown in Figure~\ref{fig:rangeFilter_memory_mb}, For low-dimensional datasets (deep, yt-audio), Faiss takes up the lowest memory due to: . 
+	DSG and WinFilter take up significantly more memory than other algorithms due to.
+
+	For high-dimensional datasets WIT, iRange achieves the lowest peak memory usage.
 It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
@@
 This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
+	In contrast, unify takes up the highest memory due to
 

### 2025-04-15 VLDB2026/main.tex
change 4.3.1

@@
 
-	ACORN-\(\gamma\) expands each node’s neighbor list to offer more candidate paths, increasing computation and storage.
-It also prunes distant neighbors to reduce storage, but this adds extra overhead, slowing construction.
+	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
+It also prunes distant neighbors to save storage space; however, this introduces additional overhead and slows down the construction process.
 
@@
 	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index structure because. 
-On low-dimensional datasets (deep, yt-audio), PASE has the largest index size because its implementation may have wasteful alignment and padding of data structures, as well as the use of storage methods such as Base64 encoding, which significantly increase storage overhead.
-	The index size of SeRF on low-dimensional datasets is not large, but on high-dimensional datasets (wit), SeRF is forced to store more edges and dynamic range information, so the index increases significantly
-
+	On low-dimensional datasets (Deep, YT-Audio), PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding (e.g., Base64).
+
+	SeRF maintains a compact index for low-dimensional data. However, for high-dimensional datasets (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
 	\textit{\textbf{Peak memory usage.}}

### 2025-04-15 VLDB2026/main.tex
change attribute-filtering 2 attribute filtering

--- 2025-04-15 VLDB2026/main.tex
@@
 
-	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute-filtering ~\cite{NHQ,diskann} and range-filtering algorithms \cite{serf,iRangeGraph}.
+	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute filtering ~\cite{NHQ,diskann} and range filtering algorithms \cite{serf,iRangeGraph}.
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute-filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
-As for range-filtering algorithms, the size of the query range and the characteristics of different datasets also play an important role in determining algorithm performance.
+For attribute filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
+As for range filtering algorithms, the size of the query range and the characteristics of different datasets also play an important role in determining algorithm performance.
 
@@
 	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods.
-For instance, attribute-filtering algorithms such as NHQ and UNG are not included in the evaluation.
+For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation.
 2) It focuses only on single-attribute and dual-attribute query scenarios, neglecting the more complex demands of multi-attribute queries.
@@
 	(1)\textbf{ Systematic Classification and Overview.}
-	We systematically classify 10 representative attribute-filtering algorithms from multiple dimensions, including index organization, filtering strategy, Boolean logic support, and index construction methods.
-Additionally, we survey range-filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
+	We systematically classify 10 representative attribute filtering algorithms from multiple dimensions, including index organization, filtering strategy, Boolean logic support, and index construction methods.
+Additionally, we survey range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
 These efforts provide a unified reference framework for future study.
 
-	(2)\textbf{ Evaluation of Attribute-Filtering Algorithms.}
+	(2)\textbf{ Evaluation of Attribute Filtering Algorithms.}
 	We conduct a systematic evaluation of 13 attribute filtering algorithms on 6 real-world datasets.
@@
 
-	(3)\textbf{ Evaluation of Range-Filtering Algorithms.}
-	We benchmark 5 mainstream range-filtering algorithms on 3 large-scale datasets, using varying query range settings in the experiments.
+	(3)\textbf{ Evaluation of Range Filtering Algorithms.}
+	We benchmark 5 mainstream range filtering algorithms on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
@@
 	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
-These challenges include limited Boolean logic support, the lack of multi-attribute range-filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution.
+These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution.
 Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.
@@
 
-	\subsection{Attribute-Filtering Algorithms}
-
-	We summarize 6 attribute-filtering algorithms and provide an intuitive comparison in Table~\ref{tab:compair_1}.
+	\subsection{Attribute Filtering Algorithms}
+
+	We summarize 6 attribute filtering algorithms and provide an intuitive comparison in Table~\ref{tab:compair_1}.
 
 	\noindent\textbf{\underline{NHQ \cite{NHQ}.}}  
-	Traditional attribute-filtering algorithms usually perform attribute constraints and ANN search separately.
+	Traditional attribute filtering algorithms usually perform attribute constraints and ANN search separately.
 In contrast, NHQ is the first to implement simultaneous filtering, integrating both aspects into a unified framework.
@@
 
-	\subsection{Range-Filtering Algorithms}
-
-	We introduce 5 representative range-filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.
+	\subsection{Range Filtering Algorithms}
+
+	We introduce 5 representative range filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.
 
@@
 Each node in the tree corresponds to an attribute range and maintains a local ANN index (e.g., Vamana).
-For a range-filtering query, WinFilter only searches within nodes overlapping the query range and merges partial results.
+For a range filtering query, WinFilter only searches within nodes overlapping the query range and merges partial results.
 With a tree height of $O(\log n)$, each query accesses at most $O(\log n)$ sub-indexes, resulting in significant speedups.
@@
 
-	For attribute-filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, and Enron~\cite{enron2015}, covering a diverse range of domains.
+	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, and Enron~\cite{enron2015}, covering a diverse range of domains.
 We independently generate attribute for each dataset.
 
-	For range-filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
+	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
 Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
@@
 	\subsection{Range Filtering}
-	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range-filtering algorithms.
+	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range filtering algorithms.
 	\subsubsection{Time and Space overhead of index construction.}
 
-	Similar to the evaluation of \textit{Attribute-Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range-Filtering} algorithms.
+	Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
 
@@
 	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
-Unlike other range-filtering algorithms, ACORN is not designed with specialized data structures  to achieve efficient range filtering.
+Unlike other range filtering algorithms, ACORN is not designed with specialized data structures (such as the $\beta$-WST in WinFilter, the rectangle tree and dynamic segment graph in SeRF, or the HSIG in UNIFY) to achieve efficient range filtering.
 In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
@@
 
-To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we added an Out-of-Distribution (OOD) dataset to the three standard datasets and tested performance under large-range queries.
-As shown in Figure~\ref{fig:exp_8_3}, most methods performed worst on the Text2Image dataset.
-This is because OOD queries make the $k$-nearest neighbor distribution more sparse.
-As a result, the search needs to visit more nodes, which leads to an exponential growth in the search space and a sharp drop in efficiency.
-
-WinFilter showed the worst performance on the WIT dataset.
-This suggests that its performance is sensitive to the data dimensionality.
-ACORN had large performance differences across datasets, indicating weak robustness.
-
-Among vector databases, Milvus performed well. PASE was not included in this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
-
-It is worth noting that most methods achieved similar performance on the Deep and YT-Audio datasets, which have similar LID values.
-This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
-A high LID and high dimensionality make hybrid queries more difficult.
-
-However, even though Deep and YT-Audio have similar LID values, the DSG algorithm showed large performance differences between them.
-This means that DSG is more sensitive to changes in data distribution.
-Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.
-%	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets.
+	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets.
 As shown in Figure~\ref{fig:exp_8_3}, the performance differences.
@@
 On Deep and YT-Audio, which have similar LID, most algorithms achieve comparable performance.
-%	This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
-%	
-%	However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID.
+	This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
+
+	However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID.
 This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.
@@
 \subsubsection{\textbf{Attribute Filtering}}
-Most existing attribute-filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
+Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
 Filtered-DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
@@
 
-Furthermore, current attribute-filtering algorithms offer limited support for complex filtering conditions.
+Furthermore, current attribute filtering algorithms offer limited support for complex filtering conditions.
 For example, Filtered-DiskANN  supports single-attribute filtering, and in multi-attribute scenarios, it only supports OR conditions between attributes.
@@
 
-Except for DSG, most range-filtering algorithms require the dataset to be pre-sorted before building the index.
+Except for DSG, most range filtering algorithms require the dataset to be pre-sorted before building the index.
 Moreover, these methods do not support multi-attribute range queries.
@@
 
-Lastly, our findings show that the distribution and cardinality of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute-filtering methods.
+Lastly, our findings show that the distribution and cardinality of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
 Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.
@@
 In this paper, we evaluate various hybrid query methods, including different algorithms, vector databases, and vector libraries.
-For attribute-filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance.
-We then perform experiments on 6 real-world datasets to analyze the effectiveness of attribute-filtering algorithms in depth.
-Additionally, we compare existing range-filtering algorithms using 3 range query datasets.
+For attribute filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance.
+We then perform experiments on 6 real-world datasets to analyze the effectiveness of attribute filtering algorithms in depth.
+Additionally, we compare existing range filtering algorithms using 3 range query datasets.
 Finally, we provide a detailed analysis of the experimental results, summarize key findings, and highlight areas for improvement.

### 2025-04-15 VLDB2026/main.tex

@@
 
-	Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
+	Similar to the evaluation of \textit{Attribute-Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
 
@@
 
-	In contrast, WinFilter has the longest construction time.
-This is mainly due to its tree-based structure, where each node requires an independent nearest neighbor graph.
-This leads to significant redundant computations and high resource costs, especially for large datasets.
-	% 如表\ref{tab:Range Filtered}所示，在五种算法中，SeRF的构建时间最短，原因是其按属性值顺序增量构建的方式，仅需一次遍历并在局部图中添加边，结构简单、无冗余操作。而 WinFilter 的构建时间最长，主要由于其采用树状结构，在每个节点上需构建独立的近邻图索引，造成大量重复计算和资源开销，尤其在数据量大时更为明显。
-
-	\textit{\textbf{Index size.}} Across the 3 datasets, iRange maintains a relatively small index size.
-It builds independent local neighbor graphs within each interval and merges indices dynamically during the query process.
-This prevents space explosion.
-On low-dimensional datasets (Deep, YT-Audio), SeRF compresses the index using sparse vector distributions, keeping it small.
-However, in the high-dimensional WIT dataset with high LID, vector connectivity increases.
-This reduces compression efficiency, leading to a sharp rise in index size.
-DSG maintains a stable index size across datasets but is generally larger.
-It uses edge structures with interval labels to support streaming insertions and range queries, increasing storage overhead.
-
+	\textit{\textbf{Index construction time.}}
+	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. Faiss builds the index fastest.
+
+	WinFilter and ACORN-\(\gamma\) take the longest.
+	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
+
+	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
+It also prunes distant neighbors to save storage space; however, this introduces additional overhead and slows down the construction process.
+
+	\textit{\textbf{Index size.}} 
+	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index structure because. 
+	On low-dimensional datasets (Deep, YT-Audio), PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding (e.g., Base64).
+
+	SeRF maintains a compact index for low-dimensional data. However, for high-dimensional datasets (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
 	\textit{\textbf{Peak memory usage.}}
-	In terms of peak memory usage, all 5 algorithms consume less memory on the first 2 datasets. However, memory usage increases significantly on WIT, likely due to its high dimensionality.
-
-	SeRF achieves the lowest memory usage on low-dimensional datasets.
-Its Segment Graph efficiently compresses sparse vector spaces.
-However, on high-dimensional datasets with high LID, the “curse of dimensionality” causes distance concentration.
-As a result, the index structure of SeRF expands rapidly, reducing compression efficiency.
-
-	In contrast, iRange achieves the lowest peak memory usage on WIT.
+	As shown in Figure~\ref{fig:rangeFilter_memory_mb}, For low-dimensional datasets (deep, yt-audio), Faiss takes up the lowest memory due to: . 
+	DSG and WinFilter take up significantly more memory than other algorithms due to.
+
+	For high-dimensional datasets WIT, iRange achieves the lowest peak memory usage.
 It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
@@
 Moreover, these methods do not support multi-attribute range queries.
-Enhancing these methods to support an arbitrary number of range-filterable attributes remains an open research challenge.
+Enhancing these methods to support an arbitrary number of range filterable attributes remains an open research challenge.
 

### 2025-04-15 VLDB2026/main.tex
change Atttribute-flitering

@@
 
-	Similar to the evaluation of \textit{Attribute-Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
+	Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
 

### 2025-04-15 VLDB2026/main.tex
change 4.3.1

@@
 	\textit{\textbf{Index construction time.}}
-	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. Faiss builds the index fastest.
+	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time.
+Faiss builds the index fastest.
+Because Faiss obtains subsamples through sampling and then calculates the cluster centroid, the computational complexity is significantly reduced.
 
@@
 	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
-
 	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
@@
 	\textit{\textbf{Index size.}} 
-	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index structure because. 
+	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index structure.
+Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
 	On low-dimensional datasets (Deep, YT-Audio), PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding (e.g., Base64).
@@
 	SeRF maintains a compact index for low-dimensional data. However, for high-dimensional datasets (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
+
 	\textit{\textbf{Peak memory usage.}}
-	As shown in Figure~\ref{fig:rangeFilter_memory_mb}, For low-dimensional datasets (deep, yt-audio), Faiss takes up the lowest memory due to: . 
-	DSG and WinFilter take up significantly more memory than other algorithms due to.
-
-	For high-dimensional datasets WIT, iRange achieves the lowest peak memory usage.
-It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
-Its index structure remains stable in high dimensions without significant graph growth.
-This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
-	In contrast, unify takes up the highest memory due to
-
+	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
+It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.
+
+	DSG and WinFilter require significantly more memory than other methods.Because……
+
+	For the high-dimensional dataset WIT, iRange achieves the lowest peak memory.
+It pre-builds graphs only for select intervals, skipping full-range index construction.
+This design keeps the index compact even in high dimensions.
+
+	In contrast, Unify consumes the most memory because...
 	\begin{figure*}[htbp]

### 2025-04-15 VLDB2026/main.tex
change 4.3.1

@@
 	\subsubsection{Time and Space overhead of index construction.}
+	\begin{figure}[t]
+		\centering
+		\setlength{\abovecaptionskip}{0.3cm}
+		\setlength{\belowcaptionskip}{0cm}
+
+		% 放大的图例（占满单栏）
+		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
+
+		\vspace{0.3cm}
+
+		% 三图横排
+		\begin{subfigure}[t]{0.31\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
+			\caption{Index construction time}
+			\label{fig:rangeFilter_build_time}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.31\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
+			\caption{Index size}
+			\label{fig:rangeFilter_ndex_size_mb}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.31\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
+			\caption{Peak memory usage}
+			\label{fig:rangeFilter_memory_mb}
+		\end{subfigure}
+
+		\caption{Time and space overhead of range filtering index construction}
+		\label{fig:rangeFilter_build_index_comparison}
+	\end{figure}
 
 	Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
-
-	\textit{\textbf{Index construction time.}}
-	As shown in Table \ref{tab:Range Filtered}, SeRF achieves the fastest index construction time among the 5 algorithms.
-It incrementally builds the index in attribute order.
-It requires only a single pass and adds edges within local graphs.
-The structure is simple, with no redundant operations.
 

### 2025-04-15 VLDB2026/main.tex
change 3.1

@@
 
-	Filtered-DiskANN proposes 2 index variants:  
+	Filtered-DiskANN proposes 2 indexes:  
 	1) \textbf{FilteredVamana}, which incrementally builds the graph index by inserting data points and dynamically adding edges, allowing adaptive expansion.  
@@
 
-	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes.
+	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} Different from the above graph-based simultaneous filtering algorithms, CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
+	%As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes.
 CAPS addresses this issue by being the first simultaneous filtering algorithm based on spatial partitioning, significantly reducing index size.
@@
 	\noindent\textbf{\underline{ACORN \cite{ACORN}.}}  
-	Above simultaneous filtering methods struggle with large-scale, unbounded, or unknown predicate sets.
+	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
 	%The above simultaneous filtering methods are less effective in scenarios involving large-scale, unbounded, or unknown predicate sets, where a predicate refers to a condition or rule used for filtering.
@@
 
-	ACORN includes 2 index variants:  
+	ACORN includes 2 indexes:  
 	1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
@@
 
-	\noindent\textbf{\underline{UNG \cite{UNG}.}} Graph-based methods (NHQ, Filtered-DiskANN, ACO-\\RN) do not guarantee result completeness. UNG is proposed to overcome both limitations.
+	\noindent\textbf{\underline{UNG \cite{UNG}.}} The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
+UNG is proposed to overcome these limitations.
 

### 2025-04-15 VLDB2026/main.tex
Modification details

@@
 	\noindent\textbf{\underline{Puck \cite{puck}.}}  
-	While simultaneous filtering performs well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
+	While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
 In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
@@
 This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
-On large-scale datasets, CPAS exhibits slightly lower memory usage compared to other algorithms.
+On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
 Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.
@@
 	\subsection{Range Filtering}
-	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range filtering algorithms.
+
 	\subsubsection{Time and Space overhead of index construction.}
@@
 			\caption{Index size}
-			\label{fig:rangeFilter_ndex_size_mb}
+			\label{fig:rangeFilter_index_size_mb}
 		\end{subfigure}

### 2025-04-15 VLDB2026/main.tex
Update main.tex
add  peak memory DSG WIN UNIFY

--- 2025-04-15 VLDB2026/main.tex
@@
 
-	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute filtering ~\cite{NHQ,diskann} and range filtering algorithms \cite{serf,iRangeGraph}.
+	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute-filtering ~\cite{NHQ,diskann} and range-filtering algorithms \cite{serf,iRangeGraph}.
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
-As for range filtering algorithms, the size of the query range and the characteristics of different datasets also play an important role in determining algorithm performance.
+For attribute-filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
+As for range-filtering algorithms, the size of the query range and the characteristics of different datasets also play an important role in determining algorithm performance.
 
@@
 	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods.
-For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation.
+For instance, attribute-filtering algorithms such as NHQ and UNG are not included in the evaluation.
 2) It focuses only on single-attribute and dual-attribute query scenarios, neglecting the more complex demands of multi-attribute queries.
@@
 	(1)\textbf{ Systematic Classification and Overview.}
-	We systematically classify 10 representative attribute filtering algorithms from multiple dimensions, including index organization, filtering strategy, Boolean logic support, and index construction methods.
-Additionally, we survey range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
+	We systematically classify 10 representative attribute-filtering algorithms from multiple dimensions, including index organization, filtering strategy, Boolean logic support, and index construction methods.
+Additionally, we survey range-filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
 These efforts provide a unified reference framework for future study.
 
-	(2)\textbf{ Evaluation of Attribute Filtering Algorithms.}
+	(2)\textbf{ Evaluation of Attribute-Filtering Algorithms.}
 	We conduct a systematic evaluation of 13 attribute filtering algorithms on 6 real-world datasets.
@@
 
-	(3)\textbf{ Evaluation of Range Filtering Algorithms.}
-	We benchmark 5 mainstream range filtering algorithms on 3 large-scale datasets, using varying query range settings in the experiments.
+	(3)\textbf{ Evaluation of Range-Filtering Algorithms.}
+	We benchmark 5 mainstream range-filtering algorithms on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
@@
 	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
-These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution.
+These challenges include limited Boolean logic support, the lack of multi-attribute range-filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution.
 Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.
@@
 
-	\subsection{Attribute Filtering Algorithms}
-
-	We summarize 6 attribute filtering algorithms and provide an intuitive comparison in Table~\ref{tab:compair_1}.
+	\subsection{Attribute-Filtering Algorithms}
+
+	We summarize 6 attribute-filtering algorithms and provide an intuitive comparison in Table~\ref{tab:compair_1}.
 
 	\noindent\textbf{\underline{NHQ \cite{NHQ}.}}  
-	Traditional attribute filtering algorithms usually perform attribute constraints and ANN search separately.
+	Traditional attribute-filtering algorithms usually perform attribute constraints and ANN search separately.
 In contrast, NHQ is the first to implement simultaneous filtering, integrating both aspects into a unified framework.
@@
 
-	\subsection{Range Filtering Algorithms}
-
-	We introduce 5 representative range filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.
+	\subsection{Range-Filtering Algorithms}
+
+	We introduce 5 representative range-filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.
 
@@
 Each node in the tree corresponds to an attribute range and maintains a local ANN index (e.g., Vamana).
-For a range filtering query, WinFilter only searches within nodes overlapping the query range and merges partial results.
+For a range-filtering query, WinFilter only searches within nodes overlapping the query range and merges partial results.
 With a tree height of $O(\log n)$, each query accesses at most $O(\log n)$ sub-indexes, resulting in significant speedups.
@@
 
-	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, and Enron~\cite{enron2015}, covering a diverse range of domains.
+	For attribute-filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, and Enron~\cite{enron2015}, covering a diverse range of domains.
 We independently generate attribute for each dataset.
 
-	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
+	For range-filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
 Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
@@
 	\subsection{Range Filtering}
-	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range filtering algorithms.
+
 	\subsubsection{Time and Space overhead of index construction.}
+	%4.2.1
+
 	\begin{figure}[t]
@@
 
-	Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
+	Similar to the evaluation of \textit{Attribute-Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range-Filtering} algorithms.
+	%serf: It incrementally builds the index in attribute order. It requires only a single pass and adds edges within local graphs. The structure is simple, with no redundant operations.
 
 	\textit{\textbf{Index construction time.}}
-	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time.
-Faiss builds the index fastest.
-Because Faiss obtains subsamples through sampling and then calculates the cluster centroid, the computational complexity is significantly reduced.
+	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. Faiss builds the index fastest.
 
@@
 	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
-	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
-It also prunes distant neighbors to save storage space; however, this introduces additional overhead and slows down the construction process.
+
+	ACORN-\(\gamma\) expands each node’s neighbor list to offer more candidate paths, increasing computation and storage.
+It also prunes distant neighbors to reduce storage, but this adds extra overhead, slowing construction.
 
 	\textit{\textbf{Index size.}} 
-	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index structure.
-Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
-	On low-dimensional datasets (Deep, YT-Audio), PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding (e.g., Base64).
-
-	SeRF maintains a compact index for low-dimensional data. However, for high-dimensional datasets (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
+	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index structure because.
+On low-dimensional datasets (deep, yt-audio), PASE has the largest index size because its implementation may have wasteful alignment and padding of data structures, as well as the use of storage methods such as Base64 encoding, which significantly increase storage overhead.
+	The index size of SeRF on low-dimensional datasets is not large, but on high-dimensional datasets (wit), SeRF is forced to store more edges and dynamic range information, so the index increases significantly
 
 	\textit{\textbf{Peak memory usage.}}
-	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
-It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.
-
-	DSG and WinFilter require significantly more memory than other methods.Because……
-
-	For the high-dimensional dataset WIT, iRange achieves the lowest peak memory.
-It pre-builds graphs only for select intervals, skipping full-range index construction.
-This design keeps the index compact even in high dimensions.
-
-	In contrast, Unify consumes the most memory because...
+	As shown in Figure~\ref{fig:rangeFilter_memory_mb}, For low-dimensional datasets (deep, yt-audio), Faiss takes up the lowest memory due to: .
+
+	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
+This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
+	%因为低维空间中数据点之间的欧氏距离普遍较小，点与点之间更易互为近邻，从而导致图索引中产生大量冗余的边连接。
+
+	For high-dimensional datasets WIT, iRange achieves the lowest peak memory usage.
+It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
+Its index structure remains stable in high dimensions without significant graph growth.
+This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
+	In contrast, Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.
+
 	\begin{figure*}[htbp]
@@
 	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
-Unlike other range filtering algorithms, ACORN is not designed with specialized data structures (such as the $\beta$-WST in WinFilter, the rectangle tree and dynamic segment graph in SeRF, or the HSIG in UNIFY) to achieve efficient range filtering.
+Unlike other range-filtering algorithms, ACORN is not designed with specialized data structures  to achieve efficient range filtering.
 In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
@@
 \subsubsection{\textbf{Attribute Filtering}}
-Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
+Most existing attribute-filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
 Filtered-DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
@@
 
-Except for DSG, most range filtering algorithms require the dataset to be pre-sorted before building the index.
+Except for DSG, most range-filtering algorithms require the dataset to be pre-sorted before building the index.
 Moreover, these methods do not support multi-attribute range queries.
-Enhancing these methods to support an arbitrary number of range filterable attributes remains an open research challenge.
+Enhancing these methods to support an arbitrary number of range-filterable attributes remains an open research challenge.
 
@@
 
-Lastly, our findings show that the distribution and cardinality of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
+Lastly, our findings show that the distribution and cardinality of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute-filtering methods.
 Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.
@@
 In this paper, we evaluate various hybrid query methods, including different algorithms, vector databases, and vector libraries.
-For attribute filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance.
-We then perform experiments on 6 real-world datasets to analyze the effectiveness of attribute filtering algorithms in depth.
-Additionally, we compare existing range filtering algorithms using 3 range query datasets.
+For attribute-filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance.
+We then perform experiments on 6 real-world datasets to analyze the effectiveness of attribute-filtering algorithms in depth.
+Additionally, we compare existing range-filtering algorithms using 3 range query datasets.
 Finally, we provide a detailed analysis of the experimental results, summarize key findings, and highlight areas for improvement.

### 2025-04-15 VLDB2026/main.tex

--- 2025-04-15 VLDB2026/main.tex
@@
 
-	DSG and WinFilter require significantly more memory than other methods.Because……
-
-	For the high-dimensional dataset WIT, iRange achieves the lowest peak memory.
-It pre-builds graphs only for select intervals, skipping full-range index construction.
-This design keeps the index compact even in high dimensions.
-
-	In contrast, Unify consumes the most memory because...
+	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
+This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
+	%因为低维空间中数据点之间的欧氏距离普遍较小，点与点之间更易互为近邻，从而导致图索引中产生大量冗余的边连接。
+
+	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
+It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.
+
+	For high-dimensional datasets WIT, iRange achieves the lowest peak memory usage.
+It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
+Its index structure remains stable in high dimensions without significant graph growth.
+This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
+	In contrast, Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.
+
 	\begin{figure*}[htbp]

### 2025-04-15 VLDB2026/main.tex
change main and rangefilter_legend

--- 2025-04-15 VLDB2026/main.tex
@@
 	\noindent\textbf{\underline{Puck \cite{puck}.}}  
-	While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
+	While simultaneous filtering performs well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
 In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
@@
 		% 上面的图例，居中并可通过 hspace 调整左右位置
-		\hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-		\includegraphics[width=0.94\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径
+		\hspace*{16pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
+		\includegraphics[width=0.92\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径
 
@@
 This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
-On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
+On large-scale datasets, CPAS exhibits slightly lower memory usage compared to other algorithms.
 Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.
@@
 	\subsection{Range Filtering}
-
+	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range filtering algorithms.
 	\subsubsection{Time and Space overhead of index construction.}
+
 	\begin{figure}[t]
@@
 		\setlength{\belowcaptionskip}{0cm}
-
+		\hspace*{11pt}
 		% 放大的图例（占满单栏）
-		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
-
-		\vspace{0.3cm}
+		\includegraphics[width=0.93\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
+
+		%\vspace{0.1cm}
 
 		% 三图横排
-		\begin{subfigure}[t]{0.31\columnwidth}
+		\begin{subfigure}[t]{0.32\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}[t]{0.31\columnwidth}
+		\begin{subfigure}[t]{0.32\columnwidth}
 			\centering
@@
 			\caption{Index size}
-			\label{fig:rangeFilter_index_size_mb}
+			\label{fig:rangeFilter_ndex_size_mb}
 		\end{subfigure}
 		\hfill
-		\begin{subfigure}[t]{0.31\columnwidth}
+		\begin{subfigure}[t]{0.32\columnwidth}
 			\centering
@@
 	For third-party libraries and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
-Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
+Faiss does not include optimizations specifically tailored for range filtering scenarios; its query mechanism is identical to that used in tag filtering scenarios.
+However, since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
+Similar to the selectivity observed in attribute filtering, Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
 With a smaller range, fewer points remain after filtering, resulting in lower computational cost.

### 2025-04-15 VLDB2026/main.tex

--- 2025-04-15 VLDB2026/main.tex
@@
 	\subsubsection{Time and Space overhead of index construction.}
+
 	\begin{figure}[t]

### 2025-04-15 VLDB2026/main.tex
modify discussion
modify recommmendations

@@
 	\subsection{Recommendations.}
-	\subsubsection{\textbf{Attribute Filtering}}
+	Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
 
@@
 				\hline
-				S2: Fast Index Construction & ACORN-1, UNG  &SeRF, iRange\\
-				\hline
-				S3: Query on Hard Datasets & CAPS, UNG &iRange, DSG\\
-				\hline
-				S4: Query on Easy Datasets & StitchedVamana, NHQ & iRange\\
+				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\
+				\hline
+				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\
+				\hline
+				S4: Query on Easy Datasets & StitchedVamana, NHQ & WinFilter, iRange\\
 
@@
 				\hline
-				S6: Resource-constrained Environments & CAPS, Faiss&SeRF, iRange \\
+				S6: Resource-constrained Environments & CAPS, Faiss&Faiss, SeRF \\
 				\hline
 				S7: High-Recall Querying & UNG & WinFilter \\
+				\hline
+				S8: OOD scenarios & CAPS &WinFilter  \\
 				\hline
@@
 
-	We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.
-	Puck and UNG excel on large-scale datasets (S1).
+	%\subsubsection{\textbf{Attribute Filtering}}
+	%We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.Puck and UNG excel on large-scale datasets (S1).
 ACORN-1 and UNG achieve fast index construction (S2).
@@
 
-	\subsubsection{\textbf{Range Filtering}}
-
-	% \end{tabular}
-% \label{tab:range_algo_scenarios}
-% \end{table}
-Table~\ref{tab:algo_scenarios} also presents the application scenarios for range filtering.
+	%\subsubsection{\textbf{Range Filtering}}
+
+	%Table~\ref{tab:algo_scenarios} also presents the application scenarios for range filtering.
 iRange demonstrates strong performance on large-scale datasets, combining efficient construction with excellent query capabilities (S1).

### 2025-04-15 VLDB2026/main.tex
change vector db range filter

@@
 	Vector databases also show relatively poor performance on range queries.
-Among them, Milvus performs better than the others, even surpassing ACORN under high recall settings.
-PASE performs poorly on small-range queries, with recall lower than 0.1, so it does not appear in Figure~\ref{fig:exp_8_2}.
-VPASE also performs better on large-range queries, but compared to PASE, its performance on small ranges is significantly better, achieving higher recall despite very low QPS.
+Among them, Milvus performs more balanced across both small-range and large-range queries, even surpassing ACORN under high recall settings.
+PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
+VBASE performs better on large-range queries.
+Compared to PASE, its performance on small ranges is significantly improved, achieving higher recall despite very low QPS.
 

### 2025-04-15 VLDB2026/main.tex
change vectordb range filter robustness

@@
 
-Among vector databases, Milvus performed well. PASE was not included in this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
+Among vector databases, Milvus performed well.
+VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image.
+PASE was excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
 

### 2025-04-15 VLDB2026/main.tex
modify recommmendations

@@
 	\subsection{Recommendations.}
-	Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
+	%Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
 
@@
 				\hline
-				S4: Query on Easy Datasets & StitchedVamana, NHQ & WinFilter, iRange\\
+				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\
 
@@
 
-	%\subsubsection{\textbf{Attribute Filtering}}
-	%We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.Puck and UNG excel on large-scale datasets (S1).
+	\subsubsection{\textbf{Attribute Filtering}}
+	We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.
+Puck and UNG excel on large-scale datasets (S1).
 ACORN-1 and UNG achieve fast index construction (S2).
-CAPS performs best on hard datasets with high LID (S3), while NHQ, StitchedVamana, and UNG are superior for easy datasets with low LID (S4).
+UNG performs well on different datasets (S3, S4).
+In addition, CAPS performs well on hard datasets with high LID (S3), while NHQ and StitchedVamana perform better on easy datasets with low LID (S4).
 	Faiss and CAPS can generate relatively compact indexes with low memory usage, which is suitable for resource-constrained situations (S6).
@@
 UNG stands out for its high recall, precision, and QPS (S7).
-
-	%\subsubsection{\textbf{Range Filtering}}
-
-	%Table~\ref{tab:algo_scenarios} also presents the application scenarios for range filtering.
-iRange demonstrates strong performance on large-scale datasets, combining efficient construction with excellent query capabilities (S1).
-For fast index construction, SeRF leads with iRange as a close second (S2).
-When handling hard datasets, iRange and DSG are recommended (S3), while iRange also performs well on easy datasets (S4).
-For general-purpose applications, DSG supports dynamic updates while UNIFY provides flexible filtering strategies (S5).
-Both SeRF and iRange show superior memory efficiency (S6).
-WinFilter emerges as the optimal choice for high-recall static queries (S7).
-
+CAPS performs well in OOD scenarios (S8).
+
+	\subsubsection{\textbf{Range Filtering}}
+
+	Table~\ref{tab:algo_scenarios} also shows the application scenarios of range filtering.
+iRange performs well on large-scale datasets, combining efficient construction and excellent query capabilities (S1).
+Faiss performs well in fast index construction (S2).
+When processing hard datasets, WinFilter, iRange, and DSG are recommended (S3), while WinFilter and iRange also perform well on easy datasets (S4).
+For general applications, DSG supports dynamic updates, while UNIFY provides flexible filtering strategies (S5).
+Faiss and SeRF show superior memory efficiency (S6).
+For static queries with high recall, WinFilter is the best choice (S7).
+In addition, WinFilter also performs well in OOD scenarios (S8).
 \subsection{Challenges}

### 2025-04-16 VLDB2026/main.tex
Update main.tex

@@
 	(2)\textbf{ Evaluation of Attribute Filtering Algorithms.}
-	We conduct a systematic evaluation of 13 attribute filtering algorithms on 6 real-world datasets.
+	We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets.
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.

### 2025-04-16 VLDB2026/main.tex
添加t2i的引用

@@
 
-	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, and Enron~\cite{enron2015}, covering a diverse range of domains.
+	For attribute filtering tasks, we employ 7 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015} and Text2Image~\cite{texttoimage}, covering a diverse range of domains.
 We independently generate attribute for each dataset.

### 2025-04-16 VLDB2026/main.tex
modify recommmendations
Update main.tex

@@
 
-	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
+	For range filtering queries, we evaluate 4 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, WIT~\cite{wit_dataset}, and Text2Image.
 Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
@@
 				\hline
-				S8: OOD scenarios & CAPS &WinFilter  \\
+				S8: OOD scenarios & UNG &WinFilter  \\
 				\hline
@@
 Milvus and Faiss serve as general-purpose solutions (S5).
-UNG stands out for its high recall, precision, and QPS (S7).
-CAPS performs well in OOD scenarios (S8).
-
+UNG stands out for its higher recall, precision, and QPS, and performs well in the OOD scenario (S7, S8).
 	\subsubsection{\textbf{Range Filtering}}

### 2025-04-16 VLDB2026/main.tex
Update main.tex

--- 2025-04-16 VLDB2026/main.tex
@@
 
-To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we added an Out-of-Distribution (OOD) dataset to the three standard datasets and tested performance under large-range queries.
+To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we added an OOD dataset to the three standard datasets and tested performance under large-range queries.
 As shown in Figure~\ref{fig:exp_8_3}, most methods performed worst on the Text2Image dataset.

### 2025-04-16 VLDB2026/main.tex
Update main.tex

@@
 
-	Most algorithms exhibit the worst performance on the OOD dataset text2image.
-However, ACORN, UNG, and FilteredVamana show relatively stable performance on text2image.
-Their performance drops less compared to in-distribution (ID) datasets such as GIST and GLOVE, indicating better adaptability to OOD queries.
+	Most algorithms exhibit the worst performance on the OOD dataset Text2Image.
+However, ACORN, UNG, and FilteredVamana show relatively stable performance on Text2Image.
+Their performance drops less compared to in-distribution (ID) datasets such as GIST1M and GloVe, indicating better adaptability to OOD queries.
 

### 2025-04-16 VLDB2026/main.tex
Update main.tex
delete SAF MAF
modify details

@@
 
-	We further classify AF-NN search according to the number of the attribute set \( s_i \): 1) Single-Attribute Filtering Nearest Neighbor (\textit{SAF-NN}) search, where $\forall i,\, |s_i| = 1$.
+%	We further classify AF-NN search according to the number of the attribute set \( s_i \): 1) Single-Attribute Filtering Nearest Neighbor (\textit{SAF-NN}) search, where $\forall i,\, |s_i| = 1$.
 2) Multi-Attribute Filtering Nearest Neighbor (\textit{MAF-NN}) search, where $\exists i,\, |s_i| > 1$.
@@
 	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
-It also prunes distant neighbors to save storage space; however, this introduces additional overhead and slows down the construction process.
+It also prunes distant neighbors to save storage space.
+However, this introduces additional overhead and slows down the construction process.
 
 	\textit{\textbf{Index size.}} 
-	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index structure.
+	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size.
 Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
@@
 
-	SeRF maintains a compact index for low-dimensional data. However, for high-dimensional datasets (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
+	SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
 
 	\textit{\textbf{Peak memory usage.}}
-	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
+	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets.
 It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.
@@
 
-	For high-dimensional datasets WIT, iRange achieves the lowest peak memory usage.
+	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage.
 It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.

### 2025-04-16 VLDB2026/main.tex
Update main.tex
change conclusion and challenges

--- 2025-04-16 VLDB2026/main.tex
@@
 
+\textcolor{blue}{
+In our experiments, we found that many range filtering algorithms perform worse than Faiss at high recall (0.95).
+This shows that the design of current algorithms still needs improvement.
+We suggest that future range filtering algorithms should include Faiss as a baseline.
+}
+
 It is also worth noting that range filtering and attribute filtering are both forms of hybrid query.
@@
 \section{CONCLUSION}
-
+\textcolor{blue}{
 	In this paper, we evaluate various hybrid query methods, including different algorithms, vector databases, and vector libraries.
 For attribute filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance.
-We then perform experiments on 6 real-world datasets to analyze the effectiveness of attribute filtering algorithms in depth.
-Additionally, we compare existing range filtering algorithms using 3 range query datasets.
+To facilitate fair and reproducible comparisons in future research, we enrich existing datasets with attribute values and design a variety of experimental scenarios based on practical needs.
+We then perform experiments on 7 real-world datasets to analyze the effectiveness of attribute filtering algorithms in depth.
+Additionally, we compare existing range filtering algorithms using 4 range query datasets.
 Finally, we provide a detailed analysis of the experimental results, summarize key findings, and highlight areas for improvement.
 Our study not only validates previous research but also offers insights for future work.
+}
 

### 2025-04-17 VLDB2026/main.tex
Update main.tex
add note
Update main.tex
add contribution

@@
 \usepackage{graphicx}
+
 \usepackage{microtype}  %处理换行
@@
 
-	(2)\textbf{ Evaluation of Attribute Filtering Algorithms.}
+	\textcolor{blue}{
+	(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
+	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
+Furthermore, we design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity levels, and query conditions.
+These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query processing.
+	}
+
+	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
 	We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets.
@@
 
-	(3)\textbf{ Evaluation of Range Filtering Algorithms.}
+	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
 	We benchmark 5 mainstream range filtering algorithms on 3 large-scale datasets, using varying query range settings in the experiments.
@@
 
-	(4)\textbf{ Recommendations and Challenges.}
+	(5)\textbf{ Recommendations and Challenges.}
 	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
@@
 	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query process.
+	\textcolor{blue}{The original NHQ implementation does not support this scenario. We modified the code to enable this experiment.}
 
@@
 \textcolor{blue}{
-In our experiments, we found that many range filtering algorithms perform worse than Faiss at high recall (0.95).
+In our experiments, we find that many range filtering algorithms perform worse than Faiss at high recall (0.95).
 This shows that the design of current algorithms still needs improvement.

### 2025-04-17 VLDB2026/main.tex
Modify the tense

@@
 
-To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we added an OOD dataset to the three standard datasets and tested performance under large-range queries.
-As shown in Figure~\ref{fig:exp_8_3}, most methods performed worst on the Text2Image dataset.
+To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we \textcolor{red}{add} an OOD dataset to the three standard datasets and \textcolor{red}{test} performance under large-range queries.
+As shown in Figure~\ref{fig:exp_8_3}, most methods \textcolor{red}{perform} worst on the Text2Image dataset.
 This is because OOD queries make the $k$-nearest neighbor distribution more sparse.
@@
 
-WinFilter showed the worst performance on the WIT dataset.
+WinFilter \textcolor{red}{shows} the worst performance on the WIT dataset.
 This suggests that its performance is sensitive to the data dimensionality.
-ACORN had large performance differences across datasets, indicating weak robustness.
-
-Among vector databases, Milvus performed well.
+ACORN \textcolor{red}{has} large performance differences across datasets, indicating weak robustness.
+
+Among vector databases, Milvus \textcolor{red}{performs} well.
 VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image.
-PASE was excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
-
-It is worth noting that most methods achieved similar performance on the Deep and YT-Audio datasets, which have similar LID values.
+PASE \textcolor{red}{is} excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
+
+It is worth noting that most methods \textcolor{red}{achieve} similar performance on the Deep and YT-Audio datasets, which have similar LID values.
 This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
@@
 
-However, even though Deep and YT-Audio have similar LID values, the DSG algorithm showed large performance differences between them.
+However, even though Deep and YT-Audio have similar LID values, the DSG algorithm \textcolor{red}{shows} large performance differences between them.
 This means that DSG is more sensitive to changes in data distribution.

### 2025-04-27 VLDB2026/main.tex
Update main.tex

@@
 		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.2cm}
+		\setlength{\belowcaptionskip}{-0.5cm}
 		\includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
@@
 For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation.
-2) It focuses only on single-attribute and dual-attribute query scenarios, neglecting the more complex demands of multi-attribute queries.
-In real-world applications, an object typically involves multiple attributes.
-For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.
+2) It \textcolor{yellow}{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries.
+In real-world applications, an object typically involves multiple attributes.\textcolor{yellow}{ For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}
 	3) It does not evaluate algorithm performance under different attribute distributions.
@@
 		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{0.2cm}
+		\setlength{\belowcaptionskip}{-0.02cm}
 		\caption{Graph index and IVF index}
@@
 			\setlength{\abovecaptionskip}{0cm}
-			\setlength{\belowcaptionskip}{-0.1cm}
+			\setlength{\belowcaptionskip}{-0.3cm}
 			\includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
@@
 		\centering
-		%        \setlength{\abovecaptionskip}{0cm}
-		%    \setlength{\belowcaptionskip}{-0.4cm}
+		        \setlength{\abovecaptionskip}{0cm}
+		    \setlength{\belowcaptionskip}{-0.5cm}
 		\includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
@@
 		\centering
-		%    \setlength{\abovecaptionskip}{0cm}
-		%    \setlength{\belowcaptionskip}{-0.4cm}
+		    \setlength{\abovecaptionskip}{0cm}
+		    \setlength{\belowcaptionskip}{-0.5cm}
 		\includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
@@
 			\centering
-			%        \setlength{\abovecaptionskip}{0cm}
-			%        \setlength{\belowcaptionskip}{0cm}
+			\setlength{\abovecaptionskip}{0.05cm}
+			\setlength{\belowcaptionskip}{0.05cm}
 			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_1.pdf}
@@
 			\centering
-			%        \setlength{\abovecaptionskip}{0cm}
-			%        \setlength{\belowcaptionskip}{0cm}
+			\setlength{\abovecaptionskip}{0.05cm}
+			\setlength{\belowcaptionskip}{0.05cm}
 			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_2.pdf}
@@
 			\centering
-			%        \setlength{\abovecaptionskip}{0cm}
-			%        \setlength{\belowcaptionskip}{0cm}
+			\setlength{\abovecaptionskip}{0.05cm}
+			\setlength{\belowcaptionskip}{0.05cm}
 			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_3.pdf}
@@
 
-		%    \setlength{\abovecaptionskip}{0cm}
-		%    \setlength{\belowcaptionskip}{-0.4cm}
+		   \setlength{\abovecaptionskip}{0cm}
+		    \setlength{\belowcaptionskip}{-0.5cm}
 		\caption{Different AS under the same algorithm}
@@
 		\centering
-		%    \setlength{\abovecaptionskip}{0cm}
-		%    \setlength{\belowcaptionskip}{-0.4cm}
+		    \setlength{\abovecaptionskip}{0cm}
+		    \setlength{\belowcaptionskip}{-0.4cm}
 		\includegraphics[width=\textwidth]{figures/exp/exp_6_1.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.3cm}
-		\setlength{\belowcaptionskip}{0cm}
+		\setlength{\abovecaptionskip}{0.02cm}
+		\setlength{\belowcaptionskip}{0.02cm}
 		\hspace*{11pt}
@@
 			\centering
+			\setlength{\abovecaptionskip}{0.02cm}
+			\setlength{\belowcaptionskip}{0.02cm}
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
@@
 			\centering
+			\setlength{\abovecaptionskip}{0.02cm}
+			\setlength{\belowcaptionskip}{0.02cm}
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
@@
 			\centering
+			\setlength{\abovecaptionskip}{0.02cm}
+			\setlength{\belowcaptionskip}{0.02cm}
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
@@
 		\centering
-		%  \setlength{\abovecaptionskip}{0cm}
-		%    \setlength{\belowcaptionskip}{-0.4cm}
+		  \setlength{\abovecaptionskip}{0cm}
+		    \setlength{\belowcaptionskip}{-0.5cm}
 		\includegraphics[width=\textwidth]{figures/exp/exp_8_2.pdf}
@@
 		\centering
-		%    \setlength{\abovecaptionskip}{0cm}
-		%    \setlength{\belowcaptionskip}{-0.5cm}
+		    \setlength{\abovecaptionskip}{0cm}
+		    \setlength{\belowcaptionskip}{-0.5cm}
 		\includegraphics[width=\textwidth]{figures/exp/exp_8_3.pdf}

### 2025-04-27 VLDB2026/main.tex
Update main.tex

@@
 		\setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
+		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
 		\caption{Hybrid query example}
@@
 	\setlength{\floatsep}{0cm}
+	\renewcommand{\arraystretch}{0.9}
 	\begin{table*}[t]
@@
 		%\setlength{\belowcaptionskip}{-0.3cm}
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.2cm}
+		\setlength{\abovecaptionskip}{0cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{Comparison of AF-ANN search algorithms}
@@
 		\end{minipage}}
-		\vspace{-0.3cm}
+		\vspace{-0.5cm}
 	\end{table*}
@@
 	\setlength{\floatsep}{0cm}
+		\renewcommand{\arraystretch}{0.9}
 	\begin{table}[t]
@@
 			\end{minipage} 
+			\vspace{-0.1cm}
 		}
@@
 	\setlength{\floatsep}{0cm}
+	\renewcommand{\arraystretch}{0.9}
 	\begin{table}[t]
@@
 
-		\setlength{\abovecaptionskip}{0.05cm}
-		\setlength{\textfloatsep}{0.cm}
+		\setlength{\abovecaptionskip}{0cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{Datasets}
@@
 				\midrule
-				Msong & 420 & 992,272 & 200 & 23& Audio \\[2pt]
-				Audio & 192 & 53,387 & 200 & 14& Audio \\[2pt]
-				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\[2pt]
-				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\[2pt]
-				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\[2pt]
-				Enron & 1369 & 94,987 & 200 & 23& Text \\[2pt]
-				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\[2pt]
-				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\[2pt] 
-				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\[2pt]
-				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\[2pt]
+				Msong & 420 & 992,272 & 200 & 23& Audio \\
+				Audio & 192 & 53,387 & 200 & 14& Audio \\
+				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\
+				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\
+				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\
+				Enron & 1369 & 94,987 & 200 & 23& Text \\
+				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
+				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
+				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
+				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\
 
@@
 			\setlength{\belowcaptionskip}{-0.1cm}
-			\includegraphics[width=\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
+			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
 			\caption{Index construction time}
@@
 			\setlength{\belowcaptionskip}{-0.1cm}
-			\includegraphics[width=\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
+			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
 			\caption{Index size}
@@
 			\setlength{\belowcaptionskip}{-0.3cm}
-			\includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
+			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
 			\caption{Peak memory usage}
@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
+		\includegraphics[width=0.98\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
 		\caption{Single-Attribute Building and Query (single thread) }
@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
+		\includegraphics[width=0.98\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
 		\caption{Single-Attribute Building and Query (16 threads)}
@@
 
-	\begin{figure}[th]
+	\begin{figure}[t]
 		\centering
@@
 		\hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-		\includegraphics[width=0.98\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
+		\includegraphics[width=0.95\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
 
 		% 下面的子图，居中显示
-		\includegraphics[width=0.8\columnwidth]{figures/exp/exp_2_1.pdf}
+		\includegraphics[width=0.7\columnwidth]{figures/exp/exp_2_1.pdf}
 		\caption{Effect of Multi-Attribute Index Construction on Single Query Performance.

### 2025-04-27 VLDB2026/main.tex
change 3.3

@@
 
-	\noindent\textbf{\underline{Faiss \cite{Faiss}.}} Faiss is a library designed for efficient similarity search and clustering of dense vectors.
+	\noindent\textbf{\underline{Faiss \cite{Faiss}.}} \textcolor{red}{Faiss is a library designed for efficient similarity search}.
 It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.
-
 In hybrid query scenarios, Faiss supports vector search with an ID selector, which is a bitmap aligned with the dataset size.
@@
 During the query process, Faiss excludes vectors based on the selector, enabling efficient integration of attribute filtering with ANN search.
-
-	% HQI~\cite{HQI} further proposes an optimization scheme for the IVF index in Faiss, improving efficiency in two aspects:  
-	% 1) Workload-Aware Vector Index: Constructs an attribute filtering tree using historical query workloads and vector cluster centroids to improve filtering efficiency.  
-	% 2) Batch Query Optimization: Groups queries sharing the same filter conditions, performs filtering once per group, and then conducts batch vector similarity computations using efficient matrix operations.
-	% Since this paper does not focus on query workload optimization, we adopt only the batch optimization strategy in our analysis.
 In addition, we adopt the batch optimization strategy of HQI~\cite{HQI} for the IVF index in Faiss.
@@
 We focus on the post-filtering strategy based on HNSW, which facilitate comparison with other methods.
-
 When a query request is received, PASE first obtains a candidate set using the HNSW index.
@@
 	\noindent\textbf{\underline{VBASE \cite{vbase}.}}  
-	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}. We focus on HNSW-based search.
-
+	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
+We focus on HNSW-based search.
 VBASE adopts a post-filtering strategy.
@@
 	\noindent\textbf{\underline{Milvus \cite{milvus}.}}  
-	Unlike PASE and VBASE, which are database extensions, Milvus is an open-source vector database purpose-built for large-scale similarity search.
+	Unlike PASE and VBASE, which are database extensions, Milvus is an vector database purpose-built for large-scale similarity search.
 It supports multiple index types, including HNSW, IVF\_Flat, and IVF\_PQ, and provides extensive optimization for real-world deployment.
-
 Among its indexes, IVF\_Flat is commonly used due to its balance between performance and simplicity.

### 2025-04-27 VLDB2026/main.tex
Merge branch 'main' of https://github.com/zhujx001/Hybrid-ANNS

@@
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution.
-Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.
+\textcolor{yellow} {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
 

### 2025-04-27 VLDB2026/main.tex
Update main.tex
table

--- 2025-04-27 VLDB2026/main.tex
@@
 		\setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
+		\includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
 		\caption{Hybrid query example}
@@
 For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation.
-2) It \textcolor{yellow}{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries.
-In real-world applications, an object typically involves multiple attributes.\textcolor{yellow}{ For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}
+2) It focuses only on single-attribute and dual-attribute query scenarios, neglecting the more complex demands of multi-attribute queries.
+In real-world applications, an object typically involves multiple attributes.
+For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.
 	3) It does not evaluate algorithm performance under different attribute distributions.
@@
 	\setlength{\floatsep}{0cm}
-	\renewcommand{\arraystretch}{0.9}
 	\begin{table*}[t]
@@
 		%\setlength{\belowcaptionskip}{-0.3cm}
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.3cm}
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.2cm}
 		\caption{Comparison of AF-ANN search algorithms}
@@
 		\label{tab:compair_1}
-		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
+%		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
+%			\hline
+%			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+%			\hline
+%			NHQ & Graph & C & Y & N& N& N & N & N \\
+%			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
+%			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
+%			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
+%			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
+%			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
+%			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
+%			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
+%			
+%			\hline
+%			
+%		\end{tabular}
+	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|l|}
 		\hline
-			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+		\textbf{Item} & \textbf{NHQ} & \textbf{FilteredVamana} & \textbf{StitchedVamana} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
 		\hline
-			NHQ & Graph & C & Y & N& N& N & N & N \\
-			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
-			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
-			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
-			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
-			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
-			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
-			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
+		Base & Graph & Graph & Graph & IVF & Graph & Graph & IVF & Graph & Graph & Graph & Graph & Graph \\
+		Dynamic Insert & N & Y & N & Y & Y & Y & Y & Y & N & Y & Y & N \\
+		Multi Thread & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\
+		Filter Type & C & C & C & C & B & B & B & - & - & - & - & - \\
+		AND & Y & N & N & Y & Y & Y & Y & - & - & - & - & - \\
+		OR & N & Y & Y & N & Y & Y & Y & - & - & - & - & - \\
+		Flexible Attributes & N & Y & Y & Y & Y & Y & Y & - & - & - & - & - \\
+		Complex Boolean & N & N & N & N & Y & N & N & - & - & - & - & - \\
 
 		\hline
-
 	\end{tabular}
@@
 		\end{minipage}}
-		\vspace{-0.5cm}
+		\vspace{-0.3cm}
 	\end{table*}
@@
 
-	\setlength{\textfloatsep}{0.1cm}
-	\setlength{\floatsep}{0cm}
-		\renewcommand{\arraystretch}{0.9}
-	\begin{table}[t]
-		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.1cm}
-		\setlength{\textfloatsep}{0.1cm}
-		\caption{Comparison of RF-ANN search algorithms}
-		\small	% 只会影响当前组的内容
-		\label{tab:range_algo}
-		\begin{tabular}{|c|c|c|c|}
-			\hline
-			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
-			\hline
-			DSG & Graph & Y & N \\
-			iRange & Graph & N & Y \\
-			SeRF & Graph & Y & Y \\
-			UNIFY & Graph & Y & Y \\
-			WinFilter & Graph & N & Y  \\
-			\hline
-		\end{tabular}
-
-		\footnotesize{
-			\begin{minipage}{\linewidth}
-				\textsuperscript{Y} Support, 
-				\textsuperscript{N} Unsupport.
-				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
-			\end{minipage} 
-			\vspace{-0.1cm}
-		}
-
-	\end{table}
+%	\setlength{\textfloatsep}{0.1cm}
+%	\setlength{\floatsep}{0cm}
+%	\begin{table}[t]
+%		\centering
+%		\setlength{\abovecaptionskip}{0.1cm}
+%		\setlength{\belowcaptionskip}{-0.1cm}
+%		\setlength{\textfloatsep}{0.1cm}
+%		\caption{Comparison of RF-ANN search algorithms}
+%		\small	% 只会影响当前组的内容
+%		\label{tab:range_algo}
+%		\begin{tabular}{|c|c|c|c|}
+%			\hline
+%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+%			\hline
+%			DSG & Graph & Y & N \\
+%			iRange & Graph & N & Y \\
+%			SeRF & Graph & Y & Y \\
+%			UNIFY & Graph & Y & Y \\
+%			WinFilter & Graph & N & Y  \\
+%			\hline
+%		\end{tabular}
+%		
+%		
+%		\footnotesize{
+%			\begin{minipage}{\linewidth}
+%				\textsuperscript{Y} Support, 
+%				\textsuperscript{N} Unsupport.
+%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
+%				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
+%			\end{minipage} 
+%		}
+%		
+%	\end{table}
 
@@
 
-	We introduce 5 representative range filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.
+	We introduce 5 representative range filtering algorithms and present a comparative overview in Table~\ref{tab:compair_1}.
 
@@
 	\setlength{\floatsep}{0cm}
-	\renewcommand{\arraystretch}{0.9}
 	\begin{table}[t]
@@
 
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.3cm}
+		\setlength{\abovecaptionskip}{0.05cm}
+		\setlength{\textfloatsep}{0.cm}
 		\caption{Datasets}
@@
 				\midrule
-				Msong & 420 & 992,272 & 200 & 23& Audio \\
-				Audio & 192 & 53,387 & 200 & 14& Audio \\
-				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\
-				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\
-				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\
-				Enron & 1369 & 94,987 & 200 & 23& Text \\
-				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
-				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
-				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\
+				Msong & 420 & 992,272 & 200 & 23& Audio \\[2pt]
+				Audio & 192 & 53,387 & 200 & 14& Audio \\[2pt]
+				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\[2pt]
+				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\[2pt]
+				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\[2pt]
+				Enron & 1369 & 94,987 & 200 & 23& Text \\[2pt]
+				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\[2pt]
+				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\[2pt] 
+				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\[2pt]
+				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\[2pt]
 
@@
 			\setlength{\belowcaptionskip}{-0.1cm}
-			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
+			\includegraphics[width=\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
 			\caption{Index construction time}
@@
 			\setlength{\belowcaptionskip}{-0.1cm}
-			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
+			\includegraphics[width=\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
 			\caption{Index size}
@@
 			\setlength{\belowcaptionskip}{-0.3cm}
-			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
+			\includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
 			\caption{Peak memory usage}
@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.98\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
+		\includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
 		\caption{Single-Attribute Building and Query (single thread) }
@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.98\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
+		\includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
 		\caption{Single-Attribute Building and Query (16 threads)}
@@
 
-	\begin{figure}[t]
+	\begin{figure}[th]
 		\centering
@@
 		\hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-		\includegraphics[width=0.95\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
+		\includegraphics[width=0.98\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
 
 		% 下面的子图，居中显示
-		\includegraphics[width=0.7\columnwidth]{figures/exp/exp_2_1.pdf}
+		\includegraphics[width=0.8\columnwidth]{figures/exp/exp_2_1.pdf}
 		\caption{Effect of Multi-Attribute Index Construction on Single Query Performance.
@@
 				\hline
-				S6: Resource-constrained Environments & CAPS, Faiss&Faiss, SeRF \\
+				S6: Resource constraint & CAPS, Faiss&Faiss, SeRF \\
 				\hline

### 2025-04-27 VLDB2026/main.tex

--- 2025-04-27 VLDB2026/main.tex
@@
 		\setlength{\abovecaptionskip}{0.3cm}
-		\setlength{\belowcaptionskip}{0cm}
+		\setlength{\belowcaptionskip}{-0.15cm}
 
@@
 			\centering
-			\setlength{\abovecaptionskip}{0cm}
+			\setlength{\abovecaptionskip}{-0.02cm}
 			\setlength{\belowcaptionskip}{-0.1cm}
@@
 			\centering
-			\setlength{\abovecaptionskip}{0cm}
+			\setlength{\abovecaptionskip}{-0.02cm}
 			\setlength{\belowcaptionskip}{-0.3cm}
@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.98\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
+		\includegraphics[width=0.96\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
 		\caption{Single-Attribute Building and Query (16 threads)}

### 2025-04-27 VLDB2026/main.tex
Update main.tex

--- 2025-04-27 VLDB2026/main.tex
@@
 
-		\caption{Time and space overhead of attribute filtering index construction}
+%		\caption{Time and space overhead of attribute filtering index construction}
+		\caption{\textcolor{red}{Time and space overhead of index construction}}
 		\label{fig:build_index_comparison}
@@
 		    \setlength{\belowcaptionskip}{-0.4cm}
-		\includegraphics[width=\textwidth]{figures/exp/exp_6_1.pdf}
+		\includegraphics[width=0.97\textwidth]{figures/exp/exp_6_1.pdf}
 		\caption{Effect of dataset on Query}
@@
 		\centering
+
 		\setlength{\abovecaptionskip}{0.02cm}
-		\setlength{\belowcaptionskip}{0.02cm}
+		\setlength{\belowcaptionskip}{-0.1cm}
 		\hspace*{11pt}
@@
 			\centering
+			\captionsetup{font=small}
 			\setlength{\abovecaptionskip}{0.02cm}
@@
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
-			\caption{Index construction time}
+			\caption{\footnotesize Construction time}
 			\label{fig:rangeFilter_build_time}
@@
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
-			\caption{Index size}
+			\caption{\footnotesize Index size}
 			\label{fig:rangeFilter_index_size_mb}
@@
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
-			\caption{Peak memory usage}
+			\caption{\footnotesize Peak memory usage}
 			\label{fig:rangeFilter_memory_mb}
@@
 
-		\caption{Time and space overhead of range filtering index construction}
+%		\caption{Time and space overhead of range filtering index construction}
+		\caption{\textcolor{red}{Time and space overhead of index construction}}
 		\label{fig:rangeFilter_build_index_comparison}
@@
 	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time.
+Faiss builds the index fastest.
+As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.
+%	shows the single-threaded index construction time.
 Faiss builds the index fastest.
@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=\textwidth]{figures/exp/exp_8_2.pdf}
+		\includegraphics[width=0.95\textwidth]{figures/exp/exp_8_2.pdf}
 		\caption{RF-ANN search }
@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=\textwidth]{figures/exp/exp_8_3.pdf}
+		\includegraphics[width=0.8\textwidth]{figures/exp/exp_8_3.pdf}
 		\caption{Dataset Effect on RF-ANN Search}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.05cm}
+		\setlength{\abovecaptionskip}{0.0cm}
 		\caption{Algorithm Recommendation per Scenario}
@@
 		\label{tab:algo_scenarios}
-
+	\vspace{-0.1cm}
 	\end{table}
@@
 \textcolor{blue}{
-In our experiments, we find that many range filtering algorithms perform worse than Faiss at high recall (0.95).
+In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement.
+We suggest future future range filtering algorithms include Faiss as a baseline.
+%In our experiments, we find that many range filtering algorithms perform worse than Faiss at high recall (0.95).
 This shows that the design of current algorithms still needs improvement.

### 2025-04-27 VLDB2026/main.tex
Update main.tex

@@
 	The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.
-
 	Filtered-DiskANN also supports simultaneous filtering.
@@
 Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.
-
 	Filtered-DiskANN proposes 2 indexes:  
@@
 	2) \textbf{StitchedVamana}, which adopts a batch construction strategy—constructing separate Vamana subgraphs for each attribute, followed by merging and edge pruning.
-
 	A key limitation of Filtered-DiskANN is that while it supports both single-attribute and multi-attribute filtering, it only supports the Boolean OR logic for multi-attribute filtering, lacking support for Boolean AND logic.
@@
 CAPS addresses this issue by being the first simultaneous filtering algorithm based on spatial partitioning, significantly reducing index size.
-
 	CAPS introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
@@
 	\noindent\textbf{\underline{ACORN \cite{ACORN}.}}  
-	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
-	%The above simultaneous filtering methods are less effective in scenarios involving large-scale, unbounded, or unknown predicate sets, where a predicate refers to a condition or rule used for filtering.
-	ACORN addresses this issue by introducing a predicate-agnostic indexing framework.
-
-	ACORN is built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}.
+%	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
+%	%The above simultaneous filtering methods are less effective in scenarios involving large-scale, unbounded, or unknown predicate sets, where a predicate refers to a condition or rule used for filtering.
+%	ACORN addresses this issue by introducing a predicate-agnostic indexing framework.
+%	ACORN is built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}.
 It supports high-cardinality and unrestricted predicate sets, overcoming the limitations of methods restricted to small-scale equality filters.
@@
 This effectively maintains a nearest neighbor graph over valid nodes only.
-	%During the query process, ACORN avoids unnecessary distance computations by filtering out nodes that do not meet attribute constraints, effectively simulating a nearest neighbor graph over valid nodes only.
-
-	ACORN includes 2 indexes:  
-	1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
-	2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.
+%	%During the query process, ACORN avoids unnecessary distance computations by filtering out nodes that do not meet attribute constraints, effectively simulating a nearest neighbor graph over valid nodes only.
+%	ACORN includes 2 indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
+%	2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.
+	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. 
+	ACORN addresses this by introducing a predicate-agnostic indexing framework.
+	Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates, overcoming limitations of methods confined to small-scale equality filters.
+	It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
+	During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
+	ACORN includes two indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, trading memory for higher performance; 
+	2) \textbf{ACORN-1}, which extends neighbor lists via second-hop neighbors during search, reducing index size with minor performance loss.
 
@@
 UNG is proposed to overcome these limitations.
-
 	UNG is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.
@@
 Within each group, UNG builds graph-based ANN indexes (e.g., Vamana, HNSW) and connects them via cross-group edges to enable efficient cross-group search.
-
-	UNG supports Boolean filtering with 2 modes:  
-	1) The query attribute set is a subset of the data attribute set.  
-	2) The query attribute set exactly matches the data attribute set.
+	UNG supports Boolean filtering with 2 modes:  1) The query attribute set is a subset of the data attribute set.  2) The query attribute set exactly matches the data attribute set.
 
@@
 In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
-
 	Developed by Baidu, Puck utilizes two-level quantization for indexing.

### 2025-04-28 VLDB2026/main.tex
Update main.tex
modify

@@
 \usepackage{graphicx}
-
+\usepackage{ulem}  % 导言区加上这一行
 \usepackage{microtype}  %处理换行
@@
 	\noindent\textbf{\underline{Filtered-DiskANN \cite{Filtered-diskann}.}}  
-	The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.
+	\sout{The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.}
 	Filtered-DiskANN also supports simultaneous filtering.
@@
 
-	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} Different from the above graph-based simultaneous filtering algorithms, CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
+	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} 
+	\sout{Different from the above graph-based simultaneous filtering algorithms,}CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
 	%As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes.
@@
 
-	\noindent\textbf{\underline{UNG \cite{UNG}.}} The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
-UNG is proposed to overcome these limitations.
+	\noindent\textbf{\underline{UNG \cite{UNG}.}} 
+	The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low. UNG is proposed to overcome these limitations.
 	UNG is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.
@@
 				\hline
-				S6: Resource-constrained Environments & CAPS, Faiss&Faiss, SeRF \\
+				S6: Resource constraint& CAPS, Faiss&Faiss, SeRF \\
 				\hline
@@
 		\label{tab:algo_scenarios}
-	\vspace{-0.1cm}
+		\vspace{0cm}
 	\end{table}

### 2025-04-28 VLDB2026/main.tex
change 4.2.2 and 3.3

@@
 
-	\noindent\textbf{\underline{UNG \cite{UNG}.}} 
-	The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low. UNG is proposed to overcome these limitations.
+	\noindent\textbf{\underline{UNG \cite{UNG}.}} The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
+UNG is proposed to overcome these limitations.
 	UNG is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.
@@
 	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
-We focus on HNSW-based search.
+\textcolor{red}{We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality}.
 VBASE adopts a post-filtering strategy.
@@
 	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query process.
-	\textcolor{blue}{The original NHQ implementation does not support this scenario. We modified the code to enable this experiment.}
+	\textcolor{red}{We modified the NHQ source code to support this experiment.}
 

### 2025-04-28 VLDB2026/main.tex
Merge branch 'main' of https://github.com/zhujx001/Hybrid-ANNS

@@
 For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation.
-2) It \textcolor{yellow}{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries.
-In real-world applications, an object typically involves multiple attributes.\textcolor{yellow}{ For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}
+2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries.
+In real-world applications, an object typically involves multiple attributes.\textcolor{blue}{ For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}
 	3) It does not evaluate algorithm performance under different attribute distributions.
@@
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution.
-\textcolor{yellow} {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
+\textcolor{blue} {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
 

### 2025-04-28 VLDB2026/main.tex
modify

@@
 	Our study focuses on the problem of ANN search in hybrid query scenarios and provides a comprehensive review and evaluation of existing algorithms and systems.
-The main contributions are summarized in the following 4 aspects.
+The main contributions are summarized in the following 5 aspects.
 
 	(1)\textbf{ Systematic Classification and Overview.}
-	We systematically classify 10 representative attribute filtering algorithms from multiple dimensions, including index organization, filtering strategy, Boolean logic support, and index construction methods.
-Additionally, we survey range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
+	%We systematically classify 6 representative attribute filtering algorithms from multiple dimensions, including index organization, filtering strategy, Boolean logic support, and index construction methods.
+Additionally, we survey 5 range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
 These efforts provide a unified reference framework for future study.
+	\textcolor{red}{We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
+In addition, we survey 5 range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
+These efforts offer a unified reference framework for future research.}
 
@@
 	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
-	We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets.
-By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
+	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
+	\textcolor{red}{We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.}By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
 We further examine their behavior under different attribute distributions and selectivity conditions to assess robustness and adaptability in complex query scenarios.
@@
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-	We benchmark 5 mainstream range filtering algorithms on 3 large-scale datasets, using varying query range settings in the experiments.
+	We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.

### 2025-04-28 VLDB2026/main.tex
updata MM

--- 2025-04-28 VLDB2026/main.tex
@@
 
-	\section{Experiments}
-	\subsection{Experimental Setup}
-	\subsubsection{Datasets}
-
-	For attribute filtering tasks, we employ 7 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015} and Text2Image~\cite{texttoimage}, covering a diverse range of domains.
-We independently generate attribute for each dataset.
-
-	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
-Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
-This ensures that the data is initially sorted.
-
-	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets.
-In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness.
-Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.
-A higher LID indicates greater intrinsic complexity.
-
 	\setlength{\textfloatsep}{0.1cm}
@@
 
+	\section{Experiments}
+	\subsection{Experimental Setup}
+	\subsubsection{Datasets}
+
+	For attribute filtering tasks, we employ 7 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015} and Text2Image~\cite{texttoimage}, covering a diverse range of domains.
+We independently generate attribute for each dataset.
+
+	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
+Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
+This ensures that the data is initially sorted.
+
+	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets.
+In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness.
+Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.
+A higher LID indicates greater intrinsic complexity.
+
 	\subsubsection{Evaluation Metrics}
@@
 	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
+For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies.
+Milvus, \textcolor{red}{as a general-purpose system}, exhibits comparatively poor performance.
+In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance.
+Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes.
+In fact, filtering can reduce the effective candidate set, improving efficiency.
+%	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
 For IVF-based methods that are not specifically optimized for hybrid query scenarios (Faiss\_IVF and Milvus), their QPS remains relatively stable as the recall varies.
@@
 
-	The IVF-based algorithm CAPS, optimized for hybrid query scenarios, employs a multi-level partitioning strategy that introduces additional overhead.
+	The IVF-based algorithm CAPS, optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead.
 This overhead negatively impacts performan-\\ce on small datasets.
@@
 
-	NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets.
+%	NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets.
 It relies on fusion distance calculations.
 The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
+	NHQ \textcolor{red}{performs moderately overall and poorly on small datasets}.
+Its reliance on fusion distance computations \textcolor{red}{makes it highly sensitive to the number of attributes}, impacting both efficiency and accuracy under multi-attribute filtering.
 
@@
 
-	\begin{figure*}[htbp]
+	\begin{figure*}[h]
 		\centering
@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.8\textwidth]{figures/exp/exp_8_3.pdf}
+		\includegraphics[width=0.75\textwidth]{figures/exp/exp_8_3.pdf}
 		\caption{Dataset Effect on RF-ANN Search}

### 2025-04-28 VLDB2026/main.tex
Update main.tex

@@
 	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
-	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
+	Compared to single-attribute filtering, multi-attribute joint filtering better reflects \textcolor{red}{real-world scenarios}.
+To evaluate algorithm performance \textcolor{red}{under this setting}, we construct the index using 3 uniformly distributed attributes and \textcolor{red}{apply filtering on all 3 attributes simultaneously during queries}.
+%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
 To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

### 2025-04-28 VLDB2026/main.tex
modify

--- 2025-04-28 VLDB2026/main.tex
@@
 Within each group, UNG builds graph-based ANN indexes (e.g., Vamana, HNSW) and connects them via cross-group edges to enable efficient cross-group search.
-	UNG supports Boolean filtering with 2 modes:  1) The query attribute set is a subset of the data attribute set.  2) The query attribute set exactly matches the data attribute set.
+	%UNG supports Boolean filtering with 2 modes:  1) The query attribute set is a subset of the data attribute set.  2) The query attribute set exactly matches the data attribute set.
 
@@
 In hybrid queries, Milvus first pre-filters the dataset using user-specified conditions, then traverses only the corresponding clusters for ANN search—similar to the ID selector mechanism of Faiss.
+
+	\section{Experiments}
+	\subsection{Experimental Setup}
+	\subsubsection{Datasets}
+
+	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015} , covering a diverse range of domains.
+We independently generate attribute for each dataset.
+	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
+Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
+This ensures that the data is initially sorted.
+	\textcolor{red}{In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.}
+
+	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets.
+In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness.
+Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.
+A higher LID indicates greater intrinsic complexity.
 
@@
 
-	\section{Experiments}
-	\subsection{Experimental Setup}
-	\subsubsection{Datasets}
-
-	For attribute filtering tasks, we employ 7 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015} and Text2Image~\cite{texttoimage}, covering a diverse range of domains.
-We independently generate attribute for each dataset.
-
-	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
-Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
-This ensures that the data is initially sorted.
-
-	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets.
-In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness.
-Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.
-A higher LID indicates greater intrinsic complexity.
-
 	\subsubsection{Evaluation Metrics}
@@
 	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
-For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies.
-Milvus, \textcolor{red}{as a general-purpose system}, exhibits comparatively poor performance.
-In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance.
-Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes.
-In fact, filtering can reduce the effective candidate set, improving efficiency.
-%	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
 For IVF-based methods that are not specifically optimized for hybrid query scenarios (Faiss\_IVF and Milvus), their QPS remains relatively stable as the recall varies.
@@
 
-	The IVF-based algorithm CAPS, optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead.
+	The IVF-based algorithm CAPS, optimized for hybrid query scenarios, employs a multi-level partitioning strategy that introduces additional overhead.
 This overhead negatively impacts performan-\\ce on small datasets.
@@
 
-%	NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets.
+	NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets.
 It relies on fusion distance calculations.
 The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
-	NHQ \textcolor{red}{performs moderately overall and poorly on small datasets}.
-Its reliance on fusion distance computations \textcolor{red}{makes it highly sensitive to the number of attributes}, impacting both efficiency and accuracy under multi-attribute filtering.
 
@@
 	\textit{\textbf{Different Datasets.}}  
-	To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset for out-of-distribution (OOD) queries.
+	To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.
 Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.
@@
 
-	\begin{figure*}[h]
+	\begin{figure*}[htbp]
 		\centering
@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.75\textwidth]{figures/exp/exp_8_3.pdf}
+		\includegraphics[width=0.8\textwidth]{figures/exp/exp_8_3.pdf}
 		\caption{Dataset Effect on RF-ANN Search}

### 2025-04-28 VLDB2026/main.tex
modify

@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\
+				Text2Image & 200 & 10,000,000 &10,000 & 59& \textcolor{red}{Text,Image} \\
 

### 2025-04-28 VLDB2026/main.tex
Update main.tex

@@
 	\textit{\textbf{Index size.}}
-	Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data.
+%	Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data.
 In order to unify the comparison standard,
-	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
+%	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
+To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.
 	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it.
@@
 \textcolor{blue}{
-	In this paper, we evaluate various hybrid query methods, including different algorithms, vector databases, and vector libraries.
-For attribute filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance.
-To facilitate fair and reproducible comparisons in future research, we enrich existing datasets with attribute values and design a variety of experimental scenarios based on practical needs.
-We then perform experiments on 7 real-world datasets to analyze the effectiveness of attribute filtering algorithms in depth.
-Additionally, we compare existing range filtering algorithms using 4 range query datasets.
-Finally, we provide a detailed analysis of the experimental results, summarize key findings, and highlight areas for improvement.
-Our study not only validates previous research but also offers insights for future work.
+In this paper, we evaluate hybrid query methods, including algorithms, vector databases, and libraries.
+We design experiments to assess the performance of attribute filtering algorithms.
+We enrich existing datasets with attribute values and create various experimental scenarios to ensure fair comparisons.
+We run experiments on 7 real-world datasets to analyze the effectiveness of attribute filtering algorithms.
+We also compare range filtering algorithms using 4 range query datasets.
+Finally, we analyze the results, summarize key findings, and identify areas for improvement.
+Our study validates previous research and provides insights for future work.
 }

### 2025-04-28 VLDB2026/main.tex
Update main.tex

--- 2025-04-28 VLDB2026/main.tex
@@
 		\setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.98\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
+		\includegraphics[width=0.96\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
 		\caption{Single-Attribute Building and Query (single thread) }
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\abovecaptionskip}{0.0cm}
 		\setlength{\belowcaptionskip}{-0.4cm}
-		\includegraphics[width=\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
+		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
 		\caption{Multi-attribute build and query (single thread)}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\abovecaptionskip}{0.0cm}
 		\setlength{\belowcaptionskip}{-0.4cm}
-		\includegraphics[width=\textwidth]{figures/exp/exp_3_1.pdf}
+		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
 		\caption{Effect of attribute distribution on query performance (single thread)}
@@
 		\setlength{\belowcaptionskip}{-0.1cm}
-		\includegraphics[width=\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
+		\includegraphics[width=0.95\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
 		\caption{Effect of Single-Attribute Selectivity on Query}
@@
 		\centering
-		    \setlength{\abovecaptionskip}{0cm}
+		    \setlength{\abovecaptionskip}{-0.1cm}
 		    \setlength{\belowcaptionskip}{-0.4cm}
@@
 
-	\begin{figure*}[h]
+	\begin{figure*}[t]
+
 		\centering
@@
 		\setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.95\textwidth]{figures/exp/exp_8_2.pdf}
+		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
 		\caption{RF-ANN search }
@@
 		\label{tab:algo_scenarios}
-	\vspace{0cm}
+	\vspace{-0.0cm}
 	\end{table}

### 2025-04-28 VLDB2026/main.tex
modify

--- 2025-04-28 VLDB2026/main.tex
@@
 			\hline
-			NHQ & Graph & C & Y & N& N& N & N & N \\
-			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
-			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
-			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
-			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
-			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
-			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
+			NHQ & Graph & Simultaneous filtering & Y & N& N& N & N & N \\
+			FilteredVamana & Graph & Simultaneous filtering & N & Y & Y & N & Y & Y \\
+			StitchedVamana & Graph & Simultaneous filtering & N & Y & Y & N & N & Y  \\
+			CAPS & IVF &Simultaneous filtering & Y & N & Y & N & Y & Y \\
+			ACORN & Graph & Pre-filtering & Y & Y & Y & Y & Y & Y \\
+			UNG & Graph & Pre-filtering & Y & Y & Y & N & Y & Y \\ 
+			Puck & IVF & Pre-filtering & Y & Y & Y & N & Y & Y \\
 			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
@@
 				\vspace{0.1cm}
-				\textsuperscript{A} Post-filtering, 
-				\textsuperscript{B} Pre-filtering, 
-				\textsuperscript{C} Simultaneous filtering, 
+%				\textsuperscript{A} Post-filtering, 
+%				\textsuperscript{B} Pre-filtering, 
+%				\textsuperscript{C} Simultaneous filtering, 
 				\textsuperscript{Y} Support, 
@@
 				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
+				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
 		\end{minipage}}
@@
 	\noindent\textbf{\underline{Filtered-DiskANN \cite{Filtered-diskann}.}}  
-	\sout{The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.}
+%	\sout{The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.}
 	Filtered-DiskANN also supports simultaneous filtering.
@@
 	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} 
-	\sout{Different from the above graph-based simultaneous filtering algorithms,}CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
+	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
+	CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
 	%As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes.
@@
 			\begin{minipage}{\linewidth}
-				\textsuperscript{Y} Support, 
-				\textsuperscript{N} Unsupport.
-				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
+				\centering
+				\textcolor{red}{The evaluation metrics are consistent with those in Table ~\ref{tab:compair_1}.}
+%				\textsuperscript{Y} Support, 
+%				\textsuperscript{N} Unsupport.
+%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
+%				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
 			\end{minipage} 
@@
 		\setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.96\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
+		\includegraphics[width=0.98\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
 		\caption{Single-Attribute Building and Query (single thread) }
@@
 	\textit{\textbf{Index size.}}
-	Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data.
-In order to unify the comparison standard,
-	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
+	\sout{Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data.
+}
+	In order to unify the comparison standard, we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
 	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it.
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.0cm}
+		\setlength{\abovecaptionskip}{0.1cm}
 		\setlength{\belowcaptionskip}{-0.4cm}
-		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
+		\includegraphics[width=\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
 		\caption{Multi-attribute build and query (single thread)}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.0cm}
+		\setlength{\abovecaptionskip}{0.1cm}
 		\setlength{\belowcaptionskip}{-0.4cm}
-		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
+		\includegraphics[width=\textwidth]{figures/exp/exp_3_1.pdf}
 		\caption{Effect of attribute distribution on query performance (single thread)}
@@
 		\setlength{\belowcaptionskip}{-0.1cm}
-		\includegraphics[width=0.95\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
+		\includegraphics[width=\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
 		\caption{Effect of Single-Attribute Selectivity on Query}
@@
 		\centering
-		    \setlength{\abovecaptionskip}{-0.1cm}
+		    \setlength{\abovecaptionskip}{0cm}
 		    \setlength{\belowcaptionskip}{-0.4cm}
@@
 
-	\begin{figure*}[t]
-
+	\begin{figure*}[h]
 		\centering
@@
 		\setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
+		\includegraphics[width=0.95\textwidth]{figures/exp/exp_8_2.pdf}
 		\caption{RF-ANN search }
@@
 		\label{tab:algo_scenarios}
-	\vspace{-0.0cm}
+	\vspace{0cm}
 	\end{table}

### 2025-04-28 VLDB2026/main.tex

@@
 	\textit{\textbf{Index size.}}
-	\sout{Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data.
-}
-	In order to unify the comparison standard, we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
+%	Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data.
+In order to unify the comparison standard,
+%	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
+To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.
 	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it.

### 2025-04-28 VLDB2026/main.tex
update main

--- 2025-04-28 VLDB2026/main.tex
@@
 				\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
-				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
+				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
 		\end{minipage}}
@@
 	\noindent\textbf{\underline{Filtered-DiskANN \cite{Filtered-diskann}.}}  
-	\sout{The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.}
+	%\sout{The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.}
 	Filtered-DiskANN also supports simultaneous filtering.
@@
 	2) \textbf{StitchedVamana}, which adopts a batch construction strategy—constructing separate Vamana subgraphs for each attribute, followed by merging and edge pruning.
-	A key limitation of Filtered-DiskANN is that while it supports both single-attribute and multi-attribute filtering, it only supports the Boolean OR logic for multi-attribute filtering, lacking support for Boolean AND logic.
+%	A key limitation of Filtered-DiskANN is that only supports the Boolean OR logic for multi-attribute filtering, lacking support for Boolean AND logic.
 
 	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} 
-	\sout{Different from the above graph-based simultaneous filtering algorithms,}CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
+	%\sout{Different from the above graph-based simultaneous filtering algorithms,}CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
 	%As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes.
@@
 	To address the query efficiency degradation caused by the graph compression in SeRF, iRange adopts a more flexible strategy.
-Rather than prebuilding indexes for all possible ranges, it dynamically assembles a query-specific subgraph at runtime.
+	%Rather than prebuilding indexes for all possible ranges, it dynamically assembles a query-specific subgraph at runtime.
 	iRange partitions the dataset into intervals based on attribute values and independently constructs a local graph for each interval, storing only edge information.
@@
 		\setlength{\abovecaptionskip}{0.3cm}
-		\setlength{\belowcaptionskip}{-0.15cm}
+		\setlength{\belowcaptionskip}{-0.0cm}
 
@@
 		\setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.96\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
+		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
 		\caption{Single-Attribute Building and Query (single thread) }
@@
 		\setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.96\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
+		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
 		\caption{Single-Attribute Building and Query (16 threads)}
@@
 		\hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-		\includegraphics[width=0.95\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
+		\includegraphics[width=0.85\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径
 
@@
 		\setlength{\abovecaptionskip}{0.0cm}
-		\setlength{\belowcaptionskip}{-0.4cm}
+		\setlength{\belowcaptionskip}{-0.5cm}
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
@@
 			\setlength{\belowcaptionskip}{0.05cm}
-			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_1.pdf}
+			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
 			\caption{Algorithms optimized for low AS levels.}
@@
 			\setlength{\belowcaptionskip}{0.05cm}
-			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_2.pdf}
+			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_2.pdf}
 			\caption{Algorithms optimized for high AS levels.}
@@
 			\setlength{\belowcaptionskip}{0.05cm}
-			\includegraphics[width=\textwidth]{figures/exp/exp_5_2_3.pdf}
+			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_3.pdf}
 			\caption{Algorithms insensitive to AS level.}
@@
 		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.5cm}
+		\setlength{\belowcaptionskip}{-0.4cm}
 		\caption{Different AS under the same algorithm}
@@
 		    \setlength{\belowcaptionskip}{-0.4cm}
-		\includegraphics[width=0.97\textwidth]{figures/exp/exp_6_1.pdf}
+		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
 		\caption{Effect of dataset on Query}
@@
 		% 放大的图例（占满单栏）
-		\includegraphics[width=0.93\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
+		\includegraphics[width=0.90\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
 

### 2025-04-28 VLDB2026/main.tex
Update main.tex

@@
 		    \setlength{\belowcaptionskip}{-0.5cm}
-		\includegraphics[width=0.75\textwidth]{figures/exp/exp_8_3.pdf}
+		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
 		\caption{Dataset Effect on RF-ANN Search}
@@
 				\hline
-				S1: Large-scale Datasets & Puck, UNG & iRange\\
-				\hline
-				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\
-				\hline
-				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\
-				\hline
-				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\
-
-				\hline
-				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\
-				\hline
-				S6: Resource constraint& CAPS, Faiss&Faiss, SeRF \\
-				\hline
-				S7: High-Recall Querying & UNG & WinFilter \\
-				\hline
-				S8: OOD scenarios & UNG &WinFilter  \\
+				S1: Large-scale Datasets & Puck, UNG & iRange\\[1pt]
+				\hline
+				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\[1pt]
+				\hline
+				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\[1pt]
+				\hline
+				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\[1pt]
+
+				\hline
+				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\[1pt]
+				\hline
+				S6: Resource constraint& CAPS, Faiss&Faiss, SeRF \\[1pt]
+				\hline
+				S7: High-Recall Querying & UNG & WinFilter \\[1pt]
+				\hline
+				S8: OOD scenarios & UNG &WinFilter  \\[1pt]
 				\hline

### 2025-04-28 VLDB2026/main.tex
update fig
modify

--- 2025-04-28 VLDB2026/main.tex
@@
 				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
+				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+			\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
 			\end{minipage} 
@@
 	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
-In contrast, CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping.
-Compared with CAPS, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
+CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping.
+In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs.
@@
 The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
-The performance of CPAS is as good as that of Puck.
-The difference between them is that CPAS further groups the results by attributes within clusters.
+The performance of CAPS is as good as that of Puck.
+The difference between them is that CAPS further groups the results by attributes within clusters.
 In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries.
@@
 To evaluate algorithm performance \textcolor{red}{under this setting}, we construct the index using 3 uniformly distributed attributes and \textcolor{red}{apply filtering on all 3 attributes simultaneously during queries}.
+	 \textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
 	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
@@
 	To investigate this effect, we evaluate 4 AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset.
-Using a single-thread execution environment, we compare the query performance of 13 algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
+Using a single-thread execution environment, we compare the query performance of attribute filtering algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
 

### 2025-04-28 VLDB2026/main.tex

@@
 		% 第二行：两张子图，左侧宽度是右侧的两倍
-		\begin{subfigure}{0.66\textwidth} % 2/3 宽度
+		\begin{subfigure}{0.64\textwidth} % 2/3 宽度
 			\centering
@@
 		\end{subfigure}
-		\hfill % 增加水平间距
-		\begin{subfigure}{0.33\textwidth} % 1/3 宽度
+		\hspace{1mm} % 增加水平间距
+		\begin{subfigure}{0.32\textwidth} % 1/3 宽度
 			\centering

### 2025-04-29 VLDB2026/main.tex
Update main.tex
modify

@@
 The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-Additionally, we conduct an in-depth analysis of how index organization impacts algorithm performance, providing valuable insights for algorithm design.
+We further analyze performance factors from an algorithmic perspective.
 
@@
 	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
-These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution.
+These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
 \textcolor{blue} {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
@@
 	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} 
-	%\sout{Different from the above graph-based simultaneous filtering algorithms,}CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
-	%As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes.
-CAPS addresses this issue by being the first simultaneous filtering algorithm based on spatial partitioning, significantly reducing index size.
-	CAPS introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
+	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
+	\textcolor{red}{CAPS is the first simultaneous filtering algorithm based on spatial partitioning.}
+	It introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
 CAPS adopts a two-level partitioning strategy:
@@
 	ACORN addresses this by introducing a predicate-agnostic indexing framework.
-	Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates, overcoming limitations of methods confined to small-scale equality filters.
+	Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
+	%, overcoming limitations of methods confined to small-scale equality filters. 
 	It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
@@
 		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.5cm}
+		\setlength{\belowcaptionskip}{-0.4cm}
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
@@
 		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.5cm}
+		\setlength{\belowcaptionskip}{-0.4cm}
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}

### 2025-04-29 VLDB2026/main.tex
Update main.tex

--- 2025-04-28 VLDB2026/main.tex
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.5cm}
+
 		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
@@
 
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.02cm}
 		\caption{Graph index and IVF index}
@@
 
-	\setlength{\textfloatsep}{0cm}
-	\setlength{\floatsep}{0cm}
 	\renewcommand{\arraystretch}{0.9}
@@
 		%\setlength{\belowcaptionskip}{-0.3cm}
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.3cm}
+
 		\caption{Comparison of AF-ANN search algorithms}
@@
 		\end{minipage}}
-		\vspace{-0.5cm}
+
 	\end{table*}
@@
 
-	\setlength{\textfloatsep}{0.1cm}
-	\setlength{\floatsep}{0cm}
 	\renewcommand{\arraystretch}{0.9}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.1cm}
+
 		\setlength{\textfloatsep}{0.1cm}
@@
 				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-			\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
 			\end{minipage}
-			\vspace{-0.1cm}
+
 		}
@@
 
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{Datasets}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.3cm}
-		\setlength{\belowcaptionskip}{-0.0cm}
 
@@
 			\centering
-			\setlength{\abovecaptionskip}{-0.02cm}
-			\setlength{\belowcaptionskip}{-0.1cm}
+
 			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
@@
 			\centering
-			\setlength{\abovecaptionskip}{-0.02cm}
-			\setlength{\belowcaptionskip}{-0.1cm}
+
 			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
@@
 			\centering
-			\setlength{\abovecaptionskip}{-0.02cm}
-			\setlength{\belowcaptionskip}{-0.3cm}
+
 			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.5cm}
+
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.5cm}
+
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.1cm}
+
 		% 上面的图例，居中并可通过 hspace 调整左右位置
@@
 	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
-CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping.
-In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
+In contrast, CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping.
+Compared with CAPS, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs.
@@
 The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
-The performance of CAPS is as good as that of Puck.
-The difference between them is that CAPS further groups the results by attributes within clusters.
+The performance of CPAS is as good as that of Puck.
+The difference between them is that CPAS further groups the results by attributes within clusters.
 In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries.
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.0cm}
-		\setlength{\belowcaptionskip}{-0.4cm}
+
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.0cm}
-		\setlength{\belowcaptionskip}{-0.5cm}
+
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
@@
 To evaluate algorithm performance \textcolor{red}{under this setting}, we construct the index using 3 uniformly distributed attributes and \textcolor{red}{apply filtering on all 3 attributes simultaneously during queries}.
-	 \textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
 %	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
@@
 	To investigate this effect, we evaluate 4 AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset.
-Using a single-thread execution environment, we compare the query performance of attribute filtering algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
+Using a single-thread execution environment, we compare the query performance of 13 algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
 
@@
 			\centering
-			\setlength{\abovecaptionskip}{0.05cm}
-			\setlength{\belowcaptionskip}{0.05cm}
+
 			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
@@
 			\centering
-			\setlength{\abovecaptionskip}{0.05cm}
-			\setlength{\belowcaptionskip}{0.05cm}
+
 			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_2.pdf}
@@
 			\centering
-			\setlength{\abovecaptionskip}{0.05cm}
-			\setlength{\belowcaptionskip}{0.05cm}
+
 			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_3.pdf}
@@
 
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.4cm}
 		\caption{Different AS under the same algorithm}
@@
 		\centering
-		    \setlength{\abovecaptionskip}{-0.1cm}
-		    \setlength{\belowcaptionskip}{-0.4cm}
+
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
@@
 
-		\setlength{\abovecaptionskip}{0.02cm}
-		\setlength{\belowcaptionskip}{-0.1cm}
 		\hspace*{11pt}
@@
 			\captionsetup{font=small}
-			\setlength{\abovecaptionskip}{0.02cm}
-			\setlength{\belowcaptionskip}{0.02cm}
+
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
@@
 			\centering
-			\setlength{\abovecaptionskip}{0.02cm}
-			\setlength{\belowcaptionskip}{0.02cm}
+
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
@@
 			\centering
-			\setlength{\abovecaptionskip}{0.02cm}
-			\setlength{\belowcaptionskip}{0.02cm}
+
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.5cm}
+
 		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
@@
 
-	% \begin{figure*}[htbp]
-		%     \centering
-		%     \setlength{\abovecaptionskip}{0cm}
-		%     \setlength{\belowcaptionskip}{-0.4cm}
-		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
-		%     \caption{Dataset Effect on RF-ANN Search}
-		%     \label{fig:exp_8_3}
-		% \end{figure*}
 	\begin{figure*}[htbp]
 		\centering
-		    \setlength{\abovecaptionskip}{0cm}
-		    \setlength{\belowcaptionskip}{-0.5cm}
+
 		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.0cm}
+
 		\caption{Algorithm Recommendation per Scenario}
@@
 		\label{tab:algo_scenarios}
-	\vspace{-0.0cm}
 	\end{table}

### 2025-04-29 VLDB2026/main.tex
Update main.tex

--- 2025-04-29 VLDB2026/main.tex
@@
 			\end{minipage}
-			\vspace{-0.1cm}
+
 		}
@@
 In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness.
-Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.
-A higher LID indicates greater intrinsic complexity.
-
-	\setlength{\textfloatsep}{0.1cm}
-	\setlength{\floatsep}{0cm}
+Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.The higher the LID value, the harder the dataset.
+
 	\renewcommand{\arraystretch}{0.9}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.4cm}
+
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.4cm}
+
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{-0.1cm}
-		\setlength{\belowcaptionskip}{-0.4cm}
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
@@
 
-	% \begin{figure*}[htbp]
-		%     \centering
-		%     \setlength{\abovecaptionskip}{0cm}
-		%     \setlength{\belowcaptionskip}{-0.4cm}
-		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
-		%     \caption{Dataset Effect on RF-ANN Search}
-		%     \label{fig:exp_8_3}
-		% \end{figure*}
 	\begin{figure*}[htbp]
 		\centering
-		\setlength{\abovecaptionskip}{0cm}
-		\setlength{\belowcaptionskip}{-0.5cm}
 		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
@@
 		\label{tab:algo_scenarios}
-		\vspace{-0.0cm}
 	\end{table}

### 2025-04-29 VLDB2026/main.tex
Merge branch 'main' of https://github.com/zhujx001/Hybrid-ANNS

@@
 For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation.
-2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries.
-In real-world applications, an object typically involves multiple attributes.\textcolor{blue}{ For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}
+2) It \sout{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries.
+In real-world applications, an object typically involves multiple attributes.
+For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.
 	3) It does not evaluate algorithm performance under different attribute distributions.
@@
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
-\textcolor{blue} {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
+\sout {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
 
@@
 In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness.
-Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.The higher the LID value, the harder the dataset.
+Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.
+A higher LID indicates greater intrinsic complexity.
 

### 2025-04-29 VLDB2026/main.tex

@@
 In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness.
-Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.
-A higher LID indicates greater intrinsic complexity.
+Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.The higher the LID value, the harder the dataset.
 

### 2025-04-29 VLDB2026/main.tex
Update main.tex

--- 2025-04-29 VLDB2026/main.tex
@@
 
-	For all evaluated algorithms, we adopt the parameter settings recommended in the original study and adjust the parameters related to search in order to obtain different recall and QPS.
+	For all evaluated algorithms, we adopt the parameter settings recommended in the original study and adjust the parameters related to search in order to obtain different Recall and QPS.
 

### 2025-04-29 VLDB2026/main.tex
Update main.tex
modify

--- 2025-04-29 VLDB2026/main.tex
@@
 	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. 
-For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation.
-2) It \sout{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries.
-In real-world applications, an object typically involves multiple attributes.
-For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.
+	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
+	2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios,} 
+	\sout{neglecting the more complex demands of multi-attribute queries.
+In real-world applications, an object typically involves multiple attributes.}\textcolor{blue}{ \sout{For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}}
 	3) It does not evaluate algorithm performance under different attribute distributions. 
-However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.
+	\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}
 
@@
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
-\sout {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
+\textcolor{blue} {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
 
@@
 
-	\noindent\textbf{\underline{UNG \cite{UNG}.}} The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
-UNG is proposed to overcome these limitations.
+	\noindent\textbf{\underline{UNG \cite{UNG}.}} 
+	\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
+UNG is proposed to overcome these limitations.}
 	UNG is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.
@@
 			\begin{minipage}{\linewidth}
-				\textsuperscript{Y} Support, 
-				\textsuperscript{N} Unsupport.
-				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+				\centering
+				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
+%				\textsuperscript{Y} Support, 
+%				\textsuperscript{N} Unsupport.
+%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
+%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
 			\end{minipage}

### 2025-04-29 VLDB2026/main.tex
Update main.tex

--- 2025-04-29 VLDB2026/main.tex
@@
 			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
-			\caption{Index size}
+			\caption{\textcolor{blue}{Index size(include original dataset)}}
 			\label{fig:index_size_mb_comparison_query1}
@@
 	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate 3 key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage.
-Notably, PASE is evaluated exclusively on Audio, GloVe, Msong, and SIFT1M as it supports only data with dimensionality less than 512.
+\textcolor{blue}{Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
+}
 
@@
 	%	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
-	To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.
+	\sout{To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.}
 	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it.

### 2025-04-30 VLDB2026/main.tex
chang 4.2.2

@@
 ACORN-1 and ACORN-\(\gamma\) are specifically designed for single-attribute indexing.
-In database systems (VBASE, PASE, Milvus), when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.
+In database systems (VBASE, PASE, Milvus), \sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.}
+	\textcolor{red}{The attributes do not participate in index construction.}
 	Hence, they are excluded from this comparison.
@@
 4) UNG has poor performance because large number of entry points that need to be traversed.
-It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.
+It is difficult for a graph with multiple entries to have good connectivity, \sout{degenerating into a situation closer to inverted retrieval,} and the effect may be greatly impaired.
 
@@
 The performance of CAPS is as good as that of Puck.
-The difference between them is that CAPS further groups the results by attributes within clusters.
-In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries.
+\sout{The difference between them is that CAPS further groups the results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.

### 2025-04-30 VLDB2026/main.tex

--- 2025-04-29 VLDB2026/main.tex
@@
 
-	For third-party libraries and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
-Faiss does not include optimizations specifically tailored for range filtering scenarios; its query mechanism is identical to that used in tag filtering scenarios.
+	For third-party \textcolor{red}{library} and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
+Faiss does not include optimizations specifically tailored for range filtering scenarios; its query mechanism is identical to that used in \textcolor{red}{attribute} filtering scenarios.
 However, since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
@@
 Under such conditions, UNIFY, iRange, SeRF, and WinFilter require the dataset to be sorted by attribute prior to index construction.
-In contrast, DSG  support dynamic index construction with unordered attribute insertions, making them more suitable for streaming or incremental data scenarios.
-This flexibility highlights their superior extensibility in real-world applications.
+In contrast, DSG  supports dynamic index construction with unordered attribute insertions, making it more suitable for streaming or incremental data scenarios.
+This flexibility highlights its superior extensibility in real-world applications.
 	\subsubsection{Robustness.}
@@
 
-	To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we \textcolor{red}{add} an OOD dataset to the three standard datasets and \textcolor{red}{test} performance under large-range queries.
+	To evaluate the robustness of the RF-ANNS \textcolor{red}{algorithms} in different scenarios, we \textcolor{red}{add} an OOD dataset Text2Image to the three standard datasets and \textcolor{red}{test} performance under large-range queries.
 As shown in Figure~\ref{fig:exp_8_3}, most methods \textcolor{red}{perform} worst on the Text2Image dataset.

### 2025-04-30 VLDB2026/main.tex
modify

@@
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-	We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} on 3 large-scale datasets, using varying query range settings in the experiments.
+	%We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} 
+	\textcolor{red}{We benchmark 5 algorithms specifically designed for range filtering, along with 5 others applicable to range filtering} on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.

### 2025-04-30 VLDB2026/main.tex
Update main.tex

@@
 	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. 
-	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
+	%\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
 	2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios,} 
-	\sout{neglecting the more complex demands of multi-attribute queries.
+	%\sout{neglecting the more complex demands of multi-attribute queries.
 In real-world applications, an object typically involves multiple attributes.}\textcolor{blue}{ \sout{For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}}
 	3) It does not evaluate algorithm performance under different attribute distributions. 
-	\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}
-
-	Moreover, aside from BigANN, there is currently a lack of systematic evaluation specifically targeting hybrid query algorithms.
-To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
+	%\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}
+
+	Moreover, \textcolor{blue}{beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.} To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
 Additionally, we further assess the robustness of each algorithm under varying conditions.
@@
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
-\sout {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
+%\sout {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
 
@@
 	\noindent\textbf{\underline{UNG \cite{UNG}.}} 
-	\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
+	%\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
 UNG is proposed to overcome these limitations.}
@@
 	%	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
-	\sout{To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.}
+	%\sout{To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.}
 	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it.
@@
 ACORN-1 and ACORN-\(\gamma\) are specifically designed for single-attribute indexing.
-In database systems (VBASE, PASE, Milvus), \sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.}
+In database systems (VBASE, PASE, Milvus), %\sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.}
 	\textcolor{red}{The attributes do not participate in index construction.}
@@
 4) UNG has poor performance because large number of entry points that need to be traversed.
-It is difficult for a graph with multiple entries to have good connectivity, \sout{degenerating into a situation closer to inverted retrieval,} and the effect may be greatly impaired.
+It is difficult for a graph with multiple entries to have good connectivity, %\sout{degenerating into a situation closer to inverted retrieval,}
+	and the effect may be greatly impaired.
 
@@
 The performance of CAPS is as good as that of Puck.
-\sout{The difference between them is that CAPS further groups the results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries.
+%\sout{The difference between them is that CAPS further groups the results by attributes within clusters.}
+	In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.

### 2025-04-30 VLDB2026/main.tex
Update main.tex

--- 2025-04-30 VLDB2026/main.tex
@@
 
-	Moreover, aside from BigANN, there is currently a lack of systematic evaluation specifically targeting hybrid query algorithms.
-To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
+	Moreover, \textcolor{blue}{beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.} To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
 Additionally, we further assess the robustness of each algorithm under varying conditions.

### 2025-04-30 VLDB2026/main.tex
modify

--- 2025-04-30 VLDB2026/main.tex
@@
 	%	2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.
-	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. 
-	ACORN addresses this by introducing a predicate-agnostic indexing framework.
-	Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
+	%Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. ACORN addresses this by introducing a predicate-agnostic indexing framework.
+	\textcolor{red}{Pre-filtering methods apply attribute constraints prior to ANN search.
+As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.
+}
+	%Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
 	%, overcoming limitations of methods confined to small-scale equality filters. 
-	It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
-	During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
+	%It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
+	%During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
+		\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
 	ACORN includes two indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, trading memory for higher performance; 
@@
 	\noindent\textbf{\underline{UNG \cite{UNG}.}} 
-	\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
-UNG is proposed to overcome these limitations.}
-	UNG is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.
-It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
+	%\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
+UNG is proposed to overcome these limitations.It is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.}
+	\textcolor{red}{Similar to ACORN, UNG adopts a pre-filtering strategy and serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.} It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
 Then, it constructs a Label Navigating Graph (LNG) to encode inclusion relationships among attribute sets.
@@
 	\noindent\textbf{\underline{Puck \cite{puck}.}}  
-	While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
+	%While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
 In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
-	Developed by Baidu, Puck utilizes two-level quantization for indexing.
+	\textcolor{red}{Puck also adopts a pre-filtering strategy.
+}Developed by Baidu, Puck utilizes two-level quantization for indexing.
 It maintains an attribute set for each cluster to track vector attributes.

### 2025-04-30 VLDB2026/main.tex
Update main.tex

--- 2025-04-30 VLDB2026/main.tex
@@
 	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance. 
-Puck performs well on large-scale datasets, but its performance degrades on small datasets.
+	%Puck performs well on large-scale datasets, but its performance degrades on small datasets.
 Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets.
+	\textcolor{blue}{Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization. }
 	CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
-The vector distribution of the dataset affects the construction of its partitioned index.
+The vector distribution of the dataset affects the construction of its partitioned %index.
 
@@
 	Faiss offers an ID filtering mechanism, it operates solely during query execution and does not influence index building.
-ACORN-1 and ACORN-\(\gamma\) are specifically designed for single-attribute indexing.
-In database systems (VBASE, PASE, Milvus), \sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.}
+\textcolor{blue}{ACORN is   designed for} single-attribute indexing.
+In database systems (VBASE, PASE, Milvus),
+	\sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.} 
 	\textcolor{red}{The attributes do not participate in index construction.}
@@
 The performance of CAPS is as good as that of Puck.
-\sout{The difference between them is that CAPS further groups the results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries.
+\sout{The difference between them is that CAPS further groups the results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.
@@
 
-	\textit{\textbf{Attribute Distribution.}} To comprehensively evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
+	\textit{\textbf{Attribute Distribution.}} \textcolor{blue}{To evaluate} performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
 We evaluate all algorithms under these distributions on each dataset.
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-Specifically, ACORN-1, ACORN-$\gamma$, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+Specifically, \textcolor{blue}{ACORN}, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
 
-	Among all algorithms, ACORN-\(\gamma\) demonstrates the highest robustness.
+	Among all algorithms, ACORN-\(\gamma\) \textcolor{blue}{shows} the highest robustness.
 During index construction, attribute is mainly used for pruning in the lowest layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
@@
 
-	To investigate this effect, we evaluate 4 AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset.
-Using a single-thread execution environment, we compare the query performance of attribute filtering algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
+	To investigate this effect, we evaluate 4 AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset \textcolor{blue}{using single-thread execution.
+We} compare the query performance of attribute filtering algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
 
@@
 
-	According to the query performance trends of different algorithms under varying AS levels, we categorize the algorithms into 3 groups:
+	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS levels, we categorize the algorithms into 3 groups:
 

### 2025-04-30 VLDB2026/main.tex
change 4.2.2

--- 2025-04-30 VLDB2026/main.tex
@@
 	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods.
-	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
-	2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios,} 
-	\sout{neglecting the more complex demands of multi-attribute queries.
-In real-world applications, an object typically involves multiple attributes.}\textcolor{blue}{ \sout{For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}}
+For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation.
+2) It \sout{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries.
+In real-world applications, an object typically involves multiple attributes.
+For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.
 	3) It does not evaluate algorithm performance under different attribute distributions.
-	\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}
-
-	Moreover, \textcolor{blue}{beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.} To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
+However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.
+
+	Moreover, aside from BigANN, there is currently a lack of systematic evaluation specifically targeting hybrid query algorithms.
+To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
 Additionally, we further assess the robustness of each algorithm under varying conditions.
@@
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-	%We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} 
-	\textcolor{red}{We benchmark 5 algorithms specifically designed for range filtering, along with 5 others applicable to range filtering} on 3 large-scale datasets, using varying query range settings in the experiments.
+	We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
@@
 	%	2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.
-	%Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. ACORN addresses this by introducing a predicate-agnostic indexing framework.
-	\textcolor{red}{Pre-filtering methods apply attribute constraints prior to ANN search.
-As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.
-}
-	%Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
+	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. 
+	ACORN addresses this by introducing a predicate-agnostic indexing framework.
+	Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
 	%, overcoming limitations of methods confined to small-scale equality filters. 
-	%It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
-	%During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
-		\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
+	It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
+	During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
 	ACORN includes two indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, trading memory for higher performance; 
@@
 
-	\noindent\textbf{\underline{UNG \cite{UNG}.}} 
-	%\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
-UNG is proposed to overcome these limitations.It is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.}
-	\textcolor{red}{Similar to ACORN, UNG adopts a pre-filtering strategy and serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.} It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
+	\noindent\textbf{\underline{UNG \cite{UNG}.}} The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
+UNG is proposed to overcome these limitations.
+	UNG is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.
+It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
 Then, it constructs a Label Navigating Graph (LNG) to encode inclusion relationships among attribute sets.
@@
 	\noindent\textbf{\underline{Puck \cite{puck}.}}  
-	%While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
+	While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
 In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
-	\textcolor{red}{Puck also adopts a pre-filtering strategy.
-}Developed by Baidu, Puck utilizes two-level quantization for indexing.
+	Developed by Baidu, Puck utilizes two-level quantization for indexing.
 It maintains an attribute set for each cluster to track vector attributes.
@@
 			\begin{minipage}{\linewidth}
-				\centering
-				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
-%				\textsuperscript{Y} Support, 
-%				\textsuperscript{N} Unsupport.
-%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+				\textsuperscript{Y} Support, 
+				\textsuperscript{N} Unsupport.
+				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
+				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
 			\end{minipage}
@@
 	Faiss offers an ID filtering mechanism, it operates solely during query execution and does not influence index building.
-ACORN-1 and ACORN-\(\gamma\) are specifically designed for single-attribute indexing.
+ACORN is designed for single-attribute indexing.
 In database systems (VBASE, PASE, Milvus), \sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.}
@@
 
-	For third-party \textcolor{red}{library} and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
-Faiss does not include optimizations specifically tailored for range filtering scenarios; its query mechanism is identical to that used in \textcolor{red}{attribute} filtering scenarios.
+	For third-party libraries and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
+Faiss does not include optimizations specifically tailored for range filtering scenarios; its query mechanism is identical to that used in tag filtering scenarios.
 However, since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
@@
 Under such conditions, UNIFY, iRange, SeRF, and WinFilter require the dataset to be sorted by attribute prior to index construction.
-In contrast, DSG  supports dynamic index construction with unordered attribute insertions, making it more suitable for streaming or incremental data scenarios.
-This flexibility highlights its superior extensibility in real-world applications.
+In contrast, DSG  support dynamic index construction with unordered attribute insertions, making them more suitable for streaming or incremental data scenarios.
+This flexibility highlights their superior extensibility in real-world applications.
 	\subsubsection{Robustness.}
@@
 
-	To evaluate the robustness of the RF-ANNS \textcolor{red}{algorithms} in different scenarios, we \textcolor{red}{add} an OOD dataset Text2Image to the three standard datasets and \textcolor{red}{test} performance under large-range queries.
+	To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we \textcolor{red}{add} an OOD dataset to the three standard datasets and \textcolor{red}{test} performance under large-range queries.
 As shown in Figure~\ref{fig:exp_8_3}, most methods \textcolor{red}{perform} worst on the Text2Image dataset.

### 2025-04-30 VLDB2026/main.tex
change 4.2.2
Update main.tex

--- 2025-04-30 VLDB2026/main.tex
@@
 2) A dynamic segment graph is a neighbor graph where each edge is annotated with its valid attribute range.
-	With these structures, only few regions need updates when inserting new data. During the query process, the system considers only edges valid for current attribute range, boosting efficiency.
+	With these structures, only few regions need updates when inserting new data. \textcolor{blue}{The system considers only edges valid for current attribute range to boost efficiency during search.}
 
@@
 VBASE adopts a post-filtering strategy.
-However, it employs an iterative filtering mechanism: during index traversal, each node is immediately checked against the WHERE clause, and non-matching nodes are discarded.
+However, it employs an iterative filtering mechanism: during index traversal, \textcolor{blue}{each node is checked} against the WHERE clause, and non-matching nodes are discarded.
 This avoids the issue in PASE where the final result set may contain fewer than $k$ results.
@@
 
-	To comprehensively assess the overall performance of different algorithms, we adopt a multi-dimensional quantitative evaluation framework~\cite{compare}, which includes the following 5 core metrics:
+	To assess the overall performance of different algorithms, we adopt a multi-dimensional quantitative evaluation framework~\cite{compare}, including the following 5 core metrics:
 
@@
 
-	For all evaluated algorithms, we adopt the parameter settings recommended in the original study and adjust the parameters related to search in order to obtain different Recall and QPS.
+	\textcolor{blue}{For all algorithms, we adopt recommended settings from the original study and adjust the parameters related to search in order to obtain different Recall and QPS.}
 
@@
 
-	We next evaluate the query performance of AF-ANN search algorithms, focusing on 3 main scenarios.
+	We next evaluate the query performance of AF-ANN search \textcolor{blue}{methods}, focusing on 3 main scenarios.
 

### 2025-04-30 VLDB2026/main.tex
Update main.tex

@@
 2) Filtering the dataset based on attribute ranges before performing ANN search.
-However, both approaches suffer from suboptimal performance.
-Building a separate neighbor graph (e.g., HNSW) for each attribute range could ensure efficient querying but incurs an $O(n^2)$ cost in constructing and storing $n$ graphs.
+\sout{However, both approaches suffer from suboptimal performance.} Building a separate neighbor graph (e.g., HNSW) for each attribute range could ensure efficient querying but incurs an $O(n^2)$ cost in constructing and storing $n$ graphs.
 Since many edges are shared across these graphs, SeRF introduces a validity-range aware design where each edge records the interval in which it is valid, indicating in which subgraphs the edge remains valid.
@@
 These segment graphs are then integrated into a unified global graph.
-SIG adheres to a graph inclusiveness principle: any query subgraph can be composed from existing segment graphs, avoiding the need for range-specific index construction.
-Its hierarchical variant, HSIG, enhances SIG by incorporating the multilayer design of HNSW, skip lists, and edge bitmaps for efficient range localization and post-filtering pruning.
-UNIFY supports 3 filtering strategies—pre-filtering, post-filtering, and  simultaneous filtering—enabling robust and flexible performance across diverse application scenarios.
+\sout{SIG adheres to a graph inclusiveness principle: any query subgraph can be composed from existing segment graphs, avoiding the need for range-specific index construction.} Its hierarchical variant, HSIG, enhances SIG by incorporating the multilayer design of HNSW, skip lists, and edge bitmaps for efficient range localization and post-filtering pruning.
+UNIFY supports 3 filtering strategies—pre-filtering, post-filtering, and  simultaneous filtering—enabling robust and flexible performance.
 

### 2025-05-01 VLDB2026/main.tex
Update main.tex
modify

@@
 	%\begin{sloppypar}
-
-	\title{An Experimental Evaluation of Hybrid Vector Search (EA\&B)}
+	\title{An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)}
 
@@
 	\textcolor{red}{Pre-filtering methods apply attribute constraints prior to ANN search.
-As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.
-}
+As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.}
 	%Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
@@
 	%During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
-		\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
+	\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.
+During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
 	ACORN includes two indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, trading memory for higher performance; 

### 2025-05-01 VLDB2026/main.tex
change 1

--- 2025-04-30 VLDB2026/main.tex
@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
-As for range filtering algorithms, the size of the query range and the characteristics of different datasets also play an important role in determining algorithm performance.
-
-	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some algorithms, it presents several notable limitations:
+For attribute filtering algorithms, factors such as \textcolor{blue}{the number of attributes}, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
+As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.
+
+	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some ANN algorithms, it presents several notable limitations:
 	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. 
@@
 	\textcolor{red}{We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
-In addition, we survey 5 range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
+In addition, we survey 5 range filtering algorithms, and provide an overview of widely used 4 vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
 These efforts offer a unified reference framework for future research.}
@@
 		To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-Furthermore, we design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity levels, and query conditions.
-These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query processing.
+Furthermore, we design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
+These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 	}
@@
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-	\textcolor{red}{We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.}By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
-We further examine their behavior under different attribute distributions and selectivity conditions to assess robustness and adaptability in complex query scenarios.
+	\textcolor{red}{We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.} By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
+We further examine their behavior under different attribute distributions and selectivity to assess robustness and adaptability in complex query scenarios.
 Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
@@
 	%We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} 
-	\textcolor{red}{We benchmark 5 algorithms specifically designed for range filtering, along with 5 others applicable to range filtering} on 3 large-scale datasets, using varying query range settings in the experiments.
-The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-We further analyze performance factors from an algorithmic perspective.
+	\textcolor{red}{We benchmark algorithms that support range filtering} on 3 large-scale datasets, using varying query range settings in the experiments.
+The experimental results \textcolor{blue}{show} the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
+\textcolor{blue}{We further analyze the factors that affect the performance of the range query algorithm.}
 
@@
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
-\sout {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
+Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.
 

### 2025-05-01 VLDB2026/main.tex
change 3.2

@@
 	Current hybrid query methods mainly adopt graph-based ~\cite{nsw,kgraph,nsg,fanng,ngt} or Inverted File Index (IVF)-based \cite{PQ} index organization.
-We briefly introduce the fundamental principles of these 2 types in the following.
+We briefly introduce the fundamental principles of these two types in the following.
 
@@
 
-	\section{Overview of Hybrid query Algorithms}
+	\section{Hybrid query Algorithms}
 
@@
 
-	\noindent\textbf{\underline{SeRF \cite{serf}.}}  
-	Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
+	\noindent\textbf{\underline{SeRF \cite{serf}.}} Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
 2) Filtering the dataset based on attribute ranges before performing ANN search.
-\sout{However, both approaches suffer from suboptimal performance.} Building a separate neighbor graph (e.g., HNSW) for each attribute range could ensure efficient querying but incurs an $O(n^2)$ cost in constructing and storing $n$ graphs.
+Building a separate neighbor graph (e.g., HNSW) for each attribute range could ensure efficient querying but incurs an $O(n^2)$ cost in constructing and storing $n$ graphs.
 Since many edges are shared across these graphs, SeRF introduces a validity-range aware design where each edge records the interval in which it is valid, indicating in which subgraphs the edge remains valid.
@@
 These segment graphs are then integrated into a unified global graph.
-\sout{SIG adheres to a graph inclusiveness principle: any query subgraph can be composed from existing segment graphs, avoiding the need for range-specific index construction.} Its hierarchical variant, HSIG, enhances SIG by incorporating the multilayer design of HNSW, skip lists, and edge bitmaps for efficient range localization and post-filtering pruning.
+Its hierarchical variant, HSIG, enhances SIG by incorporating the multilayer design of HNSW, skip lists, and edge bitmaps for efficient range localization and post-filtering pruning.
 UNIFY supports 3 filtering strategies—pre-filtering, post-filtering, and  simultaneous filtering—enabling robust and flexible performance.

### 2025-05-01 VLDB2026/main.tex
change 4.2.2

--- 2025-05-01 VLDB2026/main.tex
@@
 	\textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
-	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query process.
-	\textcolor{red}{We modified the NHQ source code to support this experiment.}
+	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query.
 
@@
 In database systems (VBASE, PASE, Milvus),
-	\sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.} 
-	\textcolor{red}{The attributes do not participate in index construction.}
+	%\sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.} 
+	\textcolor{red}{attributes do not participate in index construction.}
 	Hence, they are excluded from this comparison.
@@
 4) UNG has poor performance because large number of entry points that need to be traversed.
-It is difficult for a graph with multiple entries to have good connectivity, \sout{degenerating into a situation closer to inverted retrieval,} and the effect may be greatly impaired.
+It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.
 
@@
 The performance of CAPS is as good as that of Puck.
-\sout{The difference between them is that CAPS further groups the results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
+The difference between them is that CAPS further groups the results by attributes within clusters.
+In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.

### 2025-05-01 VLDB2026/main.tex
Update main.tex

--- 2025-05-01 VLDB2026/main.tex
@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute filtering algorithms, factors such as \textcolor{blue}{the number of attributes}, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
-As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.
-
-	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some ANN algorithms, it presents several notable limitations:
+For attribute filtering algorithms, factors such as the number of base attributes, the number of query attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
+As for range filtering algorithms, the size of the query range and the characteristics of different datasets also play an important role in determining algorithm performance.
+
+	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some algorithms, it presents several notable limitations:
 	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. 
@@
 	\textcolor{red}{We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
-In addition, we survey 5 range filtering algorithms, and provide an overview of widely used 4 vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
+In addition, we survey 5 range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
 These efforts offer a unified reference framework for future research.}
@@
 		To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-Furthermore, we design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
-These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+Furthermore, we design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity levels, and query conditions.
+These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query processing.
 	}
@@
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-	\textcolor{red}{We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.} By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
-We further examine their behavior under different attribute distributions and selectivity to assess robustness and adaptability in complex query scenarios.
+	\textcolor{red}{We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.}By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
+We further examine their behavior under different attribute distributions and selectivity conditions to assess robustness and adaptability in complex query scenarios.
 Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
@@
 	%We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} 
-	\textcolor{red}{We benchmark algorithms that support range filtering} on 3 large-scale datasets, using varying query range settings in the experiments.
-The experimental results \textcolor{blue}{show} the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-\textcolor{blue}{We further analyze the factors that affect the performance of the range query algorithm.}
+	\textcolor{red}{We benchmark 5 algorithms specifically designed for range filtering, along with 5 others applicable to range filtering} on 3 large-scale datasets, using varying query range settings in the experiments.
+The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
+We further analyze performance factors from an algorithmic perspective.
 
@@
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
-Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.
+\sout {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
 
@@
 	Current hybrid query methods mainly adopt graph-based ~\cite{nsw,kgraph,nsg,fanng,ngt} or Inverted File Index (IVF)-based \cite{PQ} index organization.
-We briefly introduce the fundamental principles of these two types in the following.
+We briefly introduce the fundamental principles of these 2 types in the following.
 
@@
 
-	\section{Hybrid query Algorithms}
+	\section{Overview of Hybrid query Algorithms}
 
@@
 	\textcolor{red}{Pre-filtering methods apply attribute constraints prior to ANN search.
-As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.}
+As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.
+}
 	%Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
@@
 	%During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
-	\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.
-During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
+		\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
 	ACORN includes two indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, trading memory for higher performance; 
@@
 
-	\noindent\textbf{\underline{SeRF \cite{serf}.}} Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
+	\noindent\textbf{\underline{SeRF \cite{serf}.}}  
+	Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
 2) Filtering the dataset based on attribute ranges before performing ANN search.
-Building a separate neighbor graph (e.g., HNSW) for each attribute range could ensure efficient querying but incurs an $O(n^2)$ cost in constructing and storing $n$ graphs.
+\sout{However, both approaches suffer from suboptimal performance.} Building a separate neighbor graph (e.g., HNSW) for each attribute range could ensure efficient querying but incurs an $O(n^2)$ cost in constructing and storing $n$ graphs.
 Since many edges are shared across these graphs, SeRF introduces a validity-range aware design where each edge records the interval in which it is valid, indicating in which subgraphs the edge remains valid.
@@
 These segment graphs are then integrated into a unified global graph.
-Its hierarchical variant, HSIG, enhances SIG by incorporating the multilayer design of HNSW, skip lists, and edge bitmaps for efficient range localization and post-filtering pruning.
+\sout{SIG adheres to a graph inclusiveness principle: any query subgraph can be composed from existing segment graphs, avoiding the need for range-specific index construction.} Its hierarchical variant, HSIG, enhances SIG by incorporating the multilayer design of HNSW, skip lists, and edge bitmaps for efficient range localization and post-filtering pruning.
 UNIFY supports 3 filtering strategies—pre-filtering, post-filtering, and  simultaneous filtering—enabling robust and flexible performance.
@@
 
-	\subsubsection{Robustness}In the following, we evaluate the robustness of these algorithms.
-
-	\textit{\textbf{Attribute Distribution.}} \textcolor{blue}{To evaluate} performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
+	\subsubsection{Robustness}In the following, we evaluate the robustness of \textcolor{blue}{attribute filtering algorithms.}
+
+	\textit{\textbf{Attribute Distribution.}} \textcolor{blue}{To evaluate the performance of these algorithms across different attribute distributions, we generate attribute} sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
 We evaluate all algorithms under these distributions on each dataset.

### 2025-05-01 VLDB2026/main.tex
Update main.tex

--- 2025-05-01 VLDB2026/main.tex
@@
 	\textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
-	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query.
+	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query process.
+	\textcolor{red}{We modified the NHQ source code to support this experiment.}
 
@@
 In database systems (VBASE, PASE, Milvus),
-	%\sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.} 
-	\textcolor{red}{attributes do not participate in index construction.}
+	\sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.} 
+	\textcolor{red}{The attributes do not participate in index construction.}
 	Hence, they are excluded from this comparison.
@@
 The performance of CAPS is as good as that of Puck.
-The difference between them is that CAPS further groups the results by attributes within clusters.
-In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
+\sout{The difference between them is that CAPS further groups the results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.
@@
 To evaluate algorithm performance \textcolor{red}{under this setting}, we construct the index using 3 uniformly distributed attributes and \textcolor{red}{apply filtering on all 3 attributes simultaneously during queries}.
-	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
+%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
 	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
@@
 Milvus, \textcolor{red}{as a general-purpose system}, exhibits comparatively poor performance.
-In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance.
+
+	{\color{red}
+		The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance.
+It naturally supports pre-filtering and remains unaffected by the increasing number of attributes.
+In fact, filtering can reduce the effective candidate set, thereby improving search efficiency.
+In contrast, the IVF-based algorithm CAPS, which is optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead.
+This overhead negatively impacts performance on small datasets.
+However, on large datasets, the overhead is amortized, and the advantages of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
+	}
+
+%	In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance.
 Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes.
@@
 
-	The IVF-based algorithm CAPS, optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead.
-This overhead negatively impacts performan-\\ce on small datasets.
+%	The IVF-based algorithm CAPS, optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead.
+This overhead negatively impacts performance on small datasets.
 However, on large datasets, the overhead is amortized, and the benefits of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
@@
 The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
-	NHQ \textcolor{red}{performs moderately overall and poorly on small datasets}.
+	NHQ \textcolor{red}{performs moderately overall but poorly on small datasets}.
 Its reliance on fusion distance computations \textcolor{red}{makes it highly sensitive to the number of attributes}, impacting both efficiency and accuracy under multi-attribute filtering.

### 2025-05-01 VLDB2026/main.tex
Update main.tex
change 4.2.2

--- 2025-05-01 VLDB2026/main.tex
@@
 The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
-The performance of CAPS is as good as that of Puck.
-The difference between them is that CAPS further groups the results by attributes within clusters.
-In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
+\textcolor{red}{CAPS performs as well as Puck, but differs by further grouping results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.
@@
 
-	\subsubsection{Robustness}In the following, we evaluate the robustness of \textcolor{blue}{attribute filtering algorithms.}
-
-	\textit{\textbf{Attribute Distribution.}} \textcolor{blue}{To evaluate the performance of these algorithms across different attribute distributions, we generate attribute} sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
+	\subsubsection{Robustness}In the following, we evaluate the robustness of these algorithms.
+
+	\textit{\textbf{Attribute Distribution.}} \textcolor{blue}{To evaluate} performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
 We evaluate all algorithms under these distributions on each dataset.

### 2025-05-01 VLDB2026/main.tex
Update main.tex

@@
 		However, current evaluations lack unified benchmarking standards and systematic assessment methodologies.
-Existing studies not only fail to cover mainstream algorithms but also omit systematic comparisons or in-depth analyses of different methods.
+Existing studies not only fail to cover mainstream algorithms but also omit systematic comparisons or in-depth analysis on different methods.
 To address this issue, we design a complete evaluation framework for hybrid queries.
-Our study introduces 15 hybrid query algorithms and systematically classifies them based on multiple dimensions such as index organization and filtering strategy, providing a reference for the categorization of hybrid queries.
-In the experiments, for attribute filtering, we construct standarded attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
-For range filtering, we systematically evaluate algorithm performance across these 3 metrics through controlled variation of query ranges.
+Our study introduces 15 hybrid query algorithms and systematically classifies them based on multiple dimensions, such as index organization and filtering strategy, providing a reference for the categorization of hybrid queries.
+In experiments, for attribute filtering, we construct standard attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
+For range filtering, we systematically evaluate performance across the 3 metrics through controlled variation of query ranges.
 Additionally, we conduct an in-depth analysis of the experimental results based on the underlying principles of the algorithms.

### 2025-05-01 VLDB2026/main.tex
modify

--- 2025-05-01 VLDB2026/main.tex
@@
 The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
-\textcolor{red}{CAPS performs as well as Puck, but differs by further grouping results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
+The performance of CAPS is as good as that of Puck.
+The difference between them is that CAPS further groups the results by attributes within clusters.
+In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.
@@
 	\textit{\textbf{Single-Attribute Selectivity.}}
-	In hybrid queries, varying levels of attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
+	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
 AS is defined as the proportion of data points sharing a given attribute value.
@@
 
-	To investigate this effect, we evaluate 4 AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset \textcolor{blue}{using single-thread execution.
-We} compare the query performance of attribute filtering algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
-
-	Experimental results show that UNG achieves the best performance across all AS levels, especially at extremely low AS (1\%). 
+	To investigate this effect, we evaluate 4 AS \textcolor{blue}{settings} (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset \textcolor{blue}{using single-thread execution.
+We} compare the query performance of attribute filtering algorithms \textcolor{blue}{across these settings}, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
+
+	Experimental results show that UNG achieves the best performance across all AS  \textcolor{blue}{settings}, especially at extremely low AS (1\%). 
 	This advantage stems from its pre-filtering strategy.
@@
 			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
-			\caption{Algorithms optimized for low AS levels.}
+			\caption{Algorithms optimized for low AS.}
 			\label{fig:exp_5_2_1}
@@
 			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_2.pdf}
-			\caption{Algorithms optimized for high AS levels.}
+			\caption{Algorithms optimized for high AS.}
 			\label{fig:exp_5_2_2}
@@
 			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_3.pdf}
-			\caption{Algorithms insensitive to AS level.}
+			\caption{Algorithms insensitive to AS.}
 			\label{fig:exp_5_2_3}
@@
 
-	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS levels, we categorize the algorithms into 3 groups:
-
-	(1) \textit{Algorithms optimized for low AS levels.}  
+	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS \textcolor{blue}{settings}, we categorize the algorithms into 3 groups:
+
+	(1) \textit{Algorithms optimized for low AS.}  
 	This group includes ACORN-1, Faiss+HQI\_Batch, StitchedVamana, UNG, Faiss, Puck, and CAPS, as illustrated in Figure~\ref{fig:exp_5_2_1}.
 
-	ACORN-1 performs well in low AS scenarios because fewer nodes share the same attribute.
+	ACORN-1 performs well in low AS \textcolor{blue}{settings} because fewer nodes share the same attribute.
 This increases the average degree of retained nodes and improves graph connectivity.
@@
 StitchedVamana optimizes local adjacency using independent subgraphs, enabling fast localization at low AS.
-However, at higher AS levels, it requires broader global exploration.
-UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS conditions, leading to better performance.
-
-	Interestingly, Faiss and Faiss+HQI\_Batch perform worst at the 50\% AS level instead of 75\%, which might seem unexpected.
-This happens because, when AS decreases from 75\% to 50\%, fewer data points are filtered out.
-As a result, more clusters must be searched, increasing computational cost.
+However, at higher AS \textcolor{blue}{settings}, it requires broader global exploration.
+UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS \textcolor{blue}{settings}, leading to better performance.
+
+	Interestingly, Faiss and Faiss+HQI\_Batch perform worst at the 50\% AS instead of 75\%.
+	%, which might seem unexpected. 
+	This happens because, when AS decreases from 75\% to 50\%, fewer data points are filtered out. As a result, more clusters must be searched, increasing computational cost.
 
 	\par
-	(2) \textit{Algorithms optimized for high AS levels.}  
+	(2) \textit{Algorithms optimized for high AS.}  
 	This group includes NHQ, FilteredVamana, VBASE, and PASE, as shown in Figure~\ref{fig:exp_5_2_2}.
 
-	At low AS levels, NHQ struggles to locate relevant regions efficiently, leading to excessive computations on non-matching nodes.
+	At low AS, NHQ struggles to locate relevant regions efficiently, leading to excessive computations on non-matching nodes.
 FilteredVamana also performs poorly in these scenarios.
@@
 	\par
-	(3) \textit{Algorithms insensitive to AS level.}  
+	(3) \textit{Algorithms insensitive to AS.}  
 	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
@@
 As a result, its query performance remains largely unaffected by AS variations.
-ACORN-\(\gamma\) maintains stable performance across different AS levels by using a higher index construction parameter $\gamma$.
+ACORN-\(\gamma\) maintains stable performance across different AS \textcolor{blue}{settings} by using a higher index construction parameter $\gamma$.
 This ensures a relatively stable average node degree, even after attribute pruning, minimizing the impact of AS changes on query efficiency.
@@
 
-	Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
+	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
+	\textcolor{blue}{Similarly}, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
 
@@
 	\textit{\textbf{Peak memory usage.}}
-	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets.
-It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.
+	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
 
@@
 
-	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
+	%As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
 It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.

### 2025-05-01 VLDB2026/main.tex
modify

@@
 
-	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS \textcolor{blue}{settings}, we categorize the algorithms into 3 groups:
+	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
 
@@
 
-	ACORN-1 performs well in low AS \textcolor{blue}{settings} because fewer nodes share the same attribute.
+	ACORN-1 performs well in low AS because fewer nodes share the same attribute.
 This increases the average degree of retained nodes and improves graph connectivity.
@@
 StitchedVamana optimizes local adjacency using independent subgraphs, enabling fast localization at low AS.
-However, at higher AS \textcolor{blue}{settings}, it requires broader global exploration.
-UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS \textcolor{blue}{settings}, leading to better performance.
+However, at higher AS, it requires broader global exploration.
+UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
 

### 2025-05-01 VLDB2026/main.tex
modify
Update main.tex

--- 2025-05-01 VLDB2026/main.tex
@@
 	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. 
-	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
+%	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
 	2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios,} 
-	\sout{neglecting the more complex demands of multi-attribute queries.
+%	\sout{neglecting the more complex demands of multi-attribute queries.
 In real-world applications, an object typically involves multiple attributes.}\textcolor{blue}{ \sout{For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}}
 	3) It does not evaluate algorithm performance under different attribute distributions. 
-	\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}
+%	\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}
 
@@
 	CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
-The vector distribution of the dataset affects the construction of its partitioned %index.
-
+The vector distribution of the dataset affects the construction of its \textcolor{blue}{partitioned index.}
 	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
@@
 	\textit{\textbf{Single-Attribute Selectivity.}}
-	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
+	In hybrid queries, varying levels of attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
 AS is defined as the proportion of data points sharing a given attribute value.
@@
 
-	To investigate this effect, we evaluate 4 AS \textcolor{blue}{settings} (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset \textcolor{blue}{using single-thread execution.
-We} compare the query performance of attribute filtering algorithms \textcolor{blue}{across these settings}, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
-
-	Experimental results show that UNG achieves the best performance across all AS  \textcolor{blue}{settings}, especially at extremely low AS (1\%). 
+	To investigate this effect, we evaluate 4 AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset \textcolor{blue}{using single-thread execution.
+We} compare the query performance of attribute filtering algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
+
+	Experimental results show that UNG achieves the best performance across all AS levels, especially at extremely low AS (1\%). 
 	This advantage stems from its pre-filtering strategy.
@@
 			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
-			\caption{Algorithms optimized for low AS.}
+			\caption{Algorithms optimized for low AS levels.}
 			\label{fig:exp_5_2_1}
@@
 			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_2.pdf}
-			\caption{Algorithms optimized for high AS.}
+			\caption{Algorithms optimized for high AS levels.}
 			\label{fig:exp_5_2_2}
@@
 			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_3.pdf}
-			\caption{Algorithms insensitive to AS.}
+			\caption{Algorithms insensitive to AS level.}
 			\label{fig:exp_5_2_3}
@@
 
-	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS \textcolor{blue}{settings}, we categorize the algorithms into 3 groups:
-
-	(1) \textit{Algorithms optimized for low AS.}  
+	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS levels, we categorize the algorithms into 3 groups:
+
+	(1) \textit{Algorithms optimized for low AS levels.}  
 	This group includes ACORN-1, Faiss+HQI\_Batch, StitchedVamana, UNG, Faiss, Puck, and CAPS, as illustrated in Figure~\ref{fig:exp_5_2_1}.
 
-	ACORN-1 performs well in low AS \textcolor{blue}{settings} because fewer nodes share the same attribute.
+	ACORN-1 performs well in low AS scenarios because fewer nodes share the same attribute.
 This increases the average degree of retained nodes and improves graph connectivity.
@@
 StitchedVamana optimizes local adjacency using independent subgraphs, enabling fast localization at low AS.
-However, at higher AS \textcolor{blue}{settings}, it requires broader global exploration.
-UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS \textcolor{blue}{settings}, leading to better performance.
-
-	Interestingly, Faiss and Faiss+HQI\_Batch perform worst at the 50\% AS instead of 75\%.
-	%, which might seem unexpected. 
-	This happens because, when AS decreases from 75\% to 50\%, fewer data points are filtered out. As a result, more clusters must be searched, increasing computational cost.
+However, at higher AS levels, it requires broader global exploration.
+UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS conditions, leading to better performance.
+
+	Interestingly, Faiss and Faiss+HQI\_Batch perform worst at the 50\% AS level instead of 75\%, which might seem unexpected.
+This happens because, when AS decreases from 75\% to 50\%, fewer data points are filtered out.
+As a result, more clusters must be searched, increasing computational cost.
 
 	\par
-	(2) \textit{Algorithms optimized for high AS.}  
+	(2) \textit{Algorithms optimized for high AS levels.}  
 	This group includes NHQ, FilteredVamana, VBASE, and PASE, as shown in Figure~\ref{fig:exp_5_2_2}.
 
-	At low AS, NHQ struggles to locate relevant regions efficiently, leading to excessive computations on non-matching nodes.
+	At low AS levels, NHQ struggles to locate relevant regions efficiently, leading to excessive computations on non-matching nodes.
 FilteredVamana also performs poorly in these scenarios.
@@
 	\par
-	(3) \textit{Algorithms insensitive to AS.}  
+	(3) \textit{Algorithms insensitive to AS level.}  
 	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
@@
 As a result, its query performance remains largely unaffected by AS variations.
-ACORN-\(\gamma\) maintains stable performance across different AS \textcolor{blue}{settings} by using a higher index construction parameter $\gamma$.
+ACORN-\(\gamma\) maintains stable performance across different AS levels by using a higher index construction parameter $\gamma$.
 This ensures a relatively stable average node degree, even after attribute pruning, minimizing the impact of AS changes on query efficiency.
@@
 
-	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
-	\textcolor{blue}{Similarly}, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
+	Similar to the evaluation of \textit{Attribute Filtering} algorithms, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
 
@@
 	\textit{\textbf{Peak memory usage.}}
-	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
+	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets.
+It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.
 
@@
 
-	%As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
+	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
 It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.
@@
 	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
-The experimental results show that across all datasets (Deep, YT-Audio, and WIT) and query ranges, WinFilter consistently delivers the best performance.
-This highlights the robustness of its design, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
+The experimental results show that across all datasets (Deep, YT-Audio, and WIT) and query ranges, WinFilter consistently delivers the best performance.\textcolor{blue}{ This highlights the robustnes} , which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
 
@@
 	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
-Unlike other range filtering algorithms, ACORN is not designed with specialized data structures (such as the $\beta$-WST in WinFilter, the rectangle tree and dynamic segment graph in SeRF, or the HSIG in UNIFY) to achieve efficient range filtering.
+Unlike other range filtering algorithms,\textcolor{blue}{ ACORN is not designed with specialized data structures  to achieve efficient range filtering}.
 In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
@@
 	For third-party \textcolor{red}{library} and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
-Faiss does not include optimizations specifically tailored for range filtering scenarios; its query mechanism is identical to that used in \textcolor{red}{attribute} filtering scenarios.
-However, since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
-Similar to the selectivity observed in attribute filtering, Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
+\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
+Similar to the selectivity observed in attribute filtering.
+}
+	Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
 With a smaller range, fewer points remain after filtering, resulting in lower computational cost.
-In addition, the performance of Faiss is influenced by data dimensionality; it tends to work better on low-dimensional datasets.
+In addition, the performance of Faiss is influenced by data dimensionality; \textcolor{blue}{ the higher the dimensionality, the worse the performance.}
 
@@
 PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
-VBASE performs better on large-range queries.
-Compared to PASE, its performance on small ranges is significantly improved, achieving higher recall despite very low QPS.
+	\textcolor{blue}{VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is very low.}ok
 
@@
 
-	To evaluate the robustness of the RF-ANNS \textcolor{red}{algorithms} in different scenarios, we \textcolor{red}{add} an OOD dataset Text2Image to the three standard datasets and \textcolor{red}{test} performance under large-range queries.
+	To evaluate the robustness of the RF-ANNS \textcolor{red}{algorithms} in different scenarios, we \textcolor{red}{ add an OOD dataset in the experiments}.
 As shown in Figure~\ref{fig:exp_8_3}, most methods \textcolor{red}{perform} worst on the Text2Image dataset.
@@
 This means that DSG is more sensitive to changes in data distribution.
-Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.
+%	Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.
 	%	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets.
@@
 
-	Lastly, our findings show that the distribution and cardinality of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
+	Lastly, our findings show that the distribution and the \textcolor{blue}{ number} of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
 Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.
@@
 	\section{CONCLUSION}
-	\textcolor{blue}{
-		In this paper, we evaluate hybrid query methods, including algorithms, vector databases, and libraries.
+	\textcolor{blue}{In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
+We enrich the dataset with attribute information and design diverse experimental settings.
+We analyze the performance of these algorithms in depth.
+We find that these algorithms have different strengths and weaknesses under large-scale data, complex queries, and resource-constrained scenarios.
+Attribute filtering algorithms show clear limitations in flexibility and Boolean logic support.
+Range filtering algorithms show weaknesses in multi-attribute queries and high-recall performance.
+Sometimes, baseline methods like Faiss perform better in high-recall settings.
+In the future, we need to improve the flexibility and robustness of attribute filtering algorithms and enhance the performance of range filtering algorithms.}
+%	\textcolor{blue}{
+%		In this paper, we evaluate hybrid query methods, including algorithms, vector databases, and libraries.
 We design experiments to assess the performance of attribute filtering algorithms.
@@
 Our study validates previous research and provides insights for future work.
-	}
+%	}
+%
 

### 2025-05-01 VLDB2026/main.tex

--- 2025-05-01 VLDB2026/main.tex
@@
 Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
-	On low-dimensional datasets (Deep, YT-Audio), PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding (e.g., Base64).
+	On low-dimensional datasets (Deep, YT-Audio), PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
 

### 2025-05-01 VLDB2026/main.tex
Update main.tex

@@
 	For third-party \textcolor{red}{library} and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
-\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
+%\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
 Similar to the selectivity observed in attribute filtering.

### 2025-05-01 VLDB2026/main.tex
modify
Update main.tex

@@
 %	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
-	2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios,} 
+	2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios.} 
 %	\sout{neglecting the more complex demands of multi-attribute queries.
@@
 	\textcolor{red}{We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
-In addition, we survey 5 range filtering algorithms, and provide an overview of widely used 4 vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
+In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
 These efforts offer a unified reference framework for future research.}
@@
 	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
-The experimental results show that across all datasets (Deep, YT-Audio, and WIT) and query ranges, WinFilter consistently delivers the best performance.\textcolor{blue}{ This highlights the robustnes} , which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
+The experimental results show that across all datasets (Deep, YT-Audio, and WIT) and query ranges, WinFilter consistently delivers the best performance.
+\textcolor{blue}{This highlights its robustnes}, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
 
@@
 	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
-Unlike other range filtering algorithms,\textcolor{blue}{ ACORN is not designed with specialized data structures  to achieve efficient range filtering}.
+Unlike other range filtering algorithms, \textcolor{blue}{ ACORN is not designed with specialized data structures  to achieve efficient range filtering}.
 In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
@@
 PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
-	\textcolor{blue}{VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is very low.}ok
+	\textcolor{blue}{VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is quite  low.}
 

### 2025-05-01 VLDB2026/main.tex
change 4.2.2

@@
 The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
-\textcolor{red}{CAPS performs as well as Puck, but differs by further grouping results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
+CAPS performs as well as Puck.
+In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.

### 2025-05-01 VLDB2026/main.tex
Update main.tex

--- 2025-05-01 VLDB2026/main.tex
@@
 
-	We provide an overview and analysis of 15 hybrid query methods, all drawn from recent studies, and collectively referred to as algorithms in the following.
+	%We provide an overview and analysis of 15 hybrid query methods, all drawn from recent studies, and collectively referred to as algorithms in the following.
 Specifically, Section~3.1 describes methods for attribute filtering, Section~3.2 discusses those for range filtering, and Section~3.3 introduces vector libraries and databases that support both attribute filtering and range filtering.
@@
 
-	\subsubsection{Parameter Settings}
-
-	\textcolor{blue}{For all algorithms, we adopt recommended settings from the original study and adjust the parameters related to search in order to obtain different Recall and QPS.}
+	%\subsubsection{Parameter Settings}
+
+	%\textcolor{blue}{For all algorithms, we adopt recommended settings from the original study and adjust the parameters related to search in order to obtain different Recall and QPS.}
 

### 2025-05-01 VLDB2026/main.tex
Update main.tex

--- 2025-05-01 VLDB2026/main.tex
@@
 
-	Lastly, our findings show that the distribution and the \textcolor{blue}{ number} of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
+	Lastly, our findings show that the distribution and the number of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
 Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.
@@
 	\section{CONCLUSION}
-	\textcolor{blue}{In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
+	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
 We enrich the dataset with attribute information and design diverse experimental settings.
@@
 Sometimes, baseline methods like Faiss perform better in high-recall settings.
-In the future, we need to improve the flexibility and robustness of attribute filtering algorithms and enhance the performance of range filtering algorithms.}
+In the future, we need to improve the flexibility and robustness of attribute filtering algorithms and enhance the performance of range filtering algorithms.
 %	\textcolor{blue}{

### 2025-05-01 VLDB2026/main.tex
Update main.tex

--- 2025-05-01 VLDB2026/main.tex
@@
 In experiments, for attribute filtering, we construct standard attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
-For range filtering, we systematically evaluate performance across the 3 metrics through controlled variation of query ranges.
-Additionally, we conduct an in-depth analysis of the experimental results based on the underlying principles of the algorithms.
-The extensive experimental results reveal the strengths and weaknesses of each algorithm.
-Based on these findings, we develop a set of practical guidelines for algorithm selection, offering reliable references for different application scenarios.
+For range filtering, we also evaluate the algorithm performance across the 3 metrics through controlled variation of query ranges.
+Additionally, we conduct an in-depth analysis of the experimental results based on the underlying principles of algorithms.
+Extensive experimental results reveal the strengths and weaknesses of each algorithm.
+Based on the findings, we develop a set of practical guidelines for algorithm selection, offering reliable references for different application scenarios.
 Furthermore, we identify potential directions for improvement to address the current limitations of these algorithms.
@@
 	However, with the exponential growth of data volume and the increasing dimensionality of vectors \cite{weber1998quantitative}, traditional NN search methods struggle to meet the demands of real-time search.
-To address this issue, researchers turn to more efficient approaches - Approximate NN search ~\cite{arya1998optimal,beis1997shape,gionis1999similarity,malkov2018efficient}.
-ANN algorithms significantly improve search efficiency by constructing effective indexing structures, albeit at the cost of reduced accuracy.
+To address this issue, studies turn to more efficient approaches - Approximate NN (ANN) search ~\cite{arya1998optimal,beis1997shape,gionis1999similarity,malkov2018efficient}, which significantly improve search efficiency by constructing effective indexing structures, albeit at the cost of reduced accuracy.
 
 	Nevertheless, as application scenarios grow increasingly complex, simple ANN search can no longer satisfy all practical needs.
-For instance, Figure ~\ref{fig:hybrid ANNS} illustrates a case where users on e-commerce platforms search for clothing items by retrieving visually similar products based on an image.
+For instance, Fig.~\ref{fig:hybrid ANNS} illustrates a case where users on e-commerce platforms search for clothing items by retrieving visually similar products based on an image.
 Additionally, users may impose further requirements such as price, color, or brand preferences.
@@
 For instance, filtering clothes priced between 100 and 200.
-To meet these application demands, hybrid query \cite{JD-e-commerce, analyticdb} techniques emerge.
+To meet these application demands, hybrid querying \cite{JD-e-commerce, analyticdb} techniques emerge.
 Hybrid queries integrate vector retrieval with conditional filtering, optimizing their interaction to significantly enhance efficiency and flexibility in complex query scenarios.
@@
 The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
-CAPS performs as well as Puck.
-In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
+\textcolor{red}{CAPS performs as well as Puck, but differs by further grouping results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.
@@
 
-	Lastly, our findings show that the distribution and the number of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
+	Lastly, our findings show that the distribution and the \textcolor{blue}{ number} of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
 Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.
@@
 	\section{CONCLUSION}
-	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
+	\textcolor{blue}{In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
 We enrich the dataset with attribute information and design diverse experimental settings.
@@
 Sometimes, baseline methods like Faiss perform better in high-recall settings.
-In the future, we need to improve the flexibility and robustness of attribute filtering algorithms and enhance the performance of range filtering algorithms.
+In the future, we need to improve the flexibility and robustness of attribute filtering algorithms and enhance the performance of range filtering algorithms.}
 %	\textcolor{blue}{

### 2025-05-01 VLDB2026/main.tex
Update main.tex

--- 2025-05-01 VLDB2026/main.tex
@@
 
-	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015} , covering a diverse range of domains.
+	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.
 We independently generate attribute for each dataset.
@@
 Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets.
-	\textcolor{blue}{Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization. }
+	Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization.
 CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
@@
 
-	\textcolor{blue}{
 		In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement.
@@
 We suggest that future range filtering algorithms should include Faiss as a baseline.
-	}
 

### 2025-05-01 VLDB2026/main.tex
delete color

--- 2025-05-01 VLDB2026/main.tex
@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute filtering algorithms, factors such as \textcolor{blue}{the number of attributes}, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
+For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
 As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.
@@
 	%	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
-	2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios.} 
+	2) It focuses only on single-attribute and dual-attribute query scenarios. 
 	%	\sout{neglecting the more complex demands of multi-attribute queries.
@@
 
-	Moreover, \textcolor{blue}{beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.} To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
+	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
+To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
 Additionally, we further assess the robustness of each algorithm under varying conditions.
@@
 These efforts provide a unified reference framework for future study.
-	\textcolor{red}{We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
+	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
 In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
-These efforts offer a unified reference framework for future research.}
-
-	\textcolor{blue}{
+These efforts offer a unified reference framework for future research.
+
 		(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
@@
 These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
-	}
 
@@
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-	\textcolor{red}{We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.} By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
+	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
+By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
 We further examine their behavior under different attribute distributions and selectivity to assess robustness and adaptability in complex query scenarios.
@@
 	%We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} 
-	\textcolor{red}{We benchmark algorithms that support range filtering} on 3 large-scale datasets, using varying query range settings in the experiments.
-The experimental results \textcolor{blue}{show} the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-\textcolor{blue}{We further analyze the factors that affect the performance of the range query algorithm.}
+	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
+The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
+We further analyze the factors that affect the performance of the range query algorithm.
 
@@
 	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
-	\textcolor{red}{CAPS is the first simultaneous filtering algorithm based on spatial partitioning.}
+	CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
 	It introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
@@
 	%Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. ACORN addresses this by introducing a predicate-agnostic indexing framework.
-	\textcolor{red}{Pre-filtering methods apply attribute constraints prior to ANN search.
-As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.}
-	%Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
-	%, overcoming limitations of methods confined to small-scale equality filters. 
-	%It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
-	%During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
-	\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.
-During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
+	Pre-filtering methods apply attribute constraints prior to ANN search.
+As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.
+	Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.
+During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.
 	ACORN includes two indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, trading memory for higher performance; 
@@
 UNG is proposed to overcome these limitations.It is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.}
-	\textcolor{red}{Similar to ACORN, UNG adopts a pre-filtering strategy and serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.} It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
+	Similar to ACORN, UNG adopts a pre-filtering strategy and serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.
+It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
 Then, it constructs a Label Navigating Graph (LNG) to encode inclusion relationships among attribute sets.
@@
 In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
-	\textcolor{red}{Puck also adopts a pre-filtering strategy.
-}Developed by Baidu, Puck utilizes two-level quantization for indexing.
+	Puck also adopts a pre-filtering strategy.
+Developed by Baidu, Puck utilizes two-level quantization for indexing.
 It maintains an attribute set for each cluster to track vector attributes.
@@
 2) A dynamic segment graph is a neighbor graph where each edge is annotated with its valid attribute range.
-	With these structures, only few regions need updates when inserting new data. \textcolor{blue}{The system considers only edges valid for current attribute range to boost efficiency during search.}
+	With these structures, only few regions need updates when inserting new data. The system considers only edges valid for current attribute range to boost efficiency during search.
 
@@
 
-	\noindent\textbf{\underline{Faiss \cite{Faiss}.}} \textcolor{red}{Faiss is a library designed for efficient similarity search}.
+	\noindent\textbf{\underline{Faiss \cite{Faiss}.}} Faiss is a library designed for efficient similarity search.
 It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.
@@
 	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
-\textcolor{red}{We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality}.
+We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality.
 VBASE adopts a post-filtering strategy.
-However, it employs an iterative filtering mechanism: during index traversal, \textcolor{blue}{each node is checked} against the WHERE clause, and non-matching nodes are discarded.
+However, it employs an iterative filtering mechanism: during index traversal, each node is checked against the WHERE clause, and non-matching nodes are discarded.
 This avoids the issue in PASE where the final result set may contain fewer than $k$ results.
@@
 
-	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.
+	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015} , covering a diverse range of domains.
 We independently generate attribute for each dataset.
@@
 This ensures that the data is initially sorted.
-	\textcolor{red}{In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.}
+	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
 
@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				Text2Image & 200 & 10,000,000 &10,000 & 59& \textcolor{red}{Text,Image} \\
+				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
 
@@
 			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
-			\caption{\textcolor{blue}{Index size(include original dataset)}}
+			\caption{Index size (including original dataset)}
 			\label{fig:index_size_mb_comparison_query1}
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
-		\caption{\textcolor{red}{Time and space overhead of index construction}}
+		\caption{Time and space overhead of index construction}
 		\label{fig:build_index_comparison}
@@
 	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate 3 key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage.
-\textcolor{blue}{Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-}
+Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
 
@@
 
-	We next evaluate the query performance of AF-ANN search \textcolor{blue}{methods}, focusing on 3 main scenarios.
+	We next evaluate the query performance of AF-ANN search methods, focusing on 3 main scenarios.
 
@@
 	CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
-The vector distribution of the dataset affects the construction of its \textcolor{blue}{partitioned index.}
+The vector distribution of the dataset affects the construction of its partitioned index.
 	ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
@@
 	Faiss offers an ID filtering mechanism, it operates solely during query execution and does not influence index building.
-\textcolor{blue}{ACORN is   designed for} single-attribute indexing.
+ACORN is   designed for single-attribute indexing.
 In database systems (VBASE, PASE, Milvus),
 	%\sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.} 
-	\textcolor{red}{attributes do not participate in index construction.}
+	attributes do not participate in index construction.
 	Hence, they are excluded from this comparison.
@@
 	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
-	Compared to single-attribute filtering, multi-attribute joint filtering better reflects \textcolor{red}{real-world scenarios}.
-To evaluate algorithm performance \textcolor{red}{under this setting}, we construct the index using 3 uniformly distributed attributes and \textcolor{red}{apply filtering on all 3 attributes simultaneously during queries}.
+	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios.
+To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
 	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
@@
 For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies.
-Milvus, \textcolor{red}{as a general-purpose system}, exhibits comparatively poor performance.
-
-	{\color{red}
+Milvus, as a general-purpose system, exhibits comparatively poor performance.
+
 		The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance.
@@
 However, on large datasets, the overhead is amortized, and the advantages of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
-	}
 
@@
 The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
-	NHQ \textcolor{red}{performs moderately overall but poorly on small datasets}.
-Its reliance on fusion distance computations \textcolor{red}{makes it highly sensitive to the number of attributes}, impacting both efficiency and accuracy under multi-attribute filtering.
+	NHQ performs moderately overall but poorly on small datasets.
+Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
 
@@
 
-	\textit{\textbf{Attribute Distribution.}} \textcolor{blue}{To evaluate} performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
+	\textit{\textbf{Attribute Distribution.}} To evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
 We evaluate all algorithms under these distributions on each dataset.
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-Specifically, \textcolor{blue}{ACORN}, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
 
-	Among all algorithms, ACORN-\(\gamma\) \textcolor{blue}{shows} the highest robustness.
+	Among all algorithms, ACORN-\(\gamma\) shows the highest robustness.
 During index construction, attribute is mainly used for pruning in the lowest layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
@@
 
-	To investigate this effect, we evaluate 4 AS \textcolor{blue}{settings} (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset \textcolor{blue}{using single-thread execution.
-We} compare the query performance of attribute filtering algorithms \textcolor{blue}{across these settings}, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
-
-	Experimental results show that UNG achieves the best performance across all AS  \textcolor{blue}{settings}, especially at extremely low AS (1\%). 
+	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution.
+We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
+
+	Experimental results show that UNG achieves the best performance across all AS settings, especially at extremely low AS (1\%). 
 	This advantage stems from its pre-filtering strategy.
@@
 
-	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
+	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
 
@@
 As a result, its query performance remains largely unaffected by AS variations.
-ACORN-\(\gamma\) maintains stable performance across different AS \textcolor{blue}{settings} by using a higher index construction parameter $\gamma$.
+ACORN-\(\gamma\) maintains stable performance across different AS settings by using a higher index construction parameter $\gamma$.
 This ensures a relatively stable average node degree, even after attribute pruning, minimizing the impact of AS changes on query efficiency.
@@
 		%		\caption{Time and space overhead of range filtering index construction}
-		\caption{\textcolor{red}{Time and space overhead of index construction}}
+		\caption{Time and space overhead of index construction}
 		\label{fig:rangeFilter_build_index_comparison}
@@
 	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
-	\textcolor{blue}{Similarly}, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
+	Similarly, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
 
@@
 The experimental results show that across all datasets (Deep, YT-Audio, and WIT) and query ranges, WinFilter consistently delivers the best performance.
-\textcolor{blue}{This highlights its robustnes}, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
+This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
 
@@
 	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
-Unlike other range filtering algorithms, \textcolor{blue}{ ACORN is not designed with specialized data structures  to achieve efficient range filtering}.
+Unlike other range filtering algorithms, ACORN is not designed with specialized data structures  to achieve efficient range filtering.
 In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
 
-	For third-party \textcolor{red}{library} and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
+	For third-party library and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
 	%\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
@@
 With a smaller range, fewer points remain after filtering, resulting in lower computational cost.
-In addition, the performance of Faiss is influenced by data dimensionality; \textcolor{blue}{ the higher the dimensionality, the worse the performance.}
+In addition, the performance of Faiss is influenced by data dimensionality; the higher the dimensionality, the worse the performance.
 
@@
 PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
-	\textcolor{blue}{VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is quite  low.}
+	VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is quite  low.
 
@@
 
-	To evaluate the robustness of the RF-ANNS \textcolor{red}{algorithms} in different scenarios, we \textcolor{red}{ add an OOD dataset in the experiments}.
-As shown in Figure~\ref{fig:exp_8_3}, most methods \textcolor{red}{perform} worst on the Text2Image dataset.
+	To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
+As shown in Figure~\ref{fig:exp_8_3}, most methods perform worst on the Text2Image dataset.
 This is because OOD queries make the $k$-nearest neighbor distribution more sparse.
@@
 
-	WinFilter \textcolor{red}{shows} the worst performance on the WIT dataset.
+	WinFilter shows the worst performance on the WIT dataset.
 This suggests that its performance is sensitive to the data dimensionality.
-ACORN \textcolor{red}{has} large performance differences across datasets, indicating weak robustness.
-
-	Among vector databases, Milvus \textcolor{red}{performs} well.
+ACORN has large performance differences across datasets, indicating weak robustness.
+
+	Among vector databases, Milvus performs well.
 VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image.
-PASE \textcolor{red}{is} excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
-
-	It is worth noting that most methods \textcolor{red}{achieve} similar performance on the Deep and YT-Audio datasets, which have similar LID values.
+PASE is excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
+
+	It is worth noting that most methods achieve similar performance on the Deep and YT-Audio datasets, which have similar LID values.
 This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
@@
 
-	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm \textcolor{red}{shows} large performance differences between them.
+	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them.
 This means that DSG is more sensitive to changes in data distribution.

### 2025-05-01 VLDB2026/main.tex

@@
 These efforts provide a unified reference framework for future study.
-	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
+	\textcolor{red}{We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
 In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
-These efforts offer a unified reference framework for future research.
+These efforts offer a unified reference framework for future research.}
 
@@
 CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
-The vector distribution of the dataset affects the construction of its partitioned index.
+The vector distribution of the dataset affects the construction of its \textcolor{blue}{partitioned index.}
 	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.

### 2025-05-01 VLDB2026/main.tex
delete color

@@
 These efforts provide a unified reference framework for future study.
-	\textcolor{red}{We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
+	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
 In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
-These efforts offer a unified reference framework for future research.}
+These efforts offer a unified reference framework for future research.
 
@@
 CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
-The vector distribution of the dataset affects the construction of its \textcolor{blue}{partitioned index.}
+The vector distribution of the dataset affects the construction of its partitioned index.
 	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.

### 2025-05-01 VLDB2026/main.tex
Update main.tex

--- 2025-05-01 VLDB2026/main.tex
@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
+For attribute filtering algorithms, factors such as \textcolor{blue}{the number of attributes}, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
 As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.
@@
 %	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
-	2) It focuses only on single-attribute and dual-attribute query scenarios. 
+	2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios.} 
 %	\sout{neglecting the more complex demands of multi-attribute queries.
@@
 
-	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
+	Moreover, \textcolor{blue}{beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.} To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
 Additionally, we further assess the robustness of each algorithm under varying conditions.
@@
 These efforts provide a unified reference framework for future study.
-	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
+	\textcolor{red}{We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
 In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
-These efforts offer a unified reference framework for future research.
-
+These efforts offer a unified reference framework for future research.}
+
+	\textcolor{blue}{
 		(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
@@
 These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+	}
 
@@
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
-By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
+	\textcolor{red}{We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.} By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
 We further examine their behavior under different attribute distributions and selectivity to assess robustness and adaptability in complex query scenarios.
@@
 	%We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} 
-	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
-The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-We further analyze the factors that affect the performance of the range query algorithm.
+	\textcolor{red}{We benchmark algorithms that support range filtering} on 3 large-scale datasets, using varying query range settings in the experiments.
+The experimental results \textcolor{blue}{show} the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
+\textcolor{blue}{We further analyze the factors that affect the performance of the range query algorithm.}
 
@@
 	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
-	CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
+	\textcolor{red}{CAPS is the first simultaneous filtering algorithm based on spatial partitioning.}
 	It introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
@@
 	%Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. ACORN addresses this by introducing a predicate-agnostic indexing framework.
-	Pre-filtering methods apply attribute constraints prior to ANN search.
-As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.
-	Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.
-During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.
+	\textcolor{red}{Pre-filtering methods apply attribute constraints prior to ANN search.
+As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.}
+	%Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
+	%, overcoming limitations of methods confined to small-scale equality filters. 
+	%It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
+	%During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
+	\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.
+During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
 	ACORN includes two indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, trading memory for higher performance; 
@@
 UNG is proposed to overcome these limitations.It is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.}
-	Similar to ACORN, UNG adopts a pre-filtering strategy and serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.
-It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
+	\textcolor{red}{Similar to ACORN, UNG adopts a pre-filtering strategy and serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.} It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
 Then, it constructs a Label Navigating Graph (LNG) to encode inclusion relationships among attribute sets.
@@
 In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
-	Puck also adopts a pre-filtering strategy.
-Developed by Baidu, Puck utilizes two-level quantization for indexing.
+	\textcolor{red}{Puck also adopts a pre-filtering strategy.
+}Developed by Baidu, Puck utilizes two-level quantization for indexing.
 It maintains an attribute set for each cluster to track vector attributes.
@@
 2) A dynamic segment graph is a neighbor graph where each edge is annotated with its valid attribute range.
-	With these structures, only few regions need updates when inserting new data. The system considers only edges valid for current attribute range to boost efficiency during search.
+	With these structures, only few regions need updates when inserting new data. \textcolor{blue}{The system considers only edges valid for current attribute range to boost efficiency during search.}
 
@@
 
-	\noindent\textbf{\underline{Faiss \cite{Faiss}.}} Faiss is a library designed for efficient similarity search.
+	\noindent\textbf{\underline{Faiss \cite{Faiss}.}} \textcolor{red}{Faiss is a library designed for efficient similarity search}.
 It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.
@@
 	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
-We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality.
+\textcolor{red}{We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality}.
 VBASE adopts a post-filtering strategy.
-However, it employs an iterative filtering mechanism: during index traversal, each node is checked against the WHERE clause, and non-matching nodes are discarded.
+However, it employs an iterative filtering mechanism: during index traversal, \textcolor{blue}{each node is checked} against the WHERE clause, and non-matching nodes are discarded.
 This avoids the issue in PASE where the final result set may contain fewer than $k$ results.
@@
 This ensures that the data is initially sorted.
-	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
+	\textcolor{red}{In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.}
 
@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
+				Text2Image & 200 & 10,000,000 &10,000 & 59& \textcolor{red}{Text,Image} \\
 
@@
 			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
-			\caption{Index size (including original dataset)}
+			\caption{\textcolor{blue}{Index size(include original dataset)}}
 			\label{fig:index_size_mb_comparison_query1}
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
-		\caption{Time and space overhead of index construction}
+		\caption{\textcolor{red}{Time and space overhead of index construction}}
 		\label{fig:build_index_comparison}
@@
 	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate 3 key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage.
-Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
+\textcolor{blue}{Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
+}
 
@@
 
-	We next evaluate the query performance of AF-ANN search methods, focusing on 3 main scenarios.
+	We next evaluate the query performance of AF-ANN search \textcolor{blue}{methods}, focusing on 3 main scenarios.
 
@@
 Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets.
-	Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization. 
+	\textcolor{blue}{Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization. }
 	CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
-The vector distribution of the dataset affects the construction of its partitioned index.
+The vector distribution of the dataset affects the construction of its \textcolor{blue}{partitioned index.}
 	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
@@
 	Faiss offers an ID filtering mechanism, it operates solely during query execution and does not influence index building.
-ACORN is   designed for single-attribute indexing.
+\textcolor{blue}{ACORN is   designed for} single-attribute indexing.
 In database systems (VBASE, PASE, Milvus),
 	%\sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.} 
-	attributes do not participate in index construction.
+	\textcolor{red}{attributes do not participate in index construction.}
 	Hence, they are excluded from this comparison.
@@
 	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
-	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios.
-To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
+	Compared to single-attribute filtering, multi-attribute joint filtering better reflects \textcolor{red}{real-world scenarios}.
+To evaluate algorithm performance \textcolor{red}{under this setting}, we construct the index using 3 uniformly distributed attributes and \textcolor{red}{apply filtering on all 3 attributes simultaneously during queries}.
 %	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
@@
 For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies.
-Milvus, as a general-purpose system, exhibits comparatively poor performance.
-
+Milvus, \textcolor{red}{as a general-purpose system}, exhibits comparatively poor performance.
+
+	{\color{red}
 		The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance.
@@
 However, on large datasets, the overhead is amortized, and the advantages of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
+	}
 
@@
 The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
-	NHQ performs moderately overall but poorly on small datasets.
-Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
+	NHQ \textcolor{red}{performs moderately overall but poorly on small datasets}.
+Its reliance on fusion distance computations \textcolor{red}{makes it highly sensitive to the number of attributes}, impacting both efficiency and accuracy under multi-attribute filtering.
 
@@
 
-	\textit{\textbf{Attribute Distribution.}} To evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
+	\textit{\textbf{Attribute Distribution.}} \textcolor{blue}{To evaluate} performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
 We evaluate all algorithms under these distributions on each dataset.
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+Specifically, \textcolor{blue}{ACORN}, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
 
-	Among all algorithms, ACORN-\(\gamma\) shows the highest robustness.
+	Among all algorithms, ACORN-\(\gamma\) \textcolor{blue}{shows} the highest robustness.
 During index construction, attribute is mainly used for pruning in the lowest layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
@@
 
-	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution.
-We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
-
-	Experimental results show that UNG achieves the best performance across all AS settings, especially at extremely low AS (1\%). 
+	To investigate this effect, we evaluate 4 AS \textcolor{blue}{settings} (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset \textcolor{blue}{using single-thread execution.
+We} compare the query performance of attribute filtering algorithms \textcolor{blue}{across these settings}, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
+
+	Experimental results show that UNG achieves the best performance across all AS  \textcolor{blue}{settings}, especially at extremely low AS (1\%). 
 	This advantage stems from its pre-filtering strategy.
@@
 
-	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
+	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
 
@@
 As a result, its query performance remains largely unaffected by AS variations.
-ACORN-\(\gamma\) maintains stable performance across different AS settings by using a higher index construction parameter $\gamma$.
+ACORN-\(\gamma\) maintains stable performance across different AS \textcolor{blue}{settings} by using a higher index construction parameter $\gamma$.
 This ensures a relatively stable average node degree, even after attribute pruning, minimizing the impact of AS changes on query efficiency.
@@
 		%		\caption{Time and space overhead of range filtering index construction}
-		\caption{Time and space overhead of index construction}
+		\caption{\textcolor{red}{Time and space overhead of index construction}}
 		\label{fig:rangeFilter_build_index_comparison}
@@
 	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
-	Similarly, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
+	\textcolor{blue}{Similarly}, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
 
@@
 The experimental results show that across all datasets (Deep, YT-Audio, and WIT) and query ranges, WinFilter consistently delivers the best performance.
-This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
+\textcolor{blue}{This highlights its robustnes}, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
 
@@
 	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
-Unlike other range filtering algorithms, ACORN is not designed with specialized data structures  to achieve efficient range filtering.
+Unlike other range filtering algorithms, \textcolor{blue}{ ACORN is not designed with specialized data structures  to achieve efficient range filtering}.
 In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
 
-	For third-party library and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
+	For third-party \textcolor{red}{library} and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases.
 %\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
@@
 With a smaller range, fewer points remain after filtering, resulting in lower computational cost.
-In addition, the performance of Faiss is influenced by data dimensionality; the higher the dimensionality, the worse the performance.
+In addition, the performance of Faiss is influenced by data dimensionality; \textcolor{blue}{ the higher the dimensionality, the worse the performance.}
 
@@
 PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
-	VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is quite  low.
+	\textcolor{blue}{VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is quite  low.}
 
@@
 
-	To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
-As shown in Figure~\ref{fig:exp_8_3}, most methods perform worst on the Text2Image dataset.
+	To evaluate the robustness of the RF-ANNS \textcolor{red}{algorithms} in different scenarios, we \textcolor{red}{ add an OOD dataset in the experiments}.
+As shown in Figure~\ref{fig:exp_8_3}, most methods \textcolor{red}{perform} worst on the Text2Image dataset.
 This is because OOD queries make the $k$-nearest neighbor distribution more sparse.
@@
 
-	WinFilter shows the worst performance on the WIT dataset.
+	WinFilter \textcolor{red}{shows} the worst performance on the WIT dataset.
 This suggests that its performance is sensitive to the data dimensionality.
-ACORN has large performance differences across datasets, indicating weak robustness.
-
-	Among vector databases, Milvus performs well.
+ACORN \textcolor{red}{has} large performance differences across datasets, indicating weak robustness.
+
+	Among vector databases, Milvus \textcolor{red}{performs} well.
 VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image.
-PASE is excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
-
-	It is worth noting that most methods achieve similar performance on the Deep and YT-Audio datasets, which have similar LID values.
+PASE \textcolor{red}{is} excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
+
+	It is worth noting that most methods \textcolor{red}{achieve} similar performance on the Deep and YT-Audio datasets, which have similar LID values.
 This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
@@
 
-	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them.
+	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm \textcolor{red}{shows} large performance differences between them.
 This means that DSG is more sensitive to changes in data distribution.
@@
 
+	\textcolor{blue}{
 		In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement.
@@
 We suggest that future range filtering algorithms should include Faiss as a baseline.
+	}
 
@@
 	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
-We enrich the dataset with attribute information and design diverse experimental settings.
-We analyze the performance of these algorithms in depth.
-We find that these algorithms have different strengths and weaknesses under large-scale data, complex queries, and resource-constrained scenarios.
-Attribute filtering algorithms show clear limitations in flexibility and Boolean logic support.
-Range filtering algorithms show weaknesses in multi-attribute queries and high-recall performance.
-Sometimes, baseline methods like Faiss perform better in high-recall settings.
-In the future, we need to improve the flexibility and robustness of attribute filtering algorithms and enhance the performance of range filtering algorithms.
+We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm.
+Experiments show that these algorithms still have shortcomings in scenarios such as large-scale data, complex queries, and resource constraints.
+There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms.
+Additionally, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries.
+Notably, some algorithms even perform worse than the baseline method (e.g., Faiss) in high recall scenarios.
+In the future, it is essential to further explore the flexibility and robustness of attribute filtering algorithms, and improving the performance of range filtering algorithms remains an important direction.
 %	\textcolor{blue}{

### 2025-06-25 Revision/response.tex
Create response.tex

% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template

\documentclass[sigconf, nonacm]{acmart}

%% The following content must be adapted for the final version
% paper-specific
\newcommand\vldbdoi{XX.XX/XXX.XX}
\newcommand\vldbpages{XXX-XXX}
% issue-specific
\newcommand\vldbvolume{18}
\newcommand\vldbissue{1}
\newcommand\vldbyear{2025}
% should be fine as it is
\newcommand\vldbauthors{\authors}
\newcommand\vldbtitle{\shorttitle} 
% leave empty if no availability url should be set
%\newcommand\vldbavailabilityurl{https://github.com/Wangwenjing1996/Sirloin}
% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
\newcommand\vldbpagestyle{plain}

\usepackage{subfigure}
\usepackage[vlined,ruled,linesnumbered]{algorithm2e}
\def\cmtb{\textcolor{blue}}
\def\cmtr{\textcolor{red}}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{balance}
\usepackage{flushend}
\usepackage{mdframed}
\usepackage{tcolorbox}
\usepackage{fancybox}

\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

\newcommand{\E}{\mathrm{E}}
\newcommand{\Var}{\mathrm{Var}}

\newenvironment{summary}[1][]{\par\medskip
	\noindent\textbf{#1}
}{\medskip}

\newcounter{weakness}[section]
\setcounter{weakness}{0}
\renewcommand{\theweakness}{\arabic{weakness}}
\newenvironment{weakness}[1][]{\refstepcounter{weakness}\par\medskip
	\noindent\textbf{W\theweakness.#1} }{\medskip}

\newcounter{detailed}[section]
\setcounter{detailed}{0}
\renewcommand{\thedetailed}{\arabic{detailed}}
\newenvironment{detailed}[1][]{\refstepcounter{detailed}\par\medskip
	\noindent\textbf{D\thedetailed.#1} }{\medskip}

\newcounter{revision}[section]
\setcounter{revision}{0}
\renewcommand{\therevision}{\arabic{revision}}
\newenvironment{revision}[1][]{\refstepcounter{revision}\par\medskip
	\noindent\textbf{R\therevision.#1} }{\medskip}

\newcounter{metarevision}[section]
\setcounter{metarevision}{0}
\renewcommand{\themetarevision}{\arabic{metarevision}}
\newenvironment{metarevision}[1][]{\refstepcounter{metarevision}\par\medskip
	\noindent\textbf{R\themetarevision.#1} }{\medskip}

%\newcommand{\myfbox}[1]{%
%	\vspace{0.2cm}
%	\noindent
%	\fbox{\parbox{8.25cm}{#1}}
%	\vspace{0.15cm}
%}
\usepackage{xcolor}  % 确保引入了 xcolor 宏包

%\newcommand{\myfbox}[2][blue!5]{%
%	\vspace{0.2cm}
%	\noindent
%	\colorbox{#1}{\parbox{8.25cm}{#2}}%
%	\vspace{0.15cm}
%}

\newcommand{\myfbox}[1]{%
	\vspace{0.2cm}
	\noindent
	{\setlength{\fboxsep}{2.8pt}\setlength{\fboxrule}{0.4pt}%
		\fcolorbox{blue}{blue!6}{\parbox{8.25cm}{#1}}}%
	\vspace{0.15cm}
}

\begin{document}
%\title{Sirloin: Streaming Time Series Subsequence Anomaly Detection via Online Product Quantization}
\title{Response to Reviewer Comments:\\ ``
	An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)''\\
Submission to VLDB 2026 Research Track (ID )
}

\author{
	Jiaxu Zhu, Jiayu Yuan, Kaiwen Yang, Xiaobao Chen, Shihuan Yu, \\
	Hongchang Lv, Yan Li, Bolong Zheng
}

\maketitle
\pagestyle{plain}

\noindent
Dear meta-reviewer and reviewers:

Thank you for giving us the opportunity to revise our paper. We are deeply grateful for the reviewers' constructive feedback and the comprehensive suggestions provided in the meta-review. 
We believe that we have addressed all the major issues
and concerns, and the changes are highlighted \textcolor{blue}{in blue} according to the reviewers' comments.

\section*{Response To Meta-reviewer}

%%%%%%%%%%%%%%%%%%%% Summary %%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{summary}[Summary Comments.]
		\textit{The paper empirically studies performance of hybrid querying methods with respect to two types of queries: attribute filtering (AF) NN search, range filtering (RF) NN search. This is a timely problem with high practical relevance. Nevertheless, several improvements would benefit the paper. We therefore recommend a revision. The main revision points are summarized below, however, we expect that the authors do their best in addressing all points raised in the individual reviews.}
	\end{summary}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% R1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Improve the readability of some figures (e.g., performance under different attribute distributions or selectivity).}
	\end{metarevision}
}

\noindent
	\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run experiments with multi-modal queries (e.g., combining text and images) or more complex query types involving both attribute and range filters.}
	\end{metarevision}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% R4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Instead of using the point ID, run experiments with meaningful attributes for RF-NN search on datasets (Deep, YT-Audio, WIT).}
	\end{metarevision}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% R5 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Evaluate if the server setting affects the relative ordering of methods in experiments}
	\end{metarevision}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{In Table 1, please clarify which methods are disk-based, and which methods are memory-based.
			For disk-based methods, it is also meaningful to report the cost breakdown (e.g., in terms of I/O time and CPU time).}
	\end{metarevision}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% R7 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Report the peak memory usage of query processing.}
	\end{metarevision}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% R8 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run Scalability experiments with larger datasets.}
	\end{metarevision}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% R9 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Clearer insights and guidelines wrt the strength and weaknesses of the compared system.}
	\end{metarevision}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% R10 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Clearer guidelines in the Discussion to the extend of recommendations on which system/algo to use for what dataset characteristics.}
	\end{metarevision}
}

\noindent
\textbf{Response:}

\section*{Response to Review 1}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Although the authors justify the synthetic attribute generation, real-world applications may involve more complex attribute semantics and correlations, which might affect generalizability.}
	\end{weakness}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Some figures (e.g., performance under different attribute distributions or selectivity) are dense and could benefit from cleaner presentation or summarization to improve readability.}
	\end{weakness}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{It would strengthen the paper to delve into multi-modal queries (e.g., combining text and images) or more complex query types involving both attribute and range filters.}
	\end{weakness}
}

\noindent
\textbf{Response:}

\section*{Response to Review 2}
\setcounter{weakness}{0}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{In the experimental study, datasets did not originate from the real applications for hybrid queries.
			Regarding the datasets for AF-NN search (Msong, Audio, SIFT1M, GIST1M, GloVe, Enron),
			the attributes were generated synthetically but not real.
			Regarding the datasets for RF-NN search (Deep, YT-Audio, WIT), the data point ID was used as attribute;
			however, it is not meaningful to issue range query on data point ID.
			In order to match with the introduction, the authors are recommended to
			include a real dataset from e-commerce platform with both vectors and attributes.
		}
	\end{weakness}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{All experiments were conducted on the same server mentioned in Section 4.1.3.
			However, in practice, server providers may use other hardware settings (with other processors and RAM).
			Would the server setting affect the relative ordering of methods in experiments?
			For example, if Intel Xeon processor is used, would there be any change of the top 3 methods in Figures 4,5,7,8?
			Would the CPU cache size affect the top 3 methods in those figures?}
	\end{weakness}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{In the experimental setup, it is unclear whether data storage (disk or SSD) is used.
			In Table 1, please clarify which methods are disk-based, and which methods are memory-based.
			For disk-based methods, it is also meaningful to report the cost breakdown (e.g., in terms of I/O time and CPU time).}
	\end{weakness}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% W4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{The authors have reported the peak memory usage of index construction only.
			They are also recommended to report the peak memory usage of query processing.}
	\end{weakness}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{The authors have cited an experimental paper [49],
			but have not discussed about the main difference between their paper and [49].}
	\end{detailed}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{In Section 1.1, I could not find convincing references for the requirements in practical applications.
			[12] and [36] are research papers only, but not from real applications.}
	\end{detailed}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{In Definition 2.3, $ s_1 $ and $ s_n $ should be replaced with $ a_1 $ and $ a_n $ , respectively.}
	\end{detailed}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{ In Section 4.1, please clarify the URL of the implementation of each method.}
	\end{detailed}
}

\noindent
\textbf{Response:}

\section*{Response to Review 3}
\setcounter{weakness}{0}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Scalability experiments are missing; largest dataset is 10M; some pitfalls will only show at large scale.}
	\end{weakness}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{The explanations provided with the performance results are not as insightful as they need to be to point out the pros and cons of the different algorithms.}
	\end{weakness}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{I'd expect general, clearer guidelines in the Discussion to the extend of recommendations on which system/algo to use for what dataset characteristics. Hence, the comprehensive perspective on their strengths and weaknesses of the approaches is missing.}
	\end{weakness}
}

\noindent
\textbf{Response:}

\setcounter{detailed}{0}

%%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{Section 2.2. Graph based and IVF are well known. Missing in the index description is the implementation of attributes for AF and RF as the section is call hybrid ANN.}
	\end{detailed}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{Section 4.2.1: It is important to run the experiments on larger datasets, e.g. 100 M vectors, or 1B bigann. Otherwise, differences will not show.
			Also, build time parameters such as Radius and Length which impact the Recall need to be considered.
			Also, approaches for partitioning and merging for building very large indexes need to be considered.
			Please also document whether quantization is included in index build time.
			There is no explanation why Vamana is not included in Figure 7.}
	\end{detailed}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{The paper lists AF algos (table 1) and RF algos (table 2). It would be good to list the systems in a table with their algos and capabilities (AF, RF, Graph, IVF, ...). Would make it easier to follow the experimental comparison. E.g., Fig 12 does not include Vamana/DiskANN. Should I assume that RF is not possible with Vamana, or just not implemented?}
	\end{detailed}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{Section 4.3.
			It is not explained, what the Range attributes are, or how many attributes. I assume 1 attribute.
			The index construction times are vastly different in Fig 12 a. This calls for a much more detailed explanation.
			Also, Milvus seems to be missing in Fig 12 c. Why?
		}
	\end{detailed}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D5 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{Section 4.3.2: This is a very vague explanation. "SeRF exhibits relatively weak overall performance, with a significant drop in recall under small-range query scenarios. This suggests that while its compressed graph structure is space-efficient, it has a substantial negative impact on query performance." It would be important to be specific about what in the design/architecture of the SeRF graph is causing this behavior.
		}
	\end{detailed}
}

\noindent
\textbf{Response:}

\balance
%\bibliographystyle{ACM-Reference-Format}
%\bibliography{Ref}

\end{document}
%\endinput

### 2025-07-02 Revision/response.tex
1

@@
 \textbf{Response:} 
+Thank you for your suggestion!
+Currently, most hybrid query methods are based on memory, except for filteredDiskANN, which supports SSD, so we will add explanation information in the paper.
+At the same time, we also use real data sets to compare the difference in search performance between filteredDiskANN in memory and on SSD.
+The results are as follows:
 
@@
 \textbf{Response:} 
+Thank you for your suggestion.
+The paper [49] is a comprehensive survey and evaluation of graph structure approximate nearest neighbor search algorithms.
+Our paper extends this to a more complex "hybrid query" scenario and evaluates approximate search algorithms that combine vector similarity and attribute filtering/range filtering.
+Since hybrid queries are developed based on ANNs, we refer to the metrics and evaluation architectures of different methods proposed in this paper.
 
@@
 \textbf{Response:} 
+Thanks to the reviewer for suggesting that there is no explanation in Figure 7 why Vamana is not included.
+Figure 7 is an experiment on multi-label construction and search, and the Boolean logic of multi-label search is AND.
+The two algorithms using Vamana, FilteredVamana and StitchedVamana, only support Boolean logic OR for multi-label search, so we did not include them.
+We will add an explanation of this in the paper.
 

### 2025-07-03 Revision/response.tex
1

@@
 At the same time, we also use real data sets to compare the difference in search performance between filteredDiskANN in memory and on SSD.
-The results are as follows:
+The results are shown in Figure \ref{fig:recall-latency}:
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
+	\caption{}
+	\label{fig:recall-latency}
+\end{figure}
+
+ In response to your request for a breakdown of I/O and CPU cost in disk-based methods, we conducted additional experiments on the real-world yt8m dataset. We compared three variants of DiskANN:
+
+ \begin{itemize}
+ 	\item SSD-based FilteredDiskANN (original disk-based method)
+ 	\item FilteredVamana (memory-based method)
+ 	\item StitchedVamana (memory-based method)
+ \end{itemize}
+
+All experiments were run with 32 search threads for fair comparison.
+The following figure shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:
+
+\textbf{ Key Observations:}
+
+Latency-Recall Tradeoff:
+As expected, SSD-based FilteredDiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
+When Recall@10 reaches 0.96, its latency increases super-linearly to over 100 ms.
+
+Cost Breakdown of DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
+The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
+This clearly shows that improving disk read efficiency or reducing I/O volume is critical for performance optimization.
+
+\textbf{In-memory Methods:}
+
+FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
+While StitchedVamana achieves extremely low latency (sub-5 ms) due to its stitched multi-label index structure, its fixed edge connectivity may limit effectiveness under highly uncorrelated label distributions.
+Nevertheless, it consistently supports 90\%+ Recall@10 across diverse datasets, as shown in our evaluations.
 

### 2025-07-04 VLDB2026/main.tex
1

@@
 On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
-Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.
+\textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index.
+}Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.
 

### 2025-07-04 VLDB2026/main.tex
Update main.tex

@@
 
-		Let \( D = \{(v_1, s_1), \ldots, (v_n, s_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
+		Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
 Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).

### 2025-07-08 VLDB2026/main.tex
Update main.tex

@@
 
-	\noindent\textbf{\underline{NHQ \cite{NHQ}.}}  
+%	\noindent\textbf{\underline{NHQ \cite{NHQ}.}}  
+%	\footnote{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}
+	\noindent\textbf{\underline{NHQ} \footnote{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS} \cite{NHQ}}
 	Traditional attribute filtering algorithms usually perform attribute constraints and ANN search separately.
@@
 
-	\noindent\textbf{\underline{Filtered-DiskANN \cite{Filtered-diskann}.}}  
+	\noindent\textbf{\underline{Filtered-DiskANN} \footnote{https://github.com/microsoft/DiskANN} \cite{Filtered-diskann}}
 	%\sout{The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.}
@@
 
-	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} 
+	\noindent\textbf{\underline{CAPS} \footnote{https://github.com/gaurav16gupta/constrainedANN} \cite{CAPS}}
 	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
@@
 
-	\noindent\textbf{\underline{ACORN \cite{ACORN}.}}  
+	\noindent\textbf{\underline{ACORN} \footnote{https://github.com/stanford-futuredata/ACORN} \cite{ACORN}}
 	%	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
@@
 
-	\noindent\textbf{\underline{UNG \cite{UNG}.}} 
+	\noindent\textbf{\underline{UNG} \footnote{https://github.com/YZ-Cai/Unified-Navigating-Graph} \cite{UNG}} 
 	%\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
@@
 
-	\noindent\textbf{\underline{Puck \cite{puck}.}}  
+	\noindent\textbf{\underline{Puck} \footnote{https://github.com/baidu/puck} \cite{puck}} 
 	%While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
@@
 
-	\noindent\textbf{\underline{SeRF \cite{serf}.}} Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
+	\noindent\textbf{\underline{SeRF} \footnote{https://github.com/rutgers-db/SeRF} \cite{serf}} Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
 2) Filtering the dataset based on attribute ranges before performing ANN search.
@@
 
-	\noindent\textbf{\underline{WinFilter \cite{winFilter}.}}  
+	\noindent\textbf{\underline{WinFilter} \footnote{https://github.com/JoshEngels/RangeFilteredANN} \cite{winFilter}}
 	Unlike SeRF, which focuses on graph compression, WinFilter proposes a structural partitioning framework called the $\beta$-Window Search Tree ($\beta$-WST).
@@
 
-	\noindent\textbf{\underline{iRange \cite{iRangeGraph}.}}  
+	\noindent\textbf{\underline{iRange} \footnote{https://github.com/YuexuanXu7/iRangeGraph} \cite{iRangeGraph}}
 	To address the query efficiency degradation caused by the graph compression in SeRF, iRange adopts a more flexible strategy.
@@
 
-	\noindent\textbf{\underline{DSG \cite{DSG}.}}   
+	\noindent\textbf{\underline{DSG} \footnote{https://github.com/rutgers-db/DynamicSegmentGraph} \cite{DSG}}
 	Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets.
@@
 
-	\noindent\textbf{\underline{UNIFY \cite{UNIFY}.}}  
+	\noindent\textbf{\underline{UNIFY} \footnote{https://github.com/sjtu-dbgroup/UNIFY} \cite{UNIFY}}
 	Unlike DSG, which relies on rectangle trees and range-aware edges, UNIFY adopts a segmentation-based approach and proposes a range query index structure.
@@
 
-	\noindent\textbf{\underline{Faiss \cite{Faiss}.}} Faiss is a library designed for efficient similarity search.
+	\noindent\textbf{\underline{Faiss} \footnote{https://github.com/facebookresearch/faiss} \cite{Faiss}}
+	Faiss is a library designed for efficient similarity search.
 It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.
@@
 
-	\noindent\textbf{\underline{PASE \cite{pase}.}}  
+	\noindent\textbf{\underline{PASE} \footnote{https://github.com/alipay/PASE} \cite{pase}}
 	PASE is a vector indexing plugin for the PostgreSQL database \cite{postgresql13.4}, supporting two index types: IVF\_Flat \cite{johnson2019billion} and HNSW.
@@
 
-	\noindent\textbf{\underline{VBASE \cite{vbase}.}}  
+	\noindent\textbf{\underline{VBASE} \footnote{https://github.com/microsoft/MSVBASE} \cite{vbase}}
 	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
@@
 
-	\noindent\textbf{\underline{Milvus \cite{milvus}.}}  
+	\noindent\textbf{\underline{Milvus} \footnote{https://github.com/milvus-io/milvus} \cite{milvus}}
 	Unlike PASE and VBASE, which are database extensions, Milvus is an vector database purpose-built for large-scale similarity search.

### 2025-07-16 Revision/response.tex
add

@@
 % The ACM Latex guide provides further information about the ACM template
-
+%!TEX program = pdflatex
 \documentclass[sigconf, nonacm]{acmart}
@@
 \noindent
-\textbf{Response:}
+\textbf{Response:} We think this is an excellent suggestion.
+We have enhanced our experiments by incorporating more complex multimodal dataset evaluations in Section \textcolor{blue}{XXX} of the paper.
+Initially, our paper utilized the Text2Image dataset, which is commonly used in existing multimodal ANN algorithms.
+This dataset presents a modality gap, as the base vectors are images while the query set consists of text, often requiring algorithms to exhibit stronger robustness for good performance.
+To further enrich the evaluation of complex multimodal queries, we selected 500,000 text vectors and 500,000 image vectors from the Text2Image dataset to form a mixed base query dataset.
+Similarly, we chose 5,000 image vectors and 5,000 text vectors as query vectors, combining both text and image modalities.
+We then performed attribute filtering and range queries on this multimodal dataset to further analyze algorithm robustness.
+The relevant experimental results are presented and discussed in Section\textcolor{blue}{XXX}of our paper.
 
@@
 \noindent
-\textbf{Response:}
+\textbf{Response:} Thank you very much for your careful review and valuable suggestions. We greatly appreciate your feedback and sincerely apologize for any lack of clarity in our paper.
+
+Regarding the issue of range attributes, we indeed used only one range attribute for evaluation.
+At present, most existing range filtering algorithms only support filtering on a single attribute.
+This is a major limitation of current range filtering methods.
+We have clearly pointed this out in \textcolor{blue}{Section 5.2.2} of the "Discussion" part of the paper and listed it as an important challenge for future work.
+Thank you for highlighting this point, which further emphasizes the significance of our work.
+
+In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
+We added more detailed and in-depth analysis to provide a clearer explanation.
+
+Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c is very insightful.
+Initially, we hesitated to include the peak memory usage of databases (including Milvus) because they are full systems that run continuously and contain many components.
+This makes them quite different from other algorithms.
+
+However, we agree with your point.
+To provide a more comprehensive evaluation, we have added the peak memory usage data of the database systems (including Milvus) in the revised version of the paper.
+This offers a more complete comparative view.
+
+Once again, thank you for your constructive comments. Your valuable feedback has helped us improve the paper further.
 
@@
 \noindent
-\textbf{Response:}
+\textbf{Response:} Thank you for your feedback. We have revised \textcolor{blue}{Section 4.3.2 in our paper to provide a more specific and clearer explanation.}
+
+Specifically, SeRF compresses the entire HNSW graph collection by adding range information to the edges.
+While this approach saves space, it leads to significant performance degradation when executing small-range queries.
+This is because SeRF’s multi-filtering mechanism needs to inspect a large number of edge entries that are irrelevant to the current small-range query, thereby introducing fixed computational and memory access overhead.
+Additionally, during graph traversal, many invalid neighbors may be visited, causing the search to fall into local optima, which further degrades query performance and recall.
+
+We believe this explanation better clarifies the specific reasons why SeRF performs poorly in small-range query scenarios. Thank you again for your valuable suggestions.
 

### 2025-07-17 VLDB2026/main.tex
add
updata 2.2

@@
 	Current hybrid query methods mainly adopt graph-based ~\cite{nsw,kgraph,nsg,fanng,ngt} or Inverted File Index (IVF)-based \cite{PQ} index organization. 
-We briefly introduce the fundamental principles of these two types in the following.
+	%We briefly introduce the fundamental principles of these two types in the following.
+	\textcolor{violet}{Here, we briefly review the core concepts of these indexes and outline how attributes and range constraints are embedded to support hybrid query functionality.}
 
@@
 
+	\textcolor{violet}{Graph-based indexes are widely adopted in Hybrid ANN search algorithms due to their excellent performance.
+To support hybrid queries, existing approaches usually augment the original graph structures by explicitly associating attribute or range information with vertices or edges.
+In attribute filtering, a common approach is to attach attribute metadata to vertices or edges, allowing the traversal process to skip nodes or edges that do not meet the query's attribute conditions (e.g., NHQ, Filtered-DiskANN, ACORN).
+In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges satisfying the range constraints, effectively narrowing down the search space (e.g., SeRF, DSG).}
+
 	\noindent\textbf{\underline{IVF.}}  IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
@@
 	During the query process, given a query point $q$, the algorithm computes distances between $q$ and all centroids, selects a small number of the closest centroids ($C_0, C_1, C_2$), and then performs a search only within the associated clusters to identify the approximate nearest neighbors.
+
+	\textcolor{violet}{IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, such as naturally supporting pre-filtering and requiring significantly lower memory consumption and smaller index sizes compared to graph-based indexes.
+With minor modifications, IVF indexes achieve attribute and range filtering by directly excluding vectors that do not meet query constraints through pre-filtering, thus skipping irrelevant vectors during intra-cluster distance computations (e.g., Faiss, Milvus).
+Moreover, clusters can be further partitioned hierarchically based on attributes (hierarchical partitioning), resulting in finer-grained sub-partitions that significantly enhance the efficiency of attribute filtering (e.g., CAPS, PUCK).}
 
@@
 			\caption{Peak memory usage}
+			\label{fig:memory_mb_comparison_query1}
+		\end{subfigure}
+
+		\begin{subfigure}{\columnwidth}
+			\centering
+
+			\includegraphics[width=0.95\linewidth]{figures/searchMem/memory_comparison.pdf}
+			\caption{Search memory usage}
 			\label{fig:memory_mb_comparison_query1}

### 2025-07-17 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} 
+We sincerely apologize for the misuse of notation in Definition 2.3. This has been corrected in the revised version. Thank you for pointing it out.
 
@@
 \textbf{Response:} 
+Thank you for the suggestion!
+Since there are multiple methods, listing all URLs in Section 4.1 would be overwhelming.
+Instead, we have added the corresponding URLs in footnotes on the relevant pages throughout the paper.
 
@@
 We will add an explanation of this in the paper.
+
+All the evaluated algorithms in our experiments build the index in a one-shot manner, without applying any partitioning or merging strategies.
+Additionally, although some of the methods we used—such as FAISS, PUCK, DiskANN, and Milvus—support vector quantization during index construction, we did not enable quantization in any of our experiments.
+Therefore, the reported index build times do not include quantization.
 

### 2025-07-17 Revision/response.tex
update 2.2 revison

--- 2025-07-16 Revision/response.tex
@@
 \textbf{Response:}
+Thank you for your suggestion!
+We recognize that the original manuscript did not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard Graph-based and IVF-based index structures.
+
+To address this, we have revised Section 2.2 to summarize how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures (with detailed implementation provided in Section 3):
+
+For Graph-based indexes, we describe the typical approaches of embedding attribute and range constraints by associating metadata with graph vertices or edges.
+Specifically, attribute filtering (AF) is usually achieved by annotating vertices or edges with attribute information, enabling the traversal algorithm to skip nodes or edges that do not satisfy the query predicates (e.g., NHQ, Filtered-DiskANN, ACORN).
+In contrast, range filtering (RF) typically involves annotating edges with valid attribute intervals so that traversal proceeds only along edges that satisfy the query's range constraints, effectively reducing the search space (e.g., SeRF, DSG).
+
+For IVF-based indexes, we point out that their inherent pre-filtering mechanism naturally supports hybrid query functionality.
+In particular, attribute and range filtering can be implemented by directly excluding irrelevant vectors during intra-cluster distance computations.
+Furthermore, we highlight the hierarchical partitioning approach based on attributes, which further divides clusters into finer-grained sub-partitions, significantly improving filtering efficiency (e.g., CAPS, PUCK).
 

### 2025-07-17 VLDB2026/main.tex
update 2.2 revison
Update main.tex

@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+\textcolor{blue}{The closer the four curves (corresponding to the four distributions) in the figure approach each other, the less the algorithm is affected by attribute distributions.
+Conversely, the farther they diverge, the more significant the impact of attribute distributions on the algorithm becomes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.

### 2025-07-17 Revision/response.tex

@@
 
+All the evaluated algorithms in our experiments build the index in a one-shot manner, without applying any partitioning or merging strategies.
+Additionally, although some of the methods we used—such as FAISS, PUCK, DiskANN, and Milvus—support vector quantization during index construction, we did not enable quantization in any of our experiments.
+Therefore, the reported index build times do not include quantization.
+
 %%%%%%%%%%%%%%%%%%%%%% D3 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-17 plot/TrinityExtension_range.py
change figure

@@ -1,0 +1,692 @@
+import os
+import pandas as pd
+import numpy as np
+import glob
+import re
+import matplotlib.pyplot as plt
+from matplotlib.gridspec import GridSpec
+import matplotlib.font_manager as fm
+import warnings
+
+warnings.filterwarnings("ignore")
+
+# 定义数据路径
+data_path = "/data/rangefilter/result"  # 请修改为实际路径
+
+libertine_font = fm.FontProperties(
+    fname='/usr/share/fonts/opentype/linux-libertine/LinLibertine_R.otf')
+
+# 定义每个数据集的TOP3算法（针对范围过滤数据集）
+TOP3_ALGORITHMS = {
+    "text2image-mix": ["UNIFY", "SeRF", "ACORN-1"],
+    "YT-Audio-real85": ["UNIFY", "SeRF", "ACORN-γ"],
+    "deep100M": ["UNIFY", "SeRF", "ACORN-1"]
+}
+
+colors = [
+  # 主色系（高饱和度）
+  '#F39C12', # 亮橙（Vivid Orange）
+  '#2ECC71', # 翡翠绿（Jade Green）
+  '#FF6B6B', # 珊瑚红（Coral Red）
+  '#34495E', # 钢蓝灰（Steel Blue Gray）
+  
+  # 扩展色（高冲击力）
+  
+  '#A569BD', # 紫水晶（Amethyst Purple）
+  '#D35400', # 南瓜深橙（Pumpkin Orange）
+  '#48D1CC', # 土耳其蓝（Turquoise）
+  '#6EC1E0', # 电光冰蓝（Electric Ice Blue）
+  '#3498DB', # 荧光蓝（Fluorescent Blue）
+  
+  # 新增补充色（保持高对比）
+  '#1ABC9C', # 加勒比绿（Caribbean Green）
+  '#9B59B6', # 宝石紫（Gem Purple）
+
+  '#E74C3C', # 警报红（Alert Red）
+  
+  '#E91E63', # 霓虹粉（Neon Pink）
+  '#2C3E50', # 午夜蓝（Midnight Blue）
+  '#27AE60', # 翡翠深绿（Deep Emerald）
+]
+
+plot_params = {
+    'markersize': 6,                # 标记大小
+    'markerfacecolor': (1, 1, 1, 0.8),     # 标记填充颜色（白色）
+    'markeredgewidth': 1,         # 标记边缘宽度
+    'linewidth': 1.2           # 线条粗细
+}
+
+plot_legend_params = {
[…]

### 2025-07-17 plot/exp_3_1.py

@@ -1,0 +1,187 @@
+import numpy as np
+import pandas as pd
+
+def fit_curve(x, y, degree=2, plot=False):
+    x = np.array(x)
+    y = np.array(y)
+    mask = x > 0.8  # 规定recall大于0.8的点才参与拟合
+    x = x[mask]
+    y = y[mask]
+    degree = min(degree, len(x)-1)
+    # 用numpy的polyfit做多项式拟合，返回多项式系数（从高到低）
+    coeffs = np.polyfit(x, y, degree)
+    # 根据多项式系数构造一个多项式函数对象，可以像普通函数一样调用
+    fit_func = np.poly1d(coeffs)
+    return fit_func, coeffs
+
+def calculate_cv_for_files(files, algorithm_name):
+    """计算给定文件列表的CV均值"""
+    import os
+    
+    # 存储每个文件的拟合函数和处理后的数据范围
+    fit_functions = []
+    data_ranges = []
+    
+    print(f"处理算法: {algorithm_name}")
+    
+    # 对每个文件进行拟合
+    for i, file_path in enumerate(files):
+        if not os.path.exists(file_path):
+            print(f"  跳过文件 {i+1}: 文件不存在")
+            continue
+            
+        print(f"  处理文件 {i+1}: {file_path.split('/')[-1]}")
+        
+        # 读取数据
+        df = pd.read_csv(file_path)
+        if 'Recall' not in df.columns or 'QPS' not in df.columns:
+            print(f"    跳过: 缺少必要列")
+            continue
+            
+        x_original = df['Recall'].to_numpy()
+        y_original = df['QPS'].to_numpy()
+        
+        # 应用过滤条件（recall > 0.8）得到拟合用的数据
+        mask = x_original > 0.8
+        x_filtered = x_original[mask]
+        y_filtered = y_original[mask]
+        
+        if len(x_filtered) < 2:
+            print(f"    跳过: 过滤后数据点太少 ({len(x_filtered)})")
+            continue
+        
+        # 拟合曲线
+        fit_func, coeffs = fit_curve(x_original, y_original, degree=2)
+        fit_functions.append(fit_func)
+        
+        # 记录过滤后数据的范围
+        x_min, x_max = x_filtered.min(), x_filtered.max()
+        data_ranges.append((x_min, x_max))
+        print(f"    拟合完成，数据范围: [{x_min:.3f}, {x_max:.3f}]")
+    
+    if len(fit_functions) == 0:
+        print(f"  {algorithm_name}: 没有成功处理任何文件")
[…]

### 2025-07-17 VLDB2026/main.tex
update fig

--- 2025-07-17 VLDB2026/main.tex
@@
 
-	\subsection{Index Organization in Hybrid ANN Search}
+%	\subsection{Index Organization in Hybrid ANN Search}
+	\subsection{Index Organization in Hybrid Query}
 
@@
 		% 上面的图例，居中并可通过 hspace 调整左右位置
-		\hspace*{16pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-		\includegraphics[width=0.92\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径
+		\hspace*{10pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
+		\includegraphics[width=0.95\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径
 
@@
 			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
-			\caption{Index construction time}
+			\caption{Construction time}
 			\label{fig:build_time_comparison_query1}
@@
 			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
-			\caption{Peak memory usage}
-			\label{fig:memory_mb_comparison_query1}
+			\caption{Build peak memory }
+			\label{fig:search_memory_mb_comparison}
 		\end{subfigure}
@@
 
-			\includegraphics[width=0.95\linewidth]{figures/searchMem/memory_comparison.pdf}
-			\caption{Search memory usage}
-			\label{fig:memory_mb_comparison_query1}
+			\includegraphics[width=0.95\linewidth]{figures/searchMem/label_memory_comparison.pdf}
+			\caption{Search peak memory}
+			\label{fig:build_memory_mb_comparison}
 		\end{subfigure}
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
-		\caption{Time and space overhead of index construction}
+		\caption{\textcolor{violet}{Time and space overhead}}
 		\label{fig:build_index_comparison}
@@
 
-		\hspace*{11pt}
+		\hspace*{5pt}
 		% 放大的图例（占满单栏）
-		\includegraphics[width=0.90\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
+		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
 
@@
 		% 三图横排
-		\begin{subfigure}[t]{0.32\columnwidth}
+		\begin{subfigure}[t]{0.49\columnwidth}
 			\centering
 			\captionsetup{font=small}
-
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
@@
 		\hfill
-		\begin{subfigure}[t]{0.32\columnwidth}
-			\centering
-
+		\begin{subfigure}[t]{0.49\columnwidth}
+			\centering
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
@@
 		\hfill
-		\begin{subfigure}[t]{0.32\columnwidth}
-			\centering
-
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
-			\caption{\footnotesize Peak memory usage}
-			\label{fig:rangeFilter_memory_mb}
+		\begin{subfigure}[t]{0.49\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
+			\caption{\footnotesize Build peak memory}
+			\label{fig:rangeFilter_build_memory_mb}
 		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.49\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
+			\caption{\footnotesize Search peak memory}
+			\label{fig:rangeFilter_search_memory_mb}
+		\end{subfigure}
 
 		%		\caption{Time and space overhead of range filtering index construction}
-		\caption{Time and space overhead of index construction}
+%		\caption{Time and space overhead of index construction}
+		\caption{\textcolor{violet}{Time and space overhead}}
 		\label{fig:rangeFilter_build_index_comparison}

### 2025-07-17 Revision/response.tex
update

--- 2025-07-17 Revision/response.tex
@@
 \textbf{Response:}
-We sincerely apologize for the misuse of notation in Definition 2.3. This has been corrected in the revised version. Thank you for pointing it out.
 
@@
 \textbf{Response:}
-Thank you for the suggestion!
-Since there are multiple methods, listing all URLs in Section 4.1 would be overwhelming.
-Instead, we have added the corresponding URLs in footnotes on the relevant pages throughout the paper.
 
@@
 \textbf{Response:} 
-Thanks to the reviewer for suggesting that there is no explanation in Figure 7 why Vamana is not included.
+Thank you for your insightful comments!
+
+\textbf{Regarding dataset scale and scalability:}
+
+We have elaborated on the scalability implementations of various algorithms on the 100-million-scale Deep dataset in \textcolor{blue}{ Section XXX of our paper.
+We also provide a comprehensive analysis of their performance on large-scale datasets.}
+
+\textbf{Regarding the experimental parameter settings:}
+
+During index construction, for datasets where recommended parameters were explicitly provided in the original papers of the respective algorithms, we strictly adhered to those settings..
+For the remaining datasets, we used the default parameters provided in their open-source code repositories.
+All detailed configurations of experimental parameters are publicly available in our code repository.
+
+ Our experimental results show that on datasets where recommended parameters were used, the relative performance ranking of the algorithms did not change significantly.
+During the search phase, we obtained performance data at different Recall and QPS by adjusting the search parameters.
+These search parameters covered a wide range to ensure we could obtain comprehensive experimental result curves.
+
+ Given the large number of datasets and algorithms involved, to maintain the conciseness of the paper, we did not list the detailed running parameters for all algorithms and datasets in the main text.
+These specific parameters can all be found in our code repository.
+For algorithms that are sensitive to specific parameters, we have highlighted them in the relevant sections of the paper.
+
+\textbf{Regarding index partitioning and merging:}
+
+For partitioning and merging, only Filtered-DiskANN, which supports disk storage, builds indices separately and then merges them.
+However, the algorithms we focused on and evaluated in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction.
+Therefore, for the vast majority of algorithms, index partitioning and merging are not involved, which differs from DiskANN's design considerations.
+
+\textbf{Regarding quantization time in index build:}
+
+f all the evaluated algorithms, only Faiss supports quantization.
+However, in our experiments, we used the IVF index structure of Faiss without employing quantization.
+Therefore, no quantization time was included in the reported index build times.
+
+\textbf{Regarding Figure 7 and the exclusion of Vamana:}
+
+We appreciate the reviewer’s observation.
+Figure 7 presents experiments on multi-label construction and search, using Boolean AND logic.
+The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-label search, which is why they were not included.
+We will clarify this point in the revised version of the paper.
+%Thanks to the reviewer for suggesting that there is no explanation in Figure 7 why Vamana is not included.
 Figure 7 is an experiment on multi-label construction and search, and the Boolean logic of multi-label search is AND.
@@
 We will add an explanation of this in the paper.
-
-All the evaluated algorithms in our experiments build the index in a one-shot manner, without applying any partitioning or merging strategies.
-Additionally, although some of the methods we used—such as FAISS, PUCK, DiskANN, and Milvus—support vector quantization during index construction, we did not enable quantization in any of our experiments.
-Therefore, the reported index build times do not include quantization.
 

### 2025-07-17 VLDB2026/main.tex
update

--- 2025-07-17 VLDB2026/main.tex
@@
 	Current hybrid query methods mainly adopt graph-based ~\cite{nsw,kgraph,nsg,fanng,ngt} or Inverted File Index (IVF)-based \cite{PQ} index organization.
-	%We briefly introduce the fundamental principles of these two types in the following.
-	\textcolor{violet}{Here, we briefly review the core concepts of these indexes and outline how attributes and range constraints are embedded to support hybrid query functionality.}
+We briefly introduce the fundamental principles of these two types in the following.
 
@@
 
-	\textcolor{violet}{Graph-based indexes are widely adopted in Hybrid ANN search algorithms due to their excellent performance.
-To support hybrid queries, existing approaches usually augment the original graph structures by explicitly associating attribute or range information with vertices or edges.
-In attribute filtering, a common approach is to attach attribute metadata to vertices or edges, allowing the traversal process to skip nodes or edges that do not meet the query's attribute conditions (e.g., NHQ, Filtered-DiskANN, ACORN).
-In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges satisfying the range constraints, effectively narrowing down the search space (e.g., SeRF, DSG).}
-
 	\noindent\textbf{\underline{IVF.}}  IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
@@
 	During the query process, given a query point $q$, the algorithm computes distances between $q$ and all centroids, selects a small number of the closest centroids ($C_0, C_1, C_2$), and then performs a search only within the associated clusters to identify the approximate nearest neighbors.
-
-	\textcolor{violet}{IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, such as naturally supporting pre-filtering and requiring significantly lower memory consumption and smaller index sizes compared to graph-based indexes.
-With minor modifications, IVF indexes achieve attribute and range filtering by directly excluding vectors that do not meet query constraints through pre-filtering, thus skipping irrelevant vectors during intra-cluster distance computations (e.g., Faiss, Milvus).
-Moreover, clusters can be further partitioned hierarchically based on attributes (hierarchical partitioning), resulting in finer-grained sub-partitions that significantly enhance the efficiency of attribute filtering (e.g., CAPS, PUCK).}
 
@@
 
-		\begin{subfigure}{\columnwidth}
-			\centering
-
-			\includegraphics[width=0.95\linewidth]{figures/searchMem/memory_comparison.pdf}
-			\caption{Search memory usage}
-			\label{fig:memory_mb_comparison_query1}
-		\end{subfigure}
-
 		%		\caption{Time and space overhead of attribute filtering index construction}
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{blue}{The closer the four curves (corresponding to the four distributions) in the figure approach each other, the less the algorithm is affected by attribute distributions.
-Conversely, the farther they diverge, the more significant the impact of attribute distributions on the algorithm becomes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
@@
 
-	SeRF exhibits relatively weak overall performance, with a significant drop in recall under small-range query scenarios.
+%	SeRF exhibits relatively weak overall performance, with a significant drop in recall under small-range query scenarios.
 This suggests that while its compressed graph structure is space-efficient, it has a substantial negative impact on query performance.
+
+	\textcolor{blue}{SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
+This is because SeRF compresses the entire HNSW graph by attaching range information to its edges.
+However, during small-range queries, its multi-filtering mechanism requires scanning a large number of edge entries that are irrelevant to the current query range, introducing fixed computational and memory access overhead.
+Additionally, graph traversal may lead to the exploration of numerous invalid neighbors, increasing the likelihood of the search becoming trapped in local optima and further degrading performance.
+	}
 

### 2025-07-17 VLDB2026/main.tex
change

--- 2025-07-17 VLDB2026/main.tex
@@
 
+	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}
+
+	\begin{figure}[t]
+		\centering
+
+		\hspace*{5pt}
+		% 放大的图例（占满单栏）
+		\includegraphics[width=0.98\columnwidth]{figures/exp/attribute_legend.pdf}
+
+		%\vspace{0.1cm}
+		\begin{subfigure}[t]{0.332\columnwidth}
+			\centering
+			\captionsetup{font=small}
+			\includegraphics[width=\linewidth]{figures/exp/attribute_multimodel.pdf}
+			\caption{\footnotesize MultiModel}
+			\label{fig:rangeFilter_build_time}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.315\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/exp/attribute_85.pdf}
+			\caption{\footnotesize Different Computer}
+			\label{fig:rangeFilter_index_size_mb}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.315\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/exp/attribute_100M.pdf}
+			\caption{\footnotesize Big Dataset}
+			\label{fig:rangeFilter_build_memory_mb}
+		\end{subfigure}
+
+		\caption{\textcolor{violet}TrinityExtension——Attribution}
+		\label{fig:TrinityExtension——Attribution}
+	\end{figure}
+
 	\subsection{Range Filtering}
@@
 This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.
+	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
+
+	\begin{figure}[t]
+		\centering
+
+		\hspace*{5pt}
+		% 放大的图例（占满单栏）
+		\includegraphics[width=0.98\columnwidth]{figures/exp/range_legend.pdf}
+
+		%\vspace{0.1cm}
+		\begin{subfigure}[t]{0.332\columnwidth}
+			\centering
+			\captionsetup{font=small}
+			\includegraphics[width=\linewidth]{figures/exp/range_multimodel.pdf}
+			\caption{\footnotesize MultiModel}
+			\label{fig:MultiModel range}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.315\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
+			\caption{\footnotesize Different Computer}
+			\label{fig:Different Computer range}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.315\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
+			\caption{\footnotesize Big Dataset}
+			\label{fig:Big Dataset range}
+		\end{subfigure}
+
+		\caption{\textcolor{red}TrinityExtension——Range}
+		\label{fig:TrinityExtension——Range}
+	\end{figure}
 

### 2025-07-17 VLDB2026/main.tex
add
1

@@
 			\caption{Build peak memory }
-			\label{fig:search_memory_mb_comparison}
+			\label{fig:build_memory_mb_comparison}
 		\end{subfigure}
@@
 			\caption{Search peak memory}
-			\label{fig:build_memory_mb_comparison}
+			\label{fig:search_memory_mb_comparison}
 		\end{subfigure}
@@
 
-	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate 3 key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage.
+	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}.
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
@@
 	\textit{\textbf{Index construction time.}}
-	As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 4 datasets, PASE has the longest index construction time due to its single-thread indexing support.
-Additionally, VBASE also supports only single-thread indexing but achieves better query performance than PASE.
-
-	For algorithms supporting 32-thread, index construction time differences are negligible on small-scale datasets (Audio and Enron) due to their limited complexity.
-On large-scale datasets (SIFT1M, GIST1M, GloVe, and Msong), ACORN-1 achieves the fastest index construction.
+	As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 6 datasets, PASE has the longest index construction time due to its single-thread indexing support.
+Additionally, VBASE also supports only single-thread indexing but achieves better performance than PASE.
+
+	For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction.
 This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.
@@
 
-	\textit{\textbf{Peak memory usage.}}
-	As shown in Figure~\ref{fig:memory_mb_comparison_query1}, on small-scale datasets, all methods except NHQ exhibit low memory usage.
+	\textit{\textbf{Build peak memory.}}
+	As shown in Figure~\ref{fig:build_memory_mb_comparison}, on small-scale datasets, all methods except NHQ exhibit low memory usage. 
 	This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
@@
 \textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index.
-}Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.
+}.
+
+	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
 
@@
 
+	\subsubsection{Scalability Study}
+
+	\textit{\textbf{\textcolor{blue}{Different Hardware Environments}}}
+
+	\textit{\textbf{\textcolor{blue}{Large-scale Datasets}}}
+
+	\textit{\textbf{\textcolor{blue}{Complex Queries}}}
+
 	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}
@@
 This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.
+
+		\subsubsection{Scalability Study}
+
+	\textit{\textbf{\textcolor{blue}{Different Hardware Environments}}}
+
+	\textit{\textbf{\textcolor{blue}{Large-scale Datasets}}}
+
+	\textit{\textbf{\textcolor{blue}{Complex Queries}}}
+
 	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}

### 2025-07-17 VLDB2026/main.tex
1

@@
 	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
-	Similarly, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
+	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
+\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.
+	However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
 
@@
 
-	\textit{\textbf{Peak memory usage.}}
-	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
+	\textit{\textbf{Build peak memory.}}
+	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
 
@@
 	In contrast, Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.
+
+		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}
+
+		\textcolor{orange}{}
 

### 2025-07-17 VLDB2026/main.tex
change
1

@@
 			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
 			\caption{\footnotesize Build peak memory}
@@
 This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
-	In contrast, Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.
+	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
+	%Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.
 
@@
 
-		\textcolor{orange}{}
+		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, Faiss and Milvus have the lowest peak memory usage during search.
+Faiss reason: Milvus reason:.
+WinFilter achieves the highest peak memory usage on almost all datasets.
+The reason is:.
+For the high-dimensional dataset WIT, UNIFY occupies the highest peak memory.
+The reason is:.}
+
+		%Faiss和Milvus在搜索时的峰值内存最低，\textcolor{orange}{Faiss原因：Milvus原因：}。WinFilter在几乎所有数据集上取得最高的峰值内存，\textcolor{orange}{原因是：}。而对于高维数据集WIT，UNIFY占用最高的峰值内存，\textcolor{orange}{原因是：}。
 

### 2025-07-17 VLDB2026/main.tex
fig

@@
 This ensures that the data is initially sorted.
-	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
+
+%	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
+
+	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluate the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability.
+Notably, the previously discussed datasets primarily relied on synthetic attributes for experimentation.
+Therefore, we additionally incorporated two datasets containing real attributes for a more comprehensive evaluation:}
+
+	YT-Audio-Real dataset: We utilized the URLs provided by the YouTube8M dataset to crawl the corresponding video category IDs and view counts as their real attributes.
 
@@
 		% 第二行：两张子图，左侧宽度是右侧的两倍
-		\begin{subfigure}{0.64\textwidth} % 2/3 宽度
-			\centering
-
-			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_2.pdf}
+		\begin{subfigure}{0.627\textwidth} % 2/3 宽度
+			\centering
+
+			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_2.pdf}
 			\caption{Algorithms optimized for high AS.}
@@
 		\hspace{1mm} % 增加水平间距
-		\begin{subfigure}{0.32\textwidth} % 1/3 宽度
-			\centering
-
-			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_3.pdf}
+		\begin{subfigure}{0.33\textwidth} % 1/3 宽度
+			\centering
+
+			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_3.pdf}
 			\caption{Algorithms insensitive to AS.}

### 2025-07-17 VLDB2026/main.tex
1

--- 2025-07-17 VLDB2026/main.tex
@@
 	\textit{\textbf{Build peak memory.}}
-	As shown in Figure~\ref{fig:build_memory_mb_comparison}, on small-scale datasets, all methods except NHQ exhibit low memory usage. 
+	As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
+	%on small-scale datasets, all methods except NHQ exhibit low memory usage. 
+	\textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
 	This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
+
 	On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.

### 2025-07-17 VLDB2026/main.tex
fig

--- 2025-07-17 VLDB2026/main.tex
@@
 
-%	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
-
 	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluate the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability.
@@
 
-	YT-Audio-Real dataset: We utilized the URLs provided by the YouTube8M dataset to crawl the corresponding video category IDs and view counts as their real attributes.
+	\textcolor{violet}{YT-Audio-Real: We utilized the URLs provided by the YouTube8M dataset to crawl the corresponding video category IDs and view counts as their real attributes.}
+
+	\textcolor{violet}{WIT-Real: For this dataset, we encoded the page\_title field into vectors using the \texttt{clip-vit-base-patch32} model, and used the language type and the length of the context\_page\_description field as real attributes.}
+%	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
 
@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
+				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
-
+				Text2Image-Mix & 200 & 10,000,000 &10,000 & 59& Text,Image \\
 				\bottomrule

### 2025-07-17 VLDB2026/main.tex
1

--- 2025-07-17 VLDB2026/main.tex
@@
 	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
+	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
+Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower.}
 

### 2025-07-18 VLDB2026/main.tex
Update main.tex

--- 2025-07-17 VLDB2026/main.tex
@@
 
-	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluate the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability.
-Notably, the previously discussed datasets primarily relied on synthetic attributes for experimentation.
-Therefore, we additionally incorporated two datasets containing real attributes for a more comprehensive evaluation:}
-
-	\textcolor{violet}{YT-Audio-Real: We utilized the URLs provided by the YouTube8M dataset to crawl the corresponding video category IDs and view counts as their real attributes.}
-
-	\textcolor{violet}{WIT-Real: For this dataset, we encoded the page\_title field into vectors using the \texttt{clip-vit-base-patch32} model, and used the language type and the length of the context\_page\_description field as real attributes.}
+	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability.
+Specifically, the Text2Image dataset comprises two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
+
+	\textcolor{violet}{Given that the preceding datasets primarily utilized synthetic attributes, we additionally introduced two datasets containing real attributes for a more comprehensive evaluation: the YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we encoded the \texttt{page\_title} field into vectors using the \texttt{clip-vit-base-patch32} model, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.}
+
 %	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.

### 2025-07-18 Revision/response.tex

@@
 \noindent
-\textbf{Response:}
+\textbf{Response:} Thank you for your suggestion!
+In real-world applications, there may indeed exist more complex semantic correlations between vectors and their associated attributes or among different attributes themselves.
+To better reflect such scenarios, we introduced two real-world datasets, where both vectors and attributes are derived from actual data.
+For example, in the YouTube dataset, the attributes include video categories and view counts, while in the WIT dataset, the attributes correspond to the language of image descriptions.
+
+We conducted experiments on both datasets and analyzed the performance of various algorithms.
+Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.
+
+Regarding the more intricate semantic relationships—such as those between vectors and attributes, or among different attributes themselves—current hybrid search algorithms do not explicitly model or leverage such correlations.
+Nevertheless, our evaluation covers a range of realistic scenarios, including multi-attribute settings and diverse  distributions, to assess the generalization ability of the algorithms.
 

### 2025-07-18 VLDB2026/main.tex
1

@@
 
-		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, Faiss and Milvus have the lowest peak memory usage during search.
-Faiss reason: Milvus reason:.
+	%	\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, Faiss and Milvus have the lowest peak memory usage during search.
+Similar to attribute filtering, Faiss also has a smaller index size and no other additional memory usage, so the peak memory usage in range queries is slightly higher than the index size.
+Milvus reason:.
 WinFilter achieves the highest peak memory usage on almost all datasets.
@@
 
-		%Faiss和Milvus在搜索时的峰值内存最低，\textcolor{orange}{Faiss原因：Milvus原因：}。WinFilter在几乎所有数据集上取得最高的峰值内存，\textcolor{orange}{原因是：}。而对于高维数据集WIT，UNIFY占用最高的峰值内存，\textcolor{orange}{原因是：}。
+		\textcolor{orange}{As for the Search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the Build peak memory usage trend.
+The algorithm needs to load the complete index into memory during search.
+Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
+For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}
 

### 2025-07-18 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} 
-
+Thank you for your suggestion.
+We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
+The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-18 VLDB2026/main.tex

@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments}}} 
+	\textcolor{red}{We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
+		Compared to the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the methods are not significantly affected by differences in CPU configurations.
+		Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}
 

### 2025-07-18 VLDB2026/main.tex
Update main.tex

@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{blue}{The closer the four curves (corresponding to the four distributions) in the figure approach each other, the less the algorithm is affected by attribute distributions.
+\textcolor{cyan}{The closer the four curves (corresponding to the four distributions) in the figure approach each other, the less the algorithm is affected by attribute distributions.
 Conversely, the farther they diverge, the more significant the impact of attribute distributions on the algorithm becomes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
@@
 
-	\textit{\textbf{\textcolor{blue}{Different Hardware Environments}}} 
+	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
 	\textcolor{red}{We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
-		Compared to the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the methods are not significantly affected by differences in CPU configurations.
+Compared with the experimental results on the original server (as shown in Figure 4d), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}
 
-	\textit{\textbf{\textcolor{blue}{Large-scale Datasets}}}
-
-	\textit{\textbf{\textcolor{blue}{Complex Queries}}}
+	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}}
+
+	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
 
@@
 
-	\textit{\textbf{\textcolor{blue}{Different Hardware Environments}}}
-
-	\textit{\textbf{\textcolor{blue}{Large-scale Datasets}}}
-
-	\textit{\textbf{\textcolor{blue}{Complex Queries}}}
+	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
+	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on the same server configuration, with results presented in Figure~\ref{fig:Different Computer range}.
+When compared with the original server's experimental results shown in Figure~\ref{fig:exp_8_2}$e$, our findings remain consistent with those reported in Section 4.2.4.
+For brevity and due to space limitations, we omit further discussion of these redundant results.}
+%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}.
+Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4.
+Due to space constraints, these details are not reiterated here.}
+
+	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}}
+
+	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
 

### 2025-07-20 VLDB2026/main.tex
change

@@
 	In this experiment, we follow the query range definition adopted by prior work~\cite{HQI}.
-Specifically, for a given query, if the range covers $n/2^i$ data points—where $n$ is the total dataset size—we define the range ratio as $2^{-i}$.
-Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
+\textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.} Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
+\textcolor{red}{Some algorithms don't support using actual attributes as search keys, instead requiring an ID (the primary key, ranging from $0$ to $n-1$).
+Therefore, we uniformly use this ID as the search key.
+This ID is pre-sorted according to its corresponding real attribute, allowing us to map an attribute to its ID without loss of generality for efficient range queries.}
 
 	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
-The experimental results show that across all datasets (Deep, YT-Audio, and WIT) and query ranges, WinFilter consistently delivers the best performance.
+The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and WIT) and query ranges, WinFilter consistently delivers the best performance.
 This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
@@
 
-	To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
+	\sout{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
 As shown in Figure~\ref{fig:exp_8_3}, most methods perform worst on the Text2Image dataset.
@@
 This means that DSG is more sensitive to changes in data distribution.
+}
 	%	Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.

### 2025-07-21 Revision/response.tex
1

@@
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
+
 \myfbox{
@@
 \textbf{Response:} 
+Thank you for your suggestion.
+We are deeply aware of this deficiency, so we added the search peak memory usage of each algorithm in \textcolor{blue}{Section 4.2.1} of attribute filtering and \textcolor{blue}{Section 4.3.1}  of range filtering, and carefully analyzed the reasons.
 
@@
 We appreciate the reviewer’s observation.
-Figure 7 presents experiments on multi-label construction and search, using Boolean AND logic.
-The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-label search, which is why they were not included.
-We will clarify this point in the revised version of the paper.
+Figure 7 presents experiments on multi-attribute construction and search, using Boolean AND logic.
+The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
+We will clarify this point in the revised version of the paper, specifically in the section on \textcolor{blue}{Multi-Attribute Construction and Multi-Attribute Query}.
 %Thanks to the reviewer for suggesting that there is no explanation in Figure 7 why Vamana is not included.

### 2025-07-21 Revision/response.tex
add

--- 2025-07-18 Revision/response.tex
@@
 \noindent
-\textbf{Response:}
+\textbf{Response:} We believe this is a very good suggestion.
+Accordingly, we have added more complex multi-modal dataset experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4 in our revised paper.
+In the original version, we used the commonly adopted text2image dataset from existing multi-modal ANN algorithms, where the base vectors are images, but the queries are text.
+This setting naturally introduces a modality gap, and achieving good performance on this dataset usually requires algorithms to be more robust.
+
+To further enrich the complexity of multi-modal queries, we additionally selected 500,000 text vectors and 500,000 image vectors to form a mixed base dataset, and we similarly selected 5,000 text vectors and 5,000 image vectors as query vectors.
+We then conducted both attribute filtering and range queries on this multi-modal dataset by combining text and image queries.
+This allows us to further analyze the robustness of the algorithms.
+The related experimental results are presented in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
+
+As for complex query types involving both attribute and range filters, to the best of our knowledge, there is currently no ANN algorithm (except for general-purpose systems like Milvus and Faiss) that can support both types of filtering simultaneously.
+For example, ACORN needs to build separate indices for each scenario and cannot support attribute and range filtering at the same time.
+Therefore, in our study, we chose to consider these query types separately, rather than jointly.
 
@@
 \noindent
-\textbf{Response:} Thank you for your suggestion!
-In real-world applications, there may indeed exist more complex semantic correlations between vectors and their associated attributes or among different attributes themselves.
-To better reflect such scenarios, we introduced two real-world datasets, where both vectors and attributes are derived from actual data.
-For example, in the YouTube dataset, the attributes include video categories and view counts, while in the WIT dataset, the attributes correspond to the language of image descriptions.
-
-We conducted experiments on both datasets and analyzed the performance of various algorithms.
-Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.
-
-Regarding the more intricate semantic relationships—such as those between vectors and attributes, or among different attributes themselves—current hybrid search algorithms do not explicitly model or leverage such correlations.
-Nevertheless, our evaluation covers a range of realistic scenarios, including multi-attribute settings and diverse  distributions, to assess the generalization ability of the algorithms.
+\textbf{Response:}
 

### 2025-07-21 VLDB2026/main.tex
Update main.tex
1
add

--- 2025-07-18 VLDB2026/main.tex
@@
 This ensures that the data is initially sorted.
-
-	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability.
-Specifically, the Text2Image dataset comprises two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
-
-	\textcolor{violet}{Given that the preceding datasets primarily utilized synthetic attributes, we additionally introduced two datasets containing real attributes for a more comprehensive evaluation: the YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we encoded the \texttt{page\_title} field into vectors using the \texttt{clip-vit-base-patch32} model, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.}
-
-%	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
+	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
 
@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
-				Text2Image-Mix & 200 & 10,000,000 &10,000 & 59& Text,Image \\
+
 				\bottomrule
@@
 			\caption{Build peak memory }
-			\label{fig:build_memory_mb_comparison}
+			\label{fig:search_memory_mb_comparison}
 		\end{subfigure}
@@
 			\caption{Search peak memory}
-			\label{fig:search_memory_mb_comparison}
+			\label{fig:build_memory_mb_comparison}
 		\end{subfigure}
@@
 
-	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}.
+	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate 3 key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage.
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
@@
 	\textit{\textbf{Index construction time.}}
-	As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 6 datasets, PASE has the longest index construction time due to its single-thread indexing support.
-Additionally, VBASE also supports only single-thread indexing but achieves better performance than PASE.
-
-	For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction.
+	As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 4 datasets, PASE has the longest index construction time due to its single-thread indexing support.
+Additionally, VBASE also supports only single-thread indexing but achieves better query performance than PASE.
+
+	For algorithms supporting 32-thread, index construction time differences are negligible on small-scale datasets (Audio and Enron) due to their limited complexity.
+On large-scale datasets (SIFT1M, GIST1M, GloVe, and Msong), ACORN-1 achieves the fastest index construction.
 This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.
@@
 
-	\textit{\textbf{Build peak memory.}}
-	As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
-	%on small-scale datasets, all methods except NHQ exhibit low memory usage. 
-	\textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
+	\textit{\textbf{Peak memory usage.}}
+	As shown in Figure~\ref{fig:memory_mb_comparison_query1}, on small-scale datasets, all methods except NHQ exhibit low memory usage.
 This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
-
 On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
 \textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index.
-}.
-
-	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
-	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower.}
+}Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.
 
@@
 		% 第二行：两张子图，左侧宽度是右侧的两倍
-		\begin{subfigure}{0.627\textwidth} % 2/3 宽度
-			\centering
-
-			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_2.pdf}
+		\begin{subfigure}{0.64\textwidth} % 2/3 宽度
+			\centering
+
+			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_2.pdf}
 			\caption{Algorithms optimized for high AS.}
@@
 		\hspace{1mm} % 增加水平间距
-		\begin{subfigure}{0.33\textwidth} % 1/3 宽度
-			\centering
-
-			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_3.pdf}
+		\begin{subfigure}{0.32\textwidth} % 1/3 宽度
+			\centering
+
+			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_3.pdf}
 			\caption{Algorithms insensitive to AS.}
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments}}}
-	\textcolor{red}{We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
-		Compared to the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the methods are not significantly affected by differences in CPU configurations.
-		Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}
 
@@
 
-	\textit{\textbf{\textcolor{blue}{Complex Queries}}}
+	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
+
+	\textcolor{blue}{
+	We conducted experiments on the text2image-mix dataset.
+This dataset contains both image and text vectors.
+It is a more complex multimodal dataset.
+As shown in Figure~\ref{fig:TrinityExtension——Attribution}, although the queries are more complex, UNG and NHQ still perform the best.
+CAPS is the next best.
+	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
+The nearest neighbors in the index are often from the same modality because they are closer in distance.
+Therefore, the search results on this dataset are similar to those in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
+UNG and NHQ perform the best.
+CAPS clusters based on vector similarity.
+It actually clusters the vectors into the same modality.
+Then it uses attribute filtering to divide the data further.
+This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
+	In contrast, the text2image dataset shown in Figure~\ref{fig:exp_6_1} is different.
+The queries and the dataset are from different modalities.
+The queries are far from the dataset.
+The ground truths are also scattered and not clustered together.
+To find the ground truths, the algorithm often needs to traverse more points.
+This is a greater challenge for the algorithms.
+%	We conducted extensive scalability experiments on the Text2Image-Mix dataset.
+This dataset contains both image and text vectors.
+It represents a more complex multimodal query scenario.
+As shown in Figure 12, the UNG and NHQ algorithms still achieve the best performance, followed closely by CAPS.
+%	In the Text2Image-Mix dataset, the ground truth of the query vector is usually the corresponding vector in the same modality.
+Since the neighbor relationships in the graph are often based on vector distance, vectors of similar modalities naturally form closer connections in the graph.
+Therefore, during the search process, the algorithm tends to traverse efficiently within the same modality.
+This makes the search mechanism similar to our experiments on single-modality datasets, thus maintaining high performance.
+%	The good performance of the CAPS algorithm is due to its unique hierarchical space partitioning strategy.
+It first clusters vectors based on similarity.
+In multimodal data, this clustering naturally groups vectors of similar modalities into the same cluster.
+Then, CAPS further partitions these clusters using attributes.
+This allows it to quickly find the nearest neighbors that meet the filtering conditions.
+%	It is worth noting that, compared to the OOD dataset discussed in the "Dataset Impact" section, the Text2Image-Mix dataset also involves modality differences.
+However, its complexity lies in modality mixing.
+The OOD dataset, on the other hand, has a modality gap.
+This often requires traversing a broader and more sparse search space to find the ground truth.
+It poses a more severe challenge to the algorithm.
+}
 
@@
 			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
 			\caption{\footnotesize Build peak memory}
@@
 	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
-	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.
-	However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
+	Similarly, we also evaluate 3 key metrics mentioned above in \textit{Range Filtering} algorithms.
 
@@
 
-	\textit{\textbf{Build peak memory.}}
-	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
+	\textit{\textbf{Peak memory usage.}}
+	As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
 
@@
 This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
-	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
-	%Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.
-
-		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}
-
-	%	\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, Faiss and Milvus have the lowest peak memory usage during search.
-Similar to attribute filtering, Faiss also has a smaller index size and no other additional memory usage, so the peak memory usage in range queries is slightly higher than the index size.
-Milvus reason:.
-WinFilter achieves the highest peak memory usage on almost all datasets.
-The reason is:.
-For the high-dimensional dataset WIT, UNIFY occupies the highest peak memory.
-The reason is:.}
-
-		\textcolor{orange}{As for the Search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the Build peak memory usage trend.
-The algorithm needs to load the complete index into memory during search.
-Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
-For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}
+	In contrast, Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.
 
@@
 
-	\textit{\textbf{\textcolor{blue}{Complex Queries}}}
+	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
+	\textcolor{blue}{
+	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModel range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets.}
 

### 2025-07-21 VLDB2026/main.tex

--- 2025-07-20 VLDB2026/main.tex
@@
 To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
+\textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
+Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
 	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
@@
 
+%ykw: 这段话看着有问题
 	As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.
@@
 
-	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
+	\textit{\textbf{\textcolor{blue}{Large-scale Datasets}}}
+
+	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
+
+	\textcolor{blue}{
+	We conducted experiments on the text2image-mix dataset.
+This dataset contains both image and text vectors.
+It is a more complex multimodal dataset.
+As shown in Figure~\ref{fig:TrinityExtension——Attribution}, although the queries are more complex, UNG and NHQ still perform the best.
+CAPS is the next best.
+	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
+The nearest neighbors in the index are often from the same modality because they are closer in distance.
+Therefore, the search results on this dataset are similar to those in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
+UNG and NHQ perform the best.
+CAPS clusters based on vector similarity.
+It actually clusters the vectors into the same modality.
+Then it uses attribute filtering to divide the data further.
+This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
+	In contrast, the text2image dataset shown in Figure~\ref{fig:exp_6_1} is different.
+The queries and the dataset are from different modalities.
+The queries are far from the dataset.
+The ground truths are also scattered and not clustered together.
+To find the ground truths, the algorithm often needs to traverse more points.
+This is a greater challenge for the algorithms.
+%	We conducted extensive scalability experiments on the Text2Image-Mix dataset.
+This dataset contains both image and text vectors.
+It represents a more complex multimodal query scenario.
+As shown in Figure 12, the UNG and NHQ algorithms still achieve the best performance, followed closely by CAPS.
+%	In the Text2Image-Mix dataset, the ground truth of the query vector is usually the corresponding vector in the same modality.
+Since the neighbor relationships in the graph are often based on vector distance, vectors of similar modalities naturally form closer connections in the graph.
+Therefore, during the search process, the algorithm tends to traverse efficiently within the same modality.
+This makes the search mechanism similar to our experiments on single-modality datasets, thus maintaining high performance.
+%	The good performance of the CAPS algorithm is due to its unique hierarchical space partitioning strategy.
+It first clusters vectors based on similarity.
+In multimodal data, this clustering naturally groups vectors of similar modalities into the same cluster.
+Then, CAPS further partitions these clusters using attributes.
+This allows it to quickly find the nearest neighbors that meet the filtering conditions.
+%	It is worth noting that, compared to the OOD dataset discussed in the "Dataset Impact" section, the Text2Image-Mix dataset also involves modality differences.
+However, its complexity lies in modality mixing.
+The OOD dataset, on the other hand, has a modality gap.
+This often requires traversing a broader and more sparse search space to find the ground truth.
+It poses a more severe challenge to the algorithm.
+}
 
@@
 
-	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
+	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
+	\textcolor{blue}{
+	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModel range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets.}
 

### 2025-07-21 VLDB2026/main.tex
up

--- 2025-07-20 VLDB2026/main.tex
@@
 We independently generate attribute for each dataset.
-	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
+	\textcolor{violet}{	For range filtering queries, we evaluate 1 widely used real-world datasets: WIT~\cite{wit_dataset}.
 Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
-This ensures that the data is initially sorted.
+This ensures that the data is initially sorted.}
 
@@
 	\textit{Single-Thread Search.}  
-	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under full-recall conditions (recall = 1), search often requires traversing larger candidate sets or deeper graph paths, leading to increased computational cost and a sharp QPS drop for most methods.
+	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths.
+This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods.
+Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
+\textcolor{violet}{Puck and CAPS perform relatively well on some datasets.
+Partition-based methods have limitations regarding different vector data distributions, and how to configure different partitions for different datasets remains a challenge.
+However, this also demonstrates that IVF-based methods are still very promising for hybrid queries.}
+
+	NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets.
+This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.
+As observed in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, StitchedVamana outperforms FilteredVamana in query efficiency.
+This difference arises from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
+
+	\textcolor{violet}{ACORN generally performs poorly, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
+Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.}
+
+	Among all methods, vector database systems (PASE, VBASE, Milvus) exhibit the worst performance.
+These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
+Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
+
+	\textit{Multi-Thread Search.}
+	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, \textcolor{violet}{the performance distribution of algorithms remains largely unchanged except for Puck, with UNG continuing to maintain the best performance.
+Puck shows significant performance improvement under multi-threading.}
+
+%	\textit{Single-Thread Search.}  
+%	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under full-recall conditions (recall = 1), search often requires traversing larger candidate sets or deeper graph paths, leading to increased computational cost and a sharp QPS drop for most methods.
 Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
@@
 CAPS leverages multi-level spatial partitioning and attribute filtering to efficiently explore sparse spaces, whereas UNG relies on structured attribute organization, which limits its adaptability to sparse high-dimensional distributions.
-
-	NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets.
+%	
+%	NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets.
 This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.
@@
 The difference arises from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
-
-	Among all methods, vector database systems (PASE, VBASE, Milvus) perform the worst.
+%	
+%	Among all methods, vector database systems (PASE, VBASE, Milvus) perform the worst.
 These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
 Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
-
-	\textit{Multi-Thread Search.}
-	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance. 
-	%Puck performs well on large-scale datasets, but its performance degrades on small datasets.
+%	
+%	\textit{Multi-Thread Search.}
+%	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance. 
+%	%Puck performs well on large-scale datasets, but its performance degrades on small datasets.
 Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets.
-	Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization.
+%	Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization.
 CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
 The vector distribution of the dataset affects the construction of its partitioned index.
-	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
+%	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
 Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.

### 2025-07-21 Revision/response.tex
1

--- 2025-07-21 Revision/response.tex
@@
 
+\textit{\textbf{ \textcolor{blue}{Section 4.2.1 Search peak memory.}}}
+
+\textcolor{blue}{As shown in Figure, we can find that the peak memory usage of each algorithm during search does not differ significantly.
+Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower.}
+
+\textit{\textbf{ \textcolor{blue}{Section 4.3.1 Search peak memory.}}}
+
+	\textcolor{blue}{As for the Search peak memory usage, we can find from the Figure that it is basically consistent with the Build peak memory usage trend.
+The algorithm needs to load the complete index into memory during search.
+Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
+For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}
+
 %%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:} 
-Thank you for your suggestion.
+Thank you for your suggestion!
 The paper [49] is a comprehensive survey and evaluation of graph structure approximate nearest neighbor search algorithms.
@@
 \textbf{Response:} 
+Thank you for your suggestion!
+We have carefully searched and found no papers describing the application of attribute distribution and attribute selectivity.
+However, the real-world application scenarios of attribute distribution and attribute selectivity are indeed very extensive.
+For attribute distribution, the label attributes of many recommended application scenarios in reality conform to the power-law distribution.
+For attribute selectivity: For example, if you need to query data in which an attribute accounts for a very small proportion of the total, choosing a more advantageous algorithm will greatly improve the search effect.
+There are also databases with actual applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
+For the two parts you suggested, we will add more comprehensive citations in the paper.
 

### 2025-07-21 VLDB2026/main.tex
1

--- 2025-07-21 VLDB2026/main.tex
@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
+For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute  selectivity \textcolor{orange}{\cite{analyticdb,milvus}} significantly impact algorithm performance.
 As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.
@@
 
-	\textit{\textbf{\textcolor{blue}{Large-scale Datasets}}}
-
-	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
-
-	\textcolor{blue}{
-	We conducted experiments on the text2image-mix dataset.
-This dataset contains both image and text vectors.
-It is a more complex multimodal dataset.
-As shown in Figure~\ref{fig:TrinityExtension——Attribution}, although the queries are more complex, UNG and NHQ still perform the best.
-CAPS is the next best.
-	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
-The nearest neighbors in the index are often from the same modality because they are closer in distance.
-Therefore, the search results on this dataset are similar to those in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
-UNG and NHQ perform the best.
-CAPS clusters based on vector similarity.
-It actually clusters the vectors into the same modality.
-Then it uses attribute filtering to divide the data further.
-This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
-	In contrast, the text2image dataset shown in Figure~\ref{fig:exp_6_1} is different.
-The queries and the dataset are from different modalities.
-The queries are far from the dataset.
-The ground truths are also scattered and not clustered together.
-To find the ground truths, the algorithm often needs to traverse more points.
-This is a greater challenge for the algorithms.
-%	We conducted extensive scalability experiments on the Text2Image-Mix dataset.
-This dataset contains both image and text vectors.
-It represents a more complex multimodal query scenario.
-As shown in Figure 12, the UNG and NHQ algorithms still achieve the best performance, followed closely by CAPS.
-%	In the Text2Image-Mix dataset, the ground truth of the query vector is usually the corresponding vector in the same modality.
-Since the neighbor relationships in the graph are often based on vector distance, vectors of similar modalities naturally form closer connections in the graph.
-Therefore, during the search process, the algorithm tends to traverse efficiently within the same modality.
-This makes the search mechanism similar to our experiments on single-modality datasets, thus maintaining high performance.
-%	The good performance of the CAPS algorithm is due to its unique hierarchical space partitioning strategy.
-It first clusters vectors based on similarity.
-In multimodal data, this clustering naturally groups vectors of similar modalities into the same cluster.
-Then, CAPS further partitions these clusters using attributes.
-This allows it to quickly find the nearest neighbors that meet the filtering conditions.
-%	It is worth noting that, compared to the OOD dataset discussed in the "Dataset Impact" section, the Text2Image-Mix dataset also involves modality differences.
-However, its complexity lies in modality mixing.
-The OOD dataset, on the other hand, has a modality gap.
-This often requires traversing a broader and more sparse search space to find the ground truth.
-It poses a more severe challenge to the algorithm.
-}
+	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
 
@@
 
-	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
-	\textcolor{blue}{
-	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModel range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
-As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
-This is because these range query algorithms are almost graph-based.
-Graph algorithms need more iterations to find true neighbors in OOD datasets.}
+	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
 

### 2025-07-21 VLDB2026/main.tex
change

@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute  selectivity \textcolor{orange}{\cite{analyticdb,milvus}} significantly impact algorithm performance.
+For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance.
 As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.
@@
 We independently generate attribute for each dataset.
-	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
-Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
-This ensures that the data is initially sorted.
+	For range filtering queries, \textcolor{red}{we evaluate 1 widely used real-world dataset: %Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and 
+	WIT~\cite{wit_dataset}.
+Following prior work~\cite{DSG}, we use the data point ID (the primary key, ranging from $0$ to $n-1$) within each dataset as its attribute.
+This ensures that the data is initially sorted.}
 
@@
 				Enron & 1369 & 94,987 & 200 & 23& Text \\
-				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
-				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
+				%Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
+				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
+				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio \\
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
@@
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
-				Text2Image-Mix & 200 & 10,000,000 &10,000 & 59& Text,Image \\
+				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image \\
+				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image \\
 				\bottomrule

### 2025-07-21 Revision/response.tex

@@
 
-\textit{\textbf{ \textcolor{blue}{Section 4.2.1 Search peak memory.}}}
-
-\textcolor{blue}{As shown in Figure, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower.}
-
-\textit{\textbf{ \textcolor{blue}{Section 4.3.1 Search peak memory.}}}
-
-	\textcolor{blue}{As for the Search peak memory usage, we can find from the Figure that it is basically consistent with the Build peak memory usage trend.
-The algorithm needs to load the complete index into memory during search.
-Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
-For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}
-
 %%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:} 
-Thank you for your suggestion!
+Thank you for your suggestion.
 The paper [49] is a comprehensive survey and evaluation of graph structure approximate nearest neighbor search algorithms.
@@
 \textbf{Response:}
-Thank you for your suggestion!
-We have carefully searched and found no papers describing the application of attribute distribution and attribute selectivity.
-However, the real-world application scenarios of attribute distribution and attribute selectivity are indeed very extensive.
-For attribute distribution, the label attributes of many recommended application scenarios in reality conform to the power-law distribution.
-For attribute selectivity: For example, if you need to query data in which an attribute accounts for a very small proportion of the total, choosing a more advantageous algorithm will greatly improve the search effect.
-There are also databases with actual applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we will add more comprehensive citations in the paper.
 

### 2025-07-21 VLDB2026/main.tex
change

@@
 \textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.} Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
-\textcolor{red}{Some algorithms don't support using actual attributes as search keys, instead requiring an ID (the primary key, ranging from $0$ to $n-1$).
+	%\textcolor{red}{Some algorithms don't support using actual attributes as search keys, instead requiring an ID (the primary key, ranging from $0$ to $n-1$).
 Therefore, we uniformly use this ID as the search key.

### 2025-07-21 VLDB2026/main.tex
1

--- 2025-07-21 VLDB2026/main.tex
@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
+				WIT-Real & 512 & 1,000,000 & 40,300 & \textcolor{blue}{xx}& Image \\
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
@@
 		\item \textbf{Index Size}: The storage size of the persisted index on disk.
-		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction.
+		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction \textcolor{orange}{and search}.
 	\end{enumerate}
@@
 
-	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}.
+	%To investigate the performance of different attribute filtering algorithms during index construction,
+	\textcolor{orange}{To explore the time and space overhead of different attribute filtering algorithms during index construction and search,}
+	 we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}.
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
@@
 	\textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
-	This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
+	NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
 
@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.
+\textcolor{orange}{Note: For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we found that the time and space overhead data of each algorithm are basically the same, which shows that the authenticity of the attribute has little effect on it.
 	However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}

### 2025-07-21 VLDB2026/main.tex
1

@@
 It also prunes distant neighbors to save storage space.
-However, this introduces additional overhead and slows down the construction process.
+However, this introduces additional overhead and slows down the construction process.\textcolor{orange}{In contrast, as we have analyzed in the corresponding section on attribute filtering, ACORN-1 trades efficiency for accuracy, so the construction time is short.
+SeRF is built on HNSW, so the time is similar to and slightly lower than ACORN-1.}
 

### 2025-07-21 VLDB2026/main.tex
Update main.tex

--- 2025-07-21 VLDB2026/main.tex
@@
 	\subsubsection{Datasets}
-
 	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.
 We independently generate attribute for each dataset.
-	For range filtering queries, \textcolor{red}{we evaluate 1 widely used real-world dataset: %Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and 
-	WIT~\cite{wit_dataset}.
-Following prior work~\cite{DSG}, we use the data point ID (the primary key, ranging from $0$ to $n-1$) within each dataset as its attribute.
+
+	\textcolor{violet}{For range filtering queries, we evaluate 1 widely used dataset: WIT~\cite{wit_dataset}.
+Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
 This ensures that the data is initially sorted.}
 
-	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability.
+	\textcolor{violet}{Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.
+It should be noted that, during range filtering, due to the limitations of some algorithms, we uniformly sorted the vectors according to the query attribute.}
+
+	\textcolor{violet}{To validate the algorithm generalization capability, we also further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M.
 Specifically, the Text2Image dataset comprises two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
-
-	\textcolor{violet}{Given that the preceding datasets primarily utilized synthetic attributes, we additionally introduced two datasets containing real attributes for a more comprehensive evaluation: the YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we encoded the \texttt{page\_title} field into vectors using the \texttt{clip-vit-base-patch32} model, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.}
 
@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				WIT-Real & 512 & 1,000,000 & 40,300 & \textcolor{blue}{xx}& Image \\
+				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
@@
 		\item \textbf{Index Size}: The storage size of the persisted index on disk.
-		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction \textcolor{orange}{and search}.
+		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction.
 	\end{enumerate}
@@
 
-	%To investigate the performance of different attribute filtering algorithms during index construction,
-	\textcolor{orange}{To explore the time and space overhead of different attribute filtering algorithms during index construction and search,}
-	 we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}.
+	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}.
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
@@
 	\textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
-	NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
+	This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
 
@@
 
-	\textit{\textbf{Different Datasets.}}  
+	\sout{\textit{\textbf{Different Datasets.}}  }
 	To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.
@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{orange}{Note: For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we found that the time and space overhead data of each algorithm are basically the same, which shows that the authenticity of the attribute has little effect on it.
+\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.
 	However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
@@
 \textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.} Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
-	%\textcolor{red}{Some algorithms don't support using actual attributes as search keys, instead requiring an ID (the primary key, ranging from $0$ to $n-1$).
+\textcolor{red}{Some algorithms don't support using actual attributes as search keys, instead requiring an ID (the primary key, ranging from $0$ to $n-1$).
 Therefore, we uniformly use this ID as the search key.

### 2025-07-21 VLDB2026/main.tex
add

--- 2025-07-21 VLDB2026/main.tex
@@
 	\subsubsection{Datasets}
+
 	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.
 We independently generate attribute for each dataset.
-
-	\textcolor{violet}{For range filtering queries, we evaluate 1 widely used dataset: WIT~\cite{wit_dataset}.
+	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}.
 Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
-This ensures that the data is initially sorted.}
-
-	\textcolor{violet}{Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.
-It should be noted that, during range filtering, due to the limitations of some algorithms, we uniformly sorted the vectors according to the query attribute.}
-
-	\textcolor{violet}{To validate the algorithm generalization capability, we also further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M.
+This ensures that the data is initially sorted.
+
+	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability.
 Specifically, the Text2Image dataset comprises two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
+
+	\textcolor{violet}{Given that the preceding datasets primarily utilized synthetic attributes, we additionally introduced two datasets containing real attributes for a more comprehensive evaluation: the YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we encoded the \texttt{page\_title} field into vectors using the \texttt{clip-vit-base-patch32} model, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.}
 
@@
 				Enron & 1369 & 94,987 & 200 & 23& Text \\
-				%Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
-				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
-				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio \\
+				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
+				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
+				WIT-Real & 512 & 1,000,000 & 10,000 & 21& Text \\
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
-				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image \\
-				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image \\
+				Text2Image-Mix & 200 & 10,000,000 &10,000 & 22& Text,Image \\
 				\bottomrule
@@
 
-	\sout{\textit{\textbf{Different Datasets.}}  }
+	\textit{\textbf{Different Datasets.}}  
 	To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.

### 2025-07-21 VLDB2026/main.tex

--- 2025-07-21 VLDB2026/main.tex
@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				WIT-Real & 512 & 1,000,000 & 40,300 & \textcolor{blue}{xx}& Image \\
+				WIT-Real & 512 & 1,000,000 & 10,000 & 21& Text \\
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
-				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image \\
-				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image \\
+				Text2Image-Mix & 200 & 10,000,000 &10,000 & 22& Text,Image \\
 				\bottomrule

### 2025-07-21 VLDB2026/main.tex
1

--- 2025-07-21 VLDB2026/main.tex
@@
 		\small
+%		\label{tab:compair_1}
+%		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
+%			\hline
+%			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+%			\hline
+%			NHQ & Graph & C & Y & N& N& N & N & N \\
+%			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
+%			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
+%			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
+%			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
+%			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
+%			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
+%			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
+%			
+%			\hline
+%			
+%		\end{tabular}
 	\label{tab:compair_1}
-		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
+	\begin{tabular}{|l|l|*{12}{c|}}
 		\hline
-			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
-			\hline
-			NHQ & Graph & C & Y & N& N& N & N & N \\
-			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
-			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
-			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
-			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
-			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
-			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
-			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
-
-			\hline
+		\multicolumn{2}{|c|}{} & NHQ & Filtered & Stitched & CAPS & ACORN & UNG 
+		& Puck & DSG & iRange & SeRF & UNIFY & Win \\ \hline
+
+		\multirow{6}{*}{AF} 
+		& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
+		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
+		& OR                  & N   & Y   & Y   & N   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
+		& Flexible Attributes & N   & Y   & Y   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
+		& Complex Boolean     & N   & N   & N   & N   & Y   & N   & N   & \multicolumn{5}{c|}{} \\ \hline
+
+		\multicolumn{2}{|l|}{RF}             & N & N & N & N & Y & N & N & Y & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{Dynamic Insert} & N & Y & N & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{Multi Thread}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{Base}           & Graph & Graph & Graph & IVF & Graph & Graph & IVF & Graph & Graph & Graph & Graph & Graph \\ \hline
 
 	\end{tabular}
+
+%			\begin{tabular}{|c|c|c|c|}
+%			\hline
+%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+%			\hline
+%			DSG & Graph & Y & N \\
+%			iRange & Graph & N & Y \\
+%			SeRF & Graph & Y & Y \\
+%			UNIFY & Graph & Y & Y \\
+%			WinFilter & Graph & N & Y  \\
+%			\hline
+%		\end{tabular}
+%
 
@@
 				\vspace{0.1cm}
+				\textcolor{orange}{Filtered: FilteredVamana
+				Stitched: StitchedVamana
+				Win: WinFilter}
 				\textsuperscript{A} Post-filtering, 
@@
 
-	\renewcommand{\arraystretch}{0.9}
-	\begin{table}[t]
-		\centering
-
-		\setlength{\textfloatsep}{0.1cm}
-		\caption{Comparison of RF-ANN search algorithms}
-		\small	% 只会影响当前组的内容
-		\label{tab:range_algo}
-		\begin{tabular}{|c|c|c|c|}
-			\hline
-			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
-			\hline
-			DSG & Graph & Y & N \\
-			iRange & Graph & N & Y \\
-			SeRF & Graph & Y & Y \\
-			UNIFY & Graph & Y & Y \\
-			WinFilter & Graph & N & Y  \\
-			\hline
-		\end{tabular}
-
-		\footnotesize{
-			\begin{minipage}{\linewidth}
-				\centering
-				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
-				%				\textsuperscript{Y} Support, 
-				%				\textsuperscript{N} Unsupport.
-				%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-				%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-				%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-			\end{minipage}
-
-		}
-
-	\end{table}
+%	\renewcommand{\arraystretch}{0.9}
+%	\begin{table}[t]
+%		\centering
+%		
+%		\setlength{\textfloatsep}{0.1cm}
+%		\caption{Comparison of RF-ANN search algorithms}
+%		\small	% 只会影响当前组的内容
+%		\label{tab:range_algo}
+%		\begin{tabular}{|c|c|c|c|}
+%			\hline
+%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+%			\hline
+%			DSG & Graph & Y & N \\
+%			iRange & Graph & N & Y \\
+%			SeRF & Graph & Y & Y \\
+%			UNIFY & Graph & Y & Y \\
+%			WinFilter & Graph & N & Y  \\
+%			\hline
+%		\end{tabular}
+
+%		\footnotesize{
+%			\begin{minipage}{\linewidth}
+%				\centering
+%				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
+%				%				\textsuperscript{Y} Support, 
+%				%				\textsuperscript{N} Unsupport.
+%				%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
+%				%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+%				%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+%			\end{minipage} 
+%			
+%		}
+%	\end{table}
 

### 2025-07-21 VLDB2026/main.tex
add

@@
 
-	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
+\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
+
+\textcolor{blue}{
+	We conducted experiments on the text2image-mix dataset.
+This dataset contains both image and text vectors.
+It is a more complex multimodal dataset.
+As shown in Figure~\ref{fig:TrinityExtension——Attribution}, although the queries are more complex, UNG and NHQ still perform the best.
+CAPS is the next best.
+	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
+The nearest neighbors in the index are often from the same modality because they are closer in distance.
+Therefore, the search results on this dataset are similar to those in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
+UNG and NHQ perform the best.
+CAPS clusters based on vector similarity.
+It actually clusters the vectors into the same modality.
+Then it uses attribute filtering to divide the data further.
+This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
+	In contrast, the text2image dataset shown in Figure~\ref{fig:exp_6_1} is different.
+The queries and the dataset are from different modalities.
+The queries are far from the dataset.
+The ground truths are also scattered and not clustered together.
+To find the ground truths, the algorithm often needs to traverse more points.
+This is a greater challenge for the algorithms.
+	%	We conducted extensive scalability experiments on the Text2Image-Mix dataset.
+This dataset contains both image and text vectors.
+It represents a more complex multimodal query scenario.
+As shown in Figure 12, the UNG and NHQ algorithms still achieve the best performance, followed closely by CAPS.
+	%	In the Text2Image-Mix dataset, the ground truth of the query vector is usually the corresponding vector in the same modality.
+Since the neighbor relationships in the graph are often based on vector distance, vectors of similar modalities naturally form closer connections in the graph.
+Therefore, during the search process, the algorithm tends to traverse efficiently within the same modality.
+This makes the search mechanism similar to our experiments on single-modality datasets, thus maintaining high performance.
+	%	The good performance of the CAPS algorithm is due to its unique hierarchical space partitioning strategy.
+It first clusters vectors based on similarity.
+In multimodal data, this clustering naturally groups vectors of similar modalities into the same cluster.
+Then, CAPS further partitions these clusters using attributes.
+This allows it to quickly find the nearest neighbors that meet the filtering conditions.
+	%	It is worth noting that, compared to the OOD dataset discussed in the "Dataset Impact" section, the Text2Image-Mix dataset also involves modality differences.
+However, its complexity lies in modality mixing.
+The OOD dataset, on the other hand, has a modality gap.
+This often requires traversing a broader and more sparse search space to find the ground truth.
+It poses a more severe challenge to the algorithm.
+}
 
@@
 
-	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
+\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
+\textcolor{blue}{
+	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModel range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets.}
 

### 2025-07-21 VLDB2026/main.tex
1

--- 2025-07-21 VLDB2026/main.tex
@@
 
-		\caption{Comparison of AF-ANN search algorithms}
+		\caption{Comparison of \textcolor{orange}{AF-ANN and RF-ANN} search algorithms}
 		\small
@@
 		\hline
-		\multicolumn{2}{|c|}{} & NHQ & Filtered & Stitched & CAPS & ACORN & UNG 
-		& Puck & DSG & iRange & SeRF & UNIFY & Win \\ \hline
-
-		\multirow{6}{*}{AF} 
+
+		\multicolumn{2}{|c|}{\textbf{Algorithm}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
+		 \\ \hline
+		\multirow{6}{*}{\textbf{AF}} 
 		& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
@@
 
-		\multicolumn{2}{|l|}{RF}             & N & N & N & N & Y & N & N & Y & Y & Y & Y & Y \\ \hline
-		\multicolumn{2}{|l|}{Dynamic Insert} & N & Y & N & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
-		\multicolumn{2}{|l|}{Multi Thread}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
-		\multicolumn{2}{|l|}{Base}           & Graph & Graph & Graph & IVF & Graph & Graph & IVF & Graph & Graph & Graph & Graph & Graph \\ \hline
+		\multicolumn{2}{|l|}{\textbf{RF}}             & N & N & N & N & Y & N & N & Y & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Dynamic Insert}} & N & Y & N & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Multi Thread}}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Base}}           & Graph & Graph & Graph & IVF & Graph & Graph & IVF & Graph & Graph & Graph & Graph & Graph \\ \hline
 

### 2025-07-21 Revision/response.tex
Update response.tex

--- 2025-07-21 Revision/response.tex
@@
 We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.
+
+\textcolor{blue}{"We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
+Compared with the experimental results on the original server (as shown in Figure 4d), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods."}
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:} 
+Thank you for the suggestion!
+We realized that the original wording was somewhat vague and led to confusion among readers.
+To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified each algorithm's support for AF and RF in the unified table.
 

### 2025-07-21 Revision/response.tex
Update response.tex

--- 2025-07-21 Revision/response.tex
@@
 
+\textcolor{blue}{Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).}
+
 %%%%%%%%%%%%%%%%%%%%%% D4 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-21 Revision/response.tex
1

@@
 \textbf{Response:} 
+Thank you for your suggestion!
+Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the feature of whether to support disk for each algorithm in Table 1.
+At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
+The results are shown in Figure\ref{fig:recall-latency}:
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
+	\caption{}
+	\label{fig:recall-latency}
+\end{figure}
+
+Due to space limitations and the fact that only one method supports disk-based execution, we provide the breakdown of I/O and CPU costs for disk-based methods in the following analysis.
+To this end, we conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
+
+\begin{itemize}
+	\item SSD-based FilteredDiskANN (original disk-based method)
+	\item FilteredVamana (memory-based method)
+	\item StitchedVamana (memory-based method)
+\end{itemize}
+
+All experiments were run with 32 search threads for fair comparison.
+The following figure shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:
+
+\textbf{ Key Observations:}
+
+Latency-Recall Tradeoff:
+As expected, SSD-based FilteredDiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
+When Recall@10 reaches 0.96, its latency increases super-linearly to over 100 ms.
+
+Cost Breakdown of DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
+The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
+This clearly shows that improving disk read efficiency or reducing I/O volume is critical for performance optimization.
+
+\textbf{In-memory Methods:}
+
+FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
+While StitchedVamana achieves extremely low latency (sub-5 ms) due to its stitched multi-label index structure, its fixed edge connectivity may limit effectiveness under highly uncorrelated label distributions.
+Nevertheless, it consistently supports 90\%+ Recall@10 across diverse datasets, as shown in our evaluations.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion!
-Currently, most hybrid query methods are based on memory, except for filteredDiskANN, which supports SSD, so we will add explanation information in the paper.
-At the same time, we also use real data sets to compare the difference in search performance between filteredDiskANN in memory and on SSD.
-The results are shown in Figure \ref{fig:recall-latency}:
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
-	\caption{}
-	\label{fig:recall-latency}
-\end{figure}
-
- In response to your request for a breakdown of I/O and CPU cost in disk-based methods, we conducted additional experiments on the real-world yt8m dataset. We compared three variants of DiskANN:
-
- \begin{itemize}
- 	\item SSD-based FilteredDiskANN (original disk-based method)
- 	\item FilteredVamana (memory-based method)
- 	\item StitchedVamana (memory-based method)
- \end{itemize}
-
-All experiments were run with 32 search threads for fair comparison.
-The following figure shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:
-
-\textbf{ Key Observations:}
-
-Latency-Recall Tradeoff:
-As expected, SSD-based FilteredDiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
-When Recall@10 reaches 0.96, its latency increases super-linearly to over 100 ms.
-
-Cost Breakdown of DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
-The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
-This clearly shows that improving disk read efficiency or reducing I/O volume is critical for performance optimization.
-
-\textbf{In-memory Methods:}
-
-FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
-While StitchedVamana achieves extremely low latency (sub-5 ms) due to its stitched multi-label index structure, its fixed edge connectivity may limit effectiveness under highly uncorrelated label distributions.
-Nevertheless, it consistently supports 90\%+ Recall@10 across diverse datasets, as shown in our evaluations.
+Thank you for your suggestion! We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
 
@@
 
-\textit{\textbf{ \textcolor{blue}{Section 4.2.1 Search peak memory.}}}
+\textit{\textbf{ \textcolor{blue}{" Search peak memory.}}}
 
 \textcolor{blue}{As shown in Figure, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower.}
+Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower."}
 
-\textit{\textbf{ \textcolor{blue}{Section 4.3.1 Search peak memory.}}}
+\textit{\textbf{ \textcolor{blue}{"Search peak memory.}}}
 
@@
 Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
-For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}
+For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend."}
 
@@
 We sincerely apologize for the misuse of notation in Definition 2.3. This has been corrected in the revised version. Thank you for pointing it out.
-
-\textcolor{blue}{Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).}
 
@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-We will clarify this point in the revised version of the paper, specifically in the section on \textcolor{blue}{Multi-Attribute Construction and Multi-Attribute Query}.
+We will clarify this point in the revised version of the paper, specifically in the section on \textcolor{blue}{Multi-Attribute Construction and Multi-Attribute Query}.\textcolor{blue}{"Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
+Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments."}
 %Thanks to the reviewer for suggesting that there is no explanation in Figure 7 why Vamana is not included.
@@
 To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified each algorithm's support for AF and RF in the unified table.
+\textcolor{blue}{The fused table is Table1: Comparison of AF-ANN and RF-ANN search algorithms.}
 

### 2025-07-21 Revision/response.tex

@@
 We sincerely apologize for the misuse of notation in Definition 2.3. This has been corrected in the revised version. Thank you for pointing it out.
+
+\textcolor{blue}{Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).}
 

### 2025-07-21 Revision/response.tex
add

--- 2025-07-21 Revision/response.tex
@@
 
+\textcolor{blue}{
+}
+
 %%%%%%%%%%%%%%%%%%%%%% R4 %%%%%%%%%%%%%%%%%%%%%%
@@
 \noindent
-\textbf{Response:} We think this is an excellent suggestion.
+\textbf{Response:} 
+Thank you for your suggestion.
+We have addressed this issue in detail in our response to Meta-Review R2.
+Specifically, we have added complex multimodal query experiments and provided an in-depth analysis of the results.
+For more details, please refer to our response to Meta-Review R2.
+%We think this is an excellent suggestion.
 We have enhanced our experiments by incorporating more complex multimodal dataset evaluations in Section \textcolor{blue}{XXX} of the paper.

### 2025-07-21 Revision/response.tex
change

@@
 
-We conducted experiments on both datasets and analyzed the performance of various algorithms.
+We conducted experiments on both datasets and present the performance analysis for various algorithms in \textcolor{blue}{Sections 4.2.2 and 4.3.2}.
 Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.

### 2025-07-21 Revision/response.tex
change response

@@
 \textcolor{blue}{
+	"We conducted experiments on the text2image-mix dataset.
+This dataset contains both image and text vectors.
+It is a more complex multimodal dataset.
+As shown in Figure 12, although the queries are more complex, UNG and NHQ still perform the best.
+CAPS is the next best.
+	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
+The nearest neighbors in the index are often from the same modality because they are closer in distance.
+Therefore, the search results on this dataset are similar to those in Figure 4.
+UNG and NHQ perform the best.
+CAPS clusters based on vector similarity.
+It actually clusters the vectors into the same modality.
+Then it uses attribute filtering to divide the data further.
+This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
+	In contrast, the text2image dataset shown in Figure 11 is different.
+The queries and the dataset are from different modalities.
+The queries are far from the dataset.
+The ground truths are also scattered and not clustered together.
+To find the ground truths, the algorithm often needs to traverse more points.
+This is a greater challenge for the algorithms."
+}
+
+\textcolor{blue}{
+		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.
+As shown in Figure 15, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets."
 }
@@
 
-We conducted experiments on both datasets and present the performance analysis for various algorithms in \textcolor{blue}{Sections 4.2.2 and 4.3.2}.
+We conducted experiments on both datasets and analyzed the performance of various algorithms.
 Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.

### 2025-07-21 Revision/response.tex

@@
 \textcolor{blue}{
-	"We conducted experiments on the text2image-mix dataset.
-This dataset contains both image and text vectors.
-It is a more complex multimodal dataset.
-As shown in Figure 12, although the queries are more complex, UNG and NHQ still perform the best.
-CAPS is the next best.
-	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
-The nearest neighbors in the index are often from the same modality because they are closer in distance.
-Therefore, the search results on this dataset are similar to those in Figure 4.
-UNG and NHQ perform the best.
-CAPS clusters based on vector similarity.
-It actually clusters the vectors into the same modality.
-Then it uses attribute filtering to divide the data further.
-This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
-	In contrast, the text2image dataset shown in Figure 11 is different.
-The queries and the dataset are from different modalities.
-The queries are far from the dataset.
-The ground truths are also scattered and not clustered together.
-To find the ground truths, the algorithm often needs to traverse more points.
-This is a greater challenge for the algorithms."
-}
-
-\textcolor{blue}{
-		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.
-As shown in Figure 15, the algorithms still perform the worst on multimodal datasets like Text2Image.
-This is because these range query algorithms are almost graph-based.
-Graph algorithms need more iterations to find true neighbors in OOD datasets."
 }

### 2025-07-21 VLDB2026/main.tex
1
change response

--- 2025-07-21 VLDB2026/main.tex
@@
 
-		\caption{Comparison of \textcolor{orange}{AF-ANN and RF-ANN} search algorithms}
+		\caption{Comparison of AF-ANN search algorithms}
 		\small
@@
 		\multicolumn{2}{|l|}{\textbf{Multi Thread}}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Disk Storage Support}}           &N  & Y& N & N & N & N & N & N & N & N & N & N \\ \hline
 		\multicolumn{2}{|l|}{\textbf{Base}}           & Graph & Graph & Graph & IVF & Graph & Graph & IVF & Graph & Graph & Graph & Graph & Graph \\ \hline
-
 	\end{tabular}
@@
 				\vspace{0.1cm}
-				\textcolor{orange}{Filtered: FilteredVamana
-				Stitched: StitchedVamana
-				Win: WinFilter}
 				\textsuperscript{A} Post-filtering, 
@@
 
-%	\renewcommand{\arraystretch}{0.9}
-%	\begin{table}[t]
-%		\centering
-%		
-%		\setlength{\textfloatsep}{0.1cm}
-%		\caption{Comparison of RF-ANN search algorithms}
-%		\small	% 只会影响当前组的内容
-%		\label{tab:range_algo}
-%		\begin{tabular}{|c|c|c|c|}
-%			\hline
-%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
-%			\hline
-%			DSG & Graph & Y & N \\
-%			iRange & Graph & N & Y \\
-%			SeRF & Graph & Y & Y \\
-%			UNIFY & Graph & Y & Y \\
-%			WinFilter & Graph & N & Y  \\
-%			\hline
-%		\end{tabular}
-
-%		\footnotesize{
-%			\begin{minipage}{\linewidth}
-%				\centering
-%				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
-%				%				\textsuperscript{Y} Support, 
-%				%				\textsuperscript{N} Unsupport.
-%				%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-%				%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-%				%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-%			\end{minipage} 
-%			
-%		}
-%	\end{table}
+	\renewcommand{\arraystretch}{0.9}
+	\begin{table}[t]
+		\centering
+
+		\setlength{\textfloatsep}{0.1cm}
+		\caption{Comparison of RF-ANN search algorithms}
+		\small	% 只会影响当前组的内容
+		\label{tab:range_algo}
+		\begin{tabular}{|c|c|c|c|}
+			\hline
+			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+			\hline
+			DSG & Graph & Y & N \\
+			iRange & Graph & N & Y \\
+			SeRF & Graph & Y & Y \\
+			UNIFY & Graph & Y & Y \\
+			WinFilter & Graph & N & Y  \\
+			\hline
+		\end{tabular}
+
+		\footnotesize{
+			\begin{minipage}{\linewidth}
+				\centering
+				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
+				%				\textsuperscript{Y} Support, 
+				%				\textsuperscript{N} Unsupport.
+				%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
+				%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+				%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+			\end{minipage}
+
+		}
+
+	\end{table}
 
@@
 
-	We introduce 5 representative range filtering algorithms and present a comparative overview in Table~\ref{tab:compair_1}.
+	We introduce 5 representative range filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.
 
@@
 	\subsubsection{Datasets}
+
 	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.
 We independently generate attribute for each dataset.
-
-	\textcolor{violet}{For range filtering queries, we evaluate 1 widely used dataset: WIT~\cite{wit_dataset}.
-Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
+	For range filtering queries, \textcolor{red}{we evaluate 1 widely used real-world dataset: %Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and 
+	WIT~\cite{wit_dataset}.
+Following prior work~\cite{DSG}, we use the data point ID (the primary key, ranging from $0$ to $n-1$) within each dataset as its attribute.
 This ensures that the data is initially sorted.}
 
-	\textcolor{violet}{Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.
-It should be noted that, during range filtering, due to the limitations of some algorithms, we uniformly sorted the vectors according to the query attribute.}
-
-	\textcolor{violet}{To validate the algorithm generalization capability, we also further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M.
+	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability.
 Specifically, the Text2Image dataset comprises two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
+
+	\textcolor{violet}{Given that the preceding datasets primarily utilized synthetic attributes, we additionally introduced two datasets containing real attributes for a more comprehensive evaluation: the YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we encoded the \texttt{page\_title} field into vectors using the \texttt{clip-vit-base-patch32} model, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.}
 
@@
 				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
-				WIT-Real & 512 & 1,000,000 & 10,000 & 21& Text \\
+				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
-				Text2Image-Mix & 200 & 10,000,000 &10,000 & 22& Text,Image \\
+				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image \\
+				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image \\
 				\bottomrule
@@
 It also prunes distant neighbors to save storage space.
-However, this introduces additional overhead and slows down the construction process.\textcolor{orange}{In contrast, as we have analyzed in the corresponding section on attribute filtering, ACORN-1 trades efficiency for accuracy, so the construction time is short.
-SeRF is built on HNSW, so the time is similar to and slightly lower than ACORN-1.}
+However, this introduces additional overhead and slows down the construction process.
 

### 2025-07-21 Revision/response.tex
1

@@
 \textbf{Response:} 
+Thank you for your suggestion.
+We are deeply aware of this deficiency, so we added the search peak memory usage of each algorithm in \textcolor{blue}{Section 4.2.1} of attribute filtering and \textcolor{blue}{Section 4.3.1}  of range filtering, and carefully analyzed the reasons.
+
+\textit{\textbf{ \textcolor{blue}{" Search peak memory.}}}
+
+\textcolor{blue}{As shown in Figure, we can find that the peak memory usage of each algorithm during search does not differ significantly.
+Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower."}
+
+\textit{\textbf{ \textcolor{blue}{"Search peak memory.}}}
+
+\textcolor{blue}{As for the Search peak memory usage, we can find from the Figure that it is basically consistent with the Build peak memory usage trend.
+The algorithm needs to load the complete index into memory during search.
+Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
+For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend."}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We are deeply aware of this deficiency, so we added the search peak memory usage of each algorithm in \textcolor{blue}{Section 4.2.1} of attribute filtering and \textcolor{blue}{Section 4.3.1}  of range filtering, and carefully analyzed the reasons.
-
-\textit{\textbf{ \textcolor{blue}{" Search peak memory.}}}
-
-\textcolor{blue}{As shown in Figure, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower."}
-
-\textit{\textbf{ \textcolor{blue}{"Search peak memory.}}}
-
-	\textcolor{blue}{As for the Search peak memory usage, we can find from the Figure that it is basically consistent with the Build peak memory usage trend.
-The algorithm needs to load the complete index into memory during search.
-Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
-For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend."}
+Thank you for your suggestion! We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
 

### 2025-07-21 Revision/response.tex
update

--- 2025-07-21 Revision/response.tex
@@
 
-\textcolor{blue}{
-}
-
 %%%%%%%%%%%%%%%%%%%%%% R4 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:} 
+Thank you for your suggestion.
+Using IDs as attributes for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
+To address this issue, we have added two datasets that use real attributes:
 
+\textbf{YT-Audio-Real dataset:} For this dataset, we utilized the URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as real attributes, and used view counts as the attribute for range filtering experiments.
+
+\textbf{WIT-Real dataset:} We used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extracted the language type and the length of the \texttt{context\_page\_description} field as real attributes, and used them for range filtering.
 %%%%%%%%%%%%%%%%%%%%%% R5 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:}
-Thank you for your suggestion!
-Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the feature of whether to support disk for each algorithm in Table 1.
-At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
-The results are shown in Figure\ref{fig:recall-latency}:
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
-	\caption{}
-	\label{fig:recall-latency}
-\end{figure}
-
-Due to space limitations and the fact that only one method supports disk-based execution, we provide the breakdown of I/O and CPU costs for disk-based methods in the following analysis.
-To this end, we conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
-
-\begin{itemize}
-	\item SSD-based FilteredDiskANN (original disk-based method)
-	\item FilteredVamana (memory-based method)
-	\item StitchedVamana (memory-based method)
-\end{itemize}
-
-All experiments were run with 32 search threads for fair comparison.
-The following figure shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:
-
-\textbf{ Key Observations:}
-
-Latency-Recall Tradeoff:
-As expected, SSD-based FilteredDiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
-When Recall@10 reaches 0.96, its latency increases super-linearly to over 100 ms.
-
-Cost Breakdown of DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
-The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
-This clearly shows that improving disk read efficiency or reducing I/O volume is critical for performance optimization.
-
-\textbf{In-memory Methods:}
-
-FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
-While StitchedVamana achieves extremely low latency (sub-5 ms) due to its stitched multi-label index structure, its fixed edge connectivity may limit effectiveness under highly uncorrelated label distributions.
-Nevertheless, it consistently supports 90\%+ Recall@10 across diverse datasets, as shown in our evaluations.
 
@@
 \textbf{Response:}
-Thank you for your suggestion.
-We are deeply aware of this deficiency, so we added the search peak memory usage of each algorithm in \textcolor{blue}{Section 4.2.1} of attribute filtering and \textcolor{blue}{Section 4.3.1}  of range filtering, and carefully analyzed the reasons.
-
-\textit{\textbf{ \textcolor{blue}{" Search peak memory.}}}
-
-\textcolor{blue}{As shown in Figure, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower."}
-
-\textit{\textbf{ \textcolor{blue}{"Search peak memory.}}}
-
-\textcolor{blue}{As for the Search peak memory usage, we can find from the Figure that it is basically consistent with the Build peak memory usage trend.
-The algorithm needs to load the complete index into memory during search.
-Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
-For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend."}
 
@@
 \noindent
-\textbf{Response:} 
-Thank you for your suggestion.
-We have addressed this issue in detail in our response to Meta-Review R2.
-Specifically, we have added complex multimodal query experiments and provided an in-depth analysis of the results.
-For more details, please refer to our response to Meta-Review R2.
-%We think this is an excellent suggestion.
+\textbf{Response:} We think this is an excellent suggestion.
 We have enhanced our experiments by incorporating more complex multimodal dataset evaluations in Section \textcolor{blue}{XXX} of the paper.
@@
 \textbf{Response:} 
+Thank you for your suggestion. We fully understand your concern regarding the use of synthetic or less meaningful attributes in our hybrid query experimental setup.
+
+To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in MetaReview R3.
+
+By incorporating the YT-Audio-Real and WIT-Real datasets with their respective real attributes, we believe our experimental study now better reflects real-world application scenarios, and, as you suggested, allows for a more comprehensive and meaningful evaluation of hybrid query functionality.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion! We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
+Thank you for your suggestion!
+Currently, most hybrid query methods are based on memory, except for filteredDiskANN, which supports SSD, so we will add explanation information in the paper.
+At the same time, we also use real data sets to compare the difference in search performance between filteredDiskANN in memory and on SSD.
+The results are shown in Figure \ref{fig:recall-latency}:
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
+	\caption{}
+	\label{fig:recall-latency}
+\end{figure}
+
+ In response to your request for a breakdown of I/O and CPU cost in disk-based methods, we conducted additional experiments on the real-world yt8m dataset. We compared three variants of DiskANN:
+
+ \begin{itemize}
+ 	\item SSD-based FilteredDiskANN (original disk-based method)
+ 	\item FilteredVamana (memory-based method)
+ 	\item StitchedVamana (memory-based method)
+ \end{itemize}
+
+All experiments were run with 32 search threads for fair comparison.
+The following figure shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:
+
+\textbf{ Key Observations:}
+
+Latency-Recall Tradeoff:
+As expected, SSD-based FilteredDiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
+When Recall@10 reaches 0.96, its latency increases super-linearly to over 100 ms.
+
+Cost Breakdown of DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
+The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
+This clearly shows that improving disk read efficiency or reducing I/O volume is critical for performance optimization.
+
+\textbf{In-memory Methods:}
+
+FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
+While StitchedVamana achieves extremely low latency (sub-5 ms) due to its stitched multi-label index structure, its fixed edge connectivity may limit effectiveness under highly uncorrelated label distributions.
+Nevertheless, it consistently supports 90\%+ Recall@10 across diverse datasets, as shown in our evaluations.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion! We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
+Thank you for your suggestion.
+We are deeply aware of this deficiency, so we added the search peak memory usage of each algorithm in \textcolor{blue}{Section 4.2.1} of attribute filtering and \textcolor{blue}{Section 4.3.1}  of range filtering, and carefully analyzed the reasons.
+
+\textit{\textbf{ \textcolor{blue}{Section 4.2.1 Search peak memory.}}}
+
+\textcolor{blue}{As shown in Figure, we can find that the peak memory usage of each algorithm during search does not differ significantly.
+Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower.}
+
+\textit{\textbf{ \textcolor{blue}{Section 4.3.1 Search peak memory.}}}
+
+	\textcolor{blue}{As for the Search peak memory usage, we can find from the Figure that it is basically consistent with the Build peak memory usage trend.
+The algorithm needs to load the complete index into memory during search.
+Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
+For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}
 
@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-We will clarify this point in the revised version of the paper, specifically in the section on \textcolor{blue}{Multi-Attribute Construction and Multi-Attribute Query}.\textcolor{blue}{"Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
-Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments."}
+We will clarify this point in the revised version of the paper, specifically in the section on \textcolor{blue}{Multi-Attribute Construction and Multi-Attribute Query}.
 %Thanks to the reviewer for suggesting that there is no explanation in Figure 7 why Vamana is not included.
@@
 To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified each algorithm's support for AF and RF in the unified table.
-\textcolor{blue}{The fused table is Table1: Comparison of AF-ANN and RF-ANN search algorithms.}
 

### 2025-07-21 VLDB2026/main.tex

@@
 
-	\renewcommand{\arraystretch}{0.9}
-	\begin{table}[t]
-		\centering
-
-		\setlength{\textfloatsep}{0.1cm}
-		\caption{Comparison of RF-ANN search algorithms}
-		\small	% 只会影响当前组的内容
-		\label{tab:range_algo}
-		\begin{tabular}{|c|c|c|c|}
-			\hline
-			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
-			\hline
-			DSG & Graph & Y & N \\
-			iRange & Graph & N & Y \\
-			SeRF & Graph & Y & Y \\
-			UNIFY & Graph & Y & Y \\
-			WinFilter & Graph & N & Y  \\
-			\hline
-		\end{tabular}
-
-		\footnotesize{
-			\begin{minipage}{\linewidth}
-				\centering
-				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
-				%				\textsuperscript{Y} Support, 
-				%				\textsuperscript{N} Unsupport.
-				%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-				%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-				%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-			\end{minipage}
-
-		}
-
-	\end{table}
+%	\renewcommand{\arraystretch}{0.9}
+%	\begin{table}[t]
+%		\centering
+%		
+%		\setlength{\textfloatsep}{0.1cm}
+%		\caption{Comparison of RF-ANN search algorithms}
+%		\small	% 只会影响当前组的内容
+%		\label{tab:range_algo}
+%		\begin{tabular}{|c|c|c|c|}
+%			\hline
+%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+%			\hline
+%			DSG & Graph & Y & N \\
+%			iRange & Graph & N & Y \\
+%			SeRF & Graph & Y & Y \\
+%			UNIFY & Graph & Y & Y \\
+%			WinFilter & Graph & N & Y  \\
+%			\hline
+%		\end{tabular}
+%		
+%		
+%		\footnotesize{
+%			\begin{minipage}{\linewidth}
+%				\centering
+%				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
+%				%				\textsuperscript{Y} Support, 
+%				%				\textsuperscript{N} Unsupport.
+%				%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
+%				%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+%				%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+%			\end{minipage} 
+%			
+%		}
+%		
+%	\end{table}
 
@@
 
-	We introduce 5 representative range filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.
+	We introduce 5 representative range filtering algorithms and present a comparative overview in \textcolor{orange}{Table~\ref{tab:compair_1}.}
 
@@
 
-	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}
+%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}
 
@@
 
-	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
+%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
 

### 2025-07-21 Revision/response.tex
Update response.tex

--- 2025-07-21 Revision/response.tex
@@
 \textbf{Response:} 
+Thank you for your suggestion.
+We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
+The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.
 
+\textcolor{blue}{"We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
+Compared with the experimental results on the original server (as shown in Figure 4d), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods."}
 %%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
-The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.
-
-\textcolor{blue}{"We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
-Compared with the experimental results on the original server (as shown in Figure 4d), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods."}
+Thank you for your suggestion! We add relevant experiments conducted on different servers. Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-21 VLDB2026/main.tex
add multimodal

--- 2025-07-21 VLDB2026/main.tex
@@
 
-	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
-
-	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}
+\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
+
+\textcolor{blue}{
+	We conducted experiments on the text2image-mix dataset.
+This dataset contains both image and text vectors.
+It is a more complex multimodal dataset.
+As shown in Figure~\ref{fig:TrinityExtension——Attribution}, although the queries are more complex, UNG and NHQ still perform the best.
+CAPS is the next best.
+	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
+The nearest neighbors in the index are often from the same modality because they are closer in distance.
+Therefore, the search results on this dataset are similar to those in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
+UNG and NHQ perform the best.
+CAPS clusters based on vector similarity.
+It actually clusters the vectors into the same modality.
+Then it uses attribute filtering to divide the data further.
+This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
+	In contrast, the text2image dataset shown in Figure~\ref{fig:exp_6_1} is different.
+The queries and the dataset are from different modalities.
+The queries are far from the dataset.
+The ground truths are also scattered and not clustered together.
+To find the ground truths, the algorithm often needs to traverse more points.
+This is a greater challenge for the algorithms.
+	%	We conducted extensive scalability experiments on the Text2Image-Mix dataset.
+This dataset contains both image and text vectors.
+It represents a more complex multimodal query scenario.
+As shown in Figure 12, the UNG and NHQ algorithms still achieve the best performance, followed closely by CAPS.
+	%	In the Text2Image-Mix dataset, the ground truth of the query vector is usually the corresponding vector in the same modality.
+Since the neighbor relationships in the graph are often based on vector distance, vectors of similar modalities naturally form closer connections in the graph.
+Therefore, during the search process, the algorithm tends to traverse efficiently within the same modality.
+This makes the search mechanism similar to our experiments on single-modality datasets, thus maintaining high performance.
+	%	The good performance of the CAPS algorithm is due to its unique hierarchical space partitioning strategy.
+It first clusters vectors based on similarity.
+In multimodal data, this clustering naturally groups vectors of similar modalities into the same cluster.
+Then, CAPS further partitions these clusters using attributes.
+This allows it to quickly find the nearest neighbors that meet the filtering conditions.
+	%	It is worth noting that, compared to the OOD dataset discussed in the "Dataset Impact" section, the Text2Image-Mix dataset also involves modality differences.
+However, its complexity lies in modality mixing.
+The OOD dataset, on the other hand, has a modality gap.
+This often requires traversing a broader and more sparse search space to find the ground truth.
+It poses a more severe challenge to the algorithm.
+}
+
+%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}
 
@@
 
-	\textit{\textbf{\textcolor{blue}{Complex Queries.}}}
-
-	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
+\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
+\textcolor{blue}{
+	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModel range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets.}
+
+%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
 

### 2025-07-22 VLDB2026/main.tex
change

@@
 	\textit{\textbf{Different Datasets.}}  
-	To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.
+	\sout{To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.
 Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.
@@
 However, ACORN, UNG, and FilteredVamana show relatively stable performance on Text2Image.
-Their performance drops less compared to in-distribution (ID) datasets such as GIST1M and GloVe, indicating better adaptability to OOD queries.
+Their performance drops less compared to in-distribution (ID) datasets such as GIST1M and GloVe, indicating better adaptability to OOD queries.}
 

### 2025-07-22 VLDB2026/main.tex
Update main.tex

@@
 		\item \textbf{Index Size}: The storage size of the persisted index on disk.
-		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction.
+		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction \textcolor{cyan}{and search}.
 	\end{enumerate}
@@
 
-	We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1} and Table~\ref{tab:range_algo}.
+	We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}.
 For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance.

### 2025-07-22 VLDB2026/main.tex
change

--- 2025-07-22 VLDB2026/main.tex
@@
 
-	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}}
+	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big Dataset range}, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB).
+At the same time, we can see that some algorithms (e.g., SeRF, ACORN-1) perform even worse than the VBASE database, which indicates that they do not adapt well to large-scale dataset scenarios.
+Although Milvus has a low QPS, it can achieve a recall of 1 with an excellent memory footprint of around 80GB}.
 

### 2025-07-22 VLDB2026/main.tex
Update main.tex

--- 2025-07-22 VLDB2026/main.tex
@@
 	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower.}
+Among them, CAPS and NHQ have relatively higher peak memory usage, while \underline{the database's peak memory usage} is comparatively lower.}
 
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{red}{We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
-Compared with the experimental results on the original server (as shown in Figure 4d), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+	\textcolor{red}{We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}
@@
 It is a more complex multimodal dataset.
-As shown in Figure~\ref{fig:TrinityExtension——Attribution}, although the queries are more complex, UNG and NHQ still perform the best.
+As shown in Figure~\ref{fig:MultiModel}, although the queries are more complex, UNG and NHQ still perform the best.
 CAPS is the next best.
@@
 			\caption{\footnotesize MultiModel}
-			\label{fig:rangeFilter_build_time}
+			\label{fig:MultiModel}
 		\end{subfigure}
@@
 			\caption{\footnotesize Different Computer}
-			\label{fig:rangeFilter_index_size_mb}
+			\label{fig:Different Computer}
 		\end{subfigure}
@@
 			\caption{\footnotesize Big Dataset}
-			\label{fig:rangeFilter_build_memory_mb}
+			\label{fig:Big Dataset}
 		\end{subfigure}
@@
 
-		\textcolor{orange}{As for the Search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the Build peak memory usage trend.
+		\textcolor{orange}{As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
 The algorithm needs to load the complete index into memory during search.
@@
 	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on the same server configuration, with results presented in Figure~\ref{fig:Different Computer range}.
-When compared with the original server's experimental results shown in Figure~\ref{fig:exp_8_2}$e$, our findings remain consistent with those reported in Section 4.2.4.
+When compared with the original server's experimental results shown in Figure~\ref{fig:exp_8_2}b, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-22 VLDB2026/main.tex
Update main.tex

@@
 Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
-But, UNG slightly underperforms on high-LID datasets such as GloVe.
-In contrast, CAPS performs better on high-LID datasets but is more sensitive to dataset characteristics.
+But, UNG slightly \sout{underperforms on high-LID datasets such as GloVe.} In contrast, CAPS performs better on high-LID datasets but is more sensitive to dataset characteristics.
 CAPS leverages multi-level spatial partitioning and attribute filtering to efficiently explore sparse spaces, whereas UNG relies on structured attribute organization, which limits its adaptability to sparse high-dimensional distributions.

### 2025-07-22 VLDB2026/main.tex
Update main.tex

--- 2025-07-22 VLDB2026/main.tex
@@
 	\textit{Single-Thread Search.}  
-	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under full-recall conditions (recall = 1), search often requires traversing larger candidate sets or deeper graph paths, leading to increased computational cost and a sharp QPS drop for most methods.
+	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths.
+This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods.
+Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
+\textcolor{violet}{Puck and CAPS perform relatively well on some datasets.
+Partition-based methods have limitations regarding different vector data distributions, and how to configure different partitions for different datasets remains a challenge.
+However, this also demonstrates that IVF-based methods are still very promising for hybrid queries.}
+
+	NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets.
+This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.
+As observed in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, StitchedVamana outperforms FilteredVamana in query efficiency.
+This difference arises from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
+
+	\textcolor{violet}{ACORN generally performs poorly, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
+Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.}
+
+	Among all methods, vector database systems (PASE, VBASE, Milvus) exhibit the worst performance.
+These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
+Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
+
+	\textit{Multi-Thread Search.}
+	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, \textcolor{violet}{the performance distribution of algorithms remains largely unchanged except for Puck, with UNG continuing to maintain the best performance.
+Puck shows significant performance improvement under multi-threading.}
+
+	%	\textit{Single-Thread Search.}  
+	%	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under full-recall conditions (recall = 1), search often requires traversing larger candidate sets or deeper graph paths, leading to increased computational cost and a sharp QPS drop for most methods.
 Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
@@
 CAPS leverages multi-level spatial partitioning and attribute filtering to efficiently explore sparse spaces, whereas UNG relies on structured attribute organization, which limits its adaptability to sparse high-dimensional distributions.
-
-	NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets.
+	%	
+	%	NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets.
 This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.
@@
 The difference arises from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
-
-	Among all methods, vector database systems (PASE, VBASE, Milvus) perform the worst.
+	%	
+	%	Among all methods, vector database systems (PASE, VBASE, Milvus) perform the worst.
 These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
 Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
-
-	\textit{Multi-Thread Search.}
-	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance. 
-	%Puck performs well on large-scale datasets, but its performance degrades on small datasets.
+	%	
+	%	\textit{Multi-Thread Search.}
+	%	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance. 
+	%	%Puck performs well on large-scale datasets, but its performance degrades on small datasets.
 Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets.
-	Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization.
+	%	Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization.
 CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
 The vector distribution of the dataset affects the construction of its partitioned index.
-	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
+	%	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
 Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.

### 2025-07-22 VLDB2026/main.tex
Update main.tex

--- 2025-07-22 VLDB2026/main.tex
@@
 The index sizes of other methods show moderate variation.
-Among these, Faiss generates slightly smaller indexes due to its efficient index design.
+Among these, \underline{Faiss generates slightly smaller indexes due to its efficient index design}.
 
@@
 	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
-CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping.
+CAPS shows a slight performance decline \underline{due to the increased query overhead caused by excessive} attribute-based grouping.
 In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.

### 2025-07-22 VLDB2026/main.tex
Update main.tex

@@
 In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
-2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs.
-3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness.
+2) The complexity of StitchedVamana increases \underline{because data points may duplicate across} \underline{multiple subgraphs}.
+3) \underline{The fusion distance of NHQ exhibits sensitivity} \underline{to the number of attributes}, which degrades its effectiveness.
 4) UNG has poor performance because large number of entry points that need to be traversed.

### 2025-07-22 VLDB2026/main.tex
Update main.tex
1

@@
 	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths.
-This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods.
+This leads to increased computational cost and a sharp QPS \sout{(queries per second)} drop for most methods.
 Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The closer the four curves (corresponding to the four distributions) in the figure approach each other, the less the algorithm is affected by attribute distributions.
-Conversely, the farther they diverge, the more significant the impact of attribute distributions on the algorithm becomes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+\textcolor{cyan}{The proximity of the four curves (representing different attribute distributions) in the figure reflects the algorithm's sensitivity to distributional variations.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
+Conversely, greater divergence among the curves indicates higher distributional dependence.
+Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.

### 2025-07-22 Revision/response.tex
Update response.tex
up

@@
 \noindent
-	\textbf{Response:}
+\textbf{Response:} Thank you very much for your suggestions.
+Ensuring the readability of the figures is indeed crucial.
+For performance under different attribute distributions(Figure 8), to illustrate how different algorithms are affected by varying attribute distributions, we have added robustness indicators (Strong and Weak) in the figure.
+For performance under different attribute selectivity(Figure 10), to reflect the performance differences of each algorithm under varying attribute selectivities, we have added performance rankings for each algorithm across different selectivity levels in the figure.
+This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
+We have revised the manuscript accordingly.
+
+\textcolor{blue}{"The proximity of the four curves (representing different attribute distributions) in the figure reflects the algorithm's sensitivity to distributional variations.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
+Conversely, greater divergence among the curves indicates higher distributional dependence.
+Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes."} (Please see Section 4.2.3, highlighted in blue in the revised manuscript)
 
@@
 \textbf{WIT-Real dataset:} We used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extracted the language type and the length of the \texttt{context\_page\_description} field as real attributes, and used them for range filtering.
+
 %%%%%%%%%%%%%%%%%%%%%% R5 %%%%%%%%%%%%%%%%%%%%%%
+
 \myfbox{
@@
 \textbf{Response:} 
-Thank you for your suggestion! We add relevant experiments conducted on different servers. Please refer to the response MR.R4 for more details.
+Thank you for your suggestion! We add relevant experiments conducted on different servers in Section 4.2.4. Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-22 VLDB2026/main.tex
change

@@
 		\multicolumn{2}{|l|}{\textbf{RF}}             & N & N & N & N & Y & N & N & Y & Y & Y & Y & Y \\ \hline
-		\multicolumn{2}{|l|}{\textbf{Dynamic Insert}} & N & Y & N & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Dynamic Insert}} & N & Y & N & Y & Y & Y & Y & Y & N & Y & Y & N \\ \hline
 		\multicolumn{2}{|l|}{\textbf{Multi Thread}}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
@@
 However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB).
-At the same time, we can see that some algorithms (e.g., SeRF, ACORN-1) perform even worse than the VBASE database, which indicates that they do not adapt well to large-scale dataset scenarios.
-Although Milvus has a low QPS, it can achieve a recall of 1 with an excellent memory footprint of around 80GB}.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms.}.
 

### 2025-07-22 VLDB2026/main.tex
Update main.tex

@@
 Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
-In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
+In contrast, Faiss, FilteredVamana, NHQ, and VBASE show notable sensitivity.
 
@@
 
-	In contrast, VBASE exhibits the weakest robustness.
-As a post-filtering system, it performs significantly better under uniform distributions but degrades under long-tailed, normal, and power-law distributions.
-This degradation stems from the low selectivity of certain attributes in the last 3 distributions, which increases unnecessary distance computations, thus reducing overall efficiency.
+	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency.
+However, its performance declines under power-law and normal distributions: power-law distributions cause excessive concentration of popular labels and fragmentation of niche labels, disrupting search path connectivity, while normal distributions produce ambiguous graph structures due to label frequency similarities, leading to search divergence.
+The search performance of VBASE exhibits a direct dependence on attribute selectivity.
+As selectivity decreases, search speed declines.
+Notably, only uniform distribution maintains sufficient selectivity among the tested cases; the other three distributions consistently show low selectivity levels that significantly degrade VBASE's operational efficiency.}
 

### 2025-07-22 VLDB2026/main.tex
Update main.tex

--- 2025-07-22 VLDB2026/main.tex
@@
 	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths.
-This leads to increased computational cost and a sharp QPS \sout{(queries per second)} drop for most methods.
+This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods.
 Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
@@
 	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
-CAPS shows a slight performance decline \underline{due to the increased query overhead caused by excessive} attribute-based grouping.
+CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping.
 In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction.
-2) The complexity of StitchedVamana increases \underline{because data points may duplicate across} \underline{multiple subgraphs}.
-3) \underline{The fusion distance of NHQ exhibits sensitivity} \underline{to the number of attributes}, which degrades its effectiveness.
+2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs.
+3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness.
 4) UNG has poor performance because large number of entry points that need to be traversed.
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the four curves (representing different attribute distributions) in the figure reflects the algorithm's sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
-Conversely, greater divergence among the curves indicates higher distributional dependence.
-Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+\textcolor{cyan}{The closer the four curves (corresponding to the four distributions) in the figure approach each other, the less the algorithm is affected by attribute distributions.
+Conversely, the farther they diverge, the more significant the impact of attribute distributions on the algorithm becomes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
@@
 	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
+	\textcolor{violet}{On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
+The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
+We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level.
+Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}
 
@@
 
+	\begin{table}[t]
+		\centering
+		\caption{Algorithm Recommendation per Scenario}
+		% 移除 \resizebox 和它对应的外层大括号
+		% 现在字体大小命令直接作用于 tabular 环境
+		\fontsize{5pt}{6pt}\selectfont % 字体大小设置为 5pt
+		\begin{tabular}{|c|c|c|c|c|}
+			\hline
+			\textbf{Algorithm} & \textbf{CT} & \textbf{IS} & \textbf{BPM} & \textbf{SPM}\\
+
+			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
+			\hline
+			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
+			\hline
+			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
+			\hline
+			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
+			\hline
+			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
+			\hline
+			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
+			\hline
+			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
+			\hline
+			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
+			\hline
+		\end{tabular}
+		\label{tab:algo_scenarios}
+	\end{table}
+
 	\subsection{Range Filtering}

### 2025-07-22 Revision/response.tex

@@
 \noindent
-\textbf{Response:} Thank you very much for your suggestions.
+\textbf{Response:} Thanks for the suggestion!
 Ensuring the readability of the figures is indeed crucial.
+We modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
+
 For performance under different attribute distributions(Figure 8), to illustrate how different algorithms are affected by varying attribute distributions, we have added robustness indicators (Strong and Weak) in the figure.
+This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
 For performance under different attribute selectivity(Figure 10), to reflect the performance differences of each algorithm under varying attribute selectivities, we have added performance rankings for each algorithm across different selectivity levels in the figure.

### 2025-07-22 Revision/response.tex
Update response.tex

@@
 \noindent
-\textbf{Response:} Thanks for the suggestion!
+\textbf{Response:} We sincerely appreciate your valuable suggestions, which provide meaningful improvements to our work.
 Ensuring the readability of the figures is indeed crucial.
 We modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
+We have revised the manuscript accordingly.
+(Please see Section 4.2.3, highlighted in blue in the revised manuscript)
 
-For performance under different attribute distributions(Figure 8), to illustrate how different algorithms are affected by varying attribute distributions, we have added robustness indicators (Strong and Weak) in the figure.
+For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we have added robustness indicators (Strong and Weak) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
-For performance under different attribute selectivity(Figure 10), to reflect the performance differences of each algorithm under varying attribute selectivities, we have added performance rankings for each algorithm across different selectivity levels in the figure.
+As shown in Figure\ref{fig:attribute_distribution} below.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{fig/attribute_distribution.png}
+	\caption{}
+	\label{fig:attribute_distribution}
+\end{figure}
+
+For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we have added performance rankings for each algorithm across different selectivity levels in the figure.
 This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
-We have revised the manuscript accordingly.
+As shown in Figure\ref{fig:attribute_selectivity} below.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{fig/attribute_selectivity.png}
+	\caption{}
+	\label{fig:attribute_selectivity}
+\end{figure}
 
@@
 Conversely, greater divergence among the curves indicates higher distributional dependence.
-Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes."} (Please see Section 4.2.3, highlighted in blue in the revised manuscript)
+Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes."}
 
@@
 \textbf{Response:} 
-We sincerely apologize for the misuse of notation in Definition 2.3. This has been corrected in the revised version. Thank you for pointing it out.
+We sincerely apologize for the misuse of notation in Definition 2.3.
+Thank you for pointing it out.
+This has been corrected in the revised version.
+(Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript)
 
@@
 Instead, we have added the corresponding URLs in footnotes on the relevant pages throughout the paper.
+(Please see the relevant footnotes in Section 3 in the revised manuscript)
 

### 2025-07-22 VLDB2026/main.tex
Update main.tex

--- 2025-07-22 VLDB2026/main.tex
@@
 
-		Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
+		Let \( D = \{(v_1, \textcolor{cyan}{a}_1), \ldots, (v_n, \textcolor{cyan}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
 Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).

### 2025-07-22 VLDB2026/main.tex
Update main.tex

@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{red}{We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
 Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.

### 2025-07-22 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
+That's a great suggestion.
+In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors. Please see section 4.2.4.
 
-\textcolor{blue}{"We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
+\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
 Compared with the experimental results on the original server (as shown in Figure 4d), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods."}
+
 %%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-22 Revision/response.tex
update

--- 2025-07-22 Revision/response.tex
@@
 
+\textcolor{blue}{
+	"Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.
+It should be noted that, during range filtering, due to the limitations of some algorithms, we uniformly sorted the vectors according to the query attribute."
+}
 %%%%%%%%%%%%%%%%%%%%%% R5 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-By incorporating the YT-Audio-Real and WIT-Real datasets with their respective real attributes, we believe our experimental study now better reflects real-world application scenarios, and, as you suggested, allows for a more comprehensive and meaningful evaluation of hybrid query functionality.
+We have revised the manuscript accordingly.
+(Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.) Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
 

### 2025-07-22 VLDB2026/main.tex
update

--- 2025-07-22 VLDB2026/main.tex
@@
 
-		Let \( D = \{(v_1, \textcolor{cyan}{a}_1), \ldots, (v_n, \textcolor{cyan}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
+		Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
 Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).
@@
 		\multicolumn{2}{|l|}{\textbf{RF}}             & N & N & N & N & Y & N & N & Y & Y & Y & Y & Y \\ \hline
-		\multicolumn{2}{|l|}{\textbf{Dynamic Insert}} & N & Y & N & Y & Y & Y & Y & Y & N & Y & Y & N \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Dynamic Insert}} & N & Y & N & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
 		\multicolumn{2}{|l|}{\textbf{Multi Thread}}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the four curves (representing different attribute distributions) in the figure reflects the algorithm's sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
-Conversely, greater divergence among the curves indicates higher distributional dependence.
-Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
-In contrast, Faiss, FilteredVamana, NHQ, and VBASE show notable sensitivity.
+\textcolor{cyan}{The closer the four curves (corresponding to the four distributions) in the figure approach each other, the less the algorithm is affected by attribute distributions.
+Conversely, the farther they diverge, the more significant the impact of attribute distributions on the algorithm becomes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
 
@@
 
-	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency.
-However, its performance declines under power-law and normal distributions: power-law distributions cause excessive concentration of popular labels and fragmentation of niche labels, disrupting search path connectivity, while normal distributions produce ambiguous graph structures due to label frequency similarities, leading to search divergence.
-The search performance of VBASE exhibits a direct dependence on attribute selectivity.
-As selectivity decreases, search speed declines.
-Notably, only uniform distribution maintains sufficient selectivity among the tested cases; the other three distributions consistently show low selectivity levels that significantly degrade VBASE's operational efficiency.}
+	In contrast, VBASE exhibits the weakest robustness.
+As a post-filtering system, it performs significantly better under uniform distributions but degrades under long-tailed, normal, and power-law distributions.
+This degradation stems from the low selectivity of certain attributes in the last 3 distributions, which increases unnecessary distance computations, thus reducing overall efficiency.
 
@@
 
-	\begin{table}[t]
-		\centering
-		\caption{Algorithm Recommendation per Scenario}
-		% 移除 \resizebox 和它对应的外层大括号
-		% 现在字体大小命令直接作用于 tabular 环境
-		\fontsize{5pt}{6pt}\selectfont % 字体大小设置为 5pt
-		\begin{tabular}{|c|c|c|c|c|}
-			\hline
-			\textbf{Algorithm} & \textbf{CT} & \textbf{IS} & \textbf{BPM} & \textbf{SPM}\\
-
-			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
-			\hline
-			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
-			\hline
-			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
-			\hline
-			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
-			\hline
-			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
-			\hline
-			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
-			\hline
-			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
-			\hline
-			ACORN-1 & Puck, UNG & iRange & iRange & iRange\\[1pt]
-			\hline
-		\end{tabular}
-		\label{tab:algo_scenarios}
-	\end{table}
-
 	\subsection{Range Filtering}
@@
 However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB).
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms.}.
+At the same time, we can see that some algorithms (e.g., SeRF, ACORN-1) perform even worse than the VBASE database, which indicates that they do not adapt well to large-scale dataset scenarios.
+Although Milvus has a low QPS, it can achieve a recall of 1 with an excellent memory footprint of around 80GB}.
 

### 2025-07-22 Revision/response.tex
1

@@
 \textbf{Response:} 
-Thank you for your suggestion!
+Thank you for your suggestion.
 Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the feature of whether to support disk for each algorithm in Table 1.
@@
 
-Due to space limitations and the fact that only one method supports disk-based execution, we provide the breakdown of I/O and CPU costs for disk-based methods in the following analysis.
-To this end, we conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
+We conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
+(1) SSD-based FilteredDiskANN (original disk-based method);
+(2) FilteredVamana (memory-based method);
+(3) StitchedVamana (memory-based method).
 
-\begin{itemize}
-	\item SSD-based FilteredDiskANN (original disk-based method)
-	\item FilteredVamana (memory-based method)
-	\item StitchedVamana (memory-based method)
-\end{itemize}
+%\begin{itemize}
+%	\item SSD-based FilteredDiskANN (original disk-based method)
+%	\item FilteredVamana (memory-based method)
+%	\item StitchedVamana (memory-based method)
+%\end{itemize}
 
@@
 \textbf{ Key Observations:}
-
 Latency-Recall Tradeoff:
@@
 \textbf{In-memory Methods:}
-
 FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
@@
 Nevertheless, it consistently supports 90\%+ Recall@10 across diverse datasets, as shown in our evaluations.
+
+\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.
 

### 2025-07-22 Revision/response.tex
1

@@
 \textbf{Response:}
+
 Thank you for your suggestion.
-We are deeply aware of this deficiency, so we added the search peak memory usage of each algorithm in \textcolor{blue}{Section 4.2.1} of attribute filtering and \textcolor{blue}{Section 4.3.1}  of range filtering, and carefully analyzed the reasons.
+We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{fig/searchMem/label_memory_comparison.pdf}
+	\caption{attribute filtering search peak memory}
+	\label{fig:attribute filtering search peak memory}
+\end{figure}
 
-\textit{\textbf{ \textcolor{blue}{" Search peak memory.}}}
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{fig/searchMem/range_memory_comparison.pdf}
+	\caption{range filtering search peak memory}
+	\label{fig:range filtering search peak memory}
+\end{figure}
 
-\textcolor{blue}{As shown in Figure, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower."}
+For attribute filtering, please see section 4.2.1.
 
-\textit{\textbf{ \textcolor{blue}{"Search peak memory.}}}
+\textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:attribute filtering search peak memory} that the peak memory usage of each algorithm during search does not differ significantly.
+Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower."}
 
-\textcolor{blue}{As for the Search peak memory usage, we can find from the Figure that it is basically consistent with the Build peak memory usage trend.
+For range filtering, please see section 4.3.1.
+
+\textcolor{blue}{"As for the Search peak memory usage, we can find from the Figure ~\ref{fig:range filtering search peak memory} that it is basically consistent with the Build peak memory usage trend.
 The algorithm needs to load the complete index into memory during search.

### 2025-07-22 Revision/response.tex
Update response.tex
change multimodal
修改多模态相关部分回复格式

--- 2025-07-22 Revision/response.tex
@@
 \noindent
-\textbf{Response:} We believe this is a very good suggestion.
-Accordingly, we have added more complex multi-modal dataset experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4 in our revised paper.
-In the original version, we used the commonly adopted text2image dataset from existing multi-modal ANN algorithms, where the base vectors are images, but the queries are text.
-This setting naturally introduces a modality gap, and achieving good performance on this dataset usually requires algorithms to be more robust.
+\textbf{Response:} We believe this is an excellent suggestion.
+In fact, in the initial version of our paper, we used the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms.
+In this dataset, the base vectors are images, while the query set consists of texts, resulting in a modality gap between the two.
+Achieving good performance on such a dataset often requires the algorithm to demonstrate stronger robustness.
+\textbf{(Please refer to the last paragraph of Section 4.2.3 and the green highlighted part in Section 4.3.3.)}
 
-To further enrich the complexity of multi-modal queries, we additionally selected 500,000 text vectors and 500,000 image vectors to form a mixed base dataset, and we similarly selected 5,000 text vectors and 5,000 image vectors as query vectors.
-We then conducted both attribute filtering and range queries on this multi-modal dataset by combining text and image queries.
-This allows us to further analyze the robustness of the algorithms.
-The related experimental results are presented in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
+To further enrich the evaluation of complex multimodal queries, we have added new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
+Specifically, we constructed a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
+We then performed both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms.
+The corresponding experimental results are presented in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.
 
-As for complex query types involving both attribute and range filters, to the best of our knowledge, there is currently no ANN algorithm (except for general-purpose systems like Milvus and Faiss) that can support both types of filtering simultaneously.
-For example, ACORN needs to build separate indices for each scenario and cannot support attribute and range filtering at the same time.
-Therefore, in our study, we chose to consider these query types separately, rather than jointly.
+As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality.
+For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously.
+Therefore, we did not consider this type of complex query in our experiments but instead studied the two query types separately.
+\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
+}
 

### 2025-07-22 VLDB2026/main.tex
1
change multimodal
修改多模态相关部分回复格式

@@
 Notably, although vanilla Faiss performs worse on SIFT1M compared to Enron dataset, Faiss+HQI\_Batch outperforms on SIFT1M.
-Because batch optimization in HQI reduces query overhead and increases throughput.
-
-	Most algorithms exhibit the worst performance on the OOD dataset Text2Image.
+Because batch optimization in HQI reduces query overhead and increases throughput.	}
+
+	\textcolor{green}{Most algorithms exhibit the worst performance on the OOD dataset Text2Image.
 However, ACORN, UNG, and FilteredVamana show relatively stable performance on Text2Image.
@@
 
-	\sout{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
+	\textcolor{green}{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
 As shown in Figure~\ref{fig:exp_8_3}, most methods perform worst on the Text2Image dataset.
 This is because OOD queries make the $k$-nearest neighbor distribution more sparse.
-As a result, the search needs to visit more nodes, which leads to an exponential growth in the search space and a sharp drop in efficiency.
-
-	WinFilter shows the worst performance on the WIT dataset.
+As a result, the search needs to visit more nodes, which leads to an exponential growth in the search space and a sharp drop in efficiency.}
+
+	\sout{WinFilter shows the worst performance on the WIT dataset.
 This suggests that its performance is sensitive to the data dimensionality.

### 2025-07-22 Revision/response.tex

@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/attribute_distribution.png}
+	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
 	\caption{}
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/attribute_selectivity.png}
+	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
 	\caption{}

### 2025-07-22 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} 
-
 Thank you for your suggestion.
@@
 \textbf{Response:} 
+Thank you for your valuable suggestion regarding our experiments.
+In Section 4.2.4, we add experiments on the Deep100M dataset.
+The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset.
+In particular, StitchedVamana performs poorly on Deep100M.
+Please see section 4.2.4.
+
+\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
+The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
+We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level.
+Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
 
@@
 \textbf{Response:} 
+Thank you for your feedback. We improve the readability of the two figures in Section 4.2.3, and please see Meta-Review R1 for details.
 

### 2025-07-22 VLDB2026/main.tex
change

--- 2025-07-22 VLDB2026/main.tex
@@
 	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while \underline{the database's peak memory usage} is comparatively lower.}
+Among them, CAPS and NHQ have relatively higher peak memory usage, while \underline{the peak memory usage of database} is comparatively lower.}
 
@@
 		%\vspace{0.1cm}
-		\begin{subfigure}[t]{0.332\columnwidth}
+		\begin{subfigure}[t]{0.507\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}[t]{0.315\columnwidth}
+		\begin{subfigure}[t]{0.48\columnwidth}
+			\centering
+			\captionsetup{font=small}
+			\includegraphics[width=\linewidth]{figures/exp/attribute_multimodel_1.pdf}
+			\caption{\footnotesize MultiModel}
+			\label{fig:MultiModel}
+		\end{subfigure}
+
+		\begin{subfigure}[t]{0.507\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}[t]{0.315\columnwidth}
+		\begin{subfigure}[t]{0.48\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}[t]{0.315\columnwidth}
+		\begin{subfigure}[t]{0.48\columnwidth}
+			\centering
+			\captionsetup{font=small}
+			\includegraphics[width=\linewidth]{figures/exp/range_multimodel_1.pdf}
+			\caption{\footnotesize MultiModel}
+			\label{fig:MultiModel range}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.507\columnwidth}
 			\centering

### 2025-07-22 VLDB2026/main.tex
1

--- 2025-07-22 VLDB2026/main.tex
@@
 
-		\caption{Comparison of AF-ANN search algorithms}
+		\caption{Comparison of AF-ANN and RF-ANN search algorithms}
 		\small
@@
 		\multicolumn{2}{|l|}{\textbf{Multi Thread}}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
-		\multicolumn{2}{|l|}{\textbf{Disk Storage Support}}           &N  & Y& N & N & N & N & N & N & N & N & N & N \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Disk Support}}           &N  & Y& N & N & N & N & N & N & N & N & N & N \\ \hline
 		\multicolumn{2}{|l|}{\textbf{Base}}           & Graph & Graph & Graph & IVF & Graph & Graph & IVF & Graph & Graph & Graph & Graph & Graph \\ \hline
@@
 				\vspace{0.1cm}
+				\textcolor{orange}{\textsuperscript{AF} Attribue-filtering,}
+				\textcolor{orange}{\textsuperscript{RF} Range-filtering,}
+				\textcolor{orange}{Filtered: FilteredVamana,}
+				\textcolor{orange}{Stitched: StitchedVamana,}
+				\textcolor{orange}{Win: WinFilter,}
 				\textsuperscript{A} Post-filtering, 
@@
 				\textsuperscript{N} Unsupport. 
-				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
 				\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
@@
 				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search,
+				\textcolor{orange}{\textit{Disk Support} indicates whether the algorithm supports disk storage,}
+				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm.
 		\end{minipage}}

### 2025-07-22 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} 
-
+Thank you for your suggestion. We add experiments on the Deep100M dataset in Section 4.2.4 and observed some pitfalls. For more details, please refer to our response to Meta Review R7.
 %%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
@@
 }
-
 \noindent
 \textbf{Response:} 
+Thank you for pointing this out.
+We agree that the initial explanations accompanying the performance results were not sufficiently detailed in highlighting the strengths and weaknesses of the compared algorithms.
+We conduct a more in-depth analysis of the reasons behind certain behaviors observed in the experimental results.
+The specific revisions are as follows:
+%下面写每个修改过的理由
+%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
 \myfbox{

### 2025-07-22 Revision/response.tex
1

--- 2025-07-22 Revision/response.tex
@@
 \textbf{Response:} 
-Thank you for your suggestion!
-The paper [49] is a comprehensive survey and evaluation of graph structure approximate nearest neighbor search algorithms.
-Our paper extends this to a more complex "hybrid query" scenario and evaluates approximate search algorithms that combine vector similarity and attribute filtering/range filtering.
-Since hybrid queries are developed based on ANNs, we refer to the metrics and evaluation architectures of different methods proposed in this paper.
+Thank you for pointing this out.
+Both paper [49] and our paper are benchmarks.
+Paper [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor search algorithms.
+Our paper is the first benchmark to evaluate hybrid queries.
+Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper.
+We realize that we did not clearly explain the difference between our paper and the cited paper, so we added a description in the introduction, please see section XXX.
+\textcolor{blue}{""}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion!
-We have carefully searched and found no papers describing the application of attribute distribution and attribute selectivity.
-However, the real-world application scenarios of attribute distribution and attribute selectivity are indeed very extensive.
-For attribute distribution, the label attributes of many recommended application scenarios in reality conform to the power-law distribution.
-For attribute selectivity: For example, if you need to query data in which an attribute accounts for a very small proportion of the total, choosing a more advantageous algorithm will greatly improve the search effect.
-There are also databases with actual applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we will add more comprehensive citations in the paper.
+Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
+In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
+For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution.
+For attribute selectivity: For example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
+There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
+For the two parts you suggested, we will add more comprehensive references in the paper.
+Please see section 1.1.
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[12], and attribute  selectivity [46,51] significantly impact algorithm performance."}
 

### 2025-07-22 Revision/response.tex
Update response.tex

--- 2025-07-22 Revision/response.tex
@@
 \textbf{Response:} 
+Thank you for your suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
+
+To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
+%下面放那个优劣势表
 

### 2025-07-22 VLDB2026/main.tex
Update main.tex

@@
 
-	In contrast, VBASE exhibits the weakest robustness.
-As a post-filtering system, it performs significantly better under uniform distributions but degrades under long-tailed, normal, and power-law distributions.
-This degradation stems from the low selectivity of certain attributes in the last 3 distributions, which increases unnecessary distance computations, thus reducing overall efficiency.
+	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency.
+However, its performance declines under power-law and normal distributions: power-law distributions cause excessive concentration of popular labels and fragmentation of niche labels, disrupting search path connectivity, while normal distributions produce ambiguous graph structures due to label frequency similarities, leading to search divergence.
+	Under the power-law distribution, when the NHQ algorithm constructs an index based on fusion distance, points corresponding to high-frequency attribute values make the graph connections extremely dense, while points corresponding to low-frequency attribute values tend to become isolated due to sparse connections.
+This extreme imbalance in connectivity severely distorts the graph's structure, ultimately significantly impairing the overall performance of the algorithm.
+	The search performance of VBASE exhibits a direct dependence on attribute selectivity.
+As selectivity decreases, search speed declines.
+Notably, only uniform distribution maintains sufficient selectivity among the tested cases; the other three distributions consistently show low selectivity levels that significantly degrade the operational efficiency of VBASE.}
 

### 2025-07-22 Revision/response.tex
Update response.tex

--- 2025-07-22 Revision/response.tex
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
+	\includegraphics[width=\linewidth]{fig/attribute_distribution.png}
 	\caption{}
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
+	\includegraphics[width=\linewidth]{fig/attribute_selectivity.png}
 	\caption{}
@@
 \noindent
-\textbf{Response:} We believe this is an excellent suggestion.
-In fact, in the initial version of our paper, we used the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms.
-In this dataset, the base vectors are images, while the query set consists of texts, resulting in a modality gap between the two.
-Achieving good performance on such a dataset often requires the algorithm to demonstrate stronger robustness.
-\textbf{(Please refer to the last paragraph of Section 4.2.3 and the green highlighted part in Section 4.3.3.)}
+\textbf{Response:} We believe this is a very good suggestion.
+Accordingly, we have added more complex multi-modal dataset experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4 in our revised paper.
+In the original version, we used the commonly adopted text2image dataset from existing multi-modal ANN algorithms, where the base vectors are images, but the queries are text.
+This setting naturally introduces a modality gap, and achieving good performance on this dataset usually requires algorithms to be more robust.
 
-To further enrich the evaluation of complex multimodal queries, we have added new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
-Specifically, we constructed a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
-We then performed both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms.
-The corresponding experimental results are presented in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.
+To further enrich the complexity of multi-modal queries, we additionally selected 500,000 text vectors and 500,000 image vectors to form a mixed base dataset, and we similarly selected 5,000 text vectors and 5,000 image vectors as query vectors.
+We then conducted both attribute filtering and range queries on this multi-modal dataset by combining text and image queries.
+This allows us to further analyze the robustness of the algorithms.
+The related experimental results are presented in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
 
-As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality.
-For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously.
-Therefore, we did not consider this type of complex query in our experiments but instead studied the two query types separately.
-\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
-}
+As for complex query types involving both attribute and range filters, to the best of our knowledge, there is currently no ANN algorithm (except for general-purpose systems like Milvus and Faiss) that can support both types of filtering simultaneously.
+For example, ACORN needs to build separate indices for each scenario and cannot support attribute and range filtering at the same time.
+Therefore, in our study, we chose to consider these query types separately, rather than jointly.
 
@@
 
-\textbf{YT-Audio-Real dataset:} For this dataset, we utilized the URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as real attributes, and used view counts as the attribute for range filtering experiments.
+\textbf{YT-Audio-Real dataset:} For this dataset, we utilized the URLs provided by the YouTube8M dataset to crawl corresponding video categories and view counts as real attributes, using \textbf{video categories as attributes for attribute filtering experiments} and \textbf{view counts as attributes for range filtering experiments}, respectively.
 
-\textbf{WIT-Real dataset:} We used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extracted the language type and the length of the \texttt{context\_page\_description} field as real attributes, and used them for range filtering.
+\textbf{WIT-Real dataset:} We used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extracted the language type and the length of the \texttt{context\_page\_description} field as real attributes, applying them in both attribute filtering and range filtering experiments.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion.
+Thank you for your suggestion!
 Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the feature of whether to support disk for each algorithm in Table 1.
@@
 
-We conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
-(1) SSD-based FilteredDiskANN (original disk-based method);
-(2) FilteredVamana (memory-based method);
-(3) StitchedVamana (memory-based method).
+Due to space limitations and the fact that only one method supports disk-based execution, we provide the breakdown of I/O and CPU costs for disk-based methods in the following analysis.
+To this end, we conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
 
-%\begin{itemize}
-%	\item SSD-based FilteredDiskANN (original disk-based method)
-%	\item FilteredVamana (memory-based method)
-%	\item StitchedVamana (memory-based method)
-%\end{itemize}
+\begin{itemize}
+	\item SSD-based FilteredDiskANN (original disk-based method)
+	\item FilteredVamana (memory-based method)
+	\item StitchedVamana (memory-based method)
+\end{itemize}
 
@@
 \textbf{ Key Observations:}
+
 Latency-Recall Tradeoff:
@@
 \textbf{In-memory Methods:}
+
 FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
@@
 Nevertheless, it consistently supports 90\%+ Recall@10 across diverse datasets, as shown in our evaluations.
-
-\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.
 
@@
 Thank you for your suggestion.
-We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\linewidth]{fig/searchMem/label_memory_comparison.pdf}
-	\caption{attribute filtering search peak memory}
-	\label{fig:attribute filtering search peak memory}
-\end{figure}
+We are deeply aware of this deficiency, so we added the search peak memory usage of each algorithm in \textcolor{blue}{Section 4.2.1} of attribute filtering and \textcolor{blue}{Section 4.3.1}  of range filtering, and carefully analyzed the reasons.
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\linewidth]{fig/searchMem/range_memory_comparison.pdf}
-	\caption{range filtering search peak memory}
-	\label{fig:range filtering search peak memory}
-\end{figure}
+\textit{\textbf{ \textcolor{blue}{" Search peak memory.}}}
 
-For attribute filtering, please see section 4.2.1.
+\textcolor{blue}{As shown in Figure, we can find that the peak memory usage of each algorithm during search does not differ significantly.
+Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower."}
 
-\textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:attribute filtering search peak memory} that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower."}
+\textit{\textbf{ \textcolor{blue}{"Search peak memory.}}}
 
-For range filtering, please see section 4.3.1.
-
-\textcolor{blue}{"As for the Search peak memory usage, we can find from the Figure ~\ref{fig:range filtering search peak memory} that it is basically consistent with the Build peak memory usage trend.
+\textcolor{blue}{As for the Search peak memory usage, we can find from the Figure that it is basically consistent with the Build peak memory usage trend.
 The algorithm needs to load the complete index into memory during search.
@@
 \textbf{Response:}
-Thank you for your valuable suggestion regarding our experiments.
-In Section 4.2.4, we add experiments on the Deep100M dataset.
-The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset.
-In particular, StitchedVamana performs poorly on Deep100M.
-Please see section 4.2.4.
-
-\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
-The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
-We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level.
-Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
 
@@
 \textbf{Response:}
-Thank you for your suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
-
-To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
-%下面放那个优劣势表
 
@@
 \textbf{Response:}
-Thank you for your feedback. We improve the readability of the two figures in Section 4.2.3, and please see Meta-Review R1 for details.
 
@@
 \textbf{Response:}
-Thank you for your suggestion. We add experiments on the Deep100M dataset in Section 4.2.4 and observed some pitfalls. For more details, please refer to our response to Meta Review R7.
+
 %%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
@@
 }
+
 \noindent
 \textbf{Response:}
-Thank you for pointing this out.
-We agree that the initial explanations accompanying the performance results were not sufficiently detailed in highlighting the strengths and weaknesses of the compared algorithms.
-We conduct a more in-depth analysis of the reasons behind certain behaviors observed in the experimental results.
-The specific revisions are as follows:
-%下面写每个修改过的理由
+
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
-
 \myfbox{
@@
 \textbf{Response:}
-Thank you for your suggestion!
-We recognize that the original manuscript did not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard Graph-based and IVF-based index structures.
+Thank you for your suggestion.
+We acknowledge that the original manuscript did not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard graph-based and IVF-based index structures.
+We have revised Section 2.2 and added two paragraphs.
+These paragraphs summarize how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures.
 
-To address this, we have revised Section 2.2 to summarize how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures (with detailed implementation provided in Section 3):
+\textcolor{blue}{"Graph-based indexes are widely adopted in Hybrid ANN search algorithms due to their excellent performance.
+To support hybrid queries, existing approaches usually augment the original graph structures by explicitly associating attribute or range information with vertices or edges.
+In attribute filtering, a common approach is to attach attribute metadata to vertices or edges, allowing the traversal process to skip nodes or edges that do not meet the query's attribute conditions (e.g., NHQ, Filtered-DiskANN, ACORN).
+In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges satisfying the range constraints, effectively narrowing down the search space (e.g., SeRF, DSG)."}
 
-For Graph-based indexes, we describe the typical approaches of embedding attribute and range constraints by associating metadata with graph vertices or edges.
-Specifically, attribute filtering (AF) is usually achieved by annotating vertices or edges with attribute information, enabling the traversal algorithm to skip nodes or edges that do not satisfy the query predicates (e.g., NHQ, Filtered-DiskANN, ACORN).
-In contrast, range filtering (RF) typically involves annotating edges with valid attribute intervals so that traversal proceeds only along edges that satisfy the query's range constraints, effectively reducing the search space (e.g., SeRF, DSG).
-
-For IVF-based indexes, we point out that their inherent pre-filtering mechanism naturally supports hybrid query functionality.
-In particular, attribute and range filtering can be implemented by directly excluding irrelevant vectors during intra-cluster distance computations.
-Furthermore, we highlight the hierarchical partitioning approach based on attributes, which further divides clusters into finer-grained sub-partitions, significantly improving filtering efficiency (e.g., CAPS, PUCK).
+\textcolor{blue}{"IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, such as naturally supporting pre-filtering and requiring significantly lower memory consumption and smaller index sizes compared to graph-based indexes.
+With minor modifications, IVF indexes achieve attribute and range filtering by directly excluding vectors that do not meet query constraints through pre-filtering, thus skipping irrelevant vectors during intra-cluster distance computations (e.g., Faiss, Milvus).
+Moreover, clusters can be further partitioned hierarchically based on attributes (hierarchical partitioning), resulting in finer-grained sub-partitions that significantly enhance the efficiency of attribute filtering (e.g., CAPS, PUCK)."}
 

### 2025-07-22 Revision/response.tex

--- 2025-07-22 Revision/response.tex
@@
 \textbf{Response:} 
-Thank you for your suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
+Thank you for your valuable suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
 

### 2025-07-22 Revision/response.tex
change

--- 2025-07-22 Revision/response.tex
@@
 \noindent
-\textbf{Response:} Thank you for your suggestion!
-In real-world applications, there may indeed exist more complex semantic correlations between vectors and their associated attributes or among different attributes themselves.
-To better reflect such scenarios, we introduced two real-world datasets, where both vectors and attributes are derived from actual data.
-For example, in the YouTube dataset, the attributes include video categories and view counts, while in the WIT dataset, the attributes correspond to the language of image descriptions.
-
-We conducted experiments on both datasets and present the performance analysis for various algorithms in \textcolor{blue}{Sections 4.2.2 and 4.3.2}.
-Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.
+\textbf{Response:} I really appreciate your suggestion.
+In real-world applications, vectors and their attributes often have complex relationships.
+To better reflect such scenarios, we have introduced two real-world datasets, which are described in detail in Meta-Review R3.
+Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.(Please see the experimental results in Section 4.2.2 and Section 4.3.2)
 
@@
 \textbf{Response:} 
-Thank you for pointing this out.
-Both paper [49] and our paper are benchmarks.
-Paper [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor search algorithms.
-Our paper is the first benchmark to evaluate hybrid queries.
-Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper.
-We realize that we did not clearly explain the difference between our paper and the cited paper, so we added a description in the introduction, please see section XXX.
-\textcolor{blue}{""}
+Thank you for your suggestion!
+The paper [49] is a comprehensive survey and evaluation of graph structure approximate nearest neighbor search algorithms.
+Our paper extends this to a more complex "hybrid query" scenario and evaluates approximate search algorithms that combine vector similarity and attribute filtering/range filtering.
+Since hybrid queries are developed based on ANNs, we refer to the metrics and evaluation architectures of different methods proposed in this paper.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
-In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
-For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution.
-For attribute selectivity: For example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
-There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we will add more comprehensive references in the paper.
-Please see section 1.1.
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[12], and attribute  selectivity [46,51] significantly impact algorithm performance."}
+Thank you for your suggestion!
+We have carefully searched and found no papers describing the application of attribute distribution and attribute selectivity.
+However, the real-world application scenarios of attribute distribution and attribute selectivity are indeed very extensive.
+For attribute distribution, the label attributes of many recommended application scenarios in reality conform to the power-law distribution.
+For attribute selectivity: For example, if you need to query data in which an attribute accounts for a very small proportion of the total, choosing a more advantageous algorithm will greatly improve the search effect.
+There are also databases with actual applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
+For the two parts you suggested, we will add more comprehensive citations in the paper.
 

### 2025-07-22 Revision/response.tex
Update response.tex

--- 2025-07-22 Revision/response.tex
@@
 \textbf{Response:} 
+Thank you for your valuable suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
+
+To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
+%下面放那个优劣势表
 
@@
 \noindent
-\textbf{Response:} I really appreciate your suggestion.
-In real-world applications, vectors and their attributes often have complex relationships.
-To better reflect such scenarios, we have introduced two real-world datasets, which are described in detail in Meta-Review R3.
-Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.(Please see the experimental results in Section 4.2.2 and Section 4.3.2)
+\textbf{Response:} Thank you for your suggestion!
+In real-world applications, there may indeed exist more complex semantic correlations between vectors and their associated attributes or among different attributes themselves.
+To better reflect such scenarios, we introduced two real-world datasets, where both vectors and attributes are derived from actual data.
+For example, in the YouTube dataset, the attributes include video categories and view counts, while in the WIT dataset, the attributes correspond to the language of image descriptions.
+
+We conducted experiments on both datasets and present the performance analysis for various algorithms in \textcolor{blue}{Sections 4.2.2 and 4.3.2}.
+Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.
 
@@
 \textbf{Response:} 
+Thank you for pointing it out.
 We sincerely apologize for the misuse of notation in Definition 2.3.
-Thank you for pointing it out.
 This has been corrected in the revised version.
@@
 \textbf{Response:} 
-Thank you for the suggestion!
+Thank you for the suggestion.
 Since there are multiple methods, listing all URLs in Section 4.1 would be overwhelming.
-Instead, we have added the corresponding URLs in footnotes on the relevant pages throughout the paper.
+Instead, we add the corresponding URLs in footnotes on the relevant pages throughout the paper.
 (Please see the relevant footnotes in Section 3 in the revised manuscript)

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} 
-Thank you for your suggestion! We add relevant experiments conducted on different servers in Section 4.2.4. Please refer to the response MR.R4 for more details.
+Thank you for your suggestion. We add relevant experiments conducted on different servers in Section 4.2.4. Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:} 
-Thank you for your suggestion! We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
+Thank you for your suggestion. We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion! We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
+Thank you for your suggestion. We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
 
@@
 Since there are multiple methods, listing all URLs in Section 4.1 would be overwhelming.
-Instead, we add the corresponding URLs in footnotes on the relevant pages throughout the paper.
+Instead, in Section 3, we add superscript markers next to each algorithm name and provide the corresponding implementation URLs as footnotes on the same page.
 (Please see the relevant footnotes in Section 3 in the revised manuscript)
@@
 \textbf{Response:} 
-Thank you for your insightful comments!
+Thank you for your insightful comments.
 
@@
 \textbf{Response:} 
-Thank you for the suggestion!
+Thank you for the suggestion.
 We realized that the original wording was somewhat vague and led to confusion among readers.

### 2025-07-23 VLDB2026/main.tex

@@
 		%\vspace{0.1cm}
-		\begin{subfigure}[t]{0.507\columnwidth}
-			\centering
+		\begin{subfigure}[t]{0.98\columnwidth}
+		\centering
+		% First plot for the shared subfigure
+		\includegraphics[width=0.507\linewidth]{figures/exp/attribute_multimodel.pdf}
+		\hfill % Pushes the two plots apart
+		% Second plot for the shared subfigure
+		\includegraphics[width=0.48\linewidth]{figures/exp/attribute_multimodel_1.pdf}
+
+		% Shared caption for the two plots above
 		\captionsetup{font=small}
-			\includegraphics[width=\linewidth]{figures/exp/attribute_multimodel.pdf}
-			\caption{\footnotesize MultiModel}
-			\label{fig:MultiModel}
-		\end{subfigure}	
-		\hfill
-		\begin{subfigure}[t]{0.48\columnwidth}
-			\centering
-			\captionsetup{font=small}
-			\includegraphics[width=\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-			\caption{\footnotesize MultiModel}
-			\label{fig:MultiModel}
+		\caption{MultiModel}
+		\label{fig:MultiModel_range} % A single label for the combined subfigure
 		\end{subfigure}
@@
 
-		\hspace*{5pt}
-		% 放大的图例（占满单栏）
+	% Legend
 	\includegraphics[width=0.98\columnwidth]{figures/exp/range_legend.pdf}
-
-		%\vspace{0.1cm}
+	\vspace{0.2cm} % Added a little space after the legend
+
+	% --- Subfigure (a) containing two plots ---
+	\begin{subfigure}[t]{0.98\columnwidth}
+		\centering
+		% First plot for the shared subfigure
+		\includegraphics[width=0.507\linewidth]{figures/exp/range_multimodel.pdf}
+		\hfill % Pushes the two plots apart
+		% Second plot for the shared subfigure
+		\includegraphics[width=0.48\linewidth]{figures/exp/range_multimodel_1.pdf}
+
+		% Shared caption for the two plots above
+		\captionsetup{font=small}
+		\caption{MultiModel}
+		\label{fig:MultiModel_range} % A single label for the combined subfigure
+	\end{subfigure}
+
+	% --- Subfigure (b) ---
 	\begin{subfigure}[t]{0.507\columnwidth}
 		\centering
+		\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
 		\captionsetup{font=small}
-			\includegraphics[width=\linewidth]{figures/exp/range_multimodel.pdf}
-			\caption{\footnotesize MultiModel}
-			\label{fig:MultiModel range}
+		\caption{Different Computer}
+		\label{fig:Different_Computer_range}
 	\end{subfigure}
 	\hfill
+	% --- Subfigure (c) ---
 	\begin{subfigure}[t]{0.48\columnwidth}
 		\centering
+		\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
 		\captionsetup{font=small}
-			\includegraphics[width=\linewidth]{figures/exp/range_multimodel_1.pdf}
-			\caption{\footnotesize MultiModel}
-			\label{fig:MultiModel range}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.507\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
-			\caption{\footnotesize Different Computer}
-			\label{fig:Different Computer range}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.48\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
-			\caption{\footnotesize Big Dataset}
-			\label{fig:Big Dataset range}
-		\end{subfigure}
-
-		\caption{\textcolor{red}TrinityExtension——Range}
+		\caption{Big Dataset}
+		\label{fig:Big_Dataset_range}
+	\end{subfigure}
+
+	\caption{\textcolor{red}{TrinityExtension——Range}}
 	\label{fig:TrinityExtension——Range}

### 2025-07-23 VLDB2026/main.tex
Update main.tex

@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on the same server configuration, with results presented in Figure~\ref{fig:Different Computer range}.
-When compared with the original server's experimental results shown in Figure~\ref{fig:exp_8_2}b, our findings remain consistent with those reported in Section 4.2.4.
+	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
+When compared with the original server's experimental results shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big Dataset range}, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB).
@@
 	\textcolor{blue}{
-	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModel range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModel_range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
 As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.

### 2025-07-23 Revision/response.tex
Update response.tex
change parameter part

--- 2025-07-22 Revision/response.tex
@@
 \textbf{Response:}
+
 Thank you for your suggestion.
@@
 \textbf{Response:}
-Thank you for your valuable suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
-
-To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
-%下面放那个优劣势表
 
@@
 \textbf{Response:} 
+We sincerely apologize for the misuse of notation in Definition 2.3.
 Thank you for pointing it out.
-We sincerely apologize for the misuse of notation in Definition 2.3.
 This has been corrected in the revised version.
@@
 \textbf{Response:} 
-Thank you for the suggestion.
+Thank you for the suggestion!
 Since there are multiple methods, listing all URLs in Section 4.1 would be overwhelming.
-Instead, we add the corresponding URLs in footnotes on the relevant pages throughout the paper.
+Instead, we have added the corresponding URLs in footnotes on the relevant pages throughout the paper.
 (Please see the relevant footnotes in Section 3 in the revised manuscript)
@@
 
-We have elaborated on the scalability implementations of various algorithms on the 100-million-scale Deep dataset in \textcolor{blue}{ Section XXX of our paper.
-We also provide a comprehensive analysis of their performance on large-scale datasets.}
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to MR.R7.
 
@@
 
-During index construction, for datasets where recommended parameters were explicitly provided in the original papers of the respective algorithms, we strictly adhered to those settings..
-For the remaining datasets, we used the default parameters provided in their open-source code repositories.
-All detailed configurations of experimental parameters are publicly available in our code repository.
+For datasets with recommended parameters provided in the original papers, we directly used those recommended settings.
+For other datasets, we selected the parameter combinations that performed best through empirical evaluation.
+All parameters used in the experiments are available in our public code repository.
 
- Our experimental results show that on datasets where recommended parameters were used, the relative performance ranking of the algorithms did not change significantly.
-During the search phase, we obtained performance data at different Recall and QPS by adjusting the search parameters.
-These search parameters covered a wide range to ensure we could obtain comprehensive experimental result curves.
+According to our experimental results, for datasets using the recommended parameters, the algorithm rankings remained unchanged.
+During the search process, we adjusted the search parameters to obtain different Recall and QPS values.
+The search parameters typically span a wide range of values to ensure the completeness of the experimental results.
 
- Given the large number of datasets and algorithms involved, to maintain the conciseness of the paper, we did not list the detailed running parameters for all algorithms and datasets in the main text.
-These specific parameters can all be found in our code repository.
-For algorithms that are sensitive to specific parameters, we have highlighted them in the relevant sections of the paper.
+Due to the large number of algorithms and datasets involved, we did not include all parameter settings in the paper because of space limitations.
+The detailed parameter configurations can be found in our public code repository.
+(\textbf{Please refer to Section 4.1.4, highlighted in blue in the revised manuscript.})
+
+	\textcolor{blue}{
+"In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
+For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository."}
 

### 2025-07-23 VLDB2026/main.tex
change parameter part

--- 2025-07-22 VLDB2026/main.tex
@@
 
-		\caption{Comparison of AF-ANN and RF-ANN search algorithms}
+		\caption{Comparison of AF-ANN search algorithms}
 		\small
@@
 		\multicolumn{2}{|l|}{\textbf{Multi Thread}}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
-		\multicolumn{2}{|l|}{\textbf{Disk Support}}           &N  & Y& N & N & N & N & N & N & N & N & N & N \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Disk Storage Support}}           &N  & Y& N & N & N & N & N & N & N & N & N & N \\ \hline
 		\multicolumn{2}{|l|}{\textbf{Base}}           & Graph & Graph & Graph & IVF & Graph & Graph & IVF & Graph & Graph & Graph & Graph & Graph \\ \hline
@@
 				\vspace{0.1cm}
-				\textcolor{orange}{\textsuperscript{AF} Attribue-filtering,}
-				\textcolor{orange}{\textsuperscript{RF} Range-filtering,}
-				\textcolor{orange}{Filtered: FilteredVamana,}
-				\textcolor{orange}{Stitched: StitchedVamana,}
-				\textcolor{orange}{Win: WinFilter,}
 				\textsuperscript{A} Post-filtering, 
@@
 				\textsuperscript{N} Unsupport. 
+				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
 				\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
@@
 				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search,
-				\textcolor{orange}{\textit{Disk Support} indicates whether the algorithm supports disk storage,}
-				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm.
+				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
 		\end{minipage}}
@@
 
+	\textcolor{blue}{
+	\subsubsection{Parameters}
+	In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
+For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository.
+}
+
 	%4.2
@@
 
-	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency.
-However, its performance declines under power-law and normal distributions: power-law distributions cause excessive concentration of popular labels and fragmentation of niche labels, disrupting search path connectivity, while normal distributions produce ambiguous graph structures due to label frequency similarities, leading to search divergence.
-	Under the power-law distribution, when the NHQ algorithm constructs an index based on fusion distance, points corresponding to high-frequency attribute values make the graph connections extremely dense, while points corresponding to low-frequency attribute values tend to become isolated due to sparse connections.
-This extreme imbalance in connectivity severely distorts the graph's structure, ultimately significantly impairing the overall performance of the algorithm.
-	The search performance of VBASE exhibits a direct dependence on attribute selectivity.
-As selectivity decreases, search speed declines.
-Notably, only uniform distribution maintains sufficient selectivity among the tested cases; the other three distributions consistently show low selectivity levels that significantly degrade the operational efficiency of VBASE.}
+	In contrast, VBASE exhibits the weakest robustness.
+As a post-filtering system, it performs significantly better under uniform distributions but degrades under long-tailed, normal, and power-law distributions.
+This degradation stems from the low selectivity of certain attributes in the last 3 distributions, which increases unnecessary distance computations, thus reducing overall efficiency.
 
@@
 		%\vspace{0.1cm}
-		\begin{subfigure}[t]{0.507\columnwidth}
+		\begin{subfigure}[t]{0.332\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}[t]{0.48\columnwidth}
-			\centering
-			\captionsetup{font=small}
-			\includegraphics[width=\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-			\caption{\footnotesize MultiModel}
-			\label{fig:MultiModel}
-		\end{subfigure}
-
-		\begin{subfigure}[t]{0.507\columnwidth}
+		\begin{subfigure}[t]{0.315\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}[t]{0.48\columnwidth}
+		\begin{subfigure}[t]{0.315\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}[t]{0.48\columnwidth}
-			\centering
-			\captionsetup{font=small}
-			\includegraphics[width=\linewidth]{figures/exp/range_multimodel_1.pdf}
-			\caption{\footnotesize MultiModel}
-			\label{fig:MultiModel range}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.507\columnwidth}
+		\begin{subfigure}[t]{0.315\columnwidth}
 			\centering

### 2025-07-23 Revision/response.tex

--- 2025-07-23 Revision/response.tex
@@
 We modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
-We have revised the manuscript accordingly.
 (Please see Section 4.2.3, highlighted in blue in the revised manuscript)

### 2025-07-23 VLDB2026/main.tex

--- 2025-07-23 VLDB2026/main.tex
@@
 For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance.
+
+	\textcolor{blue}{
+	\subsubsection{Parameters}
+	In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
+For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository.
+}
 

### 2025-07-23 Revision/response.tex
Update response.tex

--- 2025-07-23 Revision/response.tex
@@
 Thank you for your valuable suggestion regarding our experiments.
-In Section 4.2.4, we add experiments on the Deep100M dataset.
+In Section 4.2.4 and Section 4.3.4, we add experiments on the Deep100M dataset.
 The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset.
 In particular, StitchedVamana performs poorly on Deep100M.
-Please see section 4.2.4.
+For attribute filtering, please see section 4.2.4.
 
@@
 Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
+
+For range filtering, please see section 4.3.4.
+
+\textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB).
+At the same time, we can see that some algorithms (e.g., SeRF, ACORN-1) perform even worse than the VBASE database, which indicates that they do not adapt well to large-scale dataset scenarios.
+Although Milvus has a low QPS, it can achieve a recall of 1 with an excellent memory footprint of around 80GB"}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We add relevant experiments conducted on different servers in Section 4.2.4. Please refer to the response MR.R4 for more details.
+Thank you for your suggestion! We add relevant experiments conducted on different servers in Section 4.2.4. Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
+Thank you for your suggestion! We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
+Thank you for your suggestion! We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We add experiments on the Deep100M dataset in Section 4.2.4 and observed some pitfalls. For more details, please refer to our response to Meta Review R7.
+Thank you for your suggestion.
+We add experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observe some pitfalls.
+For more details, please refer to our response to Meta Review R7.
+
 %%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:} 
-Thank you for your insightful comments.
+Thank you for your insightful comments!
 
@@
 \textbf{Response:} 
-Thank you for the suggestion.
+Thank you for the suggestion!
 We realized that the original wording was somewhat vague and led to confusion among readers.

### 2025-07-23 VLDB2026/main.tex
change
1
Update main.tex

@@
 
-		\caption{Comparison of AF-ANN and RF-ANN search algorithms}
+		\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN search algorithms}}
 		\small
@@
 It is a more complex multimodal dataset.
-As shown in Figure~\ref{fig:MultiModel}, although the queries are more complex, UNG and NHQ still perform the best.
+As shown in Figure~\ref{fig:MultiModal}, although the queries are more complex, UNG and NHQ still perform the best.
 CAPS is the next best.
@@
 It poses a more severe challenge to the algorithm.
-}
+a}
 
@@
 		\captionsetup{font=small}
-		\caption{MultiModel}
-		\label{fig:MultiModel_range} % A single label for the combined subfigure
+		\caption{MultiModal}
+		\label{fig:MultiModal} % A single label for the combined subfigure
 		\end{subfigure}
@@
 	\textcolor{blue}{
-	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModel_range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModal_range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
 As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
@@
 		\captionsetup{font=small}
-		\caption{MultiModel}
-		\label{fig:MultiModel_range} % A single label for the combined subfigure
+		\caption{MultiModal}
+		\label{fig:MultiModal_range} % A single label for the combined subfigure
 	\end{subfigure}

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 
-For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we have added performance rankings for each algorithm across different selectivity levels in the figure.
+For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we add performance rankings for each algorithm across different selectivity levels in the figure.
 This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.

### 2025-07-23 VLDB2026/main.tex
Update main.tex

@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The closer the four curves (corresponding to the four distributions) in the figure approach each other, the less the algorithm is affected by attribute distributions.
-Conversely, the farther they diverge, the more significant the impact of attribute distributions on the algorithm becomes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+\textcolor{cyan}{The proximity of the four curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
+Conversely, greater divergence among the curves indicates higher distributional dependence.
+Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 Ensuring the readability of the figures is indeed crucial.
-We modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
+We modify both the figure and the related description in the paper to improve readability and ensure academic rigor.
 (Please see Section 4.2.3, highlighted in blue in the revised manuscript)
 
-For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we have added robustness indicators (Strong and Weak) in the figure.
+For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we add robustness indicators (Strong and Weak) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
@@
 
-\textcolor{blue}{"The proximity of the four curves (representing different attribute distributions) in the figure reflects the algorithm's sensitivity to distributional variations.
+\textcolor{blue}{"The proximity of the four curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.

### 2025-07-23 VLDB2026/main.tex
Update main.tex

--- 2025-07-23 VLDB2026/main.tex
@@
 		% 上面的图例，居中并可通过 hspace 调整左右位置
-		\hspace*{10pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
+		\hspace*{8pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
 		\includegraphics[width=0.95\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径
@@
 
-			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
+			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
 			\caption{Construction time}
@@
 
-			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
+			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
 			\caption{Index size (including original dataset)}
@@
 
-			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
+			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
 			\caption{Build peak memory }
@@
 
-			\includegraphics[width=0.95\linewidth]{figures/searchMem/label_memory_comparison.pdf}
+			\includegraphics[width=0.99\linewidth]{figures/searchMem/label_memory_comparison.pdf}
 			\caption{Search peak memory}
@@
 		% 三图横排
-		\begin{subfigure}[t]{0.49\columnwidth}
+		\begin{subfigure}[t]{0.495\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}[t]{0.49\columnwidth}
+		\begin{subfigure}[t]{0.495\columnwidth}
 			\centering

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} We believe this is an excellent suggestion.
-In fact, in the initial version of our paper, we used the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms.
+In fact, in the initial version of our paper, we use the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms.
 In this dataset, the base vectors are images, while the query set consists of texts, resulting in a modality gap between the two.
@@
 
-To further enrich the evaluation of complex multimodal queries, we have added new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
-Specifically, we constructed a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
-We then performed both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms.
+To further enrich the evaluation of complex multimodal queries, we add new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
+Specifically, we construct a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
+We then perform both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms.
 The corresponding experimental results are presented in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.
@@
 For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously.
-Therefore, we did not consider this type of complex query in our experiments but instead studied the two query types separately.
+Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately.
 \textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)

### 2025-07-23 VLDB2026/main.tex
change

@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB).
+	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
 Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms.}.

### 2025-07-23 VLDB2026/main.tex
Update main.tex

--- 2025-07-23 VLDB2026/main.tex
@@
 	In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
-For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository.
+For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.
+Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository.
 }

### 2025-07-23 VLDB2026/main.tex

--- 2025-07-23 VLDB2026/main.tex
@@
 
-		\multicolumn{2}{|c|}{\textbf{Algorithm}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
+		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithm}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
 		 \\ \hline
@@
 However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms.}.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.
 
@@
 
-	\begin{table}[t]
-		\centering
-
-		\caption{Algorithm Recommendation per Scenario}
-		\resizebox{\columnwidth}{!}{
-			\begin{tabular}{|l|c|c|}
+	\renewcommand{\arraystretch}{0.9}
+	\begin{table*}[t]
+		\centering
+		%\setlength{\belowcaptionskip}{-0.3cm}
+
+		\caption{\textcolor{orange}{Recommendations}}
+		\small
+
+		\label{tab:compair_2}
+
+		\resizebox{\textwidth}{!}{
+			\begin{tabular}{|l|*{16}{c|}}
 				\hline
-				\textbf{Scenario} & \textbf{Attribute Filtering} & \textbf{Range Filtering}\\
+				\textbf{Application Scenarios / Algorithm} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
 				\hline
-				S1: Large-scale Datasets & Puck, UNG & iRange\\[1pt]
-				\hline
-				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\[1pt]
-				\hline
-				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\[1pt]
-				\hline
-				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\[1pt]
-
-				\hline
-				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\[1pt]
-				\hline
-				S6: Resource constraint& CAPS, Faiss&Faiss, SeRF \\[1pt]
-				\hline
-				S7: High-Recall Querying & UNG & WinFilter \\[1pt]
-				\hline
-				S8: OOD scenarios & UNG &WinFilter  \\[1pt]
+				\textbf{Query Performance} & H & M & H &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+				\textbf{Index Time} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+				\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+				\textbf{Peak Memory} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+				\textbf{General-Purpose} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+				\textbf{Large-Scale Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+				\textbf{Rare Attribute \& Low Range} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+				\textbf{Insensitive to Data Distribution} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
 				\hline
@@
 		}
-		\label{tab:algo_scenarios}
-	\end{table}
+		\centering
+	\end{table*}
 

### 2025-07-23 Revision/response.tex

@@
 Using IDs as attributes for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have added two datasets that use real attributes:
+To address this issue, we add two datasets that use real attributes:
 
-\textbf{YT-Audio-Real dataset:} For this dataset, we utilized the URLs provided by the YouTube8M dataset to crawl corresponding video categories and view counts as real attributes, using \textbf{video categories as attributes for attribute filtering experiments} and \textbf{view counts as attributes for range filtering experiments}, respectively.
+\textbf{YT-Audio-Real dataset:} For this dataset, we utilize the URLs provided by the YouTube8M dataset to crawl corresponding video categories and view counts as real attributes, using \textbf{video categories as attributes for attribute filtering experiments} and \textbf{view counts as attributes for range filtering experiments}, respectively.
 
-\textbf{WIT-Real dataset:} We used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extracted the language type and the length of the \texttt{context\_page\_description} field as real attributes, applying them in both attribute filtering and range filtering experiments.
+\textbf{WIT-Real dataset:} We use the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes, applying them in both attribute filtering and range filtering experiments.
 

### 2025-07-23 Revision/response.tex

@@
 That's a great suggestion.
-In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
+In order to figure out if the server setting affects the relative ordering of methods, we conduct additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors. Please see section 4.2.4.
+We observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors. Please see section 4.2.4.
 

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 Thank you for your suggestion.
-Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the feature of whether to support disk for each algorithm in Table 1.
-At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
+Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we add the feature of whether to support disk for each algorithm in Table 1.
+At the same time, we also compare the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
 The results are shown in Figure\ref{fig:recall-latency}:
@@
 
-We conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
+We conduct additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
 (1) SSD-based FilteredDiskANN (original disk-based method);
@@
 
-\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.
+\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we do not include the above experiments and analysis in the revised paper.
 

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 In real-world applications, vectors and their attributes often have complex relationships.
-To better reflect such scenarios, we have introduced two real-world datasets, which are described in detail in Meta-Review R3.
+To better reflect such scenarios, we introduce two real-world datasets, which are described in detail in Meta-Review R3.
 Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.(Please see the experimental results in Section 4.2.2 and Section 4.3.2)
@@
 Thank you for your suggestion.
-We have addressed this issue in detail in our response to Meta-Review R2.
-Specifically, we have added complex multimodal query experiments and provided an in-depth analysis of the results.
+We address this issue in detail in our response to Meta-Review R2.
+Specifically, we add complex multimodal query experiments and provided an in-depth analysis of the results.
 For more details, please refer to our response to Meta-Review R2.

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 
-We have revised the manuscript accordingly.
-(Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.) Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
+We revise the manuscript accordingly.
+(Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.) Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we remove two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
 

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} 
-Thank you for your suggestion. We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
+Thank you for your suggestion. We make a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
+Thank you for your suggestion. We make a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
 

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper.
-We realize that we did not clearly explain the difference between our paper and the cited paper, so we added a description in the introduction, please see section XXX.
+We realize that we do not clearly explain the difference between our paper and the cited paper, so we add a description in the introduction, please see section XXX.
 \textcolor{blue}{""}

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} 
-Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
+Thank you for your suggestion. We cite these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
 In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
@@
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we will add more comprehensive references in the paper.
+For the two parts you suggested, we add more comprehensive references in the paper.
 Please see section 1.1.
+
 \textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[12], and attribute  selectivity [46,51] significantly impact algorithm performance."}

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 We sincerely apologize for the misuse of notation in Definition 2.3.
-This has been corrected in the revised version.
+This is corrected in the revised version.
 (Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript)
@@
 }
+
 \noindent
@@
 Thank you for your suggestion.
-We acknowledge that the original manuscript did not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard graph-based and IVF-based index structures.
-We have revised Section 2.2 and added two paragraphs.
+We acknowledge that the original manuscript do not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard graph-based and IVF-based index structures.
+We revise Section 2.2 and add two paragraphs.
 These paragraphs summarize how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures.

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 
-We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to MR.R7.
+We conduct experiments on a 100M-scale deep dataset and analyze the performance of each algorithm on the large dataset. Please refer to MR.R7.
 
@@
 
-For datasets with recommended parameters provided in the original papers, we directly used those recommended settings.
-For other datasets, we selected the parameter combinations that performed best through empirical evaluation.
+For datasets with recommended parameters provided in the original papers, we directly use those recommended settings.
+For other datasets, we select the parameter combinations that performed best through empirical evaluation.
 All parameters used in the experiments are available in our public code repository.
@@
 According to our experimental results, for datasets using the recommended parameters, the algorithm rankings remained unchanged.
-During the search process, we adjusted the search parameters to obtain different Recall and QPS values.
+During the search process, we adjust the search parameters to obtain different Recall and QPS values.
 The search parameters typically span a wide range of values to ensure the completeness of the experimental results.
 
-Due to the large number of algorithms and datasets involved, we did not include all parameter settings in the paper because of space limitations.
+Due to the large number of algorithms and datasets involved, we do not include all parameter settings in the paper because of space limitations.
 The detailed parameter configurations can be found in our public code repository.

### 2025-07-23 Revision/response.tex

@@
 For partitioning and merging, only Filtered-DiskANN, which supports disk storage, builds indices separately and then merges them.
-However, the algorithms we focused on and evaluated in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction.
+However, the algorithms we focus on and evaluate in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction.
 Therefore, for the vast majority of algorithms, index partitioning and merging are not involved, which differs from DiskANN's design considerations.
@@
 
-f all the evaluated algorithms, only Faiss supports quantization.
-However, in our experiments, we used the IVF index structure of Faiss without employing quantization.
-Therefore, no quantization time was included in the reported index build times.
+Of all the evaluated algorithms, only Faiss supports quantization.
+However, in our experiments, we use the IVF index structure of Faiss without employing quantization.
+Therefore, no quantization time is included in the reported index build times.
 

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 Figure 7 presents experiments on multi-attribute construction and search, using Boolean AND logic.
-The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-We will clarify this point in the revised version of the paper, specifically in the section on \textcolor{blue}{Multi-Attribute Construction and Multi-Attribute Query}.\textcolor{blue}{"Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
+The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they are not included.
+We clarify this point in the revised version of the paper, specifically in the section on \textcolor{blue}{Multi-Attribute Construction and Multi-Attribute Query}.\textcolor{blue}{"Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
 Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments."}
@@
 
-All the evaluated algorithms in our experiments build the index in a one-shot manner, without applying any partitioning or merging strategies.
-Additionally, although some of the methods we used—such as FAISS, PUCK, DiskANN, and Milvus—support vector quantization during index construction, we did not enable quantization in any of our experiments.
+%All the evaluated algorithms in our experiments build the index in a one-shot manner, without applying any partitioning or merging strategies.
+%Additionally, although some of the methods we used—such as FAISS, PUCK, DiskANN, and Milvus—support vector quantization during index construction, we do not enable quantization in any of our experiments.
 Therefore, the reported index build times do not include quantization.

### 2025-07-23 Revision/response.tex
Update response.tex

@@
 Thank you for the suggestion.
-We realized that the original wording was somewhat vague and led to confusion among readers.
-To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified each algorithm's support for AF and RF in the unified table.
+We realize that the original wording is somewhat vague and lead to confusion among readers.
+To address this, we merge the tables for attribute filtering (AF) and range filtering (RF), and clarify each algorithm's support for AF and RF in the unified table.
 \textcolor{blue}{The fused table is Table1: Comparison of AF-ANN and RF-ANN search algorithms.}

### 2025-07-23 VLDB2026/main.tex
change

@@
 				\textsuperscript{N} Unsupport. 
-				\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
-				\textit{OR} indicates whether the algorithm supports attribute filtering with OR operations. 
+				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
 				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
-				\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
+				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
 				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search,
-				\textcolor{orange}{\textit{Disk Support} indicates whether the algorithm supports disk storage,}
+				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+				\textit{Disk Support} indicates whether the algorithm supports disk storage.
 				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm.
@@
 Specifically, Section~3.1 describes methods for attribute filtering, Section~3.2 discusses those for range filtering, and Section~3.3 introduces vector libraries and databases that support both attribute filtering and range filtering.
+	Table~\ref{tab:compair_1} provides a comparative overview of six attribute filtering and five representative range filtering algorithms.
 
 	\subsection{Attribute Filtering Algorithms}
-
-	We summarize 6 attribute filtering algorithms and provide an intuitive comparison in Table~\ref{tab:compair_1}.
 
@@
 	\subsection{Range Filtering Algorithms}
-
-	We introduce 5 representative range filtering algorithms and present a comparative overview in \textcolor{orange}{Table~\ref{tab:compair_1}.}
 

### 2025-07-23 VLDB2026/main.tex
Update main.tex

@@
 
-	\subsubsection{Platform}
+	\subsubsection{\textcolor{cyan}{Setting}}
 
 	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) and 256GB of RAM.
-Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}.
+\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.} Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}.
 By default, queries run on a single thread.
@@
 
-	\textcolor{blue}{
-	\subsubsection{Parameters}
-	In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
+	\textcolor{cyan}{
+	Regarding experimental parameter selection, we adopted the recommended settings from original papers when available.
+For datasets without suggested parameters, we experimented with different configurations and selected the optimal one for final evaluation.
+Due to the extensive number of datasets and algorithms involved, specific parameters are not listed individually but are provided in our code repository.
+}
+%	\textcolor{blue}{
+%	\subsubsection{Parameters}
+%	In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
 For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.
 Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository.
-}
+%}
 
@@
 	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while \underline{the peak memory usage of database} is comparatively lower.}
+Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
 

### 2025-07-23 VLDB2026/main.tex
Update main.tex

@@
 	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) and 256GB of RAM.
-\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.} Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}.
+\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.
+For clarity and conciseness, we hereafter refer to the former as Server A and the latter as Server B.
+Unless otherwise specified, all experiments were conducted on Server A.}
+
+	Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}.
 By default, queries run on a single thread.
 We also report results for 16-thread parallelism in specific scenarios.
-
 We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}.
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
+%	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
 Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
-When compared with the original server's experimental results shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
+	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on Server B, with results presented in Figure~\ref{fig:Different_Computer_range}.
+When compared with the experimental results of Server A shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-23 VLDB2026/main.tex
Update main.tex

@@
 To support hybrid queries, existing approaches usually augment the original graph structures by explicitly associating attribute or range information with vertices or edges.
-In attribute filtering, a common approach is to attach attribute metadata to vertices or edges, allowing the traversal process to skip nodes or edges that do not meet the query's attribute conditions (e.g., NHQ, Filtered-DiskANN, ACORN).
+In attribute filtering, a common approach is to attach attribute metadata to vertices or edges, allowing the traversal process to skip nodes or edges that do not meet attribute conditions of the query (e.g., NHQ, Filtered-DiskANN, ACORN).
 In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges satisfying the range constraints, effectively narrowing down the search space (e.g., SeRF, DSG).}
@@
 	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods.
-The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
+The reason for the superior performance of Puck is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
 CAPS performs as well as Puck.
@@
 	Under the power-law distribution, when the NHQ algorithm constructs an index based on fusion distance, points corresponding to high-frequency attribute values make the graph connections extremely dense, while points corresponding to low-frequency attribute values tend to become isolated due to sparse connections.
-This extreme imbalance in connectivity severely distorts the graph's structure, ultimately significantly impairing the overall performance of the algorithm.
+This extreme imbalance in connectivity severely distorts the structure of the graph, ultimately significantly impairing the overall performance of the algorithm.
 	The search performance of VBASE exhibits a direct dependence on attribute selectivity.

### 2025-07-23 VLDB2026/main.tex
change

--- 2025-07-23 VLDB2026/main.tex
@@
 				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
+				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image \\
 				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio \\
-				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
 				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
@@
 	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
-The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and WIT) and query ranges, WinFilter consistently delivers the best performance.
+The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges, WinFilter consistently delivers the best performance.
 This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.

### 2025-07-23 Revision/response.tex
Update response.tex

--- 2025-07-23 Revision/response.tex
@@
 Ensuring the readability of the figures is indeed crucial.
-We modify both the figure and the related description in the paper to improve readability and ensure academic rigor.
+We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
 (Please see Section 4.2.3, highlighted in blue in the revised manuscript)
 
-For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we add robustness indicators (Strong and Weak) in the figure.
+For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
@@
 
-For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we add performance rankings for each algorithm across different selectivity levels in the figure.
+For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we added performance rankings for each algorithm across different selectivity levels in the figure.
 This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
@@
 
-\textcolor{blue}{"The proximity of the four curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
+\textcolor{blue}{"The proximity of the 4 curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
@@
 \textbf{Response:} 
-That's a great suggestion.
-In order to figure out if the server setting affects the relative ordering of methods, we conduct additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
+That is a great suggestion.
+In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors. Please see section 4.2.4.
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors. Please see section 4.2.4.
 
@@
 Thank you for your suggestion.
-Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we add the feature of whether to support disk for each algorithm in Table 1.
-At the same time, we also compare the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
+Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the feature of whether to support disk for each algorithm in Table 1.
+At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
 The results are shown in Figure\ref{fig:recall-latency}:
@@
 
-We conduct additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
+We conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
 (1) SSD-based FilteredDiskANN (original disk-based method);
@@
 
-\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we do not include the above experiments and analysis in the revised paper.
+\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.
 
@@
 In real-world applications, vectors and their attributes often have complex relationships.
-To better reflect such scenarios, we introduce two real-world datasets, which are described in detail in Meta-Review R3.
+To better reflect such scenarios, we have introduced two real-world datasets, which are described in detail in Meta-Review R3.
 Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.(Please see the experimental results in Section 4.2.2 and Section 4.3.2)
@@
 Thank you for your suggestion.
-We address this issue in detail in our response to Meta-Review R2.
+We have addressed this issue in detail in our response to Meta-Review R2.
 Specifically, we add complex multimodal query experiments and provided an in-depth analysis of the results.
@@
 
-We revise the manuscript accordingly.
-(Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.) Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we remove two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
+We have revised the manuscript accordingly.
+(Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.) Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We make a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
+Thank you for your suggestion. We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We make a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
+Thank you for your suggestion. We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
 
@@
 Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper.
-We realize that we do not clearly explain the difference between our paper and the cited paper, so we add a description in the introduction, please see section XXX.
+We realize that we did not clearly explain the difference between our paper and the cited paper, so we add a description in the introduction, please see section XXX.
 \textcolor{blue}{""}
@@
 \textbf{Response:} 
-Thank you for your suggestion. We cite these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
+Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
 In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
@@
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we add more comprehensive references in the paper.
+For the two parts you suggested, we will add more comprehensive references in the paper.
+
 Please see section 1.1.
-
 \textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[12], and attribute  selectivity [46,51] significantly impact algorithm performance."}
@@
 We sincerely apologize for the misuse of notation in Definition 2.3.
-This is corrected in the revised version.
+This has been corrected in the revised version.
 (Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript)
@@
 Thank you for your suggestion.
-We acknowledge that the original manuscript do not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard graph-based and IVF-based index structures.
+We acknowledge that the original manuscript did not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard graph-based and IVF-based index structures.
 We revise Section 2.2 and add two paragraphs.
@@
 
-We conduct experiments on a 100M-scale deep dataset and analyze the performance of each algorithm on the large dataset. Please refer to MR.R7.
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to MR.R7.
 
@@
 
-For datasets with recommended parameters provided in the original papers, we directly use those recommended settings.
+For datasets with recommended parameters provided in the original papers, we directly used those recommended settings.
 For other datasets, we select the parameter combinations that performed best through empirical evaluation.
@@
 According to our experimental results, for datasets using the recommended parameters, the algorithm rankings remained unchanged.
-During the search process, we adjust the search parameters to obtain different Recall and QPS values.
+During the search process, we adjusted the search parameters to obtain different Recall and QPS values.
 The search parameters typically span a wide range of values to ensure the completeness of the experimental results.
 
-Due to the large number of algorithms and datasets involved, we do not include all parameter settings in the paper because of space limitations.
+Due to the large number of algorithms and datasets involved, we did not include all parameter settings in the paper because of space limitations.
 The detailed parameter configurations can be found in our public code repository.
@@
 For partitioning and merging, only Filtered-DiskANN, which supports disk storage, builds indices separately and then merges them.
-However, the algorithms we focus on and evaluate in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction.
+However, the algorithms we focused on and evaluated in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction.
 Therefore, for the vast majority of algorithms, index partitioning and merging are not involved, which differs from DiskANN's design considerations.
@@
 Of all the evaluated algorithms, only Faiss supports quantization.
-However, in our experiments, we use the IVF index structure of Faiss without employing quantization.
-Therefore, no quantization time is included in the reported index build times.
+However, in our experiments, we used the IVF index structure of Faiss without employing quantization.
+Therefore, no quantization time was included in the reported index build times.
 
@@
 
-We appreciate the reviewer’s observation.
+We appreciate the observation of reviewer.
 Figure 7 presents experiments on multi-attribute construction and search, using Boolean AND logic.
@@
 Thank you for the suggestion.
-We realized that the original wording was somewhat vague and led to confusion among readers.
-To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified each algorithm's support for AF and RF in the unified table.
+We realized that the original wording is somewhat vague and lead to confusion among readers.
+To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table.
 \textcolor{blue}{The fused table is Table1: Comparison of AF-ANN and RF-ANN search algorithms.}

### 2025-07-23 VLDB2026/main.tex
Update main.tex

--- 2025-07-23 VLDB2026/main.tex
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the four curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
+\textcolor{cyan}{The proximity of the 4 curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.

### 2025-07-23 VLDB2026/main.tex
1

--- 2025-07-23 VLDB2026/main.tex
@@
 \usepackage{subcaption} % 需要subcaption宏包支持子图
+
+\usepackage{fontawesome}
+\usepackage{amssymb}
+
 % \newtheorem{definition}{DEFINITION} % 定义“定义”环境
@@
 To support hybrid queries, existing approaches usually augment the original graph structures by explicitly associating attribute or range information with vertices or edges.
-In attribute filtering, a common approach is to attach attribute metadata to vertices or edges, allowing the traversal process to skip nodes or edges that do not meet attribute conditions of the query (e.g., NHQ, Filtered-DiskANN, ACORN).
+In attribute filtering, a common approach is to attach attribute metadata to vertices or edges, allowing the traversal process to skip nodes or edges that do not meet the query's attribute conditions (e.g., NHQ, Filtered-DiskANN, ACORN).
 In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges satisfying the range constraints, effectively narrowing down the search space (e.g., SeRF, DSG).}
@@
 				\textsuperscript{N} Unsupport. 
-				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
+				\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
+				\textit{OR} indicates whether the algorithm supports attribute filtering with OR operations. 
 				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
-				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
+				\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
 				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-				\textit{Disk Support} indicates whether the algorithm supports disk storage.
+				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search,
+				\textcolor{orange}{\textit{Disk Support} indicates whether the algorithm supports disk storage,}
 				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm.
@@
 Specifically, Section~3.1 describes methods for attribute filtering, Section~3.2 discusses those for range filtering, and Section~3.3 introduces vector libraries and databases that support both attribute filtering and range filtering.
-	Table~\ref{tab:compair_1} provides a comparative overview of six attribute filtering and five representative range filtering algorithms.
 
 	\subsection{Attribute Filtering Algorithms}
+
+	We summarize 6 attribute filtering algorithms and provide an intuitive comparison in Table~\ref{tab:compair_1}.
 
@@
 
+	We introduce 5 representative range filtering algorithms and present a comparative overview in \textcolor{orange}{Table~\ref{tab:compair_1}.}
+
 	\noindent\textbf{\underline{SeRF} \footnote{https://github.com/rutgers-db/SeRF} \cite{serf}} Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
@@
 
-	\subsubsection{\textcolor{cyan}{Setting}}
+	\subsubsection{Platform}
 
 	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) and 256GB of RAM.
-\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.
-For clarity and conciseness, we hereafter refer to the former as Server A and the latter as Server B.
-Unless otherwise specified, all experiments were conducted on Server A.}
-
 Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}.
@@
 We also report results for 16-thread parallelism in specific scenarios.
+
 	We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}.
@@
 
-	\textcolor{cyan}{
-	Regarding experimental parameter selection, we adopted the recommended settings from original papers when available.
-For datasets without suggested parameters, we experimented with different configurations and selected the optimal one for final evaluation.
-Due to the extensive number of datasets and algorithms involved, specific parameters are not listed individually but are provided in our code repository.
-}
-%	\textcolor{blue}{
-%	\subsubsection{Parameters}
-%	In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
+	\textcolor{blue}{
+	\subsubsection{Parameters}
+	In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
 For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.
 Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository.
-%}
+}
 
@@
 	\textit{\textbf{Index construction time.}}
-	As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 6 datasets, PASE has the longest index construction time due to its single-thread indexing support.
+	%As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 6 datasets, PASE has the longest index construction time due to its single-thread indexing support.
 Additionally, VBASE also supports only single-thread indexing but achieves better performance than PASE.
+	 \textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time.
+The on-demand loading and caching strategy used by PASE results in frequent disk I/O and page scheduling, which significantly slow down the construction process.
+In contrast, VBASE uses full in-memory construction, leading to faster indexing.}
 
@@
 In contrast, ACORN-$\gamma$ incurs the highest index construction time, as it expands neighbor lists and evaluates a large candidate pool, leading to increased computational overhead.
+\textcolor{orange}{Its construction time on some datasets is even slower than that of the single-threaded VBASE.}
 
 	\textit{\textbf{Index size.}}
-	%	Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data.
-In order to unify the comparison standard,
-	%	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
-	%\sout{To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.}
-	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it.
-To ensure a consistent comparison, we consider both the index structure and the original data when measuring index size.
 	As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets.
@@
 The index sizes of other methods show moderate variation.
-Among these, \underline{Faiss generates slightly smaller indexes due to its efficient index design}.
+	 \textcolor{orange}{Among these, we observe a trend that IVF-based methods tend to produce more compact indexes compared to graph-based methods.}
+
+	 %\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
 
@@
 	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
+Among them, CAPS and NHQ have relatively higher peak memory usage, while \underline{the peak memory usage of database} is comparatively lower.}
 
@@
 	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods.
-The reason for the superior performance of Puck is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
+The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
 CAPS performs as well as Puck.
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the 4 curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
+\textcolor{cyan}{The proximity of the four curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
@@
 	Under the power-law distribution, when the NHQ algorithm constructs an index based on fusion distance, points corresponding to high-frequency attribute values make the graph connections extremely dense, while points corresponding to low-frequency attribute values tend to become isolated due to sparse connections.
-This extreme imbalance in connectivity severely distorts the structure of the graph, ultimately significantly impairing the overall performance of the algorithm.
+This extreme imbalance in connectivity severely distorts the graph's structure, ultimately significantly impairing the overall performance of the algorithm.
 	The search performance of VBASE exhibits a direct dependence on attribute selectivity.
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
-Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-%	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
 Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on Server B, with results presented in Figure~\ref{fig:Different_Computer_range}.
-When compared with the experimental results of Server A shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
+	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
+When compared with the original server's experimental results shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}
@@
 
-	\renewcommand{\arraystretch}{0.9}
-	\begin{table*}[t]
-		\centering
-		%\setlength{\belowcaptionskip}{-0.3cm}
-
-		\caption{\textcolor{orange}{Recommendations}}
-		\small
-
-		\label{tab:compair_2}
-
+\begin{table*}[htbp]
+	\caption{Algorithm Recommendation}
 	\resizebox{\textwidth}{!}{
@@
 			\hline
-				\textbf{Application Scenarios / Algorithm} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
+			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
+			& \multicolumn{6}{c|}{\textbf{AF}} 
+			& \multicolumn{5}{c|}{\textbf{RF}} 
+			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
+			\cline{2-17}
+			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
+			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
+			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
 			\hline
-				\textbf{Query Performance} & H & M & H &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-				\textbf{Index Time} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+			\textbf{Query Performance} & H & M & H & M &\textbf{ H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
+			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
+			\textbf{Peak Memory} &L  &M  &M  &M  &M  &H  &L  &L  &M  &L  &L  &L/L  &\textbf{H}/\textbf{H}  &M/M  &H/M  &H/H \\
+
+			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H } &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
+			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
+			\textbf{Insensitive to Data Distribution} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
 			\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-				\textbf{Peak Memory} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-				\textbf{General-Purpose} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-				\textbf{Large-Scale Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-				\textbf{Rare Attribute \& Low Range} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-				\textbf{Insensitive to Data Distribution} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
 			\hline
@@
 	\subsubsection{\textbf{Attribute Filtering}}
-	We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.
+%	We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.
 Puck and UNG excel on large-scale datasets (S1).
@@
 In addition, CAPS performs well on hard datasets with high LID (S3), while NHQ and StitchedVamana perform better on easy datasets with low LID (S4).
-	Faiss and CAPS can generate relatively compact indexes with low memory usage, which is suitable for resource-constrained situations (S6).
+%	Faiss and CAPS can generate relatively compact indexes with low memory usage, which is suitable for resource-constrained situations (S6).
 Milvus and Faiss serve as general-purpose solutions (S5).
@@
 
-	Table~\ref{tab:algo_scenarios} also shows the application scenarios of range filtering.
+%	Table~\ref{tab:algo_scenarios} also shows the application scenarios of range filtering.
 iRange performs well on large-scale datasets, combining efficient construction and excellent query capabilities (S1).

### 2025-07-23 VLDB2026/main.tex
change

@@
 \usepackage{fontawesome}
-\usepackage{amssymb}
 
@@
 		\resizebox{\columnwidth}{!}{
-			\begin{tabular}{cccccc}
+			\begin{tabular}{ccccccc}
 				\toprule
-				Dataset & Dimension & Base Data & Queries & LID & Type \\
+				Dataset & Dimension & Base Data & Queries & LID & Type& Used \\
 				\midrule
-				Msong & 420 & 992,272 & 200 & 23& Audio \\
-				Audio & 192 & 53,387 & 200 & 14& Audio \\
-				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\
-				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\
-				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\
-				Enron & 1369 & 94,987 & 200 & 23& Text \\
-				%Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
+
+				Audio & 192 & 53,387 & 200 & 14& Audio& AF \\
+				Deep & 96 & 1,000,000 & 10,000 & 22& Image& RF \\
+				Enron & 1369 & 94,987 & 200 & 23& Text& AF \\
+				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image& AF \\
+				GloVe & 100 & 1,183,514 & 10,000 & 47& Text& AF \\
+				Msong & 420 & 992,272 & 200 & 23& Audio& AF \\
+				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image& AF \\
+
 				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
@@
 	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
-	\textcolor{violet}{On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
-The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
+	\textcolor{violet}{As shown in the figure~\ref{fig:Big Dataset}, On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
+The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
 We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level.

### 2025-07-23 VLDB2026/main.tex
change

@@
 				Audio & 192 & 53,387 & 200 & 14& Audio& AF \\
-				Deep & 96 & 1,000,000 & 10,000 & 22& Image& RF \\
 				Enron & 1369 & 94,987 & 200 & 23& Text& AF \\
@@
 				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
-				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image \\
-				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio \\
-				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
-				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
-				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image \\
-				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image \\
+				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image& RF \\
+				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio& Both \\
+				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image& Both \\
+				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image& Both \\
+				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image& Both \\
+				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image& Both \\
 				\bottomrule

### 2025-07-23 VLDB2026/main.tex
Update main.tex

@@
 	\subsubsection{Datasets}
+
+	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio, Deep1M, Enron, GIST1M, GloVe, Msong, SIFT1M, WIT-Real, YT-Audio-Real, Text2image, Text2image-Mix, and Deep100M.}
+
+	\textcolor{violet}{The first seven datasets are widely used in existing literature.
+As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.}
+
+	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the \texttt{page\_title} field into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes.
+The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
+
+	\textcolor{violet}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
+The Text2Image dataset includes two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
+
+	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets and their applicable filtering scenarios.
+In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, which is a commonly used metric to quantify dataset hardness.
+Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset to compute LID.
+The higher the LID value, the harder the dataset.
+
 	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.

### 2025-07-23 VLDB2026/main.tex
change

@@
 
-	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio, Deep1M, Enron, GIST1M, GloVe, Msong, SIFT1M, WIT-Real, YT-Audio-Real, Text2image, Text2image-Mix, and Deep100M.}
+	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown}, Deep1M~\cite{yandex_deep_dataset}, Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
 
@@
 
-	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.
+	%For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.
 We independently generate attribute for each dataset.
 
-	\textcolor{violet}{For range filtering queries, we evaluate 1 widely used dataset: WIT~\cite{wit_dataset}.
+	%\textcolor{violet}{For range filtering queries, we evaluate 1 widely used dataset: WIT~\cite{wit_dataset}.
 Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
@@
 
-	\textcolor{violet}{Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.
+	%\textcolor{violet}{Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.
 It should be noted that, during range filtering, due to the limitations of some algorithms, we uniformly sorted the vectors according to the query attribute.}
 
-	\textcolor{violet}{To validate the algorithm generalization capability, we also further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M.
+	%\textcolor{violet}{To validate the algorithm generalization capability, we also further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M.
 Specifically, the Text2Image dataset comprises two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
@@
 
-	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets.
+	%Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets.
 In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness.

### 2025-07-23 VLDB2026/main.tex
change

@@
 	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
-	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
+	As shown in Figure \ref{fig:exp_2_1}, \textcolor{red}{Puck demonstrates nearly no performance degradation, because it accurately identifies the nearest clusters during a search, keeping the number of candidates constant, no matter how many attributes were used to build the index}.
 CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping.

### 2025-07-23 VLDB2026/main.tex
Update main.tex

--- 2025-07-23 VLDB2026/main.tex
@@
 	\subsubsection{Datasets}
-
-	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio, Deep1M, Enron, GIST1M, GloVe, Msong, SIFT1M, WIT-Real, YT-Audio-Real, Text2image, Text2image-Mix, and Deep100M.}
-
-	\textcolor{violet}{The first seven datasets are widely used in existing literature.
-As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.}
-
-	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the \texttt{page\_title} field into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes.
-The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
-
-	\textcolor{violet}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
-The Text2Image dataset includes two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
-
-	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets and their applicable filtering scenarios.
-In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, which is a commonly used metric to quantify dataset hardness.
-Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset to compute LID.
-The higher the LID value, the harder the dataset.
-
 	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.
@@
 				Audio & 192 & 53,387 & 200 & 14& Audio& AF \\
+				Deep & 96 & 1,000,000 & 10,000 & 22& Image& RF \\
 				Enron & 1369 & 94,987 & 200 & 23& Text& AF \\
@@
 				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
-				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image& RF \\
-				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio& Both \\
-				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image& Both \\
-				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image& Both \\
-				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image& Both \\
-				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image& Both \\
+				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image \\
+				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio \\
+				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
+				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
+				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image \\
+				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image \\
 				\bottomrule
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the 4 curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
-Conversely, greater divergence among the curves indicates higher distributional dependence.
-Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+\textcolor{cyan}{The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
@@
 			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
-			\textbf{Insensitive to Data Distribution} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-			\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &H  &L  &M  &H  &M  &H  &H  &H/H  &M/M  &L/L  &L/L  &-/-  \\
+			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &H/-  &L/-  &L/-  \\
+			\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &M  &L  &L/  &L/  \\
 			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\

### 2025-07-23 VLDB2026/main.tex
1

--- 2025-07-23 VLDB2026/main.tex
@@
 
+	for big dataset:
+
 	\textit{\textbf{Index size.}}
@@
 
+	 for big dataset:
 	 %\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
@@
 	\textit{\textbf{Build peak memory.}}
-	As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
-	%on small-scale datasets, all methods except NHQ exhibit low memory usage. 
-	\textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
-	This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
-
-	On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
+%	As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
+%	%on small-scale datasets, all methods except NHQ exhibit low memory usage. 
+%	\textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
+%	This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
+%	
+%	On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
 \textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index.
 }.
+	\textcolor{orange}{As shown in the Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size generated by the algorithm and the dataset size.
+This trend holds consistently across different datasets.
+However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the index size itself.
+For large-scale datasets, algorithms that produce larger indexes tend to cause significantly higher peak memory consumption during construction.}
 
 	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
-	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
+%	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
 Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
-
+	\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
+However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets.
+In contrast, Milvus has lower query-time memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
+	}
 	\subsubsection{Performance Evaluation}
@@
 	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
-	As shown in Figure \ref{fig:exp_2_1}, \textcolor{red}{Puck demonstrates nearly no performance degradation, because it accurately identifies the nearest clusters during a search, keeping the number of candidates constant, no matter how many attributes were used to build the index}.
+	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
 CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping.
@@
 	(1) \textit{Algorithms optimized for low AS.}  
-	This group includes ACORN-1, Faiss+HQI\_Batch, StitchedVamana, UNG, Faiss, Puck, and CAPS, as illustrated in Figure~\ref{fig:exp_5_2_1}.
+	This group includes ACORN-1, CAPS, StitchedVamana, UNG, Puck, Faiss, and Faiss+HQI\_Batch as illustrated in Figure~\ref{fig:exp_5_2_1}.
 

### 2025-07-23 VLDB2026/main.tex
1

@@
 }
+
 	\subsubsection{Performance Evaluation}
@@
 	(1) \textit{Algorithms optimized for low AS.}  
-	This group includes ACORN-1, CAPS, StitchedVamana, UNG, Puck, Faiss, and Faiss+HQI\_Batch as illustrated in Figure~\ref{fig:exp_5_2_1}.
+	This group includes ACORN-1, Faiss+HQI\_Batch, StitchedVamana, UNG, Faiss, Puck, and CAPS, as illustrated in Figure~\ref{fig:exp_5_2_1}.
 

### 2025-07-23 Revision/response.tex

@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-We will clarify this point in the revised version of the paper, specifically in the section on \textcolor{blue}{Multi-Attribute Construction and Multi-Attribute Query}.\textcolor{blue}{"Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
+We will clarify this point in the revised version of the paper.
+Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.
+
+\textcolor{blue}{"Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
 Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments."}
+
 %Thanks to the reviewer for suggesting that there is no explanation in Figure 7 why Vamana is not included.

### 2025-07-23 VLDB2026/main.tex
Update main.tex
1

@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. 
-\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.
-	However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
+%	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
 
@@
 
+	\textcolor{orange}{Note: For large-scale datasets, all algorithms are built using 64 threads for efficiency, except DSG, which only supports single-threaded construction.
+As a result, DSG takes significantly longer to build on Deep100M.
+	}
+
 	\textit{\textbf{Index size.}} 
@@
 Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
-	On low-dimensional datasets (Deep, YT-Audio), PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
-
-	SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
+	%On low-dimensional datasets (Deep, YT-Audio), 
+	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
+	\textcolor{orange}{DSG is an improvement over SeRF.
+Compared to SeRF, DSG stores additional information for each edge in its index structure, resulting in a significant increase in index size on large-scale datasets.
+	}
+
+	%SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
 
 	\textit{\textbf{Build peak memory.}}
-	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
-
-	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
+%	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
+%	
+%	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
 This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
-	%因为低维空间中数据点之间的欧氏距离普遍较小，点与点之间更易互为近邻，从而导致图索引中产生大量冗余的边连接。
-
-	%As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
-It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.
-
-	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage.
+%	
+%	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage.
 It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
@@
 This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
-	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
-	%Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.
+%	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
+
+	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows,
 
 		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}
-
-	%	\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, Faiss and Milvus have the lowest peak memory usage during search.
-Similar to attribute filtering, Faiss also has a smaller index size and no other additional memory usage, so the peak memory usage in range queries is slightly higher than the index size.
-Milvus reason:.
-WinFilter achieves the highest peak memory usage on almost all datasets.
-The reason is:.
-For the high-dimensional dataset WIT, UNIFY occupies the highest peak memory.
-The reason is:.}
-
 		\textcolor{orange}{As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
-The algorithm needs to load the complete index into memory during search.
-Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
-For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}
+As we analyzed in the section on attribute filtering.
+		}
 
@@
 			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &H/-  &L/-  &L/-  \\
-			\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &M  &L  &L/  &L/  \\
+			\textbf{High LID Dataset} &H  &M  &H  &M  &H  &M  &M  &H  &M  &H  &H  &L/L  &M/H  &L/L  &L/M  &L/L  \\
 			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\

### 2025-07-24 Revision/response.tex
1

@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-We will clarify this point in the revised version of the paper.
+Since other algorithms also do not support multi-attribute queries, we will explain this situation collectively in the corresponding section of the paper to save space.
+
 Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.
 
-\textcolor{blue}{"Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
-Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments."}
+\textcolor{blue}{"In this experiment, we only evaluate the algorithms that support this query scenario."}
 

### 2025-07-24 VLDB2026/main.tex
1

@@
 To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
-\textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
-Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
+\textcolor{orange}{In this experiment, we only evaluate the algorithms that support this query scenario.}
 	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
@@
 			\hline
-			\textbf{Query Performance} & H & M & H & M &\textbf{ H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
+			\textbf{Query Performance} & H & M & H & M &\textbf{H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
 			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
@@
 
-			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H } &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
+			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H} &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
 			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
-			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &H  &L  &M  &H  &M  &H  &H  &H/H  &M/M  &L/L  &L/L  &-/-  \\
-			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &H/-  &L/-  &L/-  \\
-			\textbf{High LID Dataset} &H  &M  &H  &M  &H  &M  &M  &H  &M  &H  &H  &L/L  &M/H  &L/L  &L/M  &L/L  \\
+			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
+			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
+			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
 			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\

### 2025-07-24 VLDB2026/main.tex
Update main.tex

@@
 		\label{fig:exp_3_1}
+
+		\footnotesize{
+		\begin{center}
+			\begin{minipage}{\linewidth}
+				\centering	
+				Note: \textit{Strong} represents robust to attribute distribution, \textit{Weak} represents sensitive to attribute distribution 
+			\end{minipage}
+		\end{center}
+		}
 	\end{figure*}
@@
 To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
-\textcolor{orange}{In this experiment, we only evaluate the algorithms that support this query scenario.}
+\textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
+Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
 	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}

### 2025-07-24 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 	\textit{\textbf{Build peak memory.}}
+	\textcolor{orange}{As explained in the build peak memory analysis for attribute filtering, the build peak memory depends on the sum of the index size and the dataset size, as shown in Figure~\ref{fig:rangeFilter_build_memory_mb}.
+Range filtering also follows this pattern.
+The reason why PASE deviates from this trend has been discussed earlier, and is not repeated here to save space.}
+
 %	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
@@
 %	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
-
-	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows,
 

### 2025-07-24 VLDB2026/main.tex
1

@@
 
-		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithm}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
+		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithms}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
 		 \\ \hline

### 2025-07-24 VLDB2026/main.tex
Update main.tex

--- 2025-07-24 VLDB2026/main.tex
@@
 				\centering	
-				Note: \textit{Strong} represents robust to attribute distribution, \textit{Weak} represents sensitive to attribute distribution 
+				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
 			\end{minipage}
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
 Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-%	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
 Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}
+Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}
 
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on Server B, with results presented in Figure~\ref{fig:Different_Computer_range}.
-When compared with the experimental results of Server A shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
+When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-24 Revision/response.tex
Revert "Update response.tex"
This reverts commit 09b50f40dd76712a4cfe475968ad9cec78df159c.

--- 2025-07-23 Revision/response.tex
@@
 Please see section 1.1.
+
 \textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[12], and attribute  selectivity [46,51] significantly impact algorithm performance."}
@@
 
-\textcolor{blue}{Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).}
+\textcolor{blue}{"Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \)."}
 

### 2025-07-24 Revision/response.tex
Update response.tex

@@
 Thank you for your valuable suggestion regarding our experiments.
-In Section 4.2.4 and Section 4.3.4, we add experiments on the Deep100M dataset.
+In Section 4.2.4 and Section 4.3.4, we have added experiments on the Deep100M dataset.
 The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset.
@@
 To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table.
-\textcolor{blue}{The fused table is Table1: Comparison of AF-ANN and RF-ANN search algorithms.}
+
+\textcolor{blue}{"The fused table is Table1: Comparison of AF-ANN and RF-ANN search algorithms."}
 

### 2025-07-24 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
+\textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the 6 datasets shown in the left figure, and 64 threads on the large-scale Deep100M dataset.}
 
@@
 \textit{\textbf{Index construction time.}}
-%As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 6 datasets, PASE has the longest index construction time due to its single-thread indexing support.
-Additionally, VBASE also supports only single-thread indexing but achieves better performance than PASE.
-\textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time.
+\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN.
+PASE and VBASE only support single-threaded builds, and PASE is the slowest to build because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster.
+ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates.
+The build time on some datasets even exceeds that of single-threaded VBASE.
+}
+
+\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also find that graph-based algorithms using pruning strategies (such as FilteredDiskANN and UNG) exhibit significantly increased construction time, especially when the pruning is complex and extensive, leading to higher computational overhead.
+In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
+
+%ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.
+
+%\textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time.
 The on-demand loading and caching strategy used by PASE results in frequent disk I/O and page scheduling, which significantly slow down the construction process.
 In contrast, VBASE uses full in-memory construction, leading to faster indexing.}
-
-For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction.
+%
+%
+%For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction.
 This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.
@@
 \textcolor{orange}{Its construction time on some datasets is even slower than that of the single-threaded VBASE.}
-
-for big dataset:
+%
+%On large dataset Deep100M, VBASE takes longer to build because it only supports single-threaded construction.
+The other time-consuming algorithms are all graph-based methods, which employ complex pruning strategies during construction to optimize query performance, leading to significantly increased build times.
 

### 2025-07-24 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 
-		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithms}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
+		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithm}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
 		 \\ \hline
@@
 				\vspace{0.1cm}
-				\textsuperscript{A} Post-filtering, 
+				Win: WinFilter, Filtered: Filtered-DiskANN, Stitched: StitchedVamana. 
 				\textsuperscript{B} Pre-filtering, 
@@
 				\textit{Disk Support} indicates whether the algorithm supports disk storage.
-				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm.
+				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
 		\end{minipage}}
@@
 		\label{fig:exp_3_1}
-
-		\footnotesize{
-		\begin{center}
-			\begin{minipage}{\linewidth}
-				\centering	
-				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
-			\end{minipage}
-		\end{center}
-		}
 	\end{figure*}
@@
 
+\begin{figure*}[t]
+	\centering
+
+	% 1. 全局图例 (Legend) - 位置保持不变
+	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}
+
+	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+
+	% 2. 第一部分：两张图，共用标题
+	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+	% 宽度从\textwidth缩小到0.32\textwidth
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
+		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
+		\hfill 
+		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
+		\caption{MultiModal}
+		\label{fig:attribute-multimodal} 
+	\end{subfigure}
+	\hfill % 在第一部分和第二部分之间添加弹性间距
+	% 3. 第二部分：两张图，共用标题
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
+		\hfill
+		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
+		\caption{Cross-Platform}
+		\label{fig:attribute-cross-platform}
+	\end{subfigure}
+	\hfill % 在第二部分和第三部分之间添加弹性间距
+	% 4. 第三部分：只有一张图
+	\begin{subfigure}[b]{0.203\textwidth}
+		\centering
+		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
+		\caption{Dig Dataset}
+		\label{fig:attribute big dataset}
+	\end{subfigure}
+
+	% 5. 全局总标题
+	\caption{\textcolor{violet}TrinityExtension——Attribution}
+	\label{fig:TrinityExtension——Attribution_main}
+\end{figure*}
+
 	\subsubsection{Scalability Study}
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
 Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+%	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
 Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}
+Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}
 
@@
 
-	\begin{figure}[t]
-		\centering
-
-		\hspace*{5pt}
-		% 放大的图例（占满单栏）
-		\includegraphics[width=0.98\columnwidth]{figures/exp/attribute_legend.pdf}
-
-		%\vspace{0.1cm}
-		\begin{subfigure}[t]{0.98\columnwidth}
-		\centering
-		% First plot for the shared subfigure
-		\includegraphics[width=0.507\linewidth]{figures/exp/attribute_multimodel.pdf}
-		\hfill % Pushes the two plots apart
-		% Second plot for the shared subfigure
-		\includegraphics[width=0.48\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-
-		% Shared caption for the two plots above
-		\captionsetup{font=small}
+% 使用 figure* 环境来实现图片横跨双栏
+% 使用 figure* 环境来实现图片横跨双栏
+
+	\subsection{Range Filtering}
+
+	\subsubsection{Time and Space overhead of index construction.}
+
+\begin{figure*}[t]
+	\centering
+
+	% 1. 全局图例 (Legend) - 位置保持不变
+	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
+
+	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+
+	% 2. 第一部分：两张图，共用标题
+	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+	% 宽度从\textwidth缩小到0.32\textwidth
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
+		\hfill 
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
 		\caption{MultiModal}
-		\label{fig:MultiModal} % A single label for the combined subfigure
-		\end{subfigure}
-
-		\begin{subfigure}[t]{0.507\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/exp/attribute_85.pdf}
-			\caption{\footnotesize Different Computer}
-			\label{fig:Different Computer}
-		\end{subfigure}
+		\label{fig:range-multimodal} 
+	\end{subfigure}
+	\hfill % 在第一部分和第二部分之间添加弹性间距
+	% 3. 第二部分：两张图，共用标题
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
 		\hfill
-		\begin{subfigure}[t]{0.48\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/exp/attribute_100M.pdf}
-			\caption{\footnotesize Big Dataset}
-			\label{fig:Big Dataset}
-		\end{subfigure}
-
-		\caption{\textcolor{violet}TrinityExtension——Attribution}
-		\label{fig:TrinityExtension——Attribution}
-	\end{figure}
-
-	\subsection{Range Filtering}
-
-	\subsubsection{Time and Space overhead of index construction.}
-
-	\begin{figure}[t]
-		\centering
-
-		\hspace*{5pt}
-		% 放大的图例（占满单栏）
-		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
-
-		%\vspace{0.1cm}
-
-		% 三图横排
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\captionsetup{font=small}
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
-			\caption{\footnotesize Construction time}
-			\label{fig:rangeFilter_build_time}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
-			\caption{\footnotesize Index size}
-			\label{fig:rangeFilter_index_size_mb}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
-			\caption{\footnotesize Build peak memory}
-			\label{fig:rangeFilter_build_memory_mb}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
-			\caption{\footnotesize Search peak memory}
-			\label{fig:rangeFilter_search_memory_mb}
-		\end{subfigure}
-
-		%		\caption{Time and space overhead of range filtering index construction}
-%		\caption{Time and space overhead of index construction}
-		\caption{\textcolor{violet}{Time and space overhead}}
-		\label{fig:rangeFilter_build_index_comparison}
-	\end{figure}
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
+		\caption{Cross-Platform}
+		\label{fig:range-cross-platform}
+	\end{subfigure}
+	\hfill % 在第二部分和第三部分之间添加弹性间距
+	% 4. 第三部分：只有一张图
+	\begin{subfigure}[b]{0.203\textwidth}
+		\centering
+		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
+		\caption{Dig Dataset}
+		\label{fig: range big dataset}
+	\end{subfigure}
+
+	% 5. 全局总标题
+	\caption{\textcolor{violet}TrinityExtension——Range}
+	\label{fig:TrinityExtension——Attribution_main}
+\end{figure*}
 
@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-%	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
+\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.
+	However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
 
@@
 
-	\textcolor{orange}{Note: For large-scale datasets, all algorithms are built using 64 threads for efficiency, except DSG, which only supports single-threaded construction.
-As a result, DSG takes significantly longer to build on Deep100M.
-	}
-
 	\textit{\textbf{Index size.}} 
@@
 Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
-	%On low-dimensional datasets (Deep, YT-Audio), 
-	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
-	\textcolor{orange}{DSG is an improvement over SeRF.
-Compared to SeRF, DSG stores additional information for each edge in its index structure, resulting in a significant increase in index size on large-scale datasets.
-	}
-
-	%SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
+	On low-dimensional datasets (Deep, YT-Audio), PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
+
+	SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
 
 	\textit{\textbf{Build peak memory.}}
-	\textcolor{orange}{As explained in the build peak memory analysis for attribute filtering, the build peak memory depends on the sum of the index size and the dataset size, as shown in Figure~\ref{fig:rangeFilter_build_memory_mb}.
-Range filtering also follows this pattern.
-The reason why PASE deviates from this trend has been discussed earlier, and is not repeated here to save space.}
-
-%	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
-%	
-%	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
+	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
+
+	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
 This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
-%	
-%	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage.
+	%因为低维空间中数据点之间的欧氏距离普遍较小，点与点之间更易互为近邻，从而导致图索引中产生大量冗余的边连接。
+
+	%As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio).
+It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.
+
+	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage.
 It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
@@
 This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
-%	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
+	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
+	%Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.
 
 		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}
+
+	%	\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, Faiss and Milvus have the lowest peak memory usage during search.
+Similar to attribute filtering, Faiss also has a smaller index size and no other additional memory usage, so the peak memory usage in range queries is slightly higher than the index size.
+Milvus reason:.
+WinFilter achieves the highest peak memory usage on almost all datasets.
+The reason is:.
+For the high-dimensional dataset WIT, UNIFY occupies the highest peak memory.
+The reason is:.}
+
 		\textcolor{orange}{As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
-As we analyzed in the section on attribute filtering.
-		}
+The algorithm needs to load the complete index into memory during search.
+Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
+For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}
 
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
-When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
+	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on Server B, with results presented in Figure~\ref{fig:Different_Computer_range}.
+When compared with the experimental results of Server A shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}
@@
 			\hline
-			\textbf{Query Performance} & H & M & H & M &\textbf{H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
+			\textbf{Query Performance} & H & M & H & M &\textbf{ H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
 			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
@@
 
-			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H} &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
+			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H } &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
 			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
-			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
-			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
-			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
+			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &H  &L  &M  &H  &M  &H  &H  &H/H  &M/M  &L/L  &L/L  &-/-  \\
+			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &H/-  &L/-  &L/-  \\
+			\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &M  &L  &L/  &L/  \\
 			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\

### 2025-07-24 VLDB2026/main.tex

--- 2025-07-24 VLDB2026/main.tex
@@
 Their performance drops less compared to in-distribution (ID) datasets such as GIST1M and GloVe, indicating better adaptability to OOD queries.}
+
+\begin{figure*}[t]
+	\centering
+
+	% 1. 全局图例 (Legend) - 位置保持不变
+	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}
+
+	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+
+	% 2. 第一部分：两张图，共用标题
+	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+	% 宽度从\textwidth缩小到0.32\textwidth
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
+		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
+		\hfill 
+		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
+		\caption{MultiModal}
+		\label{fig:attribute-multimodal} 
+	\end{subfigure}
+	\hfill % 在第一部分和第二部分之间添加弹性间距
+	% 3. 第二部分：两张图，共用标题
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
+		\hfill
+		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
+		\caption{Cross-Platform}
+		\label{fig:attribute-cross-platform}
+	\end{subfigure}
+	\hfill % 在第二部分和第三部分之间添加弹性间距
+	% 4. 第三部分：只有一张图
+	\begin{subfigure}[b]{0.203\textwidth}
+		\centering
+		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
+		\caption{Dig Dataset}
+		\label{fig:attribute big dataset}
+	\end{subfigure}
+
+	% 5. 全局总标题
+	\caption{\textcolor{violet}TrinityExtension——Attribution}
+	\label{fig:TrinityExtension——Attribution_main}
+\end{figure*}
 

### 2025-07-24 VLDB2026/main.tex
modify attribute distribution

--- 2025-07-24 VLDB2026/main.tex
@@
 
-	Among all algorithms, ACORN-\(\gamma\) shows the highest robustness.
+	{\color{blue}{
+		Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
+For instance, graph-based indexing methods like FilteredVamana and NHQ are prone to degraded connectivity or distorted structures under power-law distributions, where label frequencies are highly imbalanced.
+Similarly, VBASE, which employs a post-filtering strategy, shows efficiency that directly correlates with attribute selectivity—the more selective the filter, the more computational resources are wasted on retrieving irrelevant vectors.
+FAISS-IVF, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.
+
+		In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges.
+Milvus, for example, leverages a built-in query optimizer that dynamically determines whether to filter by attributes or search vectors first, based on the selectivity of the query, thus ensuring more robust performance.
+Other approaches enhance robustness by separating attribute and vector indexing into distinct stages: UNG uses a logical graph to navigate attribute relationships, while CAPS employs an attribute frequency tree to adapt to power-law patterns.
+ACORN takes a different approach by disregarding attribute distribution entirely during index construction—it builds an ultra-dense, oversaturated graph to ensure that the remaining subgraph, even after aggressive attribute filtering, is still likely to be well-connected and searchable.}}
+
+%	Among all algorithms, ACORN-\(\gamma\) shows the highest robustness.
 During index construction, attribute is mainly used for pruning in the lowest layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
 As a result, changes in attribute distribution have a limited impact on overall performance.
-
-	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency.
+%	
+%	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency.
 However, its performance declines under power-law and normal distributions: power-law distributions cause excessive concentration of popular labels and fragmentation of niche labels, disrupting search path connectivity, while normal distributions produce ambiguous graph structures due to label frequency similarities, leading to search divergence.
-	Under the power-law distribution, when the NHQ algorithm constructs an index based on fusion distance, points corresponding to high-frequency attribute values make the graph connections extremely dense, while points corresponding to low-frequency attribute values tend to become isolated due to sparse connections.
+%	Under the power-law distribution, when the NHQ algorithm constructs an index based on fusion distance, points corresponding to high-frequency attribute values make the graph connections extremely dense, while points corresponding to low-frequency attribute values tend to become isolated due to sparse connections.
 This extreme imbalance in connectivity severely distorts the structure of the graph, ultimately significantly impairing the overall performance of the algorithm.
-	The search performance of VBASE exhibits a direct dependence on attribute selectivity.
+%	The search performance of VBASE exhibits a direct dependence on attribute selectivity.
 As selectivity decreases, search speed declines.

### 2025-07-24 Revision/response.tex
Update response.tex

@@
 
-\textbf{WIT-Real dataset:} We use the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes, applying them in both attribute filtering and range filtering experiments.
+\textbf{WIT-Real dataset:} We use the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extract the language type and the length of the \texttt{context\_page\_}
+\texttt{description} field as real attributes, applying them in both attribute filtering and range filtering experiments.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We add relevant experiments conducted on different servers in Section 4.2.4. Please refer to the response MR.R4 for more details.
+Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4. Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 We agree that the initial explanations accompanying the performance results were not sufficiently detailed in highlighting the strengths and weaknesses of the compared algorithms.
-We conduct a more in-depth analysis of the reasons behind certain behaviors observed in the experimental results.
+We have conducted a more in-depth analysis of the reasons behind certain behaviors observed in the experimental results.
 The specific revisions are as follows:

### 2025-07-24 VLDB2026/main.tex
Update main.tex

--- 2025-07-24 VLDB2026/main.tex
@@
 				\vspace{0.1cm}
-				Win: WinFilter, Filtered: Filtered-DiskANN, Stitched: StitchedVamana. 
+				\textsuperscript{A} Post-filtering, 
 				\textsuperscript{B} Pre-filtering, 
@@
 				\textit{Disk Support} indicates whether the algorithm supports disk storage.
-				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
+				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm.
 		\end{minipage}}
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the 6 datasets shown in the left figure, and 64 threads on the large-scale Deep100M dataset.}
 
@@
 	\textit{\textbf{Index construction time.}}
-\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN.
-PASE and VBASE only support single-threaded builds, and PASE is the slowest to build because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster.
-ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates.
-The build time on some datasets even exceeds that of single-threaded VBASE.
-}
-
-\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also find that graph-based algorithms using pruning strategies (such as FilteredDiskANN and UNG) exhibit significantly increased construction time, especially when the pruning is complex and extensive, leading to higher computational overhead.
-In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
-
-%ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.
-
-%\textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time.
+	%As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 6 datasets, PASE has the longest index construction time due to its single-thread indexing support.
+Additionally, VBASE also supports only single-thread indexing but achieves better performance than PASE.
+	 \textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time.
 The on-demand loading and caching strategy used by PASE results in frequent disk I/O and page scheduling, which significantly slow down the construction process.
 In contrast, VBASE uses full in-memory construction, leading to faster indexing.}
-%
-%
-%For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction.
+
+	For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction.
 This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.
@@
 \textcolor{orange}{Its construction time on some datasets is even slower than that of the single-threaded VBASE.}
-%
-%On large dataset Deep100M, VBASE takes longer to build because it only supports single-threaded construction.
-The other time-consuming algorithms are all graph-based methods, which employ complex pruning strategies during construction to optimize query performance, leading to significantly increased build times.
 
@@
 
-for big dataset:
 	 %\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
@@
 	\textit{\textbf{Build peak memory.}}
-% As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
-% %on small-scale datasets, all methods except NHQ exhibit low memory usage. 
-% \textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
-% This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
-% 
-% On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
+	As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
+	%on small-scale datasets, all methods except NHQ exhibit low memory usage. 
+	\textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
+	This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
+
+	On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
 \textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index.
 }.
-\textcolor{orange}{As shown in the Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size generated by the algorithm and the dataset size.
-This trend holds consistently across different datasets.
-However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the index size itself.
-For large-scale datasets, algorithms that produce larger indexes tend to cause significantly higher peak memory consumption during construction.}
 
 	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
-%  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
+	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
 Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
-\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
-However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets.
-In contrast, Milvus has lower query-time memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
-}
 
@@
 To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
-\textcolor{orange}{In this experiment, we only evaluate the algorithms that support this query scenario.}
-	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
-	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
+\textcolor{violet}{In this experiment, we only evaluate algorithms that support this multi-attribute query scenario.}
+
+	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG still maintains the best performance across all datasets.
+Since some strong competing algorithms do not support multi-attribute querying, CAPS becomes the second-best algorithm, but its performance on small datasets is relatively poor.
+This is because CAPS performs multi-level partitioning based on attributes on top of the IVF index, which introduces additional overhead.
+While this overhead negatively impacts performance on small datasets, on large datasets, the overhead is amortized, and the increasing dataset scale makes the advantages of attribute-aware partitioning evident.
+
+	NHQ performs moderately overall in multi-attribute joint filtering scenarios but poorly on small datasets.
+Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
+
+	For IVF-based methods not specifically optimized for hybrid queries (Faiss and Milvus), their QPS shows a similar and relatively stable trend as recall varies.
+Among them, Milvus, as a general-purpose system, exhibits comparatively poor performance.
+
+%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios.
+To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
+\textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
+Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
+%	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
+%	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
 To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.
-
-	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
+%	
+%	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
 For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies.
 Milvus, as a general-purpose system, exhibits comparatively poor performance.
-
-		The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance.
+%	
+%
+%	The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance.
 It naturally supports pre-filtering and remains unaffected by the increasing number of attributes.
@@
 However, on large datasets, the overhead is amortized, and the advantages of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
+%	
+%	NHQ performs moderately overall but poorly on small datasets.
+Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
 
@@
 The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
-	NHQ performs moderately overall but poorly on small datasets.
-Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
 
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+\textcolor{cyan}{The proximity of the 4 curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
+Conversely, greater divergence among the curves indicates higher distributional dependence.
+Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
@@
 
-\begin{figure*}[t]
-	\centering
-
-	% 1. 全局图例 (Legend) - 位置保持不变
-	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}
-
-	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
-
-	% 2. 第一部分：两张图，共用标题
-	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
-	% 宽度从\textwidth缩小到0.32\textwidth
-	\begin{subfigure}[b]{0.39\textwidth}
-		\centering
-		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
-		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
-		\hfill 
-		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-		\caption{MultiModal}
-		\label{fig:attribute-multimodal} 
-	\end{subfigure}
-	\hfill % 在第一部分和第二部分之间添加弹性间距
-	% 3. 第二部分：两张图，共用标题
-	\begin{subfigure}[b]{0.39\textwidth}
-		\centering
-		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
-		\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
-		\caption{Cross-Platform}
-		\label{fig:attribute-cross-platform}
-	\end{subfigure}
-	\hfill % 在第二部分和第三部分之间添加弹性间距
-	% 4. 第三部分：只有一张图
-	\begin{subfigure}[b]{0.203\textwidth}
-		\centering
-		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
-		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
-		\caption{Dig Dataset}
-		\label{fig:attribute big dataset}
-	\end{subfigure}
-
-	% 5. 全局总标题
-	\caption{\textcolor{violet}TrinityExtension——Attribution}
-	\label{fig:TrinityExtension——Attribution_main}
-\end{figure*}
-
 	\subsubsection{Scalability Study}
@@
 
-% 使用 figure* 环境来实现图片横跨双栏
-% 使用 figure* 环境来实现图片横跨双栏
+	\begin{figure}[t]
+		\centering
+
+		\hspace*{5pt}
+		% 放大的图例（占满单栏）
+		\includegraphics[width=0.98\columnwidth]{figures/exp/attribute_legend.pdf}
+
+		%\vspace{0.1cm}
+		\begin{subfigure}[t]{0.98\columnwidth}
+		\centering
+		% First plot for the shared subfigure
+		\includegraphics[width=0.507\linewidth]{figures/exp/attribute_multimodel.pdf}
+		\hfill % Pushes the two plots apart
+		% Second plot for the shared subfigure
+		\includegraphics[width=0.48\linewidth]{figures/exp/attribute_multimodel_1.pdf}
+
+		% Shared caption for the two plots above
+		\captionsetup{font=small}
+		\caption{MultiModal}
+		\label{fig:MultiModal} % A single label for the combined subfigure
+		\end{subfigure}
+
+		\begin{subfigure}[t]{0.507\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/exp/attribute_85.pdf}
+			\caption{\footnotesize Different Computer}
+			\label{fig:Different Computer}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.48\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/exp/attribute_100M.pdf}
+			\caption{\footnotesize Big Dataset}
+			\label{fig:Big Dataset}
+		\end{subfigure}
+
+		\caption{\textcolor{violet}TrinityExtension——Attribution}
+		\label{fig:TrinityExtension——Attribution}
+	\end{figure}
 
@@
 
-\begin{figure*}[t]
-	\centering
-
-	% 1. 全局图例 (Legend) - 位置保持不变
-	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
-
-	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
-
-	% 2. 第一部分：两张图，共用标题
-	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
-	% 宽度从\textwidth缩小到0.32\textwidth
-	\begin{subfigure}[b]{0.39\textwidth}
-		\centering
-		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
-		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
+	\begin{figure}[t]
+		\centering
+
+		\hspace*{5pt}
+		% 放大的图例（占满单栏）
+		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
+
+		%\vspace{0.1cm}
+
+		% 三图横排
+		\begin{subfigure}[t]{0.495\columnwidth}
+			\centering
+			\captionsetup{font=small}
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
+			\caption{\footnotesize Construction time}
+			\label{fig:rangeFilter_build_time}
+		\end{subfigure}
 		\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
-		\caption{MultiModal}
-		\label{fig:range-multimodal} 
-	\end{subfigure}
-	\hfill % 在第一部分和第二部分之间添加弹性间距
-	% 3. 第二部分：两张图，共用标题
-	\begin{subfigure}[b]{0.39\textwidth}
-		\centering
-		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
+		\begin{subfigure}[t]{0.495\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
+			\caption{\footnotesize Index size}
+			\label{fig:rangeFilter_index_size_mb}
+		\end{subfigure}
 		\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
-		\caption{Cross-Platform}
-		\label{fig:range-cross-platform}
-	\end{subfigure}
-	\hfill % 在第二部分和第三部分之间添加弹性间距
-	% 4. 第三部分：只有一张图
-	\begin{subfigure}[b]{0.203\textwidth}
-		\centering
-		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
-		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
-		\caption{Dig Dataset}
-		\label{fig: range big dataset}
-	\end{subfigure}
-
-	% 5. 全局总标题
-	\caption{\textcolor{violet}TrinityExtension——Range}
-	\label{fig:TrinityExtension——Attribution_main}
-\end{figure*}
+		\begin{subfigure}[t]{0.495\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
+			\caption{\footnotesize Build peak memory}
+			\label{fig:rangeFilter_build_memory_mb}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.495\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
+			\caption{\footnotesize Search peak memory}
+			\label{fig:rangeFilter_search_memory_mb}
+		\end{subfigure}
+
+		%		\caption{Time and space overhead of range filtering index construction}
+%		\caption{Time and space overhead of index construction}
+		\caption{\textcolor{violet}{Time and space overhead}}
+		\label{fig:rangeFilter_build_index_comparison}
+	\end{figure}
 
@@
 
-			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H} &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
+			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H } &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
 			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
-			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
-			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
-			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
+			\textbf{Insensitive to Data Distribution} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
+			\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
 			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\

### 2025-07-24 VLDB2026/main.tex

--- 2025-07-24 VLDB2026/main.tex
@@
 
-	{\color{blue}{
-		Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
-For instance, graph-based indexing methods like FilteredVamana and NHQ are prone to degraded connectivity or distorted structures under power-law distributions, where label frequencies are highly imbalanced.
-Similarly, VBASE, which employs a post-filtering strategy, shows efficiency that directly correlates with attribute selectivity—the more selective the filter, the more computational resources are wasted on retrieving irrelevant vectors.
-FAISS-IVF, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.
-
-		In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges.
-Milvus, for example, leverages a built-in query optimizer that dynamically determines whether to filter by attributes or search vectors first, based on the selectivity of the query, thus ensuring more robust performance.
-Other approaches enhance robustness by separating attribute and vector indexing into distinct stages: UNG uses a logical graph to navigate attribute relationships, while CAPS employs an attribute frequency tree to adapt to power-law patterns.
-ACORN takes a different approach by disregarding attribute distribution entirely during index construction—it builds an ultra-dense, oversaturated graph to ensure that the remaining subgraph, even after aggressive attribute filtering, is still likely to be well-connected and searchable.}}
-
-%	Among all algorithms, ACORN-\(\gamma\) shows the highest robustness.
+	Among all algorithms, ACORN-\(\gamma\) shows the highest robustness.
 During index construction, attribute is mainly used for pruning in the lowest layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
 As a result, changes in attribute distribution have a limited impact on overall performance.
-%	
-%	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency.
+
+	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency.
 However, its performance declines under power-law and normal distributions: power-law distributions cause excessive concentration of popular labels and fragmentation of niche labels, disrupting search path connectivity, while normal distributions produce ambiguous graph structures due to label frequency similarities, leading to search divergence.
-%	Under the power-law distribution, when the NHQ algorithm constructs an index based on fusion distance, points corresponding to high-frequency attribute values make the graph connections extremely dense, while points corresponding to low-frequency attribute values tend to become isolated due to sparse connections.
+	Under the power-law distribution, when the NHQ algorithm constructs an index based on fusion distance, points corresponding to high-frequency attribute values make the graph connections extremely dense, while points corresponding to low-frequency attribute values tend to become isolated due to sparse connections.
 This extreme imbalance in connectivity severely distorts the structure of the graph, ultimately significantly impairing the overall performance of the algorithm.
-%	The search performance of VBASE exhibits a direct dependence on attribute selectivity.
+	The search performance of VBASE exhibits a direct dependence on attribute selectivity.
 As selectivity decreases, search speed declines.

### 2025-07-24 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 		\multirow{6}{*}{\textbf{AF}} 
-		& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
+		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
 		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
@@
 		\multicolumn{2}{|l|}{\textbf{RF}}             & N & N & N & N & Y & N & N & Y & Y & Y & Y & Y \\ \hline
+			\multicolumn{2}{|l|}{\textbf{Filter Type }}             & C & C & C & C & B & B & B & B & B & B & A/B/C & A \\ \hline
 		\multicolumn{2}{|l|}{\textbf{Dynamic Insert}} & N & Y & N & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
@@
 				\vspace{0.1cm}
-				Win: WinFilter, Filtered: Filtered-DiskANN, Stitched: StitchedVamana. 
+				Win: WinFilter, Filtered: FilteredVamana, Stitched: StitchedVamana. 
+				\textsuperscript{A} Post-filtering, 
 				\textsuperscript{B} Pre-filtering, 
@@
 To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
-\textcolor{violet}{In this experiment, we only evaluate algorithms that support this multi-attribute query scenario.}
-
-	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG still maintains the best performance across all datasets.
-Since some strong competing algorithms do not support multi-attribute querying, CAPS becomes the second-best algorithm, but its performance on small datasets is relatively poor.
-This is because CAPS performs multi-level partitioning based on attributes on top of the IVF index, which introduces additional overhead.
-While this overhead negatively impacts performance on small datasets, on large datasets, the overhead is amortized, and the increasing dataset scale makes the advantages of attribute-aware partitioning evident.
-
-	NHQ performs moderately overall in multi-attribute joint filtering scenarios but poorly on small datasets.
-Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
-
-	For IVF-based methods not specifically optimized for hybrid queries (Faiss and Milvus), their QPS shows a similar and relatively stable trend as recall varies.
-Among them, Milvus, as a general-purpose system, exhibits comparatively poor performance.
-
-%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios.
-To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
-\textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
-Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
-%	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
-%	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
+\textcolor{orange}{In this experiment, we only evaluate the algorithms that support this query scenario.}
+	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
+	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
 To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.
-%	
-%	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
+
+	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
 For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies.
 Milvus, as a general-purpose system, exhibits comparatively poor performance.
-%	
-%
-%	The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance.
+
+		The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance.
 It naturally supports pre-filtering and remains unaffected by the increasing number of attributes.
@@
 However, on large datasets, the overhead is amortized, and the advantages of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
-%	
-%	NHQ performs moderately overall but poorly on small datasets.
-Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
 
@@
 The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
+	NHQ performs moderately overall but poorly on small datasets.
+Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
 

### 2025-07-24 VLDB2026/main.tex
Update main.tex

@@
 Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
-Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
+Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}
@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
-When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
+When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-24 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 		\multirow{6}{*}{\textbf{AF}} 
-		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
+		& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
 		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
@@
 		\multicolumn{2}{|l|}{\textbf{RF}}             & N & N & N & N & Y & N & N & Y & Y & Y & Y & Y \\ \hline
-			\multicolumn{2}{|l|}{\textbf{Filter Type }}             & C & C & C & C & B & B & B & B & B & B & A/B/C & A \\ \hline
 		\multicolumn{2}{|l|}{\textbf{Dynamic Insert}} & N & Y & N & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
@@
 				\vspace{0.1cm}
-				Win: WinFilter, Filtered: FilteredVamana, Stitched: StitchedVamana. 
-				\textsuperscript{A} Post-filtering, 
+				Win: WinFilter, Filtered: Filtered-DiskANN, Stitched: StitchedVamana. 
 				\textsuperscript{B} Pre-filtering, 
@@
 
+	\begin{figure}[t]
+		\centering
+
+		\hspace*{5pt}
+		% 放大的图例（占满单栏）
+		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
+
+		%\vspace{0.1cm}
+
+		% 三图横排
+		\begin{subfigure}[t]{0.495\columnwidth}
+			\centering
+			\captionsetup{font=small}
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
+			\caption{\footnotesize Construction time}
+			\label{fig:rangeFilter_build_time}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.495\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
+			\caption{\footnotesize Index size}
+			\label{fig:rangeFilter_index_size_mb}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.495\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
+			\caption{\footnotesize Build peak memory}
+			\label{fig:rangeFilter_build_memory_mb}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.495\columnwidth}
+			\centering
+			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
+			\caption{\footnotesize Search peak memory}
+			\label{fig:rangeFilter_search_memory_mb}
+		\end{subfigure}
+
+		%		\caption{Time and space overhead of range filtering index construction}
+%		\caption{Time and space overhead of index construction}
+		\caption{\textcolor{violet}{Time and space overhead}}
+		\label{fig:rangeFilter_build_index_comparison}
+	\end{figure}
 	\subsection{Range Filtering}
@@
 	\subsubsection{Time and Space overhead of index construction.}
-
-\begin{figure*}[t]
-	\centering
-
-	% 1. 全局图例 (Legend) - 位置保持不变
-	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
-
-	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
-
-	% 2. 第一部分：两张图，共用标题
-	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
-	% 宽度从\textwidth缩小到0.32\textwidth
-	\begin{subfigure}[b]{0.39\textwidth}
-		\centering
-		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
-		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
-		\hfill 
-		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
-		\caption{MultiModal}
-		\label{fig:range-multimodal} 
-	\end{subfigure}
-	\hfill % 在第一部分和第二部分之间添加弹性间距
-	% 3. 第二部分：两张图，共用标题
-	\begin{subfigure}[b]{0.39\textwidth}
-		\centering
-		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
-		\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
-		\caption{Cross-Platform}
-		\label{fig:range-cross-platform}
-	\end{subfigure}
-	\hfill % 在第二部分和第三部分之间添加弹性间距
-	% 4. 第三部分：只有一张图
-	\begin{subfigure}[b]{0.203\textwidth}
-		\centering
-		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
-		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
-		\caption{Dig Dataset}
-		\label{fig: range big dataset}
-	\end{subfigure}
-
-	% 5. 全局总标题
-	\caption{\textcolor{violet}TrinityExtension——Range}
-	\label{fig:TrinityExtension——Attribution_main}
-\end{figure*}
 
@@
 This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.
+\begin{figure*}[t]
+	\centering
+
+	% 1. 全局图例 (Legend) - 位置保持不变
+	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
+
+	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+
+	% 2. 第一部分：两张图，共用标题
+	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+	% 宽度从\textwidth缩小到0.32\textwidth
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
+		\hfill 
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
+		\caption{MultiModal}
+		\label{fig:range-multimodal} 
+	\end{subfigure}
+	\hfill % 在第一部分和第二部分之间添加弹性间距
+	% 3. 第二部分：两张图，共用标题
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
+		\hfill
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
+		\caption{Cross-Platform}
+		\label{fig:range-cross-platform}
+	\end{subfigure}
+	\hfill % 在第二部分和第三部分之间添加弹性间距
+	% 4. 第三部分：只有一张图
+	\begin{subfigure}[b]{0.203\textwidth}
+		\centering
+		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
+		\caption{Dig Dataset}
+		\label{fig: range big dataset}
+	\end{subfigure}
+
+	% 5. 全局总标题
+	\caption{\textcolor{violet}TrinityExtension——Range}
+	\label{fig:TrinityExtension——Attribution_main}
+\end{figure*}
 
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
 When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
@@
 	\textcolor{blue}{
-	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModal_range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
 As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
@@
 %	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
-
-\begin{figure}[t]
-	\centering
-
-	% Legend
-	\includegraphics[width=0.98\columnwidth]{figures/exp/range_legend.pdf}
-	\vspace{0.2cm} % Added a little space after the legend
-
-	% --- Subfigure (a) containing two plots ---
-	\begin{subfigure}[t]{0.98\columnwidth}
-		\centering
-		% First plot for the shared subfigure
-		\includegraphics[width=0.507\linewidth]{figures/exp/range_multimodel.pdf}
-		\hfill % Pushes the two plots apart
-		% Second plot for the shared subfigure
-		\includegraphics[width=0.48\linewidth]{figures/exp/range_multimodel_1.pdf}
-
-		% Shared caption for the two plots above
-		\captionsetup{font=small}
-		\caption{MultiModal}
-		\label{fig:MultiModal_range} % A single label for the combined subfigure
-	\end{subfigure}
-
-	% --- Subfigure (b) ---
-	\begin{subfigure}[t]{0.507\columnwidth}
-		\centering
-		\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
-		\captionsetup{font=small}
-		\caption{Different Computer}
-		\label{fig:Different_Computer_range}
-	\end{subfigure}
-	\hfill
-	% --- Subfigure (c) ---
-	\begin{subfigure}[t]{0.48\columnwidth}
-		\centering
-		\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
-		\captionsetup{font=small}
-		\caption{Big Dataset}
-		\label{fig:Big_Dataset_range}
-	\end{subfigure}
-
-	\caption{\textcolor{red}{TrinityExtension——Range}}
-	\label{fig:TrinityExtension——Range}
-\end{figure}
-
 	\section{DISCUSSION}

### 2025-07-24 VLDB2026/main.tex

--- 2025-07-24 VLDB2026/main.tex
@@
 
-	% Legend
-	\includegraphics[width=0.98\columnwidth]{figures/exp/range_legend.pdf}
-	\vspace{0.2cm} % Added a little space after the legend
-
-	% --- Subfigure (a) containing two plots ---
-	\begin{subfigure}[t]{0.98\columnwidth}
-		\centering
-		% First plot for the shared subfigure
-		\includegraphics[width=0.507\linewidth]{figures/exp/range_multimodel.pdf}
-		\hfill % Pushes the two plots apart
-		% Second plot for the shared subfigure
-		\includegraphics[width=0.48\linewidth]{figures/exp/range_multimodel_1.pdf}
-
-		% Shared caption for the two plots above
-		\captionsetup{font=small}
+	% 1. 全局图例 (Legend) - 位置保持不变
+	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
+
+	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+
+	% 2. 第一部分：两张图，共用标题
+	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+	% 宽度从\textwidth缩小到0.32\textwidth
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
+		\hfill 
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
 		\caption{MultiModal}
-		\label{fig:MultiModal_range} % A single label for the combined subfigure
-	\end{subfigure}
-
-	% --- Subfigure (b) ---
-	\begin{subfigure}[t]{0.507\columnwidth}
-		\centering
-		\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
-		\captionsetup{font=small}
-		\caption{Different Computer}
-		\label{fig:Different_Computer_range}
-	\end{subfigure}
+		\label{fig:range-multimodal} 
+	\end{subfigure}
+	\hfill % 在第一部分和第二部分之间添加弹性间距
+	% 3. 第二部分：两张图，共用标题
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
 		\hfill
-	% --- Subfigure (c) ---
-	\begin{subfigure}[t]{0.48\columnwidth}
-		\centering
-		\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
-		\captionsetup{font=small}
-		\caption{Big Dataset}
-		\label{fig:Big_Dataset_range}
-	\end{subfigure}
-
-	\caption{\textcolor{red}{TrinityExtension——Range}}
-	\label{fig:TrinityExtension——Range}
-\end{figure}
-
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
+		\caption{Cross-Platform}
+		\label{fig:range-cross-platform}
+	\end{subfigure}
+	\hfill % 在第二部分和第三部分之间添加弹性间距
+	% 4. 第三部分：只有一张图
+	\begin{subfigure}[b]{0.203\textwidth}
+		\centering
+		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
+		\caption{Dig Dataset}
+		\label{fig: range big dataset}
+	\end{subfigure}
+
+	% 5. 全局总标题
+	\caption{\textcolor{violet}TrinityExtension——Range}
+	\label{fig:TrinityExtension——Attribution_main}
+\end{figure*}
+
+	\subsubsection{Scalability Study}
+
+	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
+When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
+For brevity and due to space limitations, we omit further discussion of these redundant results.}
+%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}.
+Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4.
+Due to space constraints, these details are not reiterated here.}
+
+	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.
+
+	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
+	\textcolor{blue}{
+	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets.}
+
+%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
 	\section{DISCUSSION}

### 2025-07-24 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} We believe this is an excellent suggestion.
-In fact, in the initial version of our paper, we use the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms.
+In fact, in the initial version of our paper, we used the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms.
 In this dataset, the base vectors are images, while the query set consists of texts, resulting in a modality gap between the two.
@@
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors. Please see section 4.2.4.
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.
 
-\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b).
-Compared with the experimental results on the original server (as shown in Figure 4d), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods."}
+For attribute filtering, Please see section 4.2.4.
+
+\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
+Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
+
+For range filtering,please see section 4.3.4.
+
+\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
+When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
+For brevity and due to space limitations, we omit further discussion of these redundant results."}
 

### 2025-07-24 VLDB2026/main.tex
1

@@
 
-	\subsubsection{Scalability Study}
-
-	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
-When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
-For brevity and due to space limitations, we omit further discussion of these redundant results.}
-%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}.
-Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4.
-Due to space constraints, these details are not reiterated here.}
-
-	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.
-
-	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
-	\textcolor{blue}{
-	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModal_range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
-As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
-This is because these range query algorithms are almost graph-based.
-Graph algorithms need more iterations to find true neighbors in OOD datasets.}
-
-%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
-
-\begin{figure}[t]
+\begin{figure*}[t]
 	\centering

### 2025-07-24 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 \textit{\textbf{Index size.}}
-As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets.
+\textcolor{orange}{
+	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
+For regular-scale datasets, other methods show moderate variation.
+However, on large-scale dataset, the index sizes of ACORN and FilteredDiskANN increase sharply.
+The reason is xxx.
+Overall, IVF-based methods tend to produce more compact indexes.
+}
+
+%As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets.
 This overhead stems primarily from its extensive metadata requirements.
 The index sizes of other methods show moderate variation.
-\textcolor{orange}{Among these, we observe a trend that IVF-based methods tend to produce more compact indexes compared to graph-based methods.}
-
-for big dataset:
+%\textcolor{orange}{Among these, we observe a trend that IVF-based methods tend to produce more compact indexes compared to graph-based methods.}
+
 %\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
@@
 Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
-Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}
@@
 
-	\begin{figure}[t]
-		\centering
-
-		\hspace*{5pt}
-		% 放大的图例（占满单栏）
-		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
-
-		%\vspace{0.1cm}
-
-		% 三图横排
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\captionsetup{font=small}
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
-			\caption{\footnotesize Construction time}
-			\label{fig:rangeFilter_build_time}
-		\end{subfigure}
+	\subsection{Range Filtering}
+
+	\subsubsection{Time and Space overhead of index construction.}
+
+\begin{figure*}[t]
+	\centering
+
+	% 1. 全局图例 (Legend) - 位置保持不变
+	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
+
+	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+
+	% 2. 第一部分：两张图，共用标题
+	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+	% 宽度从\textwidth缩小到0.32\textwidth
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
 		\hfill 
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
-			\caption{\footnotesize Index size}
-			\label{fig:rangeFilter_index_size_mb}
-		\end{subfigure}
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
+		\caption{MultiModal}
+		\label{fig:range-multimodal} 
+	\end{subfigure}
+	\hfill % 在第一部分和第二部分之间添加弹性间距
+	% 3. 第二部分：两张图，共用标题
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
 		\hfill
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
-			\caption{\footnotesize Build peak memory}
-			\label{fig:rangeFilter_build_memory_mb}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
-			\caption{\footnotesize Search peak memory}
-			\label{fig:rangeFilter_search_memory_mb}
-		\end{subfigure}
-
-		%		\caption{Time and space overhead of range filtering index construction}
-%		\caption{Time and space overhead of index construction}
-		\caption{\textcolor{violet}{Time and space overhead}}
-		\label{fig:rangeFilter_build_index_comparison}
-	\end{figure}
-	\subsection{Range Filtering}
-
-	\subsubsection{Time and Space overhead of index construction.}
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
+		\caption{Cross-Platform}
+		\label{fig:range-cross-platform}
+	\end{subfigure}
+	\hfill % 在第二部分和第三部分之间添加弹性间距
+	% 4. 第三部分：只有一张图
+	\begin{subfigure}[b]{0.203\textwidth}
+		\centering
+		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
+		\caption{Dig Dataset}
+		\label{fig: range big dataset}
+	\end{subfigure}
+
+	% 5. 全局总标题
+	\caption{\textcolor{violet}TrinityExtension——Range}
+	\label{fig:TrinityExtension——Attribution_main}
+\end{figure*}
 
@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
-When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
+When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}
@@
 
-	% 1. 全局图例 (Legend) - 位置保持不变
-	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
-
-	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
-
-	% 2. 第一部分：两张图，共用标题
-	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
-	% 宽度从\textwidth缩小到0.32\textwidth
-	\begin{subfigure}[b]{0.39\textwidth}
-		\centering
-		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
-		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
+	% Legend
+	\includegraphics[width=0.98\columnwidth]{figures/exp/range_legend.pdf}
+	\vspace{0.2cm} % Added a little space after the legend
+
+	% --- Subfigure (a) containing two plots ---
+	\begin{subfigure}[t]{0.98\columnwidth}
+		\centering
+		% First plot for the shared subfigure
+		\includegraphics[width=0.507\linewidth]{figures/exp/range_multimodel.pdf}
+		\hfill % Pushes the two plots apart
+		% Second plot for the shared subfigure
+		\includegraphics[width=0.48\linewidth]{figures/exp/range_multimodel_1.pdf}
+
+		% Shared caption for the two plots above
+		\captionsetup{font=small}
+		\caption{MultiModal}
+		\label{fig:MultiModal_range} % A single label for the combined subfigure
+	\end{subfigure}
+
+	% --- Subfigure (b) ---
+	\begin{subfigure}[t]{0.507\columnwidth}
+		\centering
+		\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
+		\captionsetup{font=small}
+		\caption{Different Computer}
+		\label{fig:Different_Computer_range}
+	\end{subfigure}
 	\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
-		\caption{MultiModal}
-		\label{fig:range-multimodal} 
-	\end{subfigure}
-	\hfill % 在第一部分和第二部分之间添加弹性间距
-	% 3. 第二部分：两张图，共用标题
-	\begin{subfigure}[b]{0.39\textwidth}
-		\centering
-		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
-		\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
-		\caption{Cross-Platform}
-		\label{fig:range-cross-platform}
-	\end{subfigure}
-	\hfill % 在第二部分和第三部分之间添加弹性间距
-	% 4. 第三部分：只有一张图
-	\begin{subfigure}[b]{0.203\textwidth}
-		\centering
-		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
-		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
-		\caption{Dig Dataset}
-		\label{fig: range big dataset}
-	\end{subfigure}
-
-	% 5. 全局总标题
-	\caption{\textcolor{violet}TrinityExtension——Range}
-	\label{fig:TrinityExtension——Attribution_main}
-\end{figure*}
-
-	\subsubsection{Scalability Study}
-
-	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
-For brevity and due to space limitations, we omit further discussion of these redundant results.}
-%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}.
-Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4.
-Due to space constraints, these details are not reiterated here.}
-
-	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.
-
-	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
-	\textcolor{blue}{
-	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
-As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
-This is because these range query algorithms are almost graph-based.
-Graph algorithms need more iterations to find true neighbors in OOD datasets.}
-
-%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
+	% --- Subfigure (c) ---
+	\begin{subfigure}[t]{0.48\columnwidth}
+		\centering
+		\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
+		\captionsetup{font=small}
+		\caption{Big Dataset}
+		\label{fig:Big_Dataset_range}
+	\end{subfigure}
+
+	\caption{\textcolor{red}{TrinityExtension——Range}}
+	\label{fig:TrinityExtension——Range}
+\end{figure}
+
 	\section{DISCUSSION}

### 2025-07-24 VLDB2026/main.tex
Update main.tex

@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
+When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-24 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
+\textcolor{orange}{Note: For regular-scale datasets, all algorithms build indexes using a single thread.
+For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}
 %	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
@@
 As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.
-	%	shows the single-threaded index construction time.
-Faiss builds the index fastest.
-Because Faiss obtains subsamples through sampling and then calculates the cluster centroid, the computational complexity is significantly reduced.
 
@@
 However, this introduces additional overhead and slows down the construction process.
-
-	\textcolor{orange}{Note: For large-scale datasets, all algorithms are built using 64 threads for efficiency, except DSG, which only supports single-threaded construction.
-As a result, DSG takes significantly longer to build on Deep100M.
-	}
 
@@
 			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
-			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
+			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
 			\hline

### 2025-07-24 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 \textit{\textbf{Index size.}}
-\textcolor{orange}{
-	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
-For regular-scale datasets, other methods show moderate variation.
-However, on large-scale dataset, the index sizes of ACORN and FilteredDiskANN increase sharply.
-The reason is xxx.
-Overall, IVF-based methods tend to produce more compact indexes.
-}
-
-%As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets.
+As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets.
 This overhead stems primarily from its extensive metadata requirements.
 The index sizes of other methods show moderate variation.
-%\textcolor{orange}{Among these, we observe a trend that IVF-based methods tend to produce more compact indexes compared to graph-based methods.}
-
+\textcolor{orange}{Among these, we observe a trend that IVF-based methods tend to produce more compact indexes compared to graph-based methods.}
+
+for big dataset:
 %\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
@@
 	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
-	\textcolor{violet}{As shown in the figure~\ref{fig:Big Dataset}, On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
+	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
 The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
@@
 It is a more complex multimodal dataset.
-As shown in Figure~\ref{fig:MultiModal}, although the queries are more complex, UNG and NHQ still perform the best.
+As shown in Figure~\ref{fig:attribute-multimodal}, although the queries are more complex, UNG and NHQ still perform the best.
 CAPS is the next best.
@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
+When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-24 Revision/response.tex
Update response.tex

@@
 We acknowledge that the original manuscript did not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard graph-based and IVF-based index structures.
-We revise Section 2.2 and add two paragraphs.
+We have revised Section 2.2 and add two paragraphs.
 These paragraphs summarize how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures.
@@
 For datasets with recommended parameters provided in the original papers, we directly used those recommended settings.
-For other datasets, we select the parameter combinations that performed best through empirical evaluation.
+For other datasets, we selected the parameter combinations that performed best through empirical evaluation.
 All parameters used in the experiments are available in our public code repository.

### 2025-07-24 Revision/response.tex
Update response.tex

@@
 
-Of all the evaluated algorithms, only Faiss supports quantization.
-However, in our experiments, we used the IVF index structure of Faiss without employing quantization.
+Of all the evaluated algorithms, Faiss, Puck, DiskANN, and Milvus support quantization.
+However, in our experiments, we did not enable quantization in any of our experiments.
 Therefore, no quantization time was included in the reported index build times.

### 2025-07-24 Revision/response.tex
Update response.tex

@@
 Thank you for your suggestion.
-We add experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observe some pitfalls.
+We have added experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observed some pitfalls.
 For more details, please refer to our response to Meta Review R7.
@@
 We acknowledge that the original manuscript did not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard graph-based and IVF-based index structures.
-We have revised Section 2.2 and add two paragraphs.
+We have revised Section 2.2 and added two paragraphs.
 These paragraphs summarize how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures.

### 2025-07-24 VLDB2026/main.tex
1

@@
 	\textit{\textbf{Index construction time.}}
-	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time.
-Faiss builds the index fastest.
+%	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. 
+	As shown in the Figure~\ref{fig:rangeFilter_build_time}, for regular-scale datasets, Faiss builds the index fastest.
 As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.
-	%	shows the single-threaded index construction time.
-Faiss builds the index fastest.
-Because Faiss obtains subsamples through sampling and then calculates the cluster centroid, the computational complexity is significantly reduced.
 
@@
 			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
-			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
+			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
 			\hline

### 2025-07-24 VLDB2026/main.tex
Reduce 2.2 sections

--- 2025-07-24 VLDB2026/main.tex
@@
 	\noindent\textbf{\underline{Graph.}}
-	Graph-based ANN search algorithms accelerate queries by building graph indexes on datasets.
+	Graph structures accelerate ANN search by connecting each data point with its nearest neighbors, as shown in Figure~\ref{fig:graph}.
+During querying, algorithms start from an initial point and use a greedy strategy to progressively move towards closer neighbors until convergence (e.g., the path from $c$ to $j$ in the 1NN case).
+
+	Graph indexes are widely used in Hybrid ANN due to their efficiency.
+To support hybrid queries, in attribute filtering, a common practice involves attaching attribute metadata to nodes or edges, thereby skipping parts that do not satisfy query conditions during traversal (e.g., NHQ, Filtered-DiskANN, ACORN).
+In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges that satisfy range constraints, thus narrowing the search space (e.g., SeRF, DSG).
+
+%	Graph-based ANN search algorithms accelerate queries by building graph indexes on datasets.
 As illustrated in Figure~\ref{fig:graph}, each data point in the dataset corresponds to a point in the graph, and neighboring vertices (e.g., $a$ and $b$) are connected via edges based on their distance $\textit{dist}(a, b)$.
@@
 For instance, in Figure~\ref{fig:graph}, the gray point $c$ is connected to 5 neighbors $(a, b, d, e, f)$ and can traverse to them via corresponding edges.
-
-	Given a query point $q$, the graph-based ANN search typically follows a greedy search strategy to find the $k$ nearest neighbors.
+%	
+%	Given a query point $q$, the graph-based ANN search typically follows a greedy search strategy to find the $k$ nearest neighbors.
 For illustration, consider the case where $k = 1$ (i.e., 1NN): The algorithm initiates the search from an entry point (the gray point $c$).
@@
 The final point reached (the blue point $j$) is returned as the approximate nearest neighbor of $q$.
-
-	\textcolor{violet}{Graph-based indexes are widely adopted in Hybrid ANN search algorithms due to their excellent performance.
+%	
+%	\textcolor{violet}{Graph-based indexes are widely adopted in Hybrid ANN search algorithms due to their excellent performance.
 To support hybrid queries, existing approaches usually augment the original graph structures by explicitly associating attribute or range information with vertices or edges.
@@
 
-	\noindent\textbf{\underline{IVF.}}  IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
+	\noindent\textbf{\underline{IVF.}} 
+	IVF divides data into multiple clusters through clustering (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
+During querying, algorithms search only within the few clusters closest to the query point, which reduces computational load.
+
+	IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
+Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
+Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK).
+%	IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
 Specifically, as shown in Figure~\ref{fig:ivf}, IVF first selects a subset of data points and applies a clustering algorithm (e.g., K-Means) to obtain a set of centroids $(C_0, C_1, ..., C_6)$, each representing a distinct cluster.
 Every data point (gray dots) is then assigned to the cluster corresponding to its nearest centroid based on the distance metric, thereby forming the index structure.
-
-	During the query process, given a query point $q$, the algorithm computes distances between $q$ and all centroids, selects a small number of the closest centroids ($C_0, C_1, C_2$), and then performs a search only within the associated clusters to identify the approximate nearest neighbors.
-
-	\textcolor{violet}{IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, such as naturally supporting pre-filtering and requiring significantly lower memory consumption and smaller index sizes compared to graph-based indexes.
+%	
+%	During the query process, given a query point $q$, the algorithm computes distances between $q$ and all centroids, selects a small number of the closest centroids ($C_0, C_1, C_2$), and then performs a search only within the associated clusters to identify the approximate nearest neighbors.
+%	
+%	\textcolor{violet}{IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, such as naturally supporting pre-filtering and requiring significantly lower memory consumption and smaller index sizes compared to graph-based indexes.
 With minor modifications, IVF indexes achieve attribute and range filtering by directly excluding vectors that do not meet query constraints through pre-filtering, thus skipping irrelevant vectors during intra-cluster distance computations (e.g., Faiss, Milvus).
@@
 	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
-	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
+	\textcolor{violet}{As shown in the figure~\ref{fig:Big Dataset}, On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
 The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
@@
 It is a more complex multimodal dataset.
-As shown in Figure~\ref{fig:attribute-multimodal}, although the queries are more complex, UNG and NHQ still perform the best.
+As shown in Figure~\ref{fig:MultiModal}, although the queries are more complex, UNG and NHQ still perform the best.
 CAPS is the next best.
@@
 
-	\begin{figure}[t]
-		\centering
-
-		\hspace*{5pt}
-		% 放大的图例（占满单栏）
-		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
-
-		%\vspace{0.1cm}
-
-		% 三图横排
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\captionsetup{font=small}
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
-			\caption{\footnotesize Construction time}
-			\label{fig:rangeFilter_build_time}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
-			\caption{\footnotesize Index size}
-			\label{fig:rangeFilter_index_size_mb}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
-			\caption{\footnotesize Build peak memory}
-			\label{fig:rangeFilter_build_memory_mb}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.495\columnwidth}
-			\centering
-			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
-			\caption{\footnotesize Search peak memory}
-			\label{fig:rangeFilter_search_memory_mb}
-		\end{subfigure}
-
-		%		\caption{Time and space overhead of range filtering index construction}
-%		\caption{Time and space overhead of index construction}
-		\caption{\textcolor{violet}{Time and space overhead}}
-		\label{fig:rangeFilter_build_index_comparison}
-	\end{figure}
 	\subsection{Range Filtering}
@@
 	\subsubsection{Time and Space overhead of index construction.}
-
-	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
-	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. 
-%	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
-
-	\textit{\textbf{Index construction time.}}
-	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time.
-Faiss builds the index fastest.
-As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.
-	%	shows the single-threaded index construction time.
-Faiss builds the index fastest.
-Because Faiss obtains subsamples through sampling and then calculates the cluster centroid, the computational complexity is significantly reduced.
-
-	WinFilter and ACORN-\(\gamma\) take the longest.
-	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
-	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
-It also prunes distant neighbors to save storage space.
-However, this introduces additional overhead and slows down the construction process.
-
-	\textcolor{orange}{Note: For large-scale datasets, all algorithms are built using 64 threads for efficiency, except DSG, which only supports single-threaded construction.
-As a result, DSG takes significantly longer to build on Deep100M.
-	}
-
-	\textit{\textbf{Index size.}} 
-	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size.
-Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
-	%On low-dimensional datasets (Deep, YT-Audio), 
-	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
-	\textcolor{orange}{DSG is an improvement over SeRF.
-Compared to SeRF, DSG stores additional information for each edge in its index structure, resulting in a significant increase in index size on large-scale datasets.
-	}
-
-	%SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
-
-	\textit{\textbf{Build peak memory.}}
-	\textcolor{orange}{As explained in the build peak memory analysis for attribute filtering, the build peak memory depends on the sum of the index size and the dataset size, as shown in Figure~\ref{fig:rangeFilter_build_memory_mb}.
-Range filtering also follows this pattern.
-The reason why PASE deviates from this trend has been discussed earlier, and is not repeated here to save space.}
-
-%	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
-%	
-%	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
-This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
-%	
-%	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage.
-It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
-Its index structure remains stable in high dimensions without significant graph growth.
-This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
-%	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
-
-		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}
-		\textcolor{orange}{As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
-As we analyzed in the section on attribute filtering.
-		}
-
-	\begin{figure*}[t]
-
-		\centering
-
-		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
-		\caption{RF-ANN search }
-		\label{fig:exp_8_2}
-	\end{figure*}
-
-	\subsubsection{Performance Evaluation. }
-
-	In this experiment, we follow the query range definition adopted by prior work~\cite{HQI}.
-\textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.} Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
-	%\textcolor{red}{Some algorithms don't support using actual attributes as search keys, instead requiring an ID (the primary key, ranging from $0$ to $n-1$).
-Therefore, we uniformly use this ID as the search key.
-This ID is pre-sorted according to its corresponding real attribute, allowing us to map an attribute to its ID without loss of generality for efficient range queries.}
-
-	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
-The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges, WinFilter consistently delivers the best performance.
-This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
-
-	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
-In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios.
-However, by leveraging HNSW and bitmap-based post-filtering, UNIFY performs competitively under broader range conditions, demonstrating strong scalability.
-
-%	SeRF exhibits relatively weak overall performance, with a significant drop in recall under small-range query scenarios.
-This suggests that while its compressed graph structure is space-efficient, it has a substantial negative impact on query performance.
-
-	\textcolor{blue}{SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
-This is because SeRF compresses the entire HNSW graph by attaching range information to its edges.
-However, during small-range queries, its multi-filtering mechanism requires scanning a large number of edge entries that are irrelevant to the current query range, introducing fixed computational and memory access overhead.
-Additionally, graph traversal may lead to the exploration of numerous invalid neighbors, increasing the likelihood of the search becoming trapped in local optima and further degrading performance.
-	}
-
-	%	 修改此处
-	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
-Unlike other range filtering algorithms, ACORN is not designed with specialized data structures  to achieve efficient range filtering.
-In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
-
-	For third-party library and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
-	%\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
-Similar to the selectivity observed in attribute filtering.
-}
-	Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
-With a smaller range, fewer points remain after filtering, resulting in lower computational cost.
-In addition, the performance of Faiss is influenced by data dimensionality; the higher the dimensionality, the worse the performance.
-
-	Vector databases also show relatively poor performance on range queries.
-Among them, Milvus performs more balanced across both small-range and large-range queries, even surpassing ACORN under high recall settings.
-PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
-	VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is quite  low.
-
-	It is important to note that this range query experiment is conducted under a fully static setting.
-Under such conditions, UNIFY, iRange, SeRF, and WinFilter require the dataset to be sorted by attribute prior to index construction.
-In contrast, DSG  supports dynamic index construction with unordered attribute insertions, making it more suitable for streaming or incremental data scenarios.
-This flexibility highlights its superior extensibility in real-world applications.
-	\subsubsection{Robustness.}
-
-	\begin{figure*}[htbp]
-		\centering
-		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
-		\caption{Dataset Effect on RF-ANN Search}
-		\label{fig:exp_8_3}
-	\end{figure*}
-
-	\textcolor{green}{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
-As shown in Figure~\ref{fig:exp_8_3}, most methods perform worst on the Text2Image dataset.
-This is because OOD queries make the $k$-nearest neighbor distribution more sparse.
-As a result, the search needs to visit more nodes, which leads to an exponential growth in the search space and a sharp drop in efficiency.}
-
-	\sout{WinFilter shows the worst performance on the WIT dataset.
-This suggests that its performance is sensitive to the data dimensionality.
-ACORN has large performance differences across datasets, indicating weak robustness.
-
-	Among vector databases, Milvus performs well.
-VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image.
-PASE is excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
-
-	It is worth noting that most methods achieve similar performance on the Deep and YT-Audio datasets, which have similar LID values.
-This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
-A high LID and high dimensionality make hybrid queries more difficult.
-
-	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them.
-This means that DSG is more sensitive to changes in data distribution.
-}
-	%	Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.
-	%	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets.
-As shown in Figure~\ref{fig:exp_8_3}, the performance differences.
-All methods perform worst on WIT, which has the highest LID.
-On Deep and YT-Audio, which have similar LID, most algorithms achieve comparable performance.
-	%	This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
-	%	
-	%	However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID.
-This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.
 
@@
 
+	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
+	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. 
+%	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
+
+	\textit{\textbf{Index construction time.}}
+	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time.
+Faiss builds the index fastest.
+As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.
+	%	shows the single-threaded index construction time.
+Faiss builds the index fastest.
+Because Faiss obtains subsamples through sampling and then calculates the cluster centroid, the computational complexity is significantly reduced.
+
+	WinFilter and ACORN-\(\gamma\) take the longest.
+	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
+	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
+It also prunes distant neighbors to save storage space.
+However, this introduces additional overhead and slows down the construction process.
+
+	\textcolor{orange}{Note: For large-scale datasets, all algorithms are built using 64 threads for efficiency, except DSG, which only supports single-threaded construction.
+As a result, DSG takes significantly longer to build on Deep100M.
+	}
+
+	\textit{\textbf{Index size.}} 
+	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size.
+Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
+	%On low-dimensional datasets (Deep, YT-Audio), 
+	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
+	\textcolor{orange}{DSG is an improvement over SeRF.
+Compared to SeRF, DSG stores additional information for each edge in its index structure, resulting in a significant increase in index size on large-scale datasets.
+	}
+
+	%SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
+
+	\textit{\textbf{Build peak memory.}}
+	\textcolor{orange}{As explained in the build peak memory analysis for attribute filtering, the build peak memory depends on the sum of the index size and the dataset size, as shown in Figure~\ref{fig:rangeFilter_build_memory_mb}.
+Range filtering also follows this pattern.
+The reason why PASE deviates from this trend has been discussed earlier, and is not repeated here to save space.}
+
+%	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
+%	
+%	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
+This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
+%	
+%	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage.
+It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
+Its index structure remains stable in high dimensions without significant graph growth.
+This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
+%	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
+
+		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}
+		\textcolor{orange}{As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
+As we analyzed in the section on attribute filtering.
+		}
+
+	\begin{figure*}[t]
+
+		\centering
+
+		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
+		\caption{RF-ANN search }
+		\label{fig:exp_8_2}
+	\end{figure*}
+
+	\subsubsection{Performance Evaluation. }
+
+	In this experiment, we follow the query range definition adopted by prior work~\cite{HQI}.
+\textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.} Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
+	%\textcolor{red}{Some algorithms don't support using actual attributes as search keys, instead requiring an ID (the primary key, ranging from $0$ to $n-1$).
+Therefore, we uniformly use this ID as the search key.
+This ID is pre-sorted according to its corresponding real attribute, allowing us to map an attribute to its ID without loss of generality for efficient range queries.}
+
+	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
+The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges, WinFilter consistently delivers the best performance.
+This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
+
+	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
+In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios.
+However, by leveraging HNSW and bitmap-based post-filtering, UNIFY performs competitively under broader range conditions, demonstrating strong scalability.
+
+%	SeRF exhibits relatively weak overall performance, with a significant drop in recall under small-range query scenarios.
+This suggests that while its compressed graph structure is space-efficient, it has a substantial negative impact on query performance.
+
+	\textcolor{blue}{SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
+This is because SeRF compresses the entire HNSW graph by attaching range information to its edges.
+However, during small-range queries, its multi-filtering mechanism requires scanning a large number of edge entries that are irrelevant to the current query range, introducing fixed computational and memory access overhead.
+Additionally, graph traversal may lead to the exploration of numerous invalid neighbors, increasing the likelihood of the search becoming trapped in local optima and further degrading performance.
+	}
+
+	%	 修改此处
+	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
+Unlike other range filtering algorithms, ACORN is not designed with specialized data structures  to achieve efficient range filtering.
+In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
+
+	For third-party library and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
+	%\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
+Similar to the selectivity observed in attribute filtering.
+}
+	Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
+With a smaller range, fewer points remain after filtering, resulting in lower computational cost.
+In addition, the performance of Faiss is influenced by data dimensionality; the higher the dimensionality, the worse the performance.
+
+	Vector databases also show relatively poor performance on range queries.
+Among them, Milvus performs more balanced across both small-range and large-range queries, even surpassing ACORN under high recall settings.
+PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
+	VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is quite  low.
+
+	It is important to note that this range query experiment is conducted under a fully static setting.
+Under such conditions, UNIFY, iRange, SeRF, and WinFilter require the dataset to be sorted by attribute prior to index construction.
+In contrast, DSG  supports dynamic index construction with unordered attribute insertions, making it more suitable for streaming or incremental data scenarios.
+This flexibility highlights its superior extensibility in real-world applications.
+	\subsubsection{Robustness.}
+
+	\begin{figure*}[htbp]
+		\centering
+		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
+		\caption{Dataset Effect on RF-ANN Search}
+		\label{fig:exp_8_3}
+	\end{figure*}
+
+	\textcolor{green}{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
+As shown in Figure~\ref{fig:exp_8_3}, most methods perform worst on the Text2Image dataset.
+This is because OOD queries make the $k$-nearest neighbor distribution more sparse.
+As a result, the search needs to visit more nodes, which leads to an exponential growth in the search space and a sharp drop in efficiency.}
+
+	\sout{WinFilter shows the worst performance on the WIT dataset.
+This suggests that its performance is sensitive to the data dimensionality.
+ACORN has large performance differences across datasets, indicating weak robustness.
+
+	Among vector databases, Milvus performs well.
+VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image.
+PASE is excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
+
+	It is worth noting that most methods achieve similar performance on the Deep and YT-Audio datasets, which have similar LID values.
+This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
+A high LID and high dimensionality make hybrid queries more difficult.
+
+	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them.
+This means that DSG is more sensitive to changes in data distribution.
+}
+	%	Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.
+	%	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets.
+As shown in Figure~\ref{fig:exp_8_3}, the performance differences.
+All methods perform worst on WIT, which has the highest LID.
+On Deep and YT-Audio, which have similar LID, most algorithms achieve comparable performance.
+	%	This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
+	%	
+	%	However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID.
+This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.
+
 	\subsubsection{Scalability Study}
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
 When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
@@
 	\textcolor{blue}{
-	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:MultiModal_range} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
 As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
@@
 %	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
+
+\begin{figure}[t]
+	\centering
+
+	% Legend
+	\includegraphics[width=0.98\columnwidth]{figures/exp/range_legend.pdf}
+	\vspace{0.2cm} % Added a little space after the legend
+
+	% --- Subfigure (a) containing two plots ---
+	\begin{subfigure}[t]{0.98\columnwidth}
+		\centering
+		% First plot for the shared subfigure
+		\includegraphics[width=0.507\linewidth]{figures/exp/range_multimodel.pdf}
+		\hfill % Pushes the two plots apart
+		% Second plot for the shared subfigure
+		\includegraphics[width=0.48\linewidth]{figures/exp/range_multimodel_1.pdf}
+
+		% Shared caption for the two plots above
+		\captionsetup{font=small}
+		\caption{MultiModal}
+		\label{fig:MultiModal_range} % A single label for the combined subfigure
+	\end{subfigure}
+
+	% --- Subfigure (b) ---
+	\begin{subfigure}[t]{0.507\columnwidth}
+		\centering
+		\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
+		\captionsetup{font=small}
+		\caption{Different Computer}
+		\label{fig:Different_Computer_range}
+	\end{subfigure}
+	\hfill
+	% --- Subfigure (c) ---
+	\begin{subfigure}[t]{0.48\columnwidth}
+		\centering
+		\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
+		\captionsetup{font=small}
+		\caption{Big Dataset}
+		\label{fig:Big_Dataset_range}
+	\end{subfigure}
+
+	\caption{\textcolor{red}{TrinityExtension——Range}}
+	\label{fig:TrinityExtension——Range}
+\end{figure}
+
 	\section{DISCUSSION}

### 2025-07-24 Revision/response.tex
Update response.tex

@@
 We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.
+\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Different Hardware Environments.)}
 
-For attribute filtering, Please see section 4.2.4.
-
+Attribute filtering:
 \textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
@@
 
-For range filtering,please see section 4.3.4.
-
+Range filtering:
 \textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
@@
 We have conducted a more in-depth analysis of the reasons behind certain behaviors observed in the experimental results.
-The specific revisions are as follows:
 %下面写每个修改过的理由
@@
 Thank you for the suggestion.
-We realized that the original wording is somewhat vague and lead to confusion among readers.
+We realized that the original wording is somewhat vague and led to confusion among readers.
 To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table.

### 2025-07-24 Revision/response.tex
change response

--- 2025-07-24 Revision/response.tex
@@
 Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately.
-\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
+\textbf{(Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
 }
@@
 \textcolor{blue}{
+"Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
+The Text2Image dataset includes two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
+}
+
+Attribute filtering: \textcolor{blue}{
 	"We conducted experiments on the text2image-mix dataset.
@@
 
-\textcolor{blue}{
+Range filtering:\textcolor{blue}{
 		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.

### 2025-07-24 VLDB2026/main.tex

@@
 
+\begin{figure*}[t]
+	\centering
+
+	% 1. 全局图例 (Legend) - 位置保持不变
+	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
+
+	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+
+	% 2. 第一部分：两张图，共用标题
+	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+	% 宽度从\textwidth缩小到0.32\textwidth
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
+		\hfill 
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
+		\caption{MultiModal}
+		\label{fig:range-multimodal} 
+	\end{subfigure}
+	\hfill % 在第一部分和第二部分之间添加弹性间距
+	% 3. 第二部分：两张图，共用标题
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
+		\hfill
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
+		\caption{Cross-Platform}
+		\label{fig:range-cross-platform}
+	\end{subfigure}
+	\hfill % 在第二部分和第三部分之间添加弹性间距
+	% 4. 第三部分：只有一张图
+	\begin{subfigure}[b]{0.203\textwidth}
+		\centering
+		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
+		\caption{Dig Dataset}
+		\label{fig: range big dataset}
+	\end{subfigure}
+
+	% 5. 全局总标题
+	\caption{\textcolor{violet}TrinityExtension——Range}
+	\label{fig:TrinityExtension——Attribution_main}
+\end{figure*}
+
 	\subsubsection{Scalability Study}
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}.
-When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
+When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-24 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 
+%	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
+%	To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
+Additionally, we further assess the robustness of each algorithm under varying conditions.
+
 	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
-Additionally, we further assess the robustness of each algorithm under varying conditions.
+\textcolor{orange}{Although existing work, such as the survey by \cite{compare}, reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.}
 
@@
 
-\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also find that graph-based algorithms using pruning strategies (such as FilteredDiskANN and UNG) exhibit significantly increased construction time, especially when the pruning is complex and extensive, leading to higher computational overhead.
+\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also observe that algorithms based on Vamana (such as FilteredDiskANN and UNG) exhibit significantly increased construction time.
+Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
 In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
@@
 
+	\textcolor{orange}{For large-scale dataset, DSG only supports single-threaded construction, resulting in the longest build time.}
+
 	\textit{\textbf{Index size.}} 

### 2025-07-24 Revision/response.tex
Update response.tex

@@
 In particular, StitchedVamana performs poorly on Deep100M.
-For attribute filtering, please see section 4.2.4.
+For attribute filtering.
+\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
 
-\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
+Attribute filtering:\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
 The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
@@
 
-For range filtering, please see section 4.3.4.
-
+Range filtering:
 \textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.

### 2025-07-24 Revision/response.tex
Update response.tex

@@
 We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
-(Please see Section 4.2.3, highlighted in blue in the revised manuscript)
+\textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript)}
 
@@
 
-\textcolor{blue}{"The proximity of the 4 curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
-Conversely, greater divergence among the curves indicates higher distributional dependence.
-Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes."}
+\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
 
@@
 We sincerely apologize for the misuse of notation in Definition 2.3.
-This has been corrected in the revised version.
-(Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript)
+This has been corrected in the revised version.\textbf{(Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript)}
 

### 2025-07-24 Revision/response.tex
1

--- 2025-07-24 Revision/response.tex
@@
 	\caption{attribute filtering search peak memory}
-	\label{fig:attribute filtering search peak memory}
+	\label{fig:search_memory_mb_comparison}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/searchMem/range_memory_comparison.pdf}
-	\caption{range filtering search peak memory}
-	\label{fig:range filtering search peak memory}
+	\includegraphics[height=2.5cm]{fig/searchMem/range_memory_comparison.pdf}
+	\caption{Range filtering search peak memory}
+	\label{fig:rangeFilter_search_memory_mb}
 \end{figure}
@@
 
-\textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:attribute filtering search peak memory} that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower."}
+\textcolor{blue}{"For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
+However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets.
+In contrast, Milvus has lower query-time memory usage because it does not fully load the index and incurs additional metadata overhead during construction."}
 
@@
 
-\textcolor{blue}{"As for the Search peak memory usage, we can find from the Figure ~\ref{fig:range filtering search peak memory} that it is basically consistent with the Build peak memory usage trend.
-The algorithm needs to load the complete index into memory during search.
-Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead.
-For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend."}
+\textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
+As we analyzed in the section on attribute filtering."}
 

### 2025-07-25 Revision/response.tex
change

--- 2025-07-24 Revision/response.tex
@@
 We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
-\textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript)}
+(Please see Section 4.2.3, highlighted in blue in the revised manuscript)
 
@@
 
-\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
+\textcolor{blue}{"The proximity of the 4 curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.
+Conversely, greater divergence among the curves indicates higher distributional dependence.
+Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes."}
 
@@
 In particular, StitchedVamana performs poorly on Deep100M.
-For attribute filtering.
-\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
+For attribute filtering, please see section 4.2.4.
 
-Attribute filtering:\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
+\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
 The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
@@
 
-Range filtering:
+For range filtering, please see section 4.3.4.
+
 \textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
@@
 \textbf{Response:} I really appreciate your suggestion.
-In real-world applications, vectors and their attributes often have complex relationships.
-To better reflect such scenarios, we have introduced two real-world datasets, which are described in detail in Meta-Review R3.
-Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.(Please see the experimental results in Section 4.2.2 and Section 4.3.2)
+Current hybrid search algorithms don't explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
+However, our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
 
-Regarding the more intricate semantic relationships—such as those between vectors and attributes, or among different attributes themselves—current hybrid search algorithms do not explicitly model or leverage such correlations.
-Nevertheless, our evaluation covers a range of realistic scenarios, including multi-attribute settings and diverse  distributions, to assess the generalization ability of the algorithms.
+To demonstrate that the choice between synthetic and real attributes has little impact on algorithm performance, we conducted an additional set of experiments.
+We used the YouTube-Audio dataset for vectors and compared results with both synthetic and real attributes (video classification).
+The experimental outcomes validated our hypothesis.
 
@@
 We sincerely apologize for the misuse of notation in Definition 2.3.
-This has been corrected in the revised version.\textbf{(Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript)}
+This has been corrected in the revised version.
+(Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript)
 

### 2025-07-25 VLDB2026/main.tex
Update main.tex

@@
 	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
-Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}
@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
+Our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-25 Revision/response.tex
Update response.tex

@@
 That is a great suggestion.
-In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
+In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency and smaller RAM capacity of the Xeon 6330 processors.
 \textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Different Hardware Environments.)}
@@
 Attribute filtering:
+%\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
+Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
 \textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
-Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
@@
 Range filtering:
+%\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
+When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
+For brevity and due to space limitations, we omit further discussion of these redundant results."}
 \textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
-When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
+Our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results."}

### 2025-07-25 VLDB2026/main.tex
1

--- 2025-07-24 VLDB2026/main.tex
@@
 The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges, WinFilter consistently delivers the best performance.
-This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
-
-	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
+This highlights its \textcolor{red}{robustness}, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
+
+	\textcolor{red}{iRange and Faiss} offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
 In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios.

### 2025-07-25 VLDB2026/main.tex
1

--- 2025-07-25 VLDB2026/main.tex
@@
 	\textit{\textbf{Build peak memory.}}  
-	\textcolor{orange}{As explained in the build peak memory analysis for attribute filtering, the build peak memory depends on the sum of the index size and the dataset size, as shown in Figure~\ref{fig:rangeFilter_build_memory_mb}.
-Range filtering also follows this pattern.
-The reason why PASE deviates from this trend has been discussed earlier, and is not repeated here to save space.}
+	\textcolor{orange}{As explained in the attribute filtering analysis, the peak memory usage during index construction generally depends on the combined size of the dataset and the index, as illustrated in Figure~\ref{fig:rangeFilter_build_memory_mb}.
+Range filtering adheres to this pattern, while PASE deviates due to reasons discussed earlier.}
+
+	\textcolor{orange}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism.
+Although the final index size remains relatively small, the peak memory usage increases significantly during both construction and search.
+During construction, this is caused by the parallel building of local indices for each tree node, which results in substantial temporary memory usage.
+Similarly, during search, WinFilter needs to load multiple local indices in parallel for different tree nodes, further contributing to high peak memory consumption.}
 
@@
 		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}  
-		\textcolor{orange}{As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
-As we analyzed in the section on attribute filtering.
-		}
+		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, the peak memory usage during search generally follows a similar trend to that observed during index construction.
+This observation is consistent with our earlier analysis in the attribute filtering section.}
 
@@
 The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges, WinFilter consistently delivers the best performance.
-This highlights its \textcolor{red}{robustness}, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
-
-	\textcolor{red}{iRange and Faiss} offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
+This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
+
+	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
 In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios.

### 2025-07-25 Revision/response.tex
update 2.2

--- 2025-07-25 Revision/response.tex
@@
 Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately.
-\textbf{(Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
+\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
 }
@@
 \textcolor{blue}{
-"Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
-The Text2Image dataset includes two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
-}
-
-Attribute filtering: \textcolor{blue}{
 	"We conducted experiments on the text2image-mix dataset.
@@
 
-Range filtering:\textcolor{blue}{
+\textcolor{blue}{
 		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.
@@
 We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.
-\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Different Hardware Environments.)}
 
-Attribute filtering:
+For attribute filtering, Please see section 4.2.4.
+
 \textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
@@
 
-Range filtering:
+For range filtering,please see section 4.3.4.
+
 \textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
@@
 \textbf{Response:} I really appreciate your suggestion.
-Current hybrid search algorithms don't explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
-However, our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
+In real-world applications, vectors and their attributes often have complex relationships.
+To better reflect such scenarios, we have introduced two real-world datasets, which are described in detail in Meta-Review R3.
+Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.(Please see the experimental results in Section 4.2.2 and Section 4.3.2)
 
-To demonstrate that the choice between synthetic and real attributes has little impact on algorithm performance, we conducted an additional set of experiments.
-We used the YouTube-Audio dataset for vectors and compared results with both synthetic and real attributes (video classification).
-The experimental outcomes validated our hypothesis.
+Regarding the more intricate semantic relationships—such as those between vectors and attributes, or among different attributes themselves—current hybrid search algorithms do not explicitly model or leverage such correlations.
+Nevertheless, our evaluation covers a range of realistic scenarios, including multi-attribute settings and diverse  distributions, to assess the generalization ability of the algorithms.
 
@@
 
-\textcolor{blue}{"Graph-based indexes are widely adopted in Hybrid ANN search algorithms due to their excellent performance.
-To support hybrid queries, existing approaches usually augment the original graph structures by explicitly associating attribute or range information with vertices or edges.
-In attribute filtering, a common approach is to attach attribute metadata to vertices or edges, allowing the traversal process to skip nodes or edges that do not meet the query's attribute conditions (e.g., NHQ, Filtered-DiskANN, ACORN).
-In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges satisfying the range constraints, effectively narrowing down the search space (e.g., SeRF, DSG)."}
+\textcolor{blue}{"Graph indexes are widely used in Hybrid ANN due to their efficiency.
+To support hybrid queries, in attribute filtering, a common practice involves attaching attribute metadata to nodes or edges, thereby skipping parts that do not satisfy query conditions during traversal (e.g., NHQ, Filtered-DiskANN, ACORN).
+In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges that satisfy range constraints, thus narrowing the search space (e.g., SeRF, DSG)."}
 
-\textcolor{blue}{"IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, such as naturally supporting pre-filtering and requiring significantly lower memory consumption and smaller index sizes compared to graph-based indexes.
-With minor modifications, IVF indexes achieve attribute and range filtering by directly excluding vectors that do not meet query constraints through pre-filtering, thus skipping irrelevant vectors during intra-cluster distance computations (e.g., Faiss, Milvus).
-Moreover, clusters can be further partitioned hierarchically based on attributes (hierarchical partitioning), resulting in finer-grained sub-partitions that significantly enhance the efficiency of attribute filtering (e.g., CAPS, PUCK)."}
+\textcolor{blue}{"IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
+Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
+Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK)."}
 

### 2025-07-25 VLDB2026/main.tex
update 2.2

--- 2025-07-25 VLDB2026/main.tex
@@
 
-%	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-%	To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
+	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
+To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
 Additionally, we further assess the robustness of each algorithm under varying conditions.
-
-	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-\textcolor{orange}{Although existing work, such as the survey by \cite{compare}, reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
-To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
-Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.}
 
@@
 	\noindent\textbf{\underline{Graph.}}
-	Graph structures accelerate ANN search by connecting each data point with its nearest neighbors, as shown in Figure~\ref{fig:graph}.
-During querying, algorithms start from an initial point and use a greedy strategy to progressively move towards closer neighbors until convergence (e.g., the path from $c$ to $j$ in the 1NN case).
-
-	Graph indexes are widely used in Hybrid ANN due to their efficiency.
+	\textcolor{violet}{Graph structures accelerate ANN search by connecting each data point with its nearest neighbors, as shown in Figure~\ref{fig:graph}.
+During querying, algorithms start from an initial point and use a greedy strategy to progressively move towards closer neighbors until convergence (e.g., the path from $c$ to $j$ in the 1NN case).}
+
+	\textcolor{violet}{Graph indexes are widely used in Hybrid ANN due to their efficiency.
 To support hybrid queries, in attribute filtering, a common practice involves attaching attribute metadata to nodes or edges, thereby skipping parts that do not satisfy query conditions during traversal (e.g., NHQ, Filtered-DiskANN, ACORN).
-In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges that satisfy range constraints, thus narrowing the search space (e.g., SeRF, DSG).
+In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges that satisfy range constraints, thus narrowing the search space (e.g., SeRF, DSG).}
 
@@
 	\noindent\textbf{\underline{IVF.}} 
-	IVF divides data into multiple clusters through clustering (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
-During querying, algorithms search only within the few clusters closest to the query point, which reduces computational load.
-
-	IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
+	\textcolor{violet}{IVF divides data into multiple clusters through clustering (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
+During querying, algorithms search only within the few clusters closest to the query point, which reduces computational load.}
+
+	\textcolor{violet}{IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
-Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK).
+Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK).}
 %	IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
@@
 
-\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also observe that algorithms based on Vamana (such as FilteredDiskANN and UNG) exhibit significantly increased construction time.
-Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
+\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also find that graph-based algorithms using pruning strategies (such as FilteredDiskANN and UNG) exhibit significantly increased construction time, especially when the pruning is complex and extensive, leading to higher computational overhead.
 In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
@@
 	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
-It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}
@@
 
-	\textcolor{orange}{For large-scale dataset, DSG only supports single-threaded construction, resulting in the longest build time.}
-
 	\textit{\textbf{Index size.}} 
@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-Our findings remain consistent with those reported in Section 4.2.4.
+When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-25 Revision/response.tex

--- 2025-07-25 Revision/response.tex
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4. Please refer to the response MR.R4 for more details.
+Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-25 VLDB2026/main.tex
1
update 4.2.4 Large-scale Datasets

@@
 	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
-	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
-The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
-We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level.
-Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}
+	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+However, this also comes with significant memory overhead.
+The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
+Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
+This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}
 
@@
 	%On low-dimensional datasets (Deep, YT-Audio),
+
 	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).

### 2025-07-25 Revision/response.tex
1

@@
 We used the YouTube-Audio dataset for vectors and compared results with both synthetic and real attributes (video classification).
-The experimental outcomes validated our hypothesis.
+As shown in Figure~\ref{fig:compare}, the experimental outcomes validated our hypothesis.
+
+\begin{figure}[t]
+	\centering
+
+	% 上面的图例，居中并可通过 hspace 调整左右位置
+	\hspace*{8pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
+	\includegraphics[width=0.95\columnwidth]{fig/review_real_syn_legend.pdf} % 图例图片路径
+
+	% --- 不再使用 subfigure ---
+	% 直接放置第二张图片，可以加一点垂直间距
+	\vspace{5pt} 
+	\includegraphics[width=0.99\columnwidth]{fig/review_real_syn.pdf}
+
+	\caption{Comparison of Real and Synthetic Attributes}
+	\label{fig:compare}
+
+\end{figure}
 

### 2025-07-25 VLDB2026/main.tex
Update main.tex

@@
 	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) and 256GB of RAM.  
-\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.
+%	\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.
 For clarity and conciseness, we hereafter refer to the former as Server A and the latter as Server B.
@@
 \textcolor{blue}{
-	We conducted experiments on the text2image-mix dataset.
+	We conduct experiments on the text2image-mix dataset.
 This dataset contains both image and text vectors.
@@
 It poses a more severe challenge to the algorithm.
-a}
+}
 

### 2025-07-25 VLDB2026/main.tex
change range evaluation

--- 2025-07-25 VLDB2026/main.tex
@@
 	\noindent\textbf{\underline{Graph.}}
-	\textcolor{violet}{Graph structures accelerate ANN search by connecting each data point with its nearest neighbors, as shown in Figure~\ref{fig:graph}.
-During querying, algorithms start from an initial point and use a greedy strategy to progressively move towards closer neighbors until convergence (e.g., the path from $c$ to $j$ in the 1NN case).}
-
-	\textcolor{violet}{Graph indexes are widely used in Hybrid ANN due to their efficiency.
+	Graph structures accelerate ANN search by connecting each data point with its nearest neighbors, as shown in Figure~\ref{fig:graph}.
+During querying, algorithms start from an initial point and use a greedy strategy to progressively move towards closer neighbors until convergence (e.g., the path from $c$ to $j$ in the 1NN case).
+
+	Graph indexes are widely used in Hybrid ANN due to their efficiency.
 To support hybrid queries, in attribute filtering, a common practice involves attaching attribute metadata to nodes or edges, thereby skipping parts that do not satisfy query conditions during traversal (e.g., NHQ, Filtered-DiskANN, ACORN).
-In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges that satisfy range constraints, thus narrowing the search space (e.g., SeRF, DSG).}
+In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges that satisfy range constraints, thus narrowing the search space (e.g., SeRF, DSG).
 
@@
 	\noindent\textbf{\underline{IVF.}} 
-	\textcolor{violet}{IVF divides data into multiple clusters through clustering (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
-During querying, algorithms search only within the few clusters closest to the query point, which reduces computational load.}
-
-	\textcolor{violet}{IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
+	IVF divides data into multiple clusters through clustering (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
+During querying, algorithms search only within the few clusters closest to the query point, which reduces computational load.
+
+	IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
-Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK).}
+Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK).
 %	IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
@@
 Other approaches enhance robustness by separating attribute and vector indexing into distinct stages: UNG uses a logical graph to navigate attribute relationships, while CAPS employs an attribute frequency tree to adapt to power-law patterns.
-ACORN takes a different approach by disregarding attribute distribution entirely during index construction—it builds an ultra-dense, oversaturated graph to ensure that the remaining subgraph, even after aggressive attribute filtering, is still likely to be well-connected and searchable.}}
+In ACORN--\(\gamma\), during index construction, attributes are primarily used for pruning in the lowest-layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
+Consequently, changes in attribute distribution have minimal impact on overall performance.}}
 
@@
 	\textit{\textbf{Build peak memory.}}
-	\textcolor{orange}{As explained in the attribute filtering analysis, the peak memory usage during index construction generally depends on the combined size of the dataset and the index, as illustrated in Figure~\ref{fig:rangeFilter_build_memory_mb}.
-Range filtering adheres to this pattern, while PASE deviates due to reasons discussed earlier.}
-
-	\textcolor{orange}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism.
-Although the final index size remains relatively small, the peak memory usage increases significantly during both construction and search.
-During construction, this is caused by the parallel building of local indices for each tree node, which results in substantial temporary memory usage.
-Similarly, during search, WinFilter needs to load multiple local indices in parallel for different tree nodes, further contributing to high peak memory consumption.}
+	\textcolor{orange}{As explained in the build peak memory analysis for attribute filtering, the build peak memory depends on the sum of the index size and the dataset size, as shown in Figure~\ref{fig:rangeFilter_build_memory_mb}.
+Range filtering also follows this pattern.
+The reason why PASE deviates from this trend has been discussed earlier, and is not repeated here to save space.}
 
@@
 		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}
-		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, the peak memory usage during search generally follows a similar trend to that observed during index construction.
-This observation is consistent with our earlier analysis in the attribute filtering section.}
+		\textcolor{orange}{As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
+As we analyzed in the section on attribute filtering.
+		}
 
@@
 \textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.} Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
+	\textcolor{blue}{Due to the limitations of existing range filtering algorithms, the range filtering experiment only uses one attribute, and the data set is sorted in ascending order according to the attribute value size.
+WIT-Real and YT-Audio-Real use real attribute values, and the rest use randomly generated attribute values.}
 	%\textcolor{red}{Some algorithms don't support using actual attributes as search keys, instead requiring an ID (the primary key, ranging from $0$ to $n-1$).
@@
 	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
-The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges, WinFilter consistently delivers the best performance.
-This highlights its \textcolor{red}{robustness}, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
-
-	\textcolor{red}{iRange and Faiss} offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
+The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges.
+
+	\textcolor{blue}{
+	WinFilter maintains optimal performance by building an index for each tree node.
+It then performs an Approximate Nearest Neighbor (ANN) search on the relevant nodes and post-filters the results, ensuring high recall and queries per second (QPS).
+	In contrast, iRange dynamically constructs a search graph during query time.
+This method has low overhead and performs well in small-range queries, but its performance degrades as the query range increases.
+	UNIFY utilizes a skip list for localization followed by a linear scan for searching in small-range query scenarios.
+Its performance is generally lower than graph-based structures like iRange in these cases.
+	Interestingly, Faiss, aided by its efficient ID selector for filtering, calculates distances for only a small subset of points in small-range scenarios.
+Consequently, it can outperform algorithms specifically designed for range searches.
+	}
+%	WinFilter consistently delivers the best performance.
+This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
+%	
+%	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
 In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios.
@@
 
-	For third-party library and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
-	%\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
+%	For third-party library and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
+%	%\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
 Similar to the selectivity observed in attribute filtering.
 }
-	Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
+%	Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
 With a smaller range, fewer points remain after filtering, resulting in lower computational cost.
@@
 
-	Vector databases also show relatively poor performance on range queries.
+	Vector databases  show relatively poor performance on range queries.
 Among them, Milvus performs more balanced across both small-range and large-range queries, even surpassing ACORN under high recall settings.
@@
 
-	It is important to note that this range query experiment is conducted under a fully static setting.
+	\sout{It is important to note that this range query experiment is conducted under a fully static setting.
 Under such conditions, UNIFY, iRange, SeRF, and WinFilter require the dataset to be sorted by attribute prior to index construction.
 In contrast, DSG  supports dynamic index construction with unordered attribute insertions, making it more suitable for streaming or incremental data scenarios.
-This flexibility highlights its superior extensibility in real-world applications.
+This flexibility highlights its superior extensibility in real-world applications.}
+
 	\subsubsection{Robustness.}

### 2025-07-25 Revision/response.tex

@@
 Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper.
-We realize that we did not clearly explain the difference between our paper and the cited paper, so we add a description in the introduction, please see section XXX.
-\textcolor{blue}{""}
+We realize that we did not clearly explain the difference between our paper and the cited paper, so we add a description in the introduction, please see section 1.1.
+
+\textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications."}
 

### 2025-07-25 VLDB2026/main.tex
1

--- 2025-07-25 VLDB2026/main.tex
@@
 For regular-scale datasets, other methods show moderate variation.
-However, on large-scale dataset, the index sizes of ACORN and FilteredDiskANN increase sharply.
-The reason is xxx.
+However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size as the dataset scales up, primarily due to the large number of candidate neighbors they maintain.
 Overall, IVF-based methods tend to produce more compact indexes.

### 2025-07-25 VLDB2026/main.tex
Update main.tex

--- 2025-07-25 VLDB2026/main.tex
@@
 \textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.} Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
-	\textcolor{blue}{Due to the limitations of existing range filtering algorithms, the range filtering experiment only uses one attribute, and the data set is sorted in ascending order according to the attribute value size.
+	\textcolor{blue}{Due to the limitations of existing range filtering algorithms, the range filtering experiment only uses one attribute, and the dataset is sorted in ascending order according to the attribute value size.
 WIT-Real and YT-Audio-Real use real attribute values, and the rest use randomly generated attribute values.}

### 2025-07-25 VLDB2026/main.tex
Update main.tex

--- 2025-07-25 VLDB2026/main.tex
@@
 Unless otherwise specified, all experiments were conducted on Server A.}
-
 	Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}.
@@
 For regular-scale datasets, other methods show moderate variation.
-However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size as the dataset scales up, primarily due to the large number of candidate neighbors they maintain.
+However, on large-scale dataset, the index sizes of ACORN and FilteredDiskANN increase sharply.
+The reason is xxx.
 Overall, IVF-based methods tend to produce more compact indexes.

### 2025-07-25 VLDB2026/main.tex
1

--- 2025-07-25 VLDB2026/main.tex
@@
 However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the index size itself.
-For large-scale datasets, algorithms that produce larger indexes tend to cause significantly higher peak memory consumption during construction.}
+}
+
+\textcolor{orange}{For large-scale datasets, algorithms with high build peak memory usage typically produce large index size.
+However, NHQ is an exception.
+During the construction phase, NHQ generates a large number of candidate neighbors, but only retains a small subset for each point in the final index.
+This leads to peak memory usage that is significantly higher than the eventual index size.}
 

### 2025-07-25 VLDB2026/main.tex
1

--- 2025-07-25 VLDB2026/main.tex
@@
 	In this experiment, we follow the query range definition adopted by prior work~\cite{HQI}.
-\textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.} Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
+\textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.}
+	% Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
 \textcolor{blue}{Due to the limitations of existing range filtering algorithms, the range filtering experiment only uses one attribute, and the dataset is sorted in ascending order according to the attribute value size.
@@
 This ID is pre-sorted according to its corresponding real attribute, allowing us to map an attribute to its ID without loss of generality for efficient range queries.}
-
-	Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
+	Based on this definition, we evaluate algorithm performance under four query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
+Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
+The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones.
+For space considerations, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
+The experimental results show consistent performance across all datasets and query ranges.
+
+	%Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
 The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges.

### 2025-07-25 VLDB2026/main.tex
change multi modal

--- 2025-07-25 VLDB2026/main.tex
@@
 However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the index size itself.
-}
-
-\textcolor{orange}{For large-scale datasets, algorithms with high build peak memory usage typically produce large index size.
-However, NHQ is an exception.
-During the construction phase, NHQ generates a large number of candidate neighbors, but only retains a small subset for each point in the final index.
-This leads to peak memory usage that is significantly higher than the eventual index size.}
+For large-scale datasets, algorithms that produce larger indexes tend to cause significantly higher peak memory consumption during construction.}
 
@@
 	We conduct experiments on the text2image-mix dataset.
+This dataset contains image and text vectors and is a hybrid multimodal dataset.
+As shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
+	Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
+In practice, this means that the experiments effectively treat the image and text subsets as separate datasets, since the ground truths for each query belong to the same modality.
+Therefore, the performance on this dataset is similar to the results shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
+	In contrast, the text2image dataset shown in Figure~\ref{fig:attribute-multimodal} is different.
+The query set and the base dataset belong to two completely different modalities.
+Queries are far from the dataset points, and the ground truths are more dispersed and not clustered together.
+To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance.
+%	We conduct experiments on the text2image-mix dataset.
 This dataset contains both image and text vectors.
@@
 CAPS is the next best.
-	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
+%	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
 The nearest neighbors in the index are often from the same modality because they are closer in distance.
@@
 This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
-	In contrast, the text2image dataset shown in Figure~\ref{fig:exp_6_1} is different.
+%	In contrast, the text2image dataset shown in Figure~\ref{fig:exp_6_1} is different.
 The queries and the dataset are from different modalities.

### 2025-07-26 VLDB2026/main.tex
1

@@
 
-	\textcolor{orange}{For large-scale dataset, DSG only supports single-threaded construction, resulting in the longest build time.}
+	\textcolor{orange}{For large-scale dataset, ACORN-1 achieves the fastest index construction.
+This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.DSG only supports single-threaded construction, resulting in the longest build time.}
 
@@
 Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
-	%On low-dimensional datasets (Deep, YT-Audio),
 

### 2025-07-26 VLDB2026/main.tex
1

@@
 	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
-	\textcolor{orange}{DSG is an improvement over SeRF.
+	\textcolor{orange}{Additionally, DSG also results in a large index size, especially on large-scale datasets.
+As an enhancement over SeRF, DSG stores additional metadata for each edge in its index structure.
+While this design improves retrieval accuracy, it significantly increases the index size on massive datasets.}
+%	\textcolor{orange}{DSG is an improvement over SeRF.
 Compared to SeRF, DSG stores additional information for each edge in its index structure, resulting in a significant increase in index size on large-scale datasets.
-	}
+%	}
 

### 2025-07-26 VLDB2026/main.tex
change challenge

@@
 
-	Furthermore, current attribute filtering algorithms offer limited support for complex filtering conditions.
+	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions.
+For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
+Furthermore, NHQ only supports multi-attribute filtering with conjunctions ("AND" conditions).
+UNG is relatively more flexible in this regard, as it supports both "AND" and "OR" logic; however, it still cannot handle more complex Boolean expressions involving combinations of conjunctions and disjunctions.
+	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
+However, it currently supports only single-attribute filtering and disjunctions ("OR" conditions) across multiple attributes.
+Enhancing its capability to support more flexible Boolean combinations would effectively overcome the limitations of current approaches and significantly improve its practicality for diverse and complex query requirements.
+		}
+
+	\textcolor{blue}{
+	Besides, our research findings indicate that the distribution and selectivity of attributes significantly impact the performance of attribute filtering methods.
+Therefore, when designing algorithms, efforts should be made to minimize the coupling with specific attribute value distributions, in order to enhance the robustness and generalization ability of the algorithms under varying data conditions.}
+
+%	Furthermore, current attribute filtering algorithms offer limited support for complex filtering conditions.
 For example, Filtered-DiskANN  supports single-attribute filtering, and in multi-attribute scenarios, it only supports OR conditions between attributes.
-	%The original implementations of 
-	NHQ imposes strict constraints on the number of base and query attributes and only support AND conditions.
+%	%The original implementations of 
+%	NHQ imposes strict constraints on the number of base and query attributes and only support AND conditions.
 While UNG is relatively flexible—supporting both AND and OR logic—it still lacks support for arbitrary Boolean expressions (e.g., combinations of AND and OR).
@@
 
-	Except for DSG, most range filtering algorithms require the dataset to be pre-sorted before building the index.
+	Except for DSG and UNIFY, most range filtering algorithms require the dataset to be pre-sorted before building the index.
 Moreover, these methods do not support multi-attribute range queries.
@@
 
-	Our experiments show that graph compression methods often lead to poor query performance in RF-ANN search.
+%	Our experiments show that graph compression methods often lead to poor query performance in RF-ANN search.
 To address this problem, subsequent algorithms usually optimize the index processing at the segment tree nodes.
@@
 
+\textcolor{blue}{
+Experimental results show that different algorithms exhibit varying strengths under different query ranges.
+Therefore, designing a general range query algorithm that can adapt to diverse query conditions holds significant research value.
+For example, UNIFY demonstrates strong generality by dynamically selecting execution strategies based on the query range.
+Building on this idea, further exploration of more adaptive and high-performance range query algorithms is a promising direction for future research.}
+
 		In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement.
 We suggest future future range filtering algorithms include Faiss as a baseline.
-		%In our experiments, we find that many range filtering algorithms perform worse than Faiss at high recall (0.95).
-This shows that the design of current algorithms still needs improvement.
-We suggest that future range filtering algorithms should include Faiss as a baseline.
 
@@
 
-	Lastly, our findings show that the distribution and the number of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
+	\textcolor{blue}{
+	Lastly, existing algorithms suffer from significant performance degradation on out-of-distribution (OOD) datasets.
+Exploring how to improve these algorithms to better adapt to more complex query conditions is a worthwhile direction for further research.}
+
+%	our findings show that the distribution and the number of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
 Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.
+%
 

### 2025-07-27 VLDB2026/main.tex
1

@@
 UNG stands out for its higher recall, precision, and QPS, and performs well in the OOD scenario (S7, S8).
+\textcolor{orange}{
+Overall, UNG, NHQ, and FilteredDisk\\-ANN demonstrate strong performance.
+However, UNG suffers from performance degradation when the attribute count differs between indexing and querying.
+NHQ, due to its distance fusion design, also experiences performance drops when there is a significant mismatch in attribute numbers between indexing and querying, and its performance is sensitive to attribute distribution.
+FilteredDiskANN supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.
+However, disk-based construction significantly increases indexing time.
+Additionally, it only supports single-attribute and multi-attribute OR queries, and its performance is highly affected by attribute distribution.
+}
+
+\textcolor{orange}{
+CAPS, based on clustering, features low index space overhead.
+It offers flexible support for varying numbers of attributes and is optimized for low-selectivity attribute scenarios, but its overall performance is relatively moderate.
+Puck is well-suited for large-scale datasets such as those with 100 million points.
+It offers fast index construction and low memory consumption in such scenarios.
+Moreover, it delivers high search performance in multi-threaded environments, making it an excellent choice for deployment on extremely large datasets.}
+
 	\subsubsection{\textbf{Range Filtering}}
-
+\textcolor{orange}{
+	WinFilter achieves the best search performance but requires high time and memory resources during index construction.
+For large-scale datasets (e.g., with 100 million points), parameter tuning—particularly of tree height—is needed to prevent excessive index growth.
+When QPS and recall are not strict requirements, its basic variant, Vamana-WST, offers a more efficient alternative with significantly lower indexing overhead.
+		}
+
+	\textcolor{orange}{
+	iRange has relatively low time and space costs for index construction; however, its search performance declines significantly with increasing query range.
+Despite offering threading parameters for indexing, it does not effectively utilize multi-core parallelism in practical scenarios.
+	SeRF incurs low time and space overhead but achieves only moderate overall query performance, with notably weaker results in small-range query scenarios.
+	DSG supports unordered dynamic insertions and range queries, but its index construction is limited to single-threaded execution, resulting in long build times and poor practical applicability.
+	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
+It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution.}
 %	Table~\ref{tab:algo_scenarios} also shows the application scenarios of range filtering.
@@
 In addition, WinFilter also performs well in OOD scenarios (S8).
+
+	\subsubsection{\textbf{General Algorithm}}
+\textcolor{orange}{ACORN requires a separate index construction.
+Among its variants, ACORN-1 shows significant advantages in indexing speed on billion-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}
+
+\textcolor{orange}{
+Faiss, Milvus, and VBASE are better suited for complex scenarios involving advanced filtering operations.
+While they offer strong flexibility, their overall search performance is relatively modest.
+Relatively speaking, PASE performs less well across various aspects.}
+
 	\subsection{Challenges}

### 2025-07-28 VLDB2026/main.tex
1

@@
 			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
-			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
+			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &M/M  &M/M  &L/L  &L/L  &-/-  \\
 			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
@@
 	SeRF incurs low time and space overhead but achieves only moderate overall query performance, with notably weaker results in small-range query scenarios.
-	DSG supports unordered dynamic insertions and range queries, but its index construction is limited to single-threaded execution, resulting in long build times and poor practical applicability.
+	DSG supports unordered dynamic insertions and range queries, but its index construction is limited to single-threaded execution, resulting in long build times and poor practical applicability.}
+
+		\textcolor{orange}{
 	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
@@
 	\subsubsection{\textbf{General Algorithm}}
-\textcolor{orange}{ACORN requires a separate index construction.
+\textcolor{orange}{All of the following methods support both attribute filtering and range filtering.}
+
+\textcolor{orange}{
+ACORN demonstrates average overall performance.
 Among its variants, ACORN-1 shows significant advantages in indexing speed on billion-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}

### 2025-07-28 VLDB2026/main.tex
Update main.tex

--- 2025-07-27 VLDB2026/main.tex
@@
 \textit{\textbf{Index construction time.}}
-\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN.
+\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN-$\gamma$.
 PASE and VBASE only support single-threaded builds, and PASE is the slowest to build because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster.
@@
 	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths.
-This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods.
+This leads to increased computational cost and a sharp QPS drop for most methods.
 Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.

### 2025-07-28 Revision/response.tex
change

@@
 Using IDs as attributes for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we add two datasets that use real attributes:
-
-\textbf{YT-Audio-Real dataset:} For this dataset, we utilize the URLs provided by the YouTube8M dataset to crawl corresponding video categories and view counts as real attributes, using \textbf{video categories as attributes for attribute filtering experiments} and \textbf{view counts as attributes for range filtering experiments}, respectively.
-
-\textbf{WIT-Real dataset:} We use the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extract the language type and the length of the \texttt{context\_page\_}
-\texttt{description} field as real attributes, applying them in both attribute filtering and range filtering experiments.
+To address this issue, we add two datasets that use real attributes.
 
 \textcolor{blue}{
-	"Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.
-It should be noted that, during range filtering, due to the limitations of some algorithms, we uniformly sorted the vectors according to the query attribute."
+	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the \texttt{page\_title} field into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes.
+The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."
 }

### 2025-07-28 Revision/response.tex
1

--- 2025-07-25 Revision/response.tex
@@
 \textbf{Response:} I really appreciate your suggestion.
-Current hybrid search algorithms don't explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
+Current hybrid search algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
 However, our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
 
-To demonstrate that the choice between synthetic and real attributes has little impact on algorithm performance, we conducted an additional set of experiments.
+To demonstrate that the choice between synthetic and real attributes has little impact on algorithm performance, we have conducted an additional set of experiments.
 We used the YouTube-Audio dataset for vectors and compared results with both synthetic and real attributes (video classification).
-As shown in Figure~\ref{fig:compare}, the experimental outcomes validated our hypothesis.
+As shown in Figure~\ref{fig:compare}, the experimental outcomes have validated our hypothesis.
 

### 2025-07-28 VLDB2026/main.tex
1

--- 2025-07-28 VLDB2026/main.tex
@@
 
-	\textcolor{orange}{For large-scale dataset, ACORN-1 achieves the fastest index construction.
-This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.DSG only supports single-threaded construction, resulting in the longest build time.}
+	\textcolor{orange}{On large-scale datasets, ACORN-1 achieves the fastest index construction, primarily due to its similarity to the original HNSW construction process and its use of fewer candidate neighbors in the upper layers.
+SeRF, another HNSW-based method, also exhibits very short construction time by losslessly compressing multiple HNSW graphs into a unified structure and accelerating the process through dynamic pruning and skip-connection optimizations.
+	As two methods both based on IVF\_Flat, Milvus and Faiss achieve short indexing times.
+Milvus is even faster, mainly due to its cache-aware optimization, which significantly reduces CPU cache misses.}
+
+	\textcolor{orange}{
+	DSG only supports single-threaded construction, resulting in the longest build time.}
 
@@
 NHQ, due to its distance fusion design, also experiences performance drops when there is a significant mismatch in attribute numbers between indexing and querying, and its performance is sensitive to attribute distribution.
-FilteredDiskANN supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.
-However, disk-based construction significantly increases indexing time.
-Additionally, it only supports single-attribute and multi-attribute OR queries, and its performance is highly affected by attribute distribution.
-}
+}
+
+\textcolor{orange}{The two variants of FilteredDiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
+FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.
+However, its disk-based construction significantly increases indexing time, and its performance is highly sensitive to attribute distribution.
+In contrast, StitchedVamana offers better search performance but performs poorly on 100M-scale datasets and OOD datasets.}
 
@@
 \textcolor{orange}{
-Faiss, Milvus, and VBASE are better suited for complex scenarios involving advanced filtering operations.
+Faiss, Milvus, and VBASE handle complex scenarios with advanced filtering operations more effectively.
 While they offer strong flexibility, their overall search performance is relatively modest.

### 2025-07-28 VLDB2026/main.tex
Update main.tex

--- 2025-07-28 VLDB2026/main.tex
@@
 Similarly, VBASE, which employs a post-filtering strategy, shows efficiency that directly correlates with attribute selectivity—the more selective the filter, the more computational resources are wasted on retrieving irrelevant vectors.
-FAISS-IVF, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.
+Faiss, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.
 

### 2025-07-28 Revision/response.tex
1
change

--- 2025-07-28 Revision/response.tex
@@
 \textbf{Response:} I really appreciate your suggestion.
-Current hybrid search algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
+Current hybrid search algorithms don't explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
 However, our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
 
-To demonstrate that the choice between synthetic and real attributes has little impact on algorithm performance, we have conducted an additional set of experiments.
+To demonstrate that the choice between synthetic and real attributes has little impact on algorithm performance, we conducted an additional set of experiments.
 We used the YouTube-Audio dataset for vectors and compared results with both synthetic and real attributes (video classification).
-As shown in Figure~\ref{fig:compare}, the experimental outcomes have validated our hypothesis.
+As shown in Figure~\ref{fig:compare}, the experimental outcomes validated our hypothesis.
 
@@
 
-We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to MR.R7.
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset.\textbf{ Please refer to MR.R7.}
 
@@
 Thank you for highlighting this point, which further emphasizes the significance of our work.
+To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2.
 
 In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
-We added more detailed and in-depth analysis to provide a clearer explanation.
+We added more detailed and in-depth analysis to provide a clearer explanation.(Please refer to the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript)
 
 Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c is very insightful.
-Initially, we hesitated to include the peak memory usage of databases (including Milvus) because they are full systems that run continuously and contain many components.
+Initially, we hesitated to include the peak memory usage of databases (such as Milvus) because they are full systems that run continuously and contain many components.
 This makes them quite different from other algorithms.
@@
 However, we agree with your point.
-To provide a more comprehensive evaluation, we have added the peak memory usage data of the database systems (including Milvus) in the revised version of the paper.
-This offers a more complete comparative view.
+To provide a more comprehensive evaluation, we have added the peak memory usage data of the database systems  in the revised version of the paper.
+This offers a more complete comparative view.\textbf{(Please refer to the "Build peak memory" part of Section 4.2.1 and  4.3.1, highlighted in blue in the revised manuscript)}
 

### 2025-07-28 VLDB2026/main.tex
change

--- 2025-07-28 VLDB2026/main.tex
@@
 \textit{\textbf{Index construction time.}}
-\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN-$\gamma$.
+\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN.
 PASE and VBASE only support single-threaded builds, and PASE is the slowest to build because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster.
@@
 	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths.
-This leads to increased computational cost and a sharp QPS drop for most methods.
+This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods.
 Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
@@
 Similarly, VBASE, which employs a post-filtering strategy, shows efficiency that directly correlates with attribute selectivity—the more selective the filter, the more computational resources are wasted on retrieving irrelevant vectors.
-Faiss, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.
+FAISS-IVF, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.
 
@@
 	Based on this definition, we evaluate algorithm performance under four query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
-Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
+\textcolor{blue}{Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
 The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones.
-For space considerations, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
+}For space considerations, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
 The experimental results show consistent performance across all datasets and query ranges.
@@
 			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
-			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &M/M  &M/M  &L/L  &L/L  &-/-  \\
+			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
 			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
@@
 	SeRF incurs low time and space overhead but achieves only moderate overall query performance, with notably weaker results in small-range query scenarios.
-	DSG supports unordered dynamic insertions and range queries, but its index construction is limited to single-threaded execution, resulting in long build times and poor practical applicability.}
-
-		\textcolor{orange}{
+	DSG supports unordered dynamic insertions and range queries, but its index construction is limited to single-threaded execution, resulting in long build times and poor practical applicability.
 	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
@@
 	\subsubsection{\textbf{General Algorithm}}
-\textcolor{orange}{All of the following methods support both attribute filtering and range filtering.}
-
-\textcolor{orange}{
-ACORN demonstrates average overall performance.
+\textcolor{orange}{ACORN requires a separate index construction.
 Among its variants, ACORN-1 shows significant advantages in indexing speed on billion-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}

### 2025-07-28 Revision/response.tex

--- 2025-07-28 Revision/response.tex
@@
 	\centering
+	\includegraphics[width=\linewidth]{fig/legend_only.pdf}
 	\includegraphics[width=\linewidth]{fig/searchMem/label_memory_comparison.pdf}
@@
 	\centering
+	\includegraphics[width=\linewidth]{fig/rangeFilter_legend_only.pdf}
 	\includegraphics[height=2.5cm]{fig/searchMem/range_memory_comparison.pdf}

### 2025-07-28 VLDB2026/main.tex
1

@@
 For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}
-%	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}
 
 	\textit{\textbf{Index construction time.}}
-%	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. 
-	As shown in the Figure~\ref{fig:rangeFilter_build_time}, for regular-scale datasets, Faiss builds the index fastest.
+%	As shown in the Figure~\ref{fig:rangeFilter_build_time}, for regular-scale datasets, Faiss builds the index fastest.
 As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.
-
-	WinFilter and ACORN-\(\gamma\) take the longest.
-	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
-	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
+%
+%	WinFilter and ACORN-\(\gamma\) take the longest.
+%	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
+%	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
 It also prunes distant neighbors to save storage space.
 However, this introduces additional overhead and slows down the construction process.
-
-	\textcolor{orange}{On large-scale datasets, ACORN-1 achieves the fastest index construction, primarily due to its similarity to the original HNSW construction process and its use of fewer candidate neighbors in the upper layers.
+%	
+%	\textcolor{orange}{On large-scale datasets, ACORN-1 achieves the fastest index construction, primarily due to its similarity to the original HNSW construction process and its use of fewer candidate neighbors in the upper layers.
 SeRF, another HNSW-based method, also exhibits very short construction time by losslessly compressing multiple HNSW graphs into a unified structure and accelerating the process through dynamic pruning and skip-connection optimizations.
-	As two methods both based on IVF\_Flat, Milvus and Faiss achieve short indexing times.
+%	As two methods both based on IVF\_Flat, Milvus and Faiss achieve short indexing times.
 Milvus is even faster, mainly due to its cache-aware optimization, which significantly reduces CPU cache misses.}
-
+%	\textcolor{orange}{
+%	DSG only supports single-threaded construction, resulting in the longest build time.}
 	\textcolor{orange}{
-	DSG only supports single-threaded construction, resulting in the longest build time.}
+	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss demonstrates very fast index construction speed, primarily due to its strategy of sampling subsets and computing clustering centroids, which significantly reduces overall computational complexity.
+Both Milvus and Faiss adopt the IVF\_Flat architecture, achieving short construction times on both medium-scale and large-scale datasets.
+On large-scale datasets in particular, Milvus performs faster, mainly owing to its cache-aware optimization, which substantially reduces CPU cache misses.}
+
+		\textcolor{orange}{
+	ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
+This efficiency stems from its construction process, which closely resembles that of the original HNSW, and from reducing the number of candidate neighbors in the upper layers, thereby lowering computational cost.
+SeRF, another HNSW-based method, also exhibits very short construction time.
+During construction, it attaches timestamp information to edges, keeping the total time comparable to building a single HNSW graph, which enables efficient construction even on large datasets.}
+
+		\textcolor{orange}{
+	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
+This design introduces redundant computation and high construction cost.
+However, on large-scale datasets, the preprocessing phase of WinFilter was replaced with a base algorithm in the experiments, thus avoiding significant time overhead.}
+
+		\textcolor{orange}{
+	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
+Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
+
+		\textcolor{orange}{
+	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
+This makes the construction process more complex and costly.
+In addition, DSG only supports single-threaded construction, resulting in the longest construction time on large-scale datasets.}
 

### 2025-07-28 VLDB2026/main.tex
1

@@
 	\textcolor{orange}{
-	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss demonstrates very fast index construction speed, primarily due to its strategy of sampling subsets and computing clustering centroids, which significantly reduces overall computational complexity.
-Both Milvus and Faiss adopt the IVF\_Flat architecture, achieving short construction times on both medium-scale and large-scale datasets.
-On large-scale datasets in particular, Milvus performs faster, mainly owing to its cache-aware optimization, which substantially reduces CPU cache misses.}
+	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss, based on the IVF\_Flat architecture, achieves fast index construction through subset sampling and centroid computation, which lowers the computational cost.
+	As another IVF\_Flat-based method, Milvus performs even better on large-scale datasets, mainly due to its cache-aware optimization that greatly reduces CPU cache misses.}
 

### 2025-07-28 Revision/response.tex
1

--- 2025-07-28 Revision/response.tex
@@
 Thank you for your suggestion.
-Using IDs as attributes for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
+Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
 To address this issue, we add two datasets that use real attributes.
@@
 At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
-The results are shown in Figure\ref{fig:recall-latency}:
+The results are shown in Figure~\ref{fig:recall-latency}:
 \begin{figure}[htbp]
@@
 
-We conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
+We conducted additional experiments on the YT-Audio-Real dataset, comparing three variants of DiskANN.
 (1) SSD-based FilteredDiskANN (original disk-based method);

### 2025-07-28 Revision/response.tex
change

--- 2025-07-28 Revision/response.tex
@@
 
-We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset.\textbf{ Please refer to MR.R7.}
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset.\textbf{ Please refer to the response to MetaReview R7.}
 
@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-Since other algorithms also do not support multi-attribute queries, we will explain this situation collectively in the corresponding section of the paper to save space.
-
-Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.
+Since other algorithms also do not support multi-attribute queries, we will explain this situation collectively in the corresponding section of the paper to save space.(
+\textbf{Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.})
 
@@
 We have clearly pointed this out in \textcolor{blue}{Section 5.2.2} of the "Discussion" part of the paper and listed it as an important challenge for future work.
-Thank you for highlighting this point, which further emphasizes the significance of our work.
-To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2.
+Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
+
+To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2.\textbf{(Please see paragraph 1 of Section 4.3, which is highlighted in blue in the revised manuscript.)}
 
 In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
-We added more detailed and in-depth analysis to provide a clearer explanation.(Please refer to the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript)
+We added more detailed and in-depth analysis to provide a clearer explanation.\textbf{(Please refer to the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript.)}
 
@@
 This is because SeRF’s multi-filtering mechanism needs to inspect a large number of edge entries that are irrelevant to the current small-range query, thereby introducing fixed computational and memory access overhead.
-Additionally, during graph traversal, many invalid neighbors may be visited, causing the search to fall into local optima, which further degrades query performance and recall.
+Additionally, during graph traversal, many invalid neighbors may be visited, causing the search to fall into local optima, which further degrades query performance and recall.\textbf{(Please see  Section 4.3.2, which is highlighted in blue in the revised manuscript.)}
 
-We believe this explanation better clarifies the specific reasons why SeRF performs poorly in small-range query scenarios. Thank you again for your valuable suggestions.
+\textcolor{blue}{"SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
+This is because SeRF compresses the entire HNSW graph by attaching range information to its edges.
+However, during small-range queries, its multi-filtering mechanism requires scanning a large number of edge entries that are irrelevant to the current query range, introducing fixed computational and memory access overhead.
+Additionally, graph traversal may lead to the exploration of numerous invalid neighbors, increasing the likelihood of the search becoming trapped in local optima and further degrading performance."}
+
+%We believe this explanation better clarifies the specific reasons why SeRF performs poorly in small-range query scenarios. Thank you again for your valuable suggestions.
 

### 2025-07-28 VLDB2026/main.tex
change

--- 2025-07-28 VLDB2026/main.tex
@@
 	\subsection{Range Filtering}
-
+	\textcolor{blue}{Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
+The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones.
+}
 	\subsubsection{Time and Space overhead of index construction.}
@@
 	\textit{\textbf{Index construction time.}}
-%	Figure~\ref{fig:rangeFilter_build_time} shows the single-threaded index construction time. 
+
 	As shown in the Figure~\ref{fig:rangeFilter_build_time}, for regular-scale datasets, Faiss builds the index fastest.
@@
 	Based on this definition, we evaluate algorithm performance under four query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
-\textcolor{blue}{Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
-The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones.
-}For space considerations, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
+For space considerations, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
 The experimental results show consistent performance across all datasets and query ranges.
@@
 	Except for DSG and UNIFY, most range filtering algorithms require the dataset to be pre-sorted before building the index.
-Moreover, these methods do not support multi-attribute range queries.
-Enhancing these methods to support an arbitrary number of range filterable attributes remains an open research challenge.
+\textcolor{green}{Moreover, these methods do not support multi-attribute range queries.
+}Enhancing these methods to support an arbitrary number of range filterable attributes remains an open research challenge.
 

### 2025-07-28 Revision/response.tex
Update response.tex

--- 2025-07-28 Revision/response.tex
@@
 Thank you for your suggestion.
-Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we add two datasets that use real attributes.
+Using IDs as attributes for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
+To address this issue, we add two datasets that use real attributes:
+
+\textbf{YT-Audio-Real dataset:} For this dataset, we utilize the URLs provided by the YouTube8M dataset to crawl corresponding video categories and view counts as real attributes, using \textbf{video categories as attributes for attribute filtering experiments} and \textbf{view counts as attributes for range filtering experiments}, respectively.
+
+\textbf{WIT-Real dataset:} We use the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extract the language type and the length of the \texttt{context\_page\_}
+\texttt{description} field as real attributes, applying them in both attribute filtering and range filtering experiments.
 
 \textcolor{blue}{
-	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the \texttt{page\_title} field into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes.
-The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."
+	"Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.
+It should be noted that, during range filtering, due to the limitations of some algorithms, we uniformly sorted the vectors according to the query attribute."
 }
@@
 At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
-The results are shown in Figure~\ref{fig:recall-latency}:
+The results are shown in Figure\ref{fig:recall-latency}:
 \begin{figure}[htbp]
@@
 
-We conducted additional experiments on the YT-Audio-Real dataset, comparing three variants of DiskANN.
+We conducted additional experiments on the real-world YT8M dataset, comparing three variants of DiskANN.
 (1) SSD-based FilteredDiskANN (original disk-based method);
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/legend_only.pdf}
 	\includegraphics[width=\linewidth]{fig/searchMem/label_memory_comparison.pdf}
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/rangeFilter_legend_only.pdf}
 	\includegraphics[height=2.5cm]{fig/searchMem/range_memory_comparison.pdf}
@@
 In particular, StitchedVamana performs poorly on Deep100M.
-For attribute filtering.
 \textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
@@
 
-We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset.\textbf{ Please refer to MR.R7.}
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to MR.R7.
 
@@
 Thank you for highlighting this point, which further emphasizes the significance of our work.
-To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2.
 
 In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
-We added more detailed and in-depth analysis to provide a clearer explanation.(Please refer to the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript)
+We added more detailed and in-depth analysis to provide a clearer explanation.
 
 Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c is very insightful.
-Initially, we hesitated to include the peak memory usage of databases (such as Milvus) because they are full systems that run continuously and contain many components.
+Initially, we hesitated to include the peak memory usage of databases (including Milvus) because they are full systems that run continuously and contain many components.
 This makes them quite different from other algorithms.
@@
 However, we agree with your point.
-To provide a more comprehensive evaluation, we have added the peak memory usage data of the database systems  in the revised version of the paper.
-This offers a more complete comparative view.\textbf{(Please refer to the "Build peak memory" part of Section 4.2.1 and  4.3.1, highlighted in blue in the revised manuscript)}
+To provide a more comprehensive evaluation, we have added the peak memory usage data of the database systems (including Milvus) in the revised version of the paper.
+This offers a more complete comparative view.
 

### 2025-07-28 Revision/response.tex
Update response.tex

--- 2025-07-28 Revision/response.tex
@@
 
-Attribute filtering:\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
-The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
-We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level.
-Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
+Attribute filtering:\textcolor{blue}{"As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+However, this also comes with significant memory overhead.
+The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
+Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
+This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
 
@@
 
-We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset.\textbf{ Please refer to the response to MetaReview R7.}
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset.\textbf{ Please refer to MR.R7.}
 
@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-Since other algorithms also do not support multi-attribute queries, we will explain this situation collectively in the corresponding section of the paper to save space.(
-\textbf{Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.})
+Since other algorithms also do not support multi-attribute queries, we will explain this situation collectively in the corresponding section of the paper to save space.
+
+Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.
 
@@
 We have clearly pointed this out in \textcolor{blue}{Section 5.2.2} of the "Discussion" part of the paper and listed it as an important challenge for future work.
-Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
-
-To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2.\textbf{(Please see paragraph 1 of Section 4.3, which is highlighted in blue in the revised manuscript.)}
+Thank you for highlighting this point, which further emphasizes the significance of our work.
+To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2.
 
 In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
-We added more detailed and in-depth analysis to provide a clearer explanation.\textbf{(Please refer to the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript.)}
+We added more detailed and in-depth analysis to provide a clearer explanation.(Please refer to the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript)
 
@@
 This is because SeRF’s multi-filtering mechanism needs to inspect a large number of edge entries that are irrelevant to the current small-range query, thereby introducing fixed computational and memory access overhead.
-Additionally, during graph traversal, many invalid neighbors may be visited, causing the search to fall into local optima, which further degrades query performance and recall.\textbf{(Please see  Section 4.3.2, which is highlighted in blue in the revised manuscript.)}
+Additionally, during graph traversal, many invalid neighbors may be visited, causing the search to fall into local optima, which further degrades query performance and recall.
 
-\textcolor{blue}{"SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
-This is because SeRF compresses the entire HNSW graph by attaching range information to its edges.
-However, during small-range queries, its multi-filtering mechanism requires scanning a large number of edge entries that are irrelevant to the current query range, introducing fixed computational and memory access overhead.
-Additionally, graph traversal may lead to the exploration of numerous invalid neighbors, increasing the likelihood of the search becoming trapped in local optima and further degrading performance."}
-
-%We believe this explanation better clarifies the specific reasons why SeRF performs poorly in small-range query scenarios. Thank you again for your valuable suggestions.
+We believe this explanation better clarifies the specific reasons why SeRF performs poorly in small-range query scenarios. Thank you again for your valuable suggestions.
 

### 2025-07-28 Revision/response.tex

--- 2025-07-28 Revision/response.tex
@@
 In particular, StitchedVamana performs poorly on Deep100M.
-For attribute filtering.
 \textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
 
-Attribute filtering:\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
-The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
-We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level.
-Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
+Attribute filtering:\textcolor{blue}{"As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+However, this also comes with significant memory overhead.
+The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
+Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
+This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
 

### 2025-07-28 VLDB2026/main.tex

@@
 \textit{\textbf{Index construction time.}}
-\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN-$\gamma$.
-PASE and VBASE only support single-threaded builds, and PASE is the slowest to build because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster.
+\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longer build times are mainly PASE, VBASE, and ACORN-$\gamma$.
+PASE and VBASE only support single-threaded builds, and PASE is the slowest because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster.
 ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates.
@@
 
-\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also observe that algorithms based on Vamana (such as FilteredDiskANN and UNG) exhibit significantly increased construction time.
+\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned, we also observe that algorithms based on Vamana (such as FilteredDiskANN and UNG) exhibit significantly increased construction time.
 Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
@@
 For regular-scale datasets, other methods show moderate variation.
-However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size as the dataset scales up, primarily due to the large number of candidate neighbors they maintain.
+However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.
 Overall, IVF-based methods tend to produce more compact indexes.
@@
 However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets.
-In contrast, Milvus has lower query-time memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
+In contrast, Milvus has lower peak memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
 }
@@
 
+%	The reason for the high construction time of ACORN-$\gamma$ has been explained in the attribute filtering section and is therefore omitted here.
+
 		\textcolor{orange}{
@@
 This makes the construction process more complex and costly.
-In addition, DSG only supports single-threaded construction, resulting in the longest construction time on large-scale datasets.}
+In addition, on Deep100M, DSG uses single-threaded construction, resulting in the longest build time.}
 
@@
 	}
-	\centering
+	\vspace{1mm}
+	\begin{flushleft}
+	\textbf{Note:} H = High performance, M = Medium performance, L = Low performance, 
+	\faCheck = Recommended, \faTimes = Not Recommended.
+	\end{flushleft}
+	\centering
+
 \end{table*}

### 2025-07-28 Revision/response.tex
change R9 R8

@@
 In particular, StitchedVamana performs poorly on Deep100M.
+For attribute filtering.
 \textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
 
-Attribute filtering:\textcolor{blue}{"As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
-However, this also comes with significant memory overhead.
-The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
-Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
-This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
+Attribute filtering:\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
+The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
+We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level.
+Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
 
@@
 \textbf{Response:} 
-Thank you for your valuable suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
+%Thank you for your valuable suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
+%
+%To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
+Thank you very much for your insightful comments.
+We fully agree with your views.
+We have revised the discussion section of the paper accordingly.
+In this section, we have added a recommendation table for the algorithms, which summarizes their performance under various conditions.
+Additionally, we have provided a more in-depth analysis of the internal mechanisms of each algorithm in the text, aiming to uncover the fundamental reasons behind their performance.
+\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
 
-To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
+\textcolor{blue}{
+	Attribute filtering:"Overall, UNG, NHQ, and FilteredDisk-ANN demonstrate strong performance.
+However, UNG suffers from performance degradation when the attribute count differs between indexing and querying.
+NHQ, due to its distance fusion design, also experiences performance drops when there is a significant mismatch in attribute numbers between indexing and querying, and its performance is sensitive to attribute distribution.
+}
+
+\textcolor{blue}{"The two variants of FilteredDiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
+FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.
+However, its disk-based construction significantly increases indexing time, and its performance is highly sensitive to attribute distribution.
+In contrast, StitchedVamana offers better search performance but performs poorly on 100M-scale datasets and OOD datasets.}
+
+\textcolor{blue}{
+	CAPS, based on clustering, features low index space overhead.
+It offers flexible support for varying numbers of attributes and is optimized for low-selectivity attribute scenarios, but its overall performance is relatively moderate.
+	Puck is well-suited for large-scale datasets such as those with 100 million points.
+It offers fast index construction and low memory consumption in such scenarios.
+Moreover, it delivers high search performance in multi-threaded environments, making it an excellent choice for deployment on extremely large datasets."}
+
+Range filtering:\textcolor{blue}{
+	"WinFilter achieves the best search performance but requires high time and memory resources during index construction.
+For large-scale datasets (e.g., with 100 million points), parameter tuning—particularly of tree height—is needed to prevent excessive index growth.
+When QPS and recall are not strict requirements, its basic variant, Vamana-WST, offers a more efficient alternative with significantly lower indexing overhead.
+}
+
+\textcolor{blue}{
+	iRange has relatively low time and space costs for index construction; however, its search performance declines significantly with increasing query range.
+Despite offering threading parameters for indexing, it does not effectively utilize multi-core parallelism in practical scenarios.
+	SeRF incurs low time and space overhead but achieves only moderate overall query performance, with notably weaker results in small-range query scenarios.
+	DSG supports unordered dynamic insertions and range queries, but its index construction is limited to single-threaded execution, resulting in long build times and poor practical applicability.}
+
+\textcolor{blue}{
+	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
+It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution.}
+
+General:	\textcolor{blue}{"All of the following methods support both attribute filtering and range filtering.}
+
+	\textcolor{blue}{
+		ACORN demonstrates average overall performance.
+Among its variants, ACORN-1 shows significant advantages in indexing speed on billion-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}
+
+	\textcolor{blue}{
+		Faiss, Milvus, and VBASE handle complex scenarios with advanced filtering operations more effectively.
+While they offer strong flexibility, their overall search performance is relatively modest.
+Relatively speaking, PASE performs less well across various aspects."}
 %下面放那个优劣势表
@@
 \noindent
-\textbf{Response:}
+\textbf{Response:} Thank you very much for your valuable suggestions.
+Your advice is very insightful.
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios.\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
 
@@
 We have clearly pointed this out in \textcolor{blue}{Section 5.2.2} of the "Discussion" part of the paper and listed it as an important challenge for future work.
-Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
+Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of section 5.2.2, highlighted in green in the revised manuscript.)}
 

### 2025-07-28 Revision/response.tex
1

--- 2025-07-28 Revision/response.tex
@@
 
-Attribute filtering:\textcolor{blue}{"As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
-However, this also comes with significant memory overhead.
-The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
-Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
-This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
+Attribute filtering:\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead.
+The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications.
+We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level.
+Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
 
@@
 We have addressed this issue in detail in our response to Meta-Review R2.
-Specifically, we add complex multimodal query experiments and provided an in-depth analysis of the results.
+Specifically, we added complex multimodal query experiments and provided an in-depth analysis of the results.
 For more details, please refer to our response to Meta-Review R2.
@@
 
-To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in MetaReview R3.
+To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in Meta-Review R3.
 
-We have revised the manuscript accordingly.
-(Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.) Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
+We have revised the manuscript accordingly.\textbf{ (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.)} Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response MR.R4 for more details.
+Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response Meta-Review R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper.
-We realize that we did not clearly explain the difference between our paper and the cited paper, so we add a description in the introduction, please see section 1.1.
+We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
 
@@
 Instead, in Section 3, we add superscript markers next to each algorithm name and provide the corresponding implementation URLs as footnotes on the same page.
-(Please see the relevant footnotes in Section 3 in the revised manuscript)
+\textbf{(Please see the relevant footnotes in Section 3 in the revised manuscript.)}
 
@@
 We have added experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observed some pitfalls.
-For more details, please refer to our response to Meta Review R7.
+For more details, please refer to our response to Meta-Review R7.
 
@@
 
-We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset.\textbf{ Please refer to the response to MetaReview R7.}
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to the response to Meta-Review R7.
 
@@
 This is a major limitation of current range filtering methods.
-We have clearly pointed this out in \textcolor{blue}{Section 5.2.2} of the "Discussion" part of the paper and listed it as an important challenge for future work.
-Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
+We have clearly pointed this out in Section 5.2.2 of the "Discussion" part of the paper and listed it as an important challenge for future work.
+Thank you for highlighting this point, which further emphasizes the significance of our work.
+\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
 
@@
 To provide a more comprehensive evaluation, we have added the peak memory usage data of the database systems  in the revised version of the paper.
-This offers a more complete comparative view.\textbf{(Please refer to the "Build peak memory" part of Section 4.2.1 and  4.3.1, highlighted in blue in the revised manuscript)}
+This offers a more complete comparative view.
+\textbf{(Please refer to the "Build peak memory" part of Section 4.2.1 and  4.3.1, highlighted in blue in the revised manuscript)}
 
@@
 \noindent
-\textbf{Response:} Thank you for your feedback. We have revised \textcolor{blue}{Section 4.3.2 in our paper to provide a more specific and clearer explanation.}
+\textbf{Response:} Thank you for your feedback. We have revised Section 4.3.2 in our paper to provide a more specific and clearer explanation.
 

### 2025-07-28 Revision/response.tex
Update response.tex

@@
 We have addressed this issue in detail in our response to Meta-Review R2.
-Specifically, we added complex multimodal query experiments and provided an in-depth analysis of the results.
+Specifically, we add complex multimodal query experiments and provided an in-depth analysis of the results.
 For more details, please refer to our response to Meta-Review R2.
@@
 
-To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in Meta-Review R3.
+To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in MetaReview R3.
 
-We have revised the manuscript accordingly.\textbf{ (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.)} Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
+We have revised the manuscript accordingly.
+(Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.) Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response Meta-Review R4 for more details.
+Thank you for your suggestion.
+We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4.
+The results indicated that memory size, CPU cache, and CPU model have no impact on the ranking of methods.
+Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper.
-We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
+We realize that we did not clearly explain the difference between our paper and the cited paper, so we add a description in the introduction, please see section 1.1.
 
@@
 Instead, in Section 3, we add superscript markers next to each algorithm name and provide the corresponding implementation URLs as footnotes on the same page.
-\textbf{(Please see the relevant footnotes in Section 3 in the revised manuscript.)}
+(Please see the relevant footnotes in Section 3 in the revised manuscript)
 
@@
 We have added experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observed some pitfalls.
-For more details, please refer to our response to Meta-Review R7.
+For more details, please refer to our response to Meta Review R7.
 
@@
 
-We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to the response to Meta-Review R7.
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset.\textbf{ Please refer to the response to MetaReview R7.}
 
@@
 This is a major limitation of current range filtering methods.
-We have clearly pointed this out in Section 5.2.2 of the "Discussion" part of the paper and listed it as an important challenge for future work.
-Thank you for highlighting this point, which further emphasizes the significance of our work.
-\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
+We have clearly pointed this out in \textcolor{blue}{Section 5.2.2} of the "Discussion" part of the paper and listed it as an important challenge for future work.
+Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
 
@@
 To provide a more comprehensive evaluation, we have added the peak memory usage data of the database systems  in the revised version of the paper.
-This offers a more complete comparative view.
-\textbf{(Please refer to the "Build peak memory" part of Section 4.2.1 and  4.3.1, highlighted in blue in the revised manuscript)}
+This offers a more complete comparative view.\textbf{(Please refer to the "Build peak memory" part of Section 4.2.1 and  4.3.1, highlighted in blue in the revised manuscript)}
 
@@
 \noindent
-\textbf{Response:} Thank you for your feedback. We have revised Section 4.3.2 in our paper to provide a more specific and clearer explanation.
+\textbf{Response:} Thank you for your feedback. We have revised \textcolor{blue}{Section 4.3.2 in our paper to provide a more specific and clearer explanation.}
 

### 2025-07-28 Revision/response.tex

--- 2025-07-28 Revision/response.tex
@@
 This is a major limitation of current range filtering methods.
-We have clearly pointed this out in \textcolor{blue}{Section 5.2.2} of the "Discussion" part of the paper and listed it as an important challenge for future work.
-Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of section 5.2.2, highlighted in green in the revised manuscript.)}
+We have clearly pointed this out in Section 5.2.2 of the "Discussion" part of the paper and listed it as an important challenge for future work.
+Thank you for highlighting this point, which further emphasizes the significance of our work.
+\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
 

### 2025-07-28 Revision/response.tex
Update response.tex

@@
 We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
-\textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript)}
+\textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
 
@@
 This is a major limitation of current range filtering methods.
-We have clearly pointed this out in Section 5.2.2 of the "Discussion" part of the paper and listed it as an important challenge for future work.
-Thank you for highlighting this point, which further emphasizes the significance of our work.
-\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
+We have clearly pointed this out in \textcolor{blue}{Section 5.2.2} of the "Discussion" part of the paper and listed it as an important challenge for future work.
+Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of section 5.2.2, highlighted in green in the revised manuscript.)}
 

### 2025-07-28 Revision/response.tex
Update response.tex

--- 2025-07-28 Revision/response.tex
@@
 
-To further enrich the evaluation of complex multimodal queries, we add new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
+To further enrich the evaluation of complex multimodal queries, we have added new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
 Specifically, we construct a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response Meta-Review R4 for more details.
+Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-28 Revision/response.tex
Update response.tex

@@
 To further enrich the evaluation of complex multimodal queries, we have added new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
-Specifically, we construct a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
+Specifically, we constructed a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
 We then perform both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms.
@@
 Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we add two datasets that use real attributes.
+To address this issue, we have added two datasets that use real attributes.
 

### 2025-07-28 Revision/response.tex
change

--- 2025-07-28 Revision/response.tex
@@
 We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
-\textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript)}
 
@@
 \textcolor{blue}{
-	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the \texttt{page\_title} field into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes.
+	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title field into vectors, and extract the language type and the length of the context page description field as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."
@@
 \textbf{Response:} 
-%Thank you for your valuable suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
-%
-%To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
-Thank you very much for your insightful comments.
-We fully agree with your views.
-We have revised the discussion section of the paper accordingly.
-In this section, we have added a recommendation table for the algorithms, which summarizes their performance under various conditions.
-Additionally, we have provided a more in-depth analysis of the internal mechanisms of each algorithm in the text, aiming to uncover the fundamental reasons behind their performance.
-\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+Thank you for your valuable suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
 
-\textcolor{blue}{
-	Attribute filtering:"Overall, UNG, NHQ, and FilteredDisk-ANN demonstrate strong performance.
-However, UNG suffers from performance degradation when the attribute count differs between indexing and querying.
-NHQ, due to its distance fusion design, also experiences performance drops when there is a significant mismatch in attribute numbers between indexing and querying, and its performance is sensitive to attribute distribution.
-}
-
-\textcolor{blue}{"The two variants of FilteredDiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
-FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.
-However, its disk-based construction significantly increases indexing time, and its performance is highly sensitive to attribute distribution.
-In contrast, StitchedVamana offers better search performance but performs poorly on 100M-scale datasets and OOD datasets.}
-
-\textcolor{blue}{
-	CAPS, based on clustering, features low index space overhead.
-It offers flexible support for varying numbers of attributes and is optimized for low-selectivity attribute scenarios, but its overall performance is relatively moderate.
-	Puck is well-suited for large-scale datasets such as those with 100 million points.
-It offers fast index construction and low memory consumption in such scenarios.
-Moreover, it delivers high search performance in multi-threaded environments, making it an excellent choice for deployment on extremely large datasets."}
-
-Range filtering:\textcolor{blue}{
-	"WinFilter achieves the best search performance but requires high time and memory resources during index construction.
-For large-scale datasets (e.g., with 100 million points), parameter tuning—particularly of tree height—is needed to prevent excessive index growth.
-When QPS and recall are not strict requirements, its basic variant, Vamana-WST, offers a more efficient alternative with significantly lower indexing overhead.
-}
-
-\textcolor{blue}{
-	iRange has relatively low time and space costs for index construction; however, its search performance declines significantly with increasing query range.
-Despite offering threading parameters for indexing, it does not effectively utilize multi-core parallelism in practical scenarios.
-	SeRF incurs low time and space overhead but achieves only moderate overall query performance, with notably weaker results in small-range query scenarios.
-	DSG supports unordered dynamic insertions and range queries, but its index construction is limited to single-threaded execution, resulting in long build times and poor practical applicability.}
-
-\textcolor{blue}{
-	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
-It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution.}
-
-General:	\textcolor{blue}{"All of the following methods support both attribute filtering and range filtering.}
-
-	\textcolor{blue}{
-		ACORN demonstrates average overall performance.
-Among its variants, ACORN-1 shows significant advantages in indexing speed on billion-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}
-
-	\textcolor{blue}{
-		Faiss, Milvus, and VBASE handle complex scenarios with advanced filtering operations more effectively.
-While they offer strong flexibility, their overall search performance is relatively modest.
-Relatively speaking, PASE performs less well across various aspects."}
+To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
 %下面放那个优劣势表
@@
 \noindent
-\textbf{Response:} Thank you very much for your valuable suggestions.
-Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios.\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+\textbf{Response:}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4.
-The results indicated that memory size, CPU cache, and CPU model have no impact on the ranking of methods.
-Please refer to the response MR.R4 for more details.
+Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 We have clearly pointed this out in \textcolor{blue}{Section 5.2.2} of the "Discussion" part of the paper and listed it as an important challenge for future work.
-Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of section 5.2.2, highlighted in green in the revised manuscript.)}
+Thank you for highlighting this point, which further emphasizes the significance of our work.\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
 

### 2025-07-28 VLDB2026/main.tex
1
change

@@
 
-	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the \texttt{page\_title} field into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes.
+	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title field into vectors, and extract the language type and the length of the context page description field as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
@@
 	\textit{Single-Thread Search.}  
-	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths.
-This leads to increased computational cost and a sharp QPS drop for most methods.
-Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
-\textcolor{violet}{Puck and CAPS perform relatively well on some datasets.
+	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions, search often requires traversing larger candidate sets or deeper graph paths.
+This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods.
+Despite this, UNG consistently maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes and searches only within the subgraph formed by points satisfying the filtering conditions, thereby improving query efficiency.}
+
+	\textcolor{violet}{NHQ and StitchedVamana also perform well and show similar and stable performance across all datasets.
+This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.}
+
+	\textcolor{violet}{StitchedVamana outperforms FilteredVamana in query efficiency.
+This difference stems from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.}
+
+	%	Puck and CAPS perform relatively well.
 Partition-based methods have limitations regarding different vector data distributions, and how to configure different partitions for different datasets remains a challenge.
-However, this also demonstrates that IVF-based methods are still very promising for hybrid queries.}
-
-	NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets.
-This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.
-As observed in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, StitchedVamana outperforms FilteredVamana in query efficiency.
-This difference arises from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
-
-	\textcolor{violet}{ACORN generally performs poorly, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
-Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.}
-
-	Among all methods, vector database systems (PASE, VBASE, Milvus) exhibit the worst performance.
+However, this also demonstrates that IVF-based methods remain very promising for hybrid queries.
+
+	\textcolor{violet}{Puck and CAPS perform relatively well, indicating that IVF-based methods remain very promising for hybrid query.}
+
+	\textcolor{violet}{Among all methods, vector database systems (PASE, VBASE, Milvus) show the worst performance.
 These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
-Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
-
-	\textit{Multi-Thread Search.}
-	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, \textcolor{violet}{the performance distribution of algorithms remains largely unchanged except for Puck, with UNG continuing to maintain the best performance.
-Puck shows significant performance improvement under multi-threading.}
+Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.}
+
+	\textcolor{violet}{\textit{Multi-Thread Search.} As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, under multi-threading, all algorithms except Puck show similar improvements, with UNG continuing to maintain the best performance.
+Puck achieves significant performance improvement in multi-threading scenarios.}
 

### 2025-07-28 Revision/response.tex
change

@@
 \textcolor{blue}{
-	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title field into vectors, and extract the language type and the length of the context page description field as real attributes.
+	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."

### 2025-07-28 VLDB2026/main.tex
change

@@
 
-	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title field into vectors, and extract the language type and the length of the context page description field as real attributes.
+	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
@@
 	\hline
-			\textbf{Query Performance} & H & M & H & M &\textbf{H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
-			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
-			\textbf{Peak Memory} &L  &M  &M  &M  &M  &H  &L  &L  &M  &L  &L  &L/L  &\textbf{H}/\textbf{H}  &M/M  &H/M  &H/H \\
-
-			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H} &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
-			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
-			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &M/M  &M/M  &L/L  &L/L  &-/-  \\
-			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
-			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
+	\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
+	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/ \textbf{S} &M/S  &M/M  &W/W  \\
+	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &M/M  &S/M  &S/S \\
+	\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
+	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
+	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &W  &M  &S  &M  &S  &\textbf{S}  &M/M  &M/M  &W/W  &W/W  &-/-  \\
+	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
+	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
 	\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
@@
 	\begin{flushleft}
-	\textbf{Note:} H = High performance, M = Medium performance, L = Low performance, 
+	\textbf{Note:} S = Strong performance, \textbf{S} = Strongest performance, M = Medium performance, W = Weak performance, 
 	\faCheck = Recommended, \faTimes = Not Recommended.

### 2025-07-28 Revision/response.tex
Update response.tex

@@
 \textcolor{blue}{
-	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes.
+	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the \texttt{page\_title} field into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."
@@
 
-Attribute filtering:\textcolor{blue}{"As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Attribute filtering:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.

### 2025-07-28 Revision/response.tex
1

--- 2025-07-28 Revision/response.tex
@@
 
-To further enrich the evaluation of complex multimodal queries, we have added new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
-Specifically, we constructed a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
+To further enrich the evaluation of complex multimodal queries, we add new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
+Specifically, we construct a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
 We then perform both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms.
@@
 Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have added two datasets that use real attributes.
+To address this issue, we add two datasets that use real attributes.
 
@@
 
-Attribute filtering:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Attribute filtering:\textcolor{blue}{"As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.
+Thank you for your suggestion. We have already provided a detailed response to this issue in our reply to Meta-Review R5. Please refer to that response for more information.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.
+Thank you for your suggestion. We have made a detailed response to this issue in our reply to Meta-Review R6. Please refer to that response for more information.
 
@@
 \textbf{Response:} 
+Thank you for your suggestion.
+We have already addressed this issue in detail in our responses to Meta-Review R8 and R9.
+Specifically, we analyzed the strengths and weaknesses of each algorithm and recommended those with strong performance.
+Additionally, we provided a summary table illustrating how each algorithm performs across different application scenarios.
+For more details, please refer to our responses to Meta-Review R8 and R9.
 

### 2025-07-28 VLDB2026/main.tex
1

--- 2025-07-28 VLDB2026/main.tex
@@
 The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
-Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
+Furthermore, we did not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
+StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
+CAPS, on the other hand, is limited by its implementation and achieves a recall of only around 0.2.}
+%		we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
 This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}

### 2025-07-28 Revision/response.tex
Update response.tex
1

@@
 We sincerely apologize for the misuse of notation in Definition 2.3.
-This has been corrected in the revised version.\textbf{(Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript)}
+This has been corrected in the revised version.\textbf{(Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript.)}
 
@@
 Since there are multiple methods, listing all URLs in Section 4.1 would be overwhelming.
-Instead, in Section 3, we add superscript markers next to each algorithm name and provide the corresponding implementation URLs as footnotes on the same page.
+Instead, in Section 3, we added superscript markers next to each algorithm name and provided the corresponding implementation URLs as footnotes on the same page.
 \textbf{(Please see the relevant footnotes in Section 3 in the revised manuscript.)}

### 2025-07-28 VLDB2026/main.tex
change 4.2.3 Attribute Distribution Faiss

--- 2025-07-28 VLDB2026/main.tex
@@
 Similarly, VBASE, which employs a post-filtering strategy, shows efficiency that directly correlates with attribute selectivity—the more selective the filter, the more computational resources are wasted on retrieving irrelevant vectors.
-Faiss, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.
+Faiss, which searches within the nearest clusters, may need to traverse more clusters to find sufficient results when relevant data points are unevenly distributed across clusters due to attribute skew, which impacts performance.
 

### 2025-07-28 VLDB2026/main.tex
Update main.tex
change title

--- 2025-07-28 VLDB2026/main.tex
@@
 %	\subsection{Index Organization in Hybrid ANN Search}
-	\subsection{Index Organization in Hybrid Query}
+	\subsection{Index Organization }
 
@@
 
-	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
+	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the \texttt{page\_title} field into vectors, and extract the language type and the length of the \texttt{context\_page\_description} field as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
@@
 	\textit{Single-Thread Search.}  
-	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions, search often requires traversing larger candidate sets or deeper graph paths.
-This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods.
-Despite this, UNG consistently maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes and searches only within the subgraph formed by points satisfying the filtering conditions, thereby improving query efficiency.}
-
-	\textcolor{violet}{NHQ and StitchedVamana also perform well and show similar and stable performance across all datasets.
-This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.}
-
-	\textcolor{violet}{StitchedVamana outperforms FilteredVamana in query efficiency.
-This difference stems from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.}
-
-	%	Puck and CAPS perform relatively well.
+	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths.
+This leads to increased computational cost and a sharp QPS drop for most methods.
+Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
+\textcolor{violet}{Puck and CAPS perform relatively well on some datasets.
 Partition-based methods have limitations regarding different vector data distributions, and how to configure different partitions for different datasets remains a challenge.
-However, this also demonstrates that IVF-based methods remain very promising for hybrid queries.
-
-	\textcolor{violet}{Puck and CAPS perform relatively well, indicating that IVF-based methods remain very promising for hybrid query.}
-
-	\textcolor{violet}{Among all methods, vector database systems (PASE, VBASE, Milvus) show the worst performance.
+However, this also demonstrates that IVF-based methods are still very promising for hybrid queries.}
+
+	NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets.
+This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.
+As observed in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, StitchedVamana outperforms FilteredVamana in query efficiency.
+This difference arises from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
+
+	\textcolor{violet}{ACORN generally performs poorly, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
+Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.}
+
+	Among all methods, vector database systems (PASE, VBASE, Milvus) exhibit the worst performance.
 These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
-Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.}
-
-	\textcolor{violet}{\textit{Multi-Thread Search.} As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, under multi-threading, all algorithms except Puck show similar improvements, with UNG continuing to maintain the best performance.
-Puck achieves significant performance improvement in multi-threading scenarios.}
+Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
+
+	\textit{Multi-Thread Search.}
+	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, \textcolor{violet}{the performance distribution of algorithms remains largely unchanged except for Puck, with UNG continuing to maintain the best performance.
+Puck shows significant performance improvement under multi-threading.}
 
@@
 Similarly, VBASE, which employs a post-filtering strategy, shows efficiency that directly correlates with attribute selectivity—the more selective the filter, the more computational resources are wasted on retrieving irrelevant vectors.
-Faiss, which searches within the nearest clusters, may need to traverse more clusters to find sufficient results when relevant data points are unevenly distributed across clusters due to attribute skew, which impacts performance.
+Faiss, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.
 

### 2025-07-28 Revision/response.tex
1

@@
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we will add more comprehensive references in the paper.
+For the two parts you suggested, we have added more comprehensive references in the paper.
 
@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-Since other algorithms also do not support multi-attribute queries, we will explain this situation collectively in the corresponding section of the paper to save space.(
-\textbf{Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.})
+Since other algorithms also do not support multi-attribute queries, we have explained this situation collectively in the corresponding section of the paper to save space.
+(\textbf{Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.})
 

### 2025-07-28 VLDB2026/main.tex
1

--- 2025-07-28 VLDB2026/main.tex
@@
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
+%	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
@@
 Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
+	\textcolor{orange}{We conduct a comprehensive evaluation of 6 attribute filtering algorithms, 1 library, and 3 databases across 6 basic datasets, 2 real-world datasets, one 100M-scale dataset, and 2 multimodal datasets.
+By analyzing the query performance of each method under various scenarios, we reveal their respective strengths and weaknesses.
+We further examine their robustness by evaluating performance under different attribute distributions and selectivity levels.
+To ensure fairness and generality, we evaluate the methods on two different server environments.
+The evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.}
 
@@
 %	\subsection{Index Organization in Hybrid ANN Search}
-	\subsection{Index Organization in Hybrid Query}
+	\subsection{Index Organization}
 

### 2025-07-28 VLDB2026/main.tex
Update main.tex

@@
 Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}
+Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values.}
 
@@
 	\textcolor{blue}{
-	WinFilter maintains optimal performance by building an index for each tree node.
-It then performs an Approximate Nearest Neighbor (ANN) search on the relevant nodes and post-filters the results, ensuring high recall and queries per second (QPS).
+	WinFilter maintains optimal performance by building an index for each tree node. It then performs an ANN search on the relevant nodes and post-filters the results, ensuring high recall and QPS.
 	In contrast, iRange dynamically constructs a search graph during query time.

### 2025-07-28 Revision/response.tex

@@
 
-\textcolor{blue}{
-	Attribute filtering:"Overall, UNG, NHQ, and FilteredDisk-ANN demonstrate strong performance.
+Attribute filtering: \textcolor{blue}{
+	"Overall, UNG, NHQ, and FilteredDisk-ANN demonstrate strong performance.
 However, UNG suffers from performance degradation when the attribute count differs between indexing and querying.
@@
 
-Range filtering:\textcolor{blue}{
+Range filtering: \textcolor{blue}{
 	"WinFilter achieves the best search performance but requires high time and memory resources during index construction.

### 2025-07-28 Revision/response.tex
Update response.tex

@@
 That is a great suggestion.
-In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
+In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency and smaller RAM capacity of the Xeon 6330 processors.
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.
 \textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Different Hardware Environments.)}
@@
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
-\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
+\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
+Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values."}
 

### 2025-07-28 Revision/response.tex
Update response.tex

--- 2025-07-28 Revision/response.tex
@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-Since other algorithms also do not support multi-attribute queries, we have explained this situation collectively in the corresponding section of the paper to save space.
-(\textbf{Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.})
+Since other algorithms also do not support multi-attribute queries, we will explain this situation collectively in the corresponding section of the paper to save space.(
+\textbf{Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.})
 
@@
 Thank you for highlighting this point, which further emphasizes the significance of our work.
-\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript)}
+\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript.)}
 
@@
 This offers a more complete comparative view.
-\textbf{(Please refer to the "Build peak memory" part of Section 4.2.1 and  4.3.1, highlighted in blue in the revised manuscript)}
+\textbf{(Please refer to the "Build peak memory" part of Section 4.2.1 and  4.3.1, highlighted in blue in the revised manuscript.)}
 

### 2025-07-28 VLDB2026/main.tex
Update main.tex
change caption

@@
 
-	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) and 256GB of RAM.  
+	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache .  
 %	\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
-		\caption{Single-Attribute Building and Query (single thread) }
+		\caption{Single-Attribute Building and Query performance (single thread) }
 		\label{fig:exp_1_1_SingleLabel_1thread}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
-		\caption{Single-Attribute Building and Query (16 threads)}
+		\caption{Single-Attribute Building and Query performance (16 threads)}
 		\label{fig:exp_1_2_SingleLabel_16thread}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
-		\caption{Multi-attribute build and query (single thread)}
+		\caption{Multi-attribute build and query performance (single thread)}
 		\label{fig:exp_4_1_MultiLabel_1thread}
@@
 		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
-		\caption{Dig Dataset}
+		\caption{Big Dataset}
 		\label{fig:attribute big dataset}
@@
 	% 5. 全局总标题
-	\caption{\textcolor{violet}TrinityExtension——Attribution}
+	\caption{\textcolor{violet}Scalability Study——Attribution}
 	\label{fig:TrinityExtension——Attribution_main}
@@
 		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
-		\caption{RF-ANN search }
+		\caption{RF-ANN search performance }
 		\label{fig:exp_8_2}
@@
 	% 5. 全局总标题
-	\caption{\textcolor{violet}TrinityExtension——Range}
+	\caption{\textcolor{violet}Scalability Study——Range}
 	\label{fig:TrinityExtension——Attribution_main}

### 2025-07-29 VLDB2026/main.tex

@@
 	(1)\textbf{ Systematic Classification and Overview.}
-	%We systematically classify 6 representative attribute filtering algorithms from multiple dimensions, including index organization, filtering strategy, Boolean logic support, and index construction methods.
-Additionally, we survey 5 range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
-These efforts provide a unified reference framework for future study.
-	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
+%	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
 In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
 These efforts offer a unified reference framework for future research.
+	\textcolor{orange}{We systematically categorize 6 representative attribute filtering algorithms and 5 range filtering algorithms from the perspectives of index organization, filtering strategies, disk support, and complex attribute handling.
+We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles.
+This work offers a unified reference framework and technical foundation for future research in this field.}
 
@@
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-	%We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} 
-	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
+%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
 We further analyze the factors that affect the performance of the range query algorithm.
+	\textcolor{orange}{
+		We conduct benchmark evaluations of range filtering algorithms on one synthetic and 2 real-world datasets, using various query range settings.
+Our experiments reveal and analyze the differences in time and query efficiency across these algorithms.
+Furthermore, we compare their performance on multimodal and large-scale datasets, and assess their adaptability across different server environments.
+	}
 

### 2025-07-29 VLDB2026/main.tex
Update main.tex

--- 2025-07-28 VLDB2026/main.tex
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-Our findings remain consistent with those reported in Section 4.2.4.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.Although the algorithm ranking the third is different, because the performance of the algorithm ranking the third and the fourth is similar, we approximately think that the ranking has not changed.
+So our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-29 VLDB2026/main.tex
1
Update main.tex

--- 2025-07-29 VLDB2026/main.tex
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-Our findings remain consistent with those reported in Section 4.2.4.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable.
+So our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-29 VLDB2026/main.tex
Update main.tex

@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
+Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable.
 So our findings remain consistent with those reported in Section 4.2.4.
@@
 	\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
-	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/ \textbf{S} &M/S  &M/M  &W/W  \\
-	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &M/M  &S/M  &S/S \\
+	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
+	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
 	\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\

### 2025-07-29 VLDB2026/main.tex
change introduction

@@
 	(1)\textbf{ Systematic Classification and Overview.}
-%	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
+	%We systematically classify 6 representative attribute filtering algorithms from multiple dimensions, including index organization, filtering strategy, Boolean logic support, and index construction methods.
+Additionally, we survey 5 range filtering algorithms and provide an overview of widely used vector retrieval libraries (e.g., Faiss) and vector databases (e.g., Milvus, PASE, VBASE).
+These efforts provide a unified reference framework for future study.
+	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
 In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
 These efforts offer a unified reference framework for future research.
-	\textcolor{orange}{We systematically categorize 6 representative attribute filtering algorithms and 5 range filtering algorithms from the perspectives of index organization, filtering strategies, disk support, and complex attribute handling.
-We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles.
-This work offers a unified reference framework and technical foundation for future research in this field.}
-
-		(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
-		To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
+
+	\textcolor{blue}{	(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
+To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results.
+To comprehensively reflect diverse real-world application needs, we design experiments covering varying attribute distributions, selectivity levels, and query conditions, ensuring representative and practical evaluation.
+Furthermore, we test on a large-scale dataset containing 100 million records to analyze the scalability and performance of various algorithms.
+These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid queries.}
+
+%		To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
 Furthermore, we design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
@@
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
+	%We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} 
+	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
 We further analyze the factors that affect the performance of the range query algorithm.
-	\textcolor{orange}{
-		We conduct benchmark evaluations of range filtering algorithms on one synthetic and 2 real-world datasets, using various query range settings.
-Our experiments reveal and analyze the differences in time and query efficiency across these algorithms.
-Furthermore, we compare their performance on multimodal and large-scale datasets, and assess their adaptability across different server environments.
-	}
-
-	(5)\textbf{ Recommendations and Challenges.}
-	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
+
+	\textcolor{blue}{(5)\textbf{ Recommendations and Challenges.}
+	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios.
+Readers can select suitable algorithms according to their specific application needs.
+In addition, we identify key challenges in the field of hybrid queries.
+These challenges include the lack of consideration for the correlation between attributes and vectors, limited support for Boolean logic, insufficient capability for multi-attribute range filtering, and sensitivity of algorithms to data distribution.
+Currently, few methods support both attribute filtering and range filtering at the same time.
+This indicates potential directions for future research.
+}
+%	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable.
-So our findings remain consistent with those reported in Section 4.2.4.
+Our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}
@@
 	\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
-	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
-	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
+	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/ \textbf{S} &M/S  &M/M  &W/W  \\
+	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &M/M  &S/M  &S/S \\
 	\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\

### 2025-07-29 VLDB2026/main.tex

@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-Our findings remain consistent with those reported in Section 4.2.4.
+Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable.
+So our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-29 VLDB2026/main.tex
1

--- 2025-07-29 VLDB2026/main.tex
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.Although the algorithm ranking the third is different, because the performance of the algorithm ranking the third and the fourth is similar, we approximately think that the ranking has not changed.
 So our findings remain consistent with those reported in Section 4.2.4.
@@
 	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
-	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &W  &M  &S  &M  &S  &\textbf{S}  &M/M  &M/M  &W/W  &W/W  &-/-  \\
+	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
 	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\

### 2025-07-29 VLDB2026/main.tex
1

@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-		\caption{MultiModal}
+		\caption{Multi-modal}
 		\label{fig:attribute-multimodal} 
@@
 	\subsubsection{Scalability Study}
-
-	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
-Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
-It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values.}
-
-	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
-	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
-However, this also comes with significant memory overhead.
-The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
-Furthermore, we did not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
-StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
-CAPS, on the other hand, is limited by its implementation and achieves a recall of only around 0.2.}
-%		we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
-This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}
-
-\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
-
-\textcolor{blue}{
+	\textit{\textbf{\textcolor{blue}{Multi-modal Queries.}}} \textcolor{blue}{
 		We conduct experiments on the text2image-mix dataset.
@@
 
+	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
+%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
+It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values.}
+
+	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
+	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+However, this also comes with significant memory overhead.
+The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
+Furthermore, we did not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
+StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
+CAPS, on the other hand, is limited by its implementation and achieves a recall of only around 0.2.}
+%		we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
+This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}
+
 %	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
-		\caption{MultiModal}
+		\caption{Multi-modal}
 		\label{fig:range-multimodal} 
@@
 
+	\textit{\textbf{\textcolor{blue}{Multi-modal Queries.}}}
+	\textcolor{blue}{
+		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets.}
+
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.Although the algorithm ranking the third is different, because the performance of the algorithm ranking the third and the fourth is similar, we approximately think that the ranking has not changed.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
+Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable.
 So our findings remain consistent with those reported in Section 4.2.4.
@@
 Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.
-
-	\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
-	\textcolor{blue}{
-	Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
-As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
-This is because these range query algorithms are almost graph-based.
-Graph algorithms need more iterations to find true neighbors in OOD datasets.}
 
@@
 	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
-	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
+	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &W  &M  &S  &M  &S  &\textbf{S}  &M/M  &M/M  &W/W  &W/W  &-/-  \\
 	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\

### 2025-07-29 VLDB2026/main.tex
1

--- 2025-07-29 VLDB2026/main.tex
@@
 Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
-\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
+%\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
 However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets.
 In contrast, Milvus has lower peak memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
-}
+\textcolor{orange}{
+Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
+As a result, peak memory usage during querying is generally slightly lower than during construction.
+However, exceptions exist.
+As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
 

### 2025-07-29 VLDB2026/main.tex
Update main.tex

@@
 Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
-%\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
+\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
 However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets.
 In contrast, Milvus has lower peak memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
-\textcolor{orange}{
-Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
-As a result, peak memory usage during querying is generally slightly lower than during construction.
-However, exceptions exist.
-As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
+}
 
@@
 
+	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
+%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
+Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
+It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
+Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values.}
+
+	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
+	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+However, this also comes with significant memory overhead.
+The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
+Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
+StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
+CAPS, on the other hand, is limited by its implementation and achieves a recall of only around 0.2.}
+%		we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
+This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}
+
 %	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}
@@
 
+	\textit{\textbf{\textcolor{blue}{Multi-modal Queries.}}}
+	\textcolor{blue}{
+		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets.}
+
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 

### 2025-07-29 Revision/response.tex
1

@@
 
-For attribute filtering, please see section 4.2.1.
-
+%For attribute filtering, please see section 4.2.1.
+ \textbf{(Please refer to the blue highlighted parts in Section 4.2.1 for attribute filtering.)}
 \textcolor{blue}{"For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
@@
 
-For range filtering, please see section 4.3.1.
-
+%For range filtering, please see section 4.3.1.
+ \textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
 \textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
@@
 \textbf{Response:} 
-Thank you for pointing this out.
+%Thank you for pointing this out.
 Both paper [49] and our paper are benchmarks.
@@
 We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
+Thank you for pointing this out.
+Reference [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark for hybrid queries.
+We originally cited [49] in the experimental setup section to adopt the evaluation metrics it proposed, as hybrid queries are inherently built upon ANN techniques.
+We acknowledge that the distinction between our work and the cited paper was not clearly explained in the earlier version.
+To address this, we have added a clarification in the Introduction and also referenced several experimental studies in the ANN literature.
+Please refer to Section 1.1 for details.
 

### 2025-07-29 Revision/response.tex
1

@@
 To address this, we have added a clarification in the Introduction and also referenced several experimental studies in the ANN literature.
-Please refer to Section 1.1 for details.
 
-\textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+\textbf{(Please refer to Section 1.1 for details.)} \textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.

### 2025-07-29 VLDB2026/main.tex
1

--- 2025-07-29 VLDB2026/main.tex
@@
 	\textit{\textbf{Build peak memory.}}  
-	\textcolor{orange}{As explained in the attribute filtering analysis, the peak memory usage during index construction generally depends on the combined size of the dataset and the index, as illustrated in Figure~\ref{fig:rangeFilter_build_memory_mb}.
-Range filtering adheres to this pattern, while PASE deviates due to reasons discussed earlier.}
+	\textcolor{orange}{As explained in the attribute filtering analysis, the build peak memory usage typically depends on the combined size of the dataset and the index.
+In general, algorithms with larger index sizes (including the dataset) tend to exhibit higher build peak memory consumption.
+As shown in Figure~\ref{fig:rangeFilter_build_memory_mb}, range filtering also adheres to this pattern, while PASE deviates due to reasons discussed earlier.}
 
@@
 		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
-		\caption{Dig Dataset}
+		\caption{Big Dataset}
 		\label{fig: range big dataset}
@@
 	\subsubsection{Scalability Study}
+
+	\textit{\textbf{\textcolor{blue}{Multi-modal Queries.}}}
+	\textcolor{blue}{
+		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets.}
 

### 2025-07-29 Revision/response.tex
Update response.tex

@@
 Achieving good performance on such a dataset often requires the algorithm to demonstrate stronger robustness.
-\textbf{(Please refer to the last paragraph of Section 4.2.3 and the green highlighted part in Section 4.3.3.)}
+\textbf{(Please see Section 4.2.3 and Section 4.3.3, highlighted in green in the revised manuscript.)}
 
@@
 Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately.
-\textbf{(Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
+\textbf{(Please see Section 4.1.1, Section 4.2.4 and Secntion 4.3.4, highlighted in blue in the revised manuscript.)
+	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
 }
 
-\textcolor{blue}{
+Section 4.1.1:\textcolor{blue}{
 "Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
@@
 
-Attribute filtering: \textcolor{blue}{
+Section 4.2.4: \textcolor{blue}{
 	"We conducted experiments on the text2image-mix dataset.
@@
 
-Range filtering:\textcolor{blue}{
+Section 4.3.4:\textcolor{blue}{
 		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.

### 2025-07-29 VLDB2026/main.tex
Update main.tex

--- 2025-07-29 VLDB2026/main.tex
@@
 		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
-		\caption{Hybrid query example}
+		\caption{Hybrid Query Example}
 
@@
 
-		\caption{Graph index and IVF index}
+		\caption{Graph Index and IVF Index}
 
@@
 
-		\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN search algorithms}}
+		\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN Search Algorithms}}
 		\small
@@
 			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
-			\caption{Construction time}
+			\caption{Construction Time}
 			\label{fig:build_time_comparison_query1}
@@
 			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
-			\caption{Index size (including original dataset)}
+			\caption{Index Size (Including Original Dataset)}
 			\label{fig:index_size_mb_comparison_query1}
@@
 			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
-			\caption{Build peak memory }
+			\caption{Build Peak Memory }
 			\label{fig:build_memory_mb_comparison}
@@
 			\includegraphics[width=0.99\linewidth]{figures/searchMem/label_memory_comparison.pdf}
-			\caption{Search peak memory}
+			\caption{Search Peak Memory}
 			\label{fig:search_memory_mb_comparison}
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
-		\caption{\textcolor{violet}{Time and space overhead}}
+		\caption{\textcolor{violet}{Time and Space Overhead}}
 		\label{fig:build_index_comparison}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
-		\caption{Single-Attribute Building and Query performance (single thread) }
+		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (Single Thread) }
 		\label{fig:exp_1_1_SingleLabel_1thread}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
-		\caption{Single-Attribute Building and Query performance (16 threads)}
+%		\caption{Single-Attribute Building and Query performance (16 threads)}
+		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (16 Threads)}
 		\label{fig:exp_1_2_SingleLabel_16thread}
@@
 
-	\textit{\textbf{Single-Attribute Building and Single-Attribute Query.}}
+	\textit{\textbf{Single-Attribute Index Construction and Single-Attribute Query.}}
 	In this scenario, we construct the index using an attribute and apply filtering conditions on the same attribute.
@@
 
-	\textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
+	\textit{\textbf{Multi-Attribute Index Construction and Single-Attribute Query.}}
 	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query.
@@
 		\includegraphics[width=0.7\columnwidth]{figures/exp/exp_2_1.pdf}
-		\caption{Effect of Multi-Attribute Index Construction on Single Query Performance.
-($S$ denotes single-attribute index construction and single-attribute query; $M$ denotes multi-attribute index construction and single-attribute query)}
+		\caption{Effect of Multi-Attribute Index Construction on Single-Attribute Query Performance ($S$ denotes single-attribute index construction and single-attribute query, $M$ denotes multi-attribute index construction and single-attribute query)}
 		\label{fig:exp_2_1}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
-		\caption{Multi-attribute build and query performance (single thread)}
+		\caption{Performance of Multi-Attribute Index Construction and Multi-Attribute Query (single thread)}
 		\label{fig:exp_4_1_MultiLabel_1thread}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
-		\caption{Effect of attribute distribution on query performance (single thread)}
+		\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts) (Single Thread) }
 		\label{fig:exp_3_1}
 
-		\footnotesize{
-		\begin{center}
-			\begin{minipage}{\linewidth}
-				\centering	
-				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
-			\end{minipage}
-		\end{center}
-		}
+%		\footnotesize{
+%		\begin{center}
+%			\begin{minipage}{\linewidth}
+%				\centering	
+%				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
+%			\end{minipage}
+%		\end{center}
+%		}
 	\end{figure*}
 
-	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
+	\textit{\textbf{Multi-Attribute Index Construction and Multi-Attribute Query.}}  
 	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios.
@@
 			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
-			\caption{Algorithms optimized for low AS.}
+			\caption{Algorithms Optimized for Low AS}
 			\label{fig:exp_5_2_1}
@@
 			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_2.pdf}
-			\caption{Algorithms optimized for high AS.}
+			\caption{Algorithms Optimized for High AS}
 			\label{fig:exp_5_2_2}
@@
 			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_3.pdf}
-			\caption{Algorithms insensitive to AS.}
+			\caption{Algorithms Insensitive to AS}
 			\label{fig:exp_5_2_3}
@@
 
-		\caption{Different AS under the same algorithm}
+		\caption{Different AS under the Same Algorithm}
 		\label{fig:exp_5_2_combined}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
-		\caption{Effect of dataset on Query}
+		\caption{Effect of Different Datasets on AF-ANN Search}
 		\label{fig:exp_6_1}
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-		\caption{MultiModal}
+		\caption{Multi-Modal}
 		\label{fig:attribute-multimodal} 
@@
 	% 5. 全局总标题
-	\caption{\textcolor{violet}Scalability Study——Attribution}
+	\caption{\textcolor{violet}Scalability Study——Attribute}
 	\label{fig:TrinityExtension——Attribution_main}
@@
 	\subsubsection{Scalability Study}
-
-	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
-Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
-It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values.}
-
-	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
-	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
-However, this also comes with significant memory overhead.
-The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
-Furthermore, we did not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
-StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
-CAPS, on the other hand, is limited by its implementation and achieves a recall of only around 0.2.}
-%		we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
-This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}
-
-\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}
-
-\textcolor{blue}{
+	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}} \textcolor{blue}{
 		We conduct experiments on the text2image-mix dataset.
@@
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
-			\caption{\footnotesize Construction time}
+			\caption{\footnotesize Construction Time}
 			\label{fig:rangeFilter_build_time}
@@
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
-			\caption{\footnotesize Index size}
+			\caption{\footnotesize Index Size}
 			\label{fig:rangeFilter_index_size_mb}
@@
 			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
-			\caption{\footnotesize Build peak memory}
+			\caption{\footnotesize Build Peak Memory}
 			\label{fig:rangeFilter_build_memory_mb}
@@
 			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
-			\caption{\footnotesize Search peak memory}
+			\caption{\footnotesize Search Peak Memory}
 			\label{fig:rangeFilter_search_memory_mb}
@@
 %		\caption{Time and space overhead of index construction}
-		\caption{\textcolor{violet}{Time and space overhead}}
+		\caption{\textcolor{violet}{Time and Space Overhead}}
 		\label{fig:rangeFilter_build_index_comparison}
@@
 		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
-		\caption{RF-ANN search performance }
+		\caption{Performance of RF-ANN Search}
 		\label{fig:exp_8_2}
@@
 		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
-		\caption{Dataset Effect on RF-ANN Search}
+		\caption{Effect of Different Datasets on RF-ANN Search}
 		\label{fig:exp_8_3}
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
-		\caption{MultiModal}
+		\caption{Multi-Modal}
 		\label{fig:range-multimodal} 
@@
 	\subsubsection{Scalability Study}
+
+	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}}
+	\textcolor{blue}{
+		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
+This is because these range query algorithms are almost graph-based.
+Graph algorithms need more iterations to find true neighbors in OOD datasets.}
 

### 2025-07-29 Revision/response.tex

@@
 Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have added two datasets that use real attributes.
+To address this issue, we have added two datasets that use real attributes.\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
 
@@
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.
-\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Different Hardware Environments.)}
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.\textbf{(Please see Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
 
-Attribute filtering:
+Section 4.2.4:
 %\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
@@
 
-Range filtering:
+Section 4.3.4:
 %\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
@@
 Thank you for your suggestion.
-We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.\textbf{(Please see Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
 \begin{figure}[htbp]
@@
 %For attribute filtering, please see section 4.2.1.
- \textbf{(Please refer to the blue highlighted parts in Section 4.2.1 for attribute filtering.)}
+% \textbf{(Please refer to the blue highlighted parts in Section 4.2.1 for attribute filtering.)}
+Section 4.2.1:
 \textcolor{blue}{"For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
@@
 %For range filtering, please see section 4.3.1.
- \textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
+ %\textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
+ Section 4.3.1:
 \textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
@@
 In particular, StitchedVamana performs poorly on Deep100M.
-\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
+\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
+%\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
 
-Attribute filtering:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Section 4.2.4:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 
-Range filtering:
+Section 4.3.4:
 \textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.

### 2025-07-29 Revision/response.tex
change table

--- 2025-07-29 Revision/response.tex
@@
 \usepackage{multirow}
+\usepackage{fontawesome}
 \usepackage{balance}
@@
 
-%For attribute filtering, please see section 4.2.1.
- \textbf{(Please refer to the blue highlighted parts in Section 4.2.1 for attribute filtering.)}
+For attribute filtering, please see section 4.2.1.
+
 \textcolor{blue}{"For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
@@
 
-%For range filtering, please see section 4.3.1.
- \textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
+For range filtering, please see section 4.3.1.
+
 \textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios.\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios,as shown in Table~\ref{tab:algo_scenarios}.
+\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+
+\subsection{Recommendations.}
+%Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
+
+\begin{table*}[htbp]
+	\caption{Algorithm Recommendation}
+	\label{tab:algo_scenarios}
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{|l|*{16}{c|}}
+			\hline
+			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
+			& \multicolumn{6}{c|}{\textbf{AF}} 
+			& \multicolumn{5}{c|}{\textbf{RF}} 
+			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
+			\cline{2-17}
+			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
+			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
+			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
+			\hline
+			\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
+			\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
+			\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
+			\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
+			\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
+			\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
+			\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
+			\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
+			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
+			\hline
+		\end{tabular}
+	}
+	\vspace{1mm}
+	\begin{flushleft}
+		\textbf{Note:} S = Strong performance, \textbf{S} = Strongest performance, M = Medium performance, W = Weak performance, 
+		\faCheck = Recommended, \faTimes = Not Recommended.
+	\end{flushleft}
+	\centering
+
+\end{table*}
 
@@
 \textbf{Response:} 
-%Thank you for pointing this out.
+Thank you for pointing this out.
 Both paper [49] and our paper are benchmarks.
@@
 We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
-Thank you for pointing this out.
-Reference [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark for hybrid queries.
-We originally cited [49] in the experimental setup section to adopt the evaluation metrics it proposed, as hybrid queries are inherently built upon ANN techniques.
-We acknowledge that the distinction between our work and the cited paper was not clearly explained in the earlier version.
-To address this, we have added a clarification in the Introduction and also referenced several experimental studies in the ANN literature.
 
-\textbf{(Please refer to Section 1.1 for details.)} \textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+\textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.

### 2025-07-29 VLDB2026/main.tex
change table

--- 2025-07-29 VLDB2026/main.tex
@@
 	\textit{\textbf{Build peak memory.}}  
-	\textcolor{orange}{As explained in the attribute filtering analysis, the build peak memory usage typically depends on the combined size of the dataset and the index.
-In general, algorithms with larger index sizes (including the dataset) tend to exhibit higher build peak memory consumption.
-As shown in Figure~\ref{fig:rangeFilter_build_memory_mb}, range filtering also adheres to this pattern, while PASE deviates due to reasons discussed earlier.}
+	\textcolor{orange}{As explained in the attribute filtering analysis, the peak memory usage during index construction generally depends on the combined size of the dataset and the index, as illustrated in Figure~\ref{fig:rangeFilter_build_memory_mb}.
+Range filtering adheres to this pattern, while PASE deviates due to reasons discussed earlier.}
 
@@
 		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
-		\caption{Big Dataset}
+		\caption{Dig Dataset}
 		\label{fig: range big dataset}
@@
 	\caption{Algorithm Recommendation}
+	\label{tab:algo_scenarios}
 	\resizebox{\textwidth}{!}{

### 2025-07-29 Revision/response.tex
Update response.tex

--- 2025-07-29 Revision/response.tex
@@
 Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have added two datasets that use real attributes.\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
+To address this issue, we have added two datasets that use real attributes.
+\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
 
@@
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.\textbf{(Please see Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.
+\textbf{(Please see Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
 
@@
 Thank you for your suggestion.
-We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.\textbf{(Please see Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
+We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+\textbf{(Please see Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
 \begin{figure}[htbp]
@@
 Additionally, we have provided a more in-depth analysis of the internal mechanisms of each algorithm in the text, aiming to uncover the fundamental reasons behind their performance.
-\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
 
-Attribute filtering: \textcolor{blue}{
+Section 5.1.1: \textcolor{blue}{
 	"Overall, UNG, NHQ, and FilteredDisk-ANN demonstrate strong performance.
@@
 
-Range filtering: \textcolor{blue}{
+Section 5.1.2: \textcolor{blue}{
 	"WinFilter achieves the best search performance but requires high time and memory resources during index construction.
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios.\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios.
+\textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
 
@@
 
-We have revised the manuscript accordingly.\textbf{ (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.)} Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
+We have revised the manuscript accordingly.
+%\textbf{ (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.)} 
+Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
+\textbf{(Please see Section 4.2.1 and the "Single-Attribute Building and Single-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.)}
 
@@
 To address this, we have added a clarification in the Introduction and also referenced several experimental studies in the ANN literature.
+\textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 
-\textbf{(Please refer to Section 1.1 for details.)} \textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+ \textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
@@
 For the two parts you suggested, we have added more comprehensive references in the paper.
-
-Please see section 1.1.
+\textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 
@@
 We sincerely apologize for the misuse of notation in Definition 2.3.
-This has been corrected in the revised version.\textbf{(Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript.)}
+This has been corrected in the revised version.
+\textbf{(Please see the "Definition 2.3" part of Section 2.1, highlighted in blue in the revised manuscript.)}
 
@@
 These paragraphs summarize how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures.
+\textbf{(Please see Section 2.2, highlighted in blue in the revised manuscript.)}
 
@@
 The detailed parameter configurations can be found in our public code repository.
-(\textbf{Please refer to Section 4.1.4, highlighted in blue in the revised manuscript.})
+(\textbf{Please see Section 4.1.4, highlighted in blue in the revised manuscript.})
 
@@
 Since other algorithms also do not support multi-attribute queries, we have explained this situation collectively in the corresponding section of the paper to save space.
-(\textbf{Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.})
+(\textbf{Please see the "Multi-Attribute Construction and Multi-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.})
 
@@
 Thank you for highlighting this point, which further emphasizes the significance of our work.
-\textbf{(Please refer to the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript.)}
+\textbf{(Please see the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript.)}
 
-To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2.\textbf{(Please see paragraph 1 of Section 4.3, which is highlighted in blue in the revised manuscript.)}
+To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2. \textbf{(Please see Section 4.3, highlighted in blue in the revised manuscript.)}
 
 In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
-We added more detailed and in-depth analysis to provide a clearer explanation.\textbf{(Please refer to the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript.)}
+We added more detailed and in-depth analysis to provide a clearer explanation.
+\textbf{(Please see the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript.)}
 
@@
 This offers a more complete comparative view.
-\textbf{(Please refer to the "Build peak memory" part of Section 4.2.1 and  4.3.1, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see the "Build peak memory" part of Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
 
@@
 This is because SeRF’s multi-filtering mechanism needs to inspect a large number of edge entries that are irrelevant to the current small-range query, thereby introducing fixed computational and memory access overhead.
-Additionally, during graph traversal, many invalid neighbors may be visited, causing the search to fall into local optima, which further degrades query performance and recall.\textbf{(Please see  Section 4.3.2, which is highlighted in blue in the revised manuscript.)}
+Additionally, during graph traversal, many invalid neighbors may be visited, causing the search to fall into local optima, which further degrades query performance and recall.
+\textbf{(Please see  Section 4.3.2, highlighted in blue in the revised manuscript.)}
 

### 2025-07-29 Revision/response.tex
1

--- 2025-07-29 Revision/response.tex
@@
 \usepackage{multirow}
-\usepackage{fontawesome}
 \usepackage{balance}
@@
 Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have added two datasets that use real attributes.\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
+To address this issue, we have added two datasets that use real attributes.
 
@@
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
-We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.\textbf{(Please see Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
+We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.
+\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Different Hardware Environments.)}
 
-Section 4.2.4:
+Attribute filtering:
 %\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
@@
 
-Section 4.3.4:
+Range filtering:
 %\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
@@
 Thank you for your suggestion.
-We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.\textbf{(Please see Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
+We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
 \begin{figure}[htbp]
@@
 %For attribute filtering, please see section 4.2.1.
-% \textbf{(Please refer to the blue highlighted parts in Section 4.2.1 for attribute filtering.)}
-Section 4.2.1:
+ \textbf{(Please refer to the blue highlighted parts in Section 4.2.1 for attribute filtering.)}
 \textcolor{blue}{"For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
@@
 %For range filtering, please see section 4.3.1.
- %\textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
- Section 4.3.1:
+ \textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
 \textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
@@
 In particular, StitchedVamana performs poorly on Deep100M.
-\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
-%\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
+\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
 
-Section 4.2.4:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Attribute filtering:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 
-Section 4.3.4:
+Range filtering:
 \textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios,as shown in Table~\ref{tab:algo_scenarios}.
-\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
-
-\subsection{Recommendations.}
-%Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
-
-\begin{table*}[htbp]
-	\caption{Algorithm Recommendation}
-	\label{tab:algo_scenarios}
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{|l|*{16}{c|}}
-			\hline
-			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
-			& \multicolumn{6}{c|}{\textbf{AF}} 
-			& \multicolumn{5}{c|}{\textbf{RF}} 
-			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
-			\cline{2-17}
-			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
-			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
-			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
-			\hline
-			\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
-			\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
-			\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
-			\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
-			\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
-			\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
-			\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
-			\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
-			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
-			\hline
-		\end{tabular}
-	}
-	\vspace{1mm}
-	\begin{flushleft}
-		\textbf{Note:} S = Strong performance, \textbf{S} = Strongest performance, M = Medium performance, W = Weak performance, 
-		\faCheck = Recommended, \faTimes = Not Recommended.
-	\end{flushleft}
-	\centering
-
-\end{table*}
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios.\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
 
@@
 Thank you for pointing this out.
-Reference [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark for hybrid queries.
-We originally cited [49] in the experimental setup section to adopt the evaluation metrics it proposed, as hybrid queries are inherently built upon ANN techniques.
-We acknowledge that the distinction between our work and the cited paper was not clearly explained in the earlier version.
-To address this, we have added a clarification in the Introduction and also referenced several experimental studies in the ANN literature.
+The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
+We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version.
+To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature.
 

### 2025-07-29 VLDB2026/main.tex
1

@@
 	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-\textcolor{orange}{Although existing work, such as the survey by \cite{compare}, reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+\textcolor{orange}{Although existing works, such as the surveys in \cite{compare,azizi2025graph}, conduct benchmark evaluations or experimental analyses of ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
@@
 	\caption{Algorithm Recommendation}
-	\label{tab:algo_scenarios}
 	\resizebox{\textwidth}{!}{

### 2025-07-29 Revision/response.tex
fig

--- 2025-07-29 Revision/response.tex
@@
 \usepackage{fancybox}
+\usepackage{graphicx}
+\usepackage{subcaption}
 
@@
 	\centering
+	\includegraphics[width=\linewidth]{fig/exp_3_1_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
-	\caption{}
+	\caption{Effect of attribute distribution on query performance}
 	\label{fig:attribute_distribution}
@@
 	\centering
+	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
-	\caption{}
+	\caption{Different AS under the same algorithm}
 	\label{fig:attribute_selectivity}
@@
 Achieving good performance on such a dataset often requires the algorithm to demonstrate stronger robustness.
-\textbf{(Please see Section 4.2.3 and Section 4.3.3, highlighted in green in the revised manuscript.)}
+\textbf{(Please refer to the last paragraph of Section 4.2.3 and the green highlighted part in Section 4.3.3.)}
 
@@
 Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately.
-\textbf{(Please see Section 4.1.1, Section 4.2.4 and Secntion 4.3.4, highlighted in blue in the revised manuscript.)
-	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
+\textbf{(Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
 }
 
-Section 4.1.1:\textcolor{blue}{
+\textcolor{blue}{
 "Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
@@
 
-Section 4.2.4: \textcolor{blue}{
+Attribute filtering: \textcolor{blue}{
 	"We conducted experiments on the text2image-mix dataset.
@@
 
-Section 4.3.4:\textcolor{blue}{
+Range filtering:\textcolor{blue}{
 		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.
@@
 We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
-Thank you for pointing this out.
-The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
-We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
-We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version.
-To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature.
 
-\textbf{(Please refer to Section 1.1 for details.)} \textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+\textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.

### 2025-07-29 Revision/response.tex

--- 2025-07-29 Revision/response.tex
@@
 To address this issue, we have added two datasets that use real attributes.
+\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
 
@@
 We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.
-\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Different Hardware Environments.)}
+\textbf{(Please see Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
 
-Attribute filtering:
+Section 4.2.4:
 %\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
@@
 We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+\textbf{(Please see Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
 \begin{figure}[htbp]
@@
 Thank you for pointing this out.
-The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
-We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
-We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version.
-To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature.
+Reference [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark for hybrid queries.
+We originally cited [49] in the experimental setup section to adopt the evaluation metrics it proposed, as hybrid queries are inherently built upon ANN techniques.
+We acknowledge that the distinction between our work and the cited paper was not clearly explained in the earlier version.
+To address this, we have added a clarification in the Introduction and also referenced several experimental studies in the ANN literature.
+\textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 
-\textbf{(Please refer to Section 1.1 for details.)} \textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+ \textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.

### 2025-07-29 VLDB2026/main.tex
fig

--- 2025-07-29 VLDB2026/main.tex
@@
 	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-\textcolor{orange}{Although existing works, such as the surveys in \cite{compare,azizi2025graph}, conduct benchmark evaluations or experimental analyses of ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+\textcolor{orange}{Although existing work, such as the survey by \cite{compare}, reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
@@
 The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
-Furthermore, we did not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
+Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
 StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.

### 2025-07-29 Revision/response.tex
1

--- 2025-07-29 Revision/response.tex
@@
 \usepackage{fancybox}
-\usepackage{graphicx}
-\usepackage{subcaption}
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/exp_3_1_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
-	\caption{Effect of attribute distribution on query performance}
+	\caption{}
 	\label{fig:attribute_distribution}
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
-	\caption{Different AS under the same algorithm}
+	\caption{}
 	\label{fig:attribute_selectivity}
@@
 Thank you for your suggestion.
-Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have added two datasets that use real attributes.
+Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
+To address this issue, we have changed two datasets (YT-Audio-Real, WIT-Real) to use real attributes.
+We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:attribute_distribution}.
+(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)
 
@@
 
-To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in Meta-Review R3.
+To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments.
+For detailed information on these two new datasets and our improvements to range filtering, please see Meta-Review R3.
 

### 2025-07-29 Revision/response.tex
1

--- 2025-07-29 Revision/response.tex
@@
 
-For attribute filtering, please see section 4.2.1.
-
+%For attribute filtering, please see section 4.2.1.
+% \textbf{(Please refer to the blue highlighted parts in Section 4.2.1 for attribute filtering.)}
+Section 4.2.1:
 \textcolor{blue}{"For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
@@
 
-For range filtering, please see section 4.3.1.
-
+%For range filtering, please see section 4.3.1.
+ %\textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
+ Section 4.3.1:
 \textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios.\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios,as shown in Table~\ref{tab:algo_scenarios}.
+\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+
+\subsection{Recommendations.}
+%Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
+
+\begin{table*}[htbp]
+	\caption{Algorithm Recommendation}
+	\label{tab:algo_scenarios}
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{|l|*{16}{c|}}
+			\hline
+			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
+			& \multicolumn{6}{c|}{\textbf{AF}} 
+			& \multicolumn{5}{c|}{\textbf{RF}} 
+			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
+			\cline{2-17}
+			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
+			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
+			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
+			\hline
+			\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
+			\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
+			\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
+			\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
+			\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
+			\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
+			\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
+			\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
+			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
+			\hline
+		\end{tabular}
+	}
+	\vspace{1mm}
+	\begin{flushleft}
+		\textbf{Performance Levels:}  \textbf{S} = Strongest performance, S = Strong performance, M = Medium performance, W = Weak performance, - = Not Supported \quad
+		\textbf{Recommendation:} \faCheck = Recommended, \faTimes = Not Recommended
+	\end{flushleft}
+
+	\centering
+
+\end{table*}
 
@@
 We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
+Thank you for pointing this out.
+The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
+We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version.
+To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature.
 
-\textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+\textbf{(Please refer to Section 1.1 for details.)} \textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.

### 2025-07-29 Revision/response.tex

--- 2025-07-29 Revision/response.tex
@@
 Thank you for your suggestion.
-Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have added two datasets that use real attributes.
-\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
+Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
+To address this issue, we have changed two datasets (YT-Audio-Real, WIT-Real) to use real attributes.
+We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:attribute_distribution}.
+(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)
 

### 2025-07-29 Revision/response.tex

@@
 Thank you for your suggestion.
-Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have changed two datasets (YT-Audio-Real, WIT-Real) to use real attributes.
-We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:attribute_distribution}.
-(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)
+Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
+To address this issue, we have added two datasets that use real attributes.
+\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
 
@@
 
-To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments.
-For detailed information on these two new datasets and our improvements to range filtering, please see Meta-Review R3.
+To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in Meta-Review R3.
 
@@
 Thank you for pointing this out.
-Reference [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark for hybrid queries.
-We originally cited [49] in the experimental setup section to adopt the evaluation metrics it proposed, as hybrid queries are inherently built upon ANN techniques.
-We acknowledge that the distinction between our work and the cited paper was not clearly explained in the earlier version.
-To address this, we have added a clarification in the Introduction and also referenced several experimental studies in the ANN literature.
-\textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
+The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
+We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version.
+To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature.
 

### 2025-07-29 VLDB2026/main.tex
Revert "Update main.tex"
This reverts commit 3adca58c58c42a88e5e694ca7dcd97e2c637e7f1, reversing
changes made to b3510d7fd9ce3cabc70e54020ff229a2848cd81e.

--- 2025-07-29 VLDB2026/main.tex
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
-		\caption{Performance of Multi-Attribute Index Construction and Multi-Attribute Query (single thread)}
+		\caption{Performance of Multi-Attribute Index Construction and Multi-Attribute Query}
 		\label{fig:exp_4_1_MultiLabel_1thread}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
-		\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts) (Single Thread) }
+		\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
 		\label{fig:exp_3_1}

### 2025-07-29 Revision/response.tex
1
Update response.tex

--- 2025-07-29 Revision/response.tex
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios.
-\textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios,as shown in Table~\ref{tab:algo_scenarios}.
+\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+
+\subsection{Recommendations.}
+%Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
+
+\begin{table*}[htbp]
+	\caption{Algorithm Recommendation}
+	\label{tab:algo_scenarios}
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{|l|*{16}{c|}}
+			\hline
+			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
+			& \multicolumn{6}{c|}{\textbf{AF}} 
+			& \multicolumn{5}{c|}{\textbf{RF}} 
+			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
+			\cline{2-17}
+			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
+			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
+			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
+			\hline
+			\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
+			\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
+			\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
+			\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
+			\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
+			\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
+			\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
+			\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
+			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
+			\hline
+		\end{tabular}
+	}
+	\vspace{1mm}
+	\begin{flushleft}
+		\textbf{Note:} S = Strong performance, \textbf{S} = Strongest performance, M = Medium performance, W = Weak performance, 
+		\faCheck = Recommended, \faTimes = Not Recommended.
+	\end{flushleft}
+	\centering
+
+\end{table*}
 
@@
 Thank you for pointing this out.
-The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
-We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
-We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version.
-To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature.
+Reference [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark for hybrid queries.
+We originally cited [49] in the experimental setup section to adopt the evaluation metrics it proposed, as hybrid queries are inherently built upon ANN techniques.
+We acknowledge that the distinction between our work and the cited paper was not clearly explained in the earlier version.
+To address this, we have added a clarification in the Introduction and also referenced several experimental studies in the ANN literature.
+\textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 

### 2025-07-29 Revision/response.tex

@@
 Thank you for your suggestion.
-Using ID as attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have added two datasets that use real attributes.
-\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
+Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
+To address this issue, we have changed two datasets (YT-Audio-Real, WIT-Real) to use real attributes.
+We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:attribute_distribution}.
+\textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}
 

### 2025-07-29 Revision/response.tex
Update response.tex
add table 2

@@
 
-\subsection{Recommendations.}
+%\subsection{Recommendations.}
 %Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
@@
 We realized that the original wording is somewhat vague and led to confusion among readers.
-To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table.
-
-\textcolor{blue}{"The fused table is Table1: Comparison of AF-ANN and RF-ANN search algorithms."}
+To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table,as shown in Table~\ref{tab:compair_1}.
+
+	\renewcommand{\arraystretch}{0.9}
+\begin{table*}[t]
+	\centering
+	%\setlength{\belowcaptionskip}{-0.3cm}
+
+	\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN Search Algorithms}}
+	\small
+	%		\label{tab:compair_1}
+	%		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
+		%			\hline
+		%			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+		%			\hline
+		%			NHQ & Graph & C & Y & N& N& N & N & N \\
+		%			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
+		%			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
+		%			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
+		%			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
+		%			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
+		%			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
+		%			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
+		%			
+		%			\hline
+		%			
+		%		\end{tabular}
+	\label{tab:compair_1}
+	\begin{tabular}{|l|l|*{12}{c|}}
+		\hline
+
+		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithms}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
+		\\ \hline
+		\multirow{6}{*}{\textbf{AF}} 
+		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
+		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
+		& OR                  & N   & Y   & Y   & N   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
+		& Flexible Attributes & N   & Y   & Y   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
+		& Complex Boolean     & N   & N   & N   & N   & Y   & N   & N   & \multicolumn{5}{c|}{} \\ \hline
+
+		\multicolumn{2}{|l|}{\textbf{RF}}             & N & N & N & N & Y & N & N & Y & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Filter Type }}             & C & C & C & C & B & B & B & B & B & B & A/B/C & A \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Dynamic Insert}} & N & Y & N & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Multi Thread}}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Disk Support}}           &N  & Y& N & N & N & N & N & N & N & N & N & N \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Base}}           & Graph & Graph & Graph & IVF & Graph & Graph & IVF & Graph & Graph & Graph & Graph & Graph \\ \hline
+	\end{tabular}
+
+	%		\begin{tabular}{|c|c|c|c|}
+		%			\hline
+		%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
+		%			\hline
+		%			DSG & Graph & Y & N \\
+		%			iRange & Graph & N & Y \\
+		%			SeRF & Graph & Y & Y \\
+		%			UNIFY & Graph & Y & Y \\
+		%			WinFilter & Graph & N & Y  \\
+		%			\hline
+		%		\end{tabular}
+	%
+
+	\centering
+	%	 \setlength{\abovecaptionskip}{0cm}
+	%	\setlength{\belowcaptionskip}{0.1cm}
+	\footnotesize{
+		\begin{minipage}{\linewidth}
+			\vspace{0.1cm}
+			Win: WinFilter, Filtered: FilteredVamana, Stitched: StitchedVamana. 
+			\textsuperscript{A} Post-filtering, 
+			\textsuperscript{B} Pre-filtering, 
+			\textsuperscript{C} Simultaneous filtering, 
+			\textsuperscript{Y} Support, 
+			\textsuperscript{N} Unsupport. 
+			\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
+			\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
+			\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
+			\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+			\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+			\textit{Disk Support} indicates whether the algorithm supports disk storage.
+			\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
+	\end{minipage}}
+
+\end{table*}
 

### 2025-07-29 Revision/response.tex
Update response.tex

@@
 In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios,as shown in Table~\ref{tab:algo_scenarios}.
-\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
 
@@
 
+\textcolor{blue}{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}
+
+\textcolor{blue}{https://github.com/microsoft/DiskANN}
+
+\textcolor{blue}{https://github.com/gaurav16gupta/constrainedANN}
+
+\textcolor{blue}{https://github.com/stanford-futuredata/ACORN}
+
+\textcolor{blue}{https://github.com/YZ-Cai/Unified-Navigating-Graph}
+
+\textcolor{blue}{https://github.com/baidu/puck}
+
+\textcolor{blue}{https://github.com/rutgers-db/SeRF}
+
+\textcolor{blue}{https://github.com/JoshEngels/RangeFilteredANN}
+
+\textcolor{blue}{https://github.com/YuexuanXu7/iRangeGraph}
+
+\textcolor{blue}{https://github.com/rutgers-db/DynamicSegmentGraph}
+
+\textcolor{blue}{https://github.com/sjtu-dbgroup/UNIFY}
+
+\textcolor{blue}{https://github.com/facebookresearch/faiss}
+
+\textcolor{blue}{https://github.com/alipay/PASE}
+
+\textcolor{blue}{https://github.com/microsoft/MSVBASE}
+
+\textcolor{blue}{https://github.com/milvus-io/milvus}
+
 \section*{Response to Review 3}

### 2025-07-29 Revision/response.tex
1

--- 2025-07-29 Revision/response.tex
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have already provided a detailed response to this issue in our reply to Meta-Review R5. Please refer to that response for more information.
+Thank you for your suggestion.
+We clarify in Table 1 which methods support disk-based execution.
+Since only FilteredDiskANN supports disk-based execution, we conduct additional experiments to analyze its performance and report a detailed cost breakdown (I/O vs.
+CPU).
+Figure~\ref{fig:recall-latency} shows that I/O consistently dominates total latency (accounting for 80–85\%) and becomes the primary bottleneck at high recall levels.
+We also compare it with two in-memory baselines—FilteredVamana and StitchedVamana—to highlight their efficiency and trade-offs.
+Due to space constraints and the limited relevance to other methods, we exclude this analysis from the revised paper and provide it here for completeness.
+
+We have already provided a detailed response to this issue in our reply to Meta-Review R5. Please refer to that response for more information.
 

### 2025-07-29 Revision/response.tex
Update response.tex
1

--- 2025-07-29 Revision/response.tex
@@
 
+\begin{figure}[t]
+	\centering
+
+	% 上面的图例，居中并可通过 hspace 调整左右位置
+	\hspace*{8pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
+	\includegraphics[width=0.95\columnwidth]{fig/range_2_2_legend.pdf} % 图例图片路径
+
+	% --- 不再使用 subfigure ---
+	% 直接放置第二张图片，可以加一点垂直间距
+	\vspace{5pt} 
+	\includegraphics[width=0.99\columnwidth]{fig/range_2_2.pdf}
+
+	\caption{Comparison of Real and Synthetic Attributes}
+	\label{fig:range_2_2}
+
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%% R4 %%%%%%%%%%%%%%%%%%%%%%
@@
 To address this issue, we have changed two datasets (YT-Audio-Real, WIT-Real) to use real attributes.
-We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:attribute_distribution}.
+We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:range_2_2}.
 \textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios,as shown in Table~\ref{tab:algo_scenarios}.
-\textbf{(Please refer to the "Recommendation" part of section 5.2.2, highlighted in blue in the revised manuscript.)}
-
-%\subsection{Recommendations.}
-%Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
-
-\begin{table*}[htbp]
-	\caption{Algorithm Recommendation}
-	\label{tab:algo_scenarios}
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{|l|*{16}{c|}}
-			\hline
-			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
-			& \multicolumn{6}{c|}{\textbf{AF}} 
-			& \multicolumn{5}{c|}{\textbf{RF}} 
-			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
-			\cline{2-17}
-			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
-			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
-			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
-			\hline
-			\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
-			\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
-			\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
-			\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
-			\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
-			\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
-			\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
-			\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
-			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
-			\hline
-		\end{tabular}
-	}
-	\vspace{1mm}
-	\begin{flushleft}
-		\textbf{Note:} S = Strong performance, \textbf{S} = Strongest performance, M = Medium performance, W = Weak performance, 
-		\faCheck = Recommended, \faTimes = Not Recommended.
-	\end{flushleft}
-	\centering
-
-\end{table*}
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios.
+\textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We clarify in Table 1 which methods support disk-based execution.
-Since only FilteredDiskANN supports disk-based execution, we conduct additional experiments to analyze its performance and report a detailed cost breakdown (I/O vs.
-CPU).
-Figure~\ref{fig:recall-latency} shows that I/O consistently dominates total latency (accounting for 80–85\%) and becomes the primary bottleneck at high recall levels.
-We also compare it with two in-memory baselines—FilteredVamana and StitchedVamana—to highlight their efficiency and trade-offs.
-Due to space constraints and the limited relevance to other methods, we exclude this analysis from the revised paper and provide it here for completeness.
-
-We have already provided a detailed response to this issue in our reply to Meta-Review R5. Please refer to that response for more information.
+Thank you for your suggestion. We have already provided a detailed response to this issue in our reply to Meta-Review R5. Please refer to that response for more information.
 

### 2025-07-29 VLDB2026/main.tex

@@
 %	\footnote{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}
-	\noindent\textbf{\underline{NHQ} \footnote{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS} \cite{NHQ}}
+	\noindent\textbf{\underline{NHQ} \footnote{\textcolor{blue}{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}} \cite{NHQ}}
 	Traditional attribute filtering algorithms usually perform attribute constraints and ANN search separately.
@@
 
-	\noindent\textbf{\underline{Filtered-DiskANN} \footnote{https://github.com/microsoft/DiskANN} \cite{Filtered-diskann}}
+	\noindent\textbf{\underline{Filtered-DiskANN} \footnote{\textcolor{blue}{https://github.com/microsoft/DiskANN}} \cite{Filtered-diskann}}
 	%\sout{The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.}
@@
 
-	\noindent\textbf{\underline{CAPS} \footnote{https://github.com/gaurav16gupta/constrainedANN} \cite{CAPS}}
+	\noindent\textbf{\underline{CAPS} \footnote{\textcolor{blue}{https://github.com/gaurav16gupta/constrainedANN}} \cite{CAPS}}
 	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
@@
 
-	\noindent\textbf{\underline{ACORN} \footnote{https://github.com/stanford-futuredata/ACORN} \cite{ACORN}}
+	\noindent\textbf{\underline{ACORN} \footnote{\textcolor{blue}{https://github.com/stanford-futuredata/ACORN}} \cite{ACORN}}
 	%	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
@@
 
-	\noindent\textbf{\underline{UNG} \footnote{https://github.com/YZ-Cai/Unified-Navigating-Graph} \cite{UNG}} 
+	\noindent\textbf{\underline{UNG} \footnote{\textcolor{blue}{https://github.com/YZ-Cai/Unified-Navigating-Graph}} \cite{UNG}} 
 	%\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
@@
 
-	\noindent\textbf{\underline{Puck} \footnote{https://github.com/baidu/puck} \cite{puck}} 
+	\noindent\textbf{\underline{Puck} \footnote{\textcolor{blue}{https://github.com/baidu/puck}} \cite{puck}} 
 	%While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
@@
 
-	\noindent\textbf{\underline{SeRF} \footnote{https://github.com/rutgers-db/SeRF} \cite{serf}} Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
+	\noindent\textbf{\underline{SeRF} \footnote{\textcolor{blue}{https://github.com/rutgers-db/SeRF}} \cite{serf}} Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
 2) Filtering the dataset based on attribute ranges before performing ANN search.
@@
 
-	\noindent\textbf{\underline{WinFilter} \footnote{https://github.com/JoshEngels/RangeFilteredANN} \cite{winFilter}}
+	\noindent\textbf{\underline{WinFilter} \footnote{\textcolor{blue}{https://github.com/JoshEngels/RangeFilteredANN}} \cite{winFilter}}
 	Unlike SeRF, which focuses on graph compression, WinFilter proposes a structural partitioning framework called the $\beta$-Window Search Tree ($\beta$-WST).
@@
 
-	\noindent\textbf{\underline{iRange} \footnote{https://github.com/YuexuanXu7/iRangeGraph} \cite{iRangeGraph}}
+	\noindent\textbf{\underline{iRange} \footnote{\textcolor{blue}{https://github.com/YuexuanXu7/iRangeGraph}} \cite{iRangeGraph}}
 	To address the query efficiency degradation caused by the graph compression in SeRF, iRange adopts a more flexible strategy.
@@
 
-	\noindent\textbf{\underline{DSG} \footnote{https://github.com/rutgers-db/DynamicSegmentGraph} \cite{DSG}}
+	\noindent\textbf{\underline{DSG} \footnote{\textcolor{blue}{https://github.com/rutgers-db/DynamicSegmentGraph}} \cite{DSG}}
 	Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets.
@@
 
-	\noindent\textbf{\underline{UNIFY} \footnote{https://github.com/sjtu-dbgroup/UNIFY} \cite{UNIFY}}
+	\noindent\textbf{\underline{UNIFY} \footnote{\textcolor{blue}{https://github.com/sjtu-dbgroup/UNIFY}} \cite{UNIFY}}
 	Unlike DSG, which relies on rectangle trees and range-aware edges, UNIFY adopts a segmentation-based approach and proposes a range query index structure.
@@
 
-	\noindent\textbf{\underline{Faiss} \footnote{https://github.com/facebookresearch/faiss} \cite{Faiss}}
+	\noindent\textbf{\underline{Faiss} \footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
 	Faiss is a library designed for efficient similarity search.
@@
 
-	\noindent\textbf{\underline{PASE} \footnote{https://github.com/alipay/PASE} \cite{pase}}
+	\noindent\textbf{\underline{PASE} \footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase}}
 	PASE is a vector indexing plugin for the PostgreSQL database \cite{postgresql13.4}, supporting two index types: IVF\_Flat \cite{johnson2019billion} and HNSW.
@@
 
-	\noindent\textbf{\underline{VBASE} \footnote{https://github.com/microsoft/MSVBASE} \cite{vbase}}
+	\noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}}
 	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
@@
 
-	\noindent\textbf{\underline{Milvus} \footnote{https://github.com/milvus-io/milvus} \cite{milvus}}
+	\noindent\textbf{\underline{Milvus} \footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus}}
 	Unlike PASE and VBASE, which are database extensions, Milvus is an vector database purpose-built for large-scale similarity search.

### 2025-07-29 Revision/response.tex

--- 2025-07-29 Revision/response.tex
@@
 Instead, in Section 3, we added superscript markers next to each algorithm name and provided the corresponding implementation URLs as footnotes on the same page.
-\textbf{(Please see the relevant footnotes in Section 3 in the revised manuscript.)}
+\textbf{(Please see Section 3, highlighted in blue in the revised manuscript.)}
 

### 2025-07-29 Revision/response.tex
1

--- 2025-07-29 Revision/response.tex
@@
 \begin{flushleft}
-		\textbf{Note:} S = Strong performance, \textbf{S} = Strongest performance, M = Medium performance, W = Weak performance, 
-		\faCheck = Recommended, \faTimes = Not Recommended.
+	\textbf{Performance Levels:} \quad \textbf{S} = Strongest, S = Strong, M = Medium, W = Weak, - = Not Supported \\
+	\textbf{Recommendation:} \quad \faCheck = Recommended, \faTimes = Not Recommended
 \end{flushleft}
+
 	\centering
@@
 Thank you for your suggestion.
-We clarify in Table 1 which methods support disk-based execution.
+We clarify in Table ~\ref{tab:compair_1} which methods support disk-based execution.
 Since only FilteredDiskANN supports disk-based execution, we conduct additional experiments to analyze its performance and report a detailed cost breakdown (I/O vs.
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have made a detailed response to this issue in our reply to Meta-Review R6. Please refer to that response for more information.
+Thank you for your suggestion.
+We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+
+We have made a detailed response to this issue in our reply to Meta-Review R6. Please refer to that response for more information.
 

### 2025-07-29 Revision/response.tex
change title
Update response.tex

@@
 \textbf{Response:} 
-Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response MR.R4 for more details.
+Thank you for your suggestion.
+We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4.
+The results show that differences in server configurations have little impact on the ranking of the methods.
+ Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-\textcolor{blue}{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}
-
-\textcolor{blue}{https://github.com/microsoft/DiskANN}
-
-\textcolor{blue}{https://github.com/gaurav16gupta/constrainedANN}
-
-\textcolor{blue}{https://github.com/stanford-futuredata/ACORN}
-
-\textcolor{blue}{https://github.com/YZ-Cai/Unified-Navigating-Graph}
-
-\textcolor{blue}{https://github.com/baidu/puck}
-
-\textcolor{blue}{https://github.com/rutgers-db/SeRF}
-
-\textcolor{blue}{https://github.com/JoshEngels/RangeFilteredANN}
-
-\textcolor{blue}{https://github.com/YuexuanXu7/iRangeGraph}
-
-\textcolor{blue}{https://github.com/rutgers-db/DynamicSegmentGraph}
-
-\textcolor{blue}{https://github.com/sjtu-dbgroup/UNIFY}
-
-\textcolor{blue}{https://github.com/facebookresearch/faiss}
-
-\textcolor{blue}{https://github.com/alipay/PASE}
-
-\textcolor{blue}{https://github.com/microsoft/MSVBASE}
-
-\textcolor{blue}{https://github.com/milvus-io/milvus}
+\textcolor{blue}{"https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS"}
+
+\textcolor{blue}{"https://github.com/microsoft/DiskANN"}
+
+\textcolor{blue}{"https://github.com/gaurav16gupta/constrainedANN"}
+
+\textcolor{blue}{"https://github.com/stanford-futuredata/ACORN"}
+
+\textcolor{blue}{"https://github.com/YZ-Cai/Unified-Navigating-Graph"}
+
+\textcolor{blue}{"https://github.com/baidu/puck"}
+
+\textcolor{blue}{"https://github.com/rutgers-db/SeRF"}
+
+\textcolor{blue}{"https://github.com/JoshEngels/RangeFilteredANN"}
+
+\textcolor{blue}{"https://github.com/YuexuanXu7/iRangeGraph"}
+
+\textcolor{blue}{"https://github.com/rutgers-db/DynamicSegmentGraph"}
+
+\textcolor{blue}{"https://github.com/sjtu-dbgroup/UNIFY"}
+
+\textcolor{blue}{"https://github.com/facebookresearch/faiss"}
+
+\textcolor{blue}{"https://github.com/alipay/PASE"}
+
+\textcolor{blue}{"https://github.com/microsoft/MSVBASE"}
+
+\textcolor{blue}{"https://github.com/milvus-io/milvus"}
 
@@
 
-	\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN Search Algorithms}}
+	\caption{Comparison of AF-ANN and RF-ANN Search Algorithms}
 	\small

### 2025-07-29 Revision/response.tex
Update response.tex
1

@@
 	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
-	\caption{Effect of attribute distribution on query performance}
+	\caption{Effect of Attribute Distribution on Query Performance}
 	\label{fig:attribute_distribution}
@@
 	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
-	\caption{Different AS under the same algorithm}
+	\caption{Different AS under the Same Algorithm}
 	\label{fig:attribute_selectivity}
@@
 Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have changed two datasets (YT-Audio-Real, WIT-Real) to use real attributes.
+To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.
 We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:range_2_2}.

### 2025-07-29 Revision/response.tex
Update response.tex

--- 2025-07-29 Revision/response.tex
@@
 \textbf{Response:} 
-Thank you for your feedback. We improve the readability of the two figures in Section 4.2.3, and please see Meta-Review R1 for details.
+Thank you for your feedback. We improve the readability of the two figures in Section 4.2.3, and please see Meta R1 for details.
 
@@
 Thank you for your suggestion.
-We have addressed this issue in detail in our response to Meta-Review R2.
+We have addressed this issue in detail in our response to Meta R2.
 Specifically, we added complex multimodal query experiments and provided an in-depth analysis of the results.
-For more details, please refer to our response to Meta-Review R2.
+For more details, please refer to our response to Meta R2.
 %We think this is an excellent suggestion.
@@
 To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments.
-For detailed information on these two new datasets and our improvements to range filtering, please see Meta-Review R3.
+For detailed information on these two new datasets and our improvements to range filtering, please see Meta R3.
 
@@
 The results show that differences in server configurations have little impact on the ranking of the methods.
- Please refer to the response MR.R4 for more details.
+ Please refer to the response Meta R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-We have already provided a detailed response to this issue in our reply to Meta-Review R5. Please refer to that response for more information.
+We have already provided a detailed response to this issue in our reply to Meta R5. Please refer to that response for more information.
 
@@
 
-We have made a detailed response to this issue in our reply to Meta-Review R6. Please refer to that response for more information.
+We have made a detailed response to this issue in our reply to Meta R6. Please refer to that response for more information.
 
@@
 We have added experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observed some pitfalls.
-For more details, please refer to our response to Meta-Review R7.
+For more details, please refer to our response to Meta R7.
 
@@
 Thank you for your suggestion.
-We have already addressed this issue in detail in our responses to Meta-Review R8 and R9.
+We have already addressed this issue in detail in our responses to Meta R8 and R9.
 Specifically, we analyzed the strengths and weaknesses of each algorithm and recommended those with strong performance.
 Additionally, we provided a summary table illustrating how each algorithm performs across different application scenarios.
-For more details, please refer to our responses to Meta-Review R8 and R9.
+For more details, please refer to our responses to Meta R8 and R9.
 
@@
 
-We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to the response to Meta-Review R7.
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to the response to Meta R7.
 

### 2025-07-29 Revision/response.tex
Update response.tex

--- 2025-07-29 Revision/response.tex
@@
 	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
-	\caption{Effect of Attribute Distribution on Query Performance}
+	\caption{Effect of attribute distribution on query performance}
 	\label{fig:attribute_distribution}
@@
 	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
-	\caption{Different AS under the Same Algorithm}
+	\caption{Different AS under the same algorithm}
 	\label{fig:attribute_selectivity}
@@
 Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.
+To address this issue, we have changed two datasets (YT-Audio-Real, WIT-Real) to use real attributes.
 We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:range_2_2}.
@@
 \textbf{Response:} 
-Thank you for your suggestion. We fully understand your concern regarding the use of synthetic or less meaningful attributes in our hybrid query experimental setup.
-
-To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments.
-For detailed information on these two new datasets and our improvements to range filtering, please see Meta-Review R3.
-
-We have revised the manuscript accordingly.
-%\textbf{ (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.)} 
-Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
-\textbf{(Please see Section 4.2.1 and the "Single-Attribute Building and Single-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.)}
+Thank you for your suggestion. We fully understand your concern regarding our use of synthetic or less meaningful attributes in the hybrid query experimental setup.
+
+To address this critical issue and enhance the real-world relevance of our evaluation, we have incorporated two new real-world datasets with their actual attributes into our attribute filtering and range query experiments, and we have clarified the sources of these real-world attributes.
+For more details, please refer to our Response to Meta R3.
+
+For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Building and Single-Attribute Query" experiments and amended the manuscript accordingly.
+It is also worth noting that in Section 4.2.2, under the "Single-Attribute Building and Single-Attribute Query" subsection, we have removed two previous datasets (Audio and GloVe) due to space constraints.
+The Audio dataset was removed because its smaller scale offered limited reference value.
+The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M.
+\textbf{(Please see Section 4.2.1 on page 7, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2 on page 8).}
+
+In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the algorithm's performance.
+For more details, please refer to our Response to Review 1 W1.
+
+For range filtering, we have also included the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes in our experiments.
+For more details, please refer to our response to Meta R3.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4.
-The results show that differences in server configurations have little impact on the ranking of the methods.
- Please refer to the response MR.R4 for more details.
+Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response MR.R4 for more details.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-\textcolor{blue}{"https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS"}
-
-\textcolor{blue}{"https://github.com/microsoft/DiskANN"}
-
-\textcolor{blue}{"https://github.com/gaurav16gupta/constrainedANN"}
-
-\textcolor{blue}{"https://github.com/stanford-futuredata/ACORN"}
-
-\textcolor{blue}{"https://github.com/YZ-Cai/Unified-Navigating-Graph"}
-
-\textcolor{blue}{"https://github.com/baidu/puck"}
-
-\textcolor{blue}{"https://github.com/rutgers-db/SeRF"}
-
-\textcolor{blue}{"https://github.com/JoshEngels/RangeFilteredANN"}
-
-\textcolor{blue}{"https://github.com/YuexuanXu7/iRangeGraph"}
-
-\textcolor{blue}{"https://github.com/rutgers-db/DynamicSegmentGraph"}
-
-\textcolor{blue}{"https://github.com/sjtu-dbgroup/UNIFY"}
-
-\textcolor{blue}{"https://github.com/facebookresearch/faiss"}
-
-\textcolor{blue}{"https://github.com/alipay/PASE"}
-
-\textcolor{blue}{"https://github.com/microsoft/MSVBASE"}
-
-\textcolor{blue}{"https://github.com/milvus-io/milvus"}
+\textcolor{blue}{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}
+
+\textcolor{blue}{https://github.com/microsoft/DiskANN}
+
+\textcolor{blue}{https://github.com/gaurav16gupta/constrainedANN}
+
+\textcolor{blue}{https://github.com/stanford-futuredata/ACORN}
+
+\textcolor{blue}{https://github.com/YZ-Cai/Unified-Navigating-Graph}
+
+\textcolor{blue}{https://github.com/baidu/puck}
+
+\textcolor{blue}{https://github.com/rutgers-db/SeRF}
+
+\textcolor{blue}{https://github.com/JoshEngels/RangeFilteredANN}
+
+\textcolor{blue}{https://github.com/YuexuanXu7/iRangeGraph}
+
+\textcolor{blue}{https://github.com/rutgers-db/DynamicSegmentGraph}
+
+\textcolor{blue}{https://github.com/sjtu-dbgroup/UNIFY}
+
+\textcolor{blue}{https://github.com/facebookresearch/faiss}
+
+\textcolor{blue}{https://github.com/alipay/PASE}
+
+\textcolor{blue}{https://github.com/microsoft/MSVBASE}
+
+\textcolor{blue}{https://github.com/milvus-io/milvus}
 
@@
 
-	\caption{Comparison of AF-ANN and RF-ANN Search Algorithms}
+	\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN Search Algorithms}}
 	\small

### 2025-07-29 Revision/response.tex
change W to O

@@
 	\noindent\textbf{R\themetarevision.#1} }{\medskip}
+
+\newcounter{observation}[section]
+\setcounter{observation}{0}
+\renewcommand{\theobservation}{\arabic{observation}}
+\newenvironment{observation}[1][]{\refstepcounter{observation}\par\medskip
+	\noindent\textbf{O\theobservation.#1} }{\medskip}
 
@@
 \myfbox{
-	\begin{weakness}
+	\begin{observation}
 		\textit{In the experimental study, datasets did not originate from the real applications for hybrid queries.
@@
 		}
-	\end{weakness}
-}
-
-\noindent
-\textbf{Response:} 
-Thank you for your suggestion. We fully understand your concern regarding our use of synthetic or less meaningful attributes in the hybrid query experimental setup.
-
-To address this critical issue and enhance the real-world relevance of our evaluation, we have incorporated two new real-world datasets with their actual attributes into our attribute filtering and range query experiments, and we have clarified the sources of these real-world attributes.
-For more details, please refer to our Response to Meta R3.
-
-For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Building and Single-Attribute Query" experiments and amended the manuscript accordingly.
-It is also worth noting that in Section 4.2.2, under the "Single-Attribute Building and Single-Attribute Query" subsection, we have removed two previous datasets (Audio and GloVe) due to space constraints.
-The Audio dataset was removed because its smaller scale offered limited reference value.
-The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M.
-\textbf{(Please see Section 4.2.1 on page 7, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2 on page 8).}
-
-In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the algorithm's performance.
-For more details, please refer to our Response to Review 1 W1.
-
-For range filtering, we have also included the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes in our experiments.
-For more details, please refer to our response to Meta R3.
+	\end{observation}
+}
+
+\noindent
+\textbf{Response:} 
+Thank you for your suggestion. We fully understand your concern regarding the use of synthetic or less meaningful attributes in our hybrid query experimental setup.
+
+To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments.
+For detailed information on these two new datasets and our improvements to range filtering, please see Meta-Review R3.
+
+We have revised the manuscript accordingly.
+%\textbf{ (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.)} 
+Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
+\textbf{(Please see Section 4.2.1 and the "Single-Attribute Building and Single-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.)}
 
@@
 \myfbox{
-	\begin{weakness}
+	\begin{observation}
 		\textit{All experiments were conducted on the same server mentioned in Section 4.1.3.
@@
 			Would the CPU cache size affect the top 3 methods in those figures?}
-	\end{weakness}
+	\end{observation}
 }
@@
 \myfbox{
-	\begin{weakness}
+	\begin{observation}
 		\textit{In the experimental setup, it is unclear whether data storage (disk or SSD) is used.
@@
 			For disk-based methods, it is also meaningful to report the cost breakdown (e.g., in terms of I/O time and CPU time).}
-	\end{weakness}
+	\end{observation}
 }
@@
 \myfbox{
-	\begin{weakness}
+	\begin{observation}
 		\textit{The authors have reported the peak memory usage of index construction only.
 			They are also recommended to report the peak memory usage of query processing.}
-	\end{weakness}
+	\end{observation}
 }

### 2025-07-29 VLDB2026/main.tex

@@
 }.
-\textcolor{orange}{As shown in the Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size generated by the algorithm and the dataset size.
-This trend holds consistently across different datasets.
-However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the index size itself.
-}
-
-\textcolor{orange}{For large-scale datasets, algorithms with high build peak memory usage typically produce large index size.
-However, NHQ is an exception.
-During the construction phase, NHQ generates a large number of candidate neighbors, but only retains a small subset for each point in the final index.
-This leads to peak memory usage that is significantly higher than the eventual index size.}
+\textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
+Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.
+However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size.}
+
+\textcolor{orange}{
+In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
+This leads to high peak memory usage during construction, despite the relatively small size of the final index.}
 
@@
 \begin{flushleft}
-	\textbf{Note:} S = Strong performance, \textbf{S} = Strongest performance, M = Medium performance, W = Weak performance, 
-	\faCheck = Recommended, \faTimes = Not Recommended.
+	\textbf{Performance Levels:} \quad \textbf{S} = Strongest, S = Strong, M = Medium, W = Weak, - = Not Supported \\
+	\textbf{Recommendation:} \quad \faCheck = Recommended, \faTimes = Not Recommended
 \end{flushleft}

### 2025-07-29 Revision/response.tex

--- 2025-07-29 Revision/response.tex
@@
 \textbf{Response:} 
-Thank you for your suggestion. We fully understand your concern regarding the use of synthetic or less meaningful attributes in our hybrid query experimental setup.
-
-To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments.
-For detailed information on these two new datasets and our improvements to range filtering, please see Meta R3.
-
-We have revised the manuscript accordingly.
-%\textbf{ (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.)} 
-Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
-\textbf{(Please see Section 4.2.1 and the "Single-Attribute Building and Single-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.)}
+Thank you for your suggestion. We fully understand your concern regarding our use of synthetic or less meaningful attributes in the hybrid query experimental setup.
+
+To address this critical issue and enhance the real-world relevance of our evaluation, we have incorporated two new real-world datasets with their actual attributes into our attribute filtering and range query experiments, and we have clarified the sources of these real-world attributes.
+For more details, please refer to our Response to Meta R3.
+
+For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Building and Single-Attribute Query" experiments and amended the manuscript accordingly.
+It is also worth noting that in Section 4.2.2, under the "Single-Attribute Building and Single-Attribute Query" subsection, we have removed two previous datasets (Audio and GloVe) due to space constraints.
+The Audio dataset was removed because its smaller scale offered limited reference value.
+The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M.
+\textbf{(Please see Section 4.2.1 on page 7, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2 on page 8).}
+
+In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the algorithm's performance.
+For more details, please refer to our Response to Review 1 W1.
+
+For range filtering, we have also included the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes in our experiments.
+For more details, please refer to our response to Meta R3.
 

### 2025-07-29 Revision/response.tex
Update response.tex

@@
 
-General:	\textcolor{blue}{"All of the following methods support both attribute filtering and range filtering.}
+Senction 5.1.3:	\textcolor{blue}{"All of the following methods support both attribute filtering and range filtering.}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We fully understand your concern regarding our use of synthetic or less meaningful attributes in the hybrid query experimental setup.
-
-To address this critical issue and enhance the real-world relevance of our evaluation, we have incorporated two new real-world datasets with their actual attributes into our attribute filtering and range query experiments, and we have clarified the sources of these real-world attributes.
-For more details, please refer to our Response to Meta R3.
-
-For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Building and Single-Attribute Query" experiments and amended the manuscript accordingly.
-It is also worth noting that in Section 4.2.2, under the "Single-Attribute Building and Single-Attribute Query" subsection, we have removed two previous datasets (Audio and GloVe) due to space constraints.
-The Audio dataset was removed because its smaller scale offered limited reference value.
-The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M.
-\textbf{(Please see Section 4.2.1 on page 7, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2 on page 8).}
-
-In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the algorithm's performance.
-For more details, please refer to our Response to Review 1 W1.
-
-For range filtering, we have also included the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes in our experiments.
-For more details, please refer to our response to Meta R3.
+Thank you for your suggestion. We fully understand your concern regarding the use of synthetic or less meaningful attributes in our hybrid query experimental setup.
+
+To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments.
+For detailed information on these two new datasets and our improvements to range filtering, please see Meta R3.
+
+We have revised the manuscript accordingly.
+%\textbf{ (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.)} 
+Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.
+\textbf{(Please see Section 4.2.1 and the "Single-Attribute Building and Single-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.)}
 

### 2025-07-29 Revision/response.tex
1

@@
 	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
-	\caption{}
+	\caption{Performance Comparison of SSD-Based and In-Memory Execution of FilteredDiskANN}
 	\label{fig:recall-latency}
@@
 
-Senction 5.1.3:	\textcolor{blue}{"All of the following methods support both attribute filtering and range filtering.}
+General:	\textcolor{blue}{"All of the following methods support both attribute filtering and range filtering.}
 

### 2025-07-29 Revision/response.tex

--- 2025-07-29 Revision/response.tex
@@
 		}
-	\end{weakness}
+	\end{observation}
 }

### 2025-07-29 Revision/response.tex
Update response.tex
1

@@
 	\includegraphics[width=\linewidth]{fig/searchMem/label_memory_comparison.pdf}
-	\caption{attribute filtering search peak memory}
+	\caption{Attribute filtering search peak memory}
 	\label{fig:search_memory_mb_comparison}
@@
 
-To address this critical issue and enhance the real-world relevance of our evaluation, we have incorporated two new real-world datasets with their actual attributes into our attribute filtering and range query experiments, and we have clarified the sources of these real-world attributes.
+To address this critical issue and enhance the real-world relevance of our evaluation, we have incorporated two new real-world datasets with their actual attributes into our attribute filtering and range filtering experiments, and we have clarified the sources of these real-world attributes.
 For more details, please refer to our Response to Meta R3.
@@
 To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature.
+\textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 

### 2025-07-29 Revision/response.tex
Update response.tex
update diskann fig

--- 2025-07-29 Revision/response.tex
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
-	\caption{Performance Comparison of SSD-Based and In-Memory Execution of FilteredDiskANN}
+	\includegraphics[width=\linewidth]{fig/recall_latency_all.pdf}
+	\caption{}
 	\label{fig:recall-latency}

### 2025-07-29 Revision/response.tex
Update response.tex

--- 2025-07-29 Revision/response.tex
@@
 
+\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
+
 For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure.
@@
 \end{figure}
-
-\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
 
@@
 \textbf{Response:} 
-Thank you for your feedback. We improve the readability of the two figures in Section 4.2.3, and please see Meta R1 for details.
+Thank you for your feedback. We have improved the readability of the two figures in Section 4.2.3, and please see Meta R1 for details.
 
@@
 We realized that the original wording is somewhat vague and led to confusion among readers.
-To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table,as shown in Table~\ref{tab:compair_1}.
+To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table, as shown in Table~\ref{tab:compair_1}.
 

### 2025-07-29 Revision/response.tex
Update response.tex

--- 2025-07-29 Revision/response.tex
@@
 	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
-	\caption{Effect of Attribute Distribution on Query Performance}
+	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
 	\label{fig:attribute_distribution}
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/recall_latency_all.pdf}
+	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
 	\caption{}

### 2025-07-29 Revision/response.tex

--- 2025-07-29 Revision/response.tex
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
+	\includegraphics[width=\linewidth]{fig/recall_latency_all.pdf}
 	\caption{Performance Comparison of SSD-Based and In-Memory Execution of FilteredDiskANN}

### 2025-07-29 VLDB2026/main.tex

@@
 	\textit{\textbf{Build peak memory.}}  
-	\textcolor{orange}{As explained in the attribute filtering analysis, the build peak memory usage typically depends on the combined size of the dataset and the index.
-In general, algorithms with larger index sizes (including the dataset) tend to exhibit higher build peak memory consumption.
+	\textcolor{orange}{As explained in the attribute filtering analysis, algorithms with larger index sizes (including the dataset) tend to exhibit higher build peak memory consumption.
 As shown in Figure~\ref{fig:rangeFilter_build_memory_mb}, range filtering also adheres to this pattern, while PASE deviates due to reasons discussed earlier.}

### 2025-07-29 Revision/response.tex
1

@@
 To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table, as shown in Table~\ref{tab:compair_1}.
+For the examples you mentioned—FilteredVamana and StitchedVamana—their original implementations do not support range filtering.
+Therefore, we mark "N" in the RF (Range Filtering) column of the table.
+You can refer to the table to see whether each algorithm supports attribute filtering (AF) and range filtering (RF).
 

### 2025-07-29 Revision/response.tex
1

@@
 To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.
-We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:range_2_2}.
+We observe that the impact of using real attribute versus using ID on the algorithms is negligible.
+The key factor remains the size of the query range, as shown in Figure~\ref{fig:range_2_2}.
 \textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}

### 2025-07-29 Revision/response.tex
change res

--- 2025-07-29 Revision/response.tex
@@
 
-To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2. \textbf{(Please see Section 4.3, highlighted in blue in the revised manuscript.)}
-
-In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
+To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3. \textbf{(Please see Section 4.3, highlighted in blue in the revised manuscript.)}
+
+\textcolor{blue}{"Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
+The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones.
+"}
+
+In response to the large difference in index construction time shown in Figure 12a(now 13a), we have revised the paper based on your suggestion.
 We added more detailed and in-depth analysis to provide a clearer explanation.
@@
 
-Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c is very insightful.
+	\textcolor{blue}{
+	"ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
+This efficiency stems from its construction process, which closely resembles that of the original HNSW, and from reducing the number of candidate neighbors in the upper layers, thereby lowering computational cost.
+SeRF, another HNSW-based method, also exhibits very short construction time.
+During construction, it attaches timestamp information to edges, keeping the total time comparable to building a single HNSW graph, which enables efficient construction even on large datasets.}
+
+\textcolor{blue}{
+	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
+This design introduces redundant computation and high construction cost.
+However, on large-scale datasets, the preprocessing phase of WinFilter was replaced with a base algorithm in the experiments, thus avoiding significant time overhead.}
+
+\textcolor{blue}{
+	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
+Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
+
+%	The reason for the high construction time of ACORN-$\gamma$ has been explained in the attribute filtering section and is therefore omitted here.
+
+\textcolor{blue}{
+	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
+This makes the construction process more complex and costly.
+In addition, on Deep100M, DSG uses single-threaded construction, resulting in the longest build time."}
+
+Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c(now 13c) is very insightful.
 Initially, we hesitated to include the peak memory usage of databases (such as Milvus) because they are full systems that run continuously and contain many components.

### 2025-07-29 Revision/response.tex
Update response.tex

--- 2025-07-29 Revision/response.tex
@@
 	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
-	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
+	\caption{Effect of Attribute Distribution on Query Performance}
 	\label{fig:attribute_distribution}
@@
 To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.
-We observe that the impact of using real attribute versus using ID on the algorithms is negligible.
-The key factor remains the size of the query range, as shown in Figure~\ref{fig:range_2_2}.
+We observe that the impact of using real attribute versus using ID on the algorithms is negligible; the key factor remains the size of the query range, as shown in Figure~\ref{fig:range_2_2}.
 \textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}
@@
 The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M.
-\textbf{(Please see Section 4.2.1 on page 7, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2 on page 8).}
+\textbf{(Please see Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
 
@@
 To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table, as shown in Table~\ref{tab:compair_1}.
-For the examples you mentioned—FilteredVamana and StitchedVamana—their original implementations do not support range filtering.
-Therefore, we mark "N" in the RF (Range Filtering) column of the table.
-You can refer to the table to see whether each algorithm supports attribute filtering (AF) and range filtering (RF).
 

### 2025-07-29 VLDB2026/main.tex

@@
 	Nevertheless, as application scenarios grow increasingly complex, simple ANN search can no longer satisfy all practical needs.
-For instance, Fig.~\ref{fig:hybrid ANNS} illustrates a case where users on e-commerce platforms search for clothing items by retrieving visually similar products based on an image.
+For instance, Figure~\ref{fig:hybrid ANNS} illustrates a case where users on e-commerce platforms search for clothing items by retrieving visually similar products based on an image.
 Additionally, users may impose further requirements such as price, color, or brand preferences.
@@
 	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
-	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+	\textcolor{violet}{As shown in the Figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.

### 2025-07-29 VLDB2026/main.tex
Update main.tex

--- 2025-07-29 VLDB2026/main.tex
@@
 
-	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache .  
+	We conduct most experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache.  
 %	\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.

### 2025-07-29 VLDB2026/main.tex
1
Update main.tex

@@
 Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.

### 2025-07-29 Revision/response.tex
Update response.tex

--- 2025-07-29 Revision/response.tex
@@
 That is a great suggestion.
-In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
+In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
@@
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
-\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
+\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M.
-\textbf{(Please see Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
+\textbf{(Please see Section 4.2.1 on page 7, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2 on page 8).}
 

### 2025-07-29 VLDB2026/main.tex
1

@@
 
-	We conduct most experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache.  
+	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache .  
 %	\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.
@@
 Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
+	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 	Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
-Filtered-DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
+FilteredDiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
 Moreover, the index construction phase of graph-based algorithms is computationally intensive.
@@
 
-	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions.
-For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
+	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. }
+%	For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
 Furthermore, NHQ only supports multi-attribute filtering with conjunctions ("AND" conditions).
 UNG is relatively more flexible in this regard, as it supports both "AND" and "OR" logic; however, it still cannot handle more complex Boolean expressions involving combinations of conjunctions and disjunctions.
-	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
+%	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
 However, it currently supports only single-attribute filtering and disjunctions ("OR" conditions) across multiple attributes.
 Enhancing its capability to support more flexible Boolean combinations would effectively overcome the limitations of current approaches and significantly improve its practicality for diverse and complex query requirements.
+%		}
+		\textcolor{orange}{
+For example, in multi-attribute scenarios, some algorithms only support Boolean OR logic (e.g., FilterDiskANN), while others only support Boolean AND logic (e.g., NHQ and CAPS).
+Although algorithms such as ACORN, UNG, and Puck support both AND and OR logic across multiple attributes, they still struggle to handle complex Boolean expressions that involve nested combinations of conjunctions (AND) and disjunctions (OR).
+In contrast, while databases and vector search libraries support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
+Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed.
 		}

### 2025-07-29 VLDB2026/main.tex
1

@@
 Although algorithms such as ACORN, UNG, and Puck support both AND and OR logic across multiple attributes, they still struggle to handle complex Boolean expressions that involve nested combinations of conjunctions (AND) and disjunctions (OR).
-In contrast, while databases and vector search libraries support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
+In contrast, while databases and the vector search library Faiss support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
 Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed.

### 2025-07-29 VLDB2026/main.tex
Update main.tex

--- 2025-07-29 VLDB2026/main.tex
@@
 
-	\begin{figure*}
-		\centering
-		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
-		\caption{Effect of Different Datasets on AF-ANN Search}
-		\label{fig:exp_6_1}
-	\end{figure*}
+%	\begin{figure*}
+%		\centering
+%		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
+%		\caption{Effect of Different Datasets on AF-ANN Search}
+%		\label{fig:exp_6_1}
+%	\end{figure*}
 
@@
 
-	\textit{\textbf{Different Datasets.}}  
-	\sout{To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.
+	%\textit{\textbf{Different Datasets.}}  
+	%\sout{To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.
 Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.
@@
 %ykw: 这段话看着有问题
-	As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.
+	%As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.
 Because Audio has small scale, low dimensionality, and low LID.
@@
 
-	SIFT1M and Msong are similar datasets, with the key difference being that SIFT1M has lower dimensionality.
+	%SIFT1M and Msong are similar datasets, with the key difference being that SIFT1M has lower dimensionality.
 The 4 algorithms (ACORN, Faiss, PASE, and NHQ) perform similarly on these two datasets, suggesting strong robustness to high dimensional datasets.
@@
 
-	Most algorithms struggle to achieve high recall on GloVe, because it has the highest LID.
+	%Most algorithms struggle to achieve high recall on GloVe, because it has the highest LID.
 Compare to other algorithms, the 4 algorithms (UNG, Faiss, CAPS, and Milvus) manage to maintain relatively high recall, demonstrating better adaptability to complex datasets.
@@
 
-	\textcolor{green}{Most algorithms exhibit the worst performance on the OOD dataset Text2Image.
+	%\textcolor{green}{Most algorithms exhibit the worst performance on the OOD dataset Text2Image.
 However, ACORN, UNG, and FilteredVamana show relatively stable performance on Text2Image.
@@
 
-	\subsubsection{Robustness.}
-
-	\begin{figure*}[htbp]
-		\centering
-		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
-		\caption{Effect of Different Datasets on RF-ANN Search}
-		\label{fig:exp_8_3}
-	\end{figure*}
-
-	\textcolor{green}{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
+	%\subsubsection{Robustness.}
+
+	%\begin{figure*}[htbp]
+	%	\centering
+	%	\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
+	%	\caption{Effect of Different Datasets on RF-ANN Search}
+	%	\label{fig:exp_8_3}
+	%\end{figure*}
+
+%	\textcolor{green}{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
 As shown in Figure~\ref{fig:exp_8_3}, most methods perform worst on the Text2Image dataset.
@@
 
-	\sout{WinFilter shows the worst performance on the WIT dataset.
+%	\sout{WinFilter shows the worst performance on the WIT dataset.
 This suggests that its performance is sensitive to the data dimensionality.
@@
 
-	Among vector databases, Milvus performs well.
+%	Among vector databases, Milvus performs well.
 VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image.
@@
 
-	It is worth noting that most methods achieve similar performance on the Deep and YT-Audio datasets, which have similar LID values.
+%	It is worth noting that most methods achieve similar performance on the Deep and YT-Audio datasets, which have similar LID values.
 This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
@@
 
-	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them.
+%	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them.
 This means that DSG is more sensitive to changes in data distribution.
@@
 	Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
-FilteredDiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
+Filtered-DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
 Moreover, the index construction phase of graph-based algorithms is computationally intensive.
@@
 
-	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. }
-%	For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
+	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions.
+For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
 Furthermore, NHQ only supports multi-attribute filtering with conjunctions ("AND" conditions).
 UNG is relatively more flexible in this regard, as it supports both "AND" and "OR" logic; however, it still cannot handle more complex Boolean expressions involving combinations of conjunctions and disjunctions.
-%	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
+	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
 However, it currently supports only single-attribute filtering and disjunctions ("OR" conditions) across multiple attributes.
 Enhancing its capability to support more flexible Boolean combinations would effectively overcome the limitations of current approaches and significantly improve its practicality for diverse and complex query requirements.
-%		}
-		\textcolor{orange}{
-For example, in multi-attribute scenarios, some algorithms only support Boolean OR logic (e.g., FilterDiskANN), while others only support Boolean AND logic (e.g., NHQ and CAPS).
-Although algorithms such as ACORN, UNG, and Puck support both AND and OR logic across multiple attributes, they still struggle to handle complex Boolean expressions that involve nested combinations of conjunctions (AND) and disjunctions (OR).
-In contrast, while databases and vector search libraries support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
-Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed.
 		}

### 2025-07-29 VLDB2026/main.tex

@@
 
-	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions.
-For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
+	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. }
+%	For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
 Furthermore, NHQ only supports multi-attribute filtering with conjunctions ("AND" conditions).
 UNG is relatively more flexible in this regard, as it supports both "AND" and "OR" logic; however, it still cannot handle more complex Boolean expressions involving combinations of conjunctions and disjunctions.
-	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
+%	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
 However, it currently supports only single-attribute filtering and disjunctions ("OR" conditions) across multiple attributes.
 Enhancing its capability to support more flexible Boolean combinations would effectively overcome the limitations of current approaches and significantly improve its practicality for diverse and complex query requirements.
+%		}
+		\textcolor{orange}{
+For example, in multi-attribute scenarios, some algorithms only support Boolean OR logic (e.g., FilterDiskANN), while others only support Boolean AND logic (e.g., NHQ and CAPS).
+Although algorithms such as ACORN, UNG, and Puck support both AND and OR logic across multiple attributes, they still struggle to handle complex Boolean expressions that involve nested combinations of conjunctions (AND) and disjunctions (OR).
+In contrast, while databases and the vector search library Faiss support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
+Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed.
 		}

### 2025-07-29 VLDB2026/main.tex

@@
 	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-\textcolor{orange}{Although existing works, such as the surveys in \cite{compare,azizi2025graph}, conduct benchmark evaluations or experimental analyses of ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+\textcolor{orange}{Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
-Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.}
+Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
 
@@
 These efforts offer a unified reference framework for future research.
-	\textcolor{orange}{We systematically categorize 6 representative attribute filtering algorithms and 5 range filtering algorithms from the perspectives of index organization, filtering strategies, disk support, and complex attribute handling.
+	\textcolor{orange}{We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives.
 We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles.

### 2025-07-29 VLDB2026/main.tex
Update main.tex

@@
 
-	\textcolor{violet}{The first seven datasets are widely used in existing literature.
+	\textcolor{violet}{The first seven datasets are widely used in existing works.
 As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.}
 
-	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
+	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes.
+For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}

### 2025-07-30 Revision/response.tex
1

@@
 For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution.
-For attribute selectivity: For example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
+For attribute selectivity: for example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we have added more comprehensive references in the paper.
+For the two parts you suggested, we have replaced them in the paper with more comprehensive and accurate references.
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[12], and attribute  selectivity [46,51] significantly impact algorithm performance."}
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[13], and attribute  selectivity [47,52] significantly impact algorithm performance."}
+
+[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627.
+
+[52]Chuangxian Wei, Bin Wu, Sheng Wang, Renjie Lou, Chaoqun Zhan, Feifei Liand Yuanzhe Cai.
+2020.AnalyticDB-V: A Hybrid Analytical Engine TowardsOuery Fusion for Structured and Unstructured Data.
+Proc.
+VLDB Endow.
+13, 12(2020),3152-3165.
 

### 2025-07-30 VLDB2026/main.tex
delete

@@
 
-	\sout{It is important to note that this range query experiment is conducted under a fully static setting.
+%	\sout{It is important to note that this range query experiment is conducted under a fully static setting.
 Under such conditions, UNIFY, iRange, SeRF, and WinFilter require the dataset to be sorted by attribute prior to index construction.

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 These efforts offer a unified reference framework for future research.
-	\textcolor{orange}{We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives.
+	\textcolor{orange}{%We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives.
 We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles.
 This work offers a unified reference framework and technical foundation for future research in this field.}
+	We provide an overview of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives, alongside a representative retrieval library and 3 vector databases.
+This work offers a unified reference framework and technical foundation for future research in this field.}
 
 	\textcolor{blue}{	(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
-To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+In addition to commonly used datasets, we also conduct experiments on a real-attribute dataset and a large-scale dataset (up to 100M records).
+Our benchmark design covers diverse selectivity levels and query conditions, establishing a unified and practical evaluation framework for hybrid query algorithms.}
+%To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
 We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results.

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-29 VLDB2026/main.tex
@@
 
-	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
+	(3){ Evaluation of Attribute and Range Filtering Algorithms.}
+	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases.
+We compare the index construction and query performance of each method across different scenarios, including various datasets, attribute distributions, attribute selectivity, query ranges, and server configurations.
+We identify the reasons for performance differences based on the design of the algorithms and summarize their respective strengths and weaknesses.}
+%	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-%	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
+%%	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
@@
 Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
-	\textcolor{orange}{We conduct a comprehensive evaluation of 6 attribute filtering algorithms, 1 library, and 3 databases across 6 basic datasets, 2 real-world datasets, one 100M-scale dataset, and 2 multimodal datasets.
+%	\textcolor{orange}{We conduct a comprehensive evaluation of 6 attribute filtering algorithms, 1 library, and 3 databases across 6 basic datasets, 2 real-world datasets, one 100M-scale dataset, and 2 multimodal datasets.
 By analyzing the query performance of each method under various scenarios, we reveal their respective strengths and weaknesses.
@@
 The evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.}
-
-	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
+%	
+%	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
+%%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
 We further analyze the factors that affect the performance of the range query algorithm.
-	\textcolor{orange}{
-		We conduct benchmark evaluations of range filtering algorithms on one synthetic and 2 real-world datasets, using various query range settings.
+%	\textcolor{orange}{
+%		We conduct benchmark evaluations of range filtering algorithms on one synthetic and 2 real-world datasets, using various query range settings.
 Our experiments reveal and analyze the differences in time and query efficiency across these algorithms.
 Furthermore, we compare their performance on multimodal and large-scale datasets, and assess their adaptability across different server environments.
-	}
-
-	\textcolor{blue}{(5)\textbf{ Recommendations and Challenges.}
-	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios.
+%	}
+
+	\textcolor{cyan}{{(4)\textbf{ Recommendations and Challenges.}
+	Based on the experimental results, we summarize a recommendation table in Section 5.1, which intuitively shows the suitable scenarios for each algorithm, allowing readers to select appropriate algorithms according to their own needs.
+In addition, we point out the challenges and the directions for future research in the field of hybrid querying.}}
+
+%	\textcolor{blue}{(5)\textbf{ Recommendations and Challenges.}
+%	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios.
 Readers can select suitable algorithms according to their specific application needs.
@@
 This indicates potential directions for future research.
-}
-%	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
+%}
+%%	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 
-	\begin{figure*}
-		\centering
-
-		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
-		\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
-		\label{fig:exp_3_1}
-
-%		\footnotesize{
-%		\begin{center}
-%			\begin{minipage}{\linewidth}
+%	\begin{figure*}
 %		\centering
-%				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
-%			\end{minipage}
-%		\end{center}
-%		}
-	\end{figure*}
+%		
+%		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
+%		\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
+%		\label{fig:exp_3_1}
+%		
+%%		\footnotesize{
+%%		\begin{center}
+%%			\begin{minipage}{\linewidth}
+%%				\centering	
+%%				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
+%%			\end{minipage}
+%%		\end{center}
+%%		}
+%	\end{figure*}
 
@@
 
-	\textit{\textbf{Attribute Distribution.}} To evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
+%	\textit{\textbf{Attribute Distribution.}} To evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
 We evaluate all algorithms under these distributions on each dataset.
@@
 Thus, due to space constraints, we present only the results on SIFT1M.
-
-	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
+%	
+%	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
 \textcolor{cyan}{The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
@@
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
-
-	{\color{blue}{
-		Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
+%	
+%	{\color{blue}{
+%		Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
 For instance, graph-based indexing methods like FilteredVamana and NHQ are prone to degraded connectivity or distorted structures under power-law distributions, where label frequencies are highly imbalanced.
@@
 Faiss, which searches within the nearest clusters, may need to traverse more clusters to find sufficient results when relevant data points are unevenly distributed across clusters due to attribute skew, which impacts performance.
-
-		In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges.
+%		
+%		In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges.
 Milvus, for example, leverages a built-in query optimizer that dynamically determines whether to filter by attributes or search vectors first, based on the selectivity of the query, thus ensuring more robust performance.
@@
 
-	\begin{figure}
-		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.1cm}
-		\includegraphics[width=0.95\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
-		\caption{Effect of Single-Attribute Selectivity on Query}
-		\label{fig:exp_5_1_1_SingleLabel_1thread}
-	\end{figure}
+%	\begin{figure}
+%		\centering
+%		\setlength{\abovecaptionskip}{0.1cm}
+%		\setlength{\belowcaptionskip}{-0.1cm}
+%		\includegraphics[width=0.95\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
+%		\caption{Effect of Single-Attribute Selectivity on Query}
+%		\label{fig:exp_5_1_1_SingleLabel_1thread}
+%	\end{figure}
 
@@
 	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
-We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
-
-	Experimental results show that UNG achieves the best performance across all AS settings, especially at extremely low AS (1\%). 
-	This advantage stems from its pre-filtering strategy.
+%	We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
+	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
+
+%	Experimental results show that UNG achieves the best performance across all AS settings, especially at extremely low AS (1\%). 
+%	This advantage stems from its pre-filtering strategy.
 Pre-filtering strategy significantly reduces the ANN search space by narrowing down candidates prior to vector computation.
@@
 
-	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
-
 	(1) \textit{Algorithms optimized for low AS.}  
-	This group includes ACORN-1, Faiss+HQI\_Batch, StitchedVamana, UNG, Faiss, Puck, and CAPS, as illustrated in Figure~\ref{fig:exp_5_2_1}.
-
-	ACORN-1 performs well in low AS because fewer nodes share the same attribute.
-This increases the average degree of retained nodes and improves graph connectivity.
+%	This group includes ACORN-1, CAPS, Faiss, Faiss+HQI\_Batch, Puck, StitchedVamana and UNG, as illustrated in Figure~\ref{fig:exp_5_2_1}.
+	\textcolor{orange}{Figure~\ref{fig:exp_5_2_1} shows the algorithms suitable for low AS.}
+	\textcolor{orange}{ACORN-1}, Faiss, Puck and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
 CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
@@
 However, at higher AS, it requires broader global exploration.
+
+%	ACORN-1 performs well in low AS because fewer nodes share the same attribute.
+This increases the average degree of retained nodes and improves graph connectivity.
 UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
 
-	Interestingly, Faiss and Faiss+HQI\_Batch perform worst at the 50\% AS instead of 75\%.
-	%, which might seem unexpected. 
-	This happens because, when AS decreases from 75\% to 50\%, fewer data points are filtered out. As a result, more clusters must be searched, increasing computational cost.
+%	Interestingly, Faiss and Faiss+HQI\_Batch perform worst at the 50\% AS instead of 75\%.
+%	%, which might seem unexpected. 
+%	This happens because, when AS decreases from 75\% to 50\%, fewer data points are filtered out. As a result, more clusters must be searched, increasing computational cost.
 
@@
 	(2) \textit{Algorithms optimized for high AS.}  
-	This group includes NHQ, FilteredVamana, VBASE, and PASE, as shown in Figure~\ref{fig:exp_5_2_2}.
-
-	At low AS, NHQ struggles to locate relevant regions efficiently, leading to excessive computations on non-matching nodes.
-FilteredVamana also performs poorly in these scenarios.
+%	This group includes FilteredVamana, NHQ, PASE and VBASE, as shown in Figure~\ref{fig:exp_5_2_2}.
+	\textcolor{orange}{Figure~\ref{fig:exp_5_2_2} shows the algorithms suitable for high AS.}
+	At low AS, FilteredVamana performs poorly in these scenarios.
 Its dynamic pruning strategy makes it difficult to balance vector distance and attribute relevance, resulting in overly restricted search paths.
-	VBASE relies on post-filtering, which increases computational overhead at low AS.
+NHQ struggles to locate relevant regions efficiently, leading to excessive computations on non-matching nodes.
 	 PASE performs poorly at extremely low AS (e.g., 1\%), with recall dropping below 0.2.
 Its fixed candidate set may not contain enough valid results after filtering, leading to incomplete top-$k$ results and significantly reducing recall.
+VBASE relies on post-filtering, which increases computational overhead at low AS.
 
@@
 	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
-
+	\textcolor{orange}{Figure 1 shows algorithms that are insensitive to AS.}
 	Milvus is mainly limited by system-level communication overhead, such as API latency.
@@
 
-	\subsubsection{Scalability Study}
+%	\subsubsection{Scalability Study}
 	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}} \textcolor{blue}{
@@
 
-%	\sout{It is important to note that this range query experiment is conducted under a fully static setting.
+	\sout{It is important to note that this range query experiment is conducted under a fully static setting.
 Under such conditions, UNIFY, iRange, SeRF, and WinFilter require the dataset to be sorted by attribute prior to index construction.

### 2025-07-30 Revision/response.tex
1

--- 2025-07-29 Revision/response.tex
@@
 This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
-As shown in Figure\ref{fig:attribute_selectivity} below.
+As shown in Figure~\ref{fig:attribute_selectivity} below.
 
@@
 \textbf{Response:} We believe this is an excellent suggestion.
-In fact, in the initial version of our paper, we used the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms.
-In this dataset, the base vectors are images, while the query set consists of texts, resulting in a modality gap between the two.
-Achieving good performance on such a dataset often requires the algorithm to demonstrate stronger robustness.
-\textbf{(Please see Section 4.2.3 and Section 4.3.3, highlighted in green in the revised manuscript.)}
-
-To further enrich the evaluation of complex multimodal queries, we have added new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
-Specifically, we constructed a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
-We then perform both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms.
-The corresponding experimental results are presented in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.
+To provide a more comprehensive evaluation of our algorithm's robustness, we introduce new experiments on two challenging multimodal datasets.
+
+First, we have incorporated a standard text-to-image dataset, which is widely adopted by existing multimodal ANN algorithms.
+In this dataset, the base vectors are images while the query set consists of texts, creating a modality gap that demands stronger algorithm robustness to achieve good performance.
+Second, to further test performance on complex queries, we have constructed a more challenging dataset with a base set of 500,000 text vectors and 500,000 image vectors, and a query set containing 5,000 text and 5,000 image vectors.
+On this latter dataset, we perform both attribute filtering and range queries using combined text and image inputs to analyze the algorithm's robustness under more complex, mixed-modality conditions.
+The experimental results are shown in Figure~\ref{fig:attribute_multimodel} and Figure~\ref{fig:range_multimodel}.
 
@@
 }
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.8\linewidth]{fig/attribute_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}
+	\caption{Attribute Filtering Multi-modal}
+	\label{fig:attribute_multimodel}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.8\linewidth]{fig/range_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/range_multimodel_2.pdf}
+	\caption{Range Filtering Multi-modal}
+	\label{fig:range_multimodel}
+\end{figure}
 

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-\textcolor{orange}{Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
+\textcolor{orange}{Although existing works, such as the surveys in \cite{compare,azizi2025graph}, conduct benchmark evaluations or experimental analyses of ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
-Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
+Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.}
 
@@
 These efforts offer a unified reference framework for future research.
-	\textcolor{orange}{%We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives.
+	\textcolor{orange}{We systematically categorize 6 representative attribute filtering algorithms and 5 range filtering algorithms from the perspectives of index organization, filtering strategies, disk support, and complex attribute handling.
 We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles.
 This work offers a unified reference framework and technical foundation for future research in this field.}
-	We provide an overview of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives, alongside a representative retrieval library and 3 vector databases.
-This work offers a unified reference framework and technical foundation for future research in this field.}
 
 	\textcolor{blue}{	(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
-		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
-In addition to commonly used datasets, we also conduct experiments on a real-attribute dataset and a large-scale dataset (up to 100M records).
-Our benchmark design covers diverse selectivity levels and query conditions, establishing a unified and practical evaluation framework for hybrid query algorithms.}
-%To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
 We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results.
@@
 
-	(3){ Evaluation of Attribute and Range Filtering Algorithms.}
-	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases.
-We compare the index construction and query performance of each method across different scenarios, including various datasets, attribute distributions, attribute selectivity, query ranges, and server configurations.
-We identify the reasons for performance differences based on the design of the algorithms and summarize their respective strengths and weaknesses.}
-%	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
+	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-%%	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
+%	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
@@
 Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
-%	\textcolor{orange}{We conduct a comprehensive evaluation of 6 attribute filtering algorithms, 1 library, and 3 databases across 6 basic datasets, 2 real-world datasets, one 100M-scale dataset, and 2 multimodal datasets.
+	\textcolor{orange}{We conduct a comprehensive evaluation of 6 attribute filtering algorithms, 1 library, and 3 databases across 6 basic datasets, 2 real-world datasets, one 100M-scale dataset, and 2 multimodal datasets.
 By analyzing the query performance of each method under various scenarios, we reveal their respective strengths and weaknesses.
@@
 The evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.}
-%	
-%	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-%%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
+
+	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
+%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
 We further analyze the factors that affect the performance of the range query algorithm.
-%	\textcolor{orange}{
-%		We conduct benchmark evaluations of range filtering algorithms on one synthetic and 2 real-world datasets, using various query range settings.
+	\textcolor{orange}{
+		We conduct benchmark evaluations of range filtering algorithms on one synthetic and 2 real-world datasets, using various query range settings.
 Our experiments reveal and analyze the differences in time and query efficiency across these algorithms.
 Furthermore, we compare their performance on multimodal and large-scale datasets, and assess their adaptability across different server environments.
-%	}
-
-	\textcolor{cyan}{{(4)\textbf{ Recommendations and Challenges.}
-	Based on the experimental results, we summarize a recommendation table in Section 5.1, which intuitively shows the suitable scenarios for each algorithm, allowing readers to select appropriate algorithms according to their own needs.
-In addition, we point out the challenges and the directions for future research in the field of hybrid querying.}}
-
-%	\textcolor{blue}{(5)\textbf{ Recommendations and Challenges.}
-%	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios.
+	}
+
+	\textcolor{blue}{(5)\textbf{ Recommendations and Challenges.}
+	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios.
 Readers can select suitable algorithms according to their specific application needs.
@@
 This indicates potential directions for future research.
-%}
-%%	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
+}
+%	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
@@
 
-	\textcolor{violet}{The first seven datasets are widely used in existing works.
+	\textcolor{violet}{The first seven datasets are widely used in existing literature.
 As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.}
 
-	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes.
-For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
+	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
@@
 	%4.2.1
-	\subsubsection{Time and Space overhead of index construction}
+	\subsubsection{\textcolor{violet}{Time and Space overhead}}
 	% \subsubsection{\textbf{Attribute Filtering}}
@@
 
-	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}.
+	\textcolor{violet}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}.
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
@@
 	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions, search often requires traversing larger candidate sets or deeper graph paths.
-This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods.
+This leads to increased computational cost and a sharp QPS drop for most methods.
 Despite this, UNG consistently maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes and searches only within the subgraph formed by points satisfying the filtering conditions, thereby improving query efficiency.}
@@
 	\textcolor{violet}{\textit{Multi-Thread Search.} As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, under multi-threading, all algorithms except Puck show similar improvements, with UNG continuing to maintain the best performance.
-Puck achieves significant performance improvement in multi-threading scenarios.}
+Puck achieves significant performance improvements in multi-threaded scenarios, delivering near-linear speedup by processing each query independently with a thread-local search context.
+This design eliminates synchronization overhead, enabling efficient parallel execution.}
 
@@
 
-%	\begin{figure*}
-%		\centering
-%		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
-%		\caption{Effect of Different Datasets on AF-ANN Search}
-%		\label{fig:exp_6_1}
-%	\end{figure*}
+	\begin{figure*}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
+		\caption{Effect of Different Datasets on AF-ANN Search}
+		\label{fig:exp_6_1}
+	\end{figure*}
 
@@
 
-	%\textit{\textbf{Different Datasets.}}  
-	%\sout{To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.
+	\textit{\textbf{Different Datasets.}}  
+	\sout{To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.
 Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.
@@
 %ykw: 这段话看着有问题
-	%As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.
+	As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.
 Because Audio has small scale, low dimensionality, and low LID.
@@
 
-	%SIFT1M and Msong are similar datasets, with the key difference being that SIFT1M has lower dimensionality.
+	SIFT1M and Msong are similar datasets, with the key difference being that SIFT1M has lower dimensionality.
 The 4 algorithms (ACORN, Faiss, PASE, and NHQ) perform similarly on these two datasets, suggesting strong robustness to high dimensional datasets.
@@
 
-	%Most algorithms struggle to achieve high recall on GloVe, because it has the highest LID.
+	Most algorithms struggle to achieve high recall on GloVe, because it has the highest LID.
 Compare to other algorithms, the 4 algorithms (UNG, Faiss, CAPS, and Milvus) manage to maintain relatively high recall, demonstrating better adaptability to complex datasets.
@@
 
-	%\textcolor{green}{Most algorithms exhibit the worst performance on the OOD dataset Text2Image.
+	\textcolor{green}{Most algorithms exhibit the worst performance on the OOD dataset Text2Image.
 However, ACORN, UNG, and FilteredVamana show relatively stable performance on Text2Image.
@@
 }
-	\subsubsection{Time and Space overhead of index construction.}
+	\subsubsection{\textcolor{violet}{Time and Space overhead.}}
 
@@
 
-	%\subsubsection{Robustness.}
-
-	%\begin{figure*}[htbp]
-	%	\centering
-	%	\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
-	%	\caption{Effect of Different Datasets on RF-ANN Search}
-	%	\label{fig:exp_8_3}
-	%\end{figure*}
-
-%	\textcolor{green}{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
+	\subsubsection{Robustness.}
+
+	\begin{figure*}[htbp]
+		\centering
+		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
+		\caption{Effect of Different Datasets on RF-ANN Search}
+		\label{fig:exp_8_3}
+	\end{figure*}
+
+	\textcolor{green}{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
 As shown in Figure~\ref{fig:exp_8_3}, most methods perform worst on the Text2Image dataset.
@@
 
-%	\sout{WinFilter shows the worst performance on the WIT dataset.
+	\sout{WinFilter shows the worst performance on the WIT dataset.
 This suggests that its performance is sensitive to the data dimensionality.
@@
 
-%	Among vector databases, Milvus performs well.
+	Among vector databases, Milvus performs well.
 VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image.
@@
 
-%	It is worth noting that most methods achieve similar performance on the Deep and YT-Audio datasets, which have similar LID values.
+	It is worth noting that most methods achieve similar performance on the Deep and YT-Audio datasets, which have similar LID values.
 This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
@@
 
-%	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them.
+	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them.
 This means that DSG is more sensitive to changes in data distribution.
@@
 
-	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. }
-%	For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
+	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions.
+For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
 Furthermore, NHQ only supports multi-attribute filtering with conjunctions ("AND" conditions).
 UNG is relatively more flexible in this regard, as it supports both "AND" and "OR" logic; however, it still cannot handle more complex Boolean expressions involving combinations of conjunctions and disjunctions.
-%	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
+	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
 However, it currently supports only single-attribute filtering and disjunctions ("OR" conditions) across multiple attributes.
 Enhancing its capability to support more flexible Boolean combinations would effectively overcome the limitations of current approaches and significantly improve its practicality for diverse and complex query requirements.
-%		}
-		\textcolor{orange}{
-For example, in multi-attribute scenarios, some algorithms only support Boolean OR logic (e.g., FilterDiskANN), while others only support Boolean AND logic (e.g., NHQ and CAPS).
-Although algorithms such as ACORN, UNG, and Puck support both AND and OR logic across multiple attributes, they still struggle to handle complex Boolean expressions that involve nested combinations of conjunctions (AND) and disjunctions (OR).
-In contrast, while databases and the vector search library Faiss support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
-Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed.
 		}

### 2025-07-30 VLDB2026/main.tex
大写

--- 2025-07-30 VLDB2026/main.tex
@@
 		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
-		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
+		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\Not Support}}} \\ \cline{2-9}
 		& OR                  & N   & Y   & Y   & N   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases.
-We compare the index construction and query performance of each method across different scenarios, including various datasets, attribute distributions, attribute selectivity, query ranges, and server configurations.
+We compare the index construction and query performance of each method across different scenarios using 5 core metrics.
 We identify the reasons for performance differences based on the design of the algorithms and summarize their respective strengths and weaknesses.}
@@
 		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
-		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\Not Support}}} \\ \cline{2-9}
+		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
 		& OR                  & N   & Y   & Y   & N   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 	(1)\textbf{ Systematic Classification and Overview.}
-%	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
+	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
 In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
 These efforts offer a unified reference framework for future research.
-	\textcolor{orange}{%We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives.
+%	\textcolor{orange}{%We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives.
 We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles.
 This work offers a unified reference framework and technical foundation for future research in this field.}
-	We provide an overview of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives, alongside a representative retrieval library and 3 vector databases.
+%	We provide an overview of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives, alongside a representative retrieval library and 3 vector databases.
 This work offers a unified reference framework and technical foundation for future research in this field.}
 
-	\textcolor{blue}{	(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
-		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+	(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
+%		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
 In addition to commonly used datasets, we also conduct experiments on a real-attribute dataset and a large-scale dataset (up to 100M records).
 Our benchmark design covers diverse selectivity levels and query conditions, establishing a unified and practical evaluation framework for hybrid query algorithms.}
-%To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+	To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
 We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results.
@@
 Furthermore, we test on a large-scale dataset containing 100 million records to analyze the scalability and performance of various algorithms.
-These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid queries.}
+These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 
-	(3){ Evaluation of Attribute and Range Filtering Algorithms.}
-	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases.
+%	(3){ Evaluation of Attribute and Range Filtering Algorithms.}
+%	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases.
 We compare the index construction and query performance of each method across different scenarios using 5 core metrics.
 We identify the reasons for performance differences based on the design of the algorithms and summarize their respective strengths and weaknesses.}
-%	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
+	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-%%	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
+	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
@@
 %	
-%	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-%%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
+	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
+	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
@@
 
-	\textcolor{cyan}{{(4)\textbf{ Recommendations and Challenges.}
-	Based on the experimental results, we summarize a recommendation table in Section 5.1, which intuitively shows the suitable scenarios for each algorithm, allowing readers to select appropriate algorithms according to their own needs.
+%	\textcolor{cyan}{{(4)\textbf{ Recommendations and Challenges.}
+%	Based on the experimental results, we summarize a recommendation table in Section 5.1, which intuitively shows the suitable scenarios for each algorithm, allowing readers to select appropriate algorithms according to their own needs.
 In addition, we point out the challenges and the directions for future research in the field of hybrid querying.}}
 
-%	\textcolor{blue}{(5)\textbf{ Recommendations and Challenges.}
+	{(5)\textbf{ Recommendations and Challenges.}
 %	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios.
@@
 This indicates potential directions for future research.
-%}
-%%	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
+%%}
+	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
@@
 	\textcolor{violet}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
-The Text2Image dataset includes two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
+The Text2Image dataset includes two versions.
+The original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set.
+The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
 

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 	\textcolor{orange}{ACORN-1}, Faiss, Puck and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
-CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
+\textcolor{orange}{Pre-filtering strategies significantly reduce the number of candidate points under low AS, thereby lowering the cost of  computations.
+As a result, such strategies tend to perform better in low AS scenarios.}CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
 However, as AS increases, it must process more subpartitions and handle a larger dataset.

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited. 
-\textcolor{orange}{Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
+	\textcolor{orange}{%Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
+	Although existing works\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
 	To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.

### 2025-07-30 VLDB2026/main.tex
1
Update main.tex

@@
 	Although existing works\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
-	To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+	To address this gap, we present the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
 Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
@@
 	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
-	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
+%	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
 	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
-In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
+In addition, we survey 5 range filtering algorithms, and provide an overview of a vector library and three vector databases.
 These efforts offer a unified reference framework for future research.
@@
 Our benchmark design covers diverse selectivity levels and query conditions, establishing a unified and practical evaluation framework for hybrid query algorithms.}
-	To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+%	To address the lack of standardized benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
 We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results.
 To comprehensively reflect diverse real-world application needs, we design experiments covering varying attribute distributions, selectivity levels, and query conditions, ensuring representative and practical evaluation.
-Furthermore, we test on a large-scale dataset containing 100 million records to analyze the scalability and performance of various algorithms.
-These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+\textcolor{cyan}{Furthermore, we test on a large-scale dataset containing 100 million records and a multi-modal dataset to analyze the scalability and performance of various algorithms.} These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
+Furthermore, we design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
+\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and a multi-modal dataset.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
-We further examine their behavior under different attribute distributions and selectivity to assess robustness and adaptability in complex query scenarios.
+We further examine their behavior under different attribute selectivity to assess robustness and adaptability in complex query scenarios.
 Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
@@
 %
+
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
@@
 	\textcolor{orange}{ACORN-1}, Faiss, Puck and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
-\textcolor{orange}{Pre-filtering strategies significantly reduce the number of candidate points under low AS, thereby lowering the cost of  computations.
-As a result, such strategies tend to perform better in low AS scenarios.}CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
+CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
 However, as AS increases, it must process more subpartitions and handle a larger dataset.

### 2025-07-30 VLDB2026/main.tex

@@
 	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited. 
-\textcolor{orange}{Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
-To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+	\textcolor{orange}{%Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
+	Although existing works\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
+	To address this gap, we present the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
 Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-Furthermore, we design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
+We design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
 \textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and a multi-modal dataset.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.

### 2025-07-30 VLDB2026/main.tex
1

@@
 	Although existing works\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
-	To address this gap, we present the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+	To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
 Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
@@
 	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
-In addition, we survey 5 range filtering algorithms, and provide an overview of a vector library and three vector databases.
+In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
 These efforts offer a unified reference framework for future research.
@@
 Our benchmark design covers diverse selectivity levels and query conditions, establishing a unified and practical evaluation framework for hybrid query algorithms.}
-%	To address the lack of standardized benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+	To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
 We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results.
 To comprehensively reflect diverse real-world application needs, we design experiments covering varying attribute distributions, selectivity levels, and query conditions, ensuring representative and practical evaluation.
-\textcolor{cyan}{Furthermore, we test on a large-scale dataset containing 100 million records and a multi-modal dataset to analyze the scalability and performance of various algorithms.} These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
-	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-We design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
-\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and a multi-modal dataset.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+Furthermore, we test on a large-scale dataset containing 100 million records to analyze the scalability and performance of various algorithms.
+These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
-We further examine their behavior under different attribute selectivity to assess robustness and adaptability in complex query scenarios.
+We further examine their behavior under different attribute distributions and selectivity to assess robustness and adaptability in complex query scenarios.
 Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
@@
 %	
-
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
@@
 				\vspace{0.1cm}
-				Win: WinFilter, Filtered: FilteredVamana, Stitched: StitchedVamana. 
+%				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
+%				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
+%				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
+%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+%				\textit{Disk Support} indicates whether the algorithm supports disk storage.
+%				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
+		\textcolor{orange}{
+		\textit{Win}: WinFilter, \textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana. 
+		\textit{AND} / \textit{OR}: Whether the algorithm supports the corresponding logical operations.
+		\textit{Flexible Attributes}: Allows the number of query attributes to differ from that in index construction.
+		\textit{Complex Boolean}: Supports NOT or nested Boolean expressions.
+		\textit{Dynamic Insert}: Supports dynamic data insertion.
+		\textit{Multi Thread}: Supports multi-threaded search.
+		\textit{Disk Support}: Supports disk-based storage.
+		\textit{Base}: Underlying ANN index structure used.}
 		\textsuperscript{A} Post-filtering, 
@@
 		\textsuperscript{N} Unsupport. 
-				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
-				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
-				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
-				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-				\textit{Disk Support} indicates whether the algorithm supports disk storage.
-				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
 		\end{minipage}}

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 	Although existing works\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
-	To address this gap, we present the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+	To address this gap, we carry out the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
 Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}

### 2025-07-30 Revision/response.tex
Update response.tex

--- 2025-07-30 Revision/response.tex
@@
 
-\usepackage{subfigure}
+%\usepackage{subfigure}
 \usepackage[vlined,ruled,linesnumbered]{algorithm2e}
@@
 This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
-As shown in Figure~\ref{fig:attribute_selectivity} below.
+As shown in Figure\ref{fig:attribute_selectivity} below.
 
@@
 \textbf{Response:} We believe this is an excellent suggestion.
-To provide a more comprehensive evaluation of our algorithm's robustness, we introduce new experiments on two challenging multimodal datasets.
-
-First, we have incorporated a standard text-to-image dataset, which is widely adopted by existing multimodal ANN algorithms.
-In this dataset, the base vectors are images while the query set consists of texts, creating a modality gap that demands stronger algorithm robustness to achieve good performance.
-Second, to further test performance on complex queries, we have constructed a more challenging dataset with a base set of 500,000 text vectors and 500,000 image vectors, and a query set containing 5,000 text and 5,000 image vectors.
-On this latter dataset, we perform both attribute filtering and range queries using combined text and image inputs to analyze the algorithm's robustness under more complex, mixed-modality conditions.
-The experimental results are shown in Figure~\ref{fig:attribute_multimodel} and Figure~\ref{fig:range_multimodel}.
+In fact, in the initial version of our paper, we used the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms.
+In this dataset, the base vectors are images, while the query set consists of texts, resulting in a modality gap between the two.
+Achieving good performance on such a dataset often requires the algorithm to demonstrate stronger robustness.
+\textbf{(Please see Section 4.2.3 and Section 4.3.3, highlighted in green in the revised manuscript.)}
+
+To further enrich the evaluation of complex multimodal queries, we have added new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.
+Specifically, we constructed a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set.
+We then perform both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms.
+The corresponding experimental results are presented in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.
 
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.8\linewidth]{fig/attribute_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}
-	\caption{Attribute Filtering Multi-modal}
-	\label{fig:attribute_multimodel}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.8\linewidth]{fig/range_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/range_multimodel_2.pdf}
-	\caption{Range Filtering Multi-modal}
-	\label{fig:range_multimodel}
-\end{figure}
-
 \begin{figure}[t]
@@
 That is a great suggestion.
-In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
+In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
@@
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
-\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
+\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 
-To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3. \textbf{(Please see Section 4.3, highlighted in blue in the revised manuscript.)}
-
-\textcolor{blue}{"Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
-The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones.
-"}
-
-In response to the large difference in index construction time shown in Figure 12a(now 13a), we have revised the paper based on your suggestion.
+To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3.2. \textbf{(Please see Section 4.3, highlighted in blue in the revised manuscript.)}
+
+In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
 We added more detailed and in-depth analysis to provide a clearer explanation.
@@
 
-	\textcolor{blue}{
-	"ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
-This efficiency stems from its construction process, which closely resembles that of the original HNSW, and from reducing the number of candidate neighbors in the upper layers, thereby lowering computational cost.
-SeRF, another HNSW-based method, also exhibits very short construction time.
-During construction, it attaches timestamp information to edges, keeping the total time comparable to building a single HNSW graph, which enables efficient construction even on large datasets.}
-
-\textcolor{blue}{
-	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
-This design introduces redundant computation and high construction cost.
-However, on large-scale datasets, the preprocessing phase of WinFilter was replaced with a base algorithm in the experiments, thus avoiding significant time overhead.}
-
-\textcolor{blue}{
-	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
-Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
-
-%	The reason for the high construction time of ACORN-$\gamma$ has been explained in the attribute filtering section and is therefore omitted here.
-
-\textcolor{blue}{
-	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
-This makes the construction process more complex and costly.
-In addition, on Deep100M, DSG uses single-threaded construction, resulting in the longest build time."}
-
-Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c(now 13c) is very insightful.
+Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c is very insightful.
 Initially, we hesitated to include the peak memory usage of databases (such as Milvus) because they are full systems that run continuously and contain many components.

### 2025-07-30 Revision/response.tex
1

--- 2025-07-30 Revision/response.tex
@@
 Section 4.2.1:
-\textcolor{blue}{"For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
-However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets.
-In contrast, Milvus has lower query-time memory usage because it does not fully load the index and incurs additional metadata overhead during construction."}
+\textcolor{blue}{"Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
+As a result, peak memory usage during querying is generally slightly lower than during construction.
+However, exceptions exist.
+As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set."}
 

### 2025-07-30 VLDB2026/main.tex
Update main.tex
1

@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the 6 datasets shown in the left figure, and 64 threads on the large-scale Deep100M dataset.}
+\textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the six datasets shown on the left of Figure~\ref{fig:build_index_comparison}, and 64 threads on the large-scale Deep100M dataset, shown on the right.}
 
@@
 \textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longer build times are mainly PASE, VBASE, and ACORN-$\gamma$.
-PASE and VBASE only support single-threaded builds, and PASE is the slowest because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster.
+PASE and VBASE only support single-threaded builds.
+PASE is the slowest because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency.
+VBASE uses full-memory builds and is relatively faster.
 ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates.
@@
 	% 宽度从\textwidth缩小到0.32\textwidth
-	\begin{subfigure}[b]{0.39\textwidth}
+	\begin{subfigure}[b]{0.38\textwidth}
 		\centering

### 2025-07-30 VLDB2026/main.tex
1
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-	\textcolor{orange}{%Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
-	Although existing works\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
-	To address this gap, we present the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+\textcolor{orange}{Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
+To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
 Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
@@
 	(1)\textbf{ Systematic Classification and Overview.}
-	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
-In addition, we survey 5 range filtering algorithms, and provide an overview of a vector library and three vector databases.
+%	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
+In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases.
 These efforts offer a unified reference framework for future research.
-%	\textcolor{orange}{%We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives.
+	\textcolor{orange}{%We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives.
 We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles.
 This work offers a unified reference framework and technical foundation for future research in this field.}
-%	We provide an overview of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives, alongside a representative retrieval library and 3 vector databases.
+	We provide an overview of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives, alongside a representative retrieval library and 3 vector databases.
 This work offers a unified reference framework and technical foundation for future research in this field.}
 
-	(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
-%		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+	\textcolor{blue}{	(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
+		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
 In addition to commonly used datasets, we also conduct experiments on a real-attribute dataset and a large-scale dataset (up to 100M records).
 Our benchmark design covers diverse selectivity levels and query conditions, establishing a unified and practical evaluation framework for hybrid query algorithms.}
-%	To address the lack of standardized benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
+%To address the lack of standardized evaluation benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
 We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results.
 To comprehensively reflect diverse real-world application needs, we design experiments covering varying attribute distributions, selectivity levels, and query conditions, ensuring representative and practical evaluation.
-\textcolor{cyan}{Furthermore, we test on a large-scale dataset containing 100 million records and a multi-modal dataset to analyze the scalability and performance of various algorithms.} These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
-	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-We design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
-\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and a multi-modal dataset.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+Furthermore, we test on a large-scale dataset containing 100 million records to analyze the scalability and performance of various algorithms.
+These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid queries.}
 
@@
 
-%	(3){ Evaluation of Attribute and Range Filtering Algorithms.}
-%	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases.
-We compare the index construction and query performance of each method across different scenarios using 5 core metrics.
+	(3){ Evaluation of Attribute and Range Filtering Algorithms.}
+	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases.
+We compare the index construction and query performance of each method across different scenarios, including various datasets, attribute distributions, attribute selectivity, query ranges, and server configurations.
 We identify the reasons for performance differences based on the design of the algorithms and summarize their respective strengths and weaknesses.}
-	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
+%	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
+%%	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
-We further examine their behavior under different attribute selectivity to assess robustness and adaptability in complex query scenarios.
+We further examine their behavior under different attribute distributions and selectivity to assess robustness and adaptability in complex query scenarios.
 Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
@@
 %	
-
-	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
+%	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
+%%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
@@
 
-%	\textcolor{cyan}{{(4)\textbf{ Recommendations and Challenges.}
-%	Based on the experimental results, we summarize a recommendation table in Section 5.1, which intuitively shows the suitable scenarios for each algorithm, allowing readers to select appropriate algorithms according to their own needs.
+	\textcolor{cyan}{{(4)\textbf{ Recommendations and Challenges.}
+	Based on the experimental results, we summarize a recommendation table in Section 5.1, which intuitively shows the suitable scenarios for each algorithm, allowing readers to select appropriate algorithms according to their own needs.
 In addition, we point out the challenges and the directions for future research in the field of hybrid querying.}}
 
-	{(5)\textbf{ Recommendations and Challenges.}
+%	\textcolor{blue}{(5)\textbf{ Recommendations and Challenges.}
 %	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios.
@@
 This indicates potential directions for future research.
-%%}
-	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
+%}
+%%	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
 These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
@@
 				\vspace{0.1cm}
-%				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
-%				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
-%				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
-%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-%				\textit{Disk Support} indicates whether the algorithm supports disk storage.
-%				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
-		\textcolor{orange}{
-		\textit{Win}: WinFilter, \textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana. 
-		\textit{AND} / \textit{OR}: Whether the algorithm supports the corresponding logical operations.
-		\textit{Flexible Attributes}: Allows the number of query attributes to differ from that in index construction.
-		\textit{Complex Boolean}: Supports NOT or nested Boolean expressions.
-		\textit{Dynamic Insert}: Supports dynamic data insertion.
-		\textit{Multi Thread}: Supports multi-threaded search.
-		\textit{Disk Support}: Supports disk-based storage.
-		\textit{Base}: Underlying ANN index structure used.}
+				Win: WinFilter, Filtered: FilteredVamana, Stitched: StitchedVamana. 
 				\textsuperscript{A} Post-filtering, 
@@
 				\textsuperscript{N} Unsupport. 
+				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
+				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
+				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
+				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+				\textit{Disk Support} indicates whether the algorithm supports disk storage.
+				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
 		\end{minipage}}
@@
 	\textcolor{violet}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
-The Text2Image dataset includes two versions.
-The original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set.
-The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
+The Text2Image dataset includes two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
 
@@
 	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}} \textcolor{blue}{
-		We conduct experiments on the text2image-mix dataset.
+		We conduct experiments on the Text2image-Mix dataset.
 This dataset contains image and text vectors and is a hybrid multimodal dataset.
@@
 Therefore, the performance on this dataset is similar to the results shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
-		In contrast, the text2image dataset shown in Figure~\ref{fig:attribute-multimodal} is different.
+		In contrast, the Text2image dataset shown in Figure~\ref{fig:attribute-multimodal} is different.
 The query set and the base dataset belong to two completely different modalities.
-Queries are far from the dataset points, and the ground truths are more dispersed and not clustered together.
+Queries are far from the dataset points, and the ground truths are more dispersed.
 To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance.
@@
 	\textcolor{blue}{
-		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
+		Similar to attribute filtering, the performance of multimodal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
+These algorithms on the Text2Image dataset exhibit a significant performance degradation.
+This is because these range query algorithms are almost entirely graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets.
+%		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
 As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
 This is because these range query algorithms are almost graph-based.
-Graph algorithms need more iterations to find true neighbors in OOD datasets.}
+Graph algorithms need more iterations to find true neighbors in OOD datasets.
+		}
 
@@
 	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
-%	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
+	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
 	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
@@
 	\textcolor{blue}{
-	Lastly, existing algorithms suffer from significant performance degradation on out-of-distribution (OOD) datasets.
+	Lastly, existing algorithms suffer from significant performance degradation on OOD datasets.
 Exploring how to improve these algorithms to better adapt to more complex query conditions is a worthwhile direction for further research.}

### 2025-07-30 VLDB2026/main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 
-	(2) \textbf{Enhancing Datasets and Experimental Settings for Fair Evaluation.}
+	(2) \textbf{Strengthening Datasets and Experimental Settings for Fair Evaluation.}
 %		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
@@
 %\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
-
 \textit{\textbf{Build peak memory.}}

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 We design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
-\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and a multi-modal dataset.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and 2 multi-modal datasets.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the six datasets shown on the left of Figure~\ref{fig:build_index_comparison}, and 64 threads on the large-scale Deep100M dataset, shown on the right.}
+\textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the 6 datasets shown in the left figure, and 64 threads on the large-scale Deep100M dataset.}
 
@@
 \textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longer build times are mainly PASE, VBASE, and ACORN-$\gamma$.
-PASE and VBASE only support single-threaded builds.
-PASE is the slowest because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency.
-VBASE uses full-memory builds and is relatively faster.
+PASE and VBASE only support single-threaded builds, and PASE is the slowest because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster.
 ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates.
@@
 	% 宽度从\textwidth缩小到0.32\textwidth
-	\begin{subfigure}[b]{0.38\textwidth}
+	\begin{subfigure}[b]{0.39\textwidth}
 		\centering

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 We design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
-\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and 2 multi-modal datasets.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and a multi-modal dataset.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 This design introduces redundant computation and high construction cost.
-However, on large-scale datasets, the preprocessing phase of WinFilter was replaced with a base algorithm in the experiments, thus avoiding significant time overhead.}
+However, on large-scale datasets, the preprocessing phase of WinFilter is replaced in the experiments by the base algorithm Vamana-WST, thus avoiding significant time overhead.}
 

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 \textit{\textbf{Index construction time.}}
-\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longer build times are mainly PASE, VBASE, and ACORN-$\gamma$.
+\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longest build times are mainly PASE, VBASE, and ACORN-$\gamma$.
 PASE and VBASE only support single-threaded builds.
@@
 VBASE uses full-memory builds and is relatively faster.
-ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates.
-The build time on some datasets even exceeds that of single-threaded VBASE.
-}
-
-\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned, we also observe that algorithms based on Vamana (such as FilteredDiskANN and UNG) exhibit significantly increased construction time.
+ACORN-$\gamma$  has a high computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates.
+Its build time on some datasets even exceeds that of single-threaded VBASE.
+}
+
+\textcolor{orange}{On the large-scale dataset Deep100M, besides the three methods already mentioned, we also observe that algorithms based on Vamana (such as FilteredDiskANN and UNG) exhibit significantly increased construction time.
 Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
@@
 
-\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
+\textit{\textbf{Search peak memory.}}
 %  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
@@
 This design introduces redundant computation and high construction cost.
-However, on large-scale datasets, the preprocessing phase of WinFilter is replaced in the experiments by the base algorithm Vamana-WST, thus avoiding significant time overhead.}
+However, on large-scale datasets, the preprocessing phase of WinFilter was replaced with a base algorithm in the experiments, thus avoiding significant time overhead.}
 

### 2025-07-30 Revision/response.tex
1
Update response.tex

@@
 \textbf{Response:} We believe this is an excellent suggestion.
-To provide a more comprehensive evaluation of our algorithm's robustness, we introduce new experiments on two challenging multimodal datasets.
-
-First, we have incorporated a standard text-to-image dataset, which is widely adopted by existing multimodal ANN algorithms.
+To provide a more comprehensive evaluation of the robustness of each algorithm, we introduce new experiments on two challenging multi-modal datasets.
+
+First, we have incorporated a standard text-to-image dataset, which is widely adopted by existing multi-modal ANN algorithms.
 In this dataset, the base vectors are images while the query set consists of texts, creating a modality gap that demands stronger algorithm robustness to achieve good performance.
@@
 To address this critical issue and enhance the real-world relevance of our evaluation, we have incorporated two new real-world datasets with their actual attributes into our attribute filtering and range filtering experiments, and we have clarified the sources of these real-world attributes.
-For more details, please refer to our Response to Meta R3.
-
-For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Building and Single-Attribute Query" experiments and amended the manuscript accordingly.
-It is also worth noting that in Section 4.2.2, under the "Single-Attribute Building and Single-Attribute Query" subsection, we have removed two previous datasets (Audio and GloVe) due to space constraints.
+For more details, please refer to our response to Meta R3.
+
+For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Index Construction and Single-Attribute Query" experiments and amended the manuscript accordingly.
+It is also worth noting that in Section 4.2.2, under the "Single-Attribute Index Construction and Single-Attribute Query" subsection, we have removed two previous datasets (Audio and GloVe) due to space constraints.
 The Audio dataset was removed because its smaller scale offered limited reference value.
@@
 
-In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the algorithm's performance.
-For more details, please refer to our Response to Review 1 W1.
+In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the performance of algorithms.
+For more details, please refer to our response to Review 1 W1.
 

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{orange}{Note: For regular-scale datasets, all algorithms build indexes using a single thread.
+\textcolor{orange}{Notably, for regular-scale datasets, all algorithms build indexes using a single thread.
 For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}
@@
 
-	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
+	\textcolor{violet}{Similar to attribute filtering, PASE requires the most storage. }
 	\textcolor{orange}{Additionally, DSG also results in a large index size, especially on large-scale datasets.

### 2025-07-30 Revision/response.tex
Update response.tex

@@
 The results show that differences in server configurations have little impact on the ranking of the methods.
- Please refer to the response Meta R4 for more details.
+For more details, please refer to our response Meta R4.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%
@@
 We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
-
-We have made a detailed response to this issue in our reply to Meta R6. Please refer to that response for more information.
+For more details, please refer to our response Meta R6.
+
+%We have made a detailed response to this issue in our reply to Meta R6. Please refer to that response for more information.
 
@@
 
- \textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
+ \textcolor{blue}{"
+% 	Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
 To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
-Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications."}
+Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
+ 	Although existing works [9,50] conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
+ 	To address this gap, we carry out the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications."}
 

### 2025-07-30 Revision/response.tex
Update response.tex

--- 2025-07-30 Revision/response.tex
@@
 \textbf{Response:} We believe this is an excellent suggestion.
-To provide a more comprehensive evaluation of our algorithm's robustness, we introduce new experiments on two challenging multimodal datasets.
+To provide a more comprehensive evaluation of the robustness of each algorithm, we introduce new experiments on two challenging multi-modal datasets.
 
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios,as shown in Table~\ref{tab:algo_scenarios}.
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algo_scenarios}.
 \textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}

### 2025-07-30 Revision/response.tex
1

--- 2025-07-30 Revision/response.tex
@@
 \noindent
-\textbf{Response:}
 
@@
 \noindent
-\textbf{Response:} We sincerely appreciate your valuable suggestions, which provide meaningful improvements to our work.
+%\textbf{Response:} We sincerely appreciate your valuable suggestions, which provide meaningful improvements to our work.
 Ensuring the readability of the figures is indeed crucial.
@@
 \textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
-
-\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
+%
+%\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
-
-For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure.
+%
+%For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
 As shown in Figure\ref{fig:attribute_distribution} below.
-
-\begin{figure}[htbp]
+\textbf{Response:} Thank you for your valuable suggestions.
+We agree that the original figure had readability issues.
+Based on your feedback, we have carefully revised and reanalyzed the experimental sections related to “attribute distribution” and “attribute selectivity” in the paper.
+
+In real-world applications, attribute distributions are often diverse, such as long-tail, uniform, or normal distributions.
+In our initial design, we included multiple attribute distributions to evaluate the robustness of algorithms under different data characteristics.
+However, we later realized that attribute distribution is essentially a mixture of different attribute selectivities.
+Its impact on algorithm performance is ultimately determined by attribute selectivity in each query.
+For example, in a long-tail distribution, querying a common “head” attribute is equivalent to a high attribute selectivity (High AS) case, while querying a rare “tail” attribute is equivalent to a low attribute selectivity (Low AS) case.
+Therefore, by evaluating performance under a range of attribute selectivities (e.g., AS = 1\% to AS = 75\%), we have already covered the effects of different attribute distributions.
+In this sense, the attribute selectivity experiments provide a unified and quantitative way to reflect the influence of attribute distributions.
+
+We present the results of attribute distribution and attribute selectivity in Figure~\ref{fig:attribute_distribution} and Figure~\ref{fig:attribute_selectivity} , respectively.
+The conclusions are highly consistent.
+For example, Faiss performs poorly under high attribute selectivity and also under long-tail distributions.
+This is because most queries in a long-tail distribution correspond to high-selectivity attributes, while only a few are low-selectivity, which limits the overall performance.
+
+Moreover, previous studies (e.g., FilteredDiskANN, Milvus) also commonly use attribute selectivity as a key metric for evaluating filtering performance.
+
+Based on these reasons, we decided to remove the attribute distribution experiments and retain only the attribute selectivity analysis.
+We also removed the original Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret.
+We believe these changes improve the clarity and readability of the paper, without reducing the completeness of the evaluation.
+
+\begin{figure*}[t]  % 或者 [b] 放到底部
 	\centering
-	\includegraphics[width=\linewidth]{fig/exp_3_1_legend.pdf}
+%	\includegraphics[width=\linewidth]{fig/exp_3_1_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
-	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
+	\caption{Effect of Attribute Distribution on Query Performance (Strong indicates robustness to attribute distribution shifts, Weak indicates sensitivity)}
 	\label{fig:attribute_distribution}
-\end{figure}
+\end{figure*}
 
@@
 
+\begin{figure*}[t]  % 可改为 [b] 放在页面底部
+	\centering
+%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
+	\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
+	\label{fig:attribute_selectivity}
+\end{figure*}
+
 \begin{figure}[htbp]
 	\centering
-	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
+%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
 	\caption{Different AS under the Same Algorithm}
-	\label{fig:attribute_selectivity}
+	\label{fig:attribute_selectivity_2}
 \end{figure}

### 2025-07-30 Revision/response.tex
change 4.2.4 to 4.2.3

--- 2025-07-30 Revision/response.tex
@@
 We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.
-\textbf{(Please see Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
-
-Section 4.2.4:
+\textbf{(Please see Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
+
+Section 4.2.3:
 %\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
@@
 
-Section 4.3.4:
+Section 4.3.3:
 %\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
@@
 For brevity and due to space limitations, we omit further discussion of these redundant results."}
-\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
-Our findings remain consistent with those reported in Section 4.2.4.
+\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
+Our findings remain consistent with those reported in Section 4.2.3.
 For brevity and due to space limitations, we omit further discussion of these redundant results."}
@@
 Thank you for your valuable suggestion regarding our experiments.
-In Section 4.2.4 and Section 4.3.4, we have added experiments on the Deep100M dataset.
+In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset.
 The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset.
 In particular, StitchedVamana performs poorly on Deep100M.
-\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
 %\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
 
-Section 4.2.4:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Section 4.2.3:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 
-Section 4.3.4:
+Section 4.3.3:
 \textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algo_scenarios}.
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios,as shown in Table~\ref{tab:algo_scenarios}.
 \textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
@@
 Thank you for your suggestion.
-We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4.
+We have added relevant experiments conducted on different servers in Section 4.2.3 and 4.3.3.
 The results show that differences in server configurations have little impact on the ranking of the methods.
@@
 Thank you for your suggestion.
-We have added experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observed some pitfalls.
+We have added experiments on the Deep100M dataset in Section 4.2.3 and Section 4.3.3, and we observed some pitfalls.
 For more details, please refer to our response to Meta R7.

### 2025-07-30 Revision/response.tex
1

@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{fig/attribute_legend.pdf}
+	\includegraphics[width=0.98\linewidth]{fig/attribute_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{fig/range_legend.pdf}
+	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/range_multimodel_2.pdf}
@@
 	\vspace{5pt} 
-	\includegraphics[width=0.99\columnwidth]{fig/range_2_2.pdf}
+	\includegraphics[width=0.95\columnwidth]{fig/range_2_2.pdf}
 
@@
 We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors.
-\textbf{(Please see Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
-
-Section 4.2.3:
+\textbf{(Please see Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
+
+Section 4.2.4:
 %\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
@@
 
-Section 4.3.3:
+Section 4.3.4:
 %\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
@@
 For brevity and due to space limitations, we omit further discussion of these redundant results."}
-\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
-Our findings remain consistent with those reported in Section 4.2.3.
+\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
+Our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results."}
@@
 Thank you for your valuable suggestion regarding our experiments.
-In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset.
+In Section 4.2.4 and Section 4.3.4, we have added experiments on the Deep100M dataset.
 The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset.
 In particular, StitchedVamana performs poorly on Deep100M.
-\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.4 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
 %\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
 
-Section 4.2.3:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Section 4.2.4:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 
-Section 4.3.3:
+Section 4.3.4:
 \textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
@@
 Thank you for your suggestion.
-We have added relevant experiments conducted on different servers in Section 4.2.3 and 4.3.3.
+We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4.
 The results show that differences in server configurations have little impact on the ranking of the methods.
@@
 Thank you for your suggestion.
-We have added experiments on the Deep100M dataset in Section 4.2.3 and Section 4.3.3, and we observed some pitfalls.
+We have added experiments on the Deep100M dataset in Section 4.2.4 and Section 4.3.4, and we observed some pitfalls.
 For more details, please refer to our response to Meta R7.

### 2025-07-30 Revision/response.tex
Update response.tex

--- 2025-07-30 Revision/response.tex
@@
 	\centering
-	\includegraphics[width=0.98\linewidth]{fig/attribute_legend.pdf}
+	\includegraphics[width=0.8\linewidth]{fig/attribute_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
+	\includegraphics[width=0.8\linewidth]{fig/range_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/range_multimodel_2.pdf}
@@
 	\vspace{5pt} 
-	\includegraphics[width=0.95\columnwidth]{fig/range_2_2.pdf}
+	\includegraphics[width=0.99\columnwidth]{fig/range_2_2.pdf}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
-In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
-For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution.
-For attribute selectivity: for example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
+Thank you for your suggestion.
+We cited these two papers in the introduction to show that there are several papers that study attribute selectivity.
+In practice, attribute selectivity are indeed widely used in real-world scenarios.
+For example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we have replaced them in the paper with more comprehensive and accurate references.
+We have replaced the two references ([12] and [36]) with more comprehensive and accurate references ([47] and [52]).
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[13], and attribute  selectivity [47,52] significantly impact algorithm performance."}
-
-[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627.
-
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute  selectivity [47,52] significantly impact algorithm performance."}
+
+\textcolor{blue}{"
+[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
+}
+
+\textcolor{blue}{"
 [52]Chuangxian Wei, Bin Wu, Sheng Wang, Renjie Lou, Chaoqun Zhan, Feifei Liand Yuanzhe Cai.
@@
 VLDB Endow.
-13, 12(2020),3152-3165.
+13, 12(2020),3152-3165."
+}
 

### 2025-07-30 Revision/response.tex
1

--- 2025-07-30 Revision/response.tex
@@
 
-For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we added performance rankings for each algorithm across different selectivity levels in the figure.
+%For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we added performance rankings for each algorithm across different selectivity levels in the figure.
 This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.

### 2025-07-30 Revision/response.tex
Update response.tex

--- 2025-07-30 Revision/response.tex
@@
 The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M.
-\textbf{(Please see Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
+\textbf{(Please see Section 4.2.1, and the "Single-Attribute Index Construction and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
 

### 2025-07-30 Revision/response.tex
1

--- 2025-07-30 Revision/response.tex
@@
 We agree that the original figure had readability issues.
-Based on your feedback, we have carefully revised and reanalyzed the experimental sections related to “attribute distribution” and “attribute selectivity” in the paper.
+We have first improved the readability of the attribute selectivity Figure~\ref{fig:attribute_selectivity} by adding comparative charts for each algorithm with different attribute selectivities.
+
+Furthermore, based on your feedback, we have carefully revised and reanalyzed the experimental sections related to “attribute distribution” and “attribute selectivity” in the paper.
 
@@
 
-\begin{figure*}[t]  % 可改为 [b] 放在页面底部
-	\centering
-%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
+	\begin{figure*}
+	\centering
+
+	% 第一行：单独一张大图
+	\begin{subfigure}{\textwidth}
+		\centering
+
+		\includegraphics[width=0.95\textwidth]{fig/exp_5_2_1.pdf}
+		\caption{Algorithms Optimized for Low AS}
+		\label{fig:exp_5_2_1}
+	\end{subfigure}
+
+	\vfill % 增加垂直间距
+
+	% 第二行：两张子图，左侧宽度是右侧的两倍
+	\begin{subfigure}{0.627\textwidth} % 2/3 宽度
+		\centering
+
+		\includegraphics[width=0.96\textwidth]{fig/exp_5_2_2.pdf}
+		\caption{Algorithms Optimized for High AS}
+		\label{fig:exp_5_2_2}
+	\end{subfigure}
+	\hspace{1mm} % 增加水平间距
+	\begin{subfigure}{0.33\textwidth} % 1/3 宽度
+		\centering
+
+		\includegraphics[width=0.96\textwidth]{fig/exp_5_2_3.pdf}
+		\caption{Algorithms Insensitive to AS}
+		\label{fig:exp_5_2_3}
+	\end{subfigure}
+
 	\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
@@
 \end{figure*}
-
 \begin{figure}[htbp]
@@
 \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-30 Revision/response.tex
1

@@
 We agree that the original figure had readability issues.
-We have first improved the readability of the attribute selectivity Figure~\ref{fig:attribute_selectivity} by adding comparative charts for each algorithm with different attribute selectivities.
+We have first improved the readability of the attribute selectivity Figure~\ref{fig:attribute_selectivity} by adding comparative legends for each algorithm and standardizing the y-axis scales across different subplots.
 

### 2025-07-30 Revision/response.tex
Update response.tex

--- 2025-07-30 Revision/response.tex
@@
 \noindent
+\textbf{Response:}
 
@@
 \noindent
-%\textbf{Response:} We sincerely appreciate your valuable suggestions, which provide meaningful improvements to our work.
+\textbf{Response:} We sincerely appreciate your valuable suggestions, which provide meaningful improvements to our work.
 Ensuring the readability of the figures is indeed crucial.
@@
 \textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
-%
-%\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
+
+\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
-%
-%For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure.
+
+For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
 As shown in Figure\ref{fig:attribute_distribution} below.
-\textbf{Response:} Thank you for your valuable suggestions.
-We agree that the original figure had readability issues.
-We have first improved the readability of the attribute selectivity Figure~\ref{fig:attribute_selectivity} by adding comparative charts for each algorithm with different attribute selectivities.
-
-Furthermore, based on your feedback, we have carefully revised and reanalyzed the experimental sections related to “attribute distribution” and “attribute selectivity” in the paper.
-
-In real-world applications, attribute distributions are often diverse, such as long-tail, uniform, or normal distributions.
-In our initial design, we included multiple attribute distributions to evaluate the robustness of algorithms under different data characteristics.
-However, we later realized that attribute distribution is essentially a mixture of different attribute selectivities.
-Its impact on algorithm performance is ultimately determined by attribute selectivity in each query.
-For example, in a long-tail distribution, querying a common “head” attribute is equivalent to a high attribute selectivity (High AS) case, while querying a rare “tail” attribute is equivalent to a low attribute selectivity (Low AS) case.
-Therefore, by evaluating performance under a range of attribute selectivities (e.g., AS = 1\% to AS = 75\%), we have already covered the effects of different attribute distributions.
-In this sense, the attribute selectivity experiments provide a unified and quantitative way to reflect the influence of attribute distributions.
-
-We present the results of attribute distribution and attribute selectivity in Figure~\ref{fig:attribute_distribution} and Figure~\ref{fig:attribute_selectivity} , respectively.
-The conclusions are highly consistent.
-For example, Faiss performs poorly under high attribute selectivity and also under long-tail distributions.
-This is because most queries in a long-tail distribution correspond to high-selectivity attributes, while only a few are low-selectivity, which limits the overall performance.
-
-Moreover, previous studies (e.g., FilteredDiskANN, Milvus) also commonly use attribute selectivity as a key metric for evaluating filtering performance.
-
-Based on these reasons, we decided to remove the attribute distribution experiments and retain only the attribute selectivity analysis.
-We also removed the original Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret.
-We believe these changes improve the clarity and readability of the paper, without reducing the completeness of the evaluation.
-
-\begin{figure*}[t]  % 或者 [b] 放到底部
+
+\begin{figure}[htbp]
 	\centering
-%	\includegraphics[width=\linewidth]{fig/exp_3_1_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/exp_3_1_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
-	\caption{Effect of Attribute Distribution on Query Performance (Strong indicates robustness to attribute distribution shifts, Weak indicates sensitivity)}
+	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
 	\label{fig:attribute_distribution}
-\end{figure*}
-
-%For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we added performance rankings for each algorithm across different selectivity levels in the figure.
+\end{figure}
+
+For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we added performance rankings for each algorithm across different selectivity levels in the figure.
 This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
@@
 
-	\begin{figure*}
-	\centering
-
-	% 第一行：单独一张大图
-	\begin{subfigure}{\textwidth}
-		\centering
-
-		\includegraphics[width=0.95\textwidth]{fig/exp_5_2_1.pdf}
-		\caption{Algorithms Optimized for Low AS}
-		\label{fig:exp_5_2_1}
-	\end{subfigure}
-
-	\vfill % 增加垂直间距
-
-	% 第二行：两张子图，左侧宽度是右侧的两倍
-	\begin{subfigure}{0.627\textwidth} % 2/3 宽度
-		\centering
-
-		\includegraphics[width=0.96\textwidth]{fig/exp_5_2_2.pdf}
-		\caption{Algorithms Optimized for High AS}
-		\label{fig:exp_5_2_2}
-	\end{subfigure}
-	\hspace{1mm} % 增加水平间距
-	\begin{subfigure}{0.33\textwidth} % 1/3 宽度
-		\centering
-
-		\includegraphics[width=0.96\textwidth]{fig/exp_5_2_3.pdf}
-		\caption{Algorithms Insensitive to AS}
-		\label{fig:exp_5_2_3}
-	\end{subfigure}
-
-	\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
-	\label{fig:attribute_selectivity}
-\end{figure*}
 \begin{figure}[htbp]
 	\centering
-	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
+	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
 	\caption{Different AS under the Same Algorithm}
-	\label{fig:attribute_selectivity_2}
+	\label{fig:attribute_selectivity}
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We cited these two papers in the introduction to show that there are several papers that study attribute selectivity.
-In practice, attribute selectivity are indeed widely used in real-world scenarios.
-For example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
+Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
+In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
+For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution.
+For attribute selectivity: for example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-We have replaced the two references ([12] and [36]) with more comprehensive and accurate references ([47] and [52]).
+For the two parts you suggested, we have replaced them in the paper with more comprehensive and accurate references.
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute  selectivity [47,52] significantly impact algorithm performance."}
-
-\textcolor{blue}{"
-[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
-}
-
-\textcolor{blue}{"
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[13], and attribute  selectivity [47,52] significantly impact algorithm performance."}
+
+[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627.
+
 [52]Chuangxian Wei, Bin Wu, Sheng Wang, Renjie Lou, Chaoqun Zhan, Feifei Liand Yuanzhe Cai.
@@
 VLDB Endow.
-13, 12(2020),3152-3165."
-}
+13, 12(2020),3152-3165.
 
@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We have already addressed this issue in detail in our responses to Meta R8 and R9.
-Specifically, we analyzed the strengths and weaknesses of each algorithm and recommended those with strong performance.
+Thank you for your suggestion. %We have already addressed this issue in detail in our responses to Meta R8 and R9. 
+We have addressed this issue in the revised manuscript by
+%Specifically, we 
+analyzing the strengths and weaknesses of each algorithm and recommended those with strong performance.
 Additionally, we provided a summary table illustrating how each algorithm performs across different application scenarios.

### 2025-07-30 VLDB2026/main.tex
1

@@
 We design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
-\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and 2 multi-modal datasets.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and 2 multi-modal datasets.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid queries.
 
@@
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-We further analyze the factors that affect the performance of the range query algorithm.
+We further analyze the factors that affect the performance of the range filtering algorithms.
 %	\textcolor{orange}{
@@
 	%We briefly introduce the fundamental principles of these two types in the following.
-	\textcolor{violet}{Here, we briefly review the core concepts of these indexes and outline how attributes and range constraints are embedded to support hybrid query functionality.}
+	\textcolor{violet}{Here, we briefly review the core concepts of these indexes and outline how attributes and range constraints are embedded to support hybrid queries functionality.}
 
@@
 
-	\textcolor{violet}{Graph indexes are widely used in Hybrid ANN due to their efficiency.
+	\textcolor{violet}{Graph indexes are widely used in hybrid ANN search due to their efficiency.
 To support hybrid queries, in attribute filtering, a common practice involves attaching attribute metadata to nodes or edges, thereby skipping parts that do not satisfy query conditions during traversal (e.g., NHQ, Filtered-DiskANN, ACORN).
@@
 
-	\textcolor{violet}{IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
+	\textcolor{violet}{IVF-based indexes also offer unique advantages in hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
@@
 
-	The vector libraries and databases discussed in the following are not explicitly designed for hybrid query, but they support both attribute filtering and range filtering.
+	The vector libraries and databases discussed in the following are not explicitly designed for hybrid queries, but they support both attribute filtering and range filtering.
 Additionally, all the functionalities shown in Table 1 are also supported.
@@
 
-	\textcolor{violet}{Puck and CAPS perform relatively well, indicating that IVF-based methods remain very promising for hybrid query.}
+	\textcolor{violet}{Puck and CAPS perform relatively well, indicating that IVF-based methods remain very promising for hybrid queries.}
 
@@
 
-		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}  
+		\textit{\textbf{Search peak memory.}}  
 		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, the peak memory usage during search generally follows a similar trend to that observed during index construction.
@@
 	% 1. 全局图例 (Legend) - 位置保持不变
-	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/exp/range_legend.pdf}
 
@@
 
-	\subsubsection{Scalability Study}
+	\subsubsection{Robustness}
 
@@
 
-	It is also worth noting that range filtering and attribute filtering are both forms of hybrid query.
+	It is also worth noting that range filtering and attribute filtering are both forms of hybrid queries.
 However, aside from vector databases and ACORN, few existing algorithms support both modalities simultaneously.

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 
-		\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN Search Algorithms}}
+		\caption{\textcolor{orange}{Overview of AF-ANN and RF-ANN Search Algorithms}}
 		\small
@@
 		 \\ \hline
-		\multirow{6}{*}{\textbf{AF}} 
+%		\multirow{6}{*}{\centering\textbf{AF}} 
+		\multirow{6}{*}{\raisebox{4ex}{\textbf{AF}}}
 		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
@@
 		\textcolor{orange}{
-		\textit{Win}: WinFilter, \textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana. 
+		\textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana, \textit{Win}: WinFilter.
 		\textit{AND} / \textit{OR}: Whether the algorithm supports the corresponding logical operations.
@@
 		\textit{Base}: Underlying ANN index structure used.}
-		\textsuperscript{A} Post-filtering, 
-		\textsuperscript{B} Pre-filtering, 
-		\textsuperscript{C} Simultaneous filtering, 
-		\textsuperscript{Y} Support, 
-		\textsuperscript{N} Unsupport. 
+		\textit{A}: Post-filtering, 
+		\textit{B}: Pre-filtering, 
+		\textit{C}: Simultaneous filtering, 
+		\textit{Y}: Support, 
+		\textit{N}: Unsupport. 
 		\end{minipage}}

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 For instance, filtering clothes priced between 100 and 200.
-To meet these application demands, hybrid querying \cite{JD-e-commerce, analyticdb} techniques emerge.
+To meet these application demands, hybrid querying techniques \cite{JD-e-commerce, analyticdb} emerge.
 Hybrid queries integrate vector retrieval with conditional filtering, optimizing their interaction to significantly enhance efficiency and flexibility in complex query scenarios.
@@
 	\subsection{Motivation}
-
-	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute filtering ~\cite{NHQ,diskann} and range filtering algorithms \cite{serf,iRangeGraph}.
+	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute filtering algorithms~\cite{NHQ,diskann} and range filtering algorithms~\cite{serf,iRangeGraph}.
+In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely relates to structured data.
+For attribute filtering algorithms, \textcolor{violet}{factors such as the number of attributes and attribute selectivity~\cite{analyticdb,milvus} significantly impact algorithm performance.} As for range filtering algorithms, the size of the query range and the characteristics of different datasets play an important role in determining algorithm performance.
+
+	\textcolor{violet}{Although existing works~\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking.
+Despite BigANN 2023~\cite{bigann2023} evaluates the performance of some hybrid query algorithms, it still presents the following notable limitations:
+	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods.
+	2) It only uses a single dataset and focuses solely on single-attribute and dual-attribute query scenarios, while not considering the impact of attribute selectivity on query performance.
+	3) It only simply compares the query speed and recall of different algorithms, but does not consider key metrics such as the time and space overhead of each algorithm, and also does not deeply analyze the specific reasons for algorithm performance.}
+
+	\textcolor{violet}{To fill this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
+
+%	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute filtering ~\cite{NHQ,diskann} and range filtering algorithms \cite{serf,iRangeGraph}.
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
@@
 As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.
-
-	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some ANN algorithms, it presents several notable limitations:
-	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. 
-	%	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
-	2) It focuses only on single-attribute and dual-attribute query scenarios. 
-	%	\sout{neglecting the more complex demands of multi-attribute queries.
+%	
+%	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some ANN algorithms, it presents several notable limitations:
+%	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. 
+%	%	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
+%	2) It focuses only on single-attribute and dual-attribute query scenarios. 
+%	%	\sout{neglecting the more complex demands of multi-attribute queries.
 In real-world applications, an object typically involves multiple attributes.}\textcolor{blue}{ \sout{For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}}
-	3) It does not evaluate algorithm performance under different attribute distributions. 
-	%	\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}
-
+%	3) It does not evaluate algorithm performance under different attribute distributions. 
+%	%	\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}
+%	
 %	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-%	To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
+%%	To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
 Additionally, we further assess the robustness of each algorithm under varying conditions.
-
-	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited. 
-	\textcolor{orange}{%Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
-	Although existing works\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
-	To address this gap, we carry out the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+%	
+%	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited. 
+%	\textcolor{orange}{%Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
+%	Although existing works\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
+%	To address this gap, we carry out the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
 Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
-
+%	
 	\subsection{Our Contributions}
@@
 	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-We design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
-\textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large 100M dataset and 2 multi-modal datasets.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying selectivity, number of attributes participating in index construction, and number of query attributes.} \textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large-scale dataset and 2 multi-modal datasets.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 	\noindent\textbf{\underline{IVF.}} 
-	\textcolor{violet}{IVF divides data into multiple clusters through clustering (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
+	\textcolor{violet}{IVF divides data into multiple clusters through through a clustering algorithm (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
 During querying, algorithms search only within the few clusters closest to the query point, which reduces computational load.}
@@
 
-		\caption{\textcolor{orange}{Overview of AF-ANN and RF-ANN Search Algorithms}}
+		\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN Search Algorithms}}
 		\small
@@
 		 \\ \hline
-%		\multirow{6}{*}{\centering\textbf{AF}} 
-		\multirow{6}{*}{\raisebox{4ex}{\textbf{AF}}}
+		\multirow{6}{*}{\textbf{AF}} 
 		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
@@
 		\textcolor{orange}{
-		\textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana, \textit{Win}: WinFilter.
+		\textit{Win}: WinFilter, \textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana. 
 		\textit{AND} / \textit{OR}: Whether the algorithm supports the corresponding logical operations.
@@
 		\textit{Base}: Underlying ANN index structure used.}
-		\textit{A}: Post-filtering, 
-		\textit{B}: Pre-filtering, 
-		\textit{C}: Simultaneous filtering, 
-		\textit{Y}: Support, 
-		\textit{N}: Unsupport. 
+		\textsuperscript{A} Post-filtering, 
+		\textsuperscript{B} Pre-filtering, 
+		\textsuperscript{C} Simultaneous filtering, 
+		\textsuperscript{Y} Support, 
+		\textsuperscript{N} Unsupport. 
 		\end{minipage}}
@@
 
-		\textit{\textbf{Search peak memory.}}  
+		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}  
 		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, the peak memory usage during search generally follows a similar trend to that observed during index construction.
@@
 	% 1. 全局图例 (Legend) - 位置保持不变
-	\includegraphics[width=0.8\textwidth]{figures/exp/range_legend.pdf}
+	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}
 
@@
 
-	\subsubsection{Robustness}
+	\subsubsection{Scalability Study}
 

### 2025-07-30 Revision/response.tex
1
change response

--- 2025-07-30 Revision/response.tex
@@
 We agree that the original figure had readability issues.
-We have first improved the readability of the attribute selectivity Figure~\ref{fig:attribute_selectivity} by adding comparative legends for each algorithm and standardizing the y-axis scales across different subplots.
-
-Furthermore, based on your feedback, we have carefully revised and reanalyzed the experimental sections related to “attribute distribution” and “attribute selectivity” in the paper.
+Based on your feedback, we have carefully revised and reanalyzed the experimental sections related to “attribute distribution” and “attribute selectivity” in the paper.
 
@@
 
-%For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we added performance rankings for each algorithm across different selectivity levels in the figure.
+For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we added performance rankings for each algorithm across different selectivity levels in the figure.
 This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
@@
 
-	\begin{figure*}
+\begin{figure*}[t]  % 可改为 [b] 放在页面底部
 	\centering
-
-	% 第一行：单独一张大图
-	\begin{subfigure}{\textwidth}
-		\centering
-
-		\includegraphics[width=0.95\textwidth]{fig/exp_5_2_1.pdf}
-		\caption{Algorithms Optimized for Low AS}
-		\label{fig:exp_5_2_1}
-	\end{subfigure}
-
-	\vfill % 增加垂直间距
-
-	% 第二行：两张子图，左侧宽度是右侧的两倍
-	\begin{subfigure}{0.627\textwidth} % 2/3 宽度
-		\centering
-
-		\includegraphics[width=0.96\textwidth]{fig/exp_5_2_2.pdf}
-		\caption{Algorithms Optimized for High AS}
-		\label{fig:exp_5_2_2}
-	\end{subfigure}
-	\hspace{1mm} % 增加水平间距
-	\begin{subfigure}{0.33\textwidth} % 1/3 宽度
-		\centering
-
-		\includegraphics[width=0.96\textwidth]{fig/exp_5_2_3.pdf}
-		\caption{Algorithms Insensitive to AS}
-		\label{fig:exp_5_2_3}
-	\end{subfigure}
-
+%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
 	\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
@@
 \end{figure*}
+
 \begin{figure}[htbp]
@@
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%
@@
 	\includegraphics[width=\linewidth]{fig/searchMem/label_memory_comparison.pdf}
-	\caption{Attribute filtering search peak memory}
+	\caption{Attribute Filtering Search Peak Memory}
 	\label{fig:search_memory_mb_comparison}
@@
 	\includegraphics[height=2.5cm]{fig/searchMem/range_memory_comparison.pdf}
-	\caption{Range filtering search peak memory}
+	\caption{Range Filtering Search Peak Memory}
 	\label{fig:rangeFilter_search_memory_mb}
@@
 In particular, StitchedVamana performs poorly on Deep100M.
-\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
 %\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
@@
 \textbf{Response:} I really appreciate your suggestion.
-Current hybrid search algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
+Current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
 However, our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
@@
 \textbf{Response:} 
-Thank you for your feedback. We have improved the readability of the two figures in Section 4.2.3, and please see Meta R1 for details.
+Thank you for your feedback. We have resolved this issue;For more  details,please see Meta R1 .
 
@@
 The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M.
-\textbf{(Please see Section 4.2.1, and the "Single-Attribute Index Construction and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
+\textbf{(Please see Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
 

### 2025-07-30 Revision/response.tex

--- 2025-07-30 Revision/response.tex
@@
 	\centering
-	\includegraphics[width=0.98\linewidth]{fig/attribute_legend.pdf}
+	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
 	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}

### 2025-07-30 Revision/response.tex
Update response.tex

@@
 Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately.
-\textbf{(Please see Section 4.1.1, Section 4.2.4 and Secntion 4.3.4, highlighted in blue in the revised manuscript.)
+\textbf{(Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)
 	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
@@
 
-Section 4.2.4: \textcolor{blue}{
+Section 4.2.3: \textcolor{blue}{
 	"We conducted experiments on the text2image-mix dataset.
@@
 
-Section 4.3.4:\textcolor{blue}{
+Section 4.3.3:\textcolor{blue}{
 		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.
@@
 The detailed parameter configurations can be found in our public code repository.
-(\textbf{Please see Section 4.1.4, highlighted in blue in the revised manuscript.})
+(\textbf{Please see Section 4.1.3, highlighted in blue in the revised manuscript.})
 
 	\textcolor{blue}{
-"In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
+%"In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
 For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository."}
+Regarding experimental parameter selection, we adopted the recommended settings from original papers when available.
+For datasets without suggested parameters, we experimented with different configurations and selected the optimal one for final evaluation.
+Due to the extensive number of datasets and algorithms involved, specific parameters are not listed individually but are provided in our code repository.}
 
@@
 
-In response to the large difference in index construction time shown in Figure 12a(now 13a), we have revised the paper based on your suggestion.
+In response to the large difference in index construction time shown in Figure 12a (now 13a), we have revised the paper based on your suggestion.
 We added more detailed and in-depth analysis to provide a clearer explanation.

### 2025-07-30 Revision/response.tex
Update response.tex

@@
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
-\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 12b.
+\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 9b.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 For brevity and due to space limitations, we omit further discussion of these redundant results."}
-\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
+\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 12b.
 Our findings remain consistent with those reported in Section 4.2.3.

### 2025-07-30 Revision/response.tex
change response figure

--- 2025-07-30 Revision/response.tex
@@
 It is a more complex multimodal dataset.
-As shown in Figure 12, although the queries are more complex, UNG and NHQ still perform the best.
+As shown in Figure 9a, although the queries are more complex, UNG and NHQ still perform the best.
 CAPS is the next best.
@@
 This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
-	In contrast, the text2image dataset shown in Figure 11 is different.
+	In contrast, the text2image dataset shown in Figure 9a is different.
 The queries and the dataset are from different modalities.
@@
 Section 4.3.4:\textcolor{blue}{
-		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.
-As shown in Figure 15, the algorithms still perform the worst on multimodal datasets like Text2Image.
+		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 12a is also consistent with the single-modality results in Figure 14.
+As shown in Figure 11, the algorithms still perform the worst on multimodal datasets like Text2Image.
 This is because these range query algorithms are almost graph-based.
@@
 
-In response to the large difference in index construction time shown in Figure 12a(now 13a), we have revised the paper based on your suggestion.
+In response to the large difference in index construction time shown in Figure 12a(now 10a), we have revised the paper based on your suggestion.
 We added more detailed and in-depth analysis to provide a clearer explanation.
@@
 
-Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c(now 13c) is very insightful.
+Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c(now 10c) is very insightful.
 Initially, we hesitated to include the peak memory usage of databases (such as Milvus) because they are full systems that run continuously and contain many components.

### 2025-07-30 Revision/response.tex

--- 2025-07-30 Revision/response.tex
@@
 
-Section 4.2.3: \textcolor{blue}{
+Section 4.2.4: \textcolor{blue}{
 	"We conducted experiments on the text2image-mix dataset.
@@
 
-Section 4.3.3:\textcolor{blue}{
-		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.
-As shown in Figure 15, the algorithms still perform the worst on multimodal datasets like Text2Image.
+Section 4.3.4:\textcolor{blue}{
+		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 12a is also consistent with the single-modality results in Figure 14.
+As shown in Figure 11, the algorithms still perform the worst on multimodal datasets like Text2Image.
 This is because these range query algorithms are almost graph-based.
@@
 
-In response to the large difference in index construction time shown in Figure 12a (now 13a), we have revised the paper based on your suggestion.
+In response to the large difference in index construction time shown in Figure 12a(now 10a), we have revised the paper based on your suggestion.
 We added more detailed and in-depth analysis to provide a clearer explanation.

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying selectivity, number of attributes participating in index construction, and number of query attributes.} \textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large-scale dataset and 2 multi-modal datasets.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying vector datasets, number of attributes participating in index construction, number of query attributes, and selectivity.
+Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and 2 multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
+	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 9 real-world datasets.
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
@@
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
+	We benchmark algorithms that support range filtering on 5 real-world datasets, using varying query range settings in the experiments.
+The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
+we also further analyze the factors that affect the performance of the range filtering algorithms.
+%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
@@
 %%}
-	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
-These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
+	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid query.
+These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to selectivity.
 Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.
@@
 
-	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown}, Deep1M~\cite{yandex_deep_dataset}, Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
+	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
+
+	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets and their applicable filtering scenarios.
+In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, which is a commonly used metric to quantify dataset hardness.
+Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset to compute LID.
+The higher the LID value, the harder the dataset.
 
 	\textcolor{violet}{The first seven datasets are widely used in existing works.
-As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.}
-
-	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes.
+As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.
+WIT-Real and YT-Audio-Real datasets use real attributes.
 For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
@@
 The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
-
-	Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets and their applicable filtering scenarios.
-In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, which is a commonly used metric to quantify dataset hardness.
-Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset to compute LID.
-The higher the LID value, the harder the dataset.
 
@@
 				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image& RF \\
+				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image& Both \\
 				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio& Both \\
-				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image& Both \\
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image& Both \\

### 2025-07-30 VLDB2026/main.tex
add attr distribution

--- 2025-07-30 VLDB2026/main.tex
@@
 
-	\begin{figure*}
-		\centering
-
-		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
-%		\caption{Single-Attribute Building and Query performance (16 threads)}
-		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (16 Threads)}
-		\label{fig:exp_1_2_SingleLabel_16thread}
-	\end{figure*}
+%	\begin{figure*}
+%		\centering
+%		
+%		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
+%%		\caption{Single-Attribute Building and Query performance (16 threads)}
+%		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (16 Threads)}
+%		\label{fig:exp_1_2_SingleLabel_16thread}
+%	\end{figure*}
 
@@
 
-	\textcolor{violet}{\textit{Multi-Thread Search.} As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, under multi-threading, all algorithms except Puck show similar improvements, with UNG continuing to maintain the best performance.
+%	\textcolor{violet}{\textit{Multi-Thread Search.} As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, under multi-threading, all algorithms except Puck show similar improvements, with UNG continuing to maintain the best performance.
 Puck achieves significant performance improvements in multi-threaded scenarios, delivering near-linear speedup by processing each query independently with a thread-local search context.
@@
 
-%	\begin{figure*}
+	\begin{figure*}
+	\centering
+
+	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
+	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
+	\label{fig:exp_3_1}
+
+%	\footnotesize{
+%	\begin{center}
+%			\begin{minipage}{\linewidth}
 %				\centering	
-%		
-%		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
-%		\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
-%		\label{fig:exp_3_1}
-%		
-%%		\footnotesize{
-%%		\begin{center}
-%%			\begin{minipage}{\linewidth}
-%%				\centering	
-%%				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
-%%			\end{minipage}
-%%		\end{center}
-%%		}
-%	\end{figure*}
+%				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
+%			\end{minipage}
+%	\end{center}
+%	}
+	\end{figure*}
 
@@
 
-%	\textit{\textbf{Attribute Distribution.}} To evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
+	\textit{\textbf{Attribute Distribution.}} To evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
 We evaluate all algorithms under these distributions on each dataset.
@@
 Thus, due to space constraints, we present only the results on SIFT1M.
-%	
-%	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
+
+	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
 \textcolor{cyan}{The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
@@
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
-%	
-%	{\color{blue}{
-%		Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
+
+	{\color{blue}{
+	Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
 For instance, graph-based indexing methods like FilteredVamana and NHQ are prone to degraded connectivity or distorted structures under power-law distributions, where label frequencies are highly imbalanced.
@@
 Faiss, which searches within the nearest clusters, may need to traverse more clusters to find sufficient results when relevant data points are unevenly distributed across clusters due to attribute skew, which impacts performance.
-%		
-%		In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges.
+
+	In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges.
 Milvus, for example, leverages a built-in query optimizer that dynamically determines whether to filter by attributes or search vectors first, based on the selectivity of the query, thus ensuring more robust performance.
@@
 %	\end{figure}
+%
 
 	\textit{\textbf{Single-Attribute Selectivity.}}
-	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
+%	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
 AS is defined as the proportion of data points sharing a given attribute value.
 For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute.
-
-	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
+%	
+%	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
 %	We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
-	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
-
+%	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
+%	
 %	Experimental results show that UNG achieves the best performance across all AS settings, especially at extremely low AS (1\%). 

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 Unless otherwise specified, all experiments were conducted on Server A.}
-	Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}.
-By default, queries run on a single thread.
-We also report results for 16-thread parallelism in specific scenarios.
-We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}.
+	Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}. The queries are all executed on a single thread. 
+%	In addition, We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}.
 	For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance.

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 	\textcolor{cyan}{
-	Regarding experimental parameter selection, we adopted the recommended settings from original papers when available.
-For datasets without suggested parameters, we experimented with different configurations and selected the optimal one for final evaluation.
-Due to the extensive number of datasets and algorithms involved, specific parameters are not listed individually but are provided in our code repository.
+	Regarding experimental parameter selection, we adopt the recommended settings from original papers when available.
+For datasets without suggested parameters, we test different configurations and select relatively optimal ones for final evaluation.
+Due to the large number of datasets and algorithms involved, specific parameters are not individually listed in the paper but are fully provided in our code repository.
 }

### 2025-07-30 VLDB2026/main.tex
delete sec 3  Rangefilter

--- 2025-07-30 VLDB2026/main.tex
@@
 
-	\noindent\textbf{\underline{SeRF} \footnote{\textcolor{blue}{https://github.com/rutgers-db/SeRF}} \cite{serf}} Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
+	\noindent\textbf{\underline{SeRF} \footnote{\textcolor{blue}{https://github.com/rutgers-db/SeRF}} \cite{serf}} 
+%	Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
 2) Filtering the dataset based on attribute ranges before performing ANN search.
@@
 	\noindent\textbf{\underline{WinFilter} \footnote{\textcolor{blue}{https://github.com/JoshEngels/RangeFilteredANN}} \cite{winFilter}}
-	Unlike SeRF, which focuses on graph compression, WinFilter proposes a structural partitioning framework called the $\beta$-Window Search Tree ($\beta$-WST).
+%	Unlike SeRF, which focuses on graph compression, 
+	WinFilter proposes a structural partitioning framework called the $\beta$-Window Search Tree ($\beta$-WST).
 After the dataset is sorted by attribute values, it is partitioned into multiple intervals and organized into a tree structure.
@@
 	\noindent\textbf{\underline{iRange} \footnote{\textcolor{blue}{https://github.com/YuexuanXu7/iRangeGraph}} \cite{iRangeGraph}}
-	To address the query efficiency degradation caused by the graph compression in SeRF, iRange adopts a more flexible strategy.
+%	To address the query efficiency degradation caused by the graph compression in SeRF, iRange adopts a more flexible strategy.
 	%Rather than prebuilding indexes for all possible ranges, it dynamically assembles a query-specific subgraph at runtime.
@@
 	\noindent\textbf{\underline{DSG} \footnote{\textcolor{blue}{https://github.com/rutgers-db/DynamicSegmentGraph}} \cite{DSG}}
-	Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets.
-SeRF allows incremental insertion but requires ordered attributes.
+%	Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets. SeRF allows incremental insertion but requires ordered attributes. 
 	DSG introduces the first dynamic RF-ANN framework supporting data insertion with unordered attributes while maintaining efficient range filtering.
@@
 	\noindent\textbf{\underline{UNIFY} \footnote{\textcolor{blue}{https://github.com/sjtu-dbgroup/UNIFY}} \cite{UNIFY}}
-	Unlike DSG, which relies on rectangle trees and range-aware edges, UNIFY adopts a segmentation-based approach and proposes a range query index structure.
+%	Unlike DSG, which relies on rectangle trees and range-aware edges, UNIFY adopts a segmentation-based approach and proposes a range query index structure. 
 	UNIFY introduces the Segmented Inclusive Graph (SIG), which partitions the dataset into segments by attribute and constructs an independent neighbor graph for each segment.
@@
 Unless otherwise specified, all experiments were conducted on Server A.}
-	Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}. The queries are all executed on a single thread. 
-%	In addition, We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}.
+	Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}.
+By default, queries run on a single thread.
+We also report results for 16-thread parallelism in specific scenarios.
+We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}.
 For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance.

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 This integration ensures that the index reflects both vector similarity and attribute constraints.
-Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.
+%	Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.
 	Filtered-DiskANN proposes 2 indexes:  
@@
 	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
-	CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
-	It introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
-CAPS adopts a two-level partitioning strategy:
+%	CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
+	CAPS introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
+It adopts a two-level partitioning strategy:
 	1) The first level clusters vectors based on similarity using K-Means or learning-based methods such as BLISS.
@@
 	%Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. ACORN addresses this by introducing a predicate-agnostic indexing framework.
-	Pre-filtering methods apply attribute constraints prior to ANN search.
-As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.
-	Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.
+%	ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of prior methods in large-scale or unknown predicate scenarios.
+	\textcolor{orange}{ACORN adopts a predicate-agnostic indexing framework.
+It is based on Hierarchical Navigable Small World (HNSW) \cite{hnsw} and builds a denser hierarchical graph through neighborhood expansion and edge pruning.}
+%	Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning. 
 	During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.
@@
 UNG is proposed to overcome these limitations.It is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.}
-	Similar to ACORN, UNG adopts a pre-filtering strategy and serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.
+	UNG serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.
 It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
@@
 In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
-	Puck also adopts a pre-filtering strategy.
-Developed by Baidu, Puck utilizes two-level quantization for indexing.
+%	Puck also adopts a pre-filtering strategy. Developed by Baidu, 
+	Puck utilizes two-level quantization for indexing.
 It maintains an attribute set for each cluster to track vector attributes.
@@
 	\textcolor{cyan}{
-	Regarding experimental parameter selection, we adopt the recommended settings from original papers when available.
-For datasets without suggested parameters, we test different configurations and select relatively optimal ones for final evaluation.
-Due to the large number of datasets and algorithms involved, specific parameters are not individually listed in the paper but are fully provided in our code repository.
+	Regarding experimental parameter selection, we adopted the recommended settings from original papers when available.
+For datasets without suggested parameters, we experimented with different configurations and selected the optimal one for final evaluation.
+Due to the extensive number of datasets and algorithms involved, specific parameters are not listed individually but are provided in our code repository.
 }

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 This integration ensures that the index reflects both vector similarity and attribute constraints.
-%	Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.
+Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.
 	Filtered-DiskANN proposes 2 indexes:  
@@
 	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
-%	CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
-	CAPS introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
-It adopts a two-level partitioning strategy:
+	CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
+	It introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
+CAPS adopts a two-level partitioning strategy:
 	1) The first level clusters vectors based on similarity using K-Means or learning-based methods such as BLISS.
@@
 	%Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. ACORN addresses this by introducing a predicate-agnostic indexing framework.
-%	ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of prior methods in large-scale or unknown predicate scenarios.
-	\textcolor{orange}{ACORN adopts a predicate-agnostic indexing framework.
-It is based on Hierarchical Navigable Small World (HNSW) \cite{hnsw} and builds a denser hierarchical graph through neighborhood expansion and edge pruning.}
-%	Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning. 
+	Pre-filtering methods apply attribute constraints prior to ANN search.
+As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.
+	Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.
 During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.
@@
 UNG is proposed to overcome these limitations.It is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.}
-	UNG serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.
+	Similar to ACORN, UNG adopts a pre-filtering strategy and serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.
 It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes.
@@
 In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
-%	Puck also adopts a pre-filtering strategy. Developed by Baidu, 
-	Puck utilizes two-level quantization for indexing.
+	Puck also adopts a pre-filtering strategy.
+Developed by Baidu, Puck utilizes two-level quantization for indexing.
 It maintains an attribute set for each cluster to track vector attributes.
@@
 
-%	\begin{figure*}
-%		\centering
-%		
-%		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
-%%		\caption{Single-Attribute Building and Query performance (16 threads)}
-%		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (16 Threads)}
-%		\label{fig:exp_1_2_SingleLabel_16thread}
-%	\end{figure*}
+	\begin{figure*}
+		\centering
+
+		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
+%		\caption{Single-Attribute Building and Query performance (16 threads)}
+		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (16 Threads)}
+		\label{fig:exp_1_2_SingleLabel_16thread}
+	\end{figure*}
 
@@
 	\textit{Single-Thread Search.}  
-	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions, search often requires traversing larger candidate sets or deeper graph paths.
+	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, as recall approaches 1, search often requires traversing larger candidate sets or deeper graph paths.
 This leads to increased computational cost and a sharp QPS drop for most methods.
-Despite this, UNG consistently maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes and searches only within the subgraph formed by points satisfying the filtering conditions, thereby improving query efficiency.}
+Despite this, UNG consistently maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes and searches only within the subgraph formed by points satisfying the filtering conditions, thereby improving query efficiency.
 
 	\textcolor{violet}{NHQ and StitchedVamana also perform well and show similar and stable performance across all datasets.
-This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.}
-
-	\textcolor{violet}{StitchedVamana outperforms FilteredVamana in query efficiency.
-This difference stems from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.}
+This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.} StitchedVamana outperforms FilteredVamana in query efficiency.
+This difference stems from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
 
@@
 
-	\textcolor{violet}{Among all methods, vector database systems (PASE, VBASE, Milvus) show the worst performance.
+	Among all methods, vector database systems (PASE, VBASE, Milvus) show the worst performance.
 These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
-Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.}
-
-%	\textcolor{violet}{\textit{Multi-Thread Search.} As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, under multi-threading, all algorithms except Puck show similar improvements, with UNG continuing to maintain the best performance.
+Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
+
+	\textcolor{violet}{\textit{Multi-Thread Search.} As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, under multi-threading, all algorithms except Puck show similar improvements, with UNG continuing to maintain the best performance.
 Puck achieves significant performance improvements in multi-threaded scenarios, delivering near-linear speedup by processing each query independently with a thread-local search context.
@@
 
-	\begin{figure*}
-	\centering
-
-	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
-	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
-	\label{fig:exp_3_1}
-
-%	\footnotesize{
-%	\begin{center}
-%			\begin{minipage}{\linewidth}
+%	\begin{figure*}
 %		\centering
-%				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
-%			\end{minipage}
-%	\end{center}
-%	}
-	\end{figure*}
+%		
+%		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
+%		\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
+%		\label{fig:exp_3_1}
+%		
+%%		\footnotesize{
+%%		\begin{center}
+%%			\begin{minipage}{\linewidth}
+%%				\centering	
+%%				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
+%%			\end{minipage}
+%%		\end{center}
+%%		}
+%	\end{figure*}
 
@@
 In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
-
-	{\color{blue}{
-	Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
+%	
+%	{\color{blue}{
+%		Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
 For instance, graph-based indexing methods like FilteredVamana and NHQ are prone to degraded connectivity or distorted structures under power-law distributions, where label frequencies are highly imbalanced.
@@
 Faiss, which searches within the nearest clusters, may need to traverse more clusters to find sufficient results when relevant data points are unevenly distributed across clusters due to attribute skew, which impacts performance.
-
-	In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges.
+%		
+%		In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges.
 Milvus, for example, leverages a built-in query optimizer that dynamically determines whether to filter by attributes or search vectors first, based on the selectivity of the query, thus ensuring more robust performance.
@@
 %	\end{figure}
-%
 
 	\textit{\textbf{Single-Attribute Selectivity.}}
-%	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
+	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
 AS is defined as the proportion of data points sharing a given attribute value.
 For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute.
-%	
-%	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
+
+	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
 %	We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
-%	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
-%	
+	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
+
 %	Experimental results show that UNG achieves the best performance across all AS settings, especially at extremely low AS (1\%). 

### 2025-07-30 VLDB2026/main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 
-	\textcolor{violet}{Among all methods, vector database systems (PASE, VBASE, Milvus) show the worst performance.
+	Among all methods, vector database systems (PASE, VBASE, Milvus) show the worst performance.
 These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
-Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.}
+Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
 

### 2025-07-30 Revision/response.tex
1

--- 2025-07-30 Revision/response.tex
@@
 It is a more complex multimodal dataset.
-As shown in Figure 9a, although the queries are more complex, UNG and NHQ still perform the best.
+As shown in Figure 12, although the queries are more complex, UNG and NHQ still perform the best.
 CAPS is the next best.
@@
 This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
-	In contrast, the text2image dataset shown in Figure 9a is different.
+	In contrast, the text2image dataset shown in Figure 11 is different.
 The queries and the dataset are from different modalities.
@@
 Section 4.3.4:\textcolor{blue}{
-		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 12a is also consistent with the single-modality results in Figure 14.
-As shown in Figure 11, the algorithms still perform the worst on multimodal datasets like Text2Image.
+		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14.
+As shown in Figure 15, the algorithms still perform the worst on multimodal datasets like Text2Image.
 This is because these range query algorithms are almost graph-based.
@@
 	\includegraphics[width=\linewidth]{fig/searchMem/label_memory_comparison.pdf}
-	\caption{Attribute Filtering Search Peak Memory}
+	\caption{Attribute filtering search peak memory}
 	\label{fig:search_memory_mb_comparison}
@@
 	\includegraphics[height=2.5cm]{fig/searchMem/range_memory_comparison.pdf}
-	\caption{Range Filtering Search Peak Memory}
+	\caption{Range filtering search peak memory}
 	\label{fig:rangeFilter_search_memory_mb}
@@
 In particular, StitchedVamana performs poorly on Deep100M.
-\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.4, highlighted in blue in the revised manuscript.)}
 %\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
@@
 \textbf{Response:} I really appreciate your suggestion.
-Current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
+Current hybrid search algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
 However, our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
@@
 	\hspace*{8pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-	\includegraphics[width=0.95\columnwidth]{fig/review_real_syn_legend.pdf} % 图例图片路径
+	\includegraphics[width=0.95\columnwidth]{fig/attribute_legend.pdf} % 图例图片路径
 
@@
 \textbf{Response:} 
-Thank you for your feedback. We have resolved this issue;For more  details,please see Meta R1 .
+Thank you for your feedback. We have improved the readability of the two figures in Section 4.2.3, and please see Meta R1 for details.
 
@@
 
-In response to the large difference in index construction time shown in Figure 12a(now 10a), we have revised the paper based on your suggestion.
+In response to the large difference in index construction time shown in Figure 12a(now 13a), we have revised the paper based on your suggestion.
 We added more detailed and in-depth analysis to provide a clearer explanation.
@@
 
-Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c(now 10c) is very insightful.
+Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c(now 13c) is very insightful.
 Initially, we hesitated to include the peak memory usage of databases (such as Milvus) because they are full systems that run continuously and contain many components.

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 		\centering
-
+		\setlength{\belowcaptionskip}{-0.cm}
 		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
@@
 	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying vector datasets, number of attributes participating in index construction, number of query attributes, and selectivity.
-Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and 2 multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying selectivity, number of attributes participating in index construction, and number of query attributes.} \textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large-scale dataset and 2 multi-modal datasets.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 9 real-world datasets.
+	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets.
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
@@
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-	We benchmark algorithms that support range filtering on 5 real-world datasets, using varying query range settings in the experiments.
-The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-we also further analyze the factors that affect the performance of the range filtering algorithms.
-%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
+	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
@@
 %%}
-	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid query.
-These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to selectivity.
+	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries.
+These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution.
 Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.
@@
 
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.2cm}		
 		\caption{Graph Index and IVF Index}
@@
 
-	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
+	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown}, Deep1M~\cite{yandex_deep_dataset}, Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
+
+	\textcolor{violet}{The first seven datasets are widely used in existing works.
+As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.}
+
+	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes.
+For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
+The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
+
+	\textcolor{violet}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
+The Text2Image dataset includes two versions.
+The original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set.
+The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
 
@@
 The higher the LID value, the harder the dataset.
-
-	\textcolor{violet}{The first seven datasets are widely used in existing works.
-As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.
-WIT-Real and YT-Audio-Real datasets use real attributes.
-For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
-The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
-
-	\textcolor{violet}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
-The Text2Image dataset includes two versions.
-The original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set.
-The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
 
@@
 				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image& RF \\
+				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio& Both \\
 				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image& Both \\
-				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio& Both \\
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image& Both \\
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the six datasets shown on the left of Figure~\ref{fig:build_index_comparison}, and 64 threads on the large-scale Deep100M dataset, shown on the right.}
+\textcolor{orange}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets.
+Notably, the VBASE and PASE algorithms only support single-threaded construction.}
 
@@
 \textit{\textbf{Index construction time.}}
-\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longest build times are mainly PASE, VBASE, and ACORN-$\gamma$.
+%\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longest build times are mainly PASE, VBASE, and ACORN-$\gamma$.
 PASE and VBASE only support single-threaded builds.
@@
 }
-
-\textcolor{orange}{On the large-scale dataset Deep100M, besides the three methods already mentioned, we also observe that algorithms based on Vamana (such as FilteredDiskANN and UNG) exhibit significantly increased construction time.
-Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
-In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
+\textcolor{orange}{On the regular-scale datasets (Figure~\ref{fig:build_time_comparison_query1}, left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
+This is because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency.
+In contrast, VBASE uses full-memory builds and is therefore comparatively faster.
+Among the multi-threaded algorithms, ACORN-$\gamma$ is the slowest because it needs to expand the neighbor list and evaluate a large number of candidates.
+Its build time on some datasets even exceeds that of the single-threaded VBASE.
+}
+
+\textcolor{orange}{On the large-scale dataset Deep100M(Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
+This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
+In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size.This is because their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
 
@@
 	\textit{Single-Thread Search.}  
-	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, as recall approaches 1, search often requires traversing larger candidate sets or deeper graph paths.
+	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions, search often requires traversing larger candidate sets or deeper graph paths.
 This leads to increased computational cost and a sharp QPS drop for most methods.
-Despite this, UNG consistently maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes and searches only within the subgraph formed by points satisfying the filtering conditions, thereby improving query efficiency.
+Despite this, UNG consistently maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes and searches only within the subgraph formed by points satisfying the filtering conditions, thereby improving query efficiency.}
 
 	\textcolor{violet}{NHQ and StitchedVamana also perform well and show similar and stable performance across all datasets.
-This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.} StitchedVamana outperforms FilteredVamana in query efficiency.
-This difference stems from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
+This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.}
+
+	\textcolor{violet}{StitchedVamana outperforms FilteredVamana in query efficiency.
+This difference stems from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.}
 
@@
 
-	Among all methods, vector database systems (PASE, VBASE, Milvus) show the worst performance.
+	\textcolor{violet}{Among all methods, vector database systems (PASE, VBASE, Milvus) show the worst performance.
 These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
-Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
+Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.}
 

### 2025-07-30 VLDB2026/main.tex
change third lib

@@
 	\subsection{Vector Libraries and Databases}
-
-	The vector libraries and databases discussed in the following are not explicitly designed for hybrid queries, but they support both attribute filtering and range filtering.
+	Many existing vector libraries, such as Faiss, and databases, such as Milvus, VBASE, and PASE, are designed specifically for ANN search, but they also support attribute filtering and range queries.
+We also experimented with them.
+However, since these libraries and databases do not rely on a single algorithm, their internal implementations are complex, using multiple methods and have detailed third-party documentation, so we will not elaborate on them here.
+
+%	The vector libraries and databases discussed in the following are not explicitly designed for hybrid queries, but they support both attribute filtering and range filtering.
 Additionally, all the functionalities shown in Table 1 are also supported.
-
-	\noindent\textbf{\underline{Faiss} \footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
-	Faiss is a library designed for efficient similarity search.
+%	
+%	\noindent\textbf{\underline{Faiss} \footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
+%	Faiss is a library designed for efficient similarity search.
 It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.
@@
 This strategy groups queries with the same filter conditions, performs filtering once per group, and then uses efficient matrix operations to perform batch vector similarity calculations.
-
-	\noindent\textbf{\underline{PASE} \footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase}}
-	PASE is a vector indexing plugin for the PostgreSQL database \cite{postgresql13.4}, supporting two index types: IVF\_Flat \cite{johnson2019billion} and HNSW.
+%	
+%	
+%	\noindent\textbf{\underline{PASE} \footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase}}
+%	PASE is a vector indexing plugin for the PostgreSQL database \cite{postgresql13.4}, supporting two index types: IVF\_Flat \cite{johnson2019billion} and HNSW.
 By leveraging database capabilities, PASE enables both attribute filtering and range filtering.
@@
 However, since the candidate set has a fixed size, low-selectivity filters may result in fewer than $k$ results being returned.
-
-	\noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}}
-	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
+%	
+%	
+%	\noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}}
+%	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
 We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality.
@@
 This avoids the issue in PASE where the final result set may contain fewer than $k$ results.
-
-	\noindent\textbf{\underline{Milvus} \footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus}}
-	Unlike PASE and VBASE, which are database extensions, Milvus is an vector database purpose-built for large-scale similarity search.
+%	
+%	\noindent\textbf{\underline{Milvus} \footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus}}
+%	Unlike PASE and VBASE, which are database extensions, Milvus is an vector database purpose-built for large-scale similarity search.
 It supports multiple index types, including HNSW, IVF\_Flat, and IVF\_PQ, and provides extensive optimization for real-world deployment.

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 		\centering
-		\setlength{\belowcaptionskip}{-0.cm}
+
 		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
@@
 
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.2cm}		
 		\caption{Graph Index and IVF Index}
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{orange}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets.
-Notably, the VBASE and PASE algorithms only support single-threaded construction.}
+\textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the six datasets shown on the left of Figure~\ref{fig:build_index_comparison}, and 64 threads on the large-scale Deep100M dataset, shown on the right.}
 
@@
 \textit{\textbf{Index construction time.}}
-%\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longest build times are mainly PASE, VBASE, and ACORN-$\gamma$.
+\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longest build times are mainly PASE, VBASE, and ACORN-$\gamma$.
 PASE and VBASE only support single-threaded builds.
@@
 }
-\textcolor{orange}{On the regular-scale datasets (Figure~\ref{fig:build_time_comparison_query1}, left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
-This is because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency.
-In contrast, VBASE uses full-memory builds and is therefore comparatively faster.
-Among the multi-threaded algorithms, ACORN-$\gamma$ is the slowest because it needs to expand the neighbor list and evaluate a large number of candidates.
-Its build time on some datasets even exceeds that of the single-threaded VBASE.
-}
-
-\textcolor{orange}{On the large-scale dataset Deep100M(Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
-This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
-In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size.This is because their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
+
+\textcolor{orange}{On the large-scale dataset Deep100M, besides the three methods already mentioned, we also observe that algorithms based on Vamana (such as FilteredDiskANN and UNG) exhibit significantly increased construction time.
+Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
+In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
 
@@
 
-	\textit{\textbf{Attribute Distribution.}} To evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
-We evaluate all algorithms under these distributions on each dataset.
-The performance differences observed for the same algorithm across different datasets are relatively minor.
-Thus, due to space constraints, we present only the results on SIFT1M.
-
+	\textit{\textbf{Attribute Distribution.}} To evaluate the impact of attribute distribution, we generate base and query attributes \textcolor{orange}{on the SIFT dataset using four representative distributions: long-tail, normal, power-law, and uniform.}
+%	with four representative distributions—long-tail, normal, power-law, and uniform—across six datasets. 
+%	Since performance differences across datasets are small, we report results on SIFT1M due to space limits.
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
 \textcolor{cyan}{The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
-In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.}
+%	Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
 
@@
 	\textit{\textbf{Single-Attribute Selectivity.}}
-%	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
-AS is defined as the proportion of data points sharing a given attribute value.
-For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute.
-%	
-%	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
+	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency.
+%	, as the algorithm must efficiently identify data points matching specific attributes within large datasets. 
+	AS is defined as the proportion of data points sharing a given attribute value. For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute. 
+	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
 %	We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
-%	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
+	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
 %	

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 	\subsection{Vector Libraries and Databases}
-	Many existing vector libraries, such as Faiss, and databases, such as Milvus, VBASE, and PASE, are designed specifically for ANN search, but they also support attribute filtering and range queries.
-We also experimented with them.
-However, since these libraries and databases do not rely on a single algorithm, their internal implementations are complex, using multiple methods and have detailed third-party documentation, so we will not elaborate on them here.
-
-%	The vector libraries and databases discussed in the following are not explicitly designed for hybrid queries, but they support both attribute filtering and range filtering.
+
+	The vector libraries and databases discussed in the following are not explicitly designed for hybrid queries, but they support both attribute filtering and range filtering.
 Additionally, all the functionalities shown in Table 1 are also supported.
-%	
-%	\noindent\textbf{\underline{Faiss} \footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
-%	Faiss is a library designed for efficient similarity search.
+
+	\noindent\textbf{\underline{Faiss} \footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
+	Faiss is a library designed for efficient similarity search.
 It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.
@@
 This strategy groups queries with the same filter conditions, performs filtering once per group, and then uses efficient matrix operations to perform batch vector similarity calculations.
-%	
-%	
-%	\noindent\textbf{\underline{PASE} \footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase}}
-%	PASE is a vector indexing plugin for the PostgreSQL database \cite{postgresql13.4}, supporting two index types: IVF\_Flat \cite{johnson2019billion} and HNSW.
+
+	\noindent\textbf{\underline{PASE} \footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase}}
+	PASE is a vector indexing plugin for the PostgreSQL database \cite{postgresql13.4}, supporting two index types: IVF\_Flat \cite{johnson2019billion} and HNSW.
 By leveraging database capabilities, PASE enables both attribute filtering and range filtering.
@@
 However, since the candidate set has a fixed size, low-selectivity filters may result in fewer than $k$ results being returned.
-%	
-%	
-%	\noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}}
-%	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
+
+	\noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}}
+	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
 We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality.
@@
 This avoids the issue in PASE where the final result set may contain fewer than $k$ results.
-%	
-%	\noindent\textbf{\underline{Milvus} \footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus}}
-%	Unlike PASE and VBASE, which are database extensions, Milvus is an vector database purpose-built for large-scale similarity search.
+
+	\noindent\textbf{\underline{Milvus} \footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus}}
+	Unlike PASE and VBASE, which are database extensions, Milvus is an vector database purpose-built for large-scale similarity search.
 It supports multiple index types, including HNSW, IVF\_Flat, and IVF\_PQ, and provides extensive optimization for real-world deployment.
@@
 CAPS performs as well as Puck.
-In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
+In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify two primary reasons.
+First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
+Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
+	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
-		\caption{\textcolor{violet}{Time and Space Overhead}}
+		\caption{\textcolor{violet}{Time and Space Overhead (Attribute Filtering)}}
 		\label{fig:build_index_comparison}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
-		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (Single Thread) }
+		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query }
 		\label{fig:exp_1_1_SingleLabel_1thread}
@@
 	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
-	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
+	\caption{
+		 \centering
+		Effect of Attribute Distribution on Query Performance \\
+		(Strong: robust to attribute distribution shifts; Weak: sensitive to attribute distribution shifts.)}
+
 	\label{fig:exp_3_1}
@@
 
-		\caption{Different AS under the Same Algorithm}
+		\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
 		\label{fig:exp_5_2_combined}
@@
 	% 5. 全局总标题
-	\caption{\textcolor{violet}Scalability Study——Attribute}
+	\caption{\textcolor{violet}Scalability Study (Attribute Filtering)}
 	\label{fig:TrinityExtension——Attribution_main}
@@
 %		\caption{Time and space overhead of index construction}
-		\caption{\textcolor{violet}{Time and Space Overhead}}
+		\caption{\textcolor{violet}{Time and Space Overhead (Range Filtering)}}
 		\label{fig:rangeFilter_build_index_comparison}
@@
 	% 5. 全局总标题
-	\caption{\textcolor{violet}Scalability Study——Range}
+	\caption{\textcolor{violet}Scalability Study (Range Filtering)}
 	\label{fig:TrinityExtension——Attribution_main}

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
-		\caption{\textcolor{violet}{Time and Space Overhead (Attribute Filtering)}}
+		\caption{\textcolor{violet}{Time and Space Overhead}}
 		\label{fig:build_index_comparison}
@@
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
-		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query }
+		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (Single Thread) }
 		\label{fig:exp_1_1_SingleLabel_1thread}
@@
 
-	\textcolor{violet}{Puck and CAPS perform relatively well, indicating that IVF-based methods remain very promising for hybrid queries.}
+	\textcolor{violet}{Additionally, Puck and CAPS also perform relatively well.
+They further reduce the search space on IVF indexes by using attribute partitioning, thereby achieving solid search performance.}
 
@@
 	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
-	\caption{
-		 \centering
-		Effect of Attribute Distribution on Query Performance \\
-		(Strong: robust to attribute distribution shifts; Weak: sensitive to attribute distribution shifts.)}
-
+	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
 	\label{fig:exp_3_1}
@@
 
-	\textit{\textbf{Attribute Distribution.}} To evaluate the impact of attribute distribution, we generate base and query attributes \textcolor{orange}{on the SIFT dataset using four representative distributions: long-tail, normal, power-law, and uniform.}
-%	with four representative distributions—long-tail, normal, power-law, and uniform—across six datasets. 
-%	Since performance differences across datasets are small, we report results on SIFT1M due to space limits.
+	\textit{\textbf{Attribute Distribution.}} To evaluate performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1.
+We evaluate all algorithms under these distributions on each dataset.
+The performance differences observed for the same algorithm across different datasets are relatively minor.
+Thus, due to space constraints, we present only the results on SIFT1M.
+
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
 \textcolor{cyan}{The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.}
-%	Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts.
+In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
 
@@
 	\textit{\textbf{Single-Attribute Selectivity.}}
-	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency.
-%	, as the algorithm must efficiently identify data points matching specific attributes within large datasets. 
-	AS is defined as the proportion of data points sharing a given attribute value. For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute. 
-	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
+%	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency, as the algorithm must efficiently identify data points matching specific attributes within large datasets.
+AS is defined as the proportion of data points sharing a given attribute value.
+For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute.
+%	
+%	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
 %	We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
-	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
+%	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
 %	
@@
 
-		\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
+		\caption{Different AS under the Same Algorithm}
 		\label{fig:exp_5_2_combined}
@@
 	% 5. 全局总标题
-	\caption{\textcolor{violet}Scalability Study (Attribute Filtering)}
+	\caption{\textcolor{violet}Scalability Study——Attribute}
 	\label{fig:TrinityExtension——Attribution_main}
@@
 %		\caption{Time and space overhead of index construction}
-		\caption{\textcolor{violet}{Time and Space Overhead (Range Filtering)}}
+		\caption{\textcolor{violet}{Time and Space Overhead}}
 		\label{fig:rangeFilter_build_index_comparison}
@@
 	% 5. 全局总标题
-	\caption{\textcolor{violet}Scalability Study (Range Filtering)}
+	\caption{\textcolor{violet}Scalability Study——Range}
 	\label{fig:TrinityExtension——Attribution_main}
@@
 In contrast, while databases and the vector search library Faiss support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
-Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed.
-		}
+Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed. }
+
+\textcolor{violet}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic.
+Experiments in this paper also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing.
+Therefore, IVF-based hybrid query methods represent a very promising research direction.}
 

### 2025-07-30 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 
-\textcolor{orange}{On the large-scale dataset Deep100M(Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
+\textcolor{orange}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
 This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 		We conduct experiments on the Text2image-Mix dataset.
-This dataset contains image and text vectors and is a hybrid multimodal dataset.
+This dataset contains image and text vectors and is a hybrid multi-modal dataset.
 As shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
@@
 	\textcolor{blue}{
-		Similar to attribute filtering, the performance of multimodal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
+		Similar to attribute filtering, the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
@@
 	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
-	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
+	\textbf{Robust to Multi-Modal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
 %	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\

### 2025-07-30 VLDB2026/main.tex
Update main.tex

--- 2025-07-30 VLDB2026/main.tex
@@
 	\caption{
-		 \centering
-		Effect of Attribute Distribution on Query Performance \\
-		(Strong: robust to attribute distribution shifts; Weak: sensitive to attribute distribution shifts.)}
+		Effect of Attribute Distribution on Query Performance(Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts.)}
 

### 2025-07-30 VLDB2026/main.tex
change 3.3

@@
 	\subsection{Vector Libraries and Databases}
-	Many existing vector libraries, such as Faiss, and databases, such as Milvus, VBASE, and PASE, are designed specifically for ANN search, but they also support attribute filtering and range queries.
-We also experimented with them.
-However, since these libraries and databases do not rely on a single algorithm, their internal implementations are complex, using multiple methods and have detailed third-party documentation, so we will not elaborate on them here.
+The vector library and databases discussed in the following are not explicitly designed for hybrid query, but they support both attribute filtering and range filtering.
+
+Faiss is an efficient similarity search library.
+It uses an ID selector to filter data before performing approximate nearest neighbor search.
+This supports hybrid search.In Faiss, we use the HQI batch optimization strategy in the IVF index.
+It groups queries with the same filter conditions.
+Each group only runs the filter once.
+It uses efficient matrix operations to compute vector similarity in batches.
+
+PASE is a vector index plugin for PostgreSQL. It uses a "search first, then filter" strategy. But because the candidate set size is fixed, it may not return enough top-k results.
+
+VBASE is also a vector plugin for PostgreSQL. It applies filters during the HNSW index traversal. This ensures enough results.
+
+Milvus is a vector database built for large-scale similarity search. It filters data first, then performs approximate nearest neighbor search. This supports hybrid search.
 
@@
 
-\textcolor{orange}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
+\textcolor{orange}{On the large-scale dataset Deep100M(Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
 This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
@@
 
-	\textcolor{violet}{Additionally, Puck and CAPS also perform relatively well.
-They further reduce the search space on IVF indexes by using attribute partitioning, thereby achieving solid search performance.}
+	\textcolor{violet}{Puck and CAPS perform relatively well, indicating that IVF-based methods remain very promising for hybrid queries.}
 
@@
 CAPS performs as well as Puck.
-In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify two primary reasons.
-First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
-Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
-	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
+In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
 This results in excessive traversal of irrelevant nodes, making it slower than other methods.
@@
 	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
-	\caption{
-		Effect of Attribute Distribution on Query Performance(Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts.)}
-
+	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
 	\label{fig:exp_3_1}
@@
 In contrast, while databases and the vector search library Faiss support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
-Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed. }
-
-\textcolor{violet}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic.
-Experiments in this paper also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing.
-Therefore, IVF-based hybrid query methods represent a very promising research direction.}
+Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed.
+		}
 

### 2025-07-30 Revision/response.tex

--- 2025-07-30 Revision/response.tex
@@
 \textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
-%
-%\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
+
+\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
-%
-%For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure.
+
+For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
 As shown in Figure\ref{fig:attribute_distribution} below.
-\textbf{Response:} Thank you for your valuable suggestions.
+%\textbf{Response:} Thank you for your valuable suggestions.
 We agree that the original figure had readability issues.
 We have first improved the readability of the attribute selectivity Figure~\ref{fig:attribute_selectivity} by adding comparative legends for each algorithm and standardizing the y-axis scales across different subplots.
-
-Furthermore, based on your feedback, we have carefully revised and reanalyzed the experimental sections related to “attribute distribution” and “attribute selectivity” in the paper.
-
-In real-world applications, attribute distributions are often diverse, such as long-tail, uniform, or normal distributions.
+%
+%
+%Furthermore, based on your feedback, we have carefully revised and reanalyzed the experimental sections related to “attribute distribution” and “attribute selectivity” in the paper. 
+%
+%In real-world applications, attribute distributions are often diverse, such as long-tail, uniform, or normal distributions.
 In our initial design, we included multiple attribute distributions to evaluate the robustness of algorithms under different data characteristics.
@@
 Its impact on algorithm performance is ultimately determined by attribute selectivity in each query.
-For example, in a long-tail distribution, querying a common “head” attribute is equivalent to a high attribute selectivity (High AS) case, while querying a rare “tail” attribute is equivalent to a low attribute selectivity (Low AS) case.
-Therefore, by evaluating performance under a range of attribute selectivities (e.g., AS = 1\% to AS = 75\%), we have already covered the effects of different attribute distributions.
+%For example, in a long-tail distribution, querying a common “head” attribute is equivalent to a high attribute selectivity (High AS) case, while querying a rare “tail” attribute is equivalent to a low attribute selectivity (Low AS) case.
+%Therefore, by evaluating performance under a range of attribute selectivities (e.g., AS = 1\% to AS = 75\%), we have already covered the effects of different attribute distributions.
 In this sense, the attribute selectivity experiments provide a unified and quantitative way to reflect the influence of attribute distributions.
-
-We present the results of attribute distribution and attribute selectivity in Figure~\ref{fig:attribute_distribution} and Figure~\ref{fig:attribute_selectivity} , respectively.
+%
+%We present the results of attribute distribution and attribute selectivity in Figure~\ref{fig:attribute_distribution} and Figure~\ref{fig:attribute_selectivity} , respectively.
 The conclusions are highly consistent.
@@
 This is because most queries in a long-tail distribution correspond to high-selectivity attributes, while only a few are low-selectivity, which limits the overall performance.
-
-Moreover, previous studies (e.g., FilteredDiskANN, Milvus) also commonly use attribute selectivity as a key metric for evaluating filtering performance.
-
-Based on these reasons, we decided to remove the attribute distribution experiments and retain only the attribute selectivity analysis.
+%
+%Moreover, previous studies (e.g., FilteredDiskANN, Milvus) also commonly use attribute selectivity as a key metric for evaluating filtering performance.
+%
+%Based on these reasons, we decided to remove the attribute distribution experiments and retain only the attribute selectivity analysis.
 We also removed the original Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret.
@@
 	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
-	\caption{Effect of Attribute Distribution on Query Performance (Strong indicates robustness to attribute distribution shifts, Weak indicates sensitivity)}
+	\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts)}
 	\label{fig:attribute_distribution}
@@
 
-%For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we added performance rankings for each algorithm across different selectivity levels in the figure.
+For performance under different attribute selectivity, to reflect the performance differences of each algorithm under different attribute selectivity, we added performance rankings for each algorithm across different selectivity levels in the figure.
 This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
@@
 
-	\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
+	\caption{Different AS under the Same Algorithm}
 	\label{fig:attribute_selectivity}
 \end{figure*}
-\begin{figure}[htbp]
-	\centering
-	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
-	\caption{Different AS under the Same Algorithm}
-	\label{fig:attribute_selectivity_2}
-\end{figure}
+%\begin{figure}[htbp]
+%	\centering
+%	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
+%	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
+%	\caption{Different AS under the Same Algorithm}
+%	\label{fig:attribute_selectivity_2}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-Section 4.2.4: \textcolor{blue}{
-	"We conducted experiments on the text2image-mix dataset.
-This dataset contains both image and text vectors.
-It is a more complex multimodal dataset.
-As shown in Figure 9a, although the queries are more complex, UNG and NHQ still perform the best.
-CAPS is the next best.
-	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
-The nearest neighbors in the index are often from the same modality because they are closer in distance.
-Therefore, the search results on this dataset are similar to those in Figure 4.
-UNG and NHQ perform the best.
-CAPS clusters based on vector similarity.
-It actually clusters the vectors into the same modality.
-Then it uses attribute filtering to divide the data further.
-This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
-	In contrast, the text2image dataset shown in Figure 9a is different.
-The queries and the dataset are from different modalities.
-The queries are far from the dataset.
-The ground truths are also scattered and not clustered together.
-To find the ground truths, the algorithm often needs to traverse more points.
-This is a greater challenge for the algorithms."
-}
-
-Section 4.3.4:\textcolor{blue}{
+Section 4.2.3: \textcolor{blue}{
+	"We conduct experiments on the Text2image-Mix dataset.
+This dataset contains image and text vectors and is a hybrid multimodal dataset.
+As shown in Figure 9a, UNG and NHQ consistently perform best, followed by CAPS.
+	Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
+In practice, this means that the experiments effectively treat the image and text subsets as separate datasets, since the ground truths for each query belong to the same modality.
+Therefore, the performance on this dataset is similar to the results shown in Figure 4.
+	In contrast, the Text2image dataset shown in Figure 9a is different.
+The query set and the base dataset belong to two completely different modalities.
+Queries are far from the dataset points, and the ground truths are more dispersed.
+To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance."
+}
+
+Section 4.3.3:\textcolor{blue}{
 		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 12a is also consistent with the single-modality results in Figure 14.

### 2025-07-30 VLDB2026/main.tex
1

@@
 
-\textcolor{orange}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
+\textcolor{orange}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (Filtered-DiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
 This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
@@
 For regular-scale datasets, other methods show moderate variation.
-However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.
+However, on large-scale dataset, Graph-based algorithms such as ACORN, Filtered-DiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.
 Overall, IVF-based methods tend to produce more compact indexes.
@@
 
-\textcolor{orange}{The two variants of FilteredDiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
+\textcolor{orange}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
 FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.

### 2025-07-30 VLDB2026/main.tex
Update main.tex

@@
 
-Faiss is an efficient similarity search library.
+Faiss\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss} is an efficient similarity search library.
 It uses an ID selector to filter data before performing approximate nearest neighbor search.
@@
 
-PASE is a vector index plugin for PostgreSQL. It uses a "search first, then filter" strategy. But because the candidate set size is fixed, it may not return enough top-k results.
-
-VBASE is also a vector plugin for PostgreSQL. It applies filters during the HNSW index traversal. This ensures enough results.
-
-Milvus is a vector database built for large-scale similarity search. It filters data first, then performs approximate nearest neighbor search. This supports hybrid search.
+PASE\footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase} is a vector index plugin for PostgreSQL.
+It uses a "search first, then filter" strategy.
+But because the candidate set size is fixed, it may not return enough top-k results.
+
+VBASE\footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase} is also a vector plugin for PostgreSQL.
+It applies filters during the HNSW index traversal.
+This ensures enough results.
+
+Milvus\footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus} is a vector database built for large-scale similarity search.
+It filters data first, then performs approximate nearest neighbor search.
+This supports hybrid search.
 
@@
 	\caption{
-		Effect of Attribute Distribution on Query Performance(Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts.)}
+		Effect of Attribute Distribution on Query Performance}
+%		(Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts.)}
 
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
+\textcolor{cyan}{The proximity of the curves in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.}

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 	\subsection{Vector Libraries and Databases}
-The vector library and databases discussed in the following are not explicitly designed for hybrid query, but they support both attribute filtering and range filtering.
-
-Faiss is an efficient similarity search library.
-It uses an ID selector to filter data before performing approximate nearest neighbor search.
-This supports hybrid search.In Faiss, we use the HQI batch optimization strategy in the IVF index.
-It groups queries with the same filter conditions.
-Each group only runs the filter once.
-It uses efficient matrix operations to compute vector similarity in batches.
-
-PASE is a vector index plugin for PostgreSQL. It uses a "search first, then filter" strategy. But because the candidate set size is fixed, it may not return enough top-k results.
-
-VBASE is also a vector plugin for PostgreSQL. It applies filters during the HNSW index traversal. This ensures enough results.
-
-Milvus is a vector database built for large-scale similarity search. It filters data first, then performs approximate nearest neighbor search. This supports hybrid search.
+	Many existing vector libraries, such as Faiss, and databases, such as Milvus, VBASE, and PASE, are designed specifically for ANN search, but they also support attribute filtering and range queries.
+We also experimented with them.
+However, since these libraries and databases do not rely on a single algorithm, their internal implementations are complex, using multiple methods and have detailed third-party documentation, so we will not elaborate on them here.
 
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{orange}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets.
+\textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets.
 Notably, the VBASE and PASE algorithms only support single-threaded construction.}
@@
 }
-\textcolor{orange}{On the regular-scale datasets (Figure~\ref{fig:build_time_comparison_query1}, left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
+\textcolor{red}{On the medium-scale datasets (Figure~\ref{fig:build_time_comparison_query1} left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
 This is because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency.
@@
 
-\textcolor{orange}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (Filtered-DiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
+\textcolor{red}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1} right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
 This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
@@
 
-\textit{\textbf{Index size.}}
-\textcolor{orange}{
-	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
-For regular-scale datasets, other methods show moderate variation.
-However, on large-scale dataset, Graph-based algorithms such as ACORN, Filtered-DiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.
+\textit{\textbf{Index size.}} As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
+For medium-scale datasets, other methods show moderate variation.
+However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.
 Overall, IVF-based methods tend to produce more compact indexes.
-}
 
@@
 }.
-\textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
+As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
 Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.
-However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size.}
-
-\textcolor{orange}{
+
+\textcolor{red}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
 In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
@@
 In contrast, Milvus has lower peak memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
-\textcolor{orange}{
 Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
@@
 However, exceptions exist.
-As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
+As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.
 
@@
 	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
+	\textcolor{red}{
 	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods.
-The reason for the superior performance of Puck is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
-CAPS performs as well as Puck.
+The reason for their superior performance is that they filter out irrelevant results during the retrieval process rather than searching for more candidates.
 In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify two primary reasons.
 First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
-Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
+Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.}
 	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
@@
 		We conduct experiments on the Text2image-Mix dataset.
-This dataset contains image and text vectors and is a hybrid multi-modal dataset.
+This dataset contains image and text vectors and is a hybrid multimodal dataset.
 As shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{orange}{Notably, for regular-scale datasets, all algorithms build indexes using a single thread.
+\textcolor{orange}{Notably, for medium-scale datasets, all algorithms build indexes using a single thread.
 For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}
@@
 	\textcolor{blue}{
-		Similar to attribute filtering, the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
+		Similar to attribute filtering, the performance of multimodal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
@@
 	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
-	\textbf{Robust to Multi-Modal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
+	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
 %	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
@@
 
-\textcolor{orange}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
+\textcolor{orange}{The two variants of FilteredDiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
 FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.

### 2025-07-31 VLDB2026/main.tex

@@
 	\subsection{Vector Libraries and Databases}
-	Many existing vector libraries, such as Faiss, and databases, such as Milvus, VBASE, and PASE, are designed specifically for ANN search, but they also support attribute filtering and range queries.
-We also experimented with them.
-However, since these libraries and databases do not rely on a single algorithm, their internal implementations are complex, using multiple methods and have detailed third-party documentation, so we will not elaborate on them here.
+The vector library and databases discussed in the following are not explicitly designed for hybrid query, but they support both attribute filtering and range filtering.
+
+Faiss\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss} is an efficient similarity search library.
+It uses an ID selector to filter data before performing approximate nearest neighbor search.
+This supports hybrid search.In Faiss, we use the HQI batch optimization strategy in the IVF index.
+It groups queries with the same filter conditions.
+Each group only runs the filter once.
+It uses efficient matrix operations to compute vector similarity in batches.
+
+PASE\footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase} is a vector index plugin for PostgreSQL.
+It uses a "search first, then filter" strategy.
+But because the candidate set size is fixed, it may not return enough top-k results.
+
+VBASE\footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase} is also a vector plugin for PostgreSQL.
+It applies filters during the HNSW index traversal.
+This ensures enough results.
+
+Milvus\footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus} is a vector database built for large-scale similarity search.
+It filters data first, then performs approximate nearest neighbor search.
+This supports hybrid search.
 
@@
 
-\textit{\textbf{Index size.}} As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
-For medium-scale datasets, other methods show moderate variation.
+\textit{\textbf{Index size.}}
+\textcolor{orange}{
+	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
+For regular-scale datasets, other methods show moderate variation.
 However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.
 Overall, IVF-based methods tend to produce more compact indexes.
+}
 
@@
 	\caption{
-		 \centering
-		Effect of Attribute Distribution on Query Performance \\
-		(Strong: robust to attribute distribution shifts; Weak: sensitive to attribute distribution shifts.)}
+		Effect of Attribute Distribution on Query Performance}
+%		(Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts.)}
 

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-30 VLDB2026/main.tex
@@
 
-	\textit{Single-Thread Search.}  
 	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, as recall approaches 1, search often requires traversing larger candidate sets or deeper graph paths.
@@
 CAPS performs as well as Puck.
-In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify two primary reasons.
-First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
+In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason.
+	\textcolor{orange}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity.
+This makes single-attribute queries more difficult and degrades performance.}
+%	First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
 Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
-	\textcolor{red}{
 	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods.
-The reason for their superior performance is that they filter out irrelevant results during the retrieval process rather than searching for more candidates.
-In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify two primary reasons.
-First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
-Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.}
+The reason for the superior performance of Puck is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
+CAPS performs as well as Puck.
+In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason.
+	\textcolor{orange}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity.
+This makes single-attribute queries more difficult and degrades performance.}
+%	First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
+Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
 	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.

### 2025-07-31 VLDB2026/main.tex
fig

--- 2025-07-31 VLDB2026/main.tex
@@
 \usepackage{subcaption} % 需要subcaption宏包支持子图
-
+\usepackage{caption}
 \usepackage{fontawesome}
@@
 	\subsection{Vector Libraries and Databases}
-The vector library and databases discussed in the following are not explicitly designed for hybrid query, but they support both attribute filtering and range filtering.
-
-Faiss\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss} is an efficient similarity search library.
-It uses an ID selector to filter data before performing approximate nearest neighbor search.
-This supports hybrid search.In Faiss, we use the HQI batch optimization strategy in the IVF index.
-It groups queries with the same filter conditions.
-Each group only runs the filter once.
-It uses efficient matrix operations to compute vector similarity in batches.
-
-PASE\footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase} is a vector index plugin for PostgreSQL.
-It uses a "search first, then filter" strategy.
-But because the candidate set size is fixed, it may not return enough top-k results.
-
-VBASE\footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase} is also a vector plugin for PostgreSQL.
-It applies filters during the HNSW index traversal.
-This ensures enough results.
-
-Milvus\footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus} is a vector database built for large-scale similarity search.
-It filters data first, then performs approximate nearest neighbor search.
-This supports hybrid search.
+	Many existing vector libraries, such as Faiss, and databases, such as Milvus, VBASE, and PASE, are designed specifically for ANN search, but they also support attribute filtering and range queries.
+We also experimented with them.
+However, since these libraries and databases do not rely on a single algorithm, their internal implementations are complex, using multiple methods and have detailed third-party documentation, so we will not elaborate on them here.
 
@@
 
-\textcolor{orange}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (Filtered-DiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
+\textcolor{orange}{On the large-scale dataset Deep100M(Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
 This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
@@
 For regular-scale datasets, other methods show moderate variation.
-However, on large-scale dataset, Graph-based algorithms such as ACORN, Filtered-DiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.
+However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.
 Overall, IVF-based methods tend to produce more compact indexes.
@@
 
+	\textit{Single-Thread Search.}  
 	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, as recall approaches 1, search often requires traversing larger candidate sets or deeper graph paths.
@@
 CAPS performs as well as Puck.
-In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason.
-	\textcolor{orange}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity.
-This makes single-attribute queries more difficult and degrades performance.}
-%	First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
+In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify two primary reasons.
+First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
 Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
@@
 	\caption{
-		Effect of Attribute Distribution on Query Performance}
-%		(Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts.)}
+		 \centering
+		Effect of Attribute Distribution on Query Performance \\
+		(Strong: robust to attribute distribution shifts; Weak: sensitive to attribute distribution shifts.)}
 
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the curves in the figure reflects algorithm sensitivity to distributional variations.
+\textcolor{cyan}{The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.}
@@
 Their performance drops less compared to in-distribution (ID) datasets such as GIST1M and GloVe, indicating better adaptability to OOD queries.}
-
-\begin{figure*}[t]
-	\centering
-
-	% 1. 全局图例 (Legend) - 位置保持不变
+\begin{figure*}
+	\centering
+
 	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}
 
-	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
-
-	% 2. 第一部分：两张图，共用标题
-	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
-	% 宽度从\textwidth缩小到0.32\textwidth
-	\begin{subfigure}[b]{0.38\textwidth}
+	\begin{minipage}[t]{0.38\textwidth}
 		\centering
@@
 		\label{fig:attribute-multimodal} 
-	\end{subfigure}
-	\hfill % 在第一部分和第二部分之间添加弹性间距
-	% 3. 第二部分：两张图，共用标题
-	\begin{subfigure}[b]{0.39\textwidth}
+	\end{minipage}%
+	\hfill % 在盒子之间添加弹性间距
+	%
+	\begin{minipage}[t]{0.39\textwidth}
 		\centering
@@
 		\label{fig:attribute-cross-platform}
-	\end{subfigure}
-	\hfill % 在第二部分和第三部分之间添加弹性间距
-	% 4. 第三部分：只有一张图
-	\begin{subfigure}[b]{0.203\textwidth}
-		\centering
-		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+	\end{minipage}%
+	\hfill
+	%
+	\begin{minipage}[t]{0.203\textwidth}
+		\centering
 		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
@@
 		\label{fig:attribute big dataset}
-	\end{subfigure}
-
-	% 5. 全局总标题
-	\caption{\textcolor{violet}Scalability Study (Attribute Filtering)}
-	\label{fig:TrinityExtension——Attribution_main}
+	\end{minipage}
 \end{figure*}
+
+%\begin{figure*}[t]
+%	\centering
+%	
+%	% 1. 全局图例 (Legend) - 位置保持不变
+%	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}
+%	
+%	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+%	
+%	% 2. 第一部分：两张图，共用标题
+%	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+%	% 宽度从\textwidth缩小到0.32\textwidth
+%	\begin{subfigure}[b]{0.38\textwidth}
+%		\centering
+%		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
+%		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
+%		\hfill 
+%		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
+%		\caption{Multi-Modal}
+%		\label{fig:attribute-multimodal} 
+%	\end{subfigure}
+%	\hfill % 在第一部分和第二部分之间添加弹性间距
+%	% 3. 第二部分：两张图，共用标题
+%	\begin{subfigure}[b]{0.39\textwidth}
+%		\centering
+%		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
+%		\hfill
+%		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
+%		\caption{Cross-Platform}
+%		\label{fig:attribute-cross-platform}
+%	\end{subfigure}
+%	\hfill % 在第二部分和第三部分之间添加弹性间距
+%	% 4. 第三部分：只有一张图
+%	\begin{subfigure}[b]{0.203\textwidth}
+%		\centering
+%		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+%		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
+%		\caption{Big Dataset}
+%		\label{fig:attribute big dataset}
+%	\end{subfigure}
+%	
+%	% 5. 全局总标题
+%	\caption{\textcolor{violet}Scalability Study (Attribute Filtering)}
+%	\label{fig:TrinityExtension——Attribution_main}
+%\end{figure*}
 
@@
 
-\begin{figure*}[t]
-	\centering
-
-	% 1. 全局图例 (Legend) - 位置保持不变
-	\includegraphics[width=0.8\textwidth]{figures/exp/range_legend.pdf}
-
-	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
-
-	% 2. 第一部分：两张图，共用标题
-	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
-	% 宽度从\textwidth缩小到0.32\textwidth
-	\begin{subfigure}[b]{0.39\textwidth}
-		\centering
-		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
+\begin{figure*}
+	\centering
+
+	\includegraphics[width=0.7\textwidth]{figures/exp/range_legend.pdf}
+
+	\begin{minipage}[t]{0.38\textwidth}
+		\centering
 		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
@@
 		\label{fig:range-multimodal} 
-	\end{subfigure}
-	\hfill % 在第一部分和第二部分之间添加弹性间距
-	% 3. 第二部分：两张图，共用标题
-	\begin{subfigure}[b]{0.39\textwidth}
+	\end{minipage}%
+	\hfill % 在盒子之间添加弹性间距
+	%
+	\begin{minipage}[t]{0.39\textwidth}
 		\centering
@@
 		\label{fig:range-cross-platform}
-	\end{subfigure}
-	\hfill % 在第二部分和第三部分之间添加弹性间距
-	% 4. 第三部分：只有一张图
-	\begin{subfigure}[b]{0.203\textwidth}
-		\centering
-		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
+	\end{minipage}%
+	\hfill
+	%
+	\begin{minipage}[t]{0.203\textwidth}
+		\centering
 		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
@@
 		\label{fig: range big dataset}
-	\end{subfigure}
-
-	% 5. 全局总标题
-	\caption{\textcolor{violet}Scalability Study (Range Filtering)}
-	\label{fig:TrinityExtension——Attribution_main}
+	\end{minipage}
 \end{figure*}

### 2025-07-31 VLDB2026/main.tex
Update main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
+	\textcolor{red}{
 	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods.
-The reason for the superior performance of Puck is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
-CAPS performs as well as Puck.
-In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason.
-	\textcolor{orange}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity.
-This makes single-attribute queries more difficult and degrades performance.}
-%	First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
-Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
+The reason for their superior performance is that they filter out irrelevant results during the retrieval process rather than searching for more candidates.
+In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify two primary reasons.
+First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
+Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.}
 	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
@@
 
-	\subsubsection{\textbf{Attribute Filtering}}
+	\subsubsection{Attribute Filtering}
 %	We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.
@@
 
-	\subsubsection{\textbf{Range Filtering}}
+	\subsubsection{Range Filtering}
 \textcolor{orange}{
@@
 
-	\subsubsection{\textbf{General Algorithm}}
+	\subsubsection{General Algorithm}
 \textcolor{orange}{All of the following methods support both attribute filtering and range filtering.}
@@
 	\subsection{Challenges}
-	\subsubsection{\textbf{Attribute Filtering}}
+	\subsubsection{Attribute Filtering}
 	Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
@@
 
-	\subsubsection{\textbf{Range Filtering}}
+	\subsubsection{Range Filtering}
 

### 2025-07-31 VLDB2026/main.tex
Update main.tex
1
1

@@
 \usepackage{subcaption} % 需要subcaption宏包支持子图
-\usepackage{caption}
+
 \usepackage{fontawesome}
@@
 }.
-As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
-Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.
+ \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
+Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.}
 
@@
 
-\textit{\textbf{Search peak memory.}}
+ \textcolor{orange}{\textit{\textbf{Search peak memory.}}
 %  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
@@
 However, exceptions exist.
-As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.
+As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
 
@@
 This difference stems from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
-
 	%	Puck and CAPS perform relatively well.
@@
 However, this also demonstrates that IVF-based methods remain very promising for hybrid queries.
-
 	\textcolor{violet}{Additionally, Puck and CAPS also perform relatively well.
@@
 Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
-
 	For IVF-based methods not specifically optimized for hybrid queries (Faiss and Milvus), their QPS shows a similar and relatively stable trend as recall varies.
@@
 Their performance drops less compared to in-distribution (ID) datasets such as GIST1M and GloVe, indicating better adaptability to OOD queries.}
-\begin{figure*}
-	\centering
-
+
+\begin{figure*}[t]
+	\centering
+
+	% 1. 全局图例 (Legend) - 位置保持不变
 	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}
 
-	\begin{minipage}[t]{0.38\textwidth}
+	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+
+	% 2. 第一部分：两张图，共用标题
+	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+	% 宽度从\textwidth缩小到0.32\textwidth
+	\begin{subfigure}[b]{0.38\textwidth}
 		\centering
@@
 		\label{fig:attribute-multimodal} 
-	\end{minipage}%
-	\hfill % 在盒子之间添加弹性间距
-	%
-	\begin{minipage}[t]{0.39\textwidth}
+	\end{subfigure}
+	\hfill % 在第一部分和第二部分之间添加弹性间距
+	% 3. 第二部分：两张图，共用标题
+	\begin{subfigure}[b]{0.39\textwidth}
 		\centering
@@
 		\label{fig:attribute-cross-platform}
-	\end{minipage}%
-	\hfill
-	%
-	\begin{minipage}[t]{0.203\textwidth}
-		\centering
+	\end{subfigure}
+	\hfill % 在第二部分和第三部分之间添加弹性间距
+	% 4. 第三部分：只有一张图
+	\begin{subfigure}[b]{0.203\textwidth}
+		\centering
+		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
 		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
@@
 		\label{fig:attribute big dataset}
-	\end{minipage}
+	\end{subfigure}
+
+	% 5. 全局总标题
+	\caption{\textcolor{violet}Scalability Study (Attribute Filtering)}
+	\label{fig:TrinityExtension——Attribution_main}
 \end{figure*}
-
-%\begin{figure*}[t]
-%	\centering
-%	
-%	% 1. 全局图例 (Legend) - 位置保持不变
-%	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}
-%	
-%	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
-%	
-%	% 2. 第一部分：两张图，共用标题
-%	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
-%	% 宽度从\textwidth缩小到0.32\textwidth
-%	\begin{subfigure}[b]{0.38\textwidth}
-%		\centering
-%		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
-%		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
-%		\hfill 
-%		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-%		\caption{Multi-Modal}
-%		\label{fig:attribute-multimodal} 
-%	\end{subfigure}
-%	\hfill % 在第一部分和第二部分之间添加弹性间距
-%	% 3. 第二部分：两张图，共用标题
-%	\begin{subfigure}[b]{0.39\textwidth}
-%		\centering
-%		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
-%		\hfill
-%		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
-%		\caption{Cross-Platform}
-%		\label{fig:attribute-cross-platform}
-%	\end{subfigure}
-%	\hfill % 在第二部分和第三部分之间添加弹性间距
-%	% 4. 第三部分：只有一张图
-%	\begin{subfigure}[b]{0.203\textwidth}
-%		\centering
-%		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
-%		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
-%		\caption{Big Dataset}
-%		\label{fig:attribute big dataset}
-%	\end{subfigure}
-%	
-%	% 5. 全局总标题
-%	\caption{\textcolor{violet}Scalability Study (Attribute Filtering)}
-%	\label{fig:TrinityExtension——Attribution_main}
-%\end{figure*}
 
@@
 
-\begin{figure*}
-	\centering
-
-	\includegraphics[width=0.7\textwidth]{figures/exp/range_legend.pdf}
-
-	\begin{minipage}[t]{0.38\textwidth}
-		\centering
+\begin{figure*}[t]
+	\centering
+
+	% 1. 全局图例 (Legend) - 位置保持不变
+	\includegraphics[width=0.8\textwidth]{figures/exp/range_legend.pdf}
+
+	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
+
+	% 2. 第一部分：两张图，共用标题
+	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
+	% 宽度从\textwidth缩小到0.32\textwidth
+	\begin{subfigure}[b]{0.39\textwidth}
+		\centering
+		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
 		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
@@
 		\label{fig:range-multimodal} 
-	\end{minipage}%
-	\hfill % 在盒子之间添加弹性间距
-	%
-	\begin{minipage}[t]{0.39\textwidth}
+	\end{subfigure}
+	\hfill % 在第一部分和第二部分之间添加弹性间距
+	% 3. 第二部分：两张图，共用标题
+	\begin{subfigure}[b]{0.39\textwidth}
 		\centering
@@
 		\label{fig:range-cross-platform}
-	\end{minipage}%
-	\hfill
-	%
-	\begin{minipage}[t]{0.203\textwidth}
-		\centering
+	\end{subfigure}
+	\hfill % 在第二部分和第三部分之间添加弹性间距
+	% 4. 第三部分：只有一张图
+	\begin{subfigure}[b]{0.203\textwidth}
+		\centering
+		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
 		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
@@
 		\label{fig: range big dataset}
-	\end{minipage}
+	\end{subfigure}
+
+	% 5. 全局总标题
+	\caption{\textcolor{violet}Scalability Study (Range Filtering)}
+	\label{fig:TrinityExtension——Attribution_main}
 \end{figure*}
@@
 
-	\subsubsection{Attribute Filtering}
+	\subsubsection{\textbf{Attribute Filtering}}
 %	We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.
@@
 
-	\subsubsection{Range Filtering}
+	\subsubsection{\textbf{Range Filtering}}
 \textcolor{orange}{
@@
 
-	\subsubsection{General Algorithm}
+	\subsubsection{\textbf{General Algorithm}}
 \textcolor{orange}{All of the following methods support both attribute filtering and range filtering.}
@@
 	\subsection{Challenges}
-	\subsubsection{Attribute Filtering}
+	\subsubsection{\textbf{Attribute Filtering}}
 	Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
@@
 
-	\subsubsection{Range Filtering}
+	\subsubsection{\textbf{Range Filtering}}
 

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
-For regular-scale datasets, other methods show moderate variation.
+For medium-scale datasets, other methods show moderate variation.
 However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.

### 2025-07-31 VLDB2026/main.tex
change table 2

--- 2025-07-31 VLDB2026/main.tex
@@
 }.
- \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
-Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.}
+As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
+Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.
 
@@
 
- \textcolor{orange}{\textit{\textbf{Search peak memory.}}
+\textit{\textbf{Search peak memory.}}
 %  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
@@
 This difference stems from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
+
 	%	Puck and CAPS perform relatively well.
@@
 However, this also demonstrates that IVF-based methods remain very promising for hybrid queries.
+
 	\textcolor{violet}{Additionally, Puck and CAPS also perform relatively well.
@@
 Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
+
 	For IVF-based methods not specifically optimized for hybrid queries (Faiss and Milvus), their QPS shows a similar and relatively stable trend as recall varies.
@@
 	\textbf{Robust to Multi-Modal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
-%	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
+	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
 	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets.
+\textcolor{orange}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets.
 Notably, the VBASE and PASE algorithms only support single-threaded construction.}
@@
 }
-\textcolor{red}{On the medium-scale datasets (Figure~\ref{fig:build_time_comparison_query1} left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
+\textcolor{orange}{On the regular-scale datasets (Figure~\ref{fig:build_time_comparison_query1}, left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
 This is because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency.
@@
 
-\textcolor{red}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1} right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
+\textcolor{orange}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (Filtered-DiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
 This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
@@
 \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
-Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.}
-
-\textcolor{red}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
+Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.
+However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size.}
+
+\textcolor{orange}{
 In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
@@
 In contrast, Milvus has lower peak memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
+\textcolor{orange}{
 Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{orange}{Notably, for medium-scale datasets, all algorithms build indexes using a single thread.
+\textcolor{orange}{Notably, for regular-scale datasets, all algorithms build indexes using a single thread.
 For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}
@@
 For space considerations, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
-The experimental results show consistent performance across all datasets and query ranges.
+%	The experimental results show consistent performance across all datasets and query ranges.
 
@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable.
+Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
 So our findings remain consistent with those reported in Section 4.2.4.

### 2025-07-31 VLDB2026/main.tex
Update main.tex

@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.

### 2025-07-31 VLDB2026/main.tex
Update main.tex
1

@@
 		\textit{Base}: Underlying ANN index structure used.}
-		\textit{A}: Post-filtering, 
-		\textit{B}: Pre-filtering, 
-		\textit{C}: Simultaneous filtering, 
+		\textit{A}: Post-filtering (Filter after ANN search), 
+		\textit{B}: Pre-filtering (Filter before ANN search), 
+		\textit{C}: Simultaneous filtering (Filter simultaneously with ANN search), 
 		\textit{Y}: Support, 
@@
 
-Faiss\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss} is an efficient similarity search library.
-It uses an ID selector to filter data before performing approximate nearest neighbor search.
-This supports hybrid search.In Faiss, we use the HQI batch optimization strategy in the IVF index.
+\noindent\textbf{\underline{Faiss}\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
+Faiss is an efficient similarity search library.
+It uses an ID selector to filter data before performing ANN search.
+This supports hybrid search.
+In Faiss, we use the HQI batch optimization strategy in the IVF index.
 It groups queries with the same filter conditions.
@@
 
-PASE\footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase} is a vector index plugin for PostgreSQL.
-It uses a "search first, then filter" strategy.
-But because the candidate set size is fixed, it may not return enough top-k results.
-
-VBASE\footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase} is also a vector plugin for PostgreSQL.
+\noindent\textbf{\underline{PASE} \footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase}} PASE is a vector index plugin for PostgreSQL.
+It uses a post-filtering strategy.
+Since the candidate set size is fixed, it may fail to return enough top-k results.
+
+\noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}} VBASE is also a vector plugin for PostgreSQL.
 It applies filters during the HNSW index traversal.
@@
 
-Milvus\footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus} is a vector database built for large-scale similarity search.
-It filters data first, then performs approximate nearest neighbor search.
-This supports hybrid search.
+\noindent\textbf{\underline{Milvus} \footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus}} Milvus is a vector database designed for large-scale similarity search.
+In hybrid queries, it adopts a pre-filtering strategy, similar to the ID selector mechanism used in Faiss.
+%It filters data first, then performs approximate nearest neighbor search. This supports hybrid search.
 
@@
 For space considerations, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
-%	The experimental results show consistent performance across all datasets and query ranges.
+The experimental results show consistent performance across all datasets and query ranges.
 
@@
 	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
-Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
+Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable.
 So our findings remain consistent with those reported in Section 4.2.4.
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
@@
 	\textbf{Robust to Multi-Modal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
-	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
+%	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
 	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely relates to structured data.
-For attribute filtering algorithms, \textcolor{violet}{factors such as the number of attributes and attribute selectivity~\cite{analyticdb,milvus} significantly impact algorithm performance.} As for range filtering algorithms, the size of the query range and the characteristics of different datasets play an important role in determining algorithm performance.
+For attribute filtering algorithms, \textcolor{violet}{factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity ~\cite{analyticdb,milvus} significantly impact algorithm performance.} As for range filtering algorithms, the size of the query range and the characteristics of different datasets play an important role in determining algorithm performance.
 
@@
 	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying vector datasets, number of attributes participating in index construction, number of query attributes, and selectivity.
+We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying vector datasets, attribute distributions, number of attributes participating in index construction, number of query attributes, and selectivity.
 Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and 2 multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
@@
 	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
-For medium-scale datasets, other methods show moderate variation.
+For regular-scale datasets, other methods show moderate variation.
 However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain.

### 2025-07-31 VLDB2026/main.tex
Update main.tex

@@
 	AS is defined as the proportion of data points sharing a given attribute value. For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute. 
-	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
+	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset. 
 %	We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.
@@
 However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms}.
 

### 2025-07-31 VLDB2026/main.tex

@@
 	AS is defined as the proportion of data points sharing a given attribute value. For example, AS of 1\% indicates that only 1\% of the dataset meets the given attribute. 
-	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset. 
+	To investigate this effect, we evaluate 4 AS settings (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset using single-thread execution. 
 %	We compare the query performance of attribute filtering algorithms across these settings, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.

### 2025-07-31 Revision/response.tex
change response

@@
 "Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
-The Text2Image dataset includes two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
+The Text2Image dataset includes two versions.
+The original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set.
+The Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
 }
@@
 	"We conduct experiments on the Text2image-Mix dataset.
-This dataset contains image and text vectors and is a hybrid multimodal dataset.
-As shown in Figure 9a, UNG and NHQ consistently perform best, followed by CAPS.
+This dataset contains image and text vectors and is a hybrid multi-modal dataset.
+As shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
 Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
@@
 Therefore, the performance on this dataset is similar to the results shown in Figure 4.
-	In contrast, the Text2image dataset shown in Figure 9a is different.
+In contrast, the Text2image dataset shown in Figure 9 is different.
 The query set and the base dataset belong to two completely different modalities.
@@
 Section 4.3.3:\textcolor{blue}{
-		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 12a is also consistent with the single-modality results in Figure 14.
-As shown in Figure 11, the algorithms still perform the worst on multimodal datasets like Text2Image.
-This is because these range query algorithms are almost graph-based.
-Graph algorithms need more iterations to find true neighbors in OOD datasets."
+		"Similar to attribute filtering, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
+These algorithms on the Text2Image dataset exhibit a significant performance degradation.
+This is because these range query algorithms are almost entirely graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets."
 }

### 2025-07-31 VLDB2026/main.tex

@@
 \textcolor{orange}{
-Overall, UNG, NHQ, and FilteredDisk\\-ANN demonstrate strong performance.
+Overall, UNG, NHQ and FilteredDisk\\-ANN demonstrate strong performance.
 However, UNG suffers from performance degradation when the attribute count differs between indexing and querying.
@@
 It offers flexible support for varying numbers of attributes and is optimized for low-selectivity attribute scenarios, but its overall performance is relatively moderate.
-Puck is well-suited for large-scale datasets such as those with 100 million points.
-It offers fast index construction and low memory consumption in such scenarios.
-Moreover, it delivers high search performance in multi-threaded environments, making it an excellent choice for deployment on extremely large datasets.}
+Puck is well-suited for large-scale datasets such as those with 100 million points. It offers fast index construction and low memory consumption in such scenarios. 
+%Moreover, it delivers high search performance in multi-threaded environments, making it an excellent choice for deployment on extremely large datasets.
+}
 
@@
 	\textcolor{orange}{
-	iRange has relatively low time and space costs for index construction; however, its search performance declines significantly with increasing query range.
+	iRange has relatively low time and space costs for index construction.
+However, its search performance declines significantly with increasing query range.
 Despite offering threading parameters for indexing, it does not effectively utilize multi-core parallelism in practical scenarios.
@@
 ACORN demonstrates average overall performance.
-Among its variants, ACORN-1 shows significant advantages in indexing speed on billion-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}
+Among its variants, ACORN-1 shows significant advantages in indexing speed on 100M-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}
 
 \textcolor{orange}{
-Faiss, Milvus, and VBASE handle complex scenarios with advanced filtering operations more effectively.
-While they offer strong flexibility, their overall search performance is relatively modest.
+Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability.
+This flexibility, however, is often counterbalanced by their relatively modest overall search performance.
 Relatively speaking, PASE performs less well across various aspects.}

### 2025-07-31 VLDB2026/main.tex
1

@@
 Our study introduces 15 hybrid query algorithms and systematically classifies them based on multiple dimensions, such as index organization and filtering strategy, providing a reference for the categorization of hybrid queries.
-In experiments, for attribute filtering, we construct standard attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
+%		In experiments, for attribute filtering, we construct standard attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
 For range filtering, we also evaluate the algorithm performance across the 3 metrics through controlled variation of query ranges.
+	\textcolor{orange}{In the experiments, we constructed standardized attribute and range sets for attribute filtering and range filtering, respectively, enabling a unified comparison of algorithms in terms of index construction efficiency and query performance.
+Furthermore, we evaluate the robustness of the algorithms across multiple dimensions, including different data distributions, platforms, and scalability on a 100M-scale dataset.}
 	 Additionally, we conduct an in-depth analysis of the experimental results based on the underlying principles of algorithms.

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets.
+\textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other 6 medium-scale datasets.
 Notably, the VBASE and PASE algorithms only support single-threaded construction.}
@@
 
-\textcolor{orange}{
+\textcolor{red}{
 Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability.

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other 6 medium-scale datasets.
+\textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets.
 Notably, the VBASE and PASE algorithms only support single-threaded construction.}
@@
 Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
-So our findings remain consistent with those reported in Section 4.2.4.
+So our findings remain consistent with those reported in Section 4.2.3.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}
@@
 
-\textcolor{red}{
+\textcolor{orange}{
 Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability.

### 2025-07-31 VLDB2026/main.tex
change 3.3

@@
 \noindent\textbf{\underline{Faiss}\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
-Faiss is an efficient similarity search library.
-It uses an ID selector to filter data before performing ANN search.
-This supports hybrid search.
+Faiss is an efficient similarity search library. It supports hybrid search by using an ID selector to filter data before performing ANN search.
 In Faiss, we use the HQI batch optimization strategy in the IVF index.
@@
 \noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}} VBASE is also a vector plugin for PostgreSQL.
-It applies filters during the HNSW index traversal.
-This ensures enough results.
+Unlike PASE, it applies filters during the HNSW index traversal, discarding unmatched nodes on the fly.
+This strategy ensures that enough valid results are returned .
 
@@
 Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
-So our findings remain consistent with those reported in Section 4.2.3.
+So our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}

### 2025-07-31 VLDB2026/main.tex
1

@@
 	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods.
-The reason for the superior performance of Puck is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
-CAPS performs as well as Puck.
+The reason for their superior performance is that they filter out irrelevant results during the retrieval process rather than searching for more candidates.
 In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason.

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 \noindent\textbf{\underline{Faiss}\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
-Faiss is an efficient similarity search library. It supports hybrid search by using an ID selector to filter data before performing ANN search.
+Faiss is an efficient similarity search library.
+It uses an ID selector to filter data before performing ANN search.
+This supports hybrid search.
 In Faiss, we use the HQI batch optimization strategy in the IVF index.
@@
 \noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}} VBASE is also a vector plugin for PostgreSQL.
-Unlike PASE, it applies filters during the HNSW index traversal, discarding unmatched nodes on the fly.
-This strategy ensures that enough valid results are returned .
+It applies filters during the HNSW index traversal.
+This ensures enough results.
 
@@
 \textcolor{cyan}{The proximity of the curves in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.}
+When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change.}
 %	Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
+	\textcolor{cyan}{Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
 Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.

### 2025-07-31 VLDB2026/main.tex
Update main.tex
change 2 to two

--- 2025-07-31 VLDB2026/main.tex
@@
 We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying vector datasets, attribute distributions, number of attributes participating in index construction, number of query attributes, and selectivity.
-Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and 2 multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and two multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 	As the complexity of real-world application requirements increases, NN search has evolved into hybrid NN search with attribute constraints.
-Depending on the nature of the attribute constraints, hybrid NN search can be divided into 2 categories: 1) Attribute Filtering Nearest Neighbor (\textit{AF-NN}) search.
+Depending on the nature of the attribute constraints, hybrid NN search can be divided into two categories: 1) Attribute Filtering Nearest Neighbor (\textit{AF-NN}) search.
 2) Range Filtering Nearest Neighbor (\textit{RF-NN}) search.
@@
 %	Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.
-	Filtered-DiskANN proposes 2 indexes:  
+	Filtered-DiskANN proposes two indexes:  
 	1) \textbf{FilteredVamana}, which incrementally builds the graph index by inserting data points and dynamically adding edges, allowing adaptive expansion.  
@@
 	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods.
-The reason for their superior performance is that they filter out irrelevant results during the retrieval process rather than searching for more candidates.
+The reason for the superior performance of Puck is that it filters out irrelevant results during the retrieval process rather than searching for more candidates.
+CAPS performs as well as Puck.
 In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason.

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 Our study introduces 15 hybrid query algorithms and systematically classifies them based on multiple dimensions, such as index organization and filtering strategy, providing a reference for the categorization of hybrid queries.
-%		In experiments, for attribute filtering, we construct standard attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
+In experiments, for attribute filtering, we construct standard attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
 For range filtering, we also evaluate the algorithm performance across the 3 metrics through controlled variation of query ranges.
-	\textcolor{orange}{In the experiments, we constructed standardized attribute and range sets for attribute filtering and range filtering, respectively, enabling a unified comparison of algorithms in terms of index construction efficiency and query performance.
-Furthermore, we evaluate the robustness of the algorithms across multiple dimensions, including different data distributions, platforms, and scalability on a 100M-scale dataset.}
 Additionally, we conduct an in-depth analysis of the experimental results based on the underlying principles of algorithms.
@@
 		\textit{Base}: Underlying ANN index structure used.}
-		\textit{A}: Post-filtering (Filter after ANN search), 
-		\textit{B}: Pre-filtering (Filter before ANN search), 
-		\textit{C}: Simultaneous filtering (Filter simultaneously with ANN search), 
+		\textit{A}: Post-filtering, 
+		\textit{B}: Pre-filtering, 
+		\textit{C}: Simultaneous filtering, 
 		\textit{Y}: Support, 
@@
 
-\noindent\textbf{\underline{Faiss}\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
-Faiss is an efficient similarity search library. It supports hybrid search by using an ID selector to filter data before performing ANN search.
-In Faiss, we use the HQI batch optimization strategy in the IVF index.
+Faiss\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss} is an efficient similarity search library.
+It uses an ID selector to filter data before performing approximate nearest neighbor search.
+This supports hybrid search.In Faiss, we use the HQI batch optimization strategy in the IVF index.
 It groups queries with the same filter conditions.
@@
 
-\noindent\textbf{\underline{PASE} \footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase}} PASE is a vector index plugin for PostgreSQL.
-It uses a post-filtering strategy.
-Since the candidate set size is fixed, it may fail to return enough top-k results.
-
-\noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}} VBASE is also a vector plugin for PostgreSQL.
-Unlike PASE, it applies filters during the HNSW index traversal, discarding unmatched nodes on the fly.
-This strategy ensures that enough valid results are returned .
-
-\noindent\textbf{\underline{Milvus} \footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus}} Milvus is a vector database designed for large-scale similarity search.
-In hybrid queries, it adopts a pre-filtering strategy, similar to the ID selector mechanism used in Faiss.
-%It filters data first, then performs approximate nearest neighbor search. This supports hybrid search.
+PASE\footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase} is a vector index plugin for PostgreSQL.
+It uses a "search first, then filter" strategy.
+But because the candidate set size is fixed, it may not return enough top-k results.
+
+VBASE\footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase} is also a vector plugin for PostgreSQL.
+It applies filters during the HNSW index traversal.
+This ensures enough results.
+
+Milvus\footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus} is a vector database built for large-scale similarity search.
+It filters data first, then performs approximate nearest neighbor search.
+This supports hybrid search.
 
@@
 \textcolor{cyan}{The proximity of the curves in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change.}
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts.}
 %	Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
@@
 StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
-CAPS, on the other hand, is limited by its implementation and achieves a recall of only around 0.2.}
+CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios.}
 %		we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{cyan}{Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
+	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
 Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
-So our findings remain consistent with those reported in Section 4.2.3.
+So our findings remain consistent with those reported in Section 4.2.4.
 For brevity and due to space limitations, we omit further discussion of these redundant results.}
@@
 However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms}.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.
 
@@
 \textcolor{orange}{
-Overall, UNG, NHQ and FilteredDisk\\-ANN demonstrate strong performance.
+Overall, UNG, NHQ, and FilteredDisk\\-ANN demonstrate strong performance.
 However, UNG suffers from performance degradation when the attribute count differs between indexing and querying.
@@
 It offers flexible support for varying numbers of attributes and is optimized for low-selectivity attribute scenarios, but its overall performance is relatively moderate.
-Puck is well-suited for large-scale datasets such as those with 100 million points. It offers fast index construction and low memory consumption in such scenarios. 
-%Moreover, it delivers high search performance in multi-threaded environments, making it an excellent choice for deployment on extremely large datasets.
-}
+Puck is well-suited for large-scale datasets such as those with 100 million points.
+It offers fast index construction and low memory consumption in such scenarios.
+Moreover, it delivers high search performance in multi-threaded environments, making it an excellent choice for deployment on extremely large datasets.}
 
@@
 	\textcolor{orange}{
-	iRange has relatively low time and space costs for index construction.
-However, its search performance declines significantly with increasing query range.
+	iRange has relatively low time and space costs for index construction; however, its search performance declines significantly with increasing query range.
 Despite offering threading parameters for indexing, it does not effectively utilize multi-core parallelism in practical scenarios.
@@
 ACORN demonstrates average overall performance.
-Among its variants, ACORN-1 shows significant advantages in indexing speed on 100M-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}
-
-\textcolor{red}{
-Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability.
-This flexibility, however, is often counterbalanced by their relatively modest overall search performance.
+Among its variants, ACORN-1 shows significant advantages in indexing speed on billion-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}
+
+\textcolor{orange}{
+Faiss, Milvus, and VBASE handle complex scenarios with advanced filtering operations more effectively.
+While they offer strong flexibility, their overall search performance is relatively modest.
 Relatively speaking, PASE performs less well across various aspects.}
@@
 	\subsubsection{Range Filtering}
-
 	Except for DSG and UNIFY, most range filtering algorithms require the dataset to be pre-sorted before building the index.
-\textcolor{green}{Moreover, these methods do not support multi-attribute range queries.
-}Enhancing these methods to support an arbitrary number of range filterable attributes remains an open research challenge.
+\textcolor{green}{Moreover, existing range filtering algorithms do not support range queries with more than 3 attributes.} \textcolor{violet}{Designing algorithms that support an arbitrary number of range filterable attributes remains an open research challenge.}
 

### 2025-07-31 Revision/response.tex

@@
 
-\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations.
+\textcolor{blue}{"The proximity of the curves in the figure reflects algorithm sensitivity to distributional variations.
 When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
 
-For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure.
+For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Stable and Unstable) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
@@
 
+We also removed the original Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}.
+We believe these changes improve the clarity and readability of the paper, without reducing the completeness of the evaluation.
+
 	\begin{figure*}
@@
 \end{figure*}
-%\begin{figure}[htbp]
-%	\centering
-%	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
-%	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
-%	\caption{Different AS under the Same Algorithm}
-%	\label{fig:attribute_selectivity_2}
-%\end{figure}
+\begin{figure}[htbp]
+	\centering
+	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
+	\caption{Different AS under the Same Algorithm}
+	\label{fig:attribute_selectivity_2}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying vector datasets, attribute distributions, number of attributes participating in index construction, number of query attributes, and selectivity.
-Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and two multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and 2 multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 	As the complexity of real-world application requirements increases, NN search has evolved into hybrid NN search with attribute constraints.
-Depending on the nature of the attribute constraints, hybrid NN search can be divided into two categories: 1) Attribute Filtering Nearest Neighbor (\textit{AF-NN}) search.
+Depending on the nature of the attribute constraints, hybrid NN search can be divided into 2 categories: 1) Attribute Filtering Nearest Neighbor (\textit{AF-NN}) search.
 2) Range Filtering Nearest Neighbor (\textit{RF-NN}) search.
@@
 %	Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.
-	Filtered-DiskANN proposes two indexes:  
+	Filtered-DiskANN proposes 2 indexes:  
 	1) \textbf{FilteredVamana}, which incrementally builds the graph index by inserting data points and dynamically adding edges, allowing adaptive expansion.  
@@
 	(3) \textit{Algorithms insensitive to AS.}  
-	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
-	\textcolor{orange}{Figure 1 shows algorithms that are insensitive to AS.}
+%	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
+	\textcolor{orange}{Figure~\ref{fig:exp_5_2_3} shows algorithms that are insensitive to AS.}
 	Milvus is mainly limited by system-level communication overhead, such as API latency.

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the curves in the figure reflects algorithm sensitivity to distributional variations.
+\textcolor{cyan}{The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
 When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change.}

### 2025-07-31 VLDB2026/main.tex
change attr distribution

--- 2025-07-31 VLDB2026/main.tex
@@
 Other approaches enhance robustness by separating attribute and vector indexing into distinct stages: UNG uses a logical graph to navigate attribute relationships, while CAPS employs an attribute frequency tree to adapt to power-law patterns.
-In ACORN--\(\gamma\), during index construction, attributes are primarily used for pruning in the lowest-layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
+For ACORN--\(\gamma\), during index construction, attributes are primarily used for pruning in the lowest-layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
 Consequently, changes in attribute distribution have minimal impact on overall performance.}}
@@
 StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
-CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios.}
+CAPS, on the other hand, is limited by its implementation and achieves a recall of only around 0.2.}
 %		we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
@@
 	\subsubsection{Range Filtering}
+
 	Except for DSG and UNIFY, most range filtering algorithms require the dataset to be pre-sorted before building the index.
-\textcolor{green}{Moreover, existing range filtering algorithms do not support range queries with more than 3 attributes.} \textcolor{violet}{Designing algorithms that support an arbitrary number of range filterable attributes remains an open research challenge.}
+\textcolor{green}{Moreover, these methods do not support multi-attribute range queries.
+}Enhancing these methods to support an arbitrary number of range filterable attributes remains an open research challenge.
 

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 	(3) \textit{Algorithms insensitive to AS.}  
-%	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
-	\textcolor{orange}{Figure~\ref{fig:exp_5_2_3} shows algorithms that are insensitive to AS.}
+	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
+	\textcolor{orange}{Figure 1 shows algorithms that are insensitive to AS.}
 	Milvus is mainly limited by system-level communication overhead, such as API latency.

### 2025-07-31 VLDB2026/main.tex
change multi modal
Update main.tex

@@
 Other approaches enhance robustness by separating attribute and vector indexing into distinct stages: UNG uses a logical graph to navigate attribute relationships, while CAPS employs an attribute frequency tree to adapt to power-law patterns.
-For ACORN--\(\gamma\), during index construction, attributes are primarily used for pruning in the lowest-layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
+In ACORN--\(\gamma\), during index construction, attributes are primarily used for pruning in the lowest-layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
 Consequently, changes in attribute distribution have minimal impact on overall performance.}}
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-		\caption{Multi-Modal}
+		\caption{Multi-Modal Datasets}
 		\label{fig:attribute-multimodal} 
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
-		\caption{Cross-Platform}
+		\caption{Different Platforms}
 		\label{fig:attribute-cross-platform}
@@
 		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
-		\caption{Big Dataset}
+		\caption{Large-Scale Dataset}
 		\label{fig:attribute big dataset}
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
-		\caption{Multi-Modal}
+		\caption{Multi-Modal Datasets}
 		\label{fig:range-multimodal} 
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
-		\caption{Cross-Platform}
+		\caption{Different Platforms}
 		\label{fig:range-cross-platform}
@@
 		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
-		\caption{Big Dataset}
+		\caption{Large-Scale Dataset}
 		\label{fig: range big dataset}

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}} \textcolor{blue}{
-		We conduct experiments on the Text2image-Mix dataset.
-This dataset contains image and text vectors and is a hybrid multi-modal dataset.
+	We conduct experiments on two multi-modal  datasets Text2image-Mix and Text2image. 
+%This dataset contains image and text vectors and is a hybrid multi-modal dataset. 
 As shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.

### 2025-07-31 Revision/response.tex
1

@@
  \textbf{Response:} 
-Thank you for your suggestion.
-We cited these two papers in the introduction to show that there are several papers that study attribute selectivity.
-In practice, attribute selectivity are indeed widely used in real-world scenarios.
-For example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
+ Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
+ In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
+For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution.
+For attribute selectivity: for example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-We have replaced the two references ([12] and [36]) with more comprehensive and accurate references ([47] and [52]).
+For the two parts you suggested, we have replaced them in the paper with more comprehensive and accurate references.
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
-
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute  selectivity [47,52] significantly impact algorithm performance."}
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [42,47] significantly impact algorithm performance."}
 
 \textcolor{blue}{"
-[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
+[42]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
 }
@@
 \textcolor{blue}{"
-[52]Chuangxian Wei, Bin Wu, Sheng Wang, Renjie Lou, Chaoqun Zhan, Feifei Liand Yuanzhe Cai.
+[47]Chuangxian Wei, Bin Wu, Sheng Wang, Renjie Lou, Chaoqun Zhan, Feifei Liand Yuanzhe Cai.
 2020.AnalyticDB-V: A Hybrid Analytical Engine TowardsOuery Fusion for Structured and Unstructured Data.

### 2025-07-31 VLDB2026/main.tex

@@
 
-	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
+	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} 
 	\textcolor{violet}{As shown in the Figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 
-\textcolor{blue}{"The proximity of the curves in the figure reflects algorithm sensitivity to distributional variations.
-When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
+\textcolor{blue}{"The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
+When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change."}
 

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 
-In response to the large difference in index construction time shown in Figure 12a(now 10a), we have revised the paper based on your suggestion.
+In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
 We added more detailed and in-depth analysis to provide a clearer explanation.
@@
 Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
-
-%	The reason for the high construction time of ACORN-$\gamma$ has been explained in the attribute filtering section and is therefore omitted here.
 
@@
 
-Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c(now 10c) is very insightful.
+Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c is very insightful.
 Initially, we hesitated to include the peak memory usage of databases (such as Milvus) because they are full systems that run continuously and contain many components.

### 2025-07-31 Revision/response.tex
change multi modal

--- 2025-07-31 Revision/response.tex
@@
 
-\textcolor{blue}{"The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
-When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change."}
+\textcolor{blue}{"The proximity of the curves in the figure reflects algorithm sensitivity to distributional variations.
+When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
 
@@
 
-We also removed the original Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}.
+We also removed the  Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}.
 We believe these changes improve the clarity and readability of the paper, without reducing the completeness of the evaluation.
@@
 \textbf{Response:} 
- Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
- In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
-For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution.
-For attribute selectivity: for example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
+Thank you for your suggestion.
+We cited these two papers in the introduction to show that there are several papers that study attribute selectivity.
+In practice, attribute selectivity are indeed widely used in real-world scenarios.
+For example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect.
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we have replaced them in the paper with more comprehensive and accurate references.
+We have replaced the two references ([12] and [36]) with more comprehensive and accurate references ([47] and [52]).
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [42,47] significantly impact algorithm performance."}
+
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute  selectivity [47,52] significantly impact algorithm performance."}
 
 \textcolor{blue}{"
-[42]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
+[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
 }
@@
 \textcolor{blue}{"
-[47]Chuangxian Wei, Bin Wu, Sheng Wang, Renjie Lou, Chaoqun Zhan, Feifei Liand Yuanzhe Cai.
+[52]Chuangxian Wei, Bin Wu, Sheng Wang, Renjie Lou, Chaoqun Zhan, Feifei Liand Yuanzhe Cai.
 2020.AnalyticDB-V: A Hybrid Analytical Engine TowardsOuery Fusion for Structured and Unstructured Data.

### 2025-07-31 VLDB2026/main.tex
change multi modal

--- 2025-07-31 VLDB2026/main.tex
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-		\caption{Multi-Modal Datasets}
+		\caption{Multi-Modal}
 		\label{fig:attribute-multimodal} 
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
-		\caption{Different Platforms}
+		\caption{Cross-Platform}
 		\label{fig:attribute-cross-platform}
@@
 		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
-		\caption{Large-Scale Dataset}
+		\caption{Big Dataset}
 		\label{fig:attribute big dataset}
@@
 %This dataset contains image and text vectors and is a hybrid multi-modal dataset. 
-As shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
-		Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
+On Text2image-Mix dataset,as shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
+Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space.
+The performance is similar to that of the single-modal dataset in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
+This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.This is not actually a difficult query.
+%		Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
 In practice, this means that the experiments effectively treat the image and text subsets as separate datasets, since the ground truths for each query belong to the same modality.
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
-		\caption{Multi-Modal Datasets}
+		\caption{Multi-Modal}
 		\label{fig:range-multimodal} 
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
-		\caption{Different Platforms}
+		\caption{Cross-Platform}
 		\label{fig:range-cross-platform}
@@
 		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
-		\caption{Large-Scale Dataset}
+		\caption{Big Dataset}
 		\label{fig: range big dataset}
@@
 	\textcolor{blue}{
-		Similar to attribute filtering, the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
+		Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
-This is because these range query algorithms are almost entirely graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets.
+This is because these range query algorithms most are  graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets.
 %		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.

### 2025-07-31 Revision/response.tex
change MR R2

@@
 Section 4.2.3: \textcolor{blue}{
-	"We conduct experiments on the Text2image-Mix dataset.
-This dataset contains image and text vectors and is a hybrid multi-modal dataset.
-As shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
-Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
-In practice, this means that the experiments effectively treat the image and text subsets as separate datasets, since the ground truths for each query belong to the same modality.
-Therefore, the performance on this dataset is similar to the results shown in Figure 4.
+	"We conduct experiments on two multimodal datasets Text2image-Mix and Text2image.
+On Text2imageMix dataset,as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
+Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space.
+The performance is similar to that of the single-modal dataset in Figure 4.
+This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.This is not actually a difficult query.
 In contrast, the Text2image dataset shown in Figure 9 is different.
@@
 Queries are far from the dataset points, and the ground truths are more dispersed.
-To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance."
+To find the groundtruths, algorithms typically need to examine more points, which leads to degraded performance."
 }
@@
 Section 4.3.3:\textcolor{blue}{
-		"Similar to attribute filtering, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
+		"Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
-This is because these range query algorithms are almost entirely graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets."
+This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets."
 }

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 
-We also removed the  Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}.
+We also removed the original Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}.
 We believe these changes improve the clarity and readability of the paper, without reducing the completeness of the evaluation.
@@
 Thank you for pointing this out.
-The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49], now updated to reference [45], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
@@
 Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
- 	Although existing works [9,50] conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
- 	To address this gap, we carry out the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
-Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications."}
+ 	Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
 
@@
 
-Of all the evaluated algorithms, Faiss, Puck, DiskANN, and Milvus support quantization.
+Of all the evaluated algorithms, Faiss, Puck, Filtered-DiskANN, and Milvus support quantization.
 However, in our experiments, we did not enable quantization in any of our experiments.
@@
 
-\textbf{Regarding Figure 7 and the exclusion of Vamana:}
+\textbf{Regarding the exclusion of Vamana in Figure 7 (now Figure 6):}
 
 We appreciate the observation of reviewer.
-Figure 7 presents experiments on multi-attribute construction and search, using Boolean AND logic.
+Figure 6 presents experiments on multi-attribute construction and search, using Boolean AND logic.
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
-\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 9b.
+\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 10.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 For brevity and due to space limitations, we omit further discussion of these redundant results."}
-\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 12b.
+\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 15.
 Our findings remain consistent with those reported in Section 4.2.3.
@@
 Thank you for pointing this out.
-The original reference [49], now updated to reference [45], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
@@
 Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
- 	Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
+ 	Although existing works [9,50] conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
+ 	To address this gap, we carry out the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications."}
 
@@
 
-Of all the evaluated algorithms, Faiss, Puck, Filtered-DiskANN, and Milvus support quantization.
+Of all the evaluated algorithms, Faiss, Puck, DiskANN, and Milvus support quantization.
 However, in our experiments, we did not enable quantization in any of our experiments.
@@
 
-\textbf{Regarding the exclusion of Vamana in Figure 7 (now Figure 6):}
+\textbf{Regarding Figure 7 and the exclusion of Vamana:}
 
 We appreciate the observation of reviewer.
-Figure 6 presents experiments on multi-attribute construction and search, using Boolean AND logic.
+Figure 7 presents experiments on multi-attribute construction and search, using Boolean AND logic.
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 Section 4.2.3: \textcolor{blue}{
-	"We conduct experiments on two multimodal datasets Text2image-Mix and Text2image.
-On Text2imageMix dataset,as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
+	"	We conduct experiments on two multi-modal datasets Text2image-Mix and Text2image. 
+	%This dataset contains image and text vectors and is a hybrid multi-modal dataset. 
+	On Text2image-Mix dataset, as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
 	Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space.
@@
 Queries are far from the dataset points, and the ground truths are more dispersed.
-To find the groundtruths, algorithms typically need to examine more points, which leads to degraded performance."
+To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance."
 }
@@
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
-This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets."
+This is because these range query algorithms most are  graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets."
 }

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
-\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 10.
+\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 9b.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 For brevity and due to space limitations, we omit further discussion of these redundant results."}
-\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 15.
+\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 12b.
 Our findings remain consistent with those reported in Section 4.2.3.
@@
 Thank you for your suggestion.
-Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the feature of whether to support disk for each algorithm in Table 1.
+Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper..
 At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.

### 2025-07-31 Revision/response.tex
1

@@
 	"We conduct experiments on two multimodal datasets Text2image-Mix and Text2image.
-On Text2imageMix dataset,as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
+On Text2imageMix dataset, as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
 Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space.
 The performance is similar to that of the single-modal dataset in Figure 4.
-This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.This is not actually a difficult query.
+This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.
+This is not actually a difficult query.
 In contrast, the Text2image dataset shown in Figure 9 is different.
@@
 Section 4.3.3:\textcolor{blue}{
-		"Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
+		"Similar to attribute filtering, on Text2Image-Mix dataset, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 Thank you for your suggestion.
-Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper..
+Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the feature of whether to support disk for each algorithm in Table 1.
 At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
@@
 
-Section 4.2.3:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Section 4.2.3:\textcolor{blue}{"As shown in the figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
 The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
-Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
-This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
+Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
+StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
+CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios."}
 
 Section 4.3.3:
-\textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB).
-At the same time, we can see that some algorithms (e.g., SeRF, ACORN-1) perform even worse than the VBASE database, which indicates that they do not adapt well to large-scale dataset scenarios.
-Although Milvus has a low QPS, it can achieve a recall of 1 with an excellent memory footprint of around 80GB"}
+\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}
 

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 Section 4.2.3: \textcolor{blue}{
-	"We conduct experiments on two multimodal datasets Text2image-Mix and Text2image.
-On Text2imageMix dataset,as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
-Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space.
-The performance is similar to that of the single-modal dataset in Figure 4.
-This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.This is not actually a difficult query.
+	"We conduct experiments on the Text2image-Mix dataset.
+This dataset contains image and text vectors and is a hybrid multi-modal dataset.
+As shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
+Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
+In practice, this means that the experiments effectively treat the image and text subsets as separate datasets, since the ground truths for each query belong to the same modality.
+Therefore, the performance on this dataset is similar to the results shown in Figure 4.
 In contrast, the Text2image dataset shown in Figure 9 is different.
@@
 Section 4.3.3:\textcolor{blue}{
-		"Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
+		"Similar to attribute filtering, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
-This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets."
+This is because these range query algorithms are almost entirely graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets."
 }
@@
 Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.
-We observe that the impact of using real attribute versus using ID on the algorithms is negligible.
-The key factor remains the size of the query range, as shown in Figure~\ref{fig:range_2_2}.
+To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.In fact, current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
+As shown in Figure~\ref{fig:range_2_2}, our experiments also show that the impact of using real attributes versus using IDs on the algorithms is negligible.
+The key factor remains the size of the query range.
 \textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}
@@
 
-In response to the large difference in index construction time shown in Figure 12a, we have revised the paper based on your suggestion.
+In response to the large difference in index construction time shown in Figure 12a(now 10a), we have revised the paper based on your suggestion.
 We added more detailed and in-depth analysis to provide a clearer explanation.
@@
 Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
+
+%	The reason for the high construction time of ACORN-$\gamma$ has been explained in the attribute filtering section and is therefore omitted here.
 
@@
 
-Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c is very insightful.
+Finally, your observation about the missing peak memory usage data for Milvus in Figure 12c(now 10c) is very insightful.
 Initially, we hesitated to include the peak memory usage of databases (such as Milvus) because they are full systems that run continuously and contain many components.

### 2025-07-31 Revision/response.tex
change R8

--- 2025-07-31 Revision/response.tex
@@
 	"We conduct experiments on two multimodal datasets Text2image-Mix and Text2image.
-On Text2imageMix dataset, as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
+On Text2imageMix dataset,as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
 Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space.
 The performance is similar to that of the single-modal dataset in Figure 4.
-This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.
-This is not actually a difficult query.
+This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.This is not actually a difficult query.
 In contrast, the Text2image dataset shown in Figure 9 is different.
@@
 Section 4.3.3:\textcolor{blue}{
-		"Similar to attribute filtering, on Text2Image-Mix dataset, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
+		"Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
@@
 Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.In fact, current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
-As shown in Figure~\ref{fig:range_2_2}, our experiments also show that the impact of using real attributes versus using IDs on the algorithms is negligible.
-The key factor remains the size of the query range.
+To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.
+We observe that the impact of using real attribute versus using ID on the algorithms is negligible.
+The key factor remains the size of the query range, as shown in Figure~\ref{fig:range_2_2}.
 \textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}
@@
 Additionally, we have provided a more in-depth analysis of the internal mechanisms of each algorithm in the text, aiming to uncover the fundamental reasons behind their performance.
-\textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
-
-Section 5.1.1: \textcolor{blue}{
-	"Overall, UNG, NHQ, and FilteredDisk-ANN demonstrate strong performance.
+\textbf{(Please see Section 5.1.1, Section 5.1.2 and Section 5.1.3, highlighted in blue in the revised manuscript.)}
+
+Section 5.1.1:\textcolor{blue}{
+	"Overall, UNG, NHQ and FilteredDisk-ANN demonstrate strong performance.
 However, UNG suffers from performance degradation when the attribute count differs between indexing and querying.
@@
 
-\textcolor{blue}{"The two variants of FilteredDiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
+\textcolor{blue}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
 FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.
@@
 It offers flexible support for varying numbers of attributes and is optimized for low-selectivity attribute scenarios, but its overall performance is relatively moderate.
-	Puck is well-suited for large-scale datasets such as those with 100 million points.
-It offers fast index construction and low memory consumption in such scenarios.
-Moreover, it delivers high search performance in multi-threaded environments, making it an excellent choice for deployment on extremely large datasets."}
+	Puck is well-suited for large-scale datasets such as those with 100 million points. It offers fast index construction and low memory consumption in such scenarios. "}
 
@@
 \textcolor{blue}{
-	iRange has relatively low time and space costs for index construction; however, its search performance declines significantly with increasing query range.
+	iRange has relatively low time and space costs for index construction.
+However, its search performance declines significantly with increasing query range.
 Despite offering threading parameters for indexing, it does not effectively utilize multi-core parallelism in practical scenarios.
@@
 	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
-It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution.}
+It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution."}
 
@@
 	ACORN demonstrates average overall performance.
-Among its variants, ACORN-1 shows significant advantages in indexing speed on billion-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}
+Among its variants, ACORN-1 shows significant advantages in indexing speed on 100M-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}
 
 \textcolor{blue}{
-		Faiss, Milvus, and VBASE handle complex scenarios with advanced filtering operations more effectively.
-While they offer strong flexibility, their overall search performance is relatively modest.
+	Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability.
+This flexibility, however, is often counterbalanced by their relatively modest overall search performance.
 Relatively speaking, PASE performs less well across various aspects."}

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 	\hspace*{8pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-	\includegraphics[width=0.95\columnwidth]{fig/range_2_2_legend.pdf} % 图例图片路径
+	\includegraphics[width=0.9\columnwidth]{fig/range_2_2_legend.pdf} % 图例图片路径
 
@@
 
-Section 4.2.3:\textcolor{blue}{"As shown in the figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Section 4.2.3:\textcolor{blue}{"As shown in the figure 12c, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
 The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
-Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
-StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
-CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios."}
+Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
+This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}
 
 Section 4.3.3:
-\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}
+\textcolor{blue}{"As shown in the figure 16c, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB).
+At the same time, we can see that some algorithms (e.g., SeRF, ACORN-1) perform even worse than the VBASE database, which indicates that they do not adapt well to large-scale dataset scenarios.
+Although Milvus has a low QPS, it can achieve a recall of 1 with an excellent memory footprint of around 80GB"}
 

### 2025-07-31 Revision/response.tex
Update response.tex

@@
 Section 4.2.3: \textcolor{blue}{
-	"We conduct experiments on two multimodal datasets Text2image-Mix and Text2image.
-On Text2imageMix dataset, as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
-Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space.
-The performance is similar to that of the single-modal dataset in Figure 4.
-This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.
-This is not actually a difficult query.
+	"We conduct experiments on the Text2image-Mix dataset.
+This dataset contains image and text vectors and is a hybrid multi-modal dataset.
+As shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
+Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
+In practice, this means that the experiments effectively treat the image and text subsets as separate datasets, since the ground truths for each query belong to the same modality.
+Therefore, the performance on this dataset is similar to the results shown in Figure 4.
 In contrast, the Text2image dataset shown in Figure 9 is different.
@@
 Section 4.3.3:\textcolor{blue}{
-		"Similar to attribute filtering, on Text2Image-Mix dataset, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
+		"Similar to attribute filtering, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
-This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets."
+This is because these range query algorithms are almost entirely graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets."
 }
@@
 	\hspace*{8pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-	\includegraphics[width=0.9\columnwidth]{fig/range_2_2_legend.pdf} % 图例图片路径
+	\includegraphics[width=0.95\columnwidth]{fig/range_2_2_legend.pdf} % 图例图片路径
 
@@
 \textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 15.
-Our findings remain consistent with those reported in Section 4.2.3.
+Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
+So our findings remain consistent with those reported in Section 4.2.3.
 For brevity and due to space limitations, we omit further discussion of these redundant results."}
@@
 \textbf{Response:} 
-Thank you for your feedback. We have resolved this issue;For more  details,please see Meta R1 .
+Thank you for your feedback. We have resolved this issue. For more  details, please refer to our response to Meta R1.
 
@@
 The results show that differences in server configurations have little impact on the ranking of the methods.
-For more details, please refer to our response Meta R4.
+For more details, please refer to our response to Meta R4.
 %%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-31 VLDB2026/main.tex

@@
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
-This is because these range query algorithms most are  graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets.
+This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets.
 %		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.

### 2025-07-31 VLDB2026/main.tex
1

@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{orange}{Notably, for medium-scale datasets, all algorithms build indexes using a single thread.
-For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}
+\textcolor{orange}{Notably, all algorithms use single-threaded index construction on medium-scale datasets, and 64-thread construction on the large-scale Deep100M dataset, except DSG, which only supports single-threading.
+For WinFilter, we use Super Postfiltering on medium datasets for best performance, and switch to the base algorithm Vamana-WST on Deep100M due to construction overhead.
+	}
 
@@
 	\textcolor{orange}{
-	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss, based on the IVF\_Flat architecture, achieves fast index construction through subset sampling and centroid computation, which lowers the computational cost.
-	As another IVF\_Flat-based method, Milvus performs even better on large-scale datasets, mainly due to its cache-aware optimization that greatly reduces CPU cache misses.}
-
-		\textcolor{orange}{
-	ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
+	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF\_Flat architecture, require less time.
+This indexing structure enables fast construction through subset sampling and centroid computation, thereby reducing computational cost.
+Milvus performs particularly well on large-scale datasets, mainly due to its cache-aware optimizations, which significantly reduce CPU cache misses.}
+%	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss, based on the IVF\_Flat architecture, achieves fast index construction through subset sampling and centroid computation, which lowers the computational cost.
+%	As another IVF\_Flat-based method, Milvus performs even better on large-scale datasets, mainly due to its cache-aware optimization that greatly reduces CPU cache misses.}
+
+\textcolor{orange}{In addition, the two HNSW-based methods, ACORN-1 and SeRF, also achieve short index construction time.
+ACORN-1 closely follows the original HNSW construction process and reduces the number of candidate neighbors in the upper layers to lower computational overhead.
+SeRF attaches timestamp information to edges during construction, making the total build time comparable to that of a single HNSW graph.
+	}
+%		\textcolor{orange}{
+%	ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
 This efficiency stems from its construction process, which closely resembles that of the original HNSW, and from reducing the number of candidate neighbors in the upper layers, thereby lowering computational cost.
@@
 
-		\textcolor{orange}{
-	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
+\textcolor{orange}{We observe that ACORN-\(\gamma\), DSG and WinFilter exhibit relatively long index construction time.
+Although the first two methods are also based on HNSW, ACORN-\(\gamma\) extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
+DSG, on the other hand, incorporates a rectangle tree structure for index management, making the construction process more complex and costly.
+%	Additionally, DSG builds index using a single thread on the Deep100M dataset, resulting in the longest construction time. 
+WinFilter also incurs high construction cost, as it relies on a tree structure and builds a separate nearest neighbor graph for each node, which leads to redundant computations.
+However, on large-scale datasets, its preprocessing stage is replaced by the base algorithm Vamana-WST, effectively avoiding significant time overhead.}
+%		\textcolor{orange}{
+%	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
 This design introduces redundant computation and high construction cost.
 However, on large-scale datasets, the preprocessing phase of WinFilter is replaced in the experiments by the base algorithm Vamana-WST, thus avoiding significant time overhead.}
-
-		\textcolor{orange}{
-	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
+%	
+%		\textcolor{orange}{
+%	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
 Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
 
-%	The reason for the high construction time of ACORN-$\gamma$ has been explained in the attribute filtering section and is therefore omitted here.
-
-		\textcolor{orange}{
-	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
+%		\textcolor{orange}{
+%	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
 This makes the construction process more complex and costly.

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 	\textcolor{blue}{
-		Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
+		Similar to attribute filtering, the performance of range filtering queries on the Text2image-Mix dataset (Figure~\ref{fig:range-multimodal}) is similar to the single-modality query performance (Figure~\ref{fig:exp_8_2}).
+However, on the Text2Image dataset, these algorithms exhibit a significant performance degradation (Figure~\ref{fig:range-multimodal}).
+This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets.
+%		Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 	\textcolor{blue}{
-		Similar to attribute filtering, the performance of range filtering queries on the Text2image-Mix dataset (Figure~\ref{fig:range-multimodal}) is similar to the single-modality query performance (Figure~\ref{fig:exp_8_2}).
-However, on the Text2Image dataset, these algorithms exhibit a significant performance degradation (Figure~\ref{fig:range-multimodal}).
-This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets.
-%		Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
+		Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
 These algorithms on the Text2Image dataset exhibit a significant performance degradation.
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{cyan}{Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
+	\textcolor{cyan}{Consistent with Section 4.2.3, we conduct range filtering experiments on the YT-Audio-Real dataset using two server configurations, with results presented in Figure~\ref{fig:range-cross-platform}.
 Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
-So our findings remain consistent with those reported in Section 4.2.3.
-For brevity and due to space limitations, we omit further discussion of these redundant results.}
+Therefore, different server configurations only affect the performance of individual algorithms, with minimal impact on their relative performance ranking.}
+%		So our findings remain consistent with those reported in Section 4.2.3. For brevity and due to space limitations, we omit further discussion of these redundant results.}
 %	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}.

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms}.
+However, their high performance is achieved at the cost of extremely high memory consumption ( Figure~\ref{fig:rangeFilter_search_memory_mb}).
+In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory.}
 

### 2025-07-31 VLDB2026/main.tex

@@
 	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms}.
+However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).
+In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory.}
 

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 Section 4.3.3:
-%\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b.
-When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4.
-For brevity and due to space limitations, we omit further discussion of these redundant results."}
-\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 15.
-Our findings remain consistent with those reported in Section 4.2.3.
-For brevity and due to space limitations, we omit further discussion of these redundant results."}
+\textcolor{blue}{"Consistent with Section 4.2.3, we conduct range filtering experiments on the YT-Audio-Real dataset using two server configurations, with results presented in Figure 15.
+Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
+Therefore, different server configurations only affect the performance of individual algorithms, with minimal impact on their relative performance ranking."}
 
@@
 \textbf{Response:} 
-Thank you for your feedback. We have resolved this issue;For more  details,please see Meta R1 .
+Thank you for your feedback. We have modified both the figure and the related description in the paper to improve readability. For more  details, please refer to our response to Meta R1.
 

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 %\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
-\textit{\textbf{Build peak memory.}}
-% As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
-% %on small-scale datasets, all methods except NHQ exhibit low memory usage. 
-% \textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
-% This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
-% 
-% On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
-\textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index.
-}.
- \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
+%\textit{\textbf{Build peak memory.}}
+% \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
 Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.}
-
-\textcolor{red}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
-In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
+%
+%\textcolor{red}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
+%In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
 This leads to high peak memory usage during construction, despite the relatively small size of the final index.}
-
- \textcolor{orange}{\textit{\textbf{Search peak memory.}}
-%  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
-Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
-%\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
-However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets.
-In contrast, Milvus has lower peak memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
-Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
+%
+% \textcolor{orange}{\textit{\textbf{Search peak memory.}}
+%Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
+As a result, peak memory usage during querying is generally slightly lower than during construction.
+However, exceptions exist.
+As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
+\textcolor{orange}{\textit{\textbf{Peak memory.}}	
+We present the peak memory usage during index construction and query processing in Figure~\ref{fig:build_memory_mb_comparison} and Figure~\ref{fig:search_memory_mb_comparison}, respectively.
+We observe that peak memory usage is generally correlated with the combined size of the index and the dataset.
+Methods that produce larger indexes tend to consume more memory during both construction and querying, and this trend holds consistently across different datasets.}
+
+\textcolor{orange}{However, there are notable exceptions.
+During index construction, PASE adopts an on-demand loading strategy, resulting in build peak memory usage even lower than the final index size.
+NHQ generates a large number of candidate neighbors during construction but retains only a small subset per node in the final index, leading to high peak memory usage despite a relatively compact index.
+During querying, CAPS maintains a large candidate set dynamically, which significantly increases its search peak memory consumption.}
+
+% \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
+Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.}
+%
+%\textcolor{orange}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
+%	In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
+This leads to high peak memory usage during construction, despite the relatively small size of the final index.}
+%	
+% \textcolor{orange}{Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
 As a result, peak memory usage during querying is generally slightly lower than during construction.
@@
 
-	\textit{\textbf{Build peak memory.}}  
-	\textcolor{orange}{As explained in the attribute filtering analysis, algorithms with larger index sizes (including the dataset) tend to exhibit higher build peak memory consumption.
-As shown in Figure~\ref{fig:rangeFilter_build_memory_mb}, range filtering also adheres to this pattern, while PASE deviates due to reasons discussed earlier.}
+	\textcolor{orange}{\textit{\textbf{Peak memory.}}  
+	As explained in the attribute filtering analysis, methods with larger index sizes (including the dataset) tend to exhibit higher peak memory consumption.
+As shown in Figure~\ref{fig:rangeFilter_build_memory_mb} and Figure~\ref{fig:rangeFilter_search_memory_mb}, range filtering also adheres to this pattern.}
+%	, while PASE deviates due to reasons discussed earlier
 
@@
 
-%	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
-%	
-%	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
-This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
-%	
-%	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage.
-It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
-Its index structure remains stable in high dimensions without significant graph growth.
-This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
-%	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
-
-		\textit{\textbf{Search peak memory.}}  
-		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, the peak memory usage during search generally follows a similar trend to that observed during index construction.
+%		\textit{\textbf{Search peak memory.}}  
+%		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, the peak memory usage during search generally follows a similar trend to that observed during index construction.
 This observation is consistent with our earlier analysis in the attribute filtering section.}
@@
 	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption ( Figure~\ref{fig:rangeFilter_search_memory_mb}).
-In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory.}
+However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms}.
 

### 2025-07-31 Revision/response.tex

@@
 
-\textcolor{blue}{"Graph indexes are widely used in Hybrid ANN due to their efficiency.
+\textcolor{blue}{"Graph indexes are widely used in hybrid ANN due to their efficiency.
 To support hybrid queries, in attribute filtering, a common practice involves attaching attribute metadata to nodes or edges, thereby skipping parts that do not satisfy query conditions during traversal (e.g., NHQ, Filtered-DiskANN, ACORN).
@@
 
-\textcolor{blue}{"IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
+\textcolor{blue}{"IVF-based indexes also offer unique advantages in hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).

### 2025-07-31 VLDB2026/main.tex
change performance of RF

--- 2025-07-31 VLDB2026/main.tex
@@
 	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{orange}{Notably, all algorithms use single-threaded index construction on medium-scale datasets, and 64-thread construction on the large-scale Deep100M dataset, except DSG, which only supports single-threading.
-For WinFilter, we use Super Postfiltering on medium datasets for best performance, and switch to the base algorithm Vamana-WST on Deep100M due to construction overhead.
-	}
+\textcolor{orange}{Notably, for medium-scale datasets, all algorithms build indexes using a single thread.
+For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}
 
@@
 	\textcolor{orange}{
-	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF\_Flat architecture, require less time.
-This indexing structure enables fast construction through subset sampling and centroid computation, thereby reducing computational cost.
-Milvus performs particularly well on large-scale datasets, mainly due to its cache-aware optimizations, which significantly reduce CPU cache misses.}
-%	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss, based on the IVF\_Flat architecture, achieves fast index construction through subset sampling and centroid computation, which lowers the computational cost.
-%	As another IVF\_Flat-based method, Milvus performs even better on large-scale datasets, mainly due to its cache-aware optimization that greatly reduces CPU cache misses.}
-
-\textcolor{orange}{In addition, the two HNSW-based methods, ACORN-1 and SeRF, also achieve short index construction time.
-ACORN-1 closely follows the original HNSW construction process and reduces the number of candidate neighbors in the upper layers to lower computational overhead.
-SeRF attaches timestamp information to edges during construction, making the total build time comparable to that of a single HNSW graph.
-	}
-%		\textcolor{orange}{
-%	ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
+	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss, based on the IVF\_Flat architecture, achieves fast index construction through subset sampling and centroid computation, which lowers the computational cost.
+	As another IVF\_Flat-based method, Milvus performs even better on large-scale datasets, mainly due to its cache-aware optimization that greatly reduces CPU cache misses.}
+
+		\textcolor{orange}{
+	ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
 This efficiency stems from its construction process, which closely resembles that of the original HNSW, and from reducing the number of candidate neighbors in the upper layers, thereby lowering computational cost.
@@
 
-\textcolor{orange}{We observe that ACORN-\(\gamma\), DSG and WinFilter exhibit relatively long index construction time.
-Although the first two methods are also based on HNSW, ACORN-\(\gamma\) extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
-DSG, on the other hand, incorporates a rectangle tree structure for index management, making the construction process more complex and costly.
-%	Additionally, DSG builds index using a single thread on the Deep100M dataset, resulting in the longest construction time. 
-WinFilter also incurs high construction cost, as it relies on a tree structure and builds a separate nearest neighbor graph for each node, which leads to redundant computations.
-However, on large-scale datasets, its preprocessing stage is replaced by the base algorithm Vamana-WST, effectively avoiding significant time overhead.}
-%		\textcolor{orange}{
-%	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
+		\textcolor{orange}{
+	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
 This design introduces redundant computation and high construction cost.
 However, on large-scale datasets, the preprocessing phase of WinFilter is replaced in the experiments by the base algorithm Vamana-WST, thus avoiding significant time overhead.}
-%	
-%		\textcolor{orange}{
-%	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
+
+		\textcolor{orange}{
+	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
 Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
 
-%		\textcolor{orange}{
-%	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
+%	The reason for the high construction time of ACORN-$\gamma$ has been explained in the attribute filtering section and is therefore omitted here.
+
+		\textcolor{orange}{
+	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
 This makes the construction process more complex and costly.
@@
 	\textcolor{blue}{
+		As shown in Figure~\ref{fig:exp_8_2}, the algorithms that performed well are WinFilter, iRange, UNIFY and Faiss.
 	WinFilter maintains optimal performance by building an index for each tree node. It then performs an ANN search on the relevant nodes and post-filters the results, ensuring high recall and QPS.
@@
 	}
-%	WinFilter consistently delivers the best performance.
-This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
-%	
-%	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
-In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios.
-However, by leveraging HNSW and bitmap-based post-filtering, UNIFY performs competitively under broader range conditions, demonstrating strong scalability.
-
-%	SeRF exhibits relatively weak overall performance, with a significant drop in recall under small-range query scenarios.
-This suggests that while its compressed graph structure is space-efficient, it has a substantial negative impact on query performance.
-
-	\textcolor{blue}{SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
+
+	\textcolor{blue}{SeRF, ACORN and vector databases performed poorly.
+		SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
 This is because SeRF compresses the entire HNSW graph by attaching range information to its edges.
@@
 Additionally, graph traversal may lead to the exploration of numerous invalid neighbors, increasing the likelihood of the search becoming trapped in local optima and further degrading performance.
-	}
-
-	%	 修改此处
-	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
-Unlike other range filtering algorithms, ACORN is not designed with specialized data structures  to achieve efficient range filtering.
-In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
-
-%	For third-party library and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
-%	%\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
-Similar to the selectivity observed in attribute filtering.
-}
-%	Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
-With a smaller range, fewer points remain after filtering, resulting in lower computational cost.
-In addition, the performance of Faiss is influenced by data dimensionality; the higher the dimensionality, the worse the performance.
-
-	Vector databases  show relatively poor performance on range queries.
-Among them, Milvus performs more balanced across both small-range and large-range queries, even surpassing ACORN under high recall settings.
+		The overall performance of ACORN is poor.
+Unlike other algorithms specifically designed for range filtering, ACORN does not design an index specifically for range queries; instead, it adopts a pre-filtering strategy, resulting in poorer performance.
+		The performance of vector databases in range queries is also poor, as their database systems also incorporate many other designs that can affect the algorithm's performance.
+Among them, Milvus performed well.
 PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
-	VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is quite  low.
+	}
 
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{cyan}{Consistent with Section 4.2.3, we conduct range filtering experiments on the YT-Audio-Real dataset using two server configurations, with results presented in Figure~\ref{fig:range-cross-platform}.
+	\textcolor{cyan}{Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}.
 Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
-Therefore, different server configurations only affect the performance of individual algorithms, with minimal impact on their relative performance ranking.}
-%		So our findings remain consistent with those reported in Section 4.2.3. For brevity and due to space limitations, we omit further discussion of these redundant results.}
+So our findings remain consistent with those reported in Section 4.2.3.
+For brevity and due to space limitations, we omit further discussion of these redundant results.}
 %	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}.
@@
 	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).
-In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory.}
+However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms}.
 

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 %\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
-%\textit{\textbf{Build peak memory.}}
-% \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
+\textit{\textbf{Build peak memory.}}
+% As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
+% %on small-scale datasets, all methods except NHQ exhibit low memory usage. 
+% \textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
+% This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead.
+% 
+% On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms.
+\textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index.
+}.
+ \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
 Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.}
-%
-%\textcolor{red}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
-%In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
+
+\textcolor{red}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
+In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
 This leads to high peak memory usage during construction, despite the relatively small size of the final index.}
-%
-% \textcolor{orange}{\textit{\textbf{Search peak memory.}}
-%Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
-As a result, peak memory usage during querying is generally slightly lower than during construction.
-However, exceptions exist.
-As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
-\textcolor{orange}{\textit{\textbf{Peak memory.}}	
-We present the peak memory usage during index construction and query processing in Figure~\ref{fig:build_memory_mb_comparison} and Figure~\ref{fig:search_memory_mb_comparison}, respectively.
-We observe that peak memory usage is generally correlated with the combined size of the index and the dataset.
-Methods that produce larger indexes tend to consume more memory during both construction and querying, and this trend holds consistently across different datasets.}
-
-\textcolor{orange}{However, there are notable exceptions.
-During index construction, PASE adopts an on-demand loading strategy, resulting in build peak memory usage even lower than the final index size.
-NHQ generates a large number of candidate neighbors during construction but retains only a small subset per node in the final index, leading to high peak memory usage despite a relatively compact index.
-During querying, CAPS maintains a large candidate set dynamically, which significantly increases its search peak memory consumption.}
-
-% \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
-Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.}
-%
-%\textcolor{orange}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
-%	In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
-This leads to high peak memory usage during construction, despite the relatively small size of the final index.}
-%	
-% \textcolor{orange}{Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
+
+ \textcolor{orange}{\textit{\textbf{Search peak memory.}}
+%  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly.
+Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
+%\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase.
+However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets.
+In contrast, Milvus has lower peak memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
+Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
 As a result, peak memory usage during querying is generally slightly lower than during construction.
@@
 
-	\textcolor{orange}{\textit{\textbf{Peak memory.}}  
-	As explained in the attribute filtering analysis, methods with larger index sizes (including the dataset) tend to exhibit higher peak memory consumption.
-As shown in Figure~\ref{fig:rangeFilter_build_memory_mb} and Figure~\ref{fig:rangeFilter_search_memory_mb}, range filtering also adheres to this pattern.}
-%	, while PASE deviates due to reasons discussed earlier
+	\textit{\textbf{Build peak memory.}}  
+	\textcolor{orange}{As explained in the attribute filtering analysis, algorithms with larger index sizes (including the dataset) tend to exhibit higher build peak memory consumption.
+As shown in Figure~\ref{fig:rangeFilter_build_memory_mb}, range filtering also adheres to this pattern, while PASE deviates due to reasons discussed earlier.}
 
@@
 
-%		\textit{\textbf{Search peak memory.}}  
-%		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, the peak memory usage during search generally follows a similar trend to that observed during index construction.
+%	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
+%	
+%	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms.
+This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
+%	
+%	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage.
+It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges.
+Its index structure remains stable in high dimensions without significant graph growth.
+This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
+%	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
+
+		\textit{\textbf{Search peak memory.}}  
+		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, the peak memory usage during search generally follows a similar trend to that observed during index construction.
 This observation is consistent with our earlier analysis in the attribute filtering section.}
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 	\textcolor{blue}{
-		As shown in Figure~\ref{fig:exp_8_2}, the algorithms that performed well are WinFilter, iRange, UNIFY and Faiss.
 	WinFilter maintains optimal performance by building an index for each tree node. It then performs an ANN search on the relevant nodes and post-filters the results, ensuring high recall and QPS.
@@
 	}
-
-	\textcolor{blue}{SeRF, ACORN and vector databases performed poorly.
-		SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
+%	WinFilter consistently delivers the best performance.
+This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
+%	
+%	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes.
+In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios.
+However, by leveraging HNSW and bitmap-based post-filtering, UNIFY performs competitively under broader range conditions, demonstrating strong scalability.
+
+%	SeRF exhibits relatively weak overall performance, with a significant drop in recall under small-range query scenarios.
+This suggests that while its compressed graph structure is space-efficient, it has a substantial negative impact on query performance.
+
+	\textcolor{blue}{SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
 This is because SeRF compresses the entire HNSW graph by attaching range information to its edges.
@@
 Additionally, graph traversal may lead to the exploration of numerous invalid neighbors, increasing the likelihood of the search becoming trapped in local optima and further degrading performance.
-		The overall performance of ACORN is poor.
-Unlike other algorithms specifically designed for range filtering, ACORN does not design an index specifically for range queries; instead, it adopts a pre-filtering strategy, resulting in poorer performance.
-		The performance of vector databases in range queries is also poor, as their database systems also incorporate many other designs that can affect the algorithm's performance.
-Among them, Milvus performed well.
+	}
+
+	%	 修改此处
+	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.
+Unlike other range filtering algorithms, ACORN is not designed with specialized data structures  to achieve efficient range filtering.
+In fact, the graph structure used by ACORN for attribute filtering is the same as that used for range filtering.
+
+%	For third-party library and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. 
+%	%\textcolor{blue}{since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance.
+Similar to the selectivity observed in attribute filtering.
+}
+%	Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors.
+With a smaller range, fewer points remain after filtering, resulting in lower computational cost.
+In addition, the performance of Faiss is influenced by data dimensionality; the higher the dimensionality, the worse the performance.
+
+	Vector databases  show relatively poor performance on range queries.
+Among them, Milvus performs more balanced across both small-range and large-range queries, even surpassing ACORN under high recall settings.
 PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
-	}
+	VBASE performs moderately; it works well for large-range queries, but for small-range queries, although it achieves high recall, its QPS is quite  low.
 

### 2025-07-31 Revision/response.tex

@@
 We acknowledge that the original manuscript did not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard graph-based and IVF-based index structures.
-We have revised Section 2.2 and added two paragraphs.
-These paragraphs summarize how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures.
+We have revised Section 2.2 and added descriptions related to attribute filtering and range filtering.
+We have also summarized how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures.
 \textbf{(Please see Section 2.2, highlighted in blue in the revised manuscript.)}

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).
-In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory.}
+	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms}.
 
@@
 \textcolor{violet}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic.
-Experiments in this paper also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing.
+Our experiments also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing.
 Therefore, IVF-based hybrid query methods represent a very promising research direction.}

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 This flexibility, however, is often counterbalanced by their relatively modest overall search performance.
-Relatively speaking, PASE performs less well across various aspects.}
+Relatively speaking, PASE performs less well across various aspects, which indicates that its strategy of loading data pages on-demand is unsuitable for performance-demanding scenarios.}
 

### 2025-07-31 VLDB2026/main.tex
1

@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).
@@
 	\section{DISCUSSION}
-	Based on the performance of the algorithms on different experimental scenarios, we discuss our findings as follows.
+	\textcolor{orange}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
+Next, we provide a detailed discussion of the advantages and disadvantages of each algorithm.}
 
@@
 	\caption{Algorithm Recommendation}
+	\label{tab:algorithm_recommendation}
 	\resizebox{\textwidth}{!}{
+
 \begin{tabular}{|l|*{16}{c|}}
@@
 	\cline{2-17}
-	& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
-	& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
-	& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
+	& \textbf{UNG} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{Puck} 
+	& \textbf{Win} & \textbf{iRange} & \textbf{SeRF} & \textbf{DSG} & \textbf{UNIFY} 
+	& \textbf{ACORN} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
 	\hline
-	\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
-	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
-	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
-	\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
-	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
-	\textbf{Robust to Multi-Modal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
-	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
-	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
-	\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
+	\textbf{Performance Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
+	\textbf{Fast Index Construction} & M & M & M & M & M & G & P & M & G & P & P & P/P & \textbf{B}/\textbf{B} & G/G & P/M & P/P \\
+	\textbf{Memory Constraint} & M & P & M & M & M & G & P & P & M & P & P & P/P & \textbf{B}/\textbf{B} & G/M & G/M & G/G \\
+	\textbf{Large-Scale Dataset} & \textbf{B} & G & G & P & P & G & \textbf{B} & G & M & M & G & M/P & P/M & P/P & M/M & - \\
+	\textbf{Multi-Modal Dataset} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
+	\textbf{High LID Dataset} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
+	\textbf{Rare Attribute \& Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
+	\textbf{Robust to Attribute Distribution} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
+	\textbf{General-Purpose} & G & G & G & P & P & P & G & P & P & P & G & P & G & G & G & P \\
 	\hline
 \end{tabular}
+
 	}
@@
 \begin{flushleft}
-	\textbf{Performance Levels:} \quad \textbf{S} = Strongest, S = Strong, M = Medium, W = Weak, - = Not Supported \\
-	\textbf{Recommendation:} \quad \faCheck = Recommended, \faTimes = Not Recommended
+	\textbf{Performance Levels:} \quad B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported \\
 \end{flushleft}
@@
 This flexibility, however, is often counterbalanced by their relatively modest overall search performance.
-Relatively speaking, PASE performs less well across various aspects, which indicates that its strategy of loading data pages on-demand is unsuitable for performance-demanding scenarios.}
+Relatively speaking, PASE performs less well across various aspects.}
 

### 2025-07-31 Revision/response.tex

@@
 
-We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. Please refer to the response to Meta R7.
+We conducted experiments on a 100M-scale deep dataset and analyzed the performance of each algorithm on the large dataset. For more details, please refer to our response to Meta R7.
 
@@
 For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository."}
-Regarding experimental parameter selection, we adopted the recommended settings from original papers when available.
-For datasets without suggested parameters, we experimented with different configurations and selected the optimal one for final evaluation.
-Due to the extensive number of datasets and algorithms involved, specific parameters are not listed individually but are provided in our code repository.}
+"Regarding experimental parameter selection, we adopt the recommended settings from original papers when available.
+For datasets without suggested parameters, we test different configurations and select relatively optimal ones for final evaluation.
+Due to the large number of datasets and algorithms involved, specific parameters are not individually listed in the paper but are fully provided in our code repository."}
 
@@
 However, the algorithms we focused on and evaluated in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction.
-Therefore, for the vast majority of algorithms, index partitioning and merging are not involved, which differs from DiskANN's design considerations.
+Therefore, for the vast majority of algorithms, index partitioning and merging are not involved, which differs from the design considerations of DiskANN.
 
@@
 However, in our experiments, we did not enable quantization in any of our experiments.
-Therefore, no quantization time was included in the reported index build times.
+Therefore, no quantization time was included in the reported index construction time.
 
@@
 \textcolor{blue}{"Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
-The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones.
-"}
+The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones."}
 

### 2025-07-31 VLDB2026/main.tex
update fig

@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
+
+	\end{minipage}%
+	\hfill % 在盒子之间添加弹性间距
+	%
+	\begin{minipage}[t]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
+		\hfill
+		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
+
+	\end{minipage}%
+	\hfill
+	%
+	\begin{minipage}[t]{0.203\textwidth}
+		\centering
+		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf}
+
+	\end{minipage}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\setlength{\abovecaptionskip}{0.0cm}
+	\begin{minipage}[t]{0.37\textwidth}
+		\centering
 		\caption{Multi-Modal Datasets}
@@
 	%
-	\begin{minipage}[t]{0.39\textwidth}
-		\centering
-		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
-		\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
+	\begin{minipage}[t]{0.37\textwidth}
+		\centering
 		\caption{Different Platforms}
@@
 	%
-	\begin{minipage}[t]{0.203\textwidth}
-		\centering
-		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
+	\begin{minipage}[t]{0.24\textwidth}
+		\centering
 		\caption{Large-Scale Dataset}
@@
 	\centering
-
 	\includegraphics[width=0.7\textwidth]{figures/exp/range_legend.pdf}
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
+
+	\end{minipage}%
+	\hfill % 在盒子之间添加弹性间距
+	%
+	\begin{minipage}[t]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
+		\hfill
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
+
+	\end{minipage}%
+	\hfill
+	%
+	\begin{minipage}[t]{0.203\textwidth}
+		\centering
+		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf}
+
+	\end{minipage}
+
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\setlength{\abovecaptionskip}{0.0cm}
+	\begin{minipage}[t]{0.37\textwidth}
+		\centering
 		\caption{Multi-Modal Datasets}
@@
 	%
-	\begin{minipage}[t]{0.39\textwidth}
-		\centering
-		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
-		\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
+	\begin{minipage}[t]{0.37\textwidth}
+		\centering
 		\caption{Different Platforms}
@@
 	%
-	\begin{minipage}[t]{0.203\textwidth}
-		\centering
-		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
+	\begin{minipage}[t]{0.24\textwidth}
+		\centering
 		\caption{Large-Scale Dataset}
@@
 	\section{DISCUSSION}
-	\textcolor{orange}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
-Next, we provide a detailed discussion of the advantages and disadvantages of each algorithm.}
+	Based on the performance of the algorithms on different experimental scenarios, we discuss our findings as follows.
 
@@
 	\caption{Algorithm Recommendation}
-	\label{tab:algorithm_recommendation}
 	\resizebox{\textwidth}{!}{
-
 \begin{tabular}{|l|*{16}{c|}}
@@
 	\cline{2-17}
-	& \textbf{UNG} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{Puck} 
-	& \textbf{Win} & \textbf{iRange} & \textbf{SeRF} & \textbf{DSG} & \textbf{UNIFY} 
-	& \textbf{ACORN} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
+	& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
+	& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
+	& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
 	\hline
-	\textbf{Performance Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
-	\textbf{Fast Index Construction} & M & M & M & M & M & G & P & M & G & P & P & P/P & \textbf{B}/\textbf{B} & G/G & P/M & P/P \\
-	\textbf{Memory Constraint} & M & P & M & M & M & G & P & P & M & P & P & P/P & \textbf{B}/\textbf{B} & G/M & G/M & G/G \\
-	\textbf{Large-Scale Dataset} & \textbf{B} & G & G & P & P & G & \textbf{B} & G & M & M & G & M/P & P/M & P/P & M/M & - \\
-	\textbf{Multi-Modal Dataset} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
-	\textbf{High LID Dataset} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
-	\textbf{Rare Attribute \& Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
-	\textbf{Robust to Attribute Distribution} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
-	\textbf{General-Purpose} & G & G & G & P & P & P & G & P & P & P & G & P & G & G & G & P \\
+	\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
+	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
+	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
+	\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
+	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
+	\textbf{Robust to Multi-Modal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
+	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
+	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
+	\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
 	\hline
 \end{tabular}
-
 	}
@@
 \begin{flushleft}
-	\textbf{Performance Levels:} \quad B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported \\
+	\textbf{Performance Levels:} \quad \textbf{S} = Strongest, S = Strong, M = Medium, W = Weak, - = Not Supported \\
+	\textbf{Recommendation:} \quad \faCheck = Recommended, \faTimes = Not Recommended
 \end{flushleft}

### 2025-07-31 VLDB2026/main.tex
change challenge

@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-
-	\end{minipage}%
-	\hfill % 在盒子之间添加弹性间距
-	%
-	\begin{minipage}[t]{0.39\textwidth}
-		\centering
-		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
-		\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
-
-	\end{minipage}%
-	\hfill
-	%
-	\begin{minipage}[t]{0.203\textwidth}
-		\centering
-		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf}
-
-	\end{minipage}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\setlength{\abovecaptionskip}{0.0cm}
-	\begin{minipage}[t]{0.37\textwidth}
-		\centering
 		\caption{Multi-Modal Datasets}
@@
 	%
-	\begin{minipage}[t]{0.37\textwidth}
-		\centering
+	\begin{minipage}[t]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
+		\hfill
+		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
 		\caption{Different Platforms}
@@
 	%
-	\begin{minipage}[t]{0.24\textwidth}
-		\centering
+	\begin{minipage}[t]{0.203\textwidth}
+		\centering
+		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
 		\caption{Large-Scale Dataset}
@@
 	\centering
+
 	\includegraphics[width=0.7\textwidth]{figures/exp/range_legend.pdf}
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
-
-	\end{minipage}%
-	\hfill % 在盒子之间添加弹性间距
-	%
-	\begin{minipage}[t]{0.39\textwidth}
-		\centering
-		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
-		\hfill
-		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
-
-	\end{minipage}%
-	\hfill
-	%
-	\begin{minipage}[t]{0.203\textwidth}
-		\centering
-		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf}
-
-	\end{minipage}
-
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\setlength{\abovecaptionskip}{0.0cm}
-	\begin{minipage}[t]{0.37\textwidth}
-		\centering
 		\caption{Multi-Modal Datasets}
@@
 	%
-	\begin{minipage}[t]{0.37\textwidth}
-		\centering
+	\begin{minipage}[t]{0.39\textwidth}
+		\centering
+		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
+		\hfill
+		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
 		\caption{Different Platforms}
@@
 	%
-	\begin{minipage}[t]{0.24\textwidth}
-		\centering
+	\begin{minipage}[t]{0.203\textwidth}
+		\centering
+		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
 		\caption{Large-Scale Dataset}
@@
 \textcolor{violet}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic.
-Our experiments also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing.
+Experiments in this paper also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing.
 Therefore, IVF-based hybrid query methods represent a very promising research direction.}
@@
 
-%	Our experiments show that graph compression methods often lead to poor query performance in RF-ANN search.
-To address this problem, subsequent algorithms usually optimize the index processing at the segment tree nodes.
-UNIFY newly proposes segment graphs and integrates multiple data structures to process queries.
-Although UNIFY performs slightly worse on small-range queries, its proposed index structure broadens the research direction.
-
 \textcolor{blue}{
-Experimental results show that different algorithms exhibit varying strengths under different query ranges.
+In addition,our experiments show that different algorithms exhibit varying strengths under different query ranges.
 Therefore, designing a general range query algorithm that can adapt to diverse query conditions holds significant research value.
@@
 
-In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement.
+Moreover, in our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement.
 We suggest future future range filtering algorithms include Faiss as a baseline.

### 2025-07-31 Revision/response.tex
Update response.tex
1

@@
 We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
-\textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
-
-\textcolor{blue}{"The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
-When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change."}
 
@@
 As shown in Figure\ref{fig:attribute_distribution} below.
+\textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
+
+\textcolor{blue}{"The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
+When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change."}
 %\textbf{Response:} Thank you for your valuable suggestions.
@@
 
-We also removed the  Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}.
+%We also removed the  Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}.
 We believe these changes improve the clarity and readability of the paper, without reducing the completeness of the evaluation.
@@
 
-	\caption{Different AS under the Same Algorithm}
+	\caption{Performance of Different Attribute Selectivity (AS) under the Same Algorithm}
 	\label{fig:attribute_selectivity}
 \end{figure*}
-\begin{figure}[htbp]
-	\centering
-	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
-	\caption{Different AS under the Same Algorithm}
-	\label{fig:attribute_selectivity_2}
-\end{figure}
+%\begin{figure}[htbp]
+%	\centering
+%	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
+%	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
+%	\caption{Different AS under the Same Algorithm}
+%	\label{fig:attribute_selectivity_2}
+%\end{figure}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We have addressed this issue in detail in our response to Meta R2.
-Specifically, we added complex multimodal query experiments and provided an in-depth analysis of the results.
-For more details, please refer to our response to Meta R2.
+Thank you for your suggestion. We have added complex multi-modal query experiments and provided an in-depth analysis of the results. For more details, please refer to our response to Meta R2.
 %We think this is an excellent suggestion.

### 2025-07-31 VLDB2026/main.tex
1

@@
 
-		\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
+		\caption{Performance of Different Attribute Selectivity (AS) under the Same Algorithm}
 		\label{fig:exp_5_2_combined}
@@
 
+%	Our experiments show that graph compression methods often lead to poor query performance in RF-ANN search.
+To address this problem, subsequent algorithms usually optimize the index processing at the segment tree nodes.
+UNIFY newly proposes segment graphs and integrates multiple data structures to process queries.
+Although UNIFY performs slightly worse on small-range queries, its proposed index structure broadens the research direction.
+
 \textcolor{blue}{
-In addition,our experiments show that different algorithms exhibit varying strengths under different query ranges.
+Experimental results show that different algorithms exhibit varying strengths under different query ranges.
 Therefore, designing a general range query algorithm that can adapt to diverse query conditions holds significant research value.
@@
 
-Moreover, in our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement.
+In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement.
 We suggest future future range filtering algorithms include Faiss as a baseline.

### 2025-07-31 Revision/response.tex
Update response.tex

@@
 Ensuring the readability of the figures is indeed crucial.
-We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
-
-For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Stable and Unstable) in the figure.
+We have revised the relevant figures.
+%We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
+
+As shown in Figure\ref{fig:attribute_distribution} below, for performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Stable and Unstable) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
-As shown in Figure\ref{fig:attribute_distribution} below.
+We have also added descriptions related to the figures.
 \textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
@@
 
-For performance under different attribute selectivity, to reflect the performance differences of each algorithm under different attribute selectivity, we added performance rankings for each algorithm across different selectivity levels in the figure.
-This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
-As shown in Figure~\ref{fig:attribute_selectivity} below.
+As shown in Figure~\ref{fig:attribute_selectivity} below, for performance under different attribute selectivity, to reflect the performance differences of each algorithm under different attribute selectivity, we added performance rankings for each algorithm across different selectivity levels in the figure.
+This provides a clearer illustration of how each algorithm is affected by different attribute selectivity.
 

### 2025-07-31 Revision/response.tex
Update response.tex

@@
 
-Section 4.1.1:\textcolor{blue}{
+Section 4.1.1: \textcolor{blue}{
 "Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.

### 2025-07-31 VLDB2026/main.tex
change main

--- 2025-07-31 VLDB2026/main.tex
@@
 Unlike other algorithms specifically designed for range filtering, ACORN does not design an index specifically for range queries; instead, it adopts a pre-filtering strategy, resulting in poorer performance.
-		The performance of vector databases in range queries is also poor, as their database systems also incorporate many other designs that can affect the algorithm's performance.
-Among them, Milvus performed well.
-PASE performs poorly on small-range queries, with recall lower than 0.1, due to its post-filtering strategy.
+		The performance of vector databases is also poor in range queries, as they are not specifically optimized for such queries.
+PASE performs particularly poorly in small range queries, with a recall rate lower than 0.1, mainly due to its post-filtering strategy.
 	}

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 \usepackage{fontawesome}
+\usepackage{makecell}
+\usepackage{array}
 
@@
 
-		\caption{Performance of Different Attribute Selectivity (AS) under the Same Algorithm}
+		\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
 		\label{fig:exp_5_2_combined}
@@
 	\resizebox{\textwidth}{!}{
-
+\large
 \begin{tabular}{|l|*{16}{c|}}
 	\hline
-	\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
+	\multirow{2}{*}{\textbf{Application Scenarios }} 
 	& \multicolumn{6}{c|}{\textbf{AF}} 
@@
 	\hline
-	\textbf{Performance Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
-	\textbf{Fast Index Construction} & M & M & M & M & M & G & P & M & G & P & P & P/P & \textbf{B}/\textbf{B} & G/G & P/M & P/P \\
-	\textbf{Memory Constraint} & M & P & M & M & M & G & P & P & M & P & P & P/P & \textbf{B}/\textbf{B} & G/M & G/M & G/G \\
-	\textbf{Large-Scale Dataset} & \textbf{B} & G & G & P & P & G & \textbf{B} & G & M & M & G & M/P & P/M & P/P & M/M & - \\
-	\textbf{Multi-Modal Dataset} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
-	\textbf{High LID Dataset} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
-	\textbf{Rare Attribute \& Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
-	\textbf{Robust to Attribute Distribution} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
+	\textbf{Performance-Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
+	\hline
+	\textbf{Index-Efficient} & M & M & M & M & M & G & P & M & G & P & P & P/P & \textbf{B}/\textbf{B} & G/G & P/M & P/P \\
+	\hline
+	\textbf{Memory-Constrained} & M & P & M & M & M & G & P & P & M & P & P & P/P & \textbf{B}/\textbf{B} & G/M & G/M & G/G \\
+	\hline
+	\textbf{Large-Scale} & \textbf{B} & G & G & P & P & G & \textbf{B} & G & M & M & G & M/P & P/M & P/P & M/M & - \\
+	\hline
+	\textbf{Multi-Modal} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
+	\hline
+	\textbf{High-LID} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
+	\hline
+	\textbf{Rare Attribute / Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
+	\hline
+	\textbf{Distribution-Robust} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
+	\hline
 	\textbf{General-Purpose} & G & G & G & P & P & P & G & P & P & P & G & P & G & G & G & P \\
@@
 	}
-	\vspace{1mm}
-\begin{flushleft}
-	\textbf{Performance Levels:} \quad B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported \\
-\end{flushleft}
-	\centering
+%	\vspace{1mm}
+%		\small
+%\begin{flushleft}
+%
+%	\textbf{Performance Levels:} \quad B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported \\
+%	\textit{Performance-Critical}: Requires low latency and high recall.
+%	\textit{Index-Efficient}: Emphasizes lightweight index construction.
+%	\textit{Memory-Constrained}: Operates under limited memory conditions.
+%	\textit{Large-Scale}: Designed for datasets with tens to hundreds of millions of vectors.
+%	\textit{Multi-Modal}: Supports heterogeneous data modalities.
+%	\textit{High-LID}: Robust in high local intrinsic dimensionality spaces.
+%	\textit{Rare Attribute / Low Range}: For filtering with low attribute selectivity or small ranges.
+%	\textit{Distribution-Robust}: Insensitive to shifts in attribute distribution.
+%	\textit{General-Purpose}: Balanced performance across varied scenarios.
+%	
+%\end{flushleft}
+%	\centering
+
+\centering
+
+\footnotesize{
+	\begin{minipage}{\linewidth}
+		\vspace{0.1cm}
+		\textit{Performance Levels:} B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported;
+		\textit{Performance-Critical}: Requires low latency and high recall;
+		\textit{Index-Efficient}: Emphasizes lightweight index construction;
+		\textit{Memory-Constrained}: Operates under limited memory conditions;
+		\textit{Large-Scale}: For scenarios involving datasets at the scale of 100 million vectors;
+		\textit{Multi-Modal}: For multi-modal dataset scenarios;
+		\textit{High-LID}: For complex dataset scenarios;
+		\textit{Rare Attribute / Low Range}: For filtering with low attribute selectivity or small ranges;
+		\textit{Distribution-Robust}: For scenarios with variable attribute distributions;
+		\textit{General-Purpose}: Balanced performance across varied scenarios.
+
+\end{minipage}}
 

### 2025-07-31 Revision/response.tex

@@
 On this latter dataset, we perform both attribute filtering and range queries using combined text and image inputs to analyze the algorithm's robustness under more complex, mixed-modality conditions.
-The experimental results are shown in Figure~\ref{fig:attribute_multimodel} and Figure~\ref{fig:range_multimodel}.
+The experimental results are shown in Figure~\ref{fig:attribute_multimodel} and Figure~\ref{fig:range_multimodel}.\textbf{ (Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)
+	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
+}
 
@@
 Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately.
-\textbf{(Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)
-	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
-}
 

### 2025-07-31 VLDB2026/main.tex
Update response.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 %This dataset contains image and text vectors and is a hybrid multi-modal dataset. 
-On Text2image-Mix dataset,as shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
+On Text2image-Mix dataset, as shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
 Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space.

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 Ensuring the readability of the figures is indeed crucial.
-We have revised the relevant figures.
-%We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
-
-As shown in Figure\ref{fig:attribute_distribution} below, for performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Stable and Unstable) in the figure.
-This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
-We have also added descriptions related to the figures.
+We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor.
 \textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
@@
 When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change."}
+
+For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Stable and Unstable) in the figure.
+This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
+As shown in Figure\ref{fig:attribute_distribution} below.
 %\textbf{Response:} Thank you for your valuable suggestions.
@@
 
-As shown in Figure~\ref{fig:attribute_selectivity} below, for performance under different attribute selectivity, to reflect the performance differences of each algorithm under different attribute selectivity, we added performance rankings for each algorithm across different selectivity levels in the figure.
-This provides a clearer illustration of how each algorithm is affected by different attribute selectivity.
-
-%We also removed the  Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}.
+For performance under different attribute selectivity, to reflect the performance differences of each algorithm under different attribute selectivity, we added performance rankings for each algorithm across different selectivity levels in the figure.
+This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates.
+As shown in Figure~\ref{fig:attribute_selectivity} below.
+
+We also removed the  Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret and somewhat redundant with Figure~\ref{fig:attribute_selectivity}.
 We believe these changes improve the clarity and readability of the paper, without reducing the completeness of the evaluation.
@@
 
-	\caption{Performance of Different Attribute Selectivity (AS) under the Same Algorithm}
+	\caption{Different AS under the Same Algorithm}
 	\label{fig:attribute_selectivity}
 \end{figure*}
-%\begin{figure}[htbp]
-%	\centering
-%	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
-%	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
-%	\caption{Different AS under the Same Algorithm}
-%	\label{fig:attribute_selectivity_2}
-%\end{figure}
+\begin{figure}[htbp]
+	\centering
+	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
+	\caption{Different AS under the Same Algorithm}
+	\label{fig:attribute_selectivity_2}
+\end{figure}
 
@@
 Thank you for your suggestion.
-Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.In fact, current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
-As shown in Figure~\ref{fig:range_2_2}, our experiments also show that the impact of using real attributes versus using IDs on the algorithms is negligible.
-The key factor remains the size of the query range.
-\textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}
+Using ID as an attribute is a prevalent method in current range filtering algorithm evaluations, so we also use ID as attributes in our experiments.
+To conduct a meaningful evaluation, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.
+\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
 

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 Queries are far from the dataset points, and the ground truths are more dispersed.
-To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance.
+To find the groundtruths, algorithms typically need to examine more points, which leads to degraded performance.
 		%	We conduct experiments on the text2image-mix dataset.

### 2025-07-31 Revision/response.tex
change D4

--- 2025-07-31 Revision/response.tex
@@
 	\textcolor{blue}{
-	"ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
-This efficiency stems from its construction process, which closely resembles that of the original HNSW, and from reducing the number of candidate neighbors in the upper layers, thereby lowering computational cost.
-SeRF, another HNSW-based method, also exhibits very short construction time.
-During construction, it attaches timestamp information to edges, keeping the total time comparable to building a single HNSW graph, which enables efficient construction even on large datasets.}
-
-\textcolor{blue}{
-	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
-This design introduces redundant computation and high construction cost.
-However, on large-scale datasets, the preprocessing phase of WinFilter is replaced in the experiments by the base algorithm Vamana-WST, thus avoiding significant time overhead.}
-
-\textcolor{blue}{
-	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
-Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
-
-	\textcolor{blue}{
-	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
-This makes the construction process more complex and costly.
-In addition, on Deep100M, DSG uses single-threaded construction, resulting in the longest build time."}
+	"As shown in Figure 12a, Faiss and Milvus, based on the IVF\_Flat architecture, require less time.
+This indexing structure enables fast construction through subset sampling and centroid computation, thereby reducing computational cost.
+Milvus performs particularly well on large-scale datasets, mainly due to its cache-aware optimizations, which significantly reduce CPU cache misses.}
+
+	\textcolor{blue}{In addition, the two HNSW-based methods, ACORN-1 and SeRF, also achieve short index construction time.
+ACORN-1 closely follows the original HNSW construction process and reduces the number of candidate neighbors in the upper layers to lower computational overhead.
+SeRF attaches timestamp information to edges during construction, making the total build time comparable to that of a single HNSW graph.
+	}
+
+	\textcolor{blue}{We observe that ACORN-\(\gamma\), DSG and WinFilter exhibit relatively long index construction time.
+Although the first two methods are also based on HNSW, ACORN-\(\gamma\) extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
+DSG, on the other hand, incorporates a rectangle tree structure for index management, making the construction process more complex and costly.
+		WinFilter also incurs high construction cost, as it relies on a tree structure and builds a separate nearest neighbor graph for each node, which leads to redundant computations.
+However, on large-scale datasets, its preprocessing stage is replaced by the base algorithm Vamana-WST, effectively avoiding significant time overhead."}
 

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 On this latter dataset, we perform both attribute filtering and range queries using combined text and image inputs to analyze the algorithm's robustness under more complex, mixed-modality conditions.
-The experimental results are shown in Figure~\ref{fig:attribute_multimodel} and Figure~\ref{fig:range_multimodel}.\textbf{ (Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)
-	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
-}
+The experimental results are shown in Figure~\ref{fig:attribute_multimodel} and Figure~\ref{fig:range_multimodel}.
 
@@
 Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately.
-
-Section 4.1.1: \textcolor{blue}{
+\textbf{(Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)
+	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
+}
+
+Section 4.1.1:\textcolor{blue}{
 "Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
@@
 	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}
-	\caption{Attribute Filtering Multi-modal}
+	\caption{Multi-modal Datasets (AF)}
 	\label{fig:attribute_multimodel}
@@
 	\includegraphics[width=\linewidth]{fig/range_multimodel_2.pdf}
-	\caption{Range Filtering Multi-modal}
+	\caption{Multi-modal Datasets (RF)}
 	\label{fig:range_multimodel}
@@
 Thank you for your suggestion.
-Using ID as an attribute is a prevalent method in current range filtering algorithm evaluations, so we also use ID as attributes in our experiments.
-To conduct a meaningful evaluation, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.
-\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
+Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
+To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.In fact, current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
+As shown in Figure~\ref{fig:range_2_2}, our experiments also show that the impact of using real attributes versus using IDs on the algorithms is negligible.
+The key factor remains the size of the query range.
+\textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have added complex multi-modal query experiments and provided an in-depth analysis of the results. For more details, please refer to our response to Meta R2.
+Thank you for your suggestion.
+We have addressed this issue in detail in our response to Meta R2.
+Specifically, we added complex multimodal query experiments and provided an in-depth analysis of the results.
+For more details, please refer to our response to Meta R2.
 %We think this is an excellent suggestion.

### 2025-07-31 Revision/response.tex
gt

--- 2025-07-31 Revision/response.tex
@@
 \textcolor{blue}{
-	"As shown in Figure 12a, Faiss and Milvus, based on the IVF\_Flat architecture, require less time.
-This indexing structure enables fast construction through subset sampling and centroid computation, thereby reducing computational cost.
-Milvus performs particularly well on large-scale datasets, mainly due to its cache-aware optimizations, which significantly reduce CPU cache misses.}
-
-	\textcolor{blue}{In addition, the two HNSW-based methods, ACORN-1 and SeRF, also achieve short index construction time.
-ACORN-1 closely follows the original HNSW construction process and reduces the number of candidate neighbors in the upper layers to lower computational overhead.
-SeRF attaches timestamp information to edges during construction, making the total build time comparable to that of a single HNSW graph.
-	}
-
-	\textcolor{blue}{We observe that ACORN-\(\gamma\), DSG and WinFilter exhibit relatively long index construction time.
-Although the first two methods are also based on HNSW, ACORN-\(\gamma\) extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
-DSG, on the other hand, incorporates a rectangle tree structure for index management, making the construction process more complex and costly.
-		WinFilter also incurs high construction cost, as it relies on a tree structure and builds a separate nearest neighbor graph for each node, which leads to redundant computations.
-However, on large-scale datasets, its preprocessing stage is replaced by the base algorithm Vamana-WST, effectively avoiding significant time overhead."}
+	"ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
+This efficiency stems from its construction process, which closely resembles that of the original HNSW, and from reducing the number of candidate neighbors in the upper layers, thereby lowering computational cost.
+SeRF, another HNSW-based method, also exhibits very short construction time.
+During construction, it attaches timestamp information to edges, keeping the total time comparable to building a single HNSW graph, which enables efficient construction even on large datasets.}
+
+\textcolor{blue}{
+	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
+This design introduces redundant computation and high construction cost.
+However, on large-scale datasets, the preprocessing phase of WinFilter is replaced in the experiments by the base algorithm Vamana-WST, thus avoiding significant time overhead.}
+
+\textcolor{blue}{
+	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
+Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
+
+	\textcolor{blue}{
+	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
+This makes the construction process more complex and costly.
+In addition, on Deep100M, DSG uses single-threaded construction, resulting in the longest build time."}
 

### 2025-07-31 VLDB2026/main.tex
gt

@@
 
-		\item \textbf{Recall@k}: The proportion of overlap between the returned approximate $k$ nearest neighbors and the ground-truth $k$ nearest neighbors.
+		\item \textbf{Recall@k}: The proportion of overlap between the returned approximate $k$ nearest neighbors and the ground truth $k$ nearest neighbors.
 		\item \textbf{QPS (Queries Per Second)}: The number of queries processed per second.
@@
 Queries are far from the dataset points, and the ground truths are more dispersed.
-To find the groundtruths, algorithms typically need to examine more points, which leads to degraded performance.
+To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance.
 		%	We conduct experiments on the text2image-mix dataset.

### 2025-07-31 Revision/response.tex
change D4

--- 2025-07-31 Revision/response.tex
@@
 This offers a more complete comparative view.
-\textbf{(Please see the "Build peak memory" part of Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see the "Peak memory" part of Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
 

### 2025-07-31 Revision/response.tex
1

@@
 	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}
-	\caption{Multi-modal Datasets (AF)}
+	\caption{Attribute Filtering Multi-modal}
 	\label{fig:attribute_multimodel}
@@
 	\includegraphics[width=\linewidth]{fig/range_multimodel_2.pdf}
-	\caption{Multi-modal Datasets (RF)}
+	\caption{Range Filtering Multi-modal}
 	\label{fig:range_multimodel}
@@
 We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+We present the search peak memory usage for the newly added attribute filtering and range filtering in Figure \ref{fig:search_memory_mb_comparison} and Figure \ref{fig:rangeFilter_search_memory_mb}, respectively.
 \textbf{(Please see Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
@@
 Section 4.2.1:
-\textcolor{blue}{"Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
-As a result, peak memory usage during querying is generally slightly lower than during construction.
-However, exceptions exist.
-As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set."}
+\textcolor{blue}{\textit{\textbf{"Peak memory.}}	
+	We present the peak memory usage during index construction and query processing in Figure 3c and Figure 3d, respectively.
+We observe that peak memory usage is generally correlated with the combined size of the index and the dataset.
+Methods that produce larger indexes tend to consume more memory during both construction and querying, and this trend holds consistently across different datasets.}
+
+\textcolor{blue}{However, there are notable exceptions.
+During index construction, PASE adopts an on-demand loading strategy, resulting in build peak memory usage even lower than the final index size.
+NHQ generates a large number of candidate neighbors during construction but retains only a small subset per node in the final index, leading to high peak memory usage despite a relatively compact index.
+During querying, CAPS maintains a large candidate set dynamically, which significantly increases its search peak memory consumption."}
 
@@
  Section 4.3.1:
-\textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend.
-As we analyzed in the section on attribute filtering."}
+\textcolor{blue}{\textit{\textbf{"Peak memory.}}  
+	As explained in the attribute filtering analysis, methods with larger index sizes (including the dataset) tend to exhibit higher peak memory consumption.
+As shown in Figure12c and Figure12d, range filtering also adheres to this pattern.}
+
+	\textcolor{blue}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism.
+Although the final index size remains relatively small, the peak memory usage increases significantly during both construction and search.
+During construction, this is caused by the parallel building of local indices for each tree node, which results in substantial temporary memory usage.
+Similarly, during search, WinFilter needs to load multiple local indices in parallel for different tree nodes, further contributing to high peak memory consumption."}
 
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algo_scenarios}.
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}.
 \textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
@@
 %Based on the performance of different algorithms in experiments, we recommend algorithms suitable for different scenarios, as shown in the table \ref{tab:algo_scenarios}.
-
 \begin{table*}[htbp]
 	\caption{Algorithm Recommendation}
-	\label{tab:algo_scenarios}
+	\label{tab:algorithm_recommendation}
 	\resizebox{\textwidth}{!}{
+		\large
 		\begin{tabular}{|l|*{16}{c|}}
 			\hline
-			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
+			\multirow{2}{*}{\textbf{Application Scenarios }} 
 			& \multicolumn{6}{c|}{\textbf{AF}} 
@@
 			\cline{2-17}
-			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
-			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
-			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
+			& \textbf{UNG} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{Puck} 
+			& \textbf{Win} & \textbf{iRange} & \textbf{SeRF} & \textbf{DSG} & \textbf{UNIFY} 
+			& \textbf{ACORN} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
 			\hline
-			\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
-			\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
-			\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
-			\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
-			\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
-			\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
-			\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
-			\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
-			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
+			\textbf{Performance-Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
+			\hline
+			\textbf{Index-Efficient} & M & M & M & M & M & G & P & M & G & P & P & P/P & \textbf{B}/\textbf{B} & G/G & P/M & P/P \\
+			\hline
+			\textbf{Memory-Constrained} & M & P & M & M & M & G & P & P & M & P & P & P/P & \textbf{B}/\textbf{B} & G/M & G/M & G/G \\
+			\hline
+			\textbf{Large-Scale} & \textbf{B} & G & G & P & P & G & \textbf{B} & G & M & M & G & M/P & P/M & P/P & M/M & - \\
+			\hline
+			\textbf{Multi-Modal} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
+			\hline
+			\textbf{High-LID} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
+			\hline
+			\textbf{Rare Attribute / Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
+			\hline
+			\textbf{Distribution-Robust} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
+			\hline
+			\textbf{General-Purpose} & G & G & G & P & P & P & G & P & P & P & G & P & G & G & G & P \\
 			\hline
 		\end{tabular}
-	}
-	\vspace{1mm}
-\begin{flushleft}
-	\textbf{Performance Levels:} \quad \textbf{S} = Strongest, S = Strong, M = Medium, W = Weak, - = Not Supported \\
-	\textbf{Recommendation:} \quad \faCheck = Recommended, \faTimes = Not Recommended
-\end{flushleft}
-
-	\centering
+
+	}
+
+	\centering
+
+	\footnotesize{
+		\begin{minipage}{\linewidth}
+			\vspace{0.1cm}
+			\textit{Performance Levels:} B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported;
+			\textit{Performance-Critical}: Requires low latency and high recall;
+			\textit{Index-Efficient}: Emphasizes lightweight index construction;
+			\textit{Memory-Constrained}: Operates under limited memory conditions;
+			\textit{Large-Scale}: For scenarios involving datasets at the scale of 100 million vectors;
+			\textit{Multi-Modal}: For multi-modal dataset scenarios;
+			\textit{High-LID}: For complex dataset scenarios;
+			\textit{Rare Attribute / Low Range}: For filtering with low attribute selectivity or small ranges;
+			\textit{Distribution-Robust}: For scenarios with variable attribute distributions;
+			\textit{General-Purpose}: Balanced performance across varied scenarios.
+
+	\end{minipage}}
 
@@
 DSG, on the other hand, incorporates a rectangle tree structure for index management, making the construction process more complex and costly.
+	%	Additionally, DSG builds index using a single thread on the Deep100M dataset, resulting in the longest construction time. 
 	WinFilter also incurs high construction cost, as it relies on a tree structure and builds a separate nearest neighbor graph for each node, which leads to redundant computations.
@@
 This offers a more complete comparative view.
-\textbf{(Please see the "Peak memory" part of Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see the "Build peak memory" part of Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
 

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 %This dataset contains image and text vectors and is a hybrid multi-modal dataset. 
-On Text2image-Mix dataset, as shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
+On Text2image-Mix dataset,as shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
 Although the dataset contains two modalities, due to the significant differences between the modalities, they are actually two separate regions in the vector space.
@@
 	}
-%	\vspace{1mm}
-%		\small
-%\begin{flushleft}
-%
-%	\textbf{Performance Levels:} \quad B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported \\
-%	\textit{Performance-Critical}: Requires low latency and high recall.
-%	\textit{Index-Efficient}: Emphasizes lightweight index construction.
-%	\textit{Memory-Constrained}: Operates under limited memory conditions.
-%	\textit{Large-Scale}: Designed for datasets with tens to hundreds of millions of vectors.
-%	\textit{Multi-Modal}: Supports heterogeneous data modalities.
-%	\textit{High-LID}: Robust in high local intrinsic dimensionality spaces.
-%	\textit{Rare Attribute / Low Range}: For filtering with low attribute selectivity or small ranges.
-%	\textit{Distribution-Robust}: Insensitive to shifts in attribute distribution.
-%	\textit{General-Purpose}: Balanced performance across varied scenarios.
-%	
-%\end{flushleft}
-%	\centering
 

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
+The experimental results are shown in Figure~\ref{fig:attribute_multimodel}.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
@@
 Therefore, different server configurations only affect the performance of individual algorithms, with minimal impact on their relative performance ranking."}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.495\linewidth]{fig/attribute_85.pdf}
+	\includegraphics[width=0.47\linewidth]{fig/attribute_71.pdf}
+	\caption{Different Platforms (AF)}
+	\label{fig:attribute-cross-platform}
+\end{figure}
 

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 
-		\item \textbf{Recall@k}: The proportion of overlap between the returned approximate $k$ nearest neighbors and the ground truth $k$ nearest neighbors.
+		\item \textbf{Recall@k}: The proportion of overlap between the returned approximate $k$ nearest neighbors and the ground-truth $k$ nearest neighbors.
 		\item \textbf{QPS (Queries Per Second)}: The number of queries processed per second.
@@
 Their performance drops less compared to in-distribution (ID) datasets such as GIST1M and GloVe, indicating better adaptability to OOD queries.}
+
 \begin{figure*}
@@
 
-	\end{minipage}%
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.203\textwidth}
+		\centering
+		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf}
+
+	\end{minipage}
 	\hfill % 在盒子之间添加弹性间距
-	%
 	\begin{minipage}[t]{0.39\textwidth}
@@
 
+	\end{minipage}
+
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\setlength{\abovecaptionskip}{0.0cm}
+	\begin{minipage}[t]{0.37\textwidth}
+		\centering
+		\caption{Multi-Modal Datasets (AF)}
+		\label{fig:attribute-multimodal}  
 	\end{minipage}%
 	\hfill
-	%
-	\begin{minipage}[t]{0.203\textwidth}
-		\centering
-		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf}
-
+	\begin{minipage}[t]{0.27\textwidth}
+		\centering
+		\caption{Large-Scale Dataset (AF)}
+		\label{fig:attribute big dataset}
 	\end{minipage}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\setlength{\abovecaptionskip}{0.0cm}
-	\begin{minipage}[t]{0.37\textwidth}
-		\centering
-		\caption{Multi-Modal Datasets}
-		\label{fig:attribute-multimodal}  
-	\end{minipage}%
-	\hfill % 在盒子之间添加弹性间距
-	%
-	\begin{minipage}[t]{0.37\textwidth}
-		\centering
-		\caption{Different Platforms}
+	\hfill 
+	\begin{minipage}[t]{0.35\textwidth}
+		\centering
+		\caption{Different Platforms (AF)}
 		\label{fig:attribute-cross-platform}
 	\end{minipage}%
-	\hfill
-	%
-	\begin{minipage}[t]{0.24\textwidth}
-		\centering
-		\caption{Large-Scale Dataset}
-		\label{fig:attribute big dataset}
-	\end{minipage}
 \end{figure*}
@@
 
+	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} 
+	\textcolor{violet}{As shown in the Figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+However, this also comes with significant memory overhead.
+The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
+Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
+StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
+CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios.}
+
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
@@
 
-	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} 
-	\textcolor{violet}{As shown in the Figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
-However, this also comes with significant memory overhead.
-The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance.
-Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low.
-StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
-CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios.}
 %		we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
@@
 
-	\end{minipage}%
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.203\textwidth}
+		\centering
+		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
+	\end{minipage}
 	\hfill % 在盒子之间添加弹性间距
-	%
 	\begin{minipage}[t]{0.39\textwidth}
@@
 		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
-
+	\end{minipage}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\setlength{\abovecaptionskip}{0.0cm}
+	\begin{minipage}[t]{0.37\textwidth}
+		\centering
+		\caption{Multi-Modal Datasets (RF)}
+		\label{fig:range-multimodal} 
 	\end{minipage}%
 	\hfill
-	%
-	\begin{minipage}[t]{0.203\textwidth}
-		\centering
-		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf}
-
+	\begin{minipage}[t]{0.27\textwidth}
+		\centering
+		\caption{Large-Scale Dataset (RF)}
+		\label{fig: range big dataset}
 	\end{minipage}
-
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\setlength{\abovecaptionskip}{0.0cm}
-	\begin{minipage}[t]{0.37\textwidth}
-		\centering
-		\caption{Multi-Modal Datasets}
-		\label{fig:range-multimodal} 
-	\end{minipage}%
 	\hfill % 在盒子之间添加弹性间距
-	%
-	\begin{minipage}[t]{0.37\textwidth}
-		\centering
-		\caption{Different Platforms}
+	\begin{minipage}[t]{0.35\textwidth}
+		\centering
+		\caption{Different Platforms (RF)}
 		\label{fig:range-cross-platform}
 	\end{minipage}%
-	\hfill
-	%
-	\begin{minipage}[t]{0.24\textwidth}
-		\centering
-		\caption{Large-Scale Dataset}
-		\label{fig: range big dataset}
-	\end{minipage}
+
 \end{figure*}
@@
 
+	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).
+In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory.}
+
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
@@
 Due to space constraints, these details are not reiterated here.}
-
-	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).
-In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory.}
 

### 2025-07-31 Revision/response.tex
Update response.tex

@@
 Queries are far from the dataset points, and the ground truths are more dispersed.
-To find the groundtruths, algorithms typically need to examine more points, which leads to degraded performance."
-}
-
-Section 4.3.3:\textcolor{blue}{
-		"Similar to attribute filtering, on Text2Image-Mix dataset, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
-These algorithms on the Text2Image dataset exhibit a significant performance degradation.
+To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance."
+}
+
+Section 4.3.3: \textcolor{blue}{
+		"Similar to attribute filtering, the performance of range filtering queries on the Text2image-Mix dataset (Figure 14) is similar to the single-modality query performance (Figure 13).
+However, on the Text2Image dataset, these algorithms exhibit a significant performance degradation (Figure 14).
 This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets."
@@
 Thank you for your suggestion.
-Using the ID as an attribute for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations.
-To address this issue, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.In fact, current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
-As shown in Figure~\ref{fig:range_2_2}, our experiments also show that the impact of using real attributes versus using IDs on the algorithms is negligible.
-The key factor remains the size of the query range.
-\textbf{(Please see the third paragraph of Section 4.1.1, highlighted in blue in the revised manuscript.)}
+Using ID as an attribute is a prevalent method in current range filtering algorithm evaluations, so we also use ID as attributes in our experiments.
+To conduct a meaningful evaluation, we have updated two of our datasets (YT-Audio-Real, WIT-Real) to include real attributes.
+\textbf{(Please see Section 4.1.1, highlighted in blue in the revised manuscript.)}
 
 \textcolor{blue}{
-	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes.
+	"WIT-Real and YT-Audio-Real datasets use real attributes.
+For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."
@@
 In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
-The experimental results are shown in Figure~\ref{fig:attribute_multimodel}.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
@@
 Therefore, different server configurations only affect the performance of individual algorithms, with minimal impact on their relative performance ranking."}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.495\linewidth]{fig/attribute_85.pdf}
-	\includegraphics[width=0.47\linewidth]{fig/attribute_71.pdf}
-	\caption{Different Platforms (AF)}
-	\label{fig:attribute-cross-platform}
-\end{figure}
 

### 2025-07-31 Revision/response.tex
change R2 D1

@@
 
-Section 4.3.3: \textcolor{blue}{
-		"Similar to attribute filtering, the performance of range filtering queries on the Text2image-Mix dataset (Figure 14) is similar to the single-modality query performance (Figure 13).
-However, on the Text2Image dataset, these algorithms exhibit a significant performance degradation (Figure 14).
+Section 4.3.3:\textcolor{blue}{
+		"Similar to attribute filtering, on Text2Image-Mix dataset, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
+These algorithms on the Text2Image dataset exhibit a significant performance degradation.
 This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets."
@@
 \textcolor{blue}{
-	"WIT-Real and YT-Audio-Real datasets use real attributes.
-For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes.
+	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."
@@
 Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
- 	Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
+ 	Although existing works [9,50] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
 

### 2025-07-31 Revision/response.tex

@@
 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.495\linewidth]{fig/attribute_85.pdf}
+	\includegraphics[width=0.47\linewidth]{fig/attribute_71.pdf}
+	\caption{Different Platforms (AF)}
+	\label{fig:attribute-cross-platform}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-31 Revision/response.tex

@@
 
-Section 4.3.3:\textcolor{blue}{
-		"Similar to attribute filtering, on Text2Image-Mix dataset, the performance of multi-modal range filtering queries shown in Figure 14 also aligns with the single-modality results in Figure 13.
-These algorithms on the Text2Image dataset exhibit a significant performance degradation.
+Section 4.3.3: \textcolor{blue}{
+		"Similar to attribute filtering, the performance of range filtering queries on the Text2image-Mix dataset (Figure 14) is similar to the single-modality query performance (Figure 13).
+However, on the Text2Image dataset, these algorithms exhibit a significant performance degradation (Figure 14).
 This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets."
@@
 \textcolor{blue}{
-	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes.
+	"WIT-Real and YT-Audio-Real datasets use real attributes.
+For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes.
 The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."

### 2025-07-31 Revision/response.tex
R4

--- 2025-07-31 Revision/response.tex
@@
 In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
-The experimental results are shown in Figure~\ref{fig:attribute_multimodel}.
+The experimental results of attribute filtering and range filtering are shown in Figure~\ref{fig:attribute-cross-platform} and Figure~\ref{fig:range-cross-platform}, respectively.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
@@
 	\label{fig:attribute-cross-platform}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.495\linewidth]{fig/range_85.pdf}
+	\includegraphics[width=0.47\linewidth]{fig/range_71.pdf}
+	\caption{Different Platforms (RF)}
+	\label{fig:range-cross-platform}
 \end{figure}
@@
 Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
- 	Although existing works [9,50] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
+ 	Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
 

### 2025-07-31 Revision/response.tex
change table 2

--- 2025-07-31 Revision/response.tex
@@
 
-	\caption{Comparison of AF-ANN and RF-ANN Search Algorithms}
+	\caption{Overview of AF-ANN and RF-ANN Search Algorithms}
 	\small
@@
 		\\ \hline
-		\multirow{6}{*}{\textbf{AF}} 
+		%		\multirow{6}{*}{\centering\textbf{AF}} 
+		\multirow{6}{*}{\raisebox{4ex}{\textbf{AF}}}
 		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
@@
 			\vspace{0.1cm}
-			Win: WinFilter, Filtered: FilteredVamana, Stitched: StitchedVamana. 
-			\textsuperscript{A} Post-filtering, 
-			\textsuperscript{B} Pre-filtering, 
-			\textsuperscript{C} Simultaneous filtering, 
-			\textsuperscript{Y} Support, 
-			\textsuperscript{N} Unsupport. 
-			\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
-			\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
-			\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
-			\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-			\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-			\textit{Disk Support} indicates whether the algorithm supports disk storage.
-			\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
+			%				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
+			%				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
+			%				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
+			%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+			%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+			%				\textit{Disk Support} indicates whether the algorithm supports disk storage.
+			%				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
+
+				\textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana, \textit{Win}: WinFilter.
+				\textit{AND} / \textit{OR}: Whether the algorithm supports the corresponding logical operations.
+				\textit{Flexible Attributes}: Allows the number of query attributes to differ from that in index construction.
+				\textit{Complex Boolean}: Supports NOT or nested Boolean expressions.
+				\textit{Dynamic Insert}: Supports dynamic data insertion.
+				\textit{Multi Thread}: Supports multi-threaded search.
+				\textit{Disk Support}: Supports disk-based storage.
+				\textit{Base}: Underlying ANN index structure used.
+			\textit{A}: Post-filtering (Filter after ANN search), 
+			\textit{B}: Pre-filtering (Filter before ANN search), 
+			\textit{C}: Simultaneous filtering (Filter simultaneously with ANN search), 
+			\textit{Y}: Support, 
+			\textit{N}: Unsupport. 
 	\end{minipage}}

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
-The experimental results of attribute filtering and range filtering are shown in Figure~\ref{fig:attribute-cross-platform} and Figure~\ref{fig:range-cross-platform}, respectively.
+The experimental results are shown in Figure~\ref{fig:attribute_multimodel}.
 The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.495\linewidth]{fig/range_85.pdf}
-	\includegraphics[width=0.47\linewidth]{fig/range_71.pdf}
-	\caption{Different Platforms (RF)}
-	\label{fig:range-cross-platform}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-Section 4.2.3:\textcolor{blue}{"As shown in the figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Section 4.2.3:\textcolor{blue}{"As shown in the Figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 Section 4.3.3:
-\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}
+\textcolor{blue}{"As shown in the Figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption (Figure 12d).
+In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory."}
 

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.495\linewidth]{fig/attribute_85.pdf}
-	\includegraphics[width=0.47\linewidth]{fig/attribute_71.pdf}
-	\caption{Different Platforms (AF)}
-	\label{fig:attribute-cross-platform}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%
@@
 Thank you for your suggestion.
-Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper..
-At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
-The results are shown in Figure~\ref{fig:recall-latency}:
+Currently, except for Filtered-DiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper.
 \begin{figure}[htbp]
@@
 
+ To analyze the cost breakdown of disk-based methods in greater detail, we also compared the search performance difference of Filtered-DiskANN on memory and SSD using real data sets. 
 We conducted additional experiments on the YT-Audio-Real dataset, comparing three variants of DiskANN.
-(1) SSD-based FilteredDiskANN (original disk-based method);
+(1) SSD-based Filtered-DiskANN (original disk-based method);
 (2) FilteredVamana (memory-based method);
 (3) StitchedVamana (memory-based method).
+We have run all experiments with 32 search threads for fair comparison.
+Figure~\ref{fig:recall-latency} shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:
 
@@
 
-All experiments were run with 32 search threads for fair comparison.
-The following figure shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:
-
-\textbf{ Key Observations:}
 Latency-Recall Tradeoff:
-As expected, SSD-based FilteredDiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
+As expected, SSD-based Filtered-DiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
 When Recall@10 reaches 0.96, its latency increases super-linearly to over 100 ms.
 
-Cost Breakdown of DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
+Cost Breakdown of Filtered-DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
 The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
@@
 
-\textbf{In-memory Methods:}
+In-memory Methods:
 FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
@@
 \textbf{Response:} 
-Thank you for your suggestion.
+We believe your suggestion is very reasonable, and the experiment on search peak memory is indeed an important component.
 We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
@@
 
-Section 4.2.3:\textcolor{blue}{"As shown in the Figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+Section 4.2.3:\textcolor{blue}{"As shown in the figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 Section 4.3.3:
-\textcolor{blue}{"As shown in the Figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption (Figure 12d).
-In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory."}
+\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}
 

### 2025-07-31 Revision/response.tex

--- 2025-07-31 Revision/response.tex
@@
 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.495\linewidth]{fig/range_85.pdf}
+	\includegraphics[width=0.47\linewidth]{fig/range_71.pdf}
+	\caption{Different Platforms (RF)}
+	\label{fig:range-cross-platform}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-31 Revision/response.tex
1

@@
 In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}.
-\textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see Section 5.1, highlighted in blue in the revised manuscript.)}
+
+\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
+"}
 

### 2025-07-31 Revision/response.tex
change R8

--- 2025-07-31 Revision/response.tex
@@
 Thank you for your suggestion.
-Currently, except for Filtered-DiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper.
+Currently, except for FilteredDiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper..
+At the same time, we also compared the search performance difference of FilteredDiskANN on memory and SSD using real data sets.
+The results are shown in Figure~\ref{fig:recall-latency}:
 \begin{figure}[htbp]
@@
 
- To analyze the cost breakdown of disk-based methods in greater detail, we also compared the search performance difference of Filtered-DiskANN on memory and SSD using real data sets. 
 We conducted additional experiments on the YT-Audio-Real dataset, comparing three variants of DiskANN.
-(1) SSD-based Filtered-DiskANN (original disk-based method);
+(1) SSD-based FilteredDiskANN (original disk-based method);
 (2) FilteredVamana (memory-based method);
 (3) StitchedVamana (memory-based method).
-We have run all experiments with 32 search threads for fair comparison.
-Figure~\ref{fig:recall-latency} shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:
 
@@
 
+All experiments were run with 32 search threads for fair comparison.
+The following figure shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:
+
+\textbf{ Key Observations:}
 Latency-Recall Tradeoff:
-As expected, SSD-based Filtered-DiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
+As expected, SSD-based FilteredDiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
 When Recall@10 reaches 0.96, its latency increases super-linearly to over 100 ms.
 
-Cost Breakdown of Filtered-DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
+Cost Breakdown of DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
 The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
@@
 
-In-memory Methods:
+\textbf{In-memory Methods:}
 FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
@@
 \textbf{Response:} 
-We believe your suggestion is very reasonable, and the experiment on search peak memory is indeed an important component.
+Thank you for your suggestion.
 We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
@@
 Thank you very much for your insightful comments.
-We fully agree with your views.
-We have revised the discussion section of the paper accordingly.
-In this section, we have added a recommendation table for the algorithms, which summarizes their performance under various conditions.
-Additionally, we have provided a more in-depth analysis of the internal mechanisms of each algorithm in the text, aiming to uncover the fundamental reasons behind their performance.
+We have revised the discussion section to provide a detailed analysis of the pros and cons of each algorithm, along with an in-depth examination of their internal mechanisms to uncover the fundamental reasons behind their performance.
 \textbf{(Please see Section 5.1.1, Section 5.1.2 and Section 5.1.3, highlighted in blue in the revised manuscript.)}

### 2025-07-31 Revision/response.tex
change D2

@@
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [42,47] significantly impact algorithm performance."}
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [47,52] significantly impact algorithm performance."}
 
 \textcolor{blue}{"
-[42]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
+[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
 }

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 	\centering
+	\includegraphics[width=0.48\textwidth]{fig/attribute_legend.pdf}
 	\includegraphics[width=0.495\linewidth]{fig/attribute_85.pdf}
@@
 	\label{fig:attribute-cross-platform}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.48\textwidth]{fig/range_legend.pdf}
+	\includegraphics[width=0.495\linewidth]{fig/range_85.pdf}
+	\includegraphics[width=0.47\linewidth]{fig/range_71.pdf}
+	\caption{Different Platforms (RF)}
+	\label{fig:range-cross-platform}
 \end{figure}
@@
 Thank you very much for your insightful comments.
-We have revised the discussion section to provide a detailed analysis of the pros and cons of each algorithm, along with an in-depth examination of their internal mechanisms to uncover the fundamental reasons behind their performance.
+We fully agree with your views.
+We have revised the discussion section of the paper accordingly.
+In this section, we have added a recommendation table for the algorithms, which summarizes their performance under various conditions.
+Additionally, we have provided a more in-depth analysis of the internal mechanisms of each algorithm in the text, aiming to uncover the fundamental reasons behind their performance.
 \textbf{(Please see Section 5.1.1, Section 5.1.2 and Section 5.1.3, highlighted in blue in the revised manuscript.)}

### 2025-07-31 Revision/response.tex
big 图

@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{fig/attribute_legend.pdf}
 	\includegraphics[width=0.495\linewidth]{fig/attribute_85.pdf}
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{fig/range_legend.pdf}
 	\includegraphics[width=0.495\linewidth]{fig/range_85.pdf}
@@
 In particular, StitchedVamana performs poorly on Deep100M.
+The experimental results are shown in Figure~\ref{fig:attribute big dataset} and Figure~\ref{fig:range big dataset}.
 \textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
@@
 Section 4.3.3:
-\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d.
-Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}
+\textcolor{blue}{"As shown in the Figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption (Figure 12d).
+In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory."}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/attribute_100M.pdf}
+	\caption{Large-Scale Dataset (AF)}
+	\label{fig:attribute big dataset}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/range_deep100M.pdf}
+	\caption{Large-Scale Dataset (RF)}
+	\label{fig:range big dataset}
+\end{figure}
 

### 2025-07-31 Revision/response.tex

--- 2025-07-31 Revision/response.tex
@@
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [47,52] significantly impact algorithm performance."}
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [42,47] significantly impact algorithm performance."}
 
 \textcolor{blue}{"
-[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
+[42]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
 }

### 2025-07-31 Revision/response.tex

@@
 	\centering
+	\includegraphics[width=0.48\textwidth]{fig/range_legend.pdf}
 	\includegraphics[width=0.495\linewidth]{fig/range_85.pdf}
@@
 In particular, StitchedVamana performs poorly on Deep100M.
-The experimental results are shown in Figure~\ref{fig:attribute big dataset} and Figure~\ref{fig:range big dataset}.
 \textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
@@
 Section 4.3.3:
-\textcolor{blue}{"As shown in the Figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption (Figure 12d).
-In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory."}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/attribute_100M.pdf}
-	\caption{Large-Scale Dataset (AF)}
-	\label{fig:attribute big dataset}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/range_deep100M.pdf}
-	\caption{Large-Scale Dataset (RF)}
-	\label{fig:range big dataset}
-\end{figure}
+\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}
 

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 This flexibility, however, is often counterbalanced by their relatively modest overall search performance.
-Relatively speaking, PASE performs less well across various aspects."}
+Relatively speaking, PASE performs less well across various aspects, which indicates that its strategy of loading data pages on-demand is unsuitable for performance-demanding scenarios."}
 %下面放那个优劣势表
@@
 
-\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
-"}
+\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table 1. "}
 

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 This flexibility, however, is often counterbalanced by their relatively modest overall search performance.
-Relatively speaking, PASE performs less well across various aspects, which indicates that its strategy of loading data pages on-demand is unsuitable for performance-demanding scenarios."}
+Relatively speaking, PASE performs less well across various aspects."}
 %下面放那个优劣势表
@@
 In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}.
-\textbf{(Please see Section 5.1, highlighted in blue in the revised manuscript.)}
-
-\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table 1. "}
+\textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}
 
@@
 Current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
-However, our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
+Our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
 
@@
 We used the YouTube-Audio dataset for vectors and compared results with both synthetic and real attributes (video classification).
-As shown in Figure~\ref{fig:compare}, the experimental outcomes have validated our hypothesis.
+As shown in Figure~\ref{fig:compare}, the experimental outcomes have validated our hypothesis that the impact of using synthetic versus real attributes on the algorithms is limited.
 
@@
 
-	\caption{Overview of AF-ANN and RF-ANN Search Algorithms}
+	\caption{Comparison of AF-ANN and RF-ANN Search Algorithms}
 	\small
@@
 		\\ \hline
-		%		\multirow{6}{*}{\centering\textbf{AF}} 
-		\multirow{6}{*}{\raisebox{4ex}{\textbf{AF}}}
+		\multirow{6}{*}{\textbf{AF}} 
 		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
@@
 			\vspace{0.1cm}
-			%				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
-			%				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
-			%				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
-			%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-			%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-			%				\textit{Disk Support} indicates whether the algorithm supports disk storage.
-			%				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
-
-				\textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana, \textit{Win}: WinFilter.
-				\textit{AND} / \textit{OR}: Whether the algorithm supports the corresponding logical operations.
-				\textit{Flexible Attributes}: Allows the number of query attributes to differ from that in index construction.
-				\textit{Complex Boolean}: Supports NOT or nested Boolean expressions.
-				\textit{Dynamic Insert}: Supports dynamic data insertion.
-				\textit{Multi Thread}: Supports multi-threaded search.
-				\textit{Disk Support}: Supports disk-based storage.
-				\textit{Base}: Underlying ANN index structure used.
-			\textit{A}: Post-filtering (Filter after ANN search), 
-			\textit{B}: Pre-filtering (Filter before ANN search), 
-			\textit{C}: Simultaneous filtering (Filter simultaneously with ANN search), 
-			\textit{Y}: Support, 
-			\textit{N}: Unsupport. 
+			Win: WinFilter, Filtered: FilteredVamana, Stitched: StitchedVamana. 
+			\textsuperscript{A} Post-filtering, 
+			\textsuperscript{B} Pre-filtering, 
+			\textsuperscript{C} Simultaneous filtering, 
+			\textsuperscript{Y} Support, 
+			\textsuperscript{N} Unsupport. 
+			\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
+			\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
+			\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
+			\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
+			\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
+			\textit{Disk Support} indicates whether the algorithm supports disk storage.
+			\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
 	\end{minipage}}

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 
-\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table 1. "}
+\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
+"}
 
@@
 
-\textcolor{blue}{"https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS"}
-
-\textcolor{blue}{"https://github.com/microsoft/DiskANN"}
-
-\textcolor{blue}{"https://github.com/gaurav16gupta/constrainedANN"}
-
-\textcolor{blue}{"https://github.com/stanford-futuredata/ACORN"}
-
-\textcolor{blue}{"https://github.com/YZ-Cai/Unified-Navigating-Graph"}
-
-\textcolor{blue}{"https://github.com/baidu/puck"}
-
-\textcolor{blue}{"https://github.com/rutgers-db/SeRF"}
-
-\textcolor{blue}{"https://github.com/JoshEngels/RangeFilteredANN"}
-
-\textcolor{blue}{"https://github.com/YuexuanXu7/iRangeGraph"}
-
-\textcolor{blue}{"https://github.com/rutgers-db/DynamicSegmentGraph"}
-
-\textcolor{blue}{"https://github.com/sjtu-dbgroup/UNIFY"}
-
-\textcolor{blue}{"https://github.com/facebookresearch/faiss"}
-
-\textcolor{blue}{"https://github.com/alipay/PASE"}
-
-\textcolor{blue}{"https://github.com/microsoft/MSVBASE"}
-
-\textcolor{blue}{"https://github.com/milvus-io/milvus"}
+%\textcolor{blue}{"https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS"}
+%
+%\textcolor{blue}{"https://github.com/microsoft/DiskANN"}
+%
+%\textcolor{blue}{"https://github.com/gaurav16gupta/constrainedANN"}
+%
+%\textcolor{blue}{"https://github.com/stanford-futuredata/ACORN"}
+%
+%\textcolor{blue}{"https://github.com/YZ-Cai/Unified-Navigating-Graph"}
+%
+%\textcolor{blue}{"https://github.com/baidu/puck"}
+%
+%\textcolor{blue}{"https://github.com/rutgers-db/SeRF"}
+%
+%\textcolor{blue}{"https://github.com/JoshEngels/RangeFilteredANN"}
+%
+%\textcolor{blue}{"https://github.com/YuexuanXu7/iRangeGraph"}
+%
+%\textcolor{blue}{"https://github.com/rutgers-db/DynamicSegmentGraph"}
+%
+%\textcolor{blue}{"https://github.com/sjtu-dbgroup/UNIFY"}
+%
+%\textcolor{blue}{"https://github.com/facebookresearch/faiss"}
+%
+%\textcolor{blue}{"https://github.com/alipay/PASE"}
+%
+%\textcolor{blue}{"https://github.com/microsoft/MSVBASE"}
+%
+%\textcolor{blue}{"https://github.com/milvus-io/milvus"}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion.
-We have added experiments on the Deep100M dataset in Section 4.2.3 and Section 4.3.3, and we observed some pitfalls.
-For more details, please refer to our response to Meta R7.
+Thank you for your suggestion. We have added experiments on the Deep100M dataset in Section 4.2.3 and Section 4.3.3. For more details, please refer to our response to Meta R7.
 

### 2025-07-31 Revision/response.tex
1

@@
 Thank you for pointing this out.
-The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49](now [50] in our latest version), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
@@
 
- \textcolor{blue}{"
+ \textcolor{blue}{
 % 	Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
@@
 Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
- 	Although existing works [9,50] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
+ 	"Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking."}
 
@@
  Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
- In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
+% In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
 For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution.
@@
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we have replaced them in the paper with more comprehensive and accurate references.
+Therefore, we have replaced them in the paper with more comprehensive and accurate references.
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
@@
 
-%\textcolor{blue}{"https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS"}
-%
-%\textcolor{blue}{"https://github.com/microsoft/DiskANN"}
-%
-%\textcolor{blue}{"https://github.com/gaurav16gupta/constrainedANN"}
-%
-%\textcolor{blue}{"https://github.com/stanford-futuredata/ACORN"}
-%
-%\textcolor{blue}{"https://github.com/YZ-Cai/Unified-Navigating-Graph"}
-%
-%\textcolor{blue}{"https://github.com/baidu/puck"}
-%
-%\textcolor{blue}{"https://github.com/rutgers-db/SeRF"}
-%
-%\textcolor{blue}{"https://github.com/JoshEngels/RangeFilteredANN"}
-%
-%\textcolor{blue}{"https://github.com/YuexuanXu7/iRangeGraph"}
-%
-%\textcolor{blue}{"https://github.com/rutgers-db/DynamicSegmentGraph"}
-%
-%\textcolor{blue}{"https://github.com/sjtu-dbgroup/UNIFY"}
-%
-%\textcolor{blue}{"https://github.com/facebookresearch/faiss"}
-%
-%\textcolor{blue}{"https://github.com/alipay/PASE"}
-%
-%\textcolor{blue}{"https://github.com/microsoft/MSVBASE"}
-%
-%\textcolor{blue}{"https://github.com/milvus-io/milvus"}
+\textcolor{blue}{"https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS"}
+
+\textcolor{blue}{"https://github.com/microsoft/DiskANN"}
+
+\textcolor{blue}{"https://github.com/gaurav16gupta/constrainedANN"}
+
+\textcolor{blue}{"https://github.com/stanford-futuredata/ACORN"}
+
+\textcolor{blue}{"https://github.com/YZ-Cai/Unified-Navigating-Graph"}
+
+\textcolor{blue}{"https://github.com/baidu/puck"}
+
+\textcolor{blue}{"https://github.com/rutgers-db/SeRF"}
+
+\textcolor{blue}{"https://github.com/JoshEngels/RangeFilteredANN"}
+
+\textcolor{blue}{"https://github.com/YuexuanXu7/iRangeGraph"}
+
+\textcolor{blue}{"https://github.com/rutgers-db/DynamicSegmentGraph"}
+
+\textcolor{blue}{"https://github.com/sjtu-dbgroup/UNIFY"}
+
+\textcolor{blue}{"https://github.com/facebookresearch/faiss"}
+
+\textcolor{blue}{"https://github.com/alipay/PASE"}
+
+\textcolor{blue}{"https://github.com/microsoft/MSVBASE"}
+
+\textcolor{blue}{"https://github.com/milvus-io/milvus"}
 
@@
 \textbf{Response:} 
-Thank you for your suggestion. We have added experiments on the Deep100M dataset in Section 4.2.3 and Section 4.3.3. For more details, please refer to our response to Meta R7.
+Thank you for your suggestion.
+We have added experiments on the Deep100M dataset in Section 4.2.3 and Section 4.3.3, and we observed some pitfalls.
+For more details, please refer to our response to Meta R7.
 

### 2025-07-31 Revision/response.tex
1

@@
 	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/attribute_100M.pdf}
+	\includegraphics[width=0.7\linewidth]{fig/attribute_100M.pdf}
 	\caption{Large-Scale Dataset (AF)}
@@
 	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/range_deep100M.pdf}
+	\includegraphics[width=0.7\linewidth]{fig/range_deep100M.pdf}
 	\caption{Large-Scale Dataset (RF)}

### 2025-07-31 Revision/response.tex
Update response.tex

@@
 	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
-	\includegraphics[width=0.7\linewidth]{fig/attribute_100M.pdf}
+	\includegraphics[width=\linewidth]{fig/attribute_100M.pdf}
 	\caption{Large-Scale Dataset (AF)}
@@
 	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
-	\includegraphics[width=0.7\linewidth]{fig/range_deep100M.pdf}
+	\includegraphics[width=\linewidth]{fig/range_deep100M.pdf}
 	\caption{Large-Scale Dataset (RF)}
@@
 Current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes.
-Our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
+However, our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).
 
@@
 We used the YouTube-Audio dataset for vectors and compared results with both synthetic and real attributes (video classification).
-As shown in Figure~\ref{fig:compare}, the experimental outcomes have validated our hypothesis that the impact of using synthetic versus real attributes on the algorithms is limited.
+As shown in Figure~\ref{fig:compare}, the experimental outcomes have validated our hypothesis.
 
@@
 Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
- 	Although existing works [9,50] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
+"Although existing works [9,50] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
 

### 2025-07-31 Revision/response.tex

--- 2025-07-31 Revision/response.tex
@@
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-For the two parts you suggested, we have replaced them in the paper with more comprehensive and accurate references.
+Therefore, we have replaced them in the paper with more comprehensive and accurate references.
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [47,52] significantly impact algorithm performance."}
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [42,47] significantly impact algorithm performance."}
 
 \textcolor{blue}{"
-[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
+[42]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
 }

### 2025-07-31 Revision/response.tex
1

@@
 \textbf{Response:} 
-Thank you for your suggestion. %We have already addressed this issue in detail in our responses to Meta R8 and R9. 
+Thank you for your suggestion. 
 We have addressed this issue in the revised manuscript by
-%Specifically, we 
 analyzing the strengths and weaknesses of each algorithm and recommended those with strong performance.
-Additionally, we provided a summary table illustrating how each algorithm performs across different application scenarios.
+Additionally, we provided a recommendation table illustrating how each algorithm performs across different application scenarios.
 For more details, please refer to our responses to Meta R8 and R9.

### 2025-07-31 Revision/response.tex
Update response.tex

@@
 We agree that the initial explanations accompanying the performance results were not sufficiently detailed in highlighting the strengths and weaknesses of the compared algorithms.
-We have conducted a more in-depth analysis of the reasons behind certain behaviors observed in the experimental results.
+We have meticulously examined each algorithm and incorporated relevant analyses in the experimental section.
+\textbf{(Please see Section 4.2 and 4.3, highlighted in blue in the revised manuscript.)}
 %下面写每个修改过的理由
@@
 \textbf{Response:} 
-Thank you for your suggestion. 
+Thank you for your suggestion. %We have already addressed this issue in detail in our responses to Meta R8 and R9. 
 We have addressed this issue in the revised manuscript by
+%Specifically, we 
 analyzing the strengths and weaknesses of each algorithm and recommended those with strong performance.
-Additionally, we provided a recommendation table illustrating how each algorithm performs across different application scenarios.
+Additionally, we provided a summary table illustrating how each algorithm performs across different application scenarios.
 For more details, please refer to our responses to Meta R8 and R9.
@@
 
-For datasets with recommended parameters provided in the original papers, we directly used those recommended settings.
-For other datasets, we selected the parameter combinations that performed best through empirical evaluation.
+For datasets with recommended parameters provided in the original papers, we directly used those recommended parameters.
+For other datasets, we selected relatively optimal parameters through experimental evaluation.
 All parameters used in the experiments are available in our public code repository.

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
-		\caption{\textcolor{violet}{Time and Space Overhead}}
+		\caption{\textcolor{violet}{Time and Space Overhead (AF)}}
 		\label{fig:build_index_comparison}
@@
 The performance is similar to that of the single-modal dataset in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
-This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.This is not actually a difficult query.
+This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.
+This is not actually a difficult query.
 %		Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
@@
 %		\caption{Time and space overhead of index construction}
-		\caption{\textcolor{violet}{Time and Space Overhead}}
+		\caption{\textcolor{violet}{Time and Space Overhead (RF)}}
 		\label{fig:rangeFilter_build_index_comparison}
@@
 	\textcolor{blue}{
-		As shown in Figure~\ref{fig:exp_8_2}, the algorithms that performed well are WinFilter, iRange, UNIFY and Faiss.
+		As shown in Figure~\ref{fig:exp_8_2}, the algorithms that performed well are WinFilter, iRange, UNIFY, and Faiss.
 	WinFilter maintains optimal performance by building an index for each tree node. It then performs an ANN search on the relevant nodes and post-filters the results, ensuring high recall and QPS.
@@
 
-	\textcolor{blue}{SeRF, ACORN and vector databases performed poorly.
+	\textcolor{blue}{SeRF, ACORN, and vector databases performed poorly.
 		SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
@@
 		The overall performance of ACORN is poor.
-Unlike other algorithms specifically designed for range filtering, ACORN does not design an index specifically for range queries; instead, it adopts a pre-filtering strategy, resulting in poorer performance.
+Unlike other algorithms specifically designed for range filtering, ACORN does not design an index specifically for range queries.
+Instead, it adopts a pre-filtering strategy, resulting in poorer performance.
 		The performance of vector databases is also poor in range queries, as they are not specifically optimized for such queries.

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 
-\textcolor{blue}{"In this experiment, we only evaluate the algorithms that support this query scenario."}
+\textcolor{blue}{"In this experiment, we only evaluate the algorithms that support this multi-attribute query scenario."}
 

### 2025-07-31 Revision/response.tex
1

@@
 
-\begin{figure}[t]
-	\centering
-
-	% 上面的图例，居中并可通过 hspace 调整左右位置
-	\hspace*{8pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-	\includegraphics[width=0.9\columnwidth]{fig/range_2_2_legend.pdf} % 图例图片路径
-
-	% --- 不再使用 subfigure ---
-	% 直接放置第二张图片，可以加一点垂直间距
-	\vspace{5pt} 
-	\includegraphics[width=0.95\columnwidth]{fig/range_2_2.pdf}
-
-	\caption{Comparison of Real and Synthetic Attributes}
-	\label{fig:range_2_2}
-
-\end{figure}
+%\begin{figure}[t]
+%	\centering
+%	
+%	% 上面的图例，居中并可通过 hspace 调整左右位置
+%	\hspace*{8pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
+%	\includegraphics[width=0.9\columnwidth]{fig/range_2_2_legend.pdf} % 图例图片路径
+%	
+%	% --- 不再使用 subfigure ---
+%	% 直接放置第二张图片，可以加一点垂直间距
+%	\vspace{5pt} 
+%	\includegraphics[width=0.95\columnwidth]{fig/range_2_2.pdf}
+%	
+%	\caption{Comparison of Real and Synthetic Attributes}
+%	\label{fig:range_2_2}
+%	
+%\end{figure}
 
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.48\textwidth]{fig/range_legend.pdf}
-	\includegraphics[width=0.495\linewidth]{fig/range_85.pdf}
-	\includegraphics[width=0.47\linewidth]{fig/range_71.pdf}
-	\caption{Different Platforms (RF)}
-	\label{fig:range-cross-platform}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%
@@
 Section 4.3.3:
-\textcolor{blue}{"As shown in the Figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
-However, their high performance is achieved at the cost of extremely high memory consumption (Figure 12d).
-In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory."}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
-	\includegraphics[width=0.7\linewidth]{fig/attribute_100M.pdf}
-	\caption{Large-Scale Dataset (AF)}
-	\label{fig:attribute big dataset}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
-	\includegraphics[width=0.7\linewidth]{fig/range_deep100M.pdf}
-	\caption{Large-Scale Dataset (RF)}
-	\label{fig:range big dataset}
-\end{figure}
+\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d.
+Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}
 
@@
 Thank you for pointing this out.
-The original reference [49](now [50] in our latest version), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49], now updated to reference [45], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
@@
 
- \textcolor{blue}{
+ \textcolor{blue}{"
 % 	Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms.
@@
 Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
- 	"Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking."}
+ 	Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
 
@@
  Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
-% In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
+ In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios.
 For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution.
@@
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-Therefore, we have replaced them in the paper with more comprehensive and accurate references.
+For the two parts you suggested, we have replaced them in the paper with more comprehensive and accurate references.
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
@@
 
-\textcolor{blue}{"In this experiment, we only evaluate the algorithms that support this multi-attribute query scenario."}
+\textcolor{blue}{"In this experiment, we only evaluate the algorithms that support this query scenario."}
 

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
-	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 9 real-world datasets.
+	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 11 real-world datasets.
 By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method.
@@
 	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
-	We benchmark algorithms that support range filtering on 5 real-world datasets, using varying query range settings in the experiments.
+	We benchmark algorithms that support range filtering on 6 real-world datasets, using varying query range settings in the experiments.
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
@@
 	%We briefly introduce the fundamental principles of these two types in the following.
-	\textcolor{violet}{Here, we briefly review the core concepts of these indexes and outline how attributes and range constraints are embedded to support hybrid queries functionality.}
+	\textcolor{violet}{Here, we briefly review the core concepts of these indexes and outline how attribute and range constraints are embedded to support hybrid queries functionality.}
 
@@
 This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
-In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size.This is because their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
+In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size.
+This is because their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}
 

### 2025-07-31 Revision/response.tex

--- 2025-07-31 Revision/response.tex
@@
 We agree that the initial explanations accompanying the performance results were not sufficiently detailed in highlighting the strengths and weaknesses of the compared algorithms.
-We have meticulously examined each algorithm and incorporated relevant analyses in the experimental section.
-\textbf{(Please see Section 4.2 and 4.3, highlighted in blue in the revised manuscript.)}
+We have conducted a more in-depth analysis of the reasons behind certain behaviors observed in the experimental results.
 %下面写每个修改过的理由
@@
 
-For datasets with recommended parameters provided in the original papers, we directly used those recommended parameters.
-For other datasets, we selected relatively optimal parameters through experimental evaluation.
+For datasets with recommended parameters provided in the original papers, we directly used those recommended settings.
+For other datasets, we selected the parameter combinations that performed best through empirical evaluation.
 All parameters used in the experiments are available in our public code repository.

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 
+Regarding your review comment, we did indeed try to find suitable e-commerce datasets to better align with the application scenarios mentioned in the introduction.
+We investigated some publicly available e-commerce datasets, such as ecommerce\_product\_images\_18K and MEP-3M datasets.
+However, we found that neither of these datasets fully met our requirements for conducting hybrid querying experiments.
+Specifically, the ecommerce\_product\_images\_18K dataset was too small to effectively evaluate the performance and scalability of hybrid querying algorithms under large-scale datasets.
+On the other hand, while the MEP-3M dataset was larger, it did not directly provide image data that could be encoded into vectors, and we were unable to find suitable fields for vectorization.
+As we were unable to locate an ideal e-commerce dataset that simultaneously contained sufficient scale of both vectors and structured attributes, we ultimately decided to continue using the WIT and YouTube-Audio datasets, which are widely employed in existing hybrid querying algorithm research.
+These datasets feature real attribute information and have been broadly accepted by the community as standard benchmarks for evaluating hybrid query performance.
+We believe that despite not being directly from e-commerce platforms, their data characteristics and complexity are sufficient to support our comprehensive evaluation and in-depth analysis of hybrid querying algorithms.
+
 %%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
@@
 Thank you for pointing this out.
-The original reference [49](now [50] in our latest version), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49], now updated to reference [50], provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
@@
 Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
- 	"Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking."}
+ 	Although existing works [9,50] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking. "}
 
@@
 There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V.
-Therefore, we have replaced them in the paper with more comprehensive and accurate references.
+For the two parts you suggested, we have replaced them in the paper with more comprehensive and accurate references.
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
-\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [42,47] significantly impact algorithm performance."}
+\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [47,52] significantly impact algorithm performance."}
 
 \textcolor{blue}{"
-[42]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
+[47]Jianguo Wang, Xiaomeng Yi, Rentong Guo, and et al. 2021. Milvus: A PurposeBuilt Vector Data Management System. In SIGMOD Conference. ACM, 2614-2627."
 }
@@
 This is a major limitation of current range filtering methods.
-We have clearly pointed this out in Section 5.2.2 of the "Discussion" part of the paper and listed it as an important challenge for future work.
-Thank you for highlighting this point, which further emphasizes the significance of our work.
-\textbf{(Please see the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript.)}
-
-To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3. \textbf{(Please see Section 4.3, highlighted in blue in the revised manuscript.)}
+We have added a more detailed explanation of the range attribute in Section 4.3.
+\textbf{(Please see Section 4.3, highlighted in blue in the revised manuscript.)}
 

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 Such scenarios necessitate a retrieval system capable of simultaneously addressing vector similarity (e.g., product image) and attribute constraints (e.g., brand name) \cite{tian2023approximate}.
-When the constraint involves a specific attribute value, this problem refers to Attribute Filtering Approximate Nearest Neighbor (AF-ANN) search ~\cite{NHQ,Filtered-diskann} .
+When the constraint involves a specific attribute value, this problem refers to Attribute Filtering Approximate Nearest Neighbor (AF-ANN) search ~\cite{NHQ,Filtered-diskann}.
 For example, a user may seek a green piece of clothing.
@@
 	\textcolor{orange}{Figure~\ref{fig:exp_5_2_1} shows the algorithms suitable for low AS.}
-	\textcolor{orange}{ACORN-1}, Faiss, Puck and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
+	\textcolor{orange}{ACORN-1}, Faiss, Puck, and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
 \textcolor{orange}{Pre-filtering strategies significantly reduce the number of candidate points under low AS, thereby lowering the cost of  computations.
-As a result, such strategies tend to perform better in low AS scenarios.}CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
+As a result, such strategies tend to perform better in low AS scenarios.} CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
 However, as AS increases, it must process more subpartitions and handle a larger dataset.

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
-Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK)."}
+Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, Puck)."}
 

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 Of all the evaluated algorithms, Faiss, Puck, Filtered-DiskANN, and Milvus support quantization.
-However, in our experiments, we did not enable quantization in any of our experiments.
-Therefore, no quantization time was included in the reported index construction time.
+However, quantization serves to reduce memory usage during queries by sacrificing query accuracy.
+Given that most of the graph-based algorithms involved in this paper (with the exception of Filtered-DiskANN) do not support quantization, we do not enable quantization in our experiments for a fair comparison.
+Therefore, the reported index construction time does not include quantization time.
 
@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-Since other algorithms also do not support multi-attribute queries, we have explained this situation collectively in the corresponding section of the paper to save space.
+Given that some other algorithms also do not support multi-attribute queries, we have provided a unified explanation for this situation in the corresponding section of the paper.
 (\textbf{Please see the "Multi-Attribute Construction and Multi-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.})
 
-\textcolor{blue}{"In this experiment, we only evaluate the algorithms that support this multi-attribute query scenario."}
+\textcolor{blue}{"In this experiment, we only evaluate the algorithms that support this query scenario."}
 

### 2025-07-31 Revision/response.tex

--- 2025-07-31 Revision/response.tex
@@
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
-Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, Puck)."}
+Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK)."}
 
@@
 The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included.
-Since other algorithms also do not support multi-attribute queries, we have explained this situation collectively in the corresponding section of the paper to save space.
+Given that some other algorithms also do not support multi-attribute queries, we have provided a unified explanation for this situation in the corresponding section of the paper.
 (\textbf{Please see the "Multi-Attribute Construction and Multi-Attribute Query" part of Section 4.2.2, highlighted in blue in the revised manuscript.})

### 2025-07-31 VLDB2026/main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 Such scenarios necessitate a retrieval system capable of simultaneously addressing vector similarity (e.g., product image) and attribute constraints (e.g., brand name) \cite{tian2023approximate}.
-When the constraint involves a specific attribute value, this problem refers to Attribute Filtering Approximate Nearest Neighbor (AF-ANN) search ~\cite{NHQ,Filtered-diskann}.
+When the constraint involves a specific attribute value, this problem refers to Attribute Filtering Approximate Nearest Neighbor (AF-ANN) search ~\cite{NHQ,Filtered-diskann} .
 For example, a user may seek a green piece of clothing.
@@
 	\textcolor{orange}{Figure~\ref{fig:exp_5_2_1} shows the algorithms suitable for low AS.}
-	\textcolor{orange}{ACORN-1}, Faiss, Puck, and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
+	\textcolor{orange}{ACORN-1}, Faiss, Puck and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
 \textcolor{orange}{Pre-filtering strategies significantly reduce the number of candidate points under low AS, thereby lowering the cost of  computations.
-As a result, such strategies tend to perform better in low AS scenarios.} CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
+As a result, such strategies tend to perform better in low AS scenarios.}CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
 However, as AS increases, it must process more subpartitions and handle a larger dataset.
@@
 The performance is similar to that of the single-modal dataset in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
-This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.
-This is not actually a difficult query.
+This is because mixed multi-modal queries are actually the same as conducting experiments on two datasets of the same modality.This is not actually a difficult query.
 %		Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
@@
 \textcolor{orange}{Notably, all algorithms use single-threaded index construction on medium-scale datasets, and 64-thread construction on the large-scale Deep100M dataset, except DSG, which only supports single-threading.
-For WinFilter, we use Super Postfiltering on medium datasets for best performance, and switch to the base algorithm Vamana-WST on Deep100M due to construction overhead.
+For WinFilter, we use its integrated Super-Postfiltering on medium datasets for best performance, and switch to its base algorithm Vamana-WST on Deep100M due to construction overhead.
 	}
@@
 	\textcolor{orange}{
-	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF\_Flat architecture, require less time.
+	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF architecture, require less time.
 This indexing structure enables fast construction through subset sampling and centroid computation, thereby reducing computational cost.
@@
 This ID is pre-sorted according to its corresponding real attribute, allowing us to map an attribute to its ID without loss of generality for efficient range queries.}
-	Based on this definition, we evaluate algorithm performance under four query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
-For space considerations, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
+	Based on this definition, we evaluate algorithm performance under the largest ($2^{-2}$) and smallest ($2^{-8}$) query range settings.
+We report the results for these two representative cases in Figure~\ref{fig:exp_8_2}.
 %	The experimental results show consistent performance across all datasets and query ranges.
@@
 	\textcolor{blue}{
-		As shown in Figure~\ref{fig:exp_8_2}, the algorithms that performed well are WinFilter, iRange, UNIFY, and Faiss.
+		As shown in Figure~\ref{fig:exp_8_2}, the algorithms that performed well are WinFilter, iRange, UNIFY and Faiss.
 	WinFilter maintains optimal performance by building an index for each tree node. It then performs an ANN search on the relevant nodes and post-filters the results, ensuring high recall and QPS.
@@
 
-	\textcolor{blue}{SeRF, ACORN, and vector databases performed poorly.
+	\textcolor{blue}{SeRF, ACORN and vector databases performed poorly.
 		SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
@@
 		The overall performance of ACORN is poor.
-Unlike other algorithms specifically designed for range filtering, ACORN does not design an index specifically for range queries.
-Instead, it adopts a pre-filtering strategy, resulting in poorer performance.
+Unlike other algorithms specifically designed for range filtering, ACORN does not design an index specifically for range queries; instead, it adopts a pre-filtering strategy, resulting in poorer performance.
 		The performance of vector databases is also poor in range queries, as they are not specifically optimized for such queries.
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the Deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 
-However, we agree with your point.
+We agree with your point of view.
 To provide a more comprehensive evaluation, we have added the peak memory usage data of the database systems  in the revised version of the paper.
@@
 
-Once again, thank you for your constructive comments. Your valuable feedback has helped us improve the paper further.
+\textcolor{blue}{
+}
 

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
-Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK).}
+Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, Puck).}
 %	IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 For range filtering, we also evaluate the algorithm performance across the 3 metrics through controlled variation of query ranges.
-	\textcolor{orange}{In the experiments, we constructed standardized attribute and range sets for attribute filtering and range filtering, respectively, enabling a unified comparison of algorithms in terms of index construction efficiency and query performance.
+	\textcolor{blue}{In the experiments, we constructed standardized attribute and range sets for attribute filtering and range filtering, respectively, enabling a unified comparison of algorithms in terms of index construction efficiency and query performance.
 Furthermore, we evaluate the robustness of the algorithms across multiple dimensions, including different data distributions, platforms, and scalability on a 100M-scale dataset.}
@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely relates to structured data.
-For attribute filtering algorithms, \textcolor{violet}{factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity ~\cite{analyticdb,milvus} significantly impact algorithm performance.} As for range filtering algorithms, the size of the query range and the characteristics of different datasets play an important role in determining algorithm performance.
-
-	\textcolor{violet}{Although existing works~\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking.
+For attribute filtering algorithms, \textcolor{blue}{factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity ~\cite{analyticdb,milvus} significantly impact algorithm performance.} As for range filtering algorithms, the size of the query range and the characteristics of different datasets play an important role in determining algorithm performance.
+
+	\textcolor{blue}{Although existing works~\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking.
 Despite BigANN 2023~\cite{bigann2023} evaluates the performance of some hybrid query algorithms, it still presents the following notable limitations:
@@
 
-	\textcolor{violet}{To fill this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+	\textcolor{blue}{To fill this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
 Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
@@
 	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying vector datasets, attribute distributions, number of attributes participating in index construction, number of query attributes, and selectivity.
+We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{blue}{including varying vector datasets, attribute distributions, number of attributes participating in index construction, number of query attributes, and selectivity.
 Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and two multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
@@
 
-		Let \( D = \{(v_1, \textcolor{cyan}{a}_1), \ldots, (v_n, \textcolor{cyan}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
+		Let \( D = \{(v_1, \textcolor{blue}{a}_1), \ldots, (v_n, \textcolor{blue}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
 Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).
@@
 	%We briefly introduce the fundamental principles of these two types in the following.
-	\textcolor{violet}{Here, we briefly review the core concepts of these indexes and outline how attribute and range constraints are embedded to support hybrid queries functionality.}
+	\textcolor{blue}{Here, we briefly review the core concepts of these indexes and outline how attribute and range constraints are embedded to support hybrid queries functionality.}
 
 	\noindent\textbf{\underline{Graph.}}
-	\textcolor{violet}{Graph structures accelerate ANN search by connecting each data point with its nearest neighbors, as shown in Figure~\ref{fig:graph}.
+	\textcolor{blue}{Graph structures accelerate ANN search by connecting each data point with its nearest neighbors, as shown in Figure~\ref{fig:graph}.
 During querying, algorithms start from an initial point and use a greedy strategy to progressively move towards closer neighbors until convergence (e.g., the path from $c$ to $j$ in the 1NN case).}
 
-	\textcolor{violet}{Graph indexes are widely used in hybrid ANN search due to their efficiency.
+	\textcolor{blue}{Graph indexes are widely used in hybrid ANN search due to their efficiency.
 To support hybrid queries, in attribute filtering, a common practice involves attaching attribute metadata to nodes or edges, thereby skipping parts that do not satisfy query conditions during traversal (e.g., NHQ, Filtered-DiskANN, ACORN).
@@
 	\noindent\textbf{\underline{IVF.}} 
-	\textcolor{violet}{IVF divides data into multiple clusters through through a clustering algorithm (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
+	\textcolor{blue}{IVF divides data into multiple clusters through through a clustering algorithm (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
 During querying, algorithms search only within the few clusters closest to the query point, which reduces computational load.}
 
-	\textcolor{violet}{IVF-based indexes also offer unique advantages in hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
+	\textcolor{blue}{IVF-based indexes also offer unique advantages in hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
-Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK).}
+Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, Puck).}
 %	IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
@@
 
-		\caption{\textcolor{orange}{Overview of AF-ANN and RF-ANN Search Algorithms}}
+		\caption{\textcolor{blue}{Overview of AF-ANN and RF-ANN Search Algorithms}}
 		\small
@@
 %				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
-		\textcolor{orange}{
+		\textcolor{blue}{
 		\textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana, \textit{Win}: WinFilter.
@@
 %	ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of prior methods in large-scale or unknown predicate scenarios.
-	\textcolor{orange}{ACORN adopts a predicate-agnostic indexing framework.
+	\textcolor{blue}{ACORN adopts a predicate-agnostic indexing framework.
 It is based on Hierarchical Navigable Small World (HNSW) \cite{hnsw} and builds a denser hierarchical graph through neighborhood expansion and edge pruning.}
@@
 
-	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
+	\textcolor{blue}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
 
@@
 
-	\textcolor{violet}{The first seven datasets are widely used in existing works.
+	\textcolor{blue}{The first seven datasets are widely used in existing works.
 As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.
@@
 
-	\textcolor{violet}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
+	\textcolor{blue}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
 The Text2Image dataset includes two versions.
@@
 		\item \textbf{Index Size}: The storage size of the persisted index on disk.
-		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction \textcolor{cyan}{and search}.
+		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction \textcolor{blue}{and search}.
 	\end{enumerate}
@@
 
-	\subsubsection{\textcolor{cyan}{Setting}}
+	\subsubsection{\textcolor{blue}{Setting}}
 
@@
 
-	\textcolor{cyan}{
+	\textcolor{blue}{
 	Regarding experimental parameter selection, we adopt the recommended settings from original papers when available.
@@
 	%4.2.1
-	\subsubsection{\textcolor{violet}{Time and Space overhead}}
+	\subsubsection{\textcolor{blue}{Time and Space overhead}}
 	% \subsubsection{\textbf{Attribute Filtering}}
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
-		\caption{\textcolor{violet}{Time and Space Overhead (AF)}}
+		\caption{\textcolor{blue}{Time and Space Overhead (AF)}}
 		\label{fig:build_index_comparison}
@@
 
-	\textcolor{violet}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}.
+	\textcolor{blue}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{blue}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{blue}{build peak memory and search peak memory}.
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
-\textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other 6 medium-scale datasets.
+\textcolor{blue}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other 6 medium-scale datasets.
 Notably, the VBASE and PASE algorithms only support single-threaded construction.}
@@
 }
-\textcolor{red}{On the medium-scale datasets (Figure~\ref{fig:build_time_comparison_query1} left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
+\textcolor{blue}{On the medium-scale datasets (Figure~\ref{fig:build_time_comparison_query1} left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
 This is because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency.
@@
 
-\textcolor{red}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1} right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
+\textcolor{blue}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1} right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
 This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
@@
 \textit{\textbf{Index size.}}
-\textcolor{orange}{
+\textcolor{blue}{
 	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
@@
 As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
-\textcolor{orange}{\textit{\textbf{Peak memory.}}	
+\textcolor{blue}{\textit{\textbf{Peak memory.}}	
 We present the peak memory usage during index construction and query processing in Figure~\ref{fig:build_memory_mb_comparison} and Figure~\ref{fig:search_memory_mb_comparison}, respectively.
@@
 
-\textcolor{orange}{However, there are notable exceptions.
+\textcolor{blue}{However, there are notable exceptions.
 During index construction, PASE adopts an on-demand loading strategy, resulting in build peak memory usage even lower than the final index size.
@@
 
-	\textcolor{violet}{NHQ and StitchedVamana also perform well and show similar and stable performance across all datasets.
+	\textcolor{blue}{NHQ and StitchedVamana also perform well and show similar and stable performance across all datasets.
 This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.} StitchedVamana outperforms FilteredVamana in query efficiency.
@@
 However, this also demonstrates that IVF-based methods remain very promising for hybrid queries.
-	\textcolor{violet}{Additionally, Puck and CAPS also perform relatively well.
+	\textcolor{blue}{Additionally, Puck and CAPS also perform relatively well.
 They further reduce the search space on IVF indexes by using attribute partitioning, thereby achieving solid search performance.}
@@
 In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason.
-	\textcolor{orange}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity.
+	\textcolor{blue}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity.
 This makes single-attribute queries more difficult and degrades performance.}
@@
 To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
-\textcolor{violet}{In this experiment, we only evaluate algorithms that support this multi-attribute query scenario.}
+\textcolor{blue}{In this experiment, we only evaluate algorithms that support this multi-attribute query scenario.}
 
@@
 
-	\textit{\textbf{Attribute Distribution.}} To evaluate the impact of attribute distribution, we generate base and query attributes \textcolor{orange}{on the SIFT dataset using four representative distributions: long-tail, normal, power-law, and uniform.}
+	\textit{\textbf{Attribute Distribution.}} To evaluate the impact of attribute distribution, we generate base and query attributes \textcolor{blue}{on the SIFT dataset using four representative distributions: long-tail, normal, power-law, and uniform.}
 %	with four representative distributions—long-tail, normal, power-law, and uniform—across six datasets. 
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
-\textcolor{cyan}{The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
+\textcolor{blue}{The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
 When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change.}
@@
 %	This group includes ACORN-1, CAPS, Faiss, Faiss+HQI\_Batch, Puck, StitchedVamana and UNG, as illustrated in Figure~\ref{fig:exp_5_2_1}.
-	\textcolor{orange}{Figure~\ref{fig:exp_5_2_1} shows the algorithms suitable for low AS.}
-	\textcolor{orange}{ACORN-1}, Faiss, Puck, and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
-\textcolor{orange}{Pre-filtering strategies significantly reduce the number of candidate points under low AS, thereby lowering the cost of  computations.
+	\textcolor{blue}{Figure~\ref{fig:exp_5_2_1} shows the algorithms suitable for low AS.}
+	\textcolor{blue}{ACORN-1}, Faiss, Puck, and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
+\textcolor{blue}{Pre-filtering strategies significantly reduce the number of candidate points under low AS, thereby lowering the cost of  computations.
 As a result, such strategies tend to perform better in low AS scenarios.} CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
@@
 %	This group includes FilteredVamana, NHQ, PASE and VBASE, as shown in Figure~\ref{fig:exp_5_2_2}.
-	\textcolor{orange}{Figure~\ref{fig:exp_5_2_2} shows the algorithms suitable for high AS.}
+	\textcolor{blue}{Figure~\ref{fig:exp_5_2_2} shows the algorithms suitable for high AS.}
 	At low AS, FilteredVamana performs poorly in these scenarios.
@@
 %	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
-	\textcolor{orange}{Figure~\ref{fig:exp_5_2_3} shows algorithms that are insensitive to AS.}
+	\textcolor{blue}{Figure~\ref{fig:exp_5_2_3} shows algorithms that are insensitive to AS.}
 	Milvus is mainly limited by system-level communication overhead, such as API latency.
@@
 	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} 
-	\textcolor{violet}{As shown in the Figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+	\textcolor{blue}{As shown in the Figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
+	\textcolor{blue}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 %		\caption{Time and space overhead of index construction}
-		\caption{\textcolor{violet}{Time and Space Overhead (RF)}}
+		\caption{\textcolor{blue}{Time and Space Overhead (RF)}}
 		\label{fig:rangeFilter_build_index_comparison}
@@
 }
-	\subsubsection{\textcolor{violet}{Time and Space overhead.}}
+	\subsubsection{\textcolor{blue}{Time and Space overhead.}}
 
 	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
-	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{orange}{Notably, all algorithms use single-threaded index construction on medium-scale datasets, and 64-thread construction on the large-scale Deep100M dataset, except DSG, which only supports single-threading.
+	Similarly, we also evaluate \textcolor{blue}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
+\textcolor{blue}{Notably, all algorithms use single-threaded index construction on medium-scale datasets, and 64-thread construction on the large-scale Deep100M dataset, except DSG, which only supports single-threading.
 For WinFilter, we use Super Postfiltering on medium datasets for best performance, and switch to the base algorithm Vamana-WST on Deep100M due to construction overhead.
@@
 %	DSG only supports single-threaded construction, resulting in the longest build time.}
-	\textcolor{orange}{
+	\textcolor{blue}{
 	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF\_Flat architecture, require less time.
@@
 
-\textcolor{orange}{In addition, the two HNSW-based methods, ACORN-1 and SeRF, also achieve short index construction time.
+\textcolor{blue}{In addition, the two HNSW-based methods, ACORN-1 and SeRF, also achieve short index construction time.
 ACORN-1 closely follows the original HNSW construction process and reduces the number of candidate neighbors in the upper layers to lower computational overhead.
@@
 
-\textcolor{orange}{We observe that ACORN-\(\gamma\), DSG and WinFilter exhibit relatively long index construction time.
+\textcolor{blue}{We observe that ACORN-\(\gamma\), DSG and WinFilter exhibit relatively long index construction time.
 Although the first two methods are also based on HNSW, ACORN-\(\gamma\) extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
@@
 
-	\textcolor{violet}{Similar to attribute filtering, PASE requires the most storage. }
-	\textcolor{orange}{Additionally, DSG also results in a large index size, especially on large-scale datasets.
+	\textcolor{blue}{Similar to attribute filtering, PASE requires the most storage. }
+	\textcolor{blue}{Additionally, DSG also results in a large index size, especially on large-scale datasets.
 As an enhancement over SeRF, DSG stores additional metadata for each edge in its index structure.
@@
 
-	\textcolor{orange}{\textit{\textbf{Peak memory.}}  
+	\textcolor{blue}{\textit{\textbf{Peak memory.}}  
 	As explained in the attribute filtering analysis, methods with larger index sizes (including the dataset) tend to exhibit higher peak memory consumption.
@@
 
-	\textcolor{orange}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism.
+	\textcolor{blue}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism.
 Although the final index size remains relatively small, the peak memory usage increases significantly during both construction and search.
@@
 	In this experiment, we follow the query range definition adopted by prior work~\cite{HQI}.
-\textcolor{red}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.}
+\textcolor{blue}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.}
 	% Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} \textcolor{blue}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).
@@
 	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{cyan}{Consistent with Section 4.2.3, we conduct range filtering experiments on the YT-Audio-Real dataset using two server configurations, with results presented in Figure~\ref{fig:range-cross-platform}.
+	\textcolor{blue}{Consistent with Section 4.2.3, we conduct range filtering experiments on the YT-Audio-Real dataset using two server configurations, with results presented in Figure~\ref{fig:range-cross-platform}.
 Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
@@
 	\section{DISCUSSION}
-	\textcolor{orange}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
+	\textcolor{blue}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
 Next, we provide a detailed discussion of the advantages and disadvantages of each algorithm.}
@@
 UNG stands out for its higher recall, precision, and QPS, and performs well in the OOD scenario (S7, S8).
-\textcolor{orange}{
+\textcolor{blue}{
 Overall, UNG, NHQ and FilteredDisk\\-ANN demonstrate strong performance.
@@
 
-\textcolor{orange}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
+\textcolor{blue}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
 FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.
@@
 
-\textcolor{orange}{
+\textcolor{blue}{
 CAPS, based on clustering, features low index space overhead.
@@
 	\subsubsection{Range Filtering}
-\textcolor{orange}{
+\textcolor{blue}{
 	WinFilter achieves the best search performance but requires high time and memory resources during index construction.
@@
 
-	\textcolor{orange}{
+	\textcolor{blue}{
 	iRange has relatively low time and space costs for index construction.
@@
 
-		\textcolor{orange}{
+		\textcolor{blue}{
 	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
@@
 	\subsubsection{General Algorithm}
-\textcolor{orange}{All of the following methods support both attribute filtering and range filtering.}
-
-\textcolor{orange}{
+\textcolor{blue}{All of the following methods support both attribute filtering and range filtering.}
+
+\textcolor{blue}{
 ACORN demonstrates average overall performance.
@@
 
-\textcolor{red}{
+\textcolor{blue}{
 Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability.
@@
 %		}
-		\textcolor{orange}{
+		\textcolor{blue}{
 For example, in multi-attribute scenarios, some algorithms only support Boolean OR logic (e.g., FilterDiskANN), while others only support Boolean AND logic (e.g., NHQ and CAPS).
@@
 
-\textcolor{violet}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic.
+\textcolor{blue}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic.
 Our experiments also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing.
@@
 	Except for DSG and UNIFY, most range filtering algorithms require the dataset to be pre-sorted before building the index.
-\textcolor{green}{Moreover, existing range filtering algorithms do not support range queries with more than 3 attributes.} \textcolor{violet}{Designing algorithms that support an arbitrary number of range filterable attributes remains an open research challenge.}
+\textcolor{blue}{Moreover, existing range filtering algorithms do not support range queries with more than 3 attributes.} \textcolor{blue}{Designing algorithms that support an arbitrary number of range filterable attributes remains an open research challenge.}
 

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 		\centering
-		\setlength{\belowcaptionskip}{-0.cm}
+		\setlength{\abovecaptionskip}{0.2cm}
+		\setlength{\belowcaptionskip}{-0.1cm}
+
 		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
@@
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
-Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, Puck).}
+Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, PUCK).}
 %	IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
@@
 		\centering
-		%	 \setlength{\abovecaptionskip}{0cm}
-		%	\setlength{\belowcaptionskip}{0.1cm}
 		\footnotesize{
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{\textcolor{violet}{Time and Space Overhead (AF)}}
@@
 		\centering
-
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.2cm}
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
@@
 		\centering
-
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		% 上面的图例，居中并可通过 hspace 调整左右位置
@@
 		\centering
-
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.2cm}
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
@@
 	\centering
-
+	\setlength{\abovecaptionskip}{0.1cm}
+	\setlength{\belowcaptionskip}{-0.2cm}
 	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
@@
 		\centering
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.2cm}
 		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
@@
 		\centering
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.2cm}
 		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf}
@@
 		\centering
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.2cm}
 		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
@@
 %		\caption{Time and space overhead of index construction}
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{\textcolor{violet}{Time and Space Overhead (RF)}}
@@
 \textcolor{orange}{Notably, all algorithms use single-threaded index construction on medium-scale datasets, and 64-thread construction on the large-scale Deep100M dataset, except DSG, which only supports single-threading.
-For WinFilter, we use its integrated Super-Postfiltering on medium datasets for best performance, and switch to its base algorithm Vamana-WST on Deep100M due to construction overhead.
+For WinFilter, we use Super Postfiltering on medium datasets for best performance, and switch to the base algorithm Vamana-WST on Deep100M due to construction overhead.
 	}
@@
 	\textcolor{orange}{
-	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF architecture, require less time.
+	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF\_Flat architecture, require less time.
 This indexing structure enables fast construction through subset sampling and centroid computation, thereby reducing computational cost.
@@
 This ID is pre-sorted according to its corresponding real attribute, allowing us to map an attribute to its ID without loss of generality for efficient range queries.}
-	Based on this definition, we evaluate algorithm performance under the largest ($2^{-2}$) and smallest ($2^{-8}$) query range settings.
-We report the results for these two representative cases in Figure~\ref{fig:exp_8_2}.
+	Based on this definition, we evaluate algorithm performance under four query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
+For space considerations, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
 %	The experimental results show consistent performance across all datasets and query ranges.
@@
 
-	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the Deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{red}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).

### 2025-07-31 VLDB2026/main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 \textcolor{blue}{Notably, all algorithms use single-threaded index construction on medium-scale datasets, and 64-thread construction on the large-scale Deep100M dataset, except DSG, which only supports single-threading.
-For WinFilter, we use Super Postfiltering on medium datasets for best performance, and switch to the base algorithm Vamana-WST on Deep100M due to construction overhead.
+For WinFilter, we use its integrated Super-Postfiltering on medium datasets for best performance, and switch to its base algorithm Vamana-WST on Deep100M due to construction overhead.
 	}
@@
 	\textcolor{blue}{
-	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF\_Flat architecture, require less time.
+	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF architecture, require less time.
 This indexing structure enables fast construction through subset sampling and centroid computation, thereby reducing computational cost.
@@
 
-	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} \textcolor{blue}{As shown in the Figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the Deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).

### 2025-07-31 VLDB2026/main.tex
Update main.tex

@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{\textcolor{blue}{Time and Space Overhead (AF)}}
@@
 %		\caption{Time and space overhead of index construction}
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{\textcolor{blue}{Time and Space Overhead (RF)}}
@@
 
-	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} \textcolor{red}{As shown in the Figure~\ref{fig: range big dataset}, On the Deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} \textcolor{blue}{As shown in the Figure~\ref{fig: range big dataset}, On the Deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 Thank you for your suggestion.
-Currently, except for Filtered-DiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper.
+Currently, except for Filtered-DiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}.
 \begin{figure}[htbp]
@@
 
-Latency-Recall Tradeoff:
+\textbf{Latency-Recall Tradeoff.}
 As expected, SSD-based Filtered-DiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
@@
 
-Cost Breakdown of Filtered-DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
+\textbf{Cost Breakdown of Filtered-DiskANN.} The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
 The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
@@
 
-In-memory Methods:
+\textbf{In-memory Methods.}
 FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
@@
 
-\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.
+Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.
 
@@
 We believe your suggestion is very reasonable, and the experiment on search peak memory is indeed an important component.
-We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+We provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
 We present the search peak memory usage for the newly added attribute filtering and range filtering in Figure \ref{fig:search_memory_mb_comparison} and Figure \ref{fig:rangeFilter_search_memory_mb}, respectively.
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}.
+In the recommendation section of our paper, we have added a clearer recommendation table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}.
 \textbf{(Please see Section 5.1, highlighted in blue in the revised manuscript.)}
 
-\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table 1. "}
+\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table 3. "}
 
@@
 We believe your suggestion is very reasonable, and the experiment on search peak memory is indeed an important component.
-We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+We provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
 For more details, please refer to our response Meta R6.
@@
 Thank you for pointing this out.
-The original reference [49](now [50] in our latest version), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49] ([50] in the revised manuscript), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
@@
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
+
 \textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [42,47] significantly impact algorithm performance."}
@@
 
-We agree with your point of view.
+However, we agree with your point.
 To provide a more comprehensive evaluation, we have added the peak memory usage data of the database systems  in the revised version of the paper.
@@
 
-\textcolor{blue}{
-}
+Once again, thank you for your constructive comments. Your valuable feedback has helped us improve the paper further.
 

### 2025-07-31 Revision/response.tex
1

@@
 	\includegraphics[width=\linewidth]{fig/recall_latency_all.pdf}
-	\caption{Performance Comparison of SSD-Based and In-Memory Execution of FilteredDiskANN}
+	\caption{Performance Comparison of SSD-Based and In-Memory Execution of Filtered-DiskANN}
 	\label{fig:recall-latency}
@@
 We clarify in Table ~\ref{tab:compair_1} which methods support disk-based execution.
-Since only FilteredDiskANN supports disk-based execution, we conduct additional experiments to analyze its performance and report a detailed cost breakdown (I/O vs.
+Since only Filtered-DiskANN supports disk-based execution, we conduct additional experiments to analyze its performance and report a detailed cost breakdown (I/O vs.
 CPU).

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 Thank you for your suggestion.
-Currently, except for Filtered-DiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}.
+Currently, except for Filtered-DiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper.
 \begin{figure}[htbp]
@@
 
-\textbf{Latency-Recall Tradeoff.}
+Latency-Recall Tradeoff:
 As expected, SSD-based Filtered-DiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels.
@@
 
-\textbf{Cost Breakdown of Filtered-DiskANN.} The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
+Cost Breakdown of Filtered-DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
 The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
@@
 
-\textbf{In-memory Methods.}
+In-memory Methods:
 FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
@@
 
-Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.
+\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.
 
@@
 We believe your suggestion is very reasonable, and the experiment on search peak memory is indeed an important component.
-We provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
 We present the search peak memory usage for the newly added attribute filtering and range filtering in Figure \ref{fig:search_memory_mb_comparison} and Figure \ref{fig:rangeFilter_search_memory_mb}, respectively.
@@
 Your advice is very insightful.
-In the recommendation section of our paper, we have added a clearer recommendation table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}.
+In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}.
 \textbf{(Please see Section 5.1, highlighted in blue in the revised manuscript.)}
 
-\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table 3. "}
+\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table 1. "}
 
@@
 
-To address this critical issue and enhance the real-world relevance of our evaluation, we have incorporated two new real-world datasets with their actual attributes into our attribute filtering and range filtering experiments, and we have clarified the sources of these real-world attributes.
-For more details, please refer to our response to Meta R3.
-
-For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Index Construction and Single-Attribute Query" experiments and amended the manuscript accordingly.
-It is also worth noting that in Section 4.2.2, under the "Single-Attribute Index Construction and Single-Attribute Query" subsection, we have removed two previous datasets (Audio and GloVe) due to space constraints.
-The Audio dataset was removed because its smaller scale offered limited reference value.
-The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M.
-\textbf{(Please see Section 4.2.1, and the "Single-Attribute Index Construction and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
-
-In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the performance of algorithms.
-For more details, please refer to our response to Review 1 W1.
-
-For range filtering, we have also included the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes in our experiments.
-For more details, please refer to our response to Meta R3.
-
 Regarding your review comment, we did indeed try to find suitable e-commerce datasets to better align with the application scenarios mentioned in the introduction.
@@
 On the other hand, while the MEP-3M dataset was larger, it did not directly provide image data that could be encoded into vectors, and we were unable to find suitable fields for vectorization.
-As we were unable to locate an ideal e-commerce dataset that simultaneously contained sufficient scale of both vectors and structured attributes, we ultimately decided to continue using the WIT and YouTube-Audio datasets, which are widely employed in existing hybrid querying algorithm research.
+As we were unable to locate an ideal e-commerce dataset that simultaneously contained sufficient scale of both vectors and structured attributes, we ultimately decided to continue using the WIT (Also called WIT-Real) and YouTube-Audio (Also YT-Audio-Real) datasets, which are widely employed in existing hybrid querying algorithm research.
 These datasets feature real attribute information and have been broadly accepted by the community as standard benchmarks for evaluating hybrid query performance.
-We believe that despite not being directly from e-commerce platforms, their data characteristics and complexity are sufficient to support our comprehensive evaluation and in-depth analysis of hybrid querying algorithms.
+For more details, please refer to our response to Meta R3.
+
+For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Index Construction and Single-Attribute Query" experiments and amended the manuscript accordingly.
+\textbf{(Please see Section 4.2.1, and the "Single-Attribute Index Construction and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
+
+In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the performance of algorithms.
+For more details, please refer to our response to Review 1 W1.
+
+For range filtering, we have also included the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes in our experiments.
+For more details, please refer to our response to Meta R3.
 
@@
 We believe your suggestion is very reasonable, and the experiment on search peak memory is indeed an important component.
-We provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
+We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons.
 For more details, please refer to our response Meta R6.
@@
 Thank you for pointing this out.
-The original reference [49] ([50] in the revised manuscript), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49](now [50] in our latest version), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
@@
 \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
-
 \textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [42,47] significantly impact algorithm performance."}

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 Regarding your review comment, we did indeed try to find suitable e-commerce datasets to better align with the application scenarios mentioned in the introduction.
-We investigated some publicly available e-commerce datasets, such as ecommerce\_product\_images\_18K and MEP-3M datasets.
+We investigated some publicly available e-commerce datasets, such as ecommerce\_product\_image\\-s\_18K and MEP-3M datasets.
 However, we found that neither of these datasets fully met our requirements for conducting hybrid querying experiments.
-Specifically, the ecommerce\_product\_images\_18K dataset was too small to effectively evaluate the performance and scalability of hybrid querying algorithms under large-scale datasets.
+Specifically, the ecommerce\_product\_image\\-s\_18K dataset was too small to effectively evaluate the performance and scalability of hybrid querying algorithms under large-scale datasets.
 On the other hand, while the MEP-3M dataset was larger, it did not directly provide image data that could be encoded into vectors, and we were unable to find suitable fields for vectorization.
@@
 Thank you for pointing this out.
-The original reference [49] ([50] in the revised manuscript), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49] ([45] in the revised manuscript), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.

### 2025-07-31 Revision/response.tex
1

--- 2025-07-31 Revision/response.tex
@@
 	\includegraphics[width=\linewidth]{fig/recall_latency_all.pdf}
-	\caption{Performance Comparison of SSD-Based and In-Memory Execution of Filtered-DiskANN}
+	\caption{Performance Comparison of SSD-Based and In-Memory Execution of FilteredDiskANN}
 	\label{fig:recall-latency}
@@
 Regarding your review comment, we did indeed try to find suitable e-commerce datasets to better align with the application scenarios mentioned in the introduction.
-We investigated some publicly available e-commerce datasets, such as ecommerce\_product\_image\\-s\_18K and MEP-3M datasets.
+We investigated some publicly available e-commerce datasets, such as ecommerce\_product\_images\_18K and MEP-3M datasets.
 However, we found that neither of these datasets fully met our requirements for conducting hybrid querying experiments.
-Specifically, the ecommerce\_product\_image\\-s\_18K dataset was too small to effectively evaluate the performance and scalability of hybrid querying algorithms under large-scale datasets.
+Specifically, the ecommerce\_product\_images\_18K dataset was too small to effectively evaluate the performance and scalability of hybrid querying algorithms under large-scale datasets.
 On the other hand, while the MEP-3M dataset was larger, it did not directly provide image data that could be encoded into vectors, and we were unable to find suitable fields for vectorization.
@@
 We clarify in Table ~\ref{tab:compair_1} which methods support disk-based execution.
-Since only Filtered-DiskANN supports disk-based execution, we conduct additional experiments to analyze its performance and report a detailed cost breakdown (I/O vs.
+Since only FilteredDiskANN supports disk-based execution, we conduct additional experiments to analyze its performance and report a detailed cost breakdown (I/O vs.
 CPU).
@@
 Thank you for pointing this out.
-The original reference [49] ([45] in the revised manuscript), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49](now [50] in our latest version), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
@@
 Of all the evaluated algorithms, Faiss, Puck, Filtered-DiskANN, and Milvus support quantization.
-However, quantization serves to reduce memory usage during queries by sacrificing query accuracy.
+Quantization serves to reduce memory usage during queries by sacrificing query accuracy.
 Given that most of the graph-based algorithms involved in this paper (with the exception of Filtered-DiskANN) do not support quantization, we do not enable quantization in our experiments for a fair comparison.

### 2025-07-31 VLDB2026/main.tex
1

@@
 		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.2cm}		
+		\setlength{\belowcaptionskip}{-0.3cm}		
 		\caption{Graph Index and IVF Index}
@@
 		\centering
+		\setlength{\abovecaptionskip}{0.15cm}
+		\setlength{\belowcaptionskip}{-0.1cm}
 		%\setlength{\belowcaptionskip}{-0.3cm}
@@
 		\centering
+		\setlength{\abovecaptionskip}{0.15cm}
+		\setlength{\belowcaptionskip}{-0.1cm}
 
@@
 		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.2cm}
+		\setlength{\belowcaptionskip}{-0.25cm}
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
@@
 	\setlength{\abovecaptionskip}{0.1cm}
-	\setlength{\belowcaptionskip}{-0.2cm}
+	\setlength{\belowcaptionskip}{-0.25cm}
 	\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
@@
 
-			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
+			\includegraphics[width=0.98\textwidth]{figures/exp/exp_5_2_1.pdf}
 			\caption{Algorithms Optimized for Low AS}
@@
 		% 第二行：两张子图，左侧宽度是右侧的两倍
-		\begin{subfigure}{0.627\textwidth} % 2/3 宽度
+		\begin{subfigure}{0.64\textwidth} % 2/3 宽度
 			\centering
@@
 		\hspace{1mm} % 增加水平间距
-		\begin{subfigure}{0.33\textwidth} % 1/3 宽度
+		\begin{subfigure}{0.34\textwidth} % 1/3 宽度
 			\centering
@@
 		\end{subfigure}
+
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.15cm}
 
@@
 
-	\begin{minipage}[t]{0.38\textwidth}
-		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.2cm}
+	\begin{minipage}[t]{0.36\textwidth}
+		\centering
+
 		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
@@
 	\hfill
-	\begin{minipage}[t]{0.203\textwidth}
-		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.2cm}
-		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf}
+	\begin{minipage}[t]{0.20\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{figures/exp/attribute_100M.pdf}
 
@@
 	\hfill % 在盒子之间添加弹性间距
-	\begin{minipage}[t]{0.39\textwidth}
-		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.2cm}
+	\begin{minipage}[t]{0.37\textwidth}
+		\centering
 		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
@@
 		\centering
+		\setlength{\abovecaptionskip}{-0.2cm}
+		\setlength{\belowcaptionskip}{-0.25cm}
 		\caption{Multi-Modal Datasets (AF)}
@@
 		\centering
+		\setlength{\abovecaptionskip}{-0.2cm}
+		\setlength{\belowcaptionskip}{-0.25cm}
 		\caption{Large-Scale Dataset (AF)}
@@
 		\centering
+		\setlength{\abovecaptionskip}{-0.2cm}
+		\setlength{\belowcaptionskip}{-0.25cm}
 		\caption{Different Platforms (AF)}
@@
 
-		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
+		\includegraphics[width=0.99\textwidth]{figures/exp/exp_8_2.pdf}
+		\setlength{\abovecaptionskip}{0.1cm}
+		\setlength{\belowcaptionskip}{-0.15cm}
 		\caption{Performance of RF-ANN Search}
@@
 
-	\begin{minipage}[t]{0.38\textwidth}
+	\begin{minipage}[t]{0.36\textwidth}
 		\centering
@@
 	\hfill
-	\begin{minipage}[t]{0.203\textwidth}
+	\begin{minipage}[t]{0.18\textwidth}
 		\centering
@@
 	\hfill % 在盒子之间添加弹性间距
-	\begin{minipage}[t]{0.39\textwidth}
+	\begin{minipage}[t]{0.36\textwidth}
 		\centering
@@
 	\centering
-	\setlength{\abovecaptionskip}{0.0cm}
 	\begin{minipage}[t]{0.37\textwidth}
 		\centering
+		\setlength{\abovecaptionskip}{-0.2cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{Multi-Modal Datasets (RF)}
@@
 		\centering
+		\setlength{\abovecaptionskip}{-0.2cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{Large-Scale Dataset (RF)}
@@
 		\centering
+		\setlength{\abovecaptionskip}{-0.2cm}
+		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{Different Platforms (RF)}
@@
 \begin{table*}[htbp]
+	\setlength{\abovecaptionskip}{0.1cm}
+	\setlength{\belowcaptionskip}{0.1cm}
 	\caption{Algorithm Recommendation}

### 2025-07-31 Revision/response.tex
Update response.tex

--- 2025-07-31 Revision/response.tex
@@
 
-Regarding your review comment, we did indeed try to find suitable e-commerce datasets to better align with the application scenarios mentioned in the introduction.
+We  try to find suitable e-commerce datasets to better align with the application scenarios mentioned in the introduction.
 We investigated some publicly available e-commerce datasets, such as ecommerce\_product\_images\_18K and MEP-3M datasets.
@@
 
-For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Index Construction and Single-Attribute Query" experiments and amended the manuscript accordingly.
-\textbf{(Please see Section 4.2.1, and the "Single-Attribute Index Construction and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
-
 In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the performance of algorithms.
@@
 
-For range filtering, we have also included the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes in our experiments.
+We conduct experiments on these two datasets with real attributes and analyze the experimental results.
+\textbf{(Please see Section 4.2 and  Section 4.3,  highlighted in blue in the revised manuscript.).}
+
+%
+%For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Index Construction and Single-Attribute Query" experiments and amended the manuscript accordingly.
+\textbf{(Please see Section 4.2.1, and the "Single-Attribute Index Construction and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}
+%
+%For range filtering, we have also included the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes in our experiments.
 For more details, please refer to our response to Meta R3.
@@
 Thank you for pointing this out.
-The original reference [49] ([45] in the revised manuscript), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
+The original reference [49] ([50] in the revised manuscript), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms.
 We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques.
@@
 To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature.
-\textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
+\textbf{  (Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 

### 2025-07-31 Revision/response.tex

@@
 To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature.
-\textbf{  (Please see Section 1.1, highlighted in blue in the revised manuscript.)}
+\textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
 

### 2025-07-31 VLDB2026/main.tex

@@
 
-	\textcolor{blue}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
+	\textcolor{blue}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloV-\\e~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
 
@@
 
-	\textcolor{blue}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
+	\textcolor{blue}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2-Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
 The Text2Image dataset includes two versions.
@@
 		\vspace{0.1cm}
-		\textit{Performance Levels:} B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported;
+		\textit{Performance Levels:} \textbf{B} = Best, G = Good , M = Moderate, P = Poor, - = Not Supported;
 		\textit{Performance-Critical}: Requires low latency and high recall;

### 2025-07-31 VLDB2026/main.tex
Update main.tex

@@
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image& Both \\
-				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image& Both \\
+				Text2Image-Mix & 200 & 1,000,000 &10,000 & 21& Text,Image& Both \\
 				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image& Both \\

### 2025-07-31 VLDB2026/main.tex
Update main.tex

--- 2025-07-31 VLDB2026/main.tex
@@
 	\section{CONCLUSION}
-	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
+	In this paper, we systematically evaluate various hybrid query methods, including multiple algorithms, vector databases, and libraries.
+We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm.
+Experiments show that existing algorithms still have significant shortcomings when facing challenges such as large-scale data, complex queries, and resource constraints.
+There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms.
+Furthermore, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries.
+Notably, in some high-recall scenarios, some algorithms even perform worse than the baseline method (e.g., Faiss).
+In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
+Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.
+%	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
 We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm.
@@
 Notably, some algorithms even perform worse than the baseline method (e.g., Faiss) in high recall scenarios.
-In the future, it is essential to further explore the flexibility and robustness of attribute filtering algorithms, and improving the performance of range filtering algorithms remains an important direction.
+In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
+Furthermore, in many real-time scenarios, both attribute and range filtering are required simultaneously, and therefore, exploring algorithms that support a combination of both is also an important research topic.
+%	In the future, it is essential to further explore the flexibility and robustness of attribute filtering algorithms, and improving the performance of range filtering algorithms remains an important direction.
 %	\textcolor{blue}{

### 2025-07-31 Revision/response.tex

@@
 
-In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the performance of algorithms.
+In addition, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the performance of algorithms.
 For more details, please refer to our response to Review 1 W1.
 
-We conduct experiments on these two datasets with real attributes and analyze the experimental results.
+In order to further verify the performance of these algorithms in real scenarios, we have conducted experiments on these two datasets with real attributes and have analyzed the experimental results.
 \textbf{(Please see Section 4.2 and  Section 4.3,  highlighted in blue in the revised manuscript.).}

### 2025-07-31 VLDB2026/main.tex
Update main.tex

@@
 We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm.
-Experiments show that existing algorithms still have significant shortcomings when facing challenges such as large-scale data, complex queries, and resource constraints.
+Experiments show that existing algorithms still have significant shortcomings in scenarios such as large-scale data, complex queries, and resource constraints.
 There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms.

### 2025-07-31 VLDB2026/main.tex
Update main.tex
1

@@
 				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image& Both \\
-				Text2Image-Mix & 200 & 1,000,000 &10,000 & 21& Text,Image& Both \\
+				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image& Both \\
 				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image& Both \\
@@
 	\hline
-	\textbf{High-LID} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
+	\textbf{High-LID} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/M & P/P & P/P & P/P \\
 	\hline
@@
 	\section{CONCLUSION}
-	In this paper, we systematically evaluate various hybrid query methods, including multiple algorithms, vector databases, and libraries.
-We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm.
-Experiments show that existing algorithms still have significant shortcomings in scenarios such as large-scale data, complex queries, and resource constraints.
-There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms.
-Furthermore, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries.
-Notably, in some high-recall scenarios, some algorithms even perform worse than the baseline method (e.g., Faiss).
-In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
-Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.
-%	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
+	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
 We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm.
@@
 Notably, some algorithms even perform worse than the baseline method (e.g., Faiss) in high recall scenarios.
-In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
-Furthermore, in many real-time scenarios, both attribute and range filtering are required simultaneously, and therefore, exploring algorithms that support a combination of both is also an important research topic.
-%	In the future, it is essential to further explore the flexibility and robustness of attribute filtering algorithms, and improving the performance of range filtering algorithms remains an important direction.
+In the future, it is essential to further explore the flexibility and robustness of attribute filtering algorithms, and improving the performance of range filtering algorithms remains an important direction.
 %	\textcolor{blue}{

### 2025-08-01 Revision/response.tex
Update response.tex
1

@@
 	An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)''\\
-Submission to VLDB 2026 Research Track (ID )
+Submission to VLDB 2026 Research Track (ID 263)
 }
@@
 %	\includegraphics[width=\linewidth]{fig/exp_3_1_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
+	\includegraphics[width=0.97\linewidth]{fig/exp_3_1.pdf}
 	\caption{Effect of Attribute Distribution on Query Performance}
@@
 
-		\includegraphics[width=0.95\textwidth]{fig/exp_5_2_1.pdf}
+		\includegraphics[width=0.97\textwidth]{fig/exp_5_2_1.pdf}
 		\caption{Algorithms Optimized for Low AS}
@@
 	% 第二行：两张子图，左侧宽度是右侧的两倍
-	\begin{subfigure}{0.627\textwidth} % 2/3 宽度
+	\begin{subfigure}{0.64\textwidth} % 2/3 宽度
 		\centering
@@
 	\hspace{1mm} % 增加水平间距
-	\begin{subfigure}{0.33\textwidth} % 1/3 宽度
+	\begin{subfigure}{0.333\textwidth} % 1/3 宽度
 		\centering
@@
 }
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.99\linewidth]{fig/attribute_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}
+	\caption{Multi-modal Datasets (AF)}
+	\label{fig:attribute_multimodel}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
+	\includegraphics[width=\linewidth]{fig/range_multimodel_2.pdf}
+	\setlength{\abovecaptionskip}{0.2cm}
+	\setlength{\belowcaptionskip}{-0.1cm}
+	\caption{Multi-modal Datasets (RF)}
+	\label{fig:range_multimodel}
+\end{figure}
 
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}
-	\caption{Multi-modal Datasets (AF)}
-	\label{fig:attribute_multimodel}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
-	\includegraphics[width=\linewidth]{fig/range_multimodel_2.pdf}
-	\caption{Multi-modal Datasets (RF)}
-	\label{fig:range_multimodel}
-\end{figure}
-
 %\begin{figure}[t]
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/recall_latency_all.pdf}
+	\includegraphics[width=0.7\linewidth]{fig/recall_latency_all.pdf}
 	\caption{Performance Comparison of SSD-Based and In-Memory Execution of Filtered-DiskANN}

### 2025-08-01 VLDB2026/main.tex
Update main.tex
1

--- 2025-07-31 VLDB2026/main.tex
@@
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
+Furthermore, we did not measure PASE on large-scale datasets, as we estimated it would take over 10 days.
 \textcolor{blue}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other 6 medium-scale datasets.
@@
 In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
-Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.
+\textcolor{blue}{Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.}
 %	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
@@
 	\clearpage
-
+	\balance
 	\bibliographystyle{ACM-Reference-Format}

### 2025-08-01 VLDB2026/main.tex
Update main.tex
1

@@
 	We conduct most experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache.
+\textcolor{blue}{ We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM.}
 %	\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.
@@
 	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts.
+PASE is excluded due to poor past performance.
 \textcolor{blue}{The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
@@
 	WinFilter maintains optimal performance by building an index for each tree node. It then performs an ANN search on the relevant nodes and post-filters the results, ensuring high recall and QPS.
-	In contrast, iRange dynamically constructs a search graph during query time.
+	In contrast, iRange dynamically constructs a search graph during querying.
 This method has low overhead and performs well in small-range queries, but its performance degrades as the query range increases.
@@
 	\textcolor{blue}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
-Next, we provide a detailed discussion of the advantages and disadvantages of each algorithm.}
+Next, we provide a discussion of the advantages and disadvantages of each algorithm.}
 
@@
 	\hline
-	\textbf{Performance-Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
+	\textbf{Performance-Critical} & \textbf{B} & G & M & G & M & G & G & M & M & M & M & M/M & M/M & M/M & P/P & P/P \\
 	\hline
@@
 	\hline
-	\textbf{Multi-Modal} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
+%	\textbf{Multi-Modal} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
+%	\hline
+	\textbf{Multi-Modal} & \textbf{B} & G & G & P & M & M & \textbf{B} & G & M & M & G & P/P & P/M & M/M & P/P & P/P \\
 	\hline
-	\textbf{High-LID} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/M & P/P & P/P & P/P \\
+	\textbf{Rare Attribute / Low Range} & \textbf{B} & M & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/G & P/P & P/P & P/P \\
 	\hline
-	\textbf{Rare Attribute / Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
-	\hline
-	\textbf{Distribution-Robust} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
+	\textbf{Distribution-Robust} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & - \\
 	\hline
@@
 		\textit{Multi-Modal}: For multi-modal dataset scenarios;
-		\textit{High-LID}: For complex dataset scenarios;
+%		\textit{High-LID}: For complex dataset scenarios;
 		\textit{Rare Attribute / Low Range}: For filtering with low attribute selectivity or small ranges;
@@
 	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
-It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution.}
+It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it more general-purpose.}
 %	Table~\ref{tab:algo_scenarios} also shows the application scenarios of range filtering.
@@
 	Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
-Filtered-DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
+Filtered-DiskANN leverages disk-based storage, making it suitable for  large-scale datasets even in memory-constrained environments.
 Moreover, the index construction phase of graph-based algorithms is computationally intensive.
@@
 	\textcolor{blue}{
-	Besides, our research findings indicate that the distribution and selectivity of attributes significantly impact the performance of attribute filtering methods.
+	Besides, our research indicates that the distribution and selectivity of attributes significantly impact the performance of attribute filtering methods.
 Therefore, when designing algorithms, efforts should be made to minimize the coupling with specific attribute value distributions, in order to enhance the robustness and generalization ability of the algorithms under varying data conditions.}

### 2025-08-01 VLDB2026/main.tex
Update main.tex

@@
 	\begin{definition}[AF-NN Search]
-		Let \( D = \{(v_1, s_1), \ldots, (v_n, s_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute set \( s_i \).
+		Let \( D = \{(v_1, s_1), \ldots, (v_n, s_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, where each \( v_i \) associated with an attribute set \( s_i \).
 Given a query \( Q = (q_v, q_s, k) \), where \( q_s \) is the query attribute set, the AF-NN search aims to return a set \( R \subseteq D_s \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_s \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_s = \{ v_i \mid (v_i, s_i) \in D \land q_s \subseteq s_i \} \).
@@
 
-		Let \( D = \{(v_1, \textcolor{blue}{a}_1), \ldots, (v_n, \textcolor{blue}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
+		Let \( D = \{(v_1, \textcolor{blue}{a}_1), \ldots, (v_n, \textcolor{blue}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, where each \( v_i \) associated with an attribute value \( a_i \).
 Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).

### 2025-08-01 VLDB2026/main.tex
1

--- 2025-08-01 VLDB2026/main.tex
@@
 		However, current evaluations lack unified benchmarking standards and systematic assessment methodologies.
-Existing studies not only fail to cover mainstream algorithms but also omit systematic comparisons or in-depth analysis on different methods.
-To address this issue, we design a complete evaluation framework for hybrid queries.
+Existing studies either fail to cover mainstream algorithms or omit systematic comparisons or in-depth analysis on different methods.
+To address this issue, we design a comprehensive evaluation framework for hybrid queries.
 Our study introduces 15 hybrid query algorithms and systematically classifies them based on multiple dimensions, such as index organization and filtering strategy, providing a reference for the categorization of hybrid queries.
@@
 For range filtering, we also evaluate the algorithm performance across the 3 metrics through controlled variation of query ranges.
-	\textcolor{blue}{In the experiments, we constructed standardized attribute and range sets for attribute filtering and range filtering, respectively, enabling a unified comparison of algorithms in terms of index construction efficiency and query performance.
-Furthermore, we evaluate the robustness of the algorithms across multiple dimensions, including different data distributions, platforms, and scalability on a 100M-scale dataset.}
+	\textcolor{blue}{In the experiments, we construct standardized attribute and range sets for attribute filtering and range filtering, respectively, enabling a unified comparison of algorithms in terms of index construction efficiency and query performance.
+Furthermore, we evaluate the robustness of the algorithms across multiple dimensions, including data distributions, platforms, and scalability on a 100-million-scale dataset.}
 	 Additionally, we conduct an in-depth analysis of the experimental results based on the underlying principles of algorithms.
@@
 2) Range Filtering Nearest Neighbor (\textit{RF-NN}) search.
-We provide their formal definitions below.
 
 	\begin{definition}[AF-NN Search]
-		Let \( D = \{(v_1, s_1), \ldots, (v_n, s_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute set \( s_i \).
+		Let \( D = \{(v_1, s_1), \ldots, (v_n, s_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each  \( v_i \) associated with an attribute set \( s_i \).
 Given a query \( Q = (q_v, q_s, k) \), where \( q_s \) is the query attribute set, the AF-NN search aims to return a set \( R \subseteq D_s \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_s \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_s = \{ v_i \mid (v_i, s_i) \in D \land q_s \subseteq s_i \} \).
@@
 
-		Let \( D = \{(v_1, \textcolor{blue}{a}_1), \ldots, (v_n, \textcolor{blue}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \).
+		Let \( D = \{(v_1, \textcolor{blue}{a}_1), \ldots, (v_n, \textcolor{blue}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each  \( v_i \) associated with an attribute value \( a_i \).
 Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).
@@
 	\noindent\textbf{\underline{IVF.}} 
-	\textcolor{blue}{IVF divides data into multiple clusters through through a clustering algorithm (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
-During querying, algorithms search only within the few clusters closest to the query point, which reduces computational load.}
+	\textcolor{blue}{IVF divides data into multiple clusters through a clustering algorithm (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
+During querying, algorithms search only a few clusters closest to the query point, which reduces computational load.}
 
@@
 
-	\section{Hybrid query Algorithms}
+	\section{Hybrid querying Algorithms}
 
@@
 Specifically, Section~3.1 describes methods for attribute filtering, Section~3.2 discusses those for range filtering, and Section~3.3 introduces vector libraries and databases that support both attribute filtering and range filtering.
-	Table~\ref{tab:compair_1} provides a comparative overview of six attribute filtering and five representative range filtering algorithms.
+	Table~\ref{tab:compair_1} provides a comparative overview of 6 attribute filtering and 5 representative range filtering algorithms.
 
@@
 
-	\textcolor{blue}{The first seven datasets are widely used in existing works.
+	\textcolor{blue}{The first 7 datasets are widely used in existing works.
 As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.

### 2025-08-01 Revision/response.tex
1

@@
 
-As shown in Figure\ref{fig:attribute_distribution} below, for performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Stable and Unstable) in the figure.
+As shown in Figure~\ref{fig:attribute_distribution} below, for performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Stable and Unstable) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
@@
 
-As shown in Figure~\ref{fig:attribute_selectivity} below, for performance under different attribute selectivity, to reflect the performance differences of each algorithm under different attribute selectivity, we added performance rankings for each algorithm across different selectivity levels in the figure.
+As shown in Figure~\ref{fig:attribute_selectivity}, for performance under different attribute selectivity, to reflect the performance differences of each algorithm under different attribute selectivity, we added performance rankings for each algorithm across different selectivity levels in the figure.
 This provides a clearer illustration of how each algorithm is affected by different attribute selectivity.

### 2025-08-01 VLDB2026/main.tex
1
Update main.tex

--- 2025-08-01 VLDB2026/main.tex
@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely relates to structured data.
-For attribute filtering algorithms, \textcolor{blue}{factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity ~\cite{analyticdb,milvus} significantly impact algorithm performance.} As for range filtering algorithms, the size of the query range and the characteristics of different datasets play an important role in determining algorithm performance.
-
-	\textcolor{blue}{Although existing works~\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking.
+For attribute filtering algorithms, \textcolor{blue}{factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity ~\cite{analyticdb,milvus} significantly impact algorithm performance.} As for range filtering algorithms, the width of the query range and the characteristics of different datasets play an important role in determining algorithm performance.
+
+	\textcolor{blue}{Although existing studies~\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking.
 Despite BigANN 2023~\cite{bigann2023} evaluates the performance of some hybrid query algorithms, it still presents the following notable limitations:
@@
 	2) It only uses a single dataset and focuses solely on single-attribute and dual-attribute query scenarios, while not considering the impact of attribute selectivity on query performance.
-	3) It only simply compares the query speed and recall of different algorithms, but does not consider key metrics such as the time and space overhead of each algorithm, and also does not deeply analyze the specific reasons for algorithm performance.}
+	3) It only simply compares the query speed and recall of different algorithms, but does not consider key metrics such as the time and space overhead of each algorithm, and it lacks an in-depth analysis of the specific reasons for algorithm performance.}
 
@@
 	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods.
-In addition, we survey 5 range filtering algorithms, and provide an overview of a vector library and three vector databases.
+In addition, we survey 5 range filtering algorithms, and provide an overview of one vector library and 3 vector databases.
 These efforts offer a unified reference framework for future research.
@@
 The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-we also further analyze the factors that affect the performance of the range filtering algorithms.
+We also further analyze the factors that affect the performance of the range filtering algorithms.
 %	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
@@
 %	\subsection{Index Organization in Hybrid ANN Search}
-	\subsection{Index Organization}
+	\subsection{Index Organization in Hybrid Query}
 
@@
 Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset to compute LID.
-The higher the LID value, the harder the dataset.
-
-	\textcolor{blue}{The first seven datasets are widely used in existing works.
+A higher LID value indicates a more complex dataset.
+
+	\textcolor{blue}{The first 7 datasets are widely used in existing studies, while the remaining are common datasets with added real attributes.
 As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.
@@
 For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes.
-The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}
+The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes.}
 

### 2025-08-01 VLDB2026/main.tex

--- 2025-08-01 VLDB2026/main.tex
@@
 Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset to compute LID.
-The higher the LID value, the harder the dataset.
-
-	\textcolor{blue}{The first 7 datasets are widely used in existing works.
+A higher LID value indicates a more complex dataset.
+
+	\textcolor{blue}{The first 7 datasets are widely used in existing studies, while the remaining are common datasets with added real attributes.
 As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.
@@
 
-	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
+	(1) \textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
 	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.
@@
 
-	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
+	(2) \textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
 	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods.

### 2025-08-01 Revision/response.tex
Update response.tex

@@
 \textbf{Response:} We believe this is an excellent suggestion.
-To provide a more comprehensive evaluation of the robustness of each algorithm, we introduce new experiments on two challenging multi-modal datasets.
+To provide a more comprehensive evaluation of algorithm robustness, we have conducted new experiments involving multi-modal queries and complex query types.
 
@@
 
-As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality.
+As for  query  that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, no existing  algorithm—other than general-purpose  systems such as Milvus and Faiss—supports this functionality.
+Therefore, we do not include such combined queries in our experiments and instead evaluate attribute filtering and range queries separately.
+%As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality.
 For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously.

### 2025-08-01 Revision/response.tex
1

@@
 
-As shown in Figure~\ref{fig:attribute_distribution} below, for performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Stable and Unstable) in the figure.
+As shown in Figure~\ref{fig:attribute_distribution}, for performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Stable and Unstable) in the figure.
 This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions.
@@
 In order to further verify the performance of these algorithms in real scenarios, we have conducted experiments on these two datasets with real attributes and have analyzed the experimental results.
-\textbf{(Please see Section 4.2 and  Section 4.3,  highlighted in blue in the revised manuscript.).}
+\textbf{(Please see Section 4.2 and  Section 4.3,  highlighted in blue in the revised manuscript.)}
 

### 2025-08-01 Revision/response.tex
1

@@
 The experimental results are shown in Figure~\ref{fig:attribute big dataset} and Figure~\ref{fig:range big dataset}.
-\textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
+\textbf{(Please refer to Section 4.1.3 for details on the experimental platform used for large-scale datasets.
+The corresponding experiments can be found in the "Large-scale Datasets" parts of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
 %\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}
+
+Section 4.1.3:\textcolor{blue}{"We conduct most experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache.
+However, due to memory limitations, this server cannot support large-scale datasets.
+We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM.}
 

### 2025-08-01 Revision/response.tex
1

@@
 Section 4.2.3: \textcolor{blue}{
-	"We conduct experiments on two multimodal datasets Text2image-Mix and Text2image.
+	"We conduct experiments on two multimodal data-\\sets Text2image-Mix and Text2image.
 On Text2imageMix dataset, as shown in Figure 9, UNG and NHQ consistently perform best, followed by CAPS.
@@
 In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset.
-The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset.
+Due to insufficient memory on our original server for running algorithms on such large-scale datasets, we conducted these experiments on a server with significantly larger memory capacity.
+The results show that most algorithms struggle to balance performance with time and space costs on this dataset.
 In particular, StitchedVamana performs poorly on Deep100M.

### 2025-08-01 VLDB2026/main.tex
1

@@
 	We conduct most experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache.
-\textcolor{blue}{ We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM.}
+\textcolor{blue}{We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM.}
 %	\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.
@@
 	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} 
-	\textcolor{blue}{As shown in the Figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+	\textcolor{blue}{As shown in the Figure~\ref{fig:attribute big dataset}, on the Deep100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.

### 2025-08-01 Revision/response.tex
1

@@
 In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset.
-Due to insufficient memory on our original server for running algorithms on such large-scale datasets, we conducted these experiments on a server with significantly larger memory capacity.
+Due to insufficient memory on our original server for running algorithms on such large-scale datasets, we have conducted these experiments on a server with larger memory capacity.
 The results show that most algorithms struggle to balance performance with time and space costs on this dataset.
@@
 
-Section 4.1.3:\textcolor{blue}{"We conduct most experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache.
-However, due to memory limitations, this server cannot support large-scale datasets.
-We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM.}
+Section 4.1.3:\textcolor{blue}{"We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM.}
 

### 2025-08-01 Revision/response.tex
1

@@
 In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset.
-Due to insufficient memory on our original server for running algorithms on such large-scale datasets, we have conducted these experiments on a server with larger memory capacity.
+Due to insufficient memory on our original server for running algorithms on such large-scale datasets, we have conducted these experiments on a server with larger memory capacity, equipped with 2×AMD 7Y43 processors and 1TB of RAM.
 The results show that most algorithms struggle to balance performance with time and space costs on this dataset.
@@
 
-Section 4.1.3:\textcolor{blue}{"We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM.}
+Section 4.1.3:\textcolor{blue}{"We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM."}
 

### 2025-08-01 VLDB2026/main.tex
1

@@
 	\textcolor{blue}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
-Next, we provide a discussion of the advantages and disadvantages of each algorithm.}
+Next, we provide a comprehensive discussion of the advantages and disadvantages of each algorithm.}
 
@@
 \textcolor{blue}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
-FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios.
+FilteredVamana supports dynamic insertion and disk-based indexing, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
 However, its disk-based construction significantly increases indexing time, and its performance is highly sensitive to attribute distribution.
@@
 	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
-It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it more general-purpose.}
+It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution.}
 %	Table~\ref{tab:algo_scenarios} also shows the application scenarios of range filtering.

### 2025-08-01 VLDB2026/main.tex
1

@@
 In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
-\textcolor{blue}{Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.}
+\textcolor{blue}{Additionally, exploring algorithms that support a combined and efficient use of attribute and range filtering is also an important research topic.}
 %	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.

### 2025-10-27 VLDB2026/main.tex
delete color

--- 2025-08-01 VLDB2026/main.tex
@@
 %!TEX program = pdflatex
-\documentclass[sigconf, nonacm]{acmart}
+
+\documentclass[sigconf, nonacm, pdfa]{acmart}
 %\usepackage{fontspec}
@@
 % issue-specific
-\newcommand\vldbvolume{14}
-\newcommand\vldbissue{1}
-\newcommand\vldbyear{2020}
+
+\newcommand\vldbvolume{19}
+\newcommand\vldbissue{2}
+\newcommand\vldbyear{2025}
 % should be fine as it is
@@
 % whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
-\newcommand\vldbpagestyle{plain}
+\newcommand\vldbpagestyle{empty} 
+\usepackage[a-2b]{pdfx}
 
@@
 Our study introduces 15 hybrid query algorithms and systematically classifies them based on multiple dimensions, such as index organization and filtering strategy, providing a reference for the categorization of hybrid queries.
-%		In experiments, for attribute filtering, we construct standard attribute sets, enabling a unified comparison of algorithms in terms of index construction efficiency, query performance, and robustness.
-For range filtering, we also evaluate the algorithm performance across the 3 metrics through controlled variation of query ranges.
-	\textcolor{blue}{In the experiments, we construct standardized attribute and range sets for attribute filtering and range filtering, respectively, enabling a unified comparison of algorithms in terms of index construction efficiency and query performance.
-Furthermore, we evaluate the robustness of the algorithms across multiple dimensions, including data distributions, platforms, and scalability on a 100-million-scale dataset.}
+
+In the experiments, we construct standardized attribute and range sets for attribute filtering and range filtering, respectively, enabling a unified comparison of algorithms in terms of index construction efficiency and query performance.
+Furthermore, we evaluate the robustness of the algorithms across multiple dimensions, including data distributions, platforms, and scalability on a 100-million-scale dataset.
 	 Additionally, we conduct an in-depth analysis of the experimental results based on the underlying principles of algorithms.
@@
 	Nearest Neighbor (NN) search \cite{cover1967nearest} aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems  \cite{monolith}  and image retrieval \cite{wang2012scalable}.
-	% 需要添加引用，下面这段
 	However, with the exponential growth of data volume and the increasing dimensionality of vectors \cite{weber1998quantitative}, traditional NN search methods struggle to meet the demands of real-time search.
@@
 In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely relates to structured data.
-For attribute filtering algorithms, \textcolor{blue}{factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity ~\cite{analyticdb,milvus} significantly impact algorithm performance.} As for range filtering algorithms, the width of the query range and the characteristics of different datasets play an important role in determining algorithm performance.
-
-	\textcolor{blue}{Although existing studies~\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking.
+For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity ~\cite{analyticdb,milvus} significantly impact algorithm performance.
+As for range filtering algorithms, the width of the query range and the characteristics of different datasets play an important role in determining algorithm performance.
+
+Although existing studies~\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking.
 Despite BigANN 2023~\cite{bigann2023} evaluates the performance of some hybrid query algorithms, it still presents the following notable limitations:
@@
 	2) It only uses a single dataset and focuses solely on single-attribute and dual-attribute query scenarios, while not considering the impact of attribute selectivity on query performance.
-	3) It only simply compares the query speed and recall of different algorithms, but does not consider key metrics such as the time and space overhead of each algorithm, and it lacks an in-depth analysis of the specific reasons for algorithm performance.}
-
-	\textcolor{blue}{To fill this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
-Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
-
-%	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute filtering ~\cite{NHQ,diskann} and range filtering algorithms \cite{serf,iRangeGraph}.
-In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data.
-For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute  selectivity \textcolor{orange}{\cite{analyticdb,milvus}} significantly impact algorithm performance.
-As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.
-%	
-%	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some ANN algorithms, it presents several notable limitations:
-%	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. 
-%	%	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
-%	2) It focuses only on single-attribute and dual-attribute query scenarios. 
-%	%	\sout{neglecting the more complex demands of multi-attribute queries.
-In real-world applications, an object typically involves multiple attributes.}\textcolor{blue}{ \sout{For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}}
-%	3) It does not evaluate algorithm performance under different attribute distributions. 
-%	%	\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}
-%	
-%	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
-%%	To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios.
-Additionally, we further assess the robustness of each algorithm under varying conditions.
-%	
-%	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited. 
-%	\textcolor{orange}{%Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms.
-%	Although existing works\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a dedicated experimental study on hybrid query algorithms is still lacking.
-%	To address this gap, we carry out the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
-Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}
-%	
+	3) It only simply compares the query speed and recall of different algorithms, but does not consider key metrics such as the time and space overhead of each algorithm, and it lacks an in-depth analysis of the specific reasons for algorithm performance.
+
+To fill this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios.
+Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.
+
 	\subsection{Our Contributions}
@@
 	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{blue}{including varying vector datasets, attribute distributions, number of attributes participating in index construction, number of query attributes, and selectivity.
-Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and two multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
+We design comprehensive experimental settings that reflect diverse application requirements, including varying vector datasets, attribute distributions, number of attributes participating in index construction, number of query attributes, and selectivity.
+Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and two multi-modal datasets.
+These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 
@@
 
-		Let \( D = \{(v_1, \textcolor{blue}{a}_1), \ldots, (v_n, \textcolor{blue}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each  \( v_i \) associated with an attribute value \( a_i \).
+		Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each  \( v_i \) associated with an attribute value \( a_i \).
 Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).
@@
 	%We briefly introduce the fundamental principles of these two types in the following.
-	\textcolor{blue}{Here, we briefly review the core concepts of these indexes and outline how attribute and range constraints are embedded to support hybrid queries functionality.}
+	Here, we briefly review the core concepts of these indexes and outline how attribute and range constraints are embedded to support hybrid queries functionality.
 
 	\noindent\textbf{\underline{Graph.}}
-	\textcolor{blue}{Graph structures accelerate ANN search by connecting each data point with its nearest neighbors, as shown in Figure~\ref{fig:graph}.
-During querying, algorithms start from an initial point and use a greedy strategy to progressively move towards closer neighbors until convergence (e.g., the path from $c$ to $j$ in the 1NN case).}
-
-	\textcolor{blue}{Graph indexes are widely used in hybrid ANN search due to their efficiency.
+Graph structures accelerate ANN search by connecting each data point with its nearest neighbors, as shown in Figure~\ref{fig:graph}.
+During querying, algorithms start from an initial point and use a greedy strategy to progressively move towards closer neighbors until convergence (e.g., the path from $c$ to $j$ in the 1NN case).
+
+Graph indexes are widely used in hybrid ANN search due to their efficiency.
 To support hybrid queries, in attribute filtering, a common practice involves attaching attribute metadata to nodes or edges, thereby skipping parts that do not satisfy query conditions during traversal (e.g., NHQ, Filtered-DiskANN, ACORN).
-In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges that satisfy range constraints, thus narrowing the search space (e.g., SeRF, DSG).}
-
-%	Graph-based ANN search algorithms accelerate queries by building graph indexes on datasets.
-As illustrated in Figure~\ref{fig:graph}, each data point in the dataset corresponds to a point in the graph, and neighboring vertices (e.g., $a$ and $b$) are connected via edges based on their distance $\textit{dist}(a, b)$.
-In the graph index, each point maintains connections only to its nearest neighbors to preserve query efficiency.
-For instance, in Figure~\ref{fig:graph}, the gray point $c$ is connected to 5 neighbors $(a, b, d, e, f)$ and can traverse to them via corresponding edges.
-%	
-%	Given a query point $q$, the graph-based ANN search typically follows a greedy search strategy to find the $k$ nearest neighbors.
-For illustration, consider the case where $k = 1$ (i.e., 1NN): The algorithm initiates the search from an entry point (the gray point $c$).
-If there exists a neighbor $n$ (the point $f$) of the current point such that $\textit{dist}(n, q) < \textit{dist}(c, q)$, the algorithm updates the current point to $n$.
-This process is iteratively repeated—always moving to the neighbor closest to $q$—until no neighbor is found that is closer than the current point.
-The final point reached (the blue point $j$) is returned as the approximate nearest neighbor of $q$.
-%	
-%	\textcolor{violet}{Graph-based indexes are widely adopted in Hybrid ANN search algorithms due to their excellent performance.
-To support hybrid queries, existing approaches usually augment the original graph structures by explicitly associating attribute or range information with vertices or edges.
-In attribute filtering, a common approach is to attach attribute metadata to vertices or edges, allowing the traversal process to skip nodes or edges that do not meet attribute conditions of the query (e.g., NHQ, Filtered-DiskANN, ACORN).
-In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges satisfying the range constraints, effectively narrowing down the search space (e.g., SeRF, DSG).}
+In range filtering, edges typically store valid attribute intervals, and traversal proceeds only along edges that satisfy range constraints, thus narrowing the search space (e.g., SeRF, DSG).
 
 	\noindent\textbf{\underline{IVF.}} 
-	\textcolor{blue}{IVF divides data into multiple clusters through a clustering algorithm (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
+	\textcolor{black}{IVF divides data into multiple clusters through a clustering algorithm (e.g., K-Means), with each cluster represented by a center (Figure~\ref{fig:ivf}).
 During querying, algorithms search only a few clusters closest to the query point, which reduces computational load.}
 
-	\textcolor{blue}{IVF-based indexes also offer unique advantages in hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
+	\textcolor{black}{IVF-based indexes also offer unique advantages in hybrid ANN search scenarios, including natural support for pre-filtering, low memory footprint, and small index size.
 Efficient filtering is achieved by excluding vectors that do not satisfy attribute constraints before distance computation (e.g., Faiss, Milvus).
@@
 
-		\caption{\textcolor{blue}{Overview of AF-ANN and RF-ANN Search Algorithms}}
+		\caption{\textcolor{black}{Overview of AF-ANN and RF-ANN Search Algorithms}}
 		\small
@@
 %				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
-		\textcolor{blue}{
+		\textcolor{black}{
 		\textit{Filtered}: FilteredVamana, \textit{Stitched}: StitchedVamana, \textit{Win}: WinFilter.
@@
 %	\footnote{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}
-	\noindent\textbf{\underline{NHQ} \footnote{\textcolor{blue}{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}} \cite{NHQ}}
+	\noindent\textbf{\underline{NHQ} \footnote{\textcolor{black}{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}} \cite{NHQ}}
 	Traditional attribute filtering algorithms usually perform attribute constraints and ANN search separately.
@@
 
-	\noindent\textbf{\underline{Filtered-DiskANN} \footnote{\textcolor{blue}{https://github.com/microsoft/DiskANN}} \cite{Filtered-diskann}}
+	\noindent\textbf{\underline{Filtered-DiskANN} \footnote{\textcolor{black}{https://github.com/microsoft/DiskANN}} \cite{Filtered-diskann}}
 	%\sout{The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.}
@@
 
-	\noindent\textbf{\underline{CAPS} \footnote{\textcolor{blue}{https://github.com/gaurav16gupta/constrainedANN}} \cite{CAPS}}
+	\noindent\textbf{\underline{CAPS} \footnote{\textcolor{black}{https://github.com/gaurav16gupta/constrainedANN}} \cite{CAPS}}
 	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
@@
 
-	\noindent\textbf{\underline{ACORN} \footnote{\textcolor{blue}{https://github.com/stanford-futuredata/ACORN}} \cite{ACORN}}
+	\noindent\textbf{\underline{ACORN} \footnote{\textcolor{black}{https://github.com/stanford-futuredata/ACORN}} \cite{ACORN}}
 	%	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
@@
 %	ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of prior methods in large-scale or unknown predicate scenarios.
-	\textcolor{blue}{ACORN adopts a predicate-agnostic indexing framework.
+	\textcolor{black}{ACORN adopts a predicate-agnostic indexing framework.
 It is based on Hierarchical Navigable Small World (HNSW) \cite{hnsw} and builds a denser hierarchical graph through neighborhood expansion and edge pruning.}
@@
 
-	\noindent\textbf{\underline{UNG} \footnote{\textcolor{blue}{https://github.com/YZ-Cai/Unified-Navigating-Graph}} \cite{UNG}} 
+	\noindent\textbf{\underline{UNG} \footnote{\textcolor{black}{https://github.com/YZ-Cai/Unified-Navigating-Graph}} \cite{UNG}} 
 	%\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
@@
 
-	\noindent\textbf{\underline{Puck} \footnote{\textcolor{blue}{https://github.com/baidu/puck}} \cite{puck}} 
+	\noindent\textbf{\underline{Puck} \footnote{\textcolor{black}{https://github.com/baidu/puck}} \cite{puck}} 
 	%While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
@@
 
-	\noindent\textbf{\underline{SeRF} \footnote{\textcolor{blue}{https://github.com/rutgers-db/SeRF}} \cite{serf}} 
+	\noindent\textbf{\underline{SeRF} \footnote{\textcolor{black}{https://github.com/rutgers-db/SeRF}} \cite{serf}} 
 %	Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
@@
 
-	\noindent\textbf{\underline{WinFilter} \footnote{\textcolor{blue}{https://github.com/JoshEngels/RangeFilteredANN}} \cite{winFilter}}
+	\noindent\textbf{\underline{WinFilter} \footnote{\textcolor{black}{https://github.com/JoshEngels/RangeFilteredANN}} \cite{winFilter}}
 %	Unlike SeRF, which focuses on graph compression, 
@@
 
-	\noindent\textbf{\underline{iRange} \footnote{\textcolor{blue}{https://github.com/YuexuanXu7/iRangeGraph}} \cite{iRangeGraph}}
+	\noindent\textbf{\underline{iRange} \footnote{\textcolor{black}{https://github.com/YuexuanXu7/iRangeGraph}} \cite{iRangeGraph}}
 %	To address the query efficiency degradation caused by the graph compression in SeRF, iRange adopts a more flexible strategy.
@@
 
-	\noindent\textbf{\underline{DSG} \footnote{\textcolor{blue}{https://github.com/rutgers-db/DynamicSegmentGraph}} \cite{DSG}}
+	\noindent\textbf{\underline{DSG} \footnote{\textcolor{black}{https://github.com/rutgers-db/DynamicSegmentGraph}} \cite{DSG}}
 %	Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets. SeRF allows incremental insertion but requires ordered attributes. 
@@
 
-	\noindent\textbf{\underline{UNIFY} \footnote{\textcolor{blue}{https://github.com/sjtu-dbgroup/UNIFY}} \cite{UNIFY}}
+	\noindent\textbf{\underline{UNIFY} \footnote{\textcolor{black}{https://github.com/sjtu-dbgroup/UNIFY}} \cite{UNIFY}}
 %	Unlike DSG, which relies on rectangle trees and range-aware edges, UNIFY adopts a segmentation-based approach and proposes a range query index structure. 
@@
 
-\noindent\textbf{\underline{Faiss}\footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
+\noindent\textbf{\underline{Faiss}\footnote{\textcolor{black}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
 Faiss is an efficient similarity search library. It supports hybrid search by using an ID selector to filter data before performing ANN search.
@@
 
-\noindent\textbf{\underline{PASE} \footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase}} PASE is a vector index plugin for PostgreSQL.
+\noindent\textbf{\underline{PASE} \footnote{\textcolor{black}{https://github.com/alipay/PASE}} \cite{pase}} PASE is a vector index plugin for PostgreSQL.
 It uses a post-filtering strategy.
@@
 
-\noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}} VBASE is also a vector plugin for PostgreSQL.
+\noindent\textbf{\underline{VBASE} \footnote{\textcolor{black}{https://github.com/microsoft/MSVBASE}} \cite{vbase}} VBASE is also a vector plugin for PostgreSQL.
 Unlike PASE, it applies filters during the HNSW index traversal, discarding unmatched nodes on the fly.
@@
 
-\noindent\textbf{\underline{Milvus} \footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus}} Milvus is a vector database designed for large-scale similarity search.
+\noindent\textbf{\underline{Milvus} \footnote{\textcolor{black}{https://github.com/milvus-io/milvus}} \cite{milvus}} Milvus is a vector database designed for large-scale similarity search.
 In hybrid queries, it adopts a pre-filtering strategy, similar to the ID selector mechanism used in Faiss.
@@
 %	
-%	\noindent\textbf{\underline{Faiss} \footnote{\textcolor{blue}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
+%	\noindent\textbf{\underline{Faiss} \footnote{\textcolor{black}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
 %	Faiss is a library designed for efficient similarity search.
@@
 %	
-%	\noindent\textbf{\underline{PASE} \footnote{\textcolor{blue}{https://github.com/alipay/PASE}} \cite{pase}}
+%	\noindent\textbf{\underline{PASE} \footnote{\textcolor{black}{https://github.com/alipay/PASE}} \cite{pase}}
 %	PASE is a vector indexing plugin for the PostgreSQL database \cite{postgresql13.4}, supporting two index types: IVF\_Flat \cite{johnson2019billion} and HNSW.
@@
 %	
-%	\noindent\textbf{\underline{VBASE} \footnote{\textcolor{blue}{https://github.com/microsoft/MSVBASE}} \cite{vbase}}
+%	\noindent\textbf{\underline{VBASE} \footnote{\textcolor{black}{https://github.com/microsoft/MSVBASE}} \cite{vbase}}
 %	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
@@
 %	
-%	\noindent\textbf{\underline{Milvus} \footnote{\textcolor{blue}{https://github.com/milvus-io/milvus}} \cite{milvus}}
+%	\noindent\textbf{\underline{Milvus} \footnote{\textcolor{black}{https://github.com/milvus-io/milvus}} \cite{milvus}}
 %	Unlike PASE and VBASE, which are database extensions, Milvus is an vector database purpose-built for large-scale similarity search.
@@
 
-	\textcolor{blue}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloV-\\e~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
+	\textcolor{black}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloV-\\e~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
 
@@
 
-	\textcolor{blue}{The first 7 datasets are widely used in existing studies, while the remaining are common datasets with added real attributes.
+	\textcolor{black}{The first 7 datasets are widely used in existing studies, while the remaining are common datasets with added real attributes.
 As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.
@@
 
-	\textcolor{blue}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2-Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
+	\textcolor{black}{Additionally, we use the Out-of-Distribution (OOD) dataset Text2-Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms.
 The Text2Image dataset includes two versions.
@@
 		\item \textbf{Index Size}: The storage size of the persisted index on disk.
-		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction \textcolor{blue}{and search}.
+		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction \textcolor{black}{and search}.
 	\end{enumerate}
@@
 
-	%\textcolor{blue}{For all algorithms, we adopt recommended settings from the original study and adjust the parameters related to search in order to obtain different Recall and QPS.}
-
-	\subsubsection{\textcolor{blue}{Setting}}
+	%\textcolor{black}{For all algorithms, we adopt recommended settings from the original study and adjust the parameters related to search in order to obtain different Recall and QPS.}
+
+	\subsubsection{\textcolor{black}{Setting}}
 
 	We conduct most experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache.
-\textcolor{blue}{We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM.}
+\textcolor{black}{We test on  large-scale dataset using a server with 2×AMD 7Y43 processors and 1TB RAM.}
 %	\textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.
@@
 
-	\textcolor{blue}{
+	\textcolor{black}{
 	Regarding experimental parameter selection, we adopt the recommended settings from original papers when available.
@@
 }
-%	\textcolor{blue}{
+%	\textcolor{black}{
 %	\subsubsection{Parameters}
@@
 	%4.2.1
-	\subsubsection{\textcolor{blue}{Time and Space overhead}}
+	\subsubsection{\textcolor{black}{Time and Space overhead}}
 	% \subsubsection{\textbf{Attribute Filtering}}
@@
 		\setlength{\belowcaptionskip}{-0.3cm}
-		\caption{\textcolor{blue}{Time and Space Overhead (AF)}}
+		\caption{\textcolor{black}{Time and Space Overhead (AF)}}
 		\label{fig:build_index_comparison}
@@
 
-	\textcolor{blue}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{blue}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{blue}{build peak memory and search peak memory}.
+	\textcolor{black}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{black}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{black}{build peak memory and search peak memory}.
 Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.
 Furthermore, we did not measure PASE on large-scale datasets, as we estimated it would take over 10 days.
-\textcolor{blue}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other 6 medium-scale datasets.
+\textcolor{black}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other 6 medium-scale datasets.
 Notably, the VBASE and PASE algorithms only support single-threaded construction.}
@@
 }
-\textcolor{blue}{On the medium-scale datasets (Figure~\ref{fig:build_time_comparison_query1} left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
+\textcolor{black}{On the medium-scale datasets (Figure~\ref{fig:build_time_comparison_query1} left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
 This is because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency.
@@
 
-\textcolor{blue}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1} right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
+\textcolor{black}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1} right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time.
 This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead.
@@
 \textit{\textbf{Index size.}}
-\textcolor{blue}{
+\textcolor{black}{
 	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata.
@@
 As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
-\textcolor{blue}{\textit{\textbf{Peak memory.}}	
+\textcolor{black}{\textit{\textbf{Peak memory.}}	
 We present the peak memory usage during index construction and query processing in Figure~\ref{fig:build_memory_mb_comparison} and Figure~\ref{fig:search_memory_mb_comparison}, respectively.
@@
 
-\textcolor{blue}{However, there are notable exceptions.
+\textcolor{black}{However, there are notable exceptions.
 During index construction, PASE adopts an on-demand loading strategy, resulting in build peak memory usage even lower than the final index size.
@@
 
-	\textcolor{blue}{NHQ and StitchedVamana also perform well and show similar and stable performance across all datasets.
+	\textcolor{black}{NHQ and StitchedVamana also perform well and show similar and stable performance across all datasets.
 This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.} StitchedVamana outperforms FilteredVamana in query efficiency.
@@
 However, this also demonstrates that IVF-based methods remain very promising for hybrid queries.
-	\textcolor{blue}{Additionally, Puck and CAPS also perform relatively well.
+	\textcolor{black}{Additionally, Puck and CAPS also perform relatively well.
 They further reduce the search space on IVF indexes by using attribute partitioning, thereby achieving solid search performance.}
@@
 In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason.
-	\textcolor{blue}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity.
+	\textcolor{black}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity.
 This makes single-attribute queries more difficult and degrades performance.}
@@
 To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
-\textcolor{blue}{In this experiment, we only evaluate algorithms that support this multi-attribute query scenario.}
+\textcolor{black}{In this experiment, we only evaluate algorithms that support this multi-attribute query scenario.}
 
@@
 
-	\textit{\textbf{Attribute Distribution.}} To evaluate the impact of attribute distribution, we generate base and query attributes \textcolor{blue}{on the SIFT dataset using four representative distributions: long-tail, normal, power-law, and uniform.}
+	\textit{\textbf{Attribute Distribution.}} To evaluate the impact of attribute distribution, we generate base and query attributes \textcolor{black}{on the SIFT dataset using four representative distributions: long-tail, normal, power-law, and uniform.}
 %	with four representative distributions—long-tail, normal, power-law, and uniform—across six datasets. 
@@
 PASE is excluded due to poor past performance.
-\textcolor{blue}{The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
+\textcolor{black}{The proximity of the curves in the figure reflects algorithm sensitivity to attribute distributional variations.
 When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change.}
@@
 
-	{\color{blue}{
+textcolor{black}{
 	Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
@@
 For ACORN--\(\gamma\), during index construction, attributes are primarily used for pruning in the lowest-layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
-Consequently, changes in attribute distribution have minimal impact on overall performance.}}
+Consequently, changes in attribute distribution have minimal impact on overall performance.}
 
@@
 %	This group includes ACORN-1, CAPS, Faiss, Faiss+HQI\_Batch, Puck, StitchedVamana and UNG, as illustrated in Figure~\ref{fig:exp_5_2_1}.
-	\textcolor{blue}{Figure~\ref{fig:exp_5_2_1} shows the algorithms suitable for low AS.}
-	\textcolor{blue}{ACORN-1}, Faiss, Puck, and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
-\textcolor{blue}{Pre-filtering strategies significantly reduce the number of candidate points under low AS, thereby lowering the cost of  computations.
+	\textcolor{black}{Figure~\ref{fig:exp_5_2_1} shows the algorithms suitable for low AS.}
+	\textcolor{black}{ACORN-1}, Faiss, Puck, and UNG all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
+\textcolor{black}{Pre-filtering strategies significantly reduce the number of candidate points under low AS, thereby lowering the cost of  computations.
 As a result, such strategies tend to perform better in low AS scenarios.} CAPS efficiently skips irrelevant subpartitions, reducing computational overhead.
@@
 %	This group includes FilteredVamana, NHQ, PASE and VBASE, as shown in Figure~\ref{fig:exp_5_2_2}.
-	\textcolor{blue}{Figure~\ref{fig:exp_5_2_2} shows the algorithms suitable for high AS.}
+	\textcolor{black}{Figure~\ref{fig:exp_5_2_2} shows the algorithms suitable for high AS.}
 	At low AS, FilteredVamana performs poorly in these scenarios.
@@
 %	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
-	\textcolor{blue}{Figure~\ref{fig:exp_5_2_3} shows algorithms that are insensitive to AS.}
+	\textcolor{black}{Figure~\ref{fig:exp_5_2_3} shows algorithms that are insensitive to AS.}
 	Milvus is mainly limited by system-level communication overhead, such as API latency.
@@
 %	\subsubsection{Scalability Study}
-	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}} \textcolor{blue}{
+	\textit{\textbf{\textcolor{black}{Multi-Modal Queries.}}} \textcolor{black}{
 	We conduct experiments on two multi-modal  datasets Text2image-Mix and Text2image. 
@@
 
-	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} 
-	\textcolor{blue}{As shown in the Figure~\ref{fig:attribute big dataset}, on the Deep100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+	\textit{\textbf{\textcolor{black}{Large-scale Dataset.}}} 
+	\textcolor{black}{As shown in the Figure~\ref{fig:attribute big dataset}, on the Deep100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 
-	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
+	\textit{\textbf{\textcolor{black}{Different Hardware Environments.}}} 
 %	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
@@
 Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
-	\textcolor{blue}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
+	\textcolor{black}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
 It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
@@
 		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
-
-		%\vspace{0.1cm}
 
@@
 		\setlength{\belowcaptionskip}{-0.3cm}
-		\caption{\textcolor{blue}{Time and Space Overhead (RF)}}
+		\caption{\textcolor{black}{Time and Space Overhead (RF)}}
 		\label{fig:rangeFilter_build_index_comparison}
@@
 	\subsection{Range Filtering}
-	\textcolor{blue}{Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
+	\textcolor{black}{Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value.
 The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones.
 }
-	\subsubsection{\textcolor{blue}{Time and Space overhead.}}
+	\subsubsection{\textcolor{black}{Time and Space overhead.}}
 
 	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
-	Similarly, we also evaluate \textcolor{blue}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
-\textcolor{blue}{Notably, all algorithms use single-threaded index construction on medium-scale datasets, and 64-thread construction on the large-scale Deep100M dataset, except DSG, which only supports single-threading.
+	Similarly, we also evaluate \textcolor{black}{4} key metrics mentioned above in \textit{Range Filtering} algorithms.
+\textcolor{black}{Notably, all algorithms use single-threaded index construction on medium-scale datasets, and 64-thread construction on the large-scale Deep100M dataset, except DSG, which only supports single-threading.
 For WinFilter, we use its integrated Super-Postfiltering on medium datasets for best performance, and switch to its base algorithm Vamana-WST on Deep100M due to construction overhead.
@@
 %	DSG only supports single-threaded construction, resulting in the longest build time.}
-	\textcolor{blue}{
+	\textcolor{black}{
 	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss and Milvus, based on the IVF architecture, require less time.
@@
 
-\textcolor{blue}{In addition, the two HNSW-based methods, ACORN-1 and SeRF, also achieve short index construction time.
+\textcolor{black}{In addition, the two HNSW-based methods, ACORN-1 and SeRF, also achieve short index construction time.
 ACORN-1 closely follows the original HNSW construction process and reduces the number of candidate neighbors in the upper layers to lower computational overhead.
@@
 
-\textcolor{blue}{We observe that ACORN-\(\gamma\), DSG and WinFilter exhibit relatively long index construction time.
+\textcolor{black}{We observe that ACORN-\(\gamma\), DSG and WinFilter exhibit relatively long index construction time.
 Although the first two methods are also based on HNSW, ACORN-\(\gamma\) extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
@@
 
-	\textcolor{blue}{Similar to attribute filtering, PASE requires the most storage. }
-	\textcolor{blue}{Additionally, DSG also results in a large index size, especially on large-scale datasets.
+	\textcolor{black}{Similar to attribute filtering, PASE requires the most storage. }
+	\textcolor{black}{Additionally, DSG also results in a large index size, especially on large-scale datasets.
 As an enhancement over SeRF, DSG stores additional metadata for each edge in its index structure.
@@
 
-	\textcolor{blue}{\textit{\textbf{Peak memory.}}  
+	\textcolor{black}{\textit{\textbf{Peak memory.}}  
 	As explained in the attribute filtering analysis, methods with larger index sizes (including the dataset) tend to exhibit higher peak memory consumption.
@@
 
-	\textcolor{blue}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism.
+	\textcolor{black}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism.
 Although the final index size remains relatively small, the peak memory usage increases significantly during both construction and search.
@@
 	In this experiment, we follow the query range definition adopted by prior work~\cite{HQI}.
-\textcolor{blue}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.}
+\textcolor{black}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.}
 	% Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
-\textcolor{blue}{Due to the limitations of existing range filtering algorithms, the range filtering experiment only uses one attribute, and the dataset is sorted in ascending order according to the attribute value size.
+\textcolor{black}{Due to the limitations of existing range filtering algorithms, the range filtering experiment only uses one attribute, and the dataset is sorted in ascending order according to the attribute value size.
 WIT-Real and YT-Audio-Real use real attribute values, and the rest use randomly generated attribute values.}
@@
 
-	\textcolor{blue}{
+	\textcolor{black}{
 		As shown in Figure~\ref{fig:exp_8_2}, the algorithms that performed well are WinFilter, iRange, UNIFY, and Faiss.
@@
 
-	\textcolor{blue}{SeRF, ACORN, and vector databases performed poorly.
+	\textcolor{black}{SeRF, ACORN, and vector databases performed poorly.
 		SeRF demonstrates relatively weak overall performance, with a pronounced drop in recall under small-range query scenarios.
@@
 
-	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}}
-	\textcolor{blue}{
+	\textit{\textbf{\textcolor{black}{Multi-Modal Queries.}}}
+	\textcolor{black}{
 		Similar to attribute filtering, the performance of range filtering queries on the Text2image-Mix dataset (Figure~\ref{fig:range-multimodal}) is similar to the single-modality query performance (Figure~\ref{fig:exp_8_2}).
@@
 
-	\textit{\textbf{\textcolor{blue}{Large-scale Dataset.}}} \textcolor{blue}{As shown in the Figure~\ref{fig: range big dataset}, On the Deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+	\textit{\textbf{\textcolor{black}{Large-scale Dataset.}}} \textcolor{black}{As shown in the Figure~\ref{fig: range big dataset}, On the Deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).
@@
 
-	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
-	\textcolor{blue}{Consistent with Section 4.2.3, we conduct range filtering experiments on the YT-Audio-Real dataset using two server configurations, with results presented in Figure~\ref{fig:range-cross-platform}.
+	\textit{\textbf{\textcolor{black}{Different Hardware Environments.}}} 
+	\textcolor{black}{Consistent with Section 4.2.3, we conduct range filtering experiments on the YT-Audio-Real dataset using two server configurations, with results presented in Figure~\ref{fig:range-cross-platform}.
 Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable.
@@
 	\section{DISCUSSION}
-	\textcolor{blue}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
+	\textcolor{black}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}.
 Next, we provide a comprehensive discussion of the advantages and disadvantages of each algorithm.}
@@
 UNG stands out for its higher recall, precision, and QPS, and performs well in the OOD scenario (S7, S8).
-\textcolor{blue}{
+\textcolor{black}{
 Overall, UNG, NHQ and FilteredDisk\\-ANN demonstrate strong performance.
@@
 
-\textcolor{blue}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
+\textcolor{black}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries.
 FilteredVamana supports dynamic insertion and disk-based indexing, making it more suitable for extremely large-scale datasets even in memory-constrained environments.
@@
 
-\textcolor{blue}{
+\textcolor{black}{
 CAPS, based on clustering, features low index space overhead.
@@
 	\subsubsection{Range Filtering}
-\textcolor{blue}{
+\textcolor{black}{
 	WinFilter achieves the best search performance but requires high time and memory resources during index construction.
@@
 
-	\textcolor{blue}{
+	\textcolor{black}{
 	iRange has relatively low time and space costs for index construction.
@@
 
-		\textcolor{blue}{
+		\textcolor{black}{
 	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios.
@@
 	\subsubsection{General Algorithm}
-\textcolor{blue}{All of the following methods support both attribute filtering and range filtering.}
-
-\textcolor{blue}{
+\textcolor{black}{All of the following methods support both attribute filtering and range filtering.}
+
+\textcolor{black}{
 ACORN demonstrates average overall performance.
@@
 
-\textcolor{blue}{
+\textcolor{black}{
 Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability.
@@
 
-	\textcolor{blue}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. }
+	\textcolor{black}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. }
 %	For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
@@
 %		}
-		\textcolor{blue}{
+		\textcolor{black}{
 For example, in multi-attribute scenarios, some algorithms only support Boolean OR logic (e.g., FilterDiskANN), while others only support Boolean AND logic (e.g., NHQ and CAPS).
@@
 
-\textcolor{blue}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic.
+\textcolor{black}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic.
 Our experiments also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing.
@@
 
-	\textcolor{blue}{
+	\textcolor{black}{
 	Besides, our research indicates that the distribution and selectivity of attributes significantly impact the performance of attribute filtering methods.
@@
 	Except for DSG and UNIFY, most range filtering algorithms require the dataset to be pre-sorted before building the index.
-\textcolor{blue}{Moreover, existing range filtering algorithms do not support range queries with more than 3 attributes.} \textcolor{blue}{Designing algorithms that support an arbitrary number of range filterable attributes remains an open research challenge.}
-
-\textcolor{blue}{
+\textcolor{black}{Moreover, existing range filtering algorithms do not support range queries with more than 3 attributes.} \textcolor{black}{Designing algorithms that support an arbitrary number of range filterable attributes remains an open research challenge.}
+
+\textcolor{black}{
 In addition,our experiments show that different algorithms exhibit varying strengths under different query ranges.
@@
 
-	\textcolor{blue}{
+	\textcolor{black}{
 	Lastly, existing algorithms suffer from significant performance degradation on OOD datasets.
@@
 In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
-\textcolor{blue}{Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.}
+\textcolor{black}{Additionally, exploring algorithms that support a combined and efficient use of attribute and range filtering is also an important research topic.}
 %	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
@@
 %	In the future, it is essential to further explore the flexibility and robustness of attribute filtering algorithms, and improving the performance of range filtering algorithms remains an important direction.
-%	\textcolor{blue}{
+%	\textcolor{black}{
 %		In this paper, we evaluate hybrid query methods, including algorithms, vector databases, and libraries.

### 2025-10-27 VLDB2026/copyFigures.sh
change

@@ -1,0 +1,59 @@
+#!/bin/bash
+# 检查并复制 PDF 文件到 figures2 目录，保持路径结构
+
+# 目标根目录
+TARGET_DIR="figures2"
+
+# 文件列表（可复制你贴的完整清单）
+FILES=(
+"hybridANNS.pdf"
+"figures/exp/attribute_100M.pdf"
+"figures/exp/attribute_71.pdf"
+"figures/exp/attribute_85.pdf"
+"figures/exp/attribute_legend.pdf"
+"figures/exp/attribute_multimodel_1.pdf"
+"figures/exp/attribute_multimodel.pdf"
+"figures/exp/exp_1_1_SingleLabel_1thread.pdf"
+"figures/exp/exp_2_1.pdf"
+"figures/exp/exp_2_legend.pdf"
+"figures/exp/exp_3_1.pdf"
+"figures/exp/exp_4_1_MultiLabel_1thread.pdf"
+"figures/exp/exp_5_2_1.pdf"
+"figures/exp/exp_5_2_2.pdf"
+"figures/exp/exp_5_2_3.pdf"
+"figures/exp/exp_8_2.pdf"
+"figures/exp/range_71.pdf"
+"figures/exp/range_85.pdf"
+"figures/exp/range_deep100M.pdf"
+"figures/exp/range_legend.pdf"
+"figures/exp/range_multimodel_1.pdf"
+"figures/exp/range_multimodel.pdf"
+"figures/graph.pdf"
+"figures/indexData/exp_7_build_time_comparison_query1.pdf"
+"figures/indexData/exp_7_index_size_mb_comparison_query1.pdf"
+"figures/indexData/exp_7_memory_mb_comparison_query1.pdf"
+"figures/indexData/legend_only.pdf"
+"figures/indexData/rangeFilter_build_time_comparison_query.pdf"
+"figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf"
+"figures/indexData/rangeFilter_legend_only.pdf"
+"figures/indexData/rangeFilter_memory_mb_comparison_query.pdf"
+"figures/ivf.pdf"
+"figures/searchMem/label_memory_comparison.pdf"
+"figures/searchMem/range_memory_comparison.pdf"
+)
+
+echo "检查并复制 PDF 文件到 $TARGET_DIR ..."
+
+for file in "${FILES[@]}"; do
+    if [[ -f "$file" ]]; then
+        # 生成目标路径
[…]

### 2025-10-27 VLDB2026/main.tex
change
delete type3

@@
 
-		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
+		\includegraphics[width=0.92\textwidth]{figures/hybridANNS.pdf}
 		\caption{Hybrid Query Example}
@@
 		\hspace*{8pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
-		\includegraphics[width=0.95\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径
+		\includegraphics[width=0.95\columnwidth]{figures/indexData/legend_only.png} % 图例图片路径
 
@@
 		% 放大的图例（占满单栏）
-		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}
+		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.png}
 

### 2025-10-28 VLDB2026/main.tex
change
删除注释

@@
 \documentclass[sigconf, nonacm, pdfa]{acmart}
+
 %\usepackage{fontspec}
@@
 \usepackage{enumitem}
+
 \usepackage{multirow}
@@
 \newcommand\vldbpagestyle{empty}
-\usepackage[a-2b]{pdfx}
+
+\usepackage[a-2b,mathxmp]{pdfx}
 
@@
 These efforts offer a unified reference framework for future research.
-%	\textcolor{orange}{%We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives.
-We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles.
-This work offers a unified reference framework and technical foundation for future research in this field.}
-%	We provide an overview of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives, alongside a representative retrieval library and 3 vector databases.
-This work offers a unified reference framework and technical foundation for future research in this field.}
 
 	(2) \textbf{Strengthening Datasets and Experimental Settings for Fair Evaluation.}
-%		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
-In addition to commonly used datasets, we also conduct experiments on a real-attribute dataset and a large-scale dataset (up to 100M records).
-Our benchmark design covers diverse selectivity levels and query conditions, establishing a unified and practical evaluation framework for hybrid query algorithms.}
-%	To address the lack of standardized benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets.
-We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results.
-To comprehensively reflect diverse real-world application needs, we design experiments covering varying attribute distributions, selectivity levels, and query conditions, ensuring representative and practical evaluation.
-\textcolor{cyan}{Furthermore, we test on a large-scale dataset containing 100 million records and a multi-modal dataset to analyze the scalability and performance of various algorithms.} These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
 	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
@@
 
-%		To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios.
-Furthermore, we design comprehensive experimental settings that reflect diverse application requirements, including varying attribute distributions, selectivity, and query conditions.
-These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
-
-%	(3){ Evaluation of Attribute and Range Filtering Algorithms.}
-%	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases.
-We compare the index construction and query performance of each method across different scenarios using 5 core metrics.
-We identify the reasons for performance differences based on the design of the algorithms and summarize their respective strengths and weaknesses.}
 	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
-	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
 	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 11 real-world datasets.
@@
 Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
-%	\textcolor{orange}{We conduct a comprehensive evaluation of 6 attribute filtering algorithms, 1 library, and 3 databases across 6 basic datasets, 2 real-world datasets, one 100M-scale dataset, and 2 multimodal datasets.
-By analyzing the query performance of each method under various scenarios, we reveal their respective strengths and weaknesses.
-We further examine their robustness by evaluating performance under different attribute distributions and selectivity levels.
-To ensure fairness and generality, we evaluate the methods on two different server environments.
-The evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.}
-%
 
@@
 We also further analyze the factors that affect the performance of the range filtering algorithms.
-%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments.
-The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance.
-We further analyze the factors that affect the performance of the range filtering algorithms.
-%	\textcolor{orange}{
-%		We conduct benchmark evaluations of range filtering algorithms on one synthetic and 2 real-world datasets, using various query range settings.
-Our experiments reveal and analyze the differences in time and query efficiency across these algorithms.
-Furthermore, we compare their performance on multimodal and large-scale datasets, and assess their adaptability across different server environments.
-%	}
-
-%	\textcolor{cyan}{{(4)\textbf{ Recommendations and Challenges.}
-%	Based on the experimental results, we summarize a recommendation table in Section 5.1, which intuitively shows the suitable scenarios for each algorithm, allowing readers to select appropriate algorithms according to their own needs.
-In addition, we point out the challenges and the directions for future research in the field of hybrid querying.}}
 
 	{(5)\textbf{ Recommendations and Challenges.}
-%	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios.
-Readers can select suitable algorithms according to their specific application needs.
-In addition, we identify key challenges in the field of hybrid queries.
-These challenges include the lack of consideration for the correlation between attributes and vectors, limited support for Boolean logic, insufficient capability for multi-attribute range filtering, and sensitivity of algorithms to data distribution.
-Currently, few methods support both attribute filtering and range filtering at the same time.
-This indicates potential directions for future research.
-%%}
 	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid query.
@@
 
-	%	We further classify AF-NN search according to the number of the attribute set \( s_i \): 1) Single-Attribute Filtering Nearest Neighbor (\textit{SAF-NN}) search, where $\forall i,\, |s_i| = 1$.
-2) Multi-Attribute Filtering Nearest Neighbor (\textit{MAF-NN}) search, where $\exists i,\, |s_i| > 1$.
-
 	\begin{definition}[RF-NN Search]
@@
 
-%	\subsection{Index Organization in Hybrid ANN Search}
 	\subsection{Index Organization in Hybrid Query}
@@
 	Current hybrid query methods mainly adopt graph-based ~\cite{nsw,kgraph,nsg,fanng,ngt} or Inverted File Index (IVF)-based \cite{PQ} index organization. 
-	%We briefly introduce the fundamental principles of these two types in the following.
 	Here, we briefly review the core concepts of these indexes and outline how attribute and range constraints are embedded to support hybrid queries functionality.
@@
 Furthermore, hierarchical partitioning by attributes can form finer-grained sub-clusters to enhance filtering efficiency (e.g., CAPS, Puck).}
-%	IVF-based ANN search algorithms improve computational efficiency by partitioning the dataset into clusters and restricting the search to clusters nearest to the query point.
-Specifically, as shown in Figure~\ref{fig:ivf}, IVF first selects a subset of data points and applies a clustering algorithm (e.g., K-Means) to obtain a set of centroids $(C_0, C_1, ..., C_6)$, each representing a distinct cluster.
-Every data point (gray dots) is then assigned to the cluster corresponding to its nearest centroid based on the distance metric, thereby forming the index structure.
-%	
-%	During the query process, given a query point $q$, the algorithm computes distances between $q$ and all centroids, selects a small number of the closest centroids ($C_0, C_1, C_2$), and then performs a search only within the associated clusters to identify the approximate nearest neighbors.
-%	
-%	\textcolor{violet}{IVF-based indexes also offer unique advantages in Hybrid ANN search scenarios, such as naturally supporting pre-filtering and requiring significantly lower memory consumption and smaller index sizes compared to graph-based indexes.
-With minor modifications, IVF indexes achieve attribute and range filtering by directly excluding vectors that do not meet query constraints through pre-filtering, thus skipping irrelevant vectors during intra-cluster distance computations (e.g., Faiss, Milvus).
-Moreover, clusters can be further partitioned hierarchically based on attributes (hierarchical partitioning), resulting in finer-grained sub-partitions that significantly enhance the efficiency of attribute filtering (e.g., CAPS, PUCK).}
 
@@
 		\small
-%		\label{tab:compair_1}
-%		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
-%			\hline
-%			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
-%			\hline
-%			NHQ & Graph & C & Y & N& N& N & N & N \\
-%			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
-%			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
-%			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
-%			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
-%			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
-%			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
-%			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
-%			
-%			\hline
-%			
-%		\end{tabular}
 	\label{tab:compair_1}
@@
 
-%		\begin{tabular}{|c|c|c|c|}
-%			\hline
-%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
-%			\hline
-%			DSG & Graph & Y & N \\
-%			iRange & Graph & N & Y \\
-%			SeRF & Graph & Y & Y \\
-%			UNIFY & Graph & Y & Y \\
-%			WinFilter & Graph & N & Y  \\
-%			\hline
-%		\end{tabular}
-%
-
 		\centering
@@
 				\vspace{0.1cm}
-%				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
-%				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
-%				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
-%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-%				\textit{Disk Support} indicates whether the algorithm supports disk storage.
-%				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
+
 		\textcolor{black}{
@@
 
-	%We provide an overview and analysis of 15 hybrid query methods, all drawn from recent studies, and collectively referred to as algorithms in the following.
-Specifically, Section~3.1 describes methods for attribute filtering, Section~3.2 discusses those for range filtering, and Section~3.3 introduces vector libraries and databases that support both attribute filtering and range filtering.
 	Table~\ref{tab:compair_1} provides a comparative overview of 6 attribute filtering and 5 representative range filtering algorithms.
@@
 
-%	\noindent\textbf{\underline{NHQ \cite{NHQ}.}}  
-%	\footnote{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}
 	\noindent\textbf{\underline{NHQ} \footnote{\textcolor{black}{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}} \cite{NHQ}}
@@
 	\noindent\textbf{\underline{Filtered-DiskANN} \footnote{\textcolor{black}{https://github.com/microsoft/DiskANN}} \cite{Filtered-diskann}}
-	%\sout{The effectiveness of NHQ may degrade when the number of attributes changes, as it affects the fusion distance computation. Filtered-DiskANN addresses this limitation.}
 	Filtered-DiskANN also supports simultaneous filtering.
@@
 This integration ensures that the index reflects both vector similarity and attribute constraints.
-%	Moreover, Filtered-DiskANN supports SSD-based storage, improving scalability.
 	Filtered-DiskANN proposes two indexes:  
@@
 	2) \textbf{StitchedVamana}, which adopts a batch construction strategy—constructing separate Vamana subgraphs for each attribute, followed by merging and edge pruning.
-	%	A key limitation of Filtered-DiskANN is that only supports the Boolean OR logic for multi-attribute filtering, lacking support for Boolean AND logic.
 
 	\noindent\textbf{\underline{CAPS} \footnote{\textcolor{black}{https://github.com/gaurav16gupta/constrainedANN}} \cite{CAPS}}
-	%\sout{Different from the above graph-based simultaneous filtering algorithms,}
-%	CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
 	CAPS introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
@@
 	\noindent\textbf{\underline{ACORN} \footnote{\textcolor{black}{https://github.com/stanford-futuredata/ACORN}} \cite{ACORN}}
-	%	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
-	%	%The above simultaneous filtering methods are less effective in scenarios involving large-scale, unbounded, or unknown predicate sets, where a predicate refers to a condition or rule used for filtering.
-	%	ACORN addresses this issue by introducing a predicate-agnostic indexing framework.
-	%	ACORN is built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}.
-It supports high-cardinality and unrestricted predicate sets, overcoming the limitations of methods restricted to small-scale equality filters.
-It constructs a denser hierarchical graph by expanding node neighborhoods and prunes edges at lower levels to control index size.
-During the query process, ACORN eliminates unnecessary distance computations by filtering out nodes that violate attribute constraints.
-This effectively maintains a nearest neighbor graph over valid nodes only.
-	%	%During the query process, ACORN avoids unnecessary distance computations by filtering out nodes that do not meet attribute constraints, effectively simulating a nearest neighbor graph over valid nodes only.
-	%	ACORN includes 2 indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
-	%	2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.
-	%Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. ACORN addresses this by introducing a predicate-agnostic indexing framework.
-%	ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of prior methods in large-scale or unknown predicate scenarios.
 	\textcolor{black}{ACORN adopts a predicate-agnostic indexing framework.
 It is based on Hierarchical Navigable Small World (HNSW) \cite{hnsw} and builds a denser hierarchical graph through neighborhood expansion and edge pruning.}
-%	Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning. 
 	During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.
@@
 	\noindent\textbf{\underline{UNG} \footnote{\textcolor{black}{https://github.com/YZ-Cai/Unified-Navigating-Graph}} \cite{UNG}} 
-	%\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low.
-UNG is proposed to overcome these limitations.It is a unified framework that integrates diverse graph-based ANN indexes for hybrid query.}
 	UNG serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.
@@
 Within each group, UNG builds graph-based ANN indexes (e.g., Vamana, HNSW) and connects them via cross-group edges to enable efficient cross-group search.
-	%UNG supports Boolean filtering with 2 modes:  1) The query attribute set is a subset of the data attribute set.  2) The query attribute set exactly matches the data attribute set.
 
 	\noindent\textbf{\underline{Puck} \footnote{\textcolor{black}{https://github.com/baidu/puck}} \cite{puck}} 
-	%While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints.
-In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.
-%	Puck also adopts a pre-filtering strategy. Developed by Baidu, 
 	Puck utilizes two-level quantization for indexing.
@@
 During the query process, it employs pre-filtering to exclude clusters without required attributes, thereby reducing the search space.
-	%Developed by Baidu, Puck adopts a pre-filtering approach and employs a multi-level filtering mechanism for hybrid query.
-Its index structure comprises four layers: the first two use vector quantization for training, while the latter two leverage product quantization.
-
-%	\renewcommand{\arraystretch}{0.9}
-%	\begin{table}[t]
-%		\centering
-%		
-%		\setlength{\textfloatsep}{0.1cm}
-%		\caption{Comparison of RF-ANN search algorithms}
-%		\small	% 只会影响当前组的内容
-%		\label{tab:range_algo}
-%		\begin{tabular}{|c|c|c|c|}
-%			\hline
-%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
-%			\hline
-%			DSG & Graph & Y & N \\
-%			iRange & Graph & N & Y \\
-%			SeRF & Graph & Y & Y \\
-%			UNIFY & Graph & Y & Y \\
-%			WinFilter & Graph & N & Y  \\
-%			\hline
-%		\end{tabular}
-%		
-%		
-%		\footnotesize{
-%			\begin{minipage}{\linewidth}
-%				\centering
-%				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
-%				%				\textsuperscript{Y} Support, 
-%				%				\textsuperscript{N} Unsupport.
-%				%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
-%				%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
-%				%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
-%			\end{minipage} 
-%			
-%		}
-%		
-%	\end{table}
 
@@
 
-	%For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains.
-We independently generate attribute for each dataset.
-
-	%\textcolor{violet}{For range filtering queries, we evaluate 1 widely used dataset: WIT~\cite{wit_dataset}.
-Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute.
-This ensures that the data is initially sorted.}
-
-	%\textcolor{violet}{Additionally, we introduced two datasets with real attributes for a more comprehensive evaluation of various attribute filtering and range query algorithms: The YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field into vectors, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.
-It should be noted that, during range filtering, due to the limitations of some algorithms, we uniformly sorted the vectors according to the query attribute.}
-
-	%\textcolor{violet}{To validate the algorithm generalization capability, we also further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M.
-Specifically, the Text2Image dataset comprises two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}
-
-%	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
-
-	%Table~\ref{tab:datasets_combined} summarizes the key characteristics of all datasets.
-In particular, we report the Local Intrinsic Dimensionality (LID)~\cite{Lid}, a commonly used metric to quantify dataset hardness.
-Following the standard evaluation protocol~\cite{LID2}, we randomly sample 10,000 data points from each dataset for LID computation.The higher the LID value, the harder the dataset.
-
 	\renewcommand{\arraystretch}{0.9}
@@
 
-	%\subsubsection{Parameter Settings}
-
-	%\textcolor{black}{For all algorithms, we adopt recommended settings from the original study and adjust the parameters related to search in order to obtain different Recall and QPS.}
-
 	\subsubsection{\textcolor{black}{Setting}}
@@
 \textit{\textbf{Index construction time.}}
-%\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longest build times are mainly PASE, VBASE, and ACORN-$\gamma$.
-PASE and VBASE only support single-threaded builds.
-PASE is the slowest because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency.
-VBASE uses full-memory builds and is relatively faster.
-ACORN-$\gamma$  has a high computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates.
-Its build time on some datasets even exceeds that of single-threaded VBASE.
-}
 \textcolor{black}{On the medium-scale datasets (Figure~\ref{fig:build_time_comparison_query1} left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
@@
 
-%ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.
-
-%\textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time.
-The on-demand loading and caching strategy used by PASE results in frequent disk I/O and page scheduling, which significantly slow down the construction process.
-In contrast, VBASE uses full in-memory construction, leading to faster indexing.}
-%
-%
-%For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction.
-This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.
-In contrast, ACORN-$\gamma$ incurs the highest index construction time, as it expands neighbor lists and evaluates a large candidate pool, leading to increased computational overhead.
-\textcolor{orange}{Its construction time on some datasets is even slower than that of the single-threaded VBASE.}
-%
-%On large dataset Deep100M, VBASE takes longer to build because it only supports single-threaded construction.
-The other time-consuming algorithms are all graph-based methods, which employ complex pruning strategies during construction to optimize query performance, leading to significantly increased build times.
-
 \textit{\textbf{Index size.}}
@@
 
-%As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets.
-This overhead stems primarily from its extensive metadata requirements.
-The index sizes of other methods show moderate variation.
-%\textcolor{orange}{Among these, we observe a trend that IVF-based methods tend to produce more compact indexes compared to graph-based methods.}
-
-%\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
-%\textit{\textbf{Build peak memory.}}
-% \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
-Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.}
-%
-%\textcolor{red}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
-%In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
-This leads to high peak memory usage during construction, despite the relatively small size of the final index.}
-%
-% \textcolor{orange}{\textit{\textbf{Search peak memory.}}
-%Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
-As a result, peak memory usage during querying is generally slightly lower than during construction.
-However, exceptions exist.
-As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
 \textcolor{black}{\textit{\textbf{Peak memory.}}	
@@
 During querying, CAPS maintains a large candidate set dynamically, which significantly increases its search peak memory consumption.}
-
-% \textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size.
-Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.}
-%
-%\textcolor{orange}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
-%	In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index.
-This leads to high peak memory usage during construction, despite the relatively small size of the final index.}
-%	
-% \textcolor{orange}{Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data.
-As a result, peak memory usage during querying is generally slightly lower than during construction.
-However, exceptions exist.
-As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}
 
@@
 
-%	\textcolor{violet}{\textit{Multi-Thread Search.} As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, under multi-threading, all algorithms except Puck show similar improvements, with UNG continuing to maintain the best performance.
-Puck achieves significant performance improvements in multi-threaded scenarios, delivering near-linear speedup by processing each query independently with a thread-local search context.
-This design eliminates synchronization overhead, enabling efficient parallel execution.}
-
-	%	\textit{Single-Thread Search.}  
-	%	As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under full-recall conditions (recall = 1), search often requires traversing larger candidate sets or deeper graph paths, leading to increased computational cost and a sharp QPS drop for most methods.
-Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency.
-But, UNG slightly underperforms on high-LID datasets such as GloVe.
-In contrast, CAPS performs better on high-LID datasets but is more sensitive to dataset characteristics.
-CAPS leverages multi-level spatial partitioning and attribute filtering to efficiently explore sparse spaces, whereas UNG relies on structured attribute organization, which limits its adaptability to sparse high-dimensional distributions.
-	%	
-	%	NHQ, StitchedVamana, and FilteredVamana show similar and stable performance across all datasets.
-This indicates that joint filtering and search strategies can achieve consistent effectiveness under high-recall requirements.
-As observed in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, StitchedVamana outperforms FilteredVamana in query efficiency.
-The difference arises from their pruning strategies: StitchedVamana applies pruning after merging graphs, allowing nodes to accumulate a richer candidate set; while FilteredVamana applies early pruning, potentially eliminating useful candidates prematurely.
-	%	
-	%	Among all methods, vector database systems (PASE, VBASE, Milvus) perform the worst.
-These systems target general-purpose scenarios but incur communication latency from network I/O and experience high query processing overhead due to complex query parsing.
-Additionally, we observe that Faiss+HQI\_Batch outperforms original Faiss, indicating that batch querying via HQI can effectively enhance query performance.
-	%	
-	%	\textit{Multi-Thread Search.}
-	%	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance. 
-	%	%Puck performs well on large-scale datasets, but its performance degrades on small datasets.
-Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets.
-	%	Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization.
-CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets.
-The vector distribution of the dataset affects the construction of its partitioned index.
-	%	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity.
-Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.
-
 	\textit{\textbf{Multi-Attribute Index Construction and Single-Attribute Query.}}
@@
 This makes single-attribute queries more difficult and degrades performance.}
-%	First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal.
-Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
-	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries.
-This results in excessive traversal of irrelevant nodes, making it slower than other methods.
 
@@
 
-%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios.
-To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries.
-\textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND.
-Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
-%	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
-%	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios.
-To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.
-%	
-%	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
-For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies.
-Milvus, as a general-purpose system, exhibits comparatively poor performance.
-%	
-%
-%	The IVF-based algorithm Faiss---especially when combined with HQI\_Batch---achieves moderate performance.
-It naturally supports pre-filtering and remains unaffected by the increasing number of attributes.
-In fact, filtering can reduce the effective candidate set, thereby improving search efficiency.
-In contrast, the IVF-based algorithm CAPS, which is optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead.
-This overhead negatively impacts performance on small datasets.
-However, on large datasets, the overhead is amortized, and the advantages of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
-%	
-%	NHQ performs moderately overall but poorly on small datasets.
-Its reliance on fusion distance computations makes it highly sensitive to the number of attributes, impacting both efficiency and accuracy under multi-attribute filtering.
-
-	%	In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance.
-Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes.
-In fact, filtering can reduce the effective candidate set, improving efficiency.
-	%	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets.
-For IVF-based methods that are not specifically optimized for hybrid query scenarios (Faiss\_IVF and Milvus), their QPS remains relatively stable as the recall varies.
-Milvus, being a general-purpose system, exhibits comparatively poor performance.
-In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance.
-Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes.
-In fact, filtering can reduce the effective candidate set, improving efficiency.
-
-	%	The IVF-based algorithm CAPS, optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead.
-This overhead negatively impacts performance on small datasets.
-However, on large datasets, the overhead is amortized, and the benefits of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.
-
-	%	NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets.
-It relies on fusion distance calculations.
-The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
-
 	\subsubsection{Robustness}In the following, we evaluate the robustness of these algorithms.
@@
 
-%	Among all algorithms, ACORN-\(\gamma\) shows the highest robustness.
-During index construction, attribute is mainly used for pruning in the lowest layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
-As a result, changes in attribute distribution have a limited impact on overall performance.
-%
-%	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency.
-However, its performance declines under power-law and normal distributions: power-law distributions cause excessive concentration of popular labels and fragmentation of niche labels, disrupting search path connectivity, while normal distributions produce ambiguous graph structures due to label frequency similarities, leading to search divergence.
-%	Under the power-law distribution, when the NHQ algorithm constructs an index based on fusion distance, points corresponding to high-frequency attribute values make the graph connections extremely dense, while points corresponding to low-frequency attribute values tend to become isolated due to sparse connections.
-This extreme imbalance in connectivity severely distorts the structure of the graph, ultimately significantly impairing the overall performance of the algorithm.
-%	The search performance of VBASE exhibits a direct dependence on attribute selectivity.
-As selectivity decreases, search speed declines.
-Notably, only uniform distribution maintains sufficient selectivity among the tested cases; the other three distributions consistently show low selectivity levels that significantly degrade the operational efficiency of VBASE.}
-
-%	\begin{figure}
-%	\centering
-%	\setlength{\abovecaptionskip}{0.1cm}
-%	\setlength{\belowcaptionskip}{-0.1cm}
-%	\includegraphics[width=0.95\columnwidth]{figures/exp/exp_5_1_1_SingleLabel_1thread.pdf}
-%	\caption{Effect of Single-Attribute Selectivity on Query}
-%		\label{fig:exp_5_1_1_SingleLabel_1thread}
-%	\end{figure}
-%
-
 	\textit{\textbf{Single-Attribute Selectivity.}}
@@
 	Based on the query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:
-%	
-%	Experimental results show that UNG achieves the best performance across all AS settings, especially at extremely low AS (1\%). 
-%	This advantage stems from its pre-filtering strategy.
-Pre-filtering strategy significantly reduces the ANN search space by narrowing down candidates prior to vector computation.
-In contrast, VBASE performs the worst at 1\% AS due to its post-filtering strategy.
-Post-filtering strategy first retrieves a large number of candidates and then applies filtering, incurring substantial computational overhead.
 
@@
 However, at higher AS, it requires broader global exploration.
-
-%	ACORN-1 performs well in low AS because fewer nodes share the same attribute.
-This increases the average degree of retained nodes and improves graph connectivity.
-UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
-
-%	Interestingly, Faiss and Faiss+HQI\_Batch perform worst at the 50\% AS instead of 75\%.
-%	%, which might seem unexpected. 
-%	This happens because, when AS decreases from 75\% to 50\%, fewer data points are filtered out. As a result, more clusters must be searched, increasing computational cost.
 
@@
 
-%	\begin{figure*}
-%		\centering
-%		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
-%		\caption{Effect of Different Datasets on AF-ANN Search}
-%		\label{fig:exp_6_1}
-%	\end{figure*}
-
-	%4.2.7
-
-	% \begin{table}[t]
-		% 	\centering
-		% 	\setlength{\abovecaptionskip}{0.05cm}
-		% 	\caption{Time and space overhead of range filtering index construction}
-
-		% 	\label{tab:Range Filtered}
-		% 	\resizebox{\columnwidth}{!}{
-			% 		\begin{tabular}{l l c c c c c }
-				% 			\toprule
-				% 			\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
-				% 			\midrule
-				% 			\multirow{3}{*}{DEEP} 
-				% 			& Index time(s)  & 4156 & 1128 & \textbf{189.89} & 7510 & 32843 \\
-				% 			& Index size(GB)  &  4.6 & 0.92 & \textbf{0.80} & 1.43 & 2.41  \\
-				% 			& Peak memory(GB) &  7.78 & 3.54 & \textbf{1.38} & 2.61 & 7.08   \\
-				% 			% \cmidrule{1-7}
-				% 			\midrule
-				% 			\multirow{3}{*}{YT-Audio} 
-				% 			& Index time(s)   & 15314 & 1039 & \textbf{187.20} & 5905 & 30904    \\
-				% 			& Index size(GB)    & 4.3 & \textbf{0.7} & 1.04 & 1.55 & 1.32  \\
-				% 			& Peak memory(GB)   & 7.5 & 3.16 & \textbf{1.57} & 2.97 & 6.95  \\
-				% 			\midrule
-				% 			\multirow{3}{*}{WIT} 
-				% 			& Index time(s)  & 29492 & 7068 & \textbf{828.12} & 28759 & 94909\\
-				% 			& Index size(GB) &  4.2 & \textbf{1.5 }& 15.34 & 8.71 & 1.59  \\
-				% 			& Peak memory(GB)  & 21.7 & \textbf{12.32} & 15.87 & 24.38 & 15.29\\
-				% 			% \cmidrule{1-7}
-				% 			\bottomrule
-				% 		\end{tabular}
-			% 	}
-		% \end{table}
-
-	%\textit{\textbf{Different Datasets.}}  
-	%\sout{To evaluate the performance of various methods across different datasets, we conduct experiments on 7 datasets, including one dataset Text2Image for OOD queries.
-Our analysis focuses on performance variations concerning dataset size, LID, and vector dimensionality.
-
-%ykw: 这段话看着有问题
-	%As shown in Figure~\ref{fig:exp_6_1}, all methods achieve their highest QPS and recall on Audio dataset.
-Because Audio has small scale, low dimensionality, and low LID.
-In contrast, all methods exhibit the lowest QPS and recall on the GIST1M and GloVe dataset besides the OOD dataset Text2Image.
-Because these two datasets have the largest scale and highest LID.
-
-	%SIFT1M and Msong are similar datasets, with the key difference being that SIFT1M has lower dimensionality.
-The 4 algorithms (ACORN, Faiss, PASE, and NHQ) perform similarly on these two datasets, suggesting strong robustness to high dimensional datasets.
-In contrast, the remaining algorithms exhibit degraded performance on Msong, revealing a lack of adaptability to high dimensional datasets.
-
-	%Most algorithms struggle to achieve high recall on GloVe, because it has the highest LID.
-Compare to other algorithms, the 4 algorithms (UNG, Faiss, CAPS, and Milvus) manage to maintain relatively high recall, demonstrating better adaptability to complex datasets.
-Notably, although vanilla Faiss performs worse on SIFT1M compared to Enron dataset, Faiss+HQI\_Batch outperforms on SIFT1M.
-Because batch optimization in HQI reduces query overhead and increases throughput.	}
-
-	%\textcolor{green}{Most algorithms exhibit the worst performance on the OOD dataset Text2Image.
-However, ACORN, UNG, and FilteredVamana show relatively stable performance on Text2Image.
-Their performance drops less compared to in-distribution (ID) datasets such as GIST1M and GloVe, indicating better adaptability to OOD queries.}
-
 \begin{figure*}
@@
 \end{figure*}
-
-%\begin{figure*}[t]
-%	\centering
-%	
-%	% 1. 全局图例 (Legend) - 位置保持不变
-%	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}
-%	
-%	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---
-%	
-%	% 2. 第一部分：两张图，共用标题
-%	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
-%	% 宽度从\textwidth缩小到0.32\textwidth
-%	\begin{subfigure}[b]{0.38\textwidth}
-%		\centering
-%		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
-%		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
-%		\hfill 
-%		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
-%		\caption{Multi-Modal}
-%		\label{fig:attribute-multimodal} 
-%	\end{subfigure}
-%	\hfill % 在第一部分和第二部分之间添加弹性间距
-%	% 3. 第二部分：两张图，共用标题
-%	\begin{subfigure}[b]{0.39\textwidth}
-%		\centering
-%		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
-%		\hfill
-%		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
-%		\caption{Cross-Platform}
-%		\label{fig:attribute-cross-platform}
-%	\end{subfigure}
-%	\hfill % 在第二部分和第三部分之间添加弹性间距
-%	% 4. 第三部分：只有一张图
-%	\begin{subfigure}[b]{0.203\textwidth}
-%		\centering
-%		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
-%		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
-%		\caption{Big Dataset}
-%		\label{fig:attribute big dataset}
-%	\end{subfigure}
-%	
-%	% 5. 全局总标题
-%	\caption{\textcolor{violet}Scalability Study (Attribute Filtering)}
-%	\label{fig:TrinityExtension——Attribution_main}
-%\end{figure*}
 
@@
 To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance.
-		%	We conduct experiments on the text2image-mix dataset.
-This dataset contains both image and text vectors.
-It is a more complex multimodal dataset.
-As shown in Figure~\ref{fig:attribute-multimodal}, although the queries are more complex, UNG and NHQ still perform the best.
-CAPS is the next best.
-		%	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality.
-The nearest neighbors in the index are often from the same modality because they are closer in distance.
-Therefore, the search results on this dataset are similar to those in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
-UNG and NHQ perform the best.
-CAPS clusters based on vector similarity.
-It actually clusters the vectors into the same modality.
-Then it uses attribute filtering to divide the data further.
-This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
-		%	In contrast, the text2image dataset shown in Figure~\ref{fig:exp_6_1} is different.
-The queries and the dataset are from different modalities.
-The queries are far from the dataset.
-The ground truths are also scattered and not clustered together.
-To find the ground truths, the algorithm often needs to traverse more points.
-This is a greater challenge for the algorithms.
-		%	We conducted extensive scalability experiments on the Text2Image-Mix dataset.
-This dataset contains both image and text vectors.
-It represents a more complex multimodal query scenario.
-As shown in Figure 12, the UNG and NHQ algorithms still achieve the best performance, followed closely by CAPS.
-		%	In the Text2Image-Mix dataset, the ground truth of the query vector is usually the corresponding vector in the same modality.
-Since the neighbor relationships in the graph are often based on vector distance, vectors of similar modalities naturally form closer connections in the graph.
-Therefore, during the search process, the algorithm tends to traverse efficiently within the same modality.
-This makes the search mechanism similar to our experiments on single-modality datasets, thus maintaining high performance.
-		%	The good performance of the CAPS algorithm is due to its unique hierarchical space partitioning strategy.
-It first clusters vectors based on similarity.
-In multimodal data, this clustering naturally groups vectors of similar modalities into the same cluster.
-Then, CAPS further partitions these clusters using attributes.
-This allows it to quickly find the nearest neighbors that meet the filtering conditions.
-		%	It is worth noting that, compared to the OOD dataset discussed in the "Dataset Impact" section, the Text2Image-Mix dataset also involves modality differences.
-However, its complexity lies in modality mixing.
-The OOD dataset, on the other hand, has a modality gap.
-This often requires traversing a broader and more sparse search space to find the ground truth.
-It poses a more severe challenge to the algorithm.
 	}
@@
 Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values.}
-
-%		we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level.
-This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}
-
-%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}
-
-% 使用 figure* 环境来实现图片横跨双栏
-% 使用 figure* 环境来实现图片横跨双栏
 
@@
 	\textit{\textbf{Index construction time.}}
-%	As shown in the Figure~\ref{fig:rangeFilter_build_time}, for regular-scale datasets, Faiss builds the index fastest.
-As Faiss obtains subsamples through sampling and calculates the cluster centroid, the computational complexity is significantly reduced.
-%
-%	WinFilter and ACORN-\(\gamma\) take the longest.
-%	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
-%	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs.
-It also prunes distant neighbors to save storage space.
-However, this introduces additional overhead and slows down the construction process.
-%	
-%	\textcolor{orange}{On large-scale datasets, ACORN-1 achieves the fastest index construction, primarily due to its similarity to the original HNSW construction process and its use of fewer candidate neighbors in the upper layers.
-SeRF, another HNSW-based method, also exhibits very short construction time by losslessly compressing multiple HNSW graphs into a unified structure and accelerating the process through dynamic pruning and skip-connection optimizations.
-%	As two methods both based on IVF\_Flat, Milvus and Faiss achieve short indexing times.
-Milvus is even faster, mainly due to its cache-aware optimization, which significantly reduces CPU cache misses.}
-%	\textcolor{orange}{
-%	DSG only supports single-threaded construction, resulting in the longest build time.}
+
 	\textcolor{black}{
@@
 Milvus performs particularly well on large-scale datasets, mainly due to its cache-aware optimizations, which significantly reduce CPU cache misses.}
-%	As shown in Figure~\ref{fig:rangeFilter_build_time}, Faiss, based on the IVF\_Flat architecture, achieves fast index construction through subset sampling and centroid computation, which lowers the computational cost.
-%	As another IVF\_Flat-based method, Milvus performs even better on large-scale datasets, mainly due to its cache-aware optimization that greatly reduces CPU cache misses.}
 
@@
 	}
-%		\textcolor{orange}{
-%	ACORN-1 also achieves highly efficient index construction, especially on large-scale datasets.
-This efficiency stems from its construction process, which closely resembles that of the original HNSW, and from reducing the number of candidate neighbors in the upper layers, thereby lowering computational cost.
-SeRF, another HNSW-based method, also exhibits very short construction time.
-During construction, it attaches timestamp information to edges, keeping the total time comparable to building a single HNSW graph, which enables efficient construction even on large datasets.}
 
@@
 DSG, on the other hand, incorporates a rectangle tree structure for index management, making the construction process more complex and costly.
-%	Additionally, DSG builds index using a single thread on the Deep100M dataset, resulting in the longest construction time. 
 WinFilter also incurs high construction cost, as it relies on a tree structure and builds a separate nearest neighbor graph for each node, which leads to redundant computations.
 However, on large-scale datasets, its preprocessing stage is replaced by the base algorithm Vamana-WST, effectively avoiding significant time overhead.}
-%		\textcolor{orange}{
-%	In contrast, WinFilter relies on a tree-based structure, where a separate nearest neighbor graph must be built for each node.
-This design introduces redundant computation and high construction cost.
-However, on large-scale datasets, the preprocessing phase of WinFilter is replaced in the experiments by the base algorithm Vamana-WST, thus avoiding significant time overhead.}
-%	
-%		\textcolor{orange}{
-%	ACORN-\(\gamma\)  extends the neighbor list of each node to provide more candidate paths, which increases both computational and memory overhead.
-Although it prunes distant neighbors to save storage, the additional construction logic still incurs substantial time cost.}
-
-%		\textcolor{orange}{
-%	DSG is an optimization over SeRF, incorporating a rectangular tree structure for index management.
-This makes the construction process more complex and costly.
-In addition, on Deep100M, DSG uses single-threaded construction, resulting in the longest build time.}
 
@@
 While this design improves retrieval accuracy, it significantly increases the index size on massive datasets.}
-%	\textcolor{orange}{DSG is an improvement over SeRF.
-Compared to SeRF, DSG stores additional information for each edge in its index structure, resulting in a significant increase in index size on large-scale datasets.
-%	}
-
-	%SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.
 
@@
 Similarly, during search, WinFilter needs to load multiple local indices in parallel for different tree nodes, further contributing to high peak memory consumption.}
-
-%		\textit{\textbf{Search peak memory.}}  
-%		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, the peak memory usage during search generally follows a similar trend to that observed during index construction.
-This observation is consistent with our earlier analysis in the attribute filtering section.}
 
@@
 \textcolor{black}{Specifically, for a given query, the range ratio is defined as $2^{-i}$	when the query range covers $\frac{n}{2^i}$ data points, where $n$ is the total dataset size.}
-	% Based on this definition, we evaluate algorithm performance under 4 query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
-\textcolor{black}{Due to the limitations of existing range filtering algorithms, the range filtering experiment only uses one attribute, and the dataset is sorted in ascending order according to the attribute value size.
-WIT-Real and YT-Audio-Real use real attribute values, and the rest use randomly generated attribute values.}
-	%\textcolor{red}{Some algorithms don't support using actual attributes as search keys, instead requiring an ID (the primary key, ranging from $0$ to $n-1$).
-Therefore, we uniformly use this ID as the search key.
-This ID is pre-sorted according to its corresponding real attribute, allowing us to map an attribute to its ID without loss of generality for efficient range queries.}
+
 	Based on this definition, we evaluate algorithm performance under four query range settings: $2^{-2}$, $2^{-4}$, $2^{-6}$, and $2^{-8}$.
@@
 %	The experimental results show consistent performance across all datasets and query ranges.
-
-	%Due to space constraints, Figure~\ref{fig:exp_8_2} reports results for only the largest ($2^{-2}$) and smallest ($2^{-8}$) range ratios.
-The experimental results show that across all datasets (YT-Audio-Real, WIT-Real, and Deep1M) and query ranges.
 
@@
 
-%	\sout{It is important to note that this range query experiment is conducted under a fully static setting.
-Under such conditions, UNIFY, iRange, SeRF, and WinFilter require the dataset to be sorted by attribute prior to index construction.
-In contrast, DSG  supports dynamic index construction with unordered attribute insertions, making it more suitable for streaming or incremental data scenarios.
-This flexibility highlights its superior extensibility in real-world applications.}
-
-	%\subsubsection{Robustness.}
-
-	%\begin{figure*}[htbp]
-	%	\centering
-	%	\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
-	%	\caption{Effect of Different Datasets on RF-ANN Search}
-	%	\label{fig:exp_8_3}
-	%\end{figure*}
-
-%	\textcolor{green}{To evaluate the robustness of the RF-ANNS algorithms in different scenarios, we add an OOD dataset in the experiments.
-As shown in Figure~\ref{fig:exp_8_3}, most methods perform worst on the Text2Image dataset.
-This is because OOD queries make the $k$-nearest neighbor distribution more sparse.
-As a result, the search needs to visit more nodes, which leads to an exponential growth in the search space and a sharp drop in efficiency.}
-
-%	\sout{WinFilter shows the worst performance on the WIT dataset.
-This suggests that its performance is sensitive to the data dimensionality.
-ACORN has large performance differences across datasets, indicating weak robustness.
-
-%	Among vector databases, Milvus performs well.
-VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image.
-PASE is excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
-
-%	It is worth noting that most methods achieve similar performance on the Deep and YT-Audio datasets, which have similar LID values.
-This shows that RF-ANNS performance is largely affected by both the LID and the dimensionality of the dataset.
-A high LID and high dimensionality make hybrid queries more difficult.
-
-%	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them.
-This means that DSG is more sensitive to changes in data distribution.
-}
-	%	Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.
-	%	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets.
-As shown in Figure~\ref{fig:exp_8_3}, the performance differences.
-All methods perform worst on WIT, which has the highest LID.
-On Deep and YT-Audio, which have similar LID, most algorithms achieve comparable performance.
-	%	This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
-	%	
-	%	However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID.
-This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.
-
 \begin{figure*}
@@
 This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets.
-%		Similar to attribute filtering,on Text2Image-Mix dataset,the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}.
-These algorithms on the Text2Image dataset exhibit a significant performance degradation.
-This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets.
-%		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}.
-As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image.
-This is because these range query algorithms are almost graph-based.
-Graph algorithms need more iterations to find true neighbors in OOD datasets.
 		}
@@
 Therefore, different server configurations only affect the performance of individual algorithms, with minimal impact on their relative performance ranking.}
-%		So our findings remain consistent with those reported in Section 4.2.3. For brevity and due to space limitations, we omit further discussion of these redundant results.}
-%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}.
-Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4.
-Due to space constraints, these details are not reiterated here.}
 
@@
 	\subsubsection{Attribute Filtering}
-%	We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}.
-Puck and UNG excel on large-scale datasets (S1).
-ACORN-1 and UNG achieve fast index construction (S2).
-UNG performs well on different datasets (S3, S4).
-In addition, CAPS performs well on hard datasets with high LID (S3), while NHQ and StitchedVamana perform better on easy datasets with low LID (S4).
-%	Faiss and CAPS can generate relatively compact indexes with low memory usage, which is suitable for resource-constrained situations (S6).
-Milvus and Faiss serve as general-purpose solutions (S5).
-UNG stands out for its higher recall, precision, and QPS, and performs well in the OOD scenario (S7, S8).
+
 \textcolor{black}{
@@
 Puck is well-suited for large-scale datasets such as those with 100 million points. It offers fast index construction and low memory consumption in such scenarios. 
-%Moreover, it delivers high search performance in multi-threaded environments, making it an excellent choice for deployment on extremely large datasets.
 }
@@
 It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution.}
-%	Table~\ref{tab:algo_scenarios} also shows the application scenarios of range filtering.
-iRange performs well on large-scale datasets, combining efficient construction and excellent query capabilities (S1).
-Faiss performs well in fast index construction (S2).
-When processing hard datasets, WinFilter, iRange, and DSG are recommended (S3), while WinFilter and iRange also perform well on easy datasets (S4).
-For general applications, DSG supports dynamic updates, while UNIFY provides flexible filtering strategies (S5).
-Faiss and SeRF show superior memory efficiency (S6).
-For static queries with high recall, WinFilter is the best choice (S7).
-In addition, WinFilter also performs well in OOD scenarios (S8).
 
@@
 	\textcolor{black}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. }
-%	For example, NHQ organizes attributes by column, which is suitable for uniformly structured data, but performs poorly in scenarios where the number of attributes varies across data points, resulting in poor scalability.
-Furthermore, NHQ only supports multi-attribute filtering with conjunctions ("AND" conditions).
-UNG is relatively more flexible in this regard, as it supports both "AND" and "OR" logic; however, it still cannot handle more complex Boolean expressions involving combinations of conjunctions and disjunctions.
-%	In contrast, FilterDiskANN imposes no restrictions on the number of attributes per data point, offering better scalability.
-However, it currently supports only single-attribute filtering and disjunctions ("OR" conditions) across multiple attributes.
-Enhancing its capability to support more flexible Boolean combinations would effectively overcome the limitations of current approaches and significantly improve its practicality for diverse and complex query requirements.
-%		}
+
 		\textcolor{black}{
@@
 
-%	Furthermore, current attribute filtering algorithms offer limited support for complex filtering conditions.
-For example, Filtered-DiskANN  supports single-attribute filtering, and in multi-attribute scenarios, it only supports OR conditions between attributes.
-%	%The original implementations of 
-%	NHQ imposes strict constraints on the number of base and query attributes and only support AND conditions.
-While UNG is relatively flexible—supporting both AND and OR logic—it still lacks support for arbitrary Boolean expressions (e.g., combinations of AND and OR).
-The lack of flexible Boolean filtering remains a key challenge, limiting the practicality of hybrid query methods in real-world systems with diverse and complex query requirements.
-
 	\subsubsection{Range Filtering}
@@
 Exploring how to improve these algorithms to better adapt to more complex query conditions is a worthwhile direction for further research.}
-
-%	our findings show that the distribution and the number of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods.
-Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.
-%
 
@@
 \textcolor{black}{Additionally, exploring algorithms that support a combined and efficient use of attribute and range filtering is also an important research topic.}
-%	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries.
-We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm.
-Experiments show that these algorithms still have shortcomings in scenarios such as large-scale data, complex queries, and resource constraints.
-There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms.
-Additionally, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries.
-Notably, some algorithms even perform worse than the baseline method (e.g., Faiss) in high recall scenarios.
-In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
-Furthermore, in many real-time scenarios, both attribute and range filtering are required simultaneously, and therefore, exploring algorithms that support a combination of both is also an important research topic.
-%	In the future, it is essential to further explore the flexibility and robustness of attribute filtering algorithms, and improving the performance of range filtering algorithms remains an important direction.
-%	\textcolor{black}{
-%		In this paper, we evaluate hybrid query methods, including algorithms, vector databases, and libraries.
-We design experiments to assess the performance of attribute filtering algorithms.
-We enrich existing datasets with attribute values and create various experimental scenarios to ensure fair comparisons.
-We run experiments on 7 real-world datasets to analyze the effectiveness of attribute filtering algorithms.
-We also compare range filtering algorithms using 4 range query datasets.
-Finally, we analyze the results, summarize key findings, and identify areas for improvement.
-Our study validates previous research and provides insights for future work.
-%	}
-%
 

### 2025-10-29 VLDB2026/main.tex
change bib
ok

@@
 \usepackage{array}
+\usepackage[all]{nowidow}
 
@@
 	\affiliation{%
-		\institution{Huazhong University of Science and Technology}
+		\institution{Wuhan University of Technology}
 	}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.2cm}
-		\setlength{\belowcaptionskip}{-0.1cm}
+		\setlength{\abovecaptionskip}{0.15cm}
+		\setlength{\belowcaptionskip}{-0.10cm}
 
@@
 
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.3cm}		
+	\setlength{\abovecaptionskip}{0.15cm}
+	\setlength{\belowcaptionskip}{-0.10cm}
 		\caption{Graph Index and IVF Index}
@@
 			\begin{minipage}{\linewidth}
-				\vspace{0.1cm}
 
@@
 
-	\noindent\textbf{\underline{NHQ} \footnote{\textcolor{black}{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}} \cite{NHQ}}
+	\noindent\textbf{\underline{NHQ} \footnote{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS} \cite{NHQ}}
 	Traditional attribute filtering algorithms usually perform attribute constraints and ANN search separately.
@@
 
-\noindent\textbf{\underline{Faiss}\footnote{\textcolor{black}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
+\noindent\textbf{\underline{Faiss}\footnote{\url{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
 Faiss is an efficient similarity search library. It supports hybrid search by using an ID selector to filter data before performing ANN search.
@@
 
-\noindent\textbf{\underline{PASE} \footnote{\textcolor{black}{https://github.com/alipay/PASE}} \cite{pase}} PASE is a vector index plugin for PostgreSQL.
+\noindent\textbf{\underline{PASE}\footnote{\url{https://github.com/alipay/PASE}} \cite{pase}}  PASE is a vector index plugin for PostgreSQL.
 It uses a post-filtering strategy.
@@
 
-\noindent\textbf{\underline{VBASE} \footnote{\textcolor{black}{https://github.com/microsoft/MSVBASE}} \cite{vbase}} VBASE is also a vector plugin for PostgreSQL.
+\noindent\textbf{\underline{VBASE} \footnote{\url{https://github.com/microsoft/MSVBASE}} \cite{vbase}} VBASE is also a vector plugin for PostgreSQL.
 Unlike PASE, it applies filters during the HNSW index traversal, discarding unmatched nodes on the fly.
@@
 
-\noindent\textbf{\underline{Milvus} \footnote{\textcolor{black}{https://github.com/milvus-io/milvus}} \cite{milvus}} Milvus is a vector database designed for large-scale similarity search.
+\noindent\textbf{\underline{Milvus} \footnote{\url{https://github.com/milvus-io/milvus}} \cite{milvus}} Milvus is a vector database designed for large-scale similarity search.
 In hybrid queries, it adopts a pre-filtering strategy, similar to the ID selector mechanism used in Faiss.
 %It filters data first, then performs approximate nearest neighbor search. This supports hybrid search.
-
-%	The vector libraries and databases discussed in the following are not explicitly designed for hybrid queries, but they support both attribute filtering and range filtering.
-Additionally, all the functionalities shown in Table 1 are also supported.
-%	
-%	\noindent\textbf{\underline{Faiss} \footnote{\textcolor{black}{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
-%	Faiss is a library designed for efficient similarity search.
-It supports various indexing structures, including IVF, Product Quantization (PQ) \cite{PQ}, and HNSW.
-In hybrid query scenarios, Faiss supports vector search with an ID selector, which is a bitmap aligned with the dataset size.
-Users can generate this selector by first applying custom attribute filtering methods.
-During the query process, Faiss excludes vectors based on the selector, enabling efficient integration of attribute filtering with ANN search.
-In addition, we adopt the batch optimization strategy of HQI~\cite{HQI} for the IVF index in Faiss.
-This strategy groups queries with the same filter conditions, performs filtering once per group, and then uses efficient matrix operations to perform batch vector similarity calculations.
-%	
-%	
-%	\noindent\textbf{\underline{PASE} \footnote{\textcolor{black}{https://github.com/alipay/PASE}} \cite{pase}}
-%	PASE is a vector indexing plugin for the PostgreSQL database \cite{postgresql13.4}, supporting two index types: IVF\_Flat \cite{johnson2019billion} and HNSW.
-By leveraging database capabilities, PASE enables both attribute filtering and range filtering.
-We focus on the post-filtering strategy based on HNSW, which facilitate comparison with other methods.
-When a query request is received, PASE first obtains a candidate set using the HNSW index.
-It then applies the filtering conditions from the WHERE clause to refine the results.
-However, since the candidate set has a fixed size, low-selectivity filters may result in fewer than $k$ results being returned.
-%	
-%	
-%	\noindent\textbf{\underline{VBASE} \footnote{\textcolor{black}{https://github.com/microsoft/MSVBASE}} \cite{vbase}}
-%	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}.
-We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality.
-VBASE adopts a post-filtering strategy.
-However, it employs an iterative filtering mechanism: during index traversal, each node is checked against the WHERE clause, and non-matching nodes are discarded.
-This avoids the issue in PASE where the final result set may contain fewer than $k$ results.
-%	
-%	\noindent\textbf{\underline{Milvus} \footnote{\textcolor{black}{https://github.com/milvus-io/milvus}} \cite{milvus}}
-%	Unlike PASE and VBASE, which are database extensions, Milvus is an vector database purpose-built for large-scale similarity search.
-It supports multiple index types, including HNSW, IVF\_Flat, and IVF\_PQ, and provides extensive optimization for real-world deployment.
-Among its indexes, IVF\_Flat is commonly used due to its balance between performance and simplicity.
-In hybrid queries, Milvus first pre-filters the dataset using user-specified conditions, then traverses only the corresponding clusters for ANN search—similar to the ID selector mechanism of Faiss.
 
@@
 		%		\caption{Time and space overhead of attribute filtering index construction}
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.3cm}
+		\setlength{\abovecaptionskip}{0.15cm}
+		\setlength{\belowcaptionskip}{-0.10cm}
 		\caption{\textcolor{black}{Time and Space Overhead (AF)}}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.2cm}
+		\setlength{\abovecaptionskip}{0.15cm}
+		\setlength{\belowcaptionskip}{-0.10cm}
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.3cm}
+		\setlength{\abovecaptionskip}{0.15cm}
+		\setlength{\belowcaptionskip}{-0.10cm}
 		% 上面的图例，居中并可通过 hspace 调整左右位置
@@
 		\centering
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.25cm}
+		\setlength{\abovecaptionskip}{0.15cm}
+		\setlength{\belowcaptionskip}{-0.10cm}
 		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
@@
 
-		\setlength{\abovecaptionskip}{0.1cm}
-		\setlength{\belowcaptionskip}{-0.15cm}
+		\setlength{\abovecaptionskip}{0.15cm}
+		\setlength{\belowcaptionskip}{-0.10cm}
 
@@
 	\centering
-	\setlength{\abovecaptionskip}{0.0cm}
+%	\setlength{\abovecaptionskip}{0.0cm}
 	\begin{minipage}[t]{0.37\textwidth}
@@
 	\begin{minipage}{\linewidth}
-		\vspace{0.1cm}
+
 		\textit{Performance Levels:} \textbf{B} = Best, G = Good , M = Moderate, P = Poor, - = Not Supported;

### 2025-10-29 VLDB2026/copyFigures.sh

@@ -1,59 +1,0 @@
-#!/bin/bash
-# 检查并复制 PDF 文件到 figures2 目录，保持路径结构
-
-# 目标根目录
-TARGET_DIR="figures2"
-
-# 文件列表（可复制你贴的完整清单）
-FILES=(
-"hybridANNS.pdf"
-"figures/exp/attribute_100M.pdf"
-"figures/exp/attribute_71.pdf"
-"figures/exp/attribute_85.pdf"
-"figures/exp/attribute_legend.pdf"
-"figures/exp/attribute_multimodel_1.pdf"
-"figures/exp/attribute_multimodel.pdf"
-"figures/exp/exp_1_1_SingleLabel_1thread.pdf"
-"figures/exp/exp_2_1.pdf"
-"figures/exp/exp_2_legend.pdf"
-"figures/exp/exp_3_1.pdf"
-"figures/exp/exp_4_1_MultiLabel_1thread.pdf"
-"figures/exp/exp_5_2_1.pdf"
-"figures/exp/exp_5_2_2.pdf"
-"figures/exp/exp_5_2_3.pdf"
-"figures/exp/exp_8_2.pdf"
-"figures/exp/range_71.pdf"
-"figures/exp/range_85.pdf"
-"figures/exp/range_deep100M.pdf"
-"figures/exp/range_legend.pdf"
-"figures/exp/range_multimodel_1.pdf"
-"figures/exp/range_multimodel.pdf"
-"figures/graph.pdf"
-"figures/indexData/exp_7_build_time_comparison_query1.pdf"
-"figures/indexData/exp_7_index_size_mb_comparison_query1.pdf"
-"figures/indexData/exp_7_memory_mb_comparison_query1.pdf"
-"figures/indexData/legend_only.pdf"
-"figures/indexData/rangeFilter_build_time_comparison_query.pdf"
-"figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf"
-"figures/indexData/rangeFilter_legend_only.pdf"
-"figures/indexData/rangeFilter_memory_mb_comparison_query.pdf"
-"figures/ivf.pdf"
-"figures/searchMem/label_memory_comparison.pdf"
-"figures/searchMem/range_memory_comparison.pdf"
-)
-
-echo "检查并复制 PDF 文件到 $TARGET_DIR ..."
-
-for file in "${FILES[@]}"; do
-    if [[ -f "$file" ]]; then
-        # 生成目标路径
[…]

### 2025-10-29 VLDB2026/main.tex
ok

@@
 
-%\usepackage{fontspec}
 \usepackage{balance}
@@
 \usepackage{multirow}
-% \usepackage{svg} % For SVG support
+
 \usepackage{graphicx}
-\usepackage{ulem}  % 导言区加上这一行
+
 \usepackage{microtype}  %处理换行
@@
 \usepackage{caption}
-\usepackage{fontawesome}
-\usepackage{makecell}
+
 \usepackage{array}
-\usepackage[all]{nowidow}
-
-% \newtheorem{definition}{DEFINITION} % 定义“定义”环境
-% % \newtheorem{example}{例} % 定义“例”环境，不与“定义”共享编号
+%\usepackage[all]{nowidow}
+\usepackage{times}
+
 % %% The following content must be adapted for the final version
@@
 
-	Nearest Neighbor (NN) search \cite{cover1967nearest} aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems  \cite{monolith}  and image retrieval \cite{wang2012scalable}.
+	Nearest Neighbor (NN) search \cite{cover1967nearest} aims to find the closest vector in a given space and serves as a fundamental algorithm in vector retrieval, with widespread applications in recommendation systems   and image retrieval \cite{wang2012scalable}.
 	However, with the exponential growth of data volume and the increasing dimensionality of vectors \cite{weber1998quantitative}, traditional NN search methods struggle to meet the demands of real-time search.
@@
 
-Although existing studies~\cite{compare,azizi2025graph} conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking.
+Although existing studies~\cite{compare,compare2} conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking.
 Despite BigANN 2023~\cite{bigann2023} evaluates the performance of some hybrid query algorithms, it still presents the following notable limitations:
@@
 
-	\noindent\textbf{\underline{NHQ} \footnote{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS} \cite{NHQ}}
+	\noindent\textbf{\underline{NHQ} \footnote{https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS}}  \cite{NHQ}
 	Traditional attribute filtering algorithms usually perform attribute constraints and ANN search separately.
@@
 
-	\noindent\textbf{\underline{Filtered-DiskANN} \footnote{\textcolor{black}{https://github.com/microsoft/DiskANN}} \cite{Filtered-diskann}}
+	\noindent\textbf{\underline{Filtered-DiskANN} \footnote{\textcolor{black}{https://github.com/microsoft/DiskANN}}} \cite{Filtered-diskann}
 	Filtered-DiskANN also supports simultaneous filtering.
@@
 
-	\noindent\textbf{\underline{CAPS} \footnote{\textcolor{black}{https://github.com/gaurav16gupta/constrainedANN}} \cite{CAPS}}
+	\noindent\textbf{\underline{CAPS} \footnote{\textcolor{black}{https://github.com/gaurav16gupta/constrainedANN}}}\cite{CAPS}
 	CAPS introduces a hierarchical sub-partitioning algorithm inspired by Huffman trees, termed the Attribute Frequency Tree (AFT), to overcome the coarse granularity of traditional IVF-based methods.
@@
 
-	\noindent\textbf{\underline{ACORN} \footnote{\textcolor{black}{https://github.com/stanford-futuredata/ACORN}} \cite{ACORN}}
+	\noindent\textbf{\underline{ACORN} \footnote{\textcolor{black}{https://github.com/stanford-futuredata/ACORN}}}
+	\cite{ACORN}
 	\textcolor{black}{ACORN adopts a predicate-agnostic indexing framework.
@@
 
-	\noindent\textbf{\underline{UNG} \footnote{\textcolor{black}{https://github.com/YZ-Cai/Unified-Navigating-Graph}} \cite{UNG}} 
+	\noindent\textbf{\underline{UNG} \footnote{\textcolor{black}{https://github.com/YZ-Cai/Unified-Navigating-Graph}}} \cite{UNG}
 	UNG serves as a unified framework that integrates various graph-based ANN indexes to support hybrid queries.
@@
 
-	\noindent\textbf{\underline{Puck} \footnote{\textcolor{black}{https://github.com/baidu/puck}} \cite{puck}} 
+	\noindent\textbf{\underline{Puck} \footnote{\textcolor{black}{https://github.com/baidu/puck}}} \cite{puck}
 	Puck utilizes two-level quantization for indexing.
@@
 
-	\noindent\textbf{\underline{SeRF} \footnote{\textcolor{black}{https://github.com/rutgers-db/SeRF}} \cite{serf}} 
+	\noindent\textbf{\underline{SeRF} \footnote{\textcolor{black}{https://github.com/rutgers-db/SeRF}}} \cite{serf} 
 %	Conventional RF-ANN search approaches typically follow one of two paradigms: 1) Conducting ANN search first followed by attribute-based filtering.
@@
 
-	\noindent\textbf{\underline{WinFilter} \footnote{\textcolor{black}{https://github.com/JoshEngels/RangeFilteredANN}} \cite{winFilter}}
+	\noindent\textbf{\underline{WinFilter} \footnote{\textcolor{black}{https://github.com/JoshEngels/RangeFilteredANN}}} \cite{winFilter}
 %	Unlike SeRF, which focuses on graph compression, 
@@
 
-	\noindent\textbf{\underline{iRange} \footnote{\textcolor{black}{https://github.com/YuexuanXu7/iRangeGraph}} \cite{iRangeGraph}}
+	\noindent\textbf{\underline{iRange} \footnote{\textcolor{black}{https://github.com/YuexuanXu7/iRangeGraph}}} \cite{iRangeGraph}
 %	To address the query efficiency degradation caused by the graph compression in SeRF, iRange adopts a more flexible strategy.
@@
 
-	\noindent\textbf{\underline{DSG} \footnote{\textcolor{black}{https://github.com/rutgers-db/DynamicSegmentGraph}} \cite{DSG}}
+	\noindent\textbf{\underline{DSG} \footnote{\textcolor{black}{https://github.com/rutgers-db/DynamicSegmentGraph}}}  \cite{DSG}
 %	Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets. SeRF allows incremental insertion but requires ordered attributes. 
@@
 
-	\noindent\textbf{\underline{UNIFY} \footnote{\textcolor{black}{https://github.com/sjtu-dbgroup/UNIFY}} \cite{UNIFY}}
+	\noindent\textbf{\underline{UNIFY} \footnote{\textcolor{black}{https://github.com/sjtu-dbgroup/UNIFY}}} \cite{UNIFY}
 %	Unlike DSG, which relies on rectangle trees and range-aware edges, UNIFY adopts a segmentation-based approach and proposes a range query index structure. 
@@
 
-\noindent\textbf{\underline{Faiss}\footnote{\url{https://github.com/facebookresearch/faiss}} \cite{Faiss}}
+\noindent\textbf{\underline{Faiss}\footnote{\url{https://github.com/facebookresearch/faiss}}}  \cite{Faiss}
 Faiss is an efficient similarity search library. It supports hybrid search by using an ID selector to filter data before performing ANN search.
@@
 
-\noindent\textbf{\underline{PASE}\footnote{\url{https://github.com/alipay/PASE}} \cite{pase}}  PASE is a vector index plugin for PostgreSQL.
+\noindent\textbf{\underline{PASE}\footnote{\url{https://github.com/alipay/PASE}}} \cite{pase}  PASE is a vector index plugin for PostgreSQL.
 It uses a post-filtering strategy.
@@
 
-\noindent\textbf{\underline{VBASE} \footnote{\url{https://github.com/microsoft/MSVBASE}} \cite{vbase}} VBASE is also a vector plugin for PostgreSQL.
+\noindent\textbf{\underline{VBASE} \footnote{\url{https://github.com/microsoft/MSVBASE}}} \cite{vbase} VBASE is also a vector plugin for PostgreSQL.
 Unlike PASE, it applies filters during the HNSW index traversal, discarding unmatched nodes on the fly.
@@
 
-\noindent\textbf{\underline{Milvus} \footnote{\url{https://github.com/milvus-io/milvus}} \cite{milvus}} Milvus is a vector database designed for large-scale similarity search.
+\noindent\textbf{\underline{Milvus} \footnote{\url{https://github.com/milvus-io/milvus}}}  \cite{milvus} Milvus is a vector database designed for large-scale similarity search.
 In hybrid queries, it adopts a pre-filtering strategy, similar to the ID selector mechanism used in Faiss.
@@
 
-	\textcolor{black}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloV-\\e~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
+	\textcolor{black}{Our experiments employ 12 real-world datasets: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M\\~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
 
@@
 Unless otherwise specified, all experiments were conducted on Server A.}
-	Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}. The queries are all executed on a single thread. 
+	Unless otherwise stated, we execute index construction with 32 threads to accelerate the process. The queries are all executed on a single thread. 
 %	In addition, We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}.
@@
 
-textcolor{black}{
 	Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design.
@@
 For ACORN--\(\gamma\), during index construction, attributes are primarily used for pruning in the lowest-layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected.
-Consequently, changes in attribute distribution have minimal impact on overall performance.}
+Consequently, changes in attribute distribution have minimal impact on overall performance.
 
@@
 	\textit{\textbf{Index construction time.}}
-
 	\textcolor{black}{

### 2025-10-30 VLDB2026/main.tex
ok

@@
 \usepackage{array}
-%\usepackage[all]{nowidow}
+\usepackage[all]{nowidow}
 \usepackage{times}
@@
 		\setlength{\abovecaptionskip}{-0.2cm}
-		\setlength{\belowcaptionskip}{-0.3cm}
+%		\setlength{\belowcaptionskip}{-0.15cm}
 		\caption{Multi-Modal Datasets (RF)}
@@
 		\setlength{\abovecaptionskip}{-0.2cm}
-		\setlength{\belowcaptionskip}{-0.3cm}
+%		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{Large-Scale Dataset (RF)}
@@
 		\setlength{\abovecaptionskip}{-0.2cm}
-		\setlength{\belowcaptionskip}{-0.3cm}
+%		\setlength{\belowcaptionskip}{-0.3cm}
 		\caption{Different Platforms (RF)}
@@
 
-	\textcolor{black}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. }
-
-		\textcolor{black}{
+In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. 
 For example, in multi-attribute scenarios, some algorithms only support Boolean OR logic (e.g., FilterDiskANN), while others only support Boolean AND logic (e.g., NHQ and CAPS).
@@
 In contrast, while databases and the vector search library Faiss support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
-Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed. }
+Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed.
 

### 2025-11-04 VLDB2026/main.tex
ok

@@
 	%\begin{sloppypar}
-	\title{An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)}
+	\title{An Experimental Evaluation of Hybrid Querying on Vectors}
 
@@
 	}
-
+	\authornote{Yan Li is the corresponding author}
 	\author{Bolong Zheng}
@@
 	}
+	\authornote{Bolong Zheng is the corresponding author}
 	%%
@@
 	\section{CONCLUSION}
-	In this paper, we systematically evaluate various hybrid query methods, including multiple algorithms, vector databases, and libraries.
+%In this paper, we systematically evaluate various hybrid query methods, including multiple algorithms, vector databases, and libraries.
 We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm.
@@
 In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
-\textcolor{black}{Additionally, exploring algorithms that support a combined and efficient use of attribute and range filtering is also an important research topic.}
+Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.
+In this paper, we systematically evaluate hybrid query methods across multiple algorithms, vector databases, and libraries.
+We enrich dataset attributes, design diverse scenarios, and analyze overall performance.
+Experiments show that existing algorithms still have significant shortcomings in scenarios such as large-scale data, complex queries, and resource constraints.
+Attribute filtering lacks flexibility and Boolean logic support, while range filtering remains weak under high-recall or multi-attribute conditions.
+Some even underperform the baseline (e.g., Faiss).
+Future work will focus on improving the flexibility and efficiency of filtering algorithms and exploring unified algorithms that integrate attribute and range filtering.
+
+\begin{acks}
+This work was supported in part by NSFC Grant No. 62372194 and by 2025 Open Research Program of the MIIT Key Laboratory for Software Integrated Application and Testing \& Verification.
+
+\end{acks}
 

### 2025-11-04 VLDB2026/main.tex
Update main.tex

@@
 \usepackage{enumitem}
-
 \usepackage{multirow}
-
 \usepackage{graphicx}
-
 \usepackage{microtype}  %处理换行
@@
 \usepackage{caption}
-
 \usepackage{array}
@@
 \usepackage{times}
+\usepackage[a-2b,mathxmp]{pdfx}
 
@@
 % should be fine as it is
-\newcommand\vldbauthors{\authors}
+\newcommand\vldbauthors{Jiaxu Zhu, Jiayu Yuan, Kaiwen Yang, Xiaobao Chen, Shihuan Yu, Hongchang Lv, Yan Li, and Bolong Zheng}
 \newcommand\vldbtitle{\shorttitle} 
@@
 
-\usepackage[a-2b,mathxmp]{pdfx}
-
 \begin{document}
-	%\begin{sloppypar}
+
 	\title{An Experimental Evaluation of Hybrid Querying on Vectors}
@@
 
-	\author{Yan Li}
+	\author{Yan Li$^{*}$}
 	\affiliation{%
@@
 	}
-	\authornote{Yan Li is the corresponding author}
+
 	\author{Bolong Zheng}
@@
 	}
-	\authornote{Bolong Zheng is the corresponding author}
+	\authornote{Yan Li and Bolong Zheng are the corresponding authors}
 	%%
@@
 Recent studies demonstrate the significant practical value of hybrid queries, which integrate vector search with structured filters (e.g., attribute and range filtering) for refined retrieval.
-		However, current evaluations lack unified benchmarking standards and systematic assessment methodologies.
+However, current evaluations lack unified benchmark standards and systematic assessment methodologies.
 Existing studies either fail to cover mainstream algorithms or omit systematic comparisons or in-depth analysis on different methods.
@@
 Our study introduces 15 hybrid query algorithms and systematically classifies them based on multiple dimensions, such as index organization and filtering strategy, providing a reference for the categorization of hybrid queries.
-
 In the experiments, we construct standardized attribute and range sets for attribute filtering and range filtering, respectively, enabling a unified comparison of algorithms in terms of index construction efficiency and query performance.
@@
 Furthermore, we identify potential directions for improvement to address the current limitations of these algorithms.
-
 \end{abstract}
@@
 Some even underperform the baseline (e.g., Faiss).
-Future work will focus on improving the flexibility and efficiency of filtering algorithms and exploring unified algorithms that integrate attribute and range filtering.
+
+In the future, we will focus on improving the flexibility and efficiency of filtering algorithms and exploring unified algorithms that integrate attribute and range filtering.
 

### 2025-11-19 VLDB2026/main.tex
Update main.tex
ok

@@
 \usepackage{array}
-\usepackage[all]{nowidow}
-\usepackage{times}
+%\usepackage[all]{nowidow}
+
 \usepackage[a-2b,mathxmp]{pdfx}
@@
 % % paper-specific
-\newcommand\vldbdoi{XX.XX/XXX.XX}
-\newcommand\vldbpages{XXX-XXX}
+\newcommand\vldbdoi{10.14778/3773749.3773757}
+\newcommand\vldbpages{183 - 195}
 % issue-specific
@@
 	\subsection{Experimental Setup}
-	\subsubsection{Datasets}
-
-	\textcolor{black}{Our experiments employ 12 real-world datasets: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M\\~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
+	\textbf{Datasets. }
+	\textcolor{black}{Our experiments employ 12 real-world datasets: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}
 
@@
 
-	\subsubsection{Evaluation Metrics}
-
+	\textbf{Evaluation Metrics. }
 	To assess the overall performance of different algorithms, we adopt a multi-dimensional quantitative evaluation framework~\cite{compare}, including the following 5 core metrics:
@@
 
-	\subsubsection{\textcolor{black}{Setting}}
-
+	\textbf{Setting. }
 	We conduct most experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) featuring 256GB of RAM and 192 MiB of L3 cache.
@@
 }
-%	\textcolor{black}{
-%	\subsubsection{Parameters}
-%	In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings.
-For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.
-Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository.
-%}
 
@@
 	%4.2.1
-	\subsubsection{\textcolor{black}{Time and Space overhead}}
-	% \subsubsection{\textbf{Attribute Filtering}}
+	\textbf{Time and Space overhead. }
 	\begin{figure}[t]
@@
 	\end{figure}
-
 	\textcolor{black}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{black}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{black}{build peak memory and search peak memory}.
@@
 
-\textit{\textbf{Index construction time.}}
+\textit{\textbf{A. Index construction time. }}
 \textcolor{black}{On the medium-scale datasets (Figure~\ref{fig:build_time_comparison_query1} left), among the algorithms limited to single-threaded construction, PASE has the longest build time.
@@
 
-\textit{\textbf{Index size.}}
+\textit{\textbf{B. Index size. }}
 \textcolor{black}{
@@
 
-\textcolor{black}{\textit{\textbf{Peak memory.}}	
+\textit{\textbf{C. Peak memory. }
 We present the peak memory usage during index construction and query processing in Figure~\ref{fig:build_memory_mb_comparison} and Figure~\ref{fig:search_memory_mb_comparison}, respectively.
@@
 
-	\subsubsection{Performance Evaluation}
-
-	%4.2.2
-
+	\textbf{Performance Evaluation. }
 	We next evaluate the query performance of AF-ANN search methods, focusing on 3 main scenarios.
 
-	\textit{\textbf{Single-Attribute Index Construction and Single-Attribute Query.}}
+	\textit{\textbf{A. Single-Attribute Index Construction and Single-Attribute Query. }}
 	In this scenario, we construct the index using an attribute and apply filtering conditions on the same attribute.
@@
 
-	\textit{\textbf{Multi-Attribute Index Construction and Single-Attribute Query.}}
+	\textit{\textbf{B. Multi-Attribute Index Construction and Single-Attribute Query. }}
 	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query.
@@
 
-	\textit{\textbf{Multi-Attribute Index Construction and Multi-Attribute Query.}}  
+	\textit{\textbf{C. Multi-Attribute Index Construction and Multi-Attribute Query. }}  
 	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios.
@@
 
-	\subsubsection{Robustness}In the following, we evaluate the robustness of these algorithms.
-
-	\textit{\textbf{Attribute Distribution.}} To evaluate the impact of attribute distribution, we generate base and query attributes \textcolor{black}{on the SIFT dataset using four representative distributions: long-tail, normal, power-law, and uniform.}
+	\textbf{Robustness. }In the following, we evaluate the robustness of these algorithms.
+
+	\textit{\textbf{A.
+Attribute Distribution.
+}} To evaluate the impact of attribute distribution, we generate base and query attributes \textcolor{black}{on the SIFT dataset using four representative distributions: long-tail, normal, power-law, and uniform.}
 %	with four representative distributions—long-tail, normal, power-law, and uniform—across six datasets. 
@@
 When the curves converge closely, it demonstrates that the algorithm maintains stable performance when attribute distributions change.}
-%	Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
 
@@
 
-	\textit{\textbf{Single-Attribute Selectivity.}}
+	\textit{\textbf{B. Single-Attribute Selectivity. }}
 	In hybrid queries, varying attribute selectivity (AS) can significantly impact computational cost and query efficiency.
@@
 
-%	\subsubsection{Scalability Study}
-	\textit{\textbf{\textcolor{black}{Multi-Modal Queries.}}} \textcolor{black}{
+	\textit{\textbf{C. Multi-Modal Queries. }} 
 	We conduct experiments on two multi-modal  datasets Text2image-Mix and Text2image. 
-%This dataset contains image and text vectors and is a hybrid multi-modal dataset. 
 On Text2image-Mix dataset, as shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.
@@
 This is not actually a difficult query.
-%		Although this dataset mixes two modalities, the vector space distributions of different modalities often differ significantly.
-In practice, this means that the experiments effectively treat the image and text subsets as separate datasets, since the ground truths for each query belong to the same modality.
-Therefore, the performance on this dataset is similar to the results shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}.
 		In contrast, the Text2image dataset shown in Figure~\ref{fig:attribute-multimodal} is different.
@@
 To find the ground truths, algorithms typically need to examine more points, which leads to degraded performance.
-	}
-
-	\textit{\textbf{\textcolor{black}{Large-scale Dataset.}}} 
-	\textcolor{black}{As shown in the Figure~\ref{fig:attribute big dataset}, on the Deep100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
+
+	\textit{\textbf{D. Large-scale Dataset. }} 
+As shown in the Figure~\ref{fig:attribute big dataset}, on the Deep100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets.
 However, this also comes with significant memory overhead.
@@
 StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation.
-CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios.}
-
-	\textit{\textbf{\textcolor{black}{Different Hardware Environments.}}} 
-%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}.
-Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations.
-Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
+CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios.
+
+	\textit{\textbf{E. Different Hardware Environments. }} 
 	\textcolor{black}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}.
@@
 }
-	\subsubsection{\textcolor{black}{Time and Space overhead.}}
-
+
+	\textbf{Time and Space overhead. }
 	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
@@
 
-	\textit{\textbf{Index construction time.}}
+	\textit{\textbf{A. Index construction time. }}
 	\textcolor{black}{
@@
 
-	\textit{\textbf{Index size.}} 
+	\textit{\textbf{B. Index size. }} 
 	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size.
@@
 
-	\textcolor{black}{\textit{\textbf{Peak memory.}}  
+\textit{\textbf{C. Peak memory. }}  
 	As explained in the attribute filtering analysis, methods with larger index sizes (including the dataset) tend to exhibit higher peak memory consumption.
-As shown in Figure~\ref{fig:rangeFilter_build_memory_mb} and Figure~\ref{fig:rangeFilter_search_memory_mb}, range filtering also adheres to this pattern.}
+As shown in Figure~\ref{fig:rangeFilter_build_memory_mb} and Figure~\ref{fig:rangeFilter_search_memory_mb}, range filtering also adheres to this pattern.
 %	, while PASE deviates due to reasons discussed earlier
 
-	\textcolor{black}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism.
+{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism.
 Although the final index size remains relatively small, the peak memory usage increases significantly during both construction and search.
@@
 
-	\subsubsection{Performance Evaluation. }
-
+	\textbf{Performance Evaluation. }
 	In this experiment, we follow the query range definition adopted by prior work~\cite{HQI}.
@@
 
-	\subsubsection{Robustness}
-
-	\textit{\textbf{\textcolor{black}{Multi-Modal Queries.}}}
-	\textcolor{black}{
+	\textbf{Robustness. }In the following, we evaluate the robustness of these algorithms.
+
+	\textit{\textbf{A. Multi-Modal Queries. }}
 		Similar to attribute filtering, the performance of range filtering queries on the Text2image-Mix dataset (Figure~\ref{fig:range-multimodal}) is similar to the single-modality query performance (Figure~\ref{fig:exp_8_2}).
@@
 This is because most of these range query algorithms are graph-based, and such algorithms require more iterations to find true neighbors in OOD datasets.
-		}
-
-	\textit{\textbf{\textcolor{black}{Large-scale Dataset.}}} \textcolor{black}{As shown in the Figure~\ref{fig: range big dataset}, On the Deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
+
+	\textit{\textbf{B.
+Large-scale Dataset.
+}} \textcolor{black}{As shown in the Figure~\ref{fig: range big dataset}, On the Deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged.
 However, their high performance is achieved at the cost of extremely high memory consumption (Figure~\ref{fig:rangeFilter_search_memory_mb}).
@@
 
-	\textit{\textbf{\textcolor{black}{Different Hardware Environments.}}} 
+	\textit{\textbf{C. Different Hardware Environments. }} 
 	\textcolor{black}{Consistent with Section 4.2.3, we conduct range filtering experiments on the YT-Audio-Real dataset using two server configurations, with results presented in Figure~\ref{fig:range-cross-platform}.
@@
 
-%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
 	\section{DISCUSSION}
@@
 
-	\subsubsection{Attribute Filtering}
-
-\textcolor{black}{
-Overall, UNG, NHQ and FilteredDisk\\-ANN demonstrate strong performance.
+	\textbf{Attribute Filtering. }
+Overall, UNG, NHQ and Filtered Disk-ANN demonstrate strong performance.
 However, UNG suffers from performance degradation when the attribute count differs between indexing and querying.
 NHQ, due to its distance fusion design, also experiences performance drops when there is a significant mismatch in attribute numbers between indexing and querying, and its performance is sensitive to attribute distribution.
-}
 
@@
 
-	\subsubsection{Range Filtering}
-\textcolor{black}{
+	\textbf{Range Filtering. }
 	WinFilter achieves the best search performance but requires high time and memory resources during index construction.
@@
 When QPS and recall are not strict requirements, its basic variant, Vamana-WST, offers a more efficient alternative with significantly lower indexing overhead.
-		}
 
@@
 
-	\subsubsection{General Algorithm}
-\textcolor{black}{All of the following methods support both attribute filtering and range filtering.}
+	\textbf{General Algorithm. }
+All of the following methods support both attribute filtering and range filtering.
 
@@
 	\subsection{Challenges}
-	\subsubsection{Attribute Filtering}
+	\textbf{Attribute Filtering. }
 	Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency.
@@
 
-	\subsubsection{Range Filtering}
+	\textbf{Range Filtering. }
 	Except for DSG and UNIFY, most range filtering algorithms require the dataset to be pre-sorted before building the index.
@@
 	\section{CONCLUSION}
-%In this paper, we systematically evaluate various hybrid query methods, including multiple algorithms, vector databases, and libraries.
-We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm.
-Experiments show that existing algorithms still have significant shortcomings in scenarios such as large-scale data, complex queries, and resource constraints.
-There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms.
-Furthermore, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries.
-Notably, in some high-recall scenarios, some algorithms even perform worse than the baseline method (e.g., Faiss).
-In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction.
-Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.
+
 In this paper, we systematically evaluate hybrid query methods across multiple algorithms, vector databases, and libraries.
